### 2019-12-03 annotations/face_hands/analysis/analyze_goldset.Rmd
Add relevant csvs for turk hits, start gold set annotation analysis

---
title: "Face/Hand Annotations "
output: html_notebook
---

```{r setup, echo = FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(lmerTest)
library(viridis)

library(egg)
theme_set(theme_few())
```

```{r message=FALSE}
d.raw <- data.frame()
trial_indexes = seq(1,252,1)

files <- dir("turk_annotations/")
for (f in files) {
  jf <- paste("turk_annotations/",f,sep="")
  jd <- read_csv(jf)

  ## really not sure why there's this weird discrepancy for the last trial, but OK
  jd$`Answer.trial-252` = jd$`Answer.trial-252.label`

  for (trial_ind in trial_indexes){
    trial_data = data.frame(
      ## including HITId and HITTYpe
      this_response = eval(parse(text = paste0("jd$`Answer.trial-",trial_ind,"`"))),
      full_image_path = eval(parse(text = paste0("jd$Input.img_src",trial_ind))),
      trial_number = trial_ind,
      HITID = jd$HITId,
      HITTypeId =jd$HITTypeId
    )
    d.raw <- bind_rows(d.raw, trial_data)
  }
}

```

### 2019-12-03 annotations/face_hands/analysis/analyze_goldset.Rmd
Update annotations preprocessing script

@@
 
+## function to spit back category of sanity check images
+sanity_check_category = function(shorter_image_path){
+ ## I hate this function but I couldn't make it work without 
+## going down a regex rabbithole so here it is
+  hands = str_detect(shorter_image_path,'hands')
+  faces = str_detect(shorter_image_path,'faces')
+  none = str_detect(shorter_image_path,'none')
+  both = str_detect(shorter_image_path,'face-hands')
+
+ if (both==TRUE){
+   category = 'both'
+ }
+ else if (hands==TRUE){
+   category = 'hands'
+ }
+ else if (faces==TRUE){
+   category='faces'
+ }
+ else if (none==TRUE){
+  category='none'   
+ }
+ else{
+   category=NA
+  }
+
+ return(category)
+}
+
+```
+
+```{r}
 files <- dir("turk_annotations/")
@@
 
+### Pop out sanity check category from image path
+d.raw <- d.raw %>%
+    mutate(short_image_path = str_split_fixed(full_image_path,'/',7)[,7]) %>%
+    mutate(shorter_image_path = str_split_fixed(short_image_path,'.jpg',2)[,1]) %>%
+    mutate(sanity_check_category = sanity_check_category(shorter_image_path))
+
+### Recode responses into easier to munge format
+level_key <- c("Face(s) and Hand(s)" = "both", "Hand(s) only" = "hands", "Neither face(s) nor hands(s)" = "none", "Face(s) only" = "faces")
+
+d.raw$response=array()
+d.raw$response <- recode(d.raw$this_response, !!!level_key)
+
+### Break out sanity check images and look at discrepancies
+sanity_images <- d.raw %>%
+  filter(!is.na(sanity_check_category)) %>%
+  mutate(correct_sanity = response == sanity_check_category)
+
 ```
+
+```{r}
+
+```

### 2019-12-04 annotations/face_hands/analysis/analyze_goldset.Rmd
Updated analysis code to visualize disagreements, etc.

@@
       HITID = jd$HITId,
-      HITTypeId =jd$HITTypeId
+      HITTypeId =jd$HITTypeId,
+      WorkerID = jd$WorkerId
     )
@@
 
+test <- jd %>%
+  as_tibble()
 ### Pop out sanity check category from image path
@@
     mutate(shorter_image_path = str_split_fixed(short_image_path,'.jpg',2)[,1]) %>%
+    rowwise() %>%
     mutate(sanity_check_category = sanity_check_category(shorter_image_path))
@@
 ### Break out sanity check images and look at discrepancies
-sanity_images <- d.raw %>%
+sanity_images_wrong <- d.raw %>%
   filter(!is.na(sanity_check_category)) %>%
-  mutate(correct_sanity = response == sanity_check_category)
+  mutate(correct_sanity = response == sanity_check_category) %>%
+  filter(correct_sanity == FALSE)
 
+worker_check <- sanity_images_wrong %>%
+  group_by(WorkerID) %>%
+  summarize(wrong_sanity = n())
+
+## Compute agreement
+agreement <- d.raw %>%
+  group_by(short_image_path, full_image_path) %>%
+  summarize(num_responses = length(unique(this_response)))
+
+disagreement_examples <- agreement %>%
+  filter(num_responses==2)
+
+for (i in length(disagreement_examples$full_image_path)){
+  brxowseURL(disagreement_examples$full_image_path[i])
+}
+
+percent_disagree = sum(agreement$num_responses==2) / length(agreement$num_responses)
 ```
@@
 ```{r}
+dir.create(paste0('disagreements/'))
+for (i in seq(1,length(disagreement_examples$full_image_path),1)){
+  image_read(disagreement_examples$full_image_path[i]) %>%
+  image_append(stack = FALSE) %>%
+  image_write(file.path(paste0("disagreements/", disagreement_examples$short_image_path[i])))
+}
+
+example <- d.raw %>%
+  filter(short_image_path == "582-A_20130612_0830_02.mp4-2370.jpg")
 

### 2019-12-05 analysis/analysis_dec2019.Rmd
Merging detections with goldset, rendering examples

---
title: "Analysis_dec2019"
author: "Bria Long"
date: "12/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(egg)
theme_set(theme_few())
```

## Read in list of detections (takes forever)
```{r cars}
data_file = "../data/all_frames.csv"
detections =read.csv(data_file)
```

### Filter flipped videos
```{r}
right_side_up_file = "video_right-side-up.csv"
right_side_up =read.csv(right_side_up_file)

# get INCORRECT videos
flipped_videos <- right_side_up %>%
  filter(right_side_up==1)

d <- detections %>%
  filter(!vid_name %in% flipped_videos$video)
```

## Read in turk annotations
```{r}
## Need to be able to merge turk annotations with openpose detections but don't understand how vid_name and frame number map onto .jpg names in the image names -- assuming sample index is first b/c max val ~24K

turk_annotations = "../data/turk_annotations_dec5.csv" # first 20 turkers
gold_set = read.csv(turk_annotations)

## cleanup goldset annotations so we can merge
g <- gold_set %>%
  filter(is.na(sanity_check_category)) %>% # don't consider sanity check images here
  filter(!is.na(hands)) %>%
  filter(!is.na(faces)) %>%
  mutate(sample_ind = str_split_fixed(short_image_path,"-",3)[,1], frame_ind_temp = str_split_fixed(short_image_path,"-",3)[,3], vid_name_temp = str_split_fixed(short_image_path,"-",3)[,2]) %>%
  mutate(sample_ind = as.numeric(sample_ind), frame_ind = as.numeric(str_split_fixed(frame_ind_temp,".jpg",3)[,1])) %>%
  filter(!is.na(sample_ind))  %>%
  mutate(vid_name = str_split(vid_name_temp,".mp4")[[1]][1]) %>%
  filter(!vid_name %in% flipped_videos$video)

## standardize for merging with detectinos
g$vid_name = as.factor(g$vid_name)
g$frame = g$frame_ind

# what <- gold_set %>%
#   filter(is.na(sample_ind))
```

```{r}
# no_openpose <- merged %>%
#   filter(is.na(face_openpose))
# 
# ## never run on openpose?
# unique(no_openpose$vid_name)
# "A_20150507_3124_01"

merged <- g %>%
  left_join(detections)  %>%
  filter(!is.na(face_openpose))
```

```{r}
# Function to evaluate detectors
evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

m <- merged %>%
  select(vid_name, frame, response, hands, faces, sample_ind, face_openpose, hand_openpose, short_image_path, full_image_path ) %>%
  mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
  rowwise() %>%
  mutate(face_eval = evaluate_detector(faces, face_openpose), hand_eval = evaluate_detector(hands, hand_openpose))
```

### Now calculate prfs - these are SUPER bad and not sure what is up.
```{r}
 return_prf = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  return(c(p,r,f))
}

return_prf(m$face_eval)
return_prf(m$hand_eval)

```

### Let's sanity check -- only look at face images from gold set...
```{r}
faces_only <- m %>%
  filter(faces==TRUE)

# yep these are correct
unique(faces_only$response)

# let's look at the actual iamges
dir.create(paste0('faces_check/'))
for (i in seq(1,length(faces_only$full_image_path),1)){
  image_read(as.character(faces_only$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_check/", faces_only$short_image_path[i])))
}
```

## how about true positives on faces?
```{r}
faces_only_op_cor <- m %>%
  filter(faces == TRUE) %>%
  filter(face_openpose == TRUE)

# how about images where open pose got it? these should be most obvious
dir.create(paste0('faces_tp/'))
for (i in seq(1,length(faces_only_op_cor$full_image_path),1)){
  image_read(as.character(faces_only_op_cor$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_tp/", faces_only_op_cor$short_image_path[i])))
}

```

## how about false positives on facs?
```{r}
to_write <- m %>%
  filter(faces == FALSE) %>%
  filter(face_openpose == TRUE)

# how about images where open pose got it? these should be most obvious
dir.create(paste0('faces_fp/'))
for (i in seq(1,length(to_write$full_image_path),1)){
  image_read(as.character(to_write$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_fp/", to_write$short_image_path[i])))
}

```

## how about false negatives on faces?
```{r}
to_write <- m %>%
  filter(faces == TRUE) %>%
  filter(face_openpose == FALSE)

# how about images where open pose got it? these should be most obvious
dir.create(paste0('faces_fn/'))
for (i in seq(1,length(to_write$full_image_path),1)){
  image_read(as.character(to_write$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_fn/", to_write$short_image_path[i])))
}

```

# Examine age-trends in open-pose detections
### Make age bins
```{r}
### What ages do we have detections at?

hist(d$age_days)
## bin age by 10 days
bin_size = 30
min_age = min(d$age_days)
max_age = max(d$age_days)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)
```

### Make detections into logical vectors and compute "person" as either face/hand
```{r}
d$face_openpose = as.logical(d$face_openpose)
d$hand_openpose = as.logical(d$hand_openpose)
d$person_openpose = (as.logical(d$face_openpose) | as.logical(d$hand_openpose))
d$both_openpose = (as.logical(d$face_openpose) & as.logical(d$hand_openpose))

```

```{r}
summary_by_age <- d %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect, face_or_hand = sum(person_openpose)/ num_detect, face_and_hand = sum(both_openpose)/ num_detect)

# for geom_smooth
summary_by_age$age_day_bin=as.numeric(summary_by_age$age_day_bin)
```

### Make diagnotic plots
```{r}
# person by age
ggplot(summary_by_age, aes(x=age_day_bin, y=face_or_hand, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  geom_smooth() + 
  ylab('Proportion Face OR Hand') + 
  xlab('Age bin')

# person by age
ggplot(summary_by_age, aes(x=age_day_bin, y=face_and_hand, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  geom_smooth() + 
  ylab('Proportion Face AND Hand') + 
  xlab('Age bin')

# faces
p1 = ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  geom_smooth() + 
  ylab('Proportion Faces') + 
  xlab('Age bin')

# hands
p2 = ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  geom_smooth() + 
  ylab('Proportion Hands') + 
  xlab('Age bin')
```

### Key plot for fausey comparison
```{r}
## faces - hands
p3 = ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  geom_smooth() + 
  ylab('Proportion Faces - Hands') + 
  xlab('Age bin')

```

### 2019-12-05 annotations/face_hands/analysis/analyze_goldset.Rmd
update two main analysis scripts

--- 2019-12-03 annotations/face_hands/analysis/analyze_goldset.Rmd
@@
 library(viridis)
-
+library(rhdf5)
+library(magick)
 library(egg)
@@
 
-```{r message=FALSE}
+# Preprocessing
+
+### Go through raw data and put in dataframe
+```{r}
 d.raw <- data.frame()
 trial_indexes = seq(1,252,1)
+files <- dir("turk_annotations/")
+num_workers=20
 
-files <- dir("turk_annotations/")
 for (f in files) {
@@
       this_response = eval(parse(text = paste0("jd$`Answer.trial-",trial_ind,"`"))),
+      # this_response_label = eval(parse(text = paste0("jd$`Answer.trial-",trial_ind,".label`"))),
       full_image_path = eval(parse(text = paste0("jd$Input.img_src",trial_ind))),
@@
 
+d <- d.raw
+
 ```
+
+### Sometimes we get NAs and they end up in ".label fields", but not every trial has them (so it throws errors in a loop).
+I'm too tired to write an appropriate function so just leaving those NAs for now but the data is there.
+Starter code is below.
+```{r}
+
+# empty_labels = as.character(array(matrix(data=NA, nrow=1, ncol=num_workers)))
+# 
+# 
+# for (trial_ind in trial_indexes){
+#   field_to_check = paste0("jd$`Answer.trial-",trial_ind,".label`")
+#   if (!field_to_check %in% colnames(jd)){
+#     jd$(field_to_check) = empty_labels
+#   }
+# }
+
+# na_indexes = is.na(d$this_response)
+# d$this_response[na_indexes] = d$this_response_label[na_indexes]
+```
+
+### Write function to spit back category of sanity check images
+```{r message=FALSE}
+sanity_check_category = function(shorter_image_path){
+ ## I hate this function but I couldn't make it work without 
+## going down a regex rabbithole so here it is
+  hands = str_detect(shorter_image_path,'hands')
+  faces = str_detect(shorter_image_path,'faces')
+  none = str_detect(shorter_image_path,'none')
+  both = str_detect(shorter_image_path,'face-hands')
+
+ if (both==TRUE){
+   category = 'both'
+ }
+ else if (hands==TRUE){
+   category = 'hands'
+ }
+ else if (faces==TRUE){
+   category='faces'
+ }
+ else if (none==TRUE){
+  category='none'   
+ }
+ else{
+   category=NA
+  }
+
+ return(category)
+}
+```
+
+### Pop out sanity check category from image path
+```{r}
+d <- d %>%
+    mutate(short_image_path = str_split_fixed(full_image_path,'/',7)[,7]) %>%
+    mutate(shorter_image_path = str_split_fixed(short_image_path,'.jpg',2)[,1]) %>%
+    rowwise() %>%
+    mutate(sanity_check_category = sanity_check_category(shorter_image_path))
+```
+
+### Recode responses into easier to munge format
+```{r}
+level_key <- c("Face(s) and Hand(s)" = "both", "Hand(s) only" = "hands", "Neither face(s) nor hands(s)" = "none", "Face(s) only" = "faces")
+
+d$response=array()
+d$response <- recode(d$this_response, !!!level_key)
+
+get_face_hands =function(this_response,which_type){
+  if (is.na(this_response)){
+    face=NA
+    hand=NA
+  }
+  else if (this_response=='both'){
+    face=TRUE
+    hand=TRUE
+  }
+  else if (this_response=='faces'){
+    face=TRUE
+    hand=FALSE
+  }
+  else if (this_response=='hands'){
+    face=FALSE
+    hand=TRUE
+  }
+  else if (this_response=='none'){
+    face=FALSE
+    hand=FALSE
+  }
+  else {
+    face=NA
+    hand=NA
+  }
+
+  if (which_type=='faces'){
+    return(face)
+  }
+  else if (which_type=='hands'){
+    return(hand)
+  }
+}
+
+d <- d %>%
+  mutate(hands= get_face_hands(response,'hands'), faces = get_face_hands(response,'faces')) %>%
+  mutate(sanity_hands = get_face_hands(sanity_check_category,'hands'), sanity_faces = get_face_hands(sanity_check_category,'faces'))
+```
+
+### Break out sanity check images and filter ad workers
+```{r}
+sanity_images_wrong <- d %>%
+  filter(!is.na(sanity_check_category)) %>%
+  mutate(correct_sanity = response == sanity_check_category) %>%
+  mutate(correct_faces = (faces == sanity_hands), correct_hands = (hands == sanity_hands)) %>%
+  filter(correct_sanity == FALSE)
+
+bad_workers <- sanity_images_wrong %>%
+  group_by(WorkerID) %>%
+  summarize(wrong_sanity = n()) %>%
+  filter(wrong_sanity > 6) # more than 50% wrong
+
+d.filtered <- d %>%
+  filter(!WorkerID %in% bad_workers$WorkerID)
+```
+
+### Write out csv for use in analysis
+```{r}
+write_csv(d.filtered,'turk_annotations_dec5.csv')
+```
+
+```{r}
+## Compute agreement -- not using since only 1 worker per set right now
+# agreement <- d.raw %>%
+#   group_by(short_image_path, full_image_path) %>%
+#   summarize(workers_per_image = length(this_response), num_responses = length(unique(this_response)), face_agree = (faces[1] == faces[2]), hand_agree = (hands[1]==hands[2]))
+# 
+# disagreement_examples <- agreement %>%
+#   filter(workers_per_image==2)
+
+# for (i in length(disagreement_examples$full_image_path)){
+#   brxowseURL(disagreement_examples$full_image_path[i])
+# }
+
+# percent_disagree = sum(agreement$num_responses==2) / length(agreement$num_responses)
+
+# dir.create(paste0('disagreements_take2/'))
+# for (i in seq(1,length(disagreement_examples$full_image_path),1)){
+#   image_read(disagreement_examples$full_image_path[i]) %>%
+#   image_append(stack = FALSE) %>%
+#   image_write(file.path(paste0("disagreements_take2/", disagreement_examples$short_image_path[i])))
+# }
+
+# example <- d.raw %>%
+#   filter(short_image_path == "582-A_20130612_0830_02.mp4-2370.jpg")
+```

### 2019-12-12 annotations/face_hands/analysis/preprocess_turk_segmentations.Rmd
rename/organize turk preprocessing scripts

---
title: "Preprocess turk annotations ="
output: html_notebook
---

```{r setup, echo = FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(lmerTest)
library(viridis)
library(magick)
library(egg)
library(jsonlite)
theme_set(theme_few())
```

```{r}

```
# Preprocessing

```{r}
f <- dir("turk_annotations_segmentation/")
jf <- paste("turk_annotations_segmentation/",f,sep="")
jd <- read_csv(jf)

d.raw <- data.frame()
trial_indexes = seq(1,200,1)
  for (trial_ind in trial_indexes){
    ## get annotation and see if empty
    this_annotation = jd$Answer.annotatedResult.boundingBoxes[trial_ind]
    cleaned_annotation = fromJSON(this_annotation)

    # if there was an annotation
    if (length(cleaned_annotation)>1){

        ## for each thing that was annotated, new row
        for (annotation_ind in seq(1,length(cleaned_annotation$label),1)){
              trial_data = data.frame(
              label = cleaned_annotation$label[annotation_ind],
              height = cleaned_annotation$height[annotation_ind],
              width = cleaned_annotation$width[annotation_ind],
              left = cleaned_annotation$left[annotation_ind],
              top = cleaned_annotation$top[annotation_ind],
              full_image_path = jd$Input.img_src1[trial_ind],
              trial_number = trial_ind,
              HITID = jd$HITId[trial_ind],
              HITTypeId =jd$HITTypeId[trial_ind],
              WorkerID = jd$WorkerId[trial_ind]
              )
        d.raw <- bind_rows(d.raw, trial_data)
        } # for annotation_ind
    } 
    ## if nothing was annotated
    else{
    trial_data = data.frame(
          ## including HITId and HITTYpe
          label = 'None',
          height = NA,
          width = NA,
          left = NA,
          top = NA,
          full_image_path = jd$Input.img_src1[trial_ind],
          trial_number = trial_ind,
          HITID = jd$HITId[trial_ind],
          HITTypeId =jd$HITTypeId[trial_ind],
          WorkerID = jd$WorkerId[trial_ind]
          )
     d.raw <- bind_rows(d.raw, trial_data)
    }
}
```

## look at distribution of images done per worker
```{r}
worker_summary <- jd %>%
  group_by(WorkerId) %>%
  summarize(count_images = n(), avg_time = mean(WorkTimeInSeconds))
```

```{r}
total_area = jd$Answer.annotatedResult.inputImageProperties.height[1] * jd$Answer.annotatedResult.inputImageProperties.width[1]
d.raw <- d.raw %>%
  mutate(detection_area = (height*width)/total_area)

## plot detection area by detection type
ggplot(d.raw, aes(x=label, y=log(detection_area))) +
  geom_boxplot()

## faces tend to appear towards the top of the image (i.e. 0 pixel coordinates, or upper visual field)
ggplot(d.raw, aes(x=label, y=top)) +
  geom_boxplot()

```

### Write out csv for use in analysis
```{r}
write_csv(d.raw,'turk_segmentations_dec12.csv')
```

### 2019-12-12 analysis/analysis_dec2019.Rmd
update two main analysis scripts
update main analysis script

@@
 library(viridis)
+library(magick)
 library(egg)
@@
 data_file = "../data/all_frames.csv"
-detections =read.csv(data_file)
+detections=read.csv(data_file) 
 ```
 
-### Filter flipped videos
+### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
 ```{r}
-right_side_up_file = "video_right-side-up.csv"
+right_side_up_file = "../data/video_right-side-up.csv"
 right_side_up =read.csv(right_side_up_file)
@@
 
-d <- detections %>%
-  filter(!vid_name %in% flipped_videos$video)
+# d <- detections %>%
+#   filter(!vid_name %in% flipped_videos$video)
 ```
 
-## Read in turk annotations
+### Read in turk annotations (hand/face present only here, ~4K images)
 ```{r}
-## Need to be able to merge turk annotations with openpose detections but don't understand how vid_name and frame number map onto .jpg names in the image names -- assuming sample index is first b/c max val ~24K
-
-turk_annotations = "../data/turk_annotations_dec5.csv" # first 20 turkers
+turk_annotations = "../data/turk_annotations_dec5.csv" # 20 turkers who did ~250 frames each
 gold_set = read.csv(turk_annotations)
 
-## cleanup goldset annotations so we can merge
+## cleanup these goldset annotations so we can merge
 g <- gold_set %>%
@@
   filter(!is.na(sample_ind))  %>% 
-  mutate(vid_name = str_split(vid_name_temp,".mp4")[[1]][1]) %>%
-  filter(!vid_name %in% flipped_videos$video)
+  rowwise() %>%
+  mutate(vid_name_short = str_split(vid_name_temp,"[.]")[[1]][1]) %>%
+  mutate(vid_name = str_split_fixed(vid_name_temp,".mp4",2)[,1]) %>% ## includes .avi as does detections structure
+  filter(!vid_name_short %in% flipped_videos$video)
+
+# length(unique(g$vid_name))
 
 ## standardize for merging with detectinos
-g$vid_name = as.factor(g$vid_name)
+# g$vid_name = as.factor(g$vid_name)
 g$frame = g$frame_ind
 
-# what <- gold_set %>%
-#   filter(is.na(sample_ind))
+# double_check <- gold_set %>%
+#   filter(is.na(sample_ind)) -- there's a video that doesn't have detections that is in the gold set
 ```
 
+### Merge gold set turk annotations and openpose detections
 ```{r}
@@
 
+### Can also import segmentations (this is only a small sample of 200 frames right now)
+```{r}
+turk_annotations_seg = "../data/turk_segmentations_dec12.csv" # 20 turkers who did ~250 frames each
+gold_set_seg = read.csv(turk_annotations_seg)
+g_seg <- gold_set_seg %>%
+  mutate(hands_seg = (label %in% c("Child hand","Adult hand")), face_seg = (label == "Face")) %>%
+  mutate(short_image_path = str_split_fixed(full_image_path,'/',7)[,7]) %>%
+  mutate(sample_ind = str_split_fixed(short_image_path,"-",3)[,1], frame_ind_temp = str_split_fixed(short_image_path,"-",3)[,3], vid_name_temp = str_split_fixed(short_image_path,"-",3)[,2]) %>%
+  mutate(sample_ind = as.numeric(sample_ind), frame_ind = as.numeric(str_split_fixed(frame_ind_temp,".jpg",3)[,1])) %>%
+  rowwise() %>%
+  mutate(vid_name_short = str_split(vid_name_temp,"[.]")[[1]][1]) %>%
+  mutate(vid_name = str_split_fixed(vid_name_temp,".mp4",2)[,1])
+
+## And merge with detections
+merged_g_seg <- g_seg %>%
+  mutate(frame = frame_ind) %>%
+  left_join(detections)
+```
+
+### Write functions to compute TP/FN/TN/FP
 ```{r}
@@
 
+```
+
+## Compute TP/FN/TN/FP on dataset for both faces and hands
+```{r}
 m <- merged %>%
-  select(vid_name, frame, response, hands, faces, sample_ind, face_openpose, hand_openpose, short_image_path, full_image_path ) %>%
+  select(vid_name, frame, response, hands, faces, sample_ind, face_openpose, hand_openpose, short_image_path, full_image_path, age_days, child_id) %>%
   mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
@@
   mutate(face_eval = evaluate_detector(faces, face_openpose), hand_eval = evaluate_detector(hands, hand_openpose))
+
+### on segmentation turk hits as well...
+m_seg <- merged_g_seg %>%
+  select(vid_name, frame, label, hands_seg, face_seg, sample_ind, face_openpose, hand_openpose, short_image_path, full_image_path, age_days, child_id) %>%
+  mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
+  rowwise() %>%
+  mutate(face_eval = evaluate_detector(face_seg, face_openpose), hand_eval = evaluate_detector(hands_seg, hand_openpose))
+
 ```
 
-### Now calculate prfs - these are SUPER bad and not sure what is up.
+### Write functions for returning prfs/f-scores
 ```{r}
- return_prf = function(eval){
+ return_prf_short = function(eval){
   tp=sum(eval == "TP")
@@
 
+ return_fscore = function(eval){
+  tp=sum(eval == "TP")
+  fp=sum(eval == "FP")
+  fn=sum(eval == "FN")
+  p = tp / (tp + fp)
+  r = tp / (tp + fn)
+  f=( 2 * p * r )/ (p + r)
+  return(f)
+}
+```
+
+### Load ketan's annotation and get prfs
+```{r}
+load('preprocessed_data/ketan_gold_sample.RData')
+# 
+ ketan_gold_out <- ketan_gold %>%
+   rowwise() %>%
+   mutate(vid_name = str_split_fixed(vid_name,".mp4",2)[,1])%>%
+   mutate(vid_name_short = str_split(vid_name,"[.]")[[1]][1]) %>%
+   mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
+   rename(face_present_ketan = face_present, hand_present_ketan = hand_present)
+
+ out <- ketan_gold_out %>%
+   mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose))
+
+return_prf_short(out$face_eval_ketan)
+return_prf_short(out$hand_eval_ketan)
+```
+
+### How do these f-scores change when we get rid of the weird videos?
+```{r}
+out_no_flipped <- ketan_gold_out %>%
+  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose))  %>%
+  filter(!vid_name_short %in% flipped_videos$video)
+
+return_prf_short(out_no_flipped$face_eval_ketan)
+return_prf_short(out_no_flipped$hand_eval_ketan)
+
+```
+
+### How much do Ketan and turkers agree? 
+```{r}
+ketan_vs_turk <- ketan_gold_out %>%
+  left_join(m) %>%
+  mutate(turk_vs_ketan_face = (face_present_ketan == faces))
+
+##
+agreement = mean(ketan_vs_turk$turk_vs_ketan_face, na.rm=TRUE)
+num_examples = sum(!is.na(ketan_vs_turk$turk_vs_ketan_face))
+
+```
+Ketan & turkers agreed `r agreement` percent of the time for the `r num_examples` we tested.
+
+### Merge age/child information from other dataframe back into ketan's gold set by frame/vid_name
+```{r}
+vid_info <- detections %>%
+  select(vid_name, frame, age_days, child_id)
+
+d <- ketan_gold_out %>%
+  left_join(vid_info, by=c("vid_name","frame"))
+```
+
+### What ages do we have detections at?
+```{r}
+# hist(d$age_days)
+## bin age by 10 days
+bin_size = 10
+min_age = min(d$age_days)
+max_age = max(d$age_days)
+bin_starts = seq(min_age-1, max_age+1,bin_size)
+bins = c(bin_starts, max_age)
+d <- d %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
+
+```
+
+### Write function to return prfs and num samples so we can look at changes by age/child
+```{r}
+ return_prf = function(eval){
+  tp=sum(eval == "TP")
+  fp=sum(eval == "FP")
+  fn=sum(eval == "FN")
+  p = tp / (tp + fp)
+  r = tp / (tp + fn)
+  f=( 2 * p * r )/ (p + r)
+  num_detect = length(eval)
+  out <- data.frame(p,r,f,num_detect)
+  return(out)
+ }
+
+prf_by_age <- d %>%
+  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose)) %>%
+  group_by(age_day_bin, child_id) %>%
+  do(return_prf(.$face_eval_ketan))
+```
+
+```{r}
+face_vs_hands_goldset <- d %>%
+  group_by(child_id, age_day_bin) %>%
+  summarize(prop_faces = sum(face_present_ketan) / length(face_present_ketan), prop_hands = sum(hand_present_ketan) / length(hand_present_ketan), num_detect = length(face_present_ketan)) %>%
+  mutate(faces_vs_hands = prop_faces - prop_hands)
+
+face_vs_hands_goldset$age_day_bin  = as.numeric(face_vs_hands_goldset$age_day_bin)
+
+ggplot(face_vs_hands_goldset, aes(x=age_day_bin, y=faces_vs_hands, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth()
+
+```
+
+```{r}
+prf_by_age$age_day_bin = as.numeric(prf_by_age$age_day_bin)
+
+p1  = ggplot(prf_by_age, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth()
+
+p2 = ggplot(prf_by_age, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth()
+
+p3 =ggplot(prf_by_age, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth()
+#
+ggarrange(p1,p2,p3)
+
+```
+
+```{r}
 return_prf(m$face_eval)
 return_prf(m$hand_eval)
+
+f_scores_by_age_faces <- m %>%
+  group_by(age_days, child_id) %>%
+  summarize(f_score_faces = return_fscore(face_eval), num_detect = length(face_eval))
+
+ggplot(f_scores_by_age_faces, aes(x=age_days, y=f_score_faces, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth()
+```
+
+```{r}
+f_scores_by_age_hands <- m %>%
+  group_by(age_days, child_id) %>%
+  summarize(f_score_hands = return_fscore(hand_eval), num_detect = length(hand_eval))
+
+ggplot(f_scores_by_age_hands, aes(x=age_days, y=f_score_hands, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth()
 
@@
 ### Make age bins
-```{r}
-### What ages do we have detections at?
-
-hist(d$age_days)
-## bin age by 10 days
-bin_size = 30
-min_age = min(d$age_days)
-max_age = max(d$age_days)
-bin_starts = seq(min_age-1, max_age+1,bin_size)
-bins = c(bin_starts, max_age)
-```
 
@@
 ```{r}
-summary_by_age <- d %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+summary_by_age <- detections %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/bin_size,1))) %>%
   group_by(age_day_bin, child_id) %>%
@@
 summary_by_age$age_day_bin=as.numeric(summary_by_age$age_day_bin)
+
 ```

### 2019-12-14 src/check_frame_urls.R
export frames for mturk classification and start to extract openpose keypoints in R

@@ -1,0 +1,13 @@
+require("RCurl")
+
+frame_urls = read.csv("~/Documents/GitHub/headcam-algo/src/data/frame_urls2.csv")
+
+urls = as.character(frame_urls$img_src)
+
+startTime = Sys.time()
+exists = lapply(urls, url.exists)
+stopTime = Sys.time()
+# how long to check all of them? (maybe related to slow load time?)
+stopTime - startTime
+
+missing_inds = which(exists==F)

### 2019-12-14 src/get_openpose_bounding_boxes.R

@@ -1,0 +1,100 @@
+require(stringr)
+
+# should run on master_frames_openpose.h5, but for now use gold set
+frame_size = c(640,480) # pixels; keypoint x,y coords are normalized 0-1, but go out of frame occasionally
+# min=-.22, max=1.16
+load("ketan_gold_sample.RData") 
+
+# bounding box should be x1 = min(x), y1=min(y), x2=max(x), y2=max(x)
+
+ketan_gold$face_openpose
+ketan_gold$face_keypoints
+ketan_gold$hand_left_keypoints
+ketan_gold$hand_left_keypoints
+
+# what are "face_keypoints_tuple"  and "pose_keypoints_tuple" ?
+
+table(ketan_gold$hand_openpose, ketan_gold$hand_openpose_wrist)
+
+#kg = tibble(ketan_gold)
+
+face_inds <- which(ketan_gold$face_openpose==1)
+
+fd <- ketan_gold[face_inds,] # or do on all -- no keypoints = "[]"
+
+#fd$face_keys <- vapply(fd$face_keypoints, paste, collapse = ", ", character(1L))
+
+get_hand_keypoints <- function(hd, hand="left") {
+  col_kp = paste0("hand_",hand,"_keypoints")
+  col_num = paste0("num_",hand,"_hands")
+  #hd$hand_keys = NA
+  hd[,col_kp] = gsub("\\[|\\]", "", hd[,col_kp]) # removes all left or right brackets
+  hd[,col_num] = NA
+  #which(str_length(hd
+  hkp = list()
+  for(i in 1:nrow(hd)) {
+    # no keypoints="[]", but what does it mean if all the keypoints are 0 ??
+    if(str_length(hd[i,col_kp])==0) {
+      hd[i,col_num] = 0
+    } else {
+      # if there are multiple people, these are of the form [[1,2,..,63], [64,65,..,127], ..]
+      vals = eval(parse(text=paste('c(',hd[i,col_kp],')')))
+      if(length(vals) > 63) {
+        num_hands = length(vals)/63
+        hd[i,col_num] = num_hands
+        print(paste(num_hands, "hands found"))
+        ll = list()
+        for(h in 1:num_hands) {
+          startind = 63*(h-1)+1
+          endind = 63*h
+          ll[[h]] = vals[startind:endind]
+        }
+      } else {
+        ll = list(vals)
+      }
+      #print(ll)
[…]

### 2019-12-14 src/mturkify_frame_list.R

@@ -6,26 +6,29 @@ gold = list.files("data/gold_standard")
 set.seed(123)
 gold = sample(gold, length(gold), replace=F)
 gold_urls = paste(base_url,gold,sep='')
+gold_urls = gold_urls[c(1,2,4,5,9)]
 
-d = read.csv("data/frame_urls2.csv")
+d = read.csv("data/frame_urls.csv")
 
-w = matrix(d$img_src, nrow=100, byrow=F)
+# 50 images per user = 480 turkers
 
-dim(w) # 100 Ss x 240 images (4min @ 1 rating/sec)
+w = matrix(d$img_src, nrow=480, byrow=F)
 
-gold_inds = 1:12 * 20
+dim(w) # 480 Ss x 50 images (4min @ 1 rating/sec)
 
-wg = cbind(w[,1:20], rep(gold_urls[1], nrow(w))) # 1:20; ni
+gold_inds = 1:5 * 10
+
+wg = cbind(w[,1:10], rep(gold_urls[1], nrow(w))) # 1:20; ni
 for(i in 2:length(gold_inds)) {
-  start_i = gold_inds[i-1] + 1 # 21, 41, 
+  start_i = gold_inds[i-1] + 1 # 11, 21, 
   end_i = gold_inds[i]
   wg = cbind(wg, w[,start_i:end_i], rep(gold_urls[i], nrow(w)))
 }
 
-dim(wg) # 100 x 252
+dim(wg) # 480 x 55
 wg = data.frame(wg)
 names(wg) = paste("img_src", 1:ncol(wg), sep='')
-write_csv(wg, "data/frame_urls_100x252.csv")
+write_csv(wg, "data/frame_urls_480x55.csv")
 
 # gold_standard images at column 21, 42, 63, 84, .., 252
 # col%%21 == 0

### 2019-12-14 src/get_openpose_bounding_boxes.R
better output

@@ -16,21 +16,21 @@ ketan_gold$hand_left_keypoints
 
 table(ketan_gold$hand_openpose, ketan_gold$hand_openpose_wrist)
 
-#kg = tibble(ketan_gold)
 
 face_inds <- which(ketan_gold$face_openpose==1)
-
-fd <- ketan_gold[face_inds,] # or do on all -- no keypoints = "[]"
+#fd <- ketan_gold[face_inds,] # or do on all -- no keypoints = "[]"
 
 #fd$face_keys <- vapply(fd$face_keypoints, paste, collapse = ", ", character(1L))
 
-get_hand_keypoints <- function(hd, hand="left") {
+all = list(dat=ketan_gold)
+
+get_hand_keypoints <- function(all, hand="left") {
+  hd = all$dat
   col_kp = paste0("hand_",hand,"_keypoints")
   col_num = paste0("num_",hand,"_hands")
   #hd$hand_keys = NA
   hd[,col_kp] = gsub("\\[|\\]", "", hd[,col_kp]) # removes all left or right brackets
   hd[,col_num] = NA
-  #which(str_length(hd
   hkp = list()
   for(i in 1:nrow(hd)) {
     # no keypoints="[]", but what does it mean if all the keypoints are 0 ??
@@ -42,7 +42,7 @@ get_hand_keypoints <- function(hd, hand="left") {
       if(length(vals) > 63) {
         num_hands = length(vals)/63
         hd[i,col_num] = num_hands
-        print(paste(num_hands, "hands found"))
+        #print(paste(num_hands, "hands found"))
         ll = list()
         for(h in 1:num_hands) {
           startind = 63*(h-1)+1
@@ -52,49 +52,56 @@ get_hand_keypoints <- function(hd, hand="left") {
       } else {
         ll = list(vals)
       }
-      #print(ll)
-      #fd[i,]$face_keys = ll
       hkp[[i]] = ll
     }
   }
-  return(list(dat=hd, keypoints=hkp))
+  all$dat = hd
+  all[[paste0(hand,"_keys")]] = hkp
+  return(all)
 }
 
 
-get_face_keypoints <- function(fd) {
+get_face_keypoints <- function(all) {
+  fd = all$dat
   fd$face_keys = NA
   fd$face_keypoints = gsub("\\[|\\]", "", fd$face_keypoints) # removes all left or right brackets
-  fd$num_faces = 1
+  fd$num_faces = NA
   fkp = list()
[…]

### 2019-12-14 analysis/analysis_dec2019.Rmd
Update main analysis script

--- 2019-12-05 analysis/analysis_dec2019.Rmd
@@
 ---
-title: "Analysis_dec2019"
+title: "SAYCAM_analysis_dec2019"
 author: "Bria Long"
@@
 
+# Basic data loading and setup
+## Packages
 ```{r setup, include=FALSE}
@@
 library(viridis)
+library(magick)
+library(stringr)
 library(egg)
@@
 
-## Read in list of detections (takes forever)
-```{r cars}
+## Read in data 
+### Could do list of detections (takes forever, skipping)
+```{r eval=FALSE}
 data_file = "../data/all_frames.csv"
-detections =read.csv(data_file)
+detections=read.csv(data_file) 
 ```
 
-### Filter flipped videos
+### Instead load in detections and ketan's gold set annotations from preprocessed Rdata files
 ```{r}
-right_side_up_file = "video_right-side-up.csv"
+load('../data/openpose_detections.RData')
+load('../data/ketan_gold_sample.RData')
+```
+### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
+```{r}
+right_side_up_file = "../data/video_right-side-up.csv"
 right_side_up =read.csv(right_side_up_file)
@@
   filter(right_side_up==1)
-
-d <- detections %>%
-  filter(!vid_name %in% flipped_videos$video)
 ```
 
-## Read in turk annotations
+### Read in turk anotation data  and merge
+#### First read in hand/face present only here, ~4K images
 ```{r}
-## Need to be able to merge turk annotations with openpose detections but don't understand how vid_name and frame number map onto .jpg names in the image names -- assuming sample index is first b/c max val ~24K
-
-turk_annotations = "../data/turk_annotations_dec5.csv" # first 20 turkers
+turk_annotations = "../data/turk_annotations_dec5.csv" # 20 turkers who did ~250 frames each
 gold_set = read.csv(turk_annotations)
 
-## cleanup goldset annotations so we can merge
+## cleanup these goldset annotations so we can merge
 g <- gold_set %>%
@@
   filter(!is.na(sample_ind))  %>% 
-  mutate(vid_name = str_split(vid_name_temp,".mp4")[[1]][1]) %>%
-  filter(!vid_name %in% flipped_videos$video)
+  rowwise() %>%
+  mutate(vid_name_short = str_split(vid_name_temp,"[.]")[[1]][1]) %>%
+  mutate(vid_name = str_split_fixed(vid_name_temp,".mp4",2)[,1]) %>% ## includes .avi as does detections structure
+  filter(!vid_name_short %in% flipped_videos$video)
+
+# length(unique(g$vid_name))  (checking this is >1)
 
 ## standardize for merging with detectinos
-g$vid_name = as.factor(g$vid_name)
 g$frame = g$frame_ind
 
-# what <- gold_set %>%
-#   filter(is.na(sample_ind))
 ```
 
+### Now merge gold set turk annotations and openpose detections
 ```{r}
@@
 
+### Could also import segmentations (this is only a small sample of 200 frames right now)
+```{r eval=FALSE}
+turk_annotations_seg = "../data/turk_segmentations_dec12.csv" # 20 turkers who did ~250 frames each
+gold_set_seg = read.csv(turk_annotations_seg)
+g_seg <- gold_set_seg %>%
+  mutate(hands_seg = (label %in% c("Child hand","Adult hand")), face_seg = (label == "Face")) %>%
+  mutate(short_image_path = str_split_fixed(full_image_path,'/',7)[,7]) %>%
+  mutate(sample_ind = str_split_fixed(short_image_path,"-",3)[,1], frame_ind_temp = str_split_fixed(short_image_path,"-",3)[,3], vid_name_temp = str_split_fixed(short_image_path,"-",3)[,2]) %>%
+  mutate(sample_ind = as.numeric(sample_ind), frame_ind = as.numeric(str_split_fixed(frame_ind_temp,".jpg",3)[,1])) %>%
+  rowwise() %>%
+  mutate(vid_name_short = str_split(vid_name_temp,"[.]")[[1]][1]) %>%
+  mutate(vid_name = str_split_fixed(vid_name_temp,".mp4",2)[,1])
+
+## And merge with detections
+merged_g_seg <- g_seg %>%
+  mutate(frame = frame_ind) %>%
+  left_join(detections)
+```
+
+# Evaluate overall detector performance
+
+## Set-up necessary for p/r/f calculations 
+### Write functions to compute TP/FN/TN/FP
 ```{r}
@@
 
+```
+
+### Compute TP/FN/TN/FP on dataset for both faces and hands
+```{r}
 m <- merged %>%
-  select(vid_name, frame, response, hands, faces, sample_ind, face_openpose, hand_openpose, short_image_path, full_image_path ) %>%
+  select(vid_name, frame, response, hands, faces, sample_ind, face_openpose, hand_openpose, short_image_path, full_image_path, age_days, child_id) %>%
   mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
@@
 
-### Now calculate prfs - these are SUPER bad and not sure what is up.
+### Compute TP/FN/TN/FP on dataset for both faces and hands from segmentation hits (skipping for now)
+```{r eval=FALSE}
+m_seg <- merged_g_seg %>%
+  select(vid_name, frame, label, hands_seg, face_seg, sample_ind, face_openpose, hand_openpose, short_image_path, full_image_path, age_days, child_id) %>%
+  mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
+  rowwise() %>%
+  mutate(face_eval = evaluate_detector(face_seg, face_openpose), hand_eval = evaluate_detector(hands_seg, hand_openpose))
+
+```
+
+### Write functions for returning prfs/f-scores
 ```{r}
- return_prf = function(eval){
+ return_prf_short = function(eval){
   tp=sum(eval == "TP")
@@
 
-return_prf(m$face_eval)
-return_prf(m$hand_eval)
+ return_fscore = function(eval){
+  tp=sum(eval == "TP")
+  fp=sum(eval == "FP")
+  fn=sum(eval == "FN")
+  p = tp / (tp + fp)
+  r = tp / (tp + fn)
+  f=( 2 * p * r )/ (p + r)
+  return(f)
+}
+```
+
+### Preprocess ketan's annotation, evaluate, and get prfs
+```{r}
+ ketan_gold_out <- ketan_gold %>%
+   rowwise() %>%
+   mutate(vid_name = str_split_fixed(vid_name,".mp4",2)[,1])%>%
+   mutate(vid_name_short = str_split(vid_name,"[.]")[[1]][1]) %>%
+   mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
+   rename(face_present_ketan = face_present, hand_present_ketan = hand_present)
+
+ out <- ketan_gold_out %>%
+   mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose))
+```
+
+## Detector evaluation results
+### Faces (full 24K)
+```{r}
+return_prf_short(out$face_eval_ketan)
+```
+### Faces (full 24K)
+```{r}
+return_prf_short(out$hand_eval_ketan)
+```
+
+### How do f-scores from ketan's gold set hange when we get rid of the flipped videos?
+```{r}
+out_no_flipped <- ketan_gold_out %>%
+  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose))  %>%
+  filter(!vid_name_short %in% flipped_videos$video)
+```
+
+### Faces (filtered)
+```{r}
+return_prf_short(out_no_flipped$face_eval_ketan)
+```
+### Hands (filtered)
+```{r}
+return_prf_short(out_no_flipped$hand_eval_ketan)
+```
+
+### How well do ketan and turkers agree? 
+```{r}
+ketan_vs_turk <- ketan_gold_out %>%
+  left_join(m) %>%
+  mutate(turk_vs_ketan_face = (face_present_ketan == faces))
+
+##
+agreement = mean(ketan_vs_turk$turk_vs_ketan_face, na.rm=TRUE)
+num_examples = sum(!is.na(ketan_vs_turk$turk_vs_ketan_face))
+
+```
+Ketan & turkers agreed `r agreement` percent of the time for the `r num_examples` we tested.
+
+## Analyze how detector performance might vary by child/age
+### First merge age/child information from other dataframe back into ketan's gold set by frame/vid_name
+```{r}
+vid_info <- detections %>%
+  select(vid_name, frame, age_days, child_id)
+
+d <- ketan_gold_out %>%
+  filter(!vid_name_short %in% flipped_videos$video) %>%
+  left_join(vid_info, by=c("vid_name","frame"))
+```
+
+### Bin gold set performance every so often (e.g., 10 days)
+```{r}
+bin_size = 10
+min_age = min(d$age_days)
+max_age = max(d$age_days)
+bin_starts = seq(min_age-1, max_age+1,bin_size)
+bins = c(bin_starts, max_age)
+d <- d %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
 
@@
 
-### Let's sanity check -- only look at face images from gold set...
+### Look at prf changes by age/child
 ```{r}
-faces_only <- m %>%
-  filter(faces==TRUE)
+ return_prf = function(eval){
+  tp=sum(eval == "TP")
+  fp=sum(eval == "FP")
+  fn=sum(eval == "FN")
+  p = tp / (tp + fp)
+  r = tp / (tp + fn)
+  f=( 2 * p * r )/ (p + r)
+  num_detect = length(eval)
+  out <- data.frame(p,r,f,num_detect)
+  return(out)
+ }
 
-# yep these are correct
-unique(faces_only$response)
+prf_by_age_faces <- d %>%
+  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose)) %>%
+  group_by(age_day_bin, child_id) %>%
+  do(return_prf(.$face_eval_ketan))
 
-# let's look at the actual iamges
-dir.create(paste0('faces_check/'))
-for (i in seq(1,length(faces_only$full_image_path),1)){
-  image_read(as.character(faces_only$full_image_path[i])) %>%
-  image_append(stack = FALSE) %>%
-  image_write(file.path(paste0("faces_check/", faces_only$short_image_path[i])))
-}
+prf_by_age_hands <- d %>%
+  mutate(hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose)) %>%
+  group_by(age_day_bin, child_id) %>%
+  do(return_prf(.$hand_eval_ketan))
 ```
 
-## how about true positives on faces?
+### Plot p/r/f/ by age/child for goldset annotations for FACES
 ```{r}
+prf_by_age_faces$age_day_bin = as.numeric(prf_by_age_faces$age_day_bin)
+
+p1  = ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth()  +
+  ylab('F-score - Face detection')
+
+p2 = ggplot(prf_by_age_faces, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth() +
+  ylab('Precision - Face detection')
+
+p3 =ggplot(prf_by_age_faces, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth()  +
+  ylab('Recall - Face detection')
+#
+ggarrange(p1,p2,p3)
+```
+
+### Plot p/r/f/ by age/child for goldset annotations for HANDS
+```{r}
+prf_by_age_hands$age_day_bin = as.numeric(prf_by_age_hands$age_day_bin)
+
+p4  = ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth()  +
+  ylab('F-score - Hand detection')
+
+p5 = ggplot(prf_by_age_hands, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth() +
+  ylab('Recall - Hand detection')
+
+p6 =ggplot(prf_by_age_hands, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth() +
+  ylab('Precision - Hand detection')
+#
+ggarrange(p4,p5,p6)
+```
+
+### Look at proportion of hands vs. faces in manual annotations
+```{r}
+face_vs_hands_goldset <- d %>%
+  group_by(child_id, age_day_bin) %>%
+  summarize(prop_faces = sum(face_present_ketan) / length(face_present_ketan), prop_hands = sum(hand_present_ketan) / length(hand_present_ketan), num_detect = length(face_present_ketan)) %>%
+  mutate(faces_vs_hands = prop_faces - prop_hands)
+
+face_vs_hands_goldset$age_day_bin  = as.numeric(face_vs_hands_goldset$age_day_bin)
+
+ggplot(face_vs_hands_goldset, aes(x=age_day_bin, y=faces_vs_hands, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth() +
+  ylab("Faces - Hands (manual annotations)")
+
+```
+
+# Examine age-trends in fullset of open-pose detections
+## Preprocess detections data
+
+### Make detections into logical vectors and compute "person" as either face/hand
+```{r}
+d_all <- detections
+d_all$face_openpose = as.logical(d_all$face_openpose)
+d_all$hand_openpose = as.logical(d_all$hand_openpose)
+d_all$person_openpose = (as.logical(d_all$face_openpose) | as.logical(d_all$hand_openpose))
+d_all$both_openpose = (as.logical(d_all$face_openpose) & as.logical(d_all$hand_openpose))
+
+```
+
+### Make age bins and compute summary statistics
+```{r}
+
+# Can redo this but using same bins as in gold set comparison
+# bin_size = 10
+# min_age = min(d$age_days)
+# max_age = max(d$age_days)
+# bin_starts = seq(min_age-1, max_age+1,bin_size)
+# bins = c(bin_starts, max_age)
+# d <- d %>%
+#   mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
+
+summary_by_age <- d_all %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/bin_size,1))) %>%
+  group_by(age_day_bin, child_id) %>%
+  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect, face_or_hand = sum(person_openpose)/ num_detect, face_and_hand = sum(both_openpose)/ num_detect)
+
+# need numeric on age bins for geom_smooth...
+summary_by_age$age_day_bin=as.numeric(summary_by_age$age_day_bin)
+
+```
+
+## Make diagnotic plots over age from all detections
+### Faces
+```{r}
+ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
+  geom_point(alpha=.8) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
+  geom_smooth() + 
+  ylab('Proportion Faces') + 
+  xlab('Age bin')
+```
+
+### Hands
+```{r}
+ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.8) +
+  geom_smooth() + 
+  ylab('Proportion Hands') + 
+  xlab('Age bin')
+```
+
+### Faces - Hands: Key plot for fausey comparison
+```{r}
+## faces - hands
+ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.8) +
+  geom_smooth() + 
+  ylab('Proportion Faces - Hands') + 
+  xlab('Age bin')
+
+```
+
+### Face OR hand
+```{r}
+ggplot(summary_by_age, aes(x=age_day_bin, y=face_or_hand, size=num_detect, col=child_id)) +
+  geom_point(alpha=.8) +
+  geom_smooth() + 
+  ylab('Proportion Face OR Hand') + 
+  xlab('Age bin')
+```
+
+### Face AND Hand
+```{r}
+ggplot(summary_by_age, aes(x=age_day_bin, y=face_and_hand, size=num_detect, col=child_id)) +
+  geom_point(alpha=.8) +
+  geom_smooth() + 
+  ylab('Proportion Face AND Hand') + 
+  xlab('Age bin')
+```
+
+# Render out images based on annotations if desired
+## True positives on faces?
+```{r eval=FALSE}
 faces_only_op_cor <- m %>%
@@
 
-## how about false positives on facs?
-```{r}
+## False positives on facs?
+```{r eval=FALSE}
 to_write <- m %>%
@@
 
-## how about false negatives on faces?
-```{r}
+## False negatives on faces?
+```{r eval=FALSE}
 to_write <- m %>%
@@
 ```
-
-# Examine age-trends in open-pose detections
-### Make age bins
-```{r}
-### What ages do we have detections at?
-
-hist(d$age_days)
-## bin age by 10 days
-bin_size = 30
-min_age = min(d$age_days)
-max_age = max(d$age_days)
-bin_starts = seq(min_age-1, max_age+1,bin_size)
-bins = c(bin_starts, max_age)
-```
-
-### Make detections into logical vectors and compute "person" as either face/hand
-```{r}
-d$face_openpose = as.logical(d$face_openpose)
-d$hand_openpose = as.logical(d$hand_openpose)
-d$person_openpose = (as.logical(d$face_openpose) | as.logical(d$hand_openpose))
-d$both_openpose = (as.logical(d$face_openpose) & as.logical(d$hand_openpose))
-
-```
-
-```{r}
-summary_by_age <- d %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  group_by(age_day_bin, child_id) %>%
-  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect, face_or_hand = sum(person_openpose)/ num_detect, face_and_hand = sum(both_openpose)/ num_detect)
-
-# for geom_smooth
-summary_by_age$age_day_bin=as.numeric(summary_by_age$age_day_bin)
-```
-
-### Make diagnotic plots
-```{r}
-# person by age
-ggplot(summary_by_age, aes(x=age_day_bin, y=face_or_hand, size=num_detect, col=child_id)) +
-  geom_point(alpha=.8) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
-  geom_smooth() + 
-  ylab('Proportion Face OR Hand') + 
-  xlab('Age bin')
-
-# person by age
-ggplot(summary_by_age, aes(x=age_day_bin, y=face_and_hand, size=num_detect, col=child_id)) +
-  geom_point(alpha=.8) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
-  geom_smooth() + 
-  ylab('Proportion Face AND Hand') + 
-  xlab('Age bin')
-
-# faces
-p1 = ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
-  geom_point(alpha=.8) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
-  geom_smooth() + 
-  ylab('Proportion Faces') + 
-  xlab('Age bin')
-
-# hands
-p2 = ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
-  geom_point(alpha=.8) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
-  geom_smooth() + 
-  ylab('Proportion Hands') + 
-  xlab('Age bin')
-```
-
-### Key plot for fausey comparison
-```{r}
-## faces - hands
-p3 = ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
-  geom_point(alpha=.8) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
-  geom_smooth() + 
-  ylab('Proportion Faces - Hands') + 
-  xlab('Age bin')
-
-```

### 2019-12-14 annotations/face_hands/analysis/preprocess_turk_segmentations.Rmd
Updates to .Rmd to preprocess segmentation hits

@@
 
-```{r}
-
-```
+``
 # Preprocessing
@@
 total_area = jd$Answer.annotatedResult.inputImageProperties.height[1] * jd$Answer.annotatedResult.inputImageProperties.width[1]
-d.raw <- d.raw %>%
+d <- d.raw %>%
   mutate(detection_area = (height*width)/total_area)
@@
 ## plot detection area by detection type
-ggplot(d.raw, aes(x=label, y=log(detection_area))) +
+ggplot(d, aes(x=label, y=log(detection_area))) +
   geom_boxplot()
@@
 ## faces tend to appear towards the top of the image (i.e. 0 pixel coordinates, or upper visual field)
-ggplot(d.raw, aes(x=label, y=top)) +
+ggplot(d, aes(x=label, y=top)) +
   geom_boxplot()
@@
 ```{r}
-write_csv(d.raw,'turk_segmentations_dec12.csv')
+write_csv(d,'turk_segmentations_dec12.csv')
 ```
+
+```{r}
+d <- d %>%
+  mutate(short_image_path = str_split_fixed(full_image_path,'/',7)[,7])
+```
+
+```{r eval=FALSE}
+
+unique_images = d$full_image_path
+for (image in unique_images){
+  this_image_rgb <- image_read(image)
+  img <- image_draw(this_image_rgb)
+  a <- d %>%
+    filter(full_image_path %in% image)
+
+  rect(a$left, a$top+a$height, a$left+a$width, a$top)
+  text(a$left+10, a$top+10, a$label)
+
+  annotated_file = paste0(unique(a$short_image_path), 'turk-annotated.jpg')
+  image_write(img, annotated_file)
+  dev.off()
+}
+
+```
+
+```{r}
+faces <- d %>%
+  filter(label =="Face")
+
+rect(faces$left, faces$top+faces$height, faces$left+faces$width, faces$top)
+text(faces$left+10, faces$top+10, faces$label)
+```
+
+```{r}  
+child_hand <- d %>%
+  filter(label =="Child hand")
+
+rect(child_hand$left, child_hand$top+child_hand$height, child_hand$left+child_hand$width, child_hand$top)
+text(child_hand$left+10, child_hand$top+10, child_hand$label)
+
+```

### 2019-12-16 annotations/face_hands/analysis/preprocess_turk_detections.Rmd

--- 2019-12-05 annotations/face_hands/analysis/analyze_goldset.Rmd
@@
 ---
-title: "Face/Hand Annotations "
+title: "Preprocess turk annotations (hand/face detection)"
 output: html_notebook
@@
 library(viridis)
-library(rhdf5)
 library(magick)
@@
 # Preprocessing
+
+```{r}
+f <- dir("turk_annotations_single/")
+jf <- paste("turk_annotations_single/",f,sep="")
+jd <- read_csv(jf)
+
+summary <- jd %>%
+  group_by(WorkerId) %>%
+  summarize(count_images = n(), avg_time = mean(WorkTimeInSeconds))
+
+jd$response = jd$`Answer.trial-1.label`
+
+agreement <- jd %>%
+  group_by(Input.img_src1) %>%
+  summarize(agree = response[1] == response[2])
+```
 
@@
       this_response = eval(parse(text = paste0("jd$`Answer.trial-",trial_ind,"`"))),
-      # this_response_label = eval(parse(text = paste0("jd$`Answer.trial-",trial_ind,".label`"))),
       full_image_path = eval(parse(text = paste0("jd$Input.img_src",trial_ind))),
@@
 
-```
+## Would like to get rando responses in .label field here:
 
@@
 Starter code is below.
-```{r}
 
@@
   hands = str_detect(shorter_image_path,'hands')
-  faces = str_detect(shorter_image_path,'faces')
+  faces = str_detect(shorter_image_path,'face')
   none = str_detect(shorter_image_path,'none')
@@
   summarize(wrong_sanity = n()) %>%
-  filter(wrong_sanity > 6) # more than 50% wrong
+  filter(wrong_sanity > 3) # more than 1/4 wrong
 

### 2019-12-17 src/get_openpose_bounding_boxes.R
extract bounding boxes for OpenPose detections
so far only applied to 24k gold set, but should work on all OpenPose detections

@@ -1,20 +1,13 @@
 require(stringr)
 
 # should run on master_frames_openpose.h5, but for now use gold set
-frame_size = c(640,480) # pixels; keypoint x,y coords are normalized 0-1, but go out of frame occasionally
+frame_size = list(x=640, y=480) # pixels; keypoint x,y coords are normalized 0-1, but go out of frame occasionally
 # min=-.22, max=1.16
-load("ketan_gold_sample.RData") 
+load("ketan_gold_sample.RData") # in headcam-algo/analysis, maybe should be in /src/data/
 
-# bounding box should be x1 = min(x), y1=min(y), x2=max(x), y2=max(x)
+# "face_keypoints_tuple"  and "pose_keypoints_tuple" include surrounding frames
 
-ketan_gold$face_openpose
-ketan_gold$face_keypoints
-ketan_gold$hand_left_keypoints
-ketan_gold$hand_left_keypoints
-
-# what are "face_keypoints_tuple"  and "pose_keypoints_tuple" ?
-
-table(ketan_gold$hand_openpose, ketan_gold$hand_openpose_wrist)
+#table(ketan_gold$hand_openpose, ketan_gold$hand_openpose_wrist)
 
 
 face_inds <- which(ketan_gold$face_openpose==1)
@@ -28,7 +21,6 @@ get_hand_keypoints <- function(all, hand="left") {
   hd = all$dat
   col_kp = paste0("hand_",hand,"_keypoints")
   col_num = paste0("num_",hand,"_hands")
-  #hd$hand_keys = NA
   hd[,col_kp] = gsub("\\[|\\]", "", hd[,col_kp]) # removes all left or right brackets
   hd[,col_num] = NA
   hkp = list()
@@ -39,7 +31,7 @@ get_hand_keypoints <- function(all, hand="left") {
     } else {
       # if there are multiple people, these are of the form [[1,2,..,63], [64,65,..,127], ..]
       vals = eval(parse(text=paste('c(',hd[i,col_kp],')')))
-      if(length(vals) > 63) {
+      if(length(vals) >= 63) {
         num_hands = length(vals)/63
         hd[i,col_num] = num_hands
         #print(paste(num_hands, "hands found"))
@@ -63,7 +55,6 @@ get_hand_keypoints <- function(all, hand="left") {
 
 get_face_keypoints <- function(all) {
   fd = all$dat
-  fd$face_keys = NA
[…]

### 2020-01-11 annotations/face_hands/analysis/preprocess_turk_segmentations.Rmd
preprocessing turk segmentations

@@
 ---
-title: "Preprocess turk annotations ="
+title: "Preprocess turk annotations"
 output: html_notebook
@@
 
-``
 # Preprocessing
@@
 ```{r}
-f <- dir("turk_annotations_segmentation/")
-jf <- paste("turk_annotations_segmentation/",f,sep="")
+# f <- dir("turk_annotations_segmentation/")
+# jf <- paste("turk_annotations_segmentation/",f,sep="")
+# jd <- read_csv(jf)
+
+f = "turk_segmentations_hands_only.csv"
+jf <- paste("../../../data/",f,sep="")
 jd <- read_csv(jf)
@@
 d.raw <- data.frame()
-trial_indexes = seq(1,200,1)
+trial_indexes = seq(1,length(jd$Input.img_src1),1)
   for (trial_ind in trial_indexes){
@@
 
+```{r}
+
+d <- d.raw %>%
+  mutate(hands_seg = (label %in% c("Child hand","Adult hand")), face_seg = (label == "Adult Face")) %>%
+  mutate(short_image_path = str_split_fixed(full_image_path,'/',7)[,7]) %>%
+  mutate(sample_ind = str_split_fixed(short_image_path,"-",3)[,1], frame_ind_temp = str_split_fixed(short_image_path,"-",3)[,3], vid_name_temp = str_split_fixed(short_image_path,"-",3)[,2]) %>%
+  mutate(sample_ind = as.numeric(sample_ind), frame_ind = as.numeric(str_split_fixed(frame_ind_temp,".jpg",3)[,1])) %>%
+  rowwise() %>%
+  mutate(vid_name_short = str_split(vid_name_temp,"[.]")[[1]][1]) %>%
+  mutate(vid_name = str_split_fixed(vid_name_temp,".mp4",2)[,1]) 
+```
+
+### How many frames/videos had children's faces?
+```{r}
+child_face_frames <- d %>%
+  filter(label=="Child face")
+
+# render out some of these...
+# dir.create(paste0('child_face/'))
+# for (i in seq(1,length(child_face_frames$full_image_path),1)){
+#   image_read(as.character(child_face_frames$full_image_path[i])) %>%
+#   image_append(stack = FALSE) %>%
+#   image_write(file.path(paste0("child_face/", child_face_frames$short_image_path[i])))
+# }
+
+# dir.create(paste0('annotated-images-child-face/'))
+# unique_images = child_face_frames$full_image_path
+# for (image in unique_images){
+#   this_image_rgb <- image_read(image)
+#   img <- image_draw(this_image_rgb)
+#   a <- d %>%
+#     filter(full_image_path %in% image) 
+#   
+### rect(xleft, ybottom, xright, ytop
+#   rect(a$left, a$top+a$height, a$left+a$width, a$top)
+#   text(a$left+10, a$top+10, a$label)
+#   
+#   annotated_file = paste0('annotated-images-child-face/',unique(a$short_image_path), 'turk-annotated.jpg')
+#   image_write(img, annotated_file)
+#   dev.off()
+# }
+
+```
+
 ### Write out csv for use in analysis
 ```{r}
-write_csv(d,'turk_segmentations_dec12.csv')
+write_csv(d,'turk_segmentations_hands_only_processed.csv')
 ```
@@
 
-  annotated_file = paste0(unique(a$short_image_path), 'turk-annotated.jpg')
+  annotated_file = paste0('annotated-images/',unique(a$short_image_path), 'turk-annotated.jpg')
   image_write(img, annotated_file)

### 2020-01-11 analysis/analysis_fulldataset.Rmd
separate& complete analyses scripts for validation / goldset / fullset

---
title: "saycam full dataset analysis"
author: "Bria Long"
date: "1/9/2020"
output: html_document
---

# Basic data loading and setup
## Packages
```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(egg)
theme_set(theme_few())
```

## Read in data

### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
```{r}
right_side_up_file = "../data/video_right-side-up.csv"
right_side_up =read.csv(right_side_up_file)

# get INCORRECT videos 
flipped_videos <- right_side_up %>%
  filter(right_side_up==1) %>%
  rename(vid_name = video)

```

### Load SAYCAM metadata from csv file; get metadata from detections .csv
```{r}
metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"

meta=read.csv(metadata_file) %>%
  rowwise() %>%
  mutate(vid_name = str_split(File.Name,"[.]")[[1]][1]) %>%
  mutate(count_locations = length(str_split(Location,',')[[1]]))

# collapse duplicate labels
meta$Location[meta$Location=='Bedroom Alice/Sam'] = 'Bedroom'

```

### Load in detections from preprocessed Rdata file; 
```{r eval=FALSE}
 # Could do list of detections  from csv (takes forever, skipping)
# data_file = "../data/all_frames.csv"
# detections=read.csv(data_file)

## rdata is faster
load('../data/openpose_detections.RData')
```

### Preprocess data (doesn't exceute; loads processed data below)
```{r eval=FALSE}
# get shortened video names so they match across all files
all_video_names = as.tibble(unique(detections$vid_name))
all_video_names <- all_video_names %>%
  rowwise() %>%
  mutate(vid_name = str_split(value,"[.]")[[1]][1])

# reset levels of vid_name in big detections array (very slow rowwise)
levels(detections$vid_name) <- all_video_names$vid_name

# join with metadata and flip the videos
d_all <- detections %>%
  left_join(meta, by='vid_name') %>%
  filter(!vid_name %in% flipped_videos$vid_name)

# check that we actually excluded the videos
num_orig_videos = length(unique(detections$vid_name))
num_videos_retained = length(unique(d_all$vid_name))
assert_that(num_videos_retained < num_orig_videos)

## All 6 of the video that were not in this file (but were in the detections file) happened to be 6 very bad quality videos; excluding from detections
exclude_bad_quality <- d_all %>%
  filter(!vid_name %in% right_side_up$video)

d_all <- d_all %>%
  filter(!vid_name %in% exclude_bad_quality$vid_name)

### Make detections into logical vectors and compute "person" as either face/hand
d_all$face_openpose = as.logical(d_all$face_openpose)
d_all$hand_openpose = as.logical(d_all$hand_openpose)
d_all$person_openpose = (as.logical(d_all$face_openpose) | as.logical(d_all$hand_openpose))
d_all$both_openpose = (as.logical(d_all$face_openpose) & as.logical(d_all$hand_openpose))

### Look at any suspicious videos with very high face detections (candidate missed allocentric videos)
vid_check <- d_all %>%
  filter(child_id == "S") %>%
  group_by(vid_name,vid_name, Databrary.Link) %>%
  summarize(prop_faces =mean(face_openpose))

high_faces <- vid_check %>%
  filter(prop_faces>.8)

## save this data so this doesn't have to be redone again
save(d_all, file = '../data/openpose_detections_filtered.RData')

```

### Instead, load preprocess and filtered detections
```{r}
load('../data/openpose_detections_filtered.RData')
```

### Make bins across which to analyze data
```{r}
bin_size = 7
min_age = min(d_all$age_days)
max_age = max(d_all$age_days)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)
d_all <- d_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))

d_all$age_day_bin = as.numeric(as.character(d_all$age_day_bin))

```

## How do face/hand detection vary by age? 
### Compute summary statistics
```{r}
summary_by_age <- d_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect, face_or_hand = sum(person_openpose)/ num_detect, face_and_hand = sum(both_openpose)/ num_detect)

```

### Plot faces x age x child
```{r}
ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  geom_smooth(span=10) + 
  ylab('Proportion Faces') + 
  xlab('Age bin (months)') +
  ylim(0,.5)
```

### Plot hands x age x child
```{r}
ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  geom_smooth(span=10) + 
  ylab('Proportion Hands') + 
  xlab('Age bin (months)') +
  ylim(0,.5)
```

### Plot Faces - Hands x age x child:  Key plot for fausey comparison
```{r}
## faces - hands
ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  geom_smooth(span=10) + 
  theme_few(base_size=18) +
  ylab('Proportion Faces - Hands') + 
  xlab('Age (months)')

```

### Plot Face OR hand x age x child
```{r}
ggplot(summary_by_age, aes(x=age_day_bin, y=face_or_hand, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  geom_smooth(span=10) + 
  ylab('Proportion Face OR Hand') + 
  xlab('Age bin')
```

### Plot Face AND hand x age x child
```{r}
ggplot(summary_by_age, aes(x=age_day_bin, y=face_and_hand, size=num_detect, col=child_id)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10) + 
  ylab('Proportion Face AND Hand') + 
  xlab('Age bin')
```

## Look at trends in full dataset by location
```{r}
face_hand_by_location <- d_all %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_openpose), num_detect = length(face_openpose))  %>%
  filter(num_detect > 9000) %>% ## 9000 frames = 5 minutes of video at 30 fps %>%
  mutate(faces_vs_hands = prop_faces - prop_hands)

hands_by_location_to_plot <- face_hand_by_location %>%
  multi_boot_standard(col="prop_hands") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(Location = fct_reorder(Location, mean))

faces_by_location_to_plot <- face_hand_by_location %>%
  multi_boot_standard(col="prop_faces") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(Location = fct_reorder(Location, mean))

faces_vs_hands_to_plot <- face_hand_by_location %>%
  multi_boot_standard(col="faces_vs_hands") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(Location = fct_reorder(Location, mean))

```

### Plot faces and hands by location
```{r}
(plot_faces_loc = ggplot(faces_by_location_to_plot, aes(x = Location, y = mean, col=child_id)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_nudge(x = .4, y = 0)) +
  geom_point(aes(x=Location, y=prop_faces, size=num_detect, alpha=.01)) +
  geom_point() +
  ylim(0,1) +
  coord_flip() + 
  ylab('Proportion Faces') +
  facet_grid(~child_id) )

(plot_hand_loc = ggplot(hands_by_location_to_plot, aes(x = Location, y = mean, col=age_day_bin)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(x=Location, y=prop_hands, size=num_detect, alpha=.01)) +
  geom_point() +
  ylim(0,1) +
  coord_flip() + 
  ylab('Proportion Hands') +
  facet_grid(~child_id) +
  theme(legend.position = "none"))

(plot_hands_vs_faces = ggplot(faces_vs_hands_to_plot, aes(x = Location, y = mean, col=age_day_bin)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(x=Location, y=faces_vs_hands, size=num_detect, alpha=.01)) +
  geom_point() +
  # ylim(0,1) +
  coord_flip() + 
  ylab('Proportion Faces - Hands') +
  facet_grid(~child_id) +  theme(legend.position = "none"))

# ggarrange(plot_faces_loc, plot_hand_loc,plot_hands_vs_faces)
```
## what percentage of the dataset is this? 
```{r}
percentage_of_dataset = sum(faces_vs_hands_to_plot$num_detect)/length(d_all$frame)
```

```{r}

# faces_by_location <- d_all %>%
#   filter(!is.na(Location)) %>%
#   filter(count_locations==1) %>%
#   group_by(Location,child_id,age_day_bin) %>%
#   summarize(prop_face = mean(face_openpose))  
# 
# ggplot(faces_by_location, aes(x = Location, y = prop_face, col=child_id)) + 
#   # geom_flat_violin() +
#   geom_boxplot() +
#   # geom_point() +
#   ylim(0,.8) +
#   ylab('Proportion Faces') +
#   coord_flip()

```

```{r}
# face_vs_hands_location_all <- d_all %>%
#   filter(count_locations==1) %>%
#   filter(!Location=='NA') %>%
#   group_by(child_id,Location, age_day_bin) %>%
#   summarize(prop_faces = sum(face_openpose) / length(face_openpose), prop_hands = sum(hand_openpose) / length(hand_openpose), num_detect = length(face_openpose)) %>%
#   mutate(faces_vs_hands = prop_faces - prop_hands)
# 
# ggplot(face_vs_hands_location_all, aes(x=age_day_bin, y=prop_faces, col=child_id, size=num_detect)) +
#   geom_point() +
#   # geom_smooth() +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#   ylab("Faces") +
#   facet_grid(~Location)
# 
# ggplot(face_vs_hands_location_all, aes(x=age_day_bin, y=prop_hands, col=child_id, size=num_detect)) +
#   geom_point() +
#   # geom_smooth() +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#   ylab("Hands") +
#   facet_grid(~Location)
# 
# ggplot(face_vs_hands_location_all, aes(x=age_day_bin, y=faces_vs_hands, col=child_id, size=num_detect)) +
#   geom_point() +
#   # geom_smooth() +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#   ylab("Faces vs Hands") +
#   facet_grid(~Location)

```

# Render out images based on annotations if desired
## True positives on faces?
```{r eval=FALSE}
faces_only_op_cor <- m %>%
  filter(faces == TRUE) %>%
  filter(face_openpose == TRUE)

# how about images where open pose got it? these should be most obvious
dir.create(paste0('faces_tp/'))
for (i in seq(1,length(faces_only_op_cor$full_image_path),1)){
  image_read(as.character(faces_only_op_cor$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_tp/", faces_only_op_cor$short_image_path[i])))
}

```

## False positives on facs?
```{r eval=FALSE}
to_write <- m %>%
  filter(faces == FALSE) %>%
  filter(face_openpose == TRUE)

# how about images where open pose got it? these should be most obvious
dir.create(paste0('faces_fp/'))
for (i in seq(1,length(to_write$full_image_path),1)){
  image_read(as.character(to_write$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_fp/", to_write$short_image_path[i])))
}

```

## False negatives on faces?
```{r eval=FALSE}
to_write <- m %>%
  filter(faces == TRUE) %>%
  filter(face_openpose == FALSE)

# how about images where open pose got it? these should be most obvious
dir.create(paste0('faces_fn/'))
for (i in seq(1,length(to_write$full_image_path),1)){
  image_read(as.character(to_write$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_fn/", to_write$short_image_path[i])))
}

```

### 2020-01-11 analysis/analysis_goldset.Rmd
separate& complete analyses scripts for validation / goldset / fullset

---
title: "saycam goldset analysis"
author: "Bria Long"
date: "12/4/2019, continued 1/9/2020"
output: html_document
---

# Basic data loading and setup
## Packages
```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(egg)
theme_set(theme_few())
```

## Read in data 
### Load ketan's gold set annotations from preprocessed Rdata files
```{r}

### Get video/frame info from full cleaned dataset (saved)
# load('../data/openpose_detections_filtered.RData')
# vid_info <- d_all %>%
#   select(vid_name, frame, age_days, child_id)
# save(vid_info, file = '../data/vid_info.RData')

load('../data/vid_info.RData')
load('../data/ketan_gold_sample.RData')
```

### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
```{r}
right_side_up_file = "../data/video_right-side-up.csv"
right_side_up =read.csv(right_side_up_file)

# get videos that are flipped, i.e., 
flipped_videos <- right_side_up %>%
  filter(right_side_up==1) %>%
  rename(vid_name = video)
```

### Load SAYCAM metadata from csv file; get metadata from detections .csv
```{r}
metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"
meta=read.csv(metadata_file) %>%
  rowwise() %>%
  mutate(vid_name = str_split(File.Name,"[.]")[[1]][1]) %>%
  mutate(count_locations = length(str_split(Location,',')[[1]]))

# collapse duplicate labels
meta$Location[meta$Location=='Bedroom Alice/Sam'] = 'Bedroom'
```

### Import bounding boxes for goldset & preprocess: filter videos, gather metadata, convert to pixel coordinates
```{r}
bounding_boxes = "../data/gold_sample_bounding_boxes.csv" 
height_px = 480; width_px = 640

bb = read.csv(bounding_boxes) %>%
  rowwise() %>%
  mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
  filter(!vid_name %in% flipped_videos$vid_name) %>%
  left_join(vid_info) %>%
  mutate(height_y = height*height_px, width_x = width*width_px, area = (height_y*width_x)/(height_px*width_px)) 
```
### Read in turk segmentations to get child vs. adult hands
```{r}
turk_annotations_seg = "../data/turk_segmentations_hands_only_processed.csv" 
g_seg = read.csv(turk_annotations_seg) %>%
  select(-HITID, -HITTypeId, -WorkerID)

## preprocess such that each frame has a true/false value for whether there was a child or adult hand
child_adult_hand_annotations <- g_seg %>%
    mutate(child_hands = (label=="Child hand"), adult_hands = (label=="Adult hand")) %>%
    select(-vid_name) %>%
    rename(vid_name = vid_name_short) %>%
    group_by(full_image_path, vid_name, frame_ind) %>%
    summarize(child_hand_seg = (sum(child_hands))>0,  adult_hand_seg = (sum(adult_hands)>0)) %>%
    mutate(frame = frame_ind) %>%
    select(child_hand_seg, adult_hand_seg, full_image_path, vid_name, frame) 
```

### Preprocess gold set data
```{r}
 ketan_gold_out <- ketan_gold %>%
   rowwise() %>%
   mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
   mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
   rename(face_present_ketan = face_present, hand_present_ketan = hand_present)

### Join metadata with gold set annotations (hereafter 'd')
d <- ketan_gold_out %>%
  filter(!vid_name %in% flipped_videos$vid_name) %>%
  left_join(vid_info, by=c("vid_name","frame")) %>%
  left_join(meta, by="vid_name")
```

# Analyze gold set annotations
### Make bins for collapsing across anotations
```{r}
bin_size = 7 # so it's weeks or months
min_age = min(d$age_days)
max_age = max(d$age_days)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)
d <- d %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))

# and make numeric
d$age_day_bin <- as.numeric(as.character(d$age_day_bin))

```

### Hands vs. faces in manual annotations, broken down by child vs. adult hands
```{r}
face_vs_hands_goldset <- d %>%
  full_join(child_adult_hand_annotations, by=c("vid_name", "frame")) %>%
  mutate(frame_id = paste0(vid_name, '-', frame)) %>%
  replace_na(list(adult_hand_seg = FALSE, child_hand_seg = FALSE)) %>% ## replace NAs from segmentation with false for hands since all we got annotations for all frames with hands 
  group_by(child_id, age_day_bin) %>%
  summarize(num_detect = length(unique(frame_id)), prop_faces = sum(face_present_ketan) / num_detect, prop_hands = sum(hand_present_ketan) / num_detect, prop_adult_hands = sum(adult_hand_seg) / num_detect, prop_child_hands = sum(child_hand_seg) / num_detect) %>%
  filter(num_detect > 50) %>% ## need at least x samples per point
  mutate(faces_vs_hands = prop_faces - prop_hands, faces_vs_adult_hands = prop_faces - prop_adult_hands, faces_vs_child_hands = prop_faces - prop_child_hands)  %>%
  filter(!is.na(child_id))

```

### Faces, Adult Hands, Child Hands x Age/Child
```{r}
a_hands = ggplot(face_vs_hands_goldset, aes(x=age_day_bin, y=prop_adult_hands, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10) +
  ylab("Prop adult hands") +
  xlab("Age (weeks)") +
  ylim(0,1) +
  theme(legend.position = "none")

c_hands = ggplot(face_vs_hands_goldset, aes(x=age_day_bin, y=prop_child_hands, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10) +
  ylab("Prop child hands") +
  xlab("Age (weeks)") + 
  ylim(0,1) +
  theme(legend.position = "none")

faces = ggplot(face_vs_hands_goldset, aes(x=age_day_bin, y=prop_faces, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10) +
  ylab("Prop faces") +
  xlab("Age (weeks)")
  ylim(0,1)

ggarrange(a_hands, c_hands, faces, nrow=1)

```

### Faces vs Hands (all), Faces vs Adult Hands
```{r}
faces_vs_adult_hands = ggplot(face_vs_hands_goldset, aes(x=age_day_bin, y=faces_vs_adult_hands, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=5) +
  ylab(" faces - adult hands") +
  ylim(-.5,.5)

faces_vs_all_hands = ggplot(face_vs_hands_goldset, aes(x=age_day_bin, y=prop_faces - prop_hands, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=5) +
  ylab(" faces - all hands") +
  ylim(-.5,.5)

ggarrange(faces_vs_adult_hands, faces_vs_all_hands, nrow=1)
```

### Look at any variance by location from single-location videos
```{r}
faces_by_location <- d %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="face_present_ketan") %>%
  ungroup %>%
  mutate(Location = fct_reorder(Location, mean))

hands_by_location <- d %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="hand_present_ketan") %>%
  ungroup %>%
  mutate(Location = fct_reorder(Location, mean))

(plot_faces_loc = ggplot(faces_by_location, aes(x = Location, y = mean, col=child_id)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ylim(0,.8) +
  coord_flip() + 
  ylab('Proportion Faces'))

(plot_hand_loc = ggplot(hands_by_location, aes(x = Location, y = mean, col=child_id)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  coord_flip() + 
  ylim(0,.8) +
  ylab('Proportion Hands'))

# ggarrange(plot_faces_loc, plot_hand_loc)

```

## Analyze basics from bounding boxes on goldset
### Preprocess bb data
```{r}
bb <- bb %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  mutate(x_pos = left*width_px, y_pos = top*height_px) %>%
  mutate(center_x = x_pos + width_x/2, center_y = y_pos - height_y/2) %>%
  filter(!is.na(child_id))

bb_forheatmap <- bb %>%
  filter(height>0)
```

### Number of people, face/hand area, position descriptives
```{r}
##
num_people_goldset <- bb %>%
  group_by(child_id, age_day_bin) %>%
  summarize(num_people = mean(num_faces), num_detect = length(num_faces))

face_area_goldset <- bb %>%
  filter(mean_conf > 0) %>%
  filter(face_openpose==1) %>%
  group_by(child_id, age_day_bin) %>%
  summarize(face_area = mean(area), num_detect = length(area))

hand_area_goldset <- bb %>%
  filter(mean_conf > 0) %>%
  filter(hand_openpose==1) %>%
  group_by(child_id, age_day_bin) %>%
  summarize(hand_area = mean(area), num_detect = length(area))

pos_goldset <- bb %>%
  filter(mean_conf > 0) %>%
  group_by(child_id, age_day_bin, label) %>%
  summarize(x_center = mean(center_x), num_detect = length(center_x))

top_pos_goldset <- bb %>%
   filter(mean_conf > 0) %>%
  group_by(child_id, age_day_bin, label) %>%
  summarize(y_center = mean(center_y), num_detect = length(center_y))

## number of people
num_people_goldset$age_day_bin  = as.numeric(num_people_goldset$age_day_bin)
ggplot(num_people_goldset, aes(x=age_day_bin, y=num_people, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth() +
  ylab("# people")

## face size
face_area_goldset$age_day_bin  = as.numeric(face_area_goldset$age_day_bin)
ggplot(face_area_goldset, aes(x=age_day_bin, y=face_area, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth() +
  ylab("face size")

## hand size
hand_area_goldset$age_day_bin  = as.numeric(hand_area_goldset$age_day_bin)
ggplot(hand_area_goldset, aes(x=age_day_bin, y=hand_area, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth() +
  ylab("hand size")

## y position
top_pos_goldset$age_day_bin  = as.numeric(top_pos_goldset$age_day_bin)
ggplot(top_pos_goldset, aes(x=age_day_bin, y=y_center, col=label)) +
  geom_point(alpha=.5) +
  geom_smooth() +
  ylab("detection_position_y")

```

### Code ot render out bounding boxes from OP on sample frames
```{r}
# g_seg_info <- g_seg %>%
#   distinct(full_image_path, vid_name_short, frame_ind)
#   
# bb_check <- bb %>%
#   mutate(frame_ind = frame, vid_name_short = vid_name) %>%
#   left_join(g_seg_info, by=c("vid_name_short","frame_ind")) %>%
#   filter(!is.na(full_image_path)) %>%
#   filter(mean_conf > 0)

# # dir.create(paste0('bbcheck/'))
# unique_images <- bb_check$full_image_path[101:200]
# 
# for (image in unique_images){
#   this_image_rgb <- image_read(image)
#   img <- image_draw(this_image_rgb)
#   a <- bb_check %>%
#     filter(full_image_path %in% image) 
#   
#   # rect(a$x_pos, a$y_pos-a$height_y, a$x_pos+a$width_x, a$y_pos)
#   text(a$center_x, a$center_y, a$center_y)
#   
#   annotated_file = paste0('bbcheck/',unique(a$vid_name_short), unique(a$frame_ind), 'OP-center.jpg')
#   image_write(img, annotated_file)
#   dev.off()
# }
```

### Heatmaps of face detection positions across age groups
```{r}
face_heatmap_young <- bb_forheatmap %>%
  filter(label=='face') %>%
  filter(age_day_bin<12)

face_heatmap_middle<- bb_forheatmap %>%
  filter(label=='face') %>%
  filter(age_day_bin>12 & age_day_bin<18.1)

face_heatmap_oldest <- bb_forheatmap %>%
  filter(label=='face') %>%
  filter(age_day_bin>18.1)

(p1_youngest <- ggplot(face_heatmap_young, aes(x=center_x, y=center_y)) +
  geom_point() + 
  stat_density_2d(aes(fill = ..level..), geom="polygon") +
  coord_fixed(ratio=1) +
  ggtitle('Faces: 6-12m') +
  ylim(0,height_px) +
  scale_y_reverse())

(p2_middle <- ggplot(face_heatmap_middle, aes(x=center_x, y=center_y)) +
  geom_point() + 
  stat_density_2d(aes(fill = ..level..), geom="polygon") +
  coord_fixed(ratio=1) +
  ggtitle('Faces: 12-18m') +
  ylim(0,height_px) +
  scale_y_reverse())

(p3_oldest <- ggplot(face_heatmap_oldest, aes(x=x_pos, y=y_pos)) +
  geom_point() + 
  stat_density_2d(aes(fill = ..level..), geom="polygon") +
  coord_fixed(ratio=1) +
  ggtitle('Faces: 18m +') +
  ylim(0,height_px) +
  scale_y_reverse())

# ggarrange(p1_youngest, p2_middle,p3_oldest, nrow=1)
```

### Heatmaps of hand detection positions across age groups
```{r}
hand_heatmap_young <- bb_forheatmap %>%
  filter(label=='hand') %>%
  filter(age_day_bin<12)

hand_heatmap_middle<- bb_forheatmap %>%
  filter(label=='hand') %>%
  filter(age_day_bin>12 & age_day_bin<18.1)

hand_heatmap_oldest <- bb_forheatmap %>%
  filter(label=='hand') %>%
  filter(age_day_bin>18.1)

(p1_youngest <- ggplot(hand_heatmap_young, aes(x=center_x, y=center_y)) +
  geom_point() + 
  stat_density_2d(aes(fill = ..level..), geom="polygon") +
  coord_fixed(ratio=1) +
  ggtitle('Hands: 6-12m') +
  ylim(0,height_px) +
  scale_y_reverse())

(p2_middle <- ggplot(hand_heatmap_middle, aes(x=center_x, y=center_y)) +
  geom_point() + 
  stat_density_2d(aes(fill = ..level..), geom="polygon") +
  coord_fixed(ratio=1) +
  ggtitle('Hands: 12-18m') +
  ylim(0,height_px) +
  scale_y_reverse())

(p3_oldest <- ggplot(hand_heatmap_oldest, aes(x=x_pos, y=y_pos)) +
  geom_point() + 
  stat_density_2d(aes(fill = ..level..), geom="polygon") +
  coord_fixed(ratio=1) +
  ggtitle('Hands: 18m +') +
  ylim(0,height_px) +
  scale_y_reverse())

# ggarrange(p1_youngest, p2_middle,p3_oldest, nrow=1)

```

### CHild vs adult hand heatmaps from mturk sample
```{r}

child_hands <- g_seg %>%
  filter(label=="Child hand")

adult_hands <- g_seg %>%
  filter(label=="Adult hand")
##
ggplot(child_hands, aes(x=left, y=top)) +
  geom_point() + 
  stat_density_2d(aes(fill = ..level..), geom="polygon") +
  coord_fixed(ratio=1) +
  ggtitle('Child hands (mturk)') +
  ylim(0,height_px) +
  scale_y_reverse()
##
ggplot(adult_hands, aes(x=left, y=top)) +
  geom_point() + 
  stat_density_2d(aes(fill = ..level..), geom="polygon") +
  coord_fixed(ratio=1) +
  ylim(0,height_px) +
  scale_y_reverse() +
  ggtitle('Adult hands (mturk)')

```

### 2020-01-11 analysis/detector_validation.Rmd
separate& complete analyses scripts for validation / goldset / fullset

--- 2019-12-14 analysis/analysis_dec2019.Rmd
@@
 ---
-title: "SAYCAM_analysis_dec2019"
+title: "Detector_Validation"
 author: "Bria Long"
-date: "12/4/2019"
+date: "1/8/2020"
 output: html_document
@@
 
-## Read in data 
-### Could do list of detections (takes forever, skipping)
-```{r eval=FALSE}
-data_file = "../data/all_frames.csv"
-detections=read.csv(data_file) 
-```
-
 ### Instead load in detections and ketan's gold set annotations from preprocessed Rdata files
@@
 ```
+
 ### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
@@
   filter(right_side_up==1)
+```
+
+### Get metadata from file
+```{r}
+metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"
+
+meta=read.csv(metadata_file) %>%
+  mutate(vid_name_short = str_split_fixed(File.Name,'.AVI',2)[,1]) %>%
+  rowwise() %>%
+  mutate(count_locations = length(str_split(Location,',')[[1]]))
+
+# location_data <- meta %>%
+#   filter(count_locations==1) %>%
+
 ```
@@
 
-### Could also import segmentations (this is only a small sample of 200 frames right now)
+### Import hand segmentations
 ```{r eval=FALSE}
-turk_annotations_seg = "../data/turk_segmentations_dec12.csv" # 20 turkers who did ~250 frames each
-gold_set_seg = read.csv(turk_annotations_seg)
-g_seg <- gold_set_seg %>%
-  mutate(hands_seg = (label %in% c("Child hand","Adult hand")), face_seg = (label == "Face")) %>%
-  mutate(short_image_path = str_split_fixed(full_image_path,'/',7)[,7]) %>%
-  mutate(sample_ind = str_split_fixed(short_image_path,"-",3)[,1], frame_ind_temp = str_split_fixed(short_image_path,"-",3)[,3], vid_name_temp = str_split_fixed(short_image_path,"-",3)[,2]) %>%
-  mutate(sample_ind = as.numeric(sample_ind), frame_ind = as.numeric(str_split_fixed(frame_ind_temp,".jpg",3)[,1])) %>%
-  rowwise() %>%
-  mutate(vid_name_short = str_split(vid_name_temp,"[.]")[[1]][1]) %>%
-  mutate(vid_name = str_split_fixed(vid_name_temp,".mp4",2)[,1])
+turk_annotations_seg = "../data/turk_segmentations_hands_only_processed.csv" 
+g_seg = read.csv(turk_annotations_seg)
 
@@
 
-### Compute TP/FN/TN/FP on dataset for both faces and hands from segmentation hits (skipping for now)
+### Compute TP/FN/TN/FP on dataset for both kinds of hands from segmentation hits 
 ```{r eval=FALSE}
@@
   select(vid_name, frame, label, hands_seg, face_seg, sample_ind, face_openpose, hand_openpose, short_image_path, full_image_path, age_days, child_id) %>%
+  mutate(child_hand_seg = (label=="Child hand"), adult_hand_seg = (label=="Adult hand")) %>%
   mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
+  mutate(possible_allocentric=(label=='Child face')) %>%
   rowwise() %>%
-  mutate(face_eval = evaluate_detector(face_seg, face_openpose), hand_eval = evaluate_detector(hands_seg, hand_openpose))
+  mutate(face_eval = evaluate_detector(face_seg, face_openpose), hand_eval = evaluate_detector(hands_seg, hand_openpose), child_hand_eval = evaluate_detector(child_hand_seg, hand_openpose), adult_hand_eval = evaluate_detector(adult_hand_seg, hand_openpose))
+
+## Hand-dense 
+return_prf_short(m_seg$hand_eval)
+return_prf_short(m_seg$child_hand_eval)
+return_prf_short(m_seg$adult_hand_eval)
+
+# weird_gs_frames <- m_seg %>%
+#   mutate(weird = (label=='Child face')) %>%
+#   filter(weird==TRUE)
 
@@
   filter(!vid_name_short %in% flipped_videos$video) %>%
-  left_join(vid_info, by=c("vid_name","frame"))
+  left_join(vid_info, by=c("vid_name","frame")) %>%
+  left_join(meta, by="vid_name_short")
 ```
@@
 ```{r}
-bin_size = 10
+bin_size = 30
 min_age = min(d$age_days)
@@
 
-### Look at prf changes by age/child
+### Short prf function def.
 ```{r}
@@
  }
-
+```
+### Look at prf changes by age/child
+```{r}
 prf_by_age_faces <- d %>%
@@
 
-### Look at proportion of hands vs. faces in manual annotations
-```{r}
-face_vs_hands_goldset <- d %>%
-  group_by(child_id, age_day_bin) %>%
-  summarize(prop_faces = sum(face_present_ketan) / length(face_present_ketan), prop_hands = sum(hand_present_ketan) / length(hand_present_ketan), num_detect = length(face_present_ketan)) %>%
-  mutate(faces_vs_hands = prop_faces - prop_hands)
+### Plot p/r/f/ by age/child for goldset annotations for locations for faces
 
-face_vs_hands_goldset$age_day_bin  = as.numeric(face_vs_hands_goldset$age_day_bin)
-
-ggplot(face_vs_hands_goldset, aes(x=age_day_bin, y=faces_vs_hands, col=child_id, size=num_detect)) +
-  geom_point(alpha=.5) +
-  geom_smooth() +
-  ylab("Faces - Hands (manual annotations)")
-
-```
-
-# Examine age-trends in fullset of open-pose detections
-## Preprocess detections data
-
-### Make detections into logical vectors and compute "person" as either face/hand
-```{r}
-d_all <- detections
-d_all$face_openpose = as.logical(d_all$face_openpose)
-d_all$hand_openpose = as.logical(d_all$hand_openpose)
-d_all$person_openpose = (as.logical(d_all$face_openpose) | as.logical(d_all$hand_openpose))
-d_all$both_openpose = (as.logical(d_all$face_openpose) & as.logical(d_all$hand_openpose))
-
-```
-
-### Make age bins and compute summary statistics
 ```{r}
 
-# Can redo this but using same bins as in gold set comparison
-# bin_size = 10
-# min_age = min(d$age_days)
-# max_age = max(d$age_days)
-# bin_starts = seq(min_age-1, max_age+1,bin_size)
-# bins = c(bin_starts, max_age)
-# d <- d %>%
-#   mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
+prf_by_location_faces <- d %>%
+  filter(!is.na(Location)) %>%
+  filter(!Location=='N/A') %>%
+  filter(count_locations==1) %>%
+  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose)) %>%
+  group_by(age_day_bin, Location) %>%
+  do(return_prf(.$face_eval_ketan))
 
-summary_by_age <- d_all %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/bin_size,1))) %>%
-  group_by(age_day_bin, child_id) %>%
-  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect, face_or_hand = sum(person_openpose)/ num_detect, face_and_hand = sum(both_openpose)/ num_detect)
-
-# need numeric on age bins for geom_smooth...
-summary_by_age$age_day_bin=as.numeric(summary_by_age$age_day_bin)
-
+prf_by_location_faces$age_day_bin  = as.numeric(as.character(prf_by_location_faces$age_day_bin))
+ggplot(prf_by_location_faces, aes(x=age_day_bin, y=f, col=Location, size=num_detect)) +
+  geom_point(alpha=.5) +
+  facet_grid(~Location)
+  geom_smooth()  +
+  ylab('F-score - Face detection')
 ```
-
-## Make diagnotic plots over age from all detections
-### Faces
-```{r}
-ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
-  geom_point(alpha=.8) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
-  geom_smooth() + 
-  ylab('Proportion Faces') + 
-  xlab('Age bin')
-```
-
-### Hands
-```{r}
-ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
-  geom_point(alpha=.8) +
-  geom_smooth() + 
-  ylab('Proportion Hands') + 
-  xlab('Age bin')
-```
-
-### Faces - Hands: Key plot for fausey comparison
-```{r}
-## faces - hands
-ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
-  geom_point(alpha=.8) +
-  geom_smooth() + 
-  ylab('Proportion Faces - Hands') + 
-  xlab('Age bin')
-
-```
-
-### Face OR hand
-```{r}
-ggplot(summary_by_age, aes(x=age_day_bin, y=face_or_hand, size=num_detect, col=child_id)) +
-  geom_point(alpha=.8) +
-  geom_smooth() + 
-  ylab('Proportion Face OR Hand') + 
-  xlab('Age bin')
-```
-
-### Face AND Hand
-```{r}
-ggplot(summary_by_age, aes(x=age_day_bin, y=face_and_hand, size=num_detect, col=child_id)) +
-  geom_point(alpha=.8) +
-  geom_smooth() + 
-  ylab('Proportion Face AND Hand') + 
-  xlab('Age bin')
-```
-
-# Render out images based on annotations if desired
-## True positives on faces?
-```{r eval=FALSE}
-faces_only_op_cor <- m %>%
-  filter(faces == TRUE) %>%
-  filter(face_openpose == TRUE)
-
-# how about images where open pose got it? these should be most obvious
-dir.create(paste0('faces_tp/'))
-for (i in seq(1,length(faces_only_op_cor$full_image_path),1)){
-  image_read(as.character(faces_only_op_cor$full_image_path[i])) %>%
-  image_append(stack = FALSE) %>%
-  image_write(file.path(paste0("faces_tp/", faces_only_op_cor$short_image_path[i])))
-}
-
-```
-
-## False positives on facs?
-```{r eval=FALSE}
-to_write <- m %>%
-  filter(faces == FALSE) %>%
-  filter(face_openpose == TRUE)
-
-# how about images where open pose got it? these should be most obvious
-dir.create(paste0('faces_fp/'))
-for (i in seq(1,length(to_write$full_image_path),1)){
-  image_read(as.character(to_write$full_image_path[i])) %>%
-  image_append(stack = FALSE) %>%
-  image_write(file.path(paste0("faces_fp/", to_write$short_image_path[i])))
-}
-
-```
-
-## False negatives on faces?
-```{r eval=FALSE}
-to_write <- m %>%
-  filter(faces == TRUE) %>%
-  filter(face_openpose == FALSE)
-
-# how about images where open pose got it? these should be most obvious
-dir.create(paste0('faces_fn/'))
-for (i in seq(1,length(to_write$full_image_path),1)){
-  image_read(as.character(to_write$full_image_path[i])) %>%
-  image_append(stack = FALSE) %>%
-  image_write(file.path(paste0("faces_fn/", to_write$short_image_path[i])))
-}
-
-```

### 2020-01-11 paper/cogsci/paper.Rmd
adding CogSci paper outline

---
title: "Quantifying social information in natural infant visual experience"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Bria Long (bria@stanford.edu)} 
    \AND {\large \bf George Kachergis (kachergis@stanford.edu)} 
    \AND {\large \bf Ketan Jay Agarwal (agrawalk@stanford.edu)} 
    \AND {\large \bf Michael C. Frank (mcfrank@stanford.edu)} \\ Department of Psychology, Street Address \\ Stanford, CA 91305 USA}

abstract: >
    Faces are a critical part of infants' visual experience, as they convey social and 
    linguistic information.

keywords: >
    Add your choice of indexing terms or keywords; kindly use a semi-colon; between each term.

output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
```

# Introduction

Previous work has suggested:
- Relative changes in prevalence of faces vs. hands (Fausey 2016), though perhaps this is driven by infants younger than 4 months of age (e.g., Jayaraman, Fausey, & Smith, 2015; Sugden, Mohamed-Ali, & Moulson, 2014) who see both more frequent and more persistent faces (Jayaraman & Smith, 2018)

- Surprising attention to hand movements and their interactions with objects (Yu & Smith, 2013), particularly in older infants

- Differences in the availability of social information depending on motor abilities (Sanchez, Long et al., 2018 CogSci; @Franchak2011 and more)

One limitation of past work is that it has relied on cross-sectional data, and thus cannot speak to whether these trajectories are present in individual children.

Here, we analyze a longitudinal corpus of head-mounted camera data, leveraging over XX hours of videos from XX children, totaling more than XX frames.  
(briefly describe dataset; sampling strategy: location of two households, number of hours of video, variability in location, etc; reference published paper on what this dataset is, large field of view (fisheye lens))

To do so, we first test and validate novel computer vision methods for extracting social information from these egocentric viewpoints on a small subset of randomly selected frames from the dataset.  We then apply these methods at scale to the larger dataset, allowing us to extract key descriptive variables hypothesized to vary across development.

Part 1: How well can we capture social information using computer vision?
- Description of OpenPose (Figure 1) 
- Description of annotation strategy (24K by Ketan, ~4K on turk, reliability)
- Describe main P/R/F statistics for 24K for faces and hands; interpret. Relatively higher precision vs. recall.
- P/R/F variation across child/age for faces
- Describe possible sources of variation that decrease scores for:
    - Faces: weird viewpoints, occluded/side viewpoint, faces in books
    - Hands: children’s own hands, hands in books, side viewpoints
- Describe additional child vs. hand annotation; P/R/F variation across child vs. adult hands (better for adult hands, still OK for child hands)

Part 2: Access to social information across age
Prevalence of hands vs faces across age (in goldset, full dataset) (Figure 2)
Why so many hands? 
More child hands as in gold set
Cropped analysis

Variation across location contexts (goldset, full dataset)

# Method

If the authors' names are
included in the sentence, place only the year in parentheses, as in
[-@Franchak2011], but otherwise place the entire reference in
parentheses with the authors and year separated by a comma
[@Fausey2016]. List multiple references alphabetically and
separate them by semicolons [@Frank2012; @Smith2011]. 
Use the et. al. construction only after listing all the authors to a
publication in an earlier reference and for citations with four or
more authors.

You might want to display a wide figure across both columns. To do this, you change the `fig.env` chunk option to `figure*`. To align the image in the center of the page, set `fig.align` option to `center`. To format the width of your caption text, you set the `num.cols.cap` option to `2`.

## One-column images

Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.

```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
img <- png::readPNG("figs/lab_logo_stanford.png")
grid::grid.raster(img)
```

## R Plots

You can use R chunks directly to plot graphs. And you can use latex floats in the
fig.pos chunk option to have more control over the location of your plot on the page. For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**

```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
x <- 0:100
y <- 2 * (x + rnorm(length(x), sd = 3) + 3)

ggplot2::ggplot(data = data.frame(x, y), 
                aes(x = x, y = y)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## Tables

You can use the xtable function in the xtable package.

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)

tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
                       caption = "This table prints across one column.")

print(tab1, type="latex", comment = F, table.placement = "H")
```

# Discussion

Fausey 2016: 103,383 images; 
Here: 30,000,000 frames; 300 fold increase in data

# Acknowledgements

We would like to thank X and Y for helpful comments, and...

# References

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent

### 2020-01-11 paper/cogsci/paper.tex
adding CogSci paper outline

% Template for Cogsci submission with R Markdown

% Stuff changed from original Markdown PLOS Template
\documentclass[10pt, letterpaper]{article}

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{float}
\usepackage{caption}

% amsmath package, useful for mathematical formulas
\usepackage{amsmath}

% amssymb package, useful for mathematical symbols
\usepackage{amssymb}

% hyperref package, useful for hyperlinks
\usepackage{hyperref}

% graphicx package, useful for including eps and pdf graphics
% include graphics with the command \includegraphics
\usepackage{graphicx}

% Sweave(-like)
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
\newenvironment{Schunk}{}{}
\DefineVerbatimEnvironment{Code}{Verbatim}{}
\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
\newenvironment{CodeChunk}{}{}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{apacite}

% KM added 1/4/18 to allow control of blind submission

\usepackage{color}

% Use doublespacing - comment out for single spacing
%\usepackage{setspace}
%\doublespacing

% % Text layout
% \topmargin 0.0cm
% \oddsidemargin 0.5cm
% \evensidemargin 0.5cm
% \textwidth 16cm
% \textheight 21cm

\title{Quantifying social information in natural infant visual experience}

\author{{\large \bf Bria Long (bria@stanford.edu)}  \AND {\large \bf George Kachergis (kachergis@stanford.edu)}  \AND {\large \bf Ketan Jay Agarwal (agrawalk@stanford.edu)}  \AND {\large \bf Michael C. Frank (mcfrank@stanford.edu)} \\ Department of Psychology, Street Address \\ Stanford, CA 91305 USA}

\begin{document}

\maketitle

\begin{abstract}
Faces are a critical part of infants' visual experience, as they convey
social and linguistic information.

\textbf{Keywords:}
Add your choice of indexing terms or keywords; kindly use a semi-colon;
between each term.
\end{abstract}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Previous work has suggested: - Relative changes in prevalence of faces
vs.~hands (Fausey 2016), though perhaps this is driven by infants
younger than 4 months of age (e.g., Jayaraman, Fausey, \& Smith, 2015;
Sugden, Mohamed-Ali, \& Moulson, 2014) who see both more frequent and
more persistent faces (Jayaraman \& Smith, 2018)

\begin{itemize}
\item
  Surprising attention to hand movements and their interactions with
  objects (Yu \& Smith, 2013), particularly in older infants
\item
  Differences in the availability of social information depending on
  motor abilities (Sanchez, Long et al., 2018 CogSci; Franchack papers)
\end{itemize}

One limitation of past work is that it has relied on cross-sectional
data, and thus cannot speak to whether these trajectories are present in
individual children.

Here, we analyze a longitudinal corpus of head-mounted camera data,
leveraging over XX hours of videos from XX children, totaling more than
XX frames. \{briefly describe dataset; sampling strategy: location of
two households, number of hours of video, variability in location, etc;
reference published paper on what this dataset is, large field of view
(fisheye lens))

To do so, we first test and validate novel computer vision methods for
extracting social information from these egocentric viewpoints on a
small subset of randomly selected frames from the dataset. We then apply
these methods at scale to the larger dataset, allowing us to extract key
descriptive variables hypothesized to vary across development.

Part 1: How well can we capture social information using computer
vision? - Description of OpenPose (Figure 1) - Description of annotation
strategy (24K by Ketan, \textasciitilde{}4K on turk, reliability) -
Describe main P/R/F statistics for 24K for faces and hands; interpret.
Relatively higher precision vs.~recall. - P/R/F variation across
child/age for faces - Describe possible sources of variation that
decrease scores for: - Faces: weird viewpoints, occluded/side viewpoint,
faces in books - Hands: children's own hands, hands in books, side
viewpoints - Describe additional child vs.~hand annotation; P/R/F
variation across child vs.~adult hands (better for adult hands, still OK
for child hands)

Part 2: Access to social information across age Prevalence of hands vs
faces across age (in goldset, full dataset) (Figure 2) Why so many
hands? More child hands as in gold set Cropped analysis

Variation across location contexts (goldset, full dataset)

\hypertarget{method}{%
\section{Method}\label{method}}

If the authors' names are included in the sentence, place only the year
in parentheses, as in (2011), but otherwise place the entire reference
in parentheses with the authors and year separated by a comma (Fausey,
Jayaraman, \& Smith, 2016). List multiple references alphabetically and
separate them by semicolons (Frank, 2012; Smith, Yu, \& Pereira, 2011).
Use the et. al.~construction only after listing all the authors to a
publication in an earlier reference and for citations with four or more
authors.

You might want to display a wide figure across both columns. To do this,
you change the \texttt{fig.env} chunk option to \texttt{figure*}. To
align the image in the center of the page, set \texttt{fig.align} option
to \texttt{center}. To format the width of your caption text, you set
the \texttt{num.cols.cap} option to \texttt{2}.

\hypertarget{one-column-images}{%
\subsection{One-column images}\label{one-column-images}}

Single column is the default option, but if you want set it explicitly,
set \texttt{fig.env} to \texttt{figure}. Notice that the
\texttt{num.cols} option for the caption width is set to \texttt{1}.

\begin{CodeChunk}
\begin{figure}[H]

{\centering \includegraphics{figs/image-1}

}

\caption[One column image]{One column image.}\label{fig:image}
\end{figure}
\end{CodeChunk}

\hypertarget{r-plots}{%
\subsection{R Plots}\label{r-plots}}

You can use R chunks directly to plot graphs. And you can use latex
floats in the fig.pos chunk option to have more control over the
location of your plot on the page. For more information on latex
placement specifiers see
\textbf{\href{https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions}{here}}

\begin{CodeChunk}
\begin{figure}[H]

{\centering \includegraphics{figs/plot-1}

}

\caption[R plot]{R plot}\label{fig:plot}
\end{figure}
\end{CodeChunk}

\hypertarget{tables}{%
\subsection{Tables}\label{tables}}

You can use the xtable function in the xtable package.

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 0.00 & 0.10 & 0.0 & 0.98 \\ 
  x & 1.90 & 0.09 & 20.1 & 0.00 \\ 
   \hline
\end{tabular}
\caption{This table prints across one column.} 
\end{table}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Fausey 2016: 103,383 images; Here: 30,000,000 frames; 300 fold increase
in data

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

We would like to thank X and Y for helpful comments, and\ldots{}

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}

\noindent

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Fausey2016}{}%
Fausey, C. M., Jayaraman, S., \& Smith, L. B. (2016). From faces to
hands: Changing visual input in the first two years. \emph{Cognition},
\emph{152}, 101--107.

\leavevmode\hypertarget{ref-Franchak2011}{}%
Franchak, J. M., Kretch, K. S., Soska, K. C., \& Adolph, K. E. (2011).
Head-mounted eye- tracking: A new method to describe infant looking.
\emph{Child Development}, \emph{82}(6), 1738--1750.

\leavevmode\hypertarget{ref-Frank2012}{}%
Frank, M. C. (2012). Measuring children's visual access to social
information using face detection. In \emph{Proceedings of the nth annual
conference of the cognitive science society} (pp. XXX--XXX). Hillsdale,
NJ: Cognitive Science Society.

\leavevmode\hypertarget{ref-Smith2011}{}%
Smith, L. B., Yu, C., \& Pereira, A. (2011). Not your mother's view: The
dynamics of toddler visual experience. \emph{Developmental Science},
\emph{14}(1), 9--17.

\bibliographystyle{apacite}

\end{document}

### 2020-01-12 analysis/analysis_fulldataset.Rmd
more intro

@@
 ```{r}
-right_side_up_file = "../data/video_right-side-up.csv"
+right_side_up_file = "../src/data/video_right-side-up.csv"
 right_side_up =read.csv(right_side_up_file)
@@
 ```{r}
-metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"
+metadata_file = "../src/data/SAYcam-2019-12-0922_54_28.csv"
 

### 2020-01-12 paper/cogsci/paper.Rmd
more intro

@@
     \AND {\large \bf Ketan Jay Agarwal (agrawalk@stanford.edu)} 
-    \AND {\large \bf Michael C. Frank (mcfrank@stanford.edu)} \\ Department of Psychology, Street Address \\ Stanford, CA 91305 USA}
+    \AND {\large \bf Michael C. Frank (mcfrank@stanford.edu)} \\ 
+    Department of Psychology, Street Address \\ Stanford, CA 91305 USA}
 
 abstract: >
-    Faces are a critical part of infants' visual experience, as they convey social and 
-    linguistic information.
+    The faces and hands of infants' caregivers and other social partners offer a rich source of social and
+    causal information that may be critical for infants' cognitive and linguistic development.
 
 keywords: >
-    Add your choice of indexing terms or keywords; kindly use a semi-colon; between each term.
+    social cognition; face perception; infancy; head cameras; deep learning
 
@@
 
+Infants are famously confronted by a blooming, buzzing onslaught of stimuli (James, 1891) which they must learn to parse and navigate as their cognitive and social skills develop.
+Fortunately, they can depend on regularities not only in their visual environments [@Aslin2009] and linguistic environments, but also in the presence and actions of their caregivers and other social partners [@].
+From a very young age, infants show great attention to faces CITE, and indeed faces are a critical part of infants' visual experience as an important conduit of social and linguistic information.
+As infants mature, they begin to also attend more to the manual actions taken by their social partners, engaging in joint attention to objects and events around them. 
+Such episodes are prompted not only by a glance from a caregiver, but also through pointing and offering; thus, hands are also an important carrier of information, especially relevant for learning language and actions.
+It is unsurprising, then, that both hands and faces are prevalent in even young infants' visual experiences, as evidenced through analyses of egocentric views collected with head-mounted cameras (i.e., headcams; CITES).
+
+Of course, not only is children's interest and attention to hands and faces
+
 Previous work has suggested:
-- Relative changes in prevalence of faces vs.
-hands (Fausey 2016), though perhaps this is driven by infants younger than 4 months of age (e.g., Jayaraman, Fausey, & Smith, 2015; Sugden, Mohamed-Ali, & Moulson, 2014) who see both more frequent and more persistent faces (Jayaraman & Smith, 2018)
 
-- Surprising attention to hand movements and their interactions with objects (Yu & Smith, 2013), particularly in older infants
+Previous work has found changes in the prevalence of faces vs.
+hands for infants of different ages.
+For example, Fausey et al.
+[-@Fausey2016] found that infants less than 12 months of age received face-dense input, relative to 1- to 2-year-olds who received more hand-dense input.
+However, it may be that this effect is driven by infants younger than 4 months of age [e.g., @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018].
+Once infants begin to crawl (~6 months) they may see far fewer hands and faces, overall.
 
-- Differences in the availability of social information depending on motor abilities (Sanchez, Long et al., 2018 CogSci; @Franchak2011 and more)
+Earlier work has also found surprising attention to hand movements and their interactions with objects (Yu & Smith, 2013), particularly in older infants (ages?).
+
+Differences in the availability of social information depending on motor abilities [@Sanchez2018; @Franchak2011] (more Franchak papers?)
 
@@
 
-Here, we analyze a longitudinal corpus of head-mounted camera data, leveraging over XX hours of videos from XX children, totaling more than XX frames.  
-(briefly describe dataset; sampling strategy: location of two households, number of hours of video, variability in location, etc; reference published paper on what this dataset is, large field of view (fisheye lens))
+Here, we analyze the SAYcam dataset [@SAYcam], a longitudinal corpus of head-mounted camera data comprising more than 1700 videos from three children, for a total of over 300 hours of videos (>100 million frames).
+Over a span of 6 to 32 months of age, the three children (S, A, and Y) in the dataset wore headcams at least twice weekly, for approximately one hour per recording session. 
+One weekly session was on the same day each week at a roughly constant time of day, while the other(s) were chosen arbitrarily at the participating family's discretion.
+
+This dataset differs in four key ways: 1) number of hours/frames 2) not just mealtimes--naturalistic sample of many contexts, 3) longitudinal, 4) much larger field-of-view.
 
@@
 
-Part 1: How well can we capture social information using computer vision?
-- Description of OpenPose (Figure 1) 
-- Description of annotation strategy (24K by Ketan, ~4K on turk, reliability)
-- Describe main P/R/F statistics for 24K for faces and hands; interpret. Relatively higher precision vs. recall.
+# Method
+
+## Dataset
+
+(briefly describe dataset; sampling strategy: location of two households, number of hours of video, variability in location, etc; reference published paper on what this dataset is, large field of view (fisheye lens))
+(109 degrees horizontal x 70 degrees vertical)
+
+## Part 1: How well can we capture social information using computer vision?
+
+### Description of OpenPose (Figure 1) 
+To automatically annotate the millions of frames in SAYcam, we use OpenPose [@Cao2018openpose; @Simon2017hand], a computer vision model optimized for jointly detecting human face, body, hand, and foot keypoints (135 in total) that operates well on scenes including multiple people even if they are partially-occluded.
+
+### Description of annotation strategy (24K by Ketan, 4K on Amazon Mechanical Turk, reliability)
+To test the validity of OpenPose's hand and face detections, we compared to human annotations of 24,000 frames selected uniformly at random from the videos of two children (S and A).
+
+### Describe main PRF statistics for 24K for faces and hands; interpret.
+Relatively higher precision vs. recall.
 - P/R/F variation across child/age for faces
@@
     - Faces: weird viewpoints, occluded/side viewpoint, faces in books
-    - Hands: children’s own hands, hands in books, side viewpoints
+    - Hands: children's own hands, hands in books, side viewpoints
 - Describe additional child vs. hand annotation; P/R/F variation across child vs. adult hands (better for adult hands, still OK for child hands)
 
-Part 2: Access to social information across age
-Prevalence of hands vs faces across age (in goldset, full dataset) (Figure 2)
-Why so many hands? 
-More child hands as in gold set
-Cropped analysis
+## Part 2: Access to social information across age
 
-Variation across location contexts (goldset, full dataset)
+### Prevalence of hands vs faces across age (in goldset, full dataset) (Figure 2)
 
-# Method
+### Why so many hands?
 
-If the authors' names are
-included in the sentence, place only the year in parentheses, as in
-[-@Franchak2011], but otherwise place the entire reference in
-parentheses with the authors and year separated by a comma
-[@Fausey2016]. List multiple references alphabetically and
+### More child hands as in gold set
+
+## Field-of-View Comparison
+
+The field of view (FOV) of the fisheye lens used in @SAYcam is much wider (109 degrees horizontal x 70 degrees vertical) than the FOV of the lens used in @Fausey2016 (69 deg. x 41 deg.). 
+Looks like child hands make up about ~34% of the hands detected in our gold set (in Fausey 2016, they are only 8% of the hands). 
+Furthermore, a lot of the lower proportions of hands come from the infants <6 months of age.
+
+## Variability by Location
+
+Next we examine variation in the presence of hands and faces across different locations.
+Of the 3,027 videos, the content of 1,829 have been manually manuallly annotated for filming location, activities taking place, and visible objects (see @SAYcam). 
+To give a sense of the contexts the children experienced, the most frequent filming locations were the living room (339 videos), bedroom (182), kitchen (150), outside on property (129), child's bedroom (81), deck/porch (73), hallway (70), and off property (57).
+Filming only took place twice in the dining room.
+
+The most frequent activities were sitting (410), playing (375), being held (352), and standing (297). Eating was the 11th most-frequent activity (117 videos).
+
+(goldset, full dataset)
+
+List multiple references alphabetically and
 separate them by semicolons [@Frank2012; @Smith2011].
-Use the et. al. construction only after listing all the authors to a
-publication in an earlier reference and for citations with four or
-more authors.
 

### 2020-01-12 paper/cogsci/paper.tex
more intro

@@
 \begin{abstract}
-Faces are a critical part of infants' visual experience, as they convey
-social and linguistic information.
+The faces and hands of infants' caregivers and other social partners
+offer a rich source of social and causal information that may be
+critical for infants' cognitive and linguistic development.
 
 \textbf{Keywords:}
-Add your choice of indexing terms or keywords; kindly use a semi-colon;
-between each term.
+social cognition; face perception; infancy; head cameras; deep learning
 \end{abstract}
@@
 
-Previous work has suggested: - Relative changes in prevalence of faces
-vs.~hands (Fausey 2016), though perhaps this is driven by infants
-younger than 4 months of age (e.g., Jayaraman, Fausey, \& Smith, 2015;
-Sugden, Mohamed-Ali, \& Moulson, 2014) who see both more frequent and
-more persistent faces (Jayaraman \& Smith, 2018)
+Infants are famously confronted by a blooming, buzzing onslaught of
+stimuli (James, 1891) which they must learn to parse and navigate as
+their cognitive and social skills develop. Fortunately, they can depend
+on regularities not only in their visual environments (Aslin, 2009) and
+linguistic environments, but also in the presence and actions of their
+caregivers and other social partners {[}@{]}. From a very young age,
+infants show great attention to faces CITE, and indeed faces are a
+critical part of infants' visual experience as an important conduit of
+social and linguistic information. As infants mature, they begin to also
+attend more to the manual actions taken by their social partners,
+engaging in joint attention to objects and events around them. Such
+episodes are prompted not only by a glance from a caregiver, but also
+through pointing and offering; thus, hands are also an important carrier
+of information, especially relevant for learning language and actions.
+It is unsurprising, then, that both hands and faces are prevalent in
+even young infants' visual experiences, as evidenced through analyses of
+egocentric views collected with head-mounted cameras (i.e., headcams;
+CITES).
 
-\begin{itemize}
-\item
-  Surprising attention to hand movements and their interactions with
-  objects (Yu \& Smith, 2013), particularly in older infants
-\item
-  Differences in the availability of social information depending on
-  motor abilities (Sanchez, Long et al., 2018 CogSci; Franchack papers)
-\end{itemize}
+Of course, not only is children's interest and attention to hands and
+faces
+
+Previous work has suggested:
+
+Previous work has found changes in the prevalence of faces vs.~hands for
+infants of different ages. For example, Fausey et al. (2016) found that
+infants less than 12 months of age received face-dense input, relative
+to 1- to 2-year-olds who received more hand-dense input. However, it may
+be that this effect is driven by infants younger than 4 months of age
+(e.g., Jayaraman, Fausey, \& Smith, 2015; Sugden, Mohamed-Ali, \&
+Moulson, n.d.) who see both more frequent and more persistent faces
+(Jayaraman \& Smith, 2018). Once infants begin to crawl
+(\textasciitilde{}6 months) they may see far fewer hands and faces,
+overall.
+
+Earlier work has also found surprising attention to hand movements and
+their interactions with objects (Yu \& Smith, 2013), particularly in
+older infants (ages?).
+
+Differences in the availability of social information depending on motor
+abilities (Franchak, Kretch, Soska, \& Adolph, 2011; Sanchez, Long,
+Kraus, \& Frank, 2018) (more Franchak papers?)
 
@@
 
-Here, we analyze a longitudinal corpus of head-mounted camera data,
-leveraging over XX hours of videos from XX children, totaling more than
-XX frames. \{briefly describe dataset; sampling strategy: location of
-two households, number of hours of video, variability in location, etc;
-reference published paper on what this dataset is, large field of view
-(fisheye lens))
+Here, we analyze the SAYcam dataset (Sullivan, Mei, Perfors, Wojcik, \&
+Frank, n.d.), a longitudinal corpus of head-mounted camera data
+comprising more than 1700 videos from three children, for a total of
+over 300 hours of videos (\textgreater{}100 million frames). Over a span
+of 6 to 32 months of age, the three children (S, A, and Y) in the
+dataset wore headcams at least twice weekly, for approximately one hour
+per recording session. One weekly session was on the same day each week
+at a roughly constant time of day, while the other(s) were chosen
+arbitrarily at the participating family's discretion.
+
+This dataset differs in four key ways: 1) number of hours/frames 2) not
+just mealtimes--naturalistic sample of many contexts, 3) longitudinal,
+4) much larger field-of-view.
 
@@
 extracting social information from these egocentric viewpoints on a
-small subset of randomly selected frames from the dataset. We then apply
-these methods at scale to the larger dataset, allowing us to extract key
-descriptive variables hypothesized to vary across development.
+small subset of randomly selected frames from the dataset.\\
+We then apply these methods at scale to the larger dataset, allowing us
+to extract key descriptive variables hypothesized to vary across
+development.
 
-Part 1: How well can we capture social information using computer
-vision? - Description of OpenPose (Figure 1) - Description of annotation
-strategy (24K by Ketan, \textasciitilde{}4K on turk, reliability) -
-Describe main P/R/F statistics for 24K for faces and hands; interpret.
+\hypertarget{method}{%
+\section{Method}\label{method}}
+
+\hypertarget{dataset}{%
+\subsection{Dataset}\label{dataset}}
+
+(briefly describe dataset; sampling strategy: location of two
+households, number of hours of video, variability in location, etc;
+reference published paper on what this dataset is, large field of view
+(fisheye lens)) (109 degrees horizontal x 70 degrees vertical)
+
+\hypertarget{part-1-how-well-can-we-capture-social-information-using-computer-vision}{%
+\subsection{Part 1: How well can we capture social information using
+computer
+vision?}\label{part-1-how-well-can-we-capture-social-information-using-computer-vision}}
+
+\hypertarget{description-of-openpose-figure-1}{%
+\subsubsection{Description of OpenPose (Figure
+1)}\label{description-of-openpose-figure-1}}
+
+To automatically annotate the millions of frames in SAYcam, we use
+OpenPose (Cao, Hidalgo, Simon, Wei, \& Sheikh, 2018; Simon, Joo,
+Matthews, \& Sheikh, 2017), a computer vision model optimized for
+jointly detecting human face, body, hand, and foot keypoints (135 in
+total) that operates well on scenes including multiple people even if
+they are partially-occluded.
+
+\hypertarget{description-of-annotation-strategy-24k-by-ketan-4k-on-amazon-mechanical-turk-reliability}{%
+\subsubsection{Description of annotation strategy (24K by Ketan, 4K on
+Amazon Mechanical Turk,
+reliability)}\label{description-of-annotation-strategy-24k-by-ketan-4k-on-amazon-mechanical-turk-reliability}}
+
+To test the validity of OpenPose's hand and face detections, we compared
+to human annotations of 24,000 frames selected uniformly at random from
+the videos of two children (S and A).
+
+\hypertarget{describe-main-prf-statistics-for-24k-for-faces-and-hands-interpret.}{%
+\subsubsection{Describe main PRF statistics for 24K for faces and hands;
+interpret.}\label{describe-main-prf-statistics-for-24k-for-faces-and-hands-interpret.}}
+
 Relatively higher precision vs.~recall. - P/R/F variation across
@@
 
-Part 2: Access to social information across age Prevalence of hands vs
-faces across age (in goldset, full dataset) (Figure 2) Why so many
-hands? More child hands as in gold set Cropped analysis
+\hypertarget{part-2-access-to-social-information-across-age}{%
+\subsection{Part 2: Access to social information across
+age}\label{part-2-access-to-social-information-across-age}}
 
-Variation across location contexts (goldset, full dataset)
+\hypertarget{prevalence-of-hands-vs-faces-across-age-in-goldset-full-dataset-figure-2}{%
+\subsubsection{Prevalence of hands vs faces across age (in goldset, full
+dataset) (Figure
+2)}\label{prevalence-of-hands-vs-faces-across-age-in-goldset-full-dataset-figure-2}}
 
-\hypertarget{method}{%
-\section{Method}\label{method}}
+\hypertarget{why-so-many-hands}{%
+\subsubsection{Why so many hands?}\label{why-so-many-hands}}
 
-If the authors' names are included in the sentence, place only the year
-in parentheses, as in (2011), but otherwise place the entire reference
-in parentheses with the authors and year separated by a comma (Fausey,
-Jayaraman, \& Smith, 2016). List multiple references alphabetically and
-separate them by semicolons (Frank, 2012; Smith, Yu, \& Pereira, 2011).
-Use the et. al.~construction only after listing all the authors to a
-publication in an earlier reference and for citations with four or more
-authors.
+\hypertarget{more-child-hands-as-in-gold-set}{%
+\subsubsection{More child hands as in gold
+set}\label{more-child-hands-as-in-gold-set}}
+
+\hypertarget{field-of-view-comparison}{%
+\subsection{Field-of-View Comparison}\label{field-of-view-comparison}}
+
+The field of view (FOV) of the fisheye lens used in Sullivan et al.
+(n.d.) is much wider (109 degrees horizontal x 70 degrees vertical) than
+the FOV of the lens used in Fausey et al. (2016) (69 deg. x 41 deg.).
+Looks like child hands make up about \textasciitilde{}34\% of the hands
+detected in our gold set (in Fausey 2016, they are only 8\% of the
+hands). Furthermore, a lot of the lower proportions of hands come from
+the infants \textless{}6 months of age.
+
+\hypertarget{variability-by-location}{%
+\subsection{Variability by Location}\label{variability-by-location}}
+
+Next we examine variation in the presence of hands and faces across
+different locations. Of the 3,027 videos, the content of 1,829 have been
+manually manuallly annotated for filming location, activities taking
+place, and visible objects (see Sullivan et al. (n.d.)). To give a sense
+of the contexts the children experienced, the most frequent filming
+locations were the living room (339 videos), bedroom (182), kitchen
+(150), outside on property (129), child's bedroom (81), deck/porch (73),
+hallway (70), and off property (57). Filming only took place twice in
+the dining room.
+
+The most frequent activities were sitting (410), playing (375), being
+held (352), and standing (297). Eating was the 11th most-frequent
+activity (117 videos).
+
+(goldset, full dataset)
+
+List multiple references alphabetically and separate them by semicolons
+(Frank, 2012; Smith, Yu, \& Pereira, 2011).
 
@@
   \hline
-(Intercept) & 0.00 & 0.10 & 0.0 & 0.98 \\ 
-  x & 1.90 & 0.09 & 20.1 & 0.00 \\ 
+(Intercept) & -0.09 & 0.10 & -0.9 & 0.35 \\ 
+  x & 2.06 & 0.11 & 18.5 & 0.00 \\ 
    \hline
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-Aslin2009}{}%
+Aslin, R. N. (2009). How infants view natural scenes gathered from a
+head-mounted camera. \emph{Optometry and Vision Science: Official
+Publication of the American Academy of Optometry}, \emph{86}(6),
+561--565.
+
+\leavevmode\hypertarget{ref-Cao2018openpose}{}%
+Cao, Z., Hidalgo, G., Simon, T., Wei, S.-E., \& Sheikh, Y. (2018).
+OpenPose: Realtime multi-person 2D pose estimation using Part Affinity
+Fields. In \emph{ArXiv preprint arXiv:1812.08008}.
+
 \leavevmode\hypertarget{ref-Fausey2016}{}%
@@
 
+\leavevmode\hypertarget{ref-Jayaraman2015}{}%
+Jayaraman, S., Fausey, C. M., \& Smith, L. B. (2015). The faces in
+infant-perspective scenes change over the first year of life. \emph{PLoS
+One}. \url{http://doi.org/10.1371/journal.pone.0123780}
+
+\leavevmode\hypertarget{ref-Jayaraman2018}{}%
+Jayaraman, S., \& Smith, L. B. (2018). Faces in early visual
+environments are persistent not just frequent. \emph{Vision Research}.
+
+\leavevmode\hypertarget{ref-Sanchez2018}{}%
+Sanchez, A., Long, B., Kraus, A. M., \& Frank, M. C. (2018). Postural
+developments modulate children's visual access to social information. In
+\emph{Proceedings of the 40th annual conference of the cognitive science
+society}.
+
+\leavevmode\hypertarget{ref-Simon2017hand}{}%
+Simon, T., Joo, H., Matthews, I., \& Sheikh, Y. (2017). Hand keypoint
+detection in single images using multiview bootstrapping. In
+\emph{CVPR}.
+
 \leavevmode\hypertarget{ref-Smith2011}{}%
@@
 
+\leavevmode\hypertarget{ref-Sugden2014}{}%
+Sugden, N. A., Mohamed-Ali, M. I., \& Moulson, M. C. (n.d.). I spy with
+my little eye: Typical, daily exposure to faces documented from a
+first-person infant perspective. \emph{Developmental Psychobiology},
+\emph{56}(2), 249--261.
+
+\leavevmode\hypertarget{ref-SAYcam}{}%
+Sullivan, J., Mei, M., Perfors, A., Wojcik, E., \& Frank, M. (n.d.).
+Head cameras on children aged 6 months through 31 months.
+
 \bibliographystyle{apacite}

### 2020-01-13 paper/cogsci/paper.Rmd
updated intro and methods sections

--- 2020-01-11 paper/cogsci/paper.Rmd
@@
     \AND {\large \bf Ketan Jay Agarwal (agrawalk@stanford.edu)} 
-    \AND {\large \bf Michael C. Frank (mcfrank@stanford.edu)} \\ Department of Psychology, Street Address \\ Stanford, CA 91305 USA}
+    \AND {\large \bf Michael C. Frank (mcfrank@stanford.edu)} \\ 
+    Department of Psychology, Street Address \\ Stanford, CA 91305 USA}
 
 abstract: >
-    Faces are a critical part of infants' visual experience, as they convey social and 
-    linguistic information.
+    The faces and hands of infants' caregivers and other social partners offer a rich source of social and causal information that may be critical for infants' cognitive and linguistic development.
+Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants.
+The present research aims to test the generality of these findings using the SAYcam dataset (Sullivan, Mei, Perfors, Wojcik, & Frank, under review), a longitudinal collection of over 1700 headcam videos collected from three children along a span of 6 to 32 months of age.
+To do so, we validate the use of a modern convolutional neural network for pose detection (OpenPose)  for the detection of people, faces, and hands for use with these naturalistic infant egocentric videos.
+We then apply this network to the entire dataset, analyzing the prevalence of faces across age, individuals, and activity contexts.
+Overall, we find a higher prevalence of hands seen by infants than previously reported, considerably variability in the proportion of faces/hands seen across different locations (e.g., living room vs.
+kitchen), yet surprising consistency across our XX individuals.
 
 keywords: >
-    Add your choice of indexing terms or keywords; kindly use a semi-colon; between each term.
+    social cognition; face perception; infancy; head cameras; deep learning
 
@@
 library(xtable)
+library(knitr)
+library(tidyverse)
+library(assertthat)
+library(ggthemes)
+library(lme4)
+library(langcog)
+library(viridis)
+library(magick)
+library(stringr)
+library(egg)
+theme_set(theme_few())
 ```
@@
 
-Previous work has suggested:
-- Relative changes in prevalence of faces vs.
-hands (Fausey 2016), though perhaps this is driven by infants younger than 4 months of age (e.g., Jayaraman, Fausey, & Smith, 2015; Sugden, Mohamed-Ali, & Moulson, 2014) who see both more frequent and more persistent faces (Jayaraman & Smith, 2018)
+  Infants are confronted by a blooming, buzzing onslaught of stimuli (James, 1891) which they must learn to parse to make sense of the world around them.
+Yet infants do not embark on this learning process alone: infants are engaged in learning from their caregivers from early infancy.
+From as early as 3 months of age, young infants follow overt gaze shifts (@Gredeback2010), and even newborns prefer to look at faces with direct vs.
+averted gaze [@Farroni2002; @Farroni2005], despite their limited acuity.
+Faces are thus likely to be an important conduit of social information that scaffolds infants cognitive development.
+Given this importance, developmentalists have long hypothesized that faces are prevalent in the visual experience of young infants.
+However, as even the viewpoint of a walking child is not easily predicted by our own adult intuitions (Clerkin, Hart, Rehg, Yu, & Smith, 2017; Franchak et al., 2011; Yoshida & Smith, 2008), researchers have begun to record the egocentric views collected from infants and toddlers wearing head-mounted cameras to test theories about the infant perspective.
+ A growing body of work now demonstrates that the viewpoints of very young infants—less than 4 months of age—are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @Sugden2014; @Jayaraman2018].
+However, as infants mature, their perspective starts to capture views of hands paired with the objects they are acting on [@fausey2016].
+As infants learn to use their own hands to act on the world, they may focus on manual actions taken by their social partners.
+Furthermore, caregivers may start to use their hands more with communicative intent, directing infants attention with pointing and gestures to particular events or objects during play (Yu & Smith, 2013).
+	The present research aims to test the generality of these findings using the SAYcam dataset [@SAYcam], a longitudinal collection of over 1700 headcam videos collected from three children along a span of 6 to 32 months of age.
+This In addition to its size and longitudinal nature, this dataset builds on those used in previous research in two key ways.
+First, recordings were from a variety of many different naturalistic contexts, encompassing infants’ viewpoints during both activities outside and inside the home.
+Second, the cameras used in this longitudinal study encompassed a much wider field of view than those typically used, allowing a more complete picture of the infant perspective.
+  However, with many hundreds of hours of footage (>100M frames), this large dataset truly necessitates a shift to an automated annotation strategy.
+Indeed, annotation of the frames extracted from egocentric videos has been to be prohibitively time-consuming, meaning that many of the frames are not inspected.
+For example, in @fausey2016, collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand annotated (by four coders), totalling 103,383 frames (per coder)—an impressive number of annotations but nonetheless only 0.67% of the collected footage.
+To address this challenge, we  first validate the use modern computer vision model [@cao2017realtime] to automatically detect the presence of hands and faces from the infant egocentric viewpoint.
+In particular, we focus on OpenPose   [@cao2017realtime], a model optimized for jointly detecting human face, body, hand, and foot keypoints (135 in total) that operates well on scenes including multiple people even if they are partially-occluded (see Figure 1).
+We then apply these methods at scale to the larger dataset, allowing us to analyze the proportion of faces and hands observed by each child across age and activity context.
 
-- Surprising attention to hand movements and their interactions with objects (Yu & Smith, 2013), particularly in older infants
+# Method
 
-- Differences in the availability of social information depending on motor abilities (Sanchez, Long et al., 2018 CogSci; @Franchak2011 and more)
+## Dataset
 
-One limitation of past work is that it has relied on cross-sectional data, and thus cannot speak to whether these trajectories are present in individual children.
+Videos captured by the headcam were 680x480 pixels, and a fisheye lens was attached to the camera to increase 109 degrees horizontal x 70 degrees vertical.
+Children wore headcams at least twice weekly, for approximately one hour per recording session.
+One weekly session was on the same day each week at a roughly constant time of day, while the other(s) were chosen arbitrarily at the participating family’s discretion.
+At the time of the recording, all three children were only children.
+Videos with technical errors or that were not taken from the egocentric perspective were excluded from the dataset.
+All videos are available at https://nyu.databrary.org/volume/564.
+)
 
-Here, we analyze a longitudinal corpus of head-mounted camera data, leveraging over XX hours of videos from XX children, totaling more than XX frames.  
-(briefly describe dataset; sampling strategy: location of two households, number of hours of video, variability in location, etc; reference published paper on what this dataset is, large field of view (fisheye lens))
+## Part 1: How well can we capture social information using computer vision?
 
-To do so, we first test and validate novel computer vision methods for extracting social information from these egocentric viewpoints on a small subset of randomly selected frames from the dataset.
-We then apply these methods at scale to the larger dataset, allowing us to extract key descriptive variables hypothesized to vary across development.
+### Computer vision model (OpenPose)
+To automatically annotate the millions of frames in SAYcam, we use OpenPose [@Cao2018openpose; @Simon2017hand], a computer vision model optimized for jointly detecting human face, body, hand, and foot keypoints (135 in total) that operates well on scenes including multiple people even if they are partially-occluded.
+This CNN-based pose detector (OpenPose; Cao et al., 2017; Simon, Joo, Matthews, & Sheikh, 2017; Wei, Ramakrishna, Kanade, & Sheikh, 2016) provided the locations of 18 body parts (ears, nose, wrists, etc.) and is available at https://github.com/ CMU-Perceptual-Computing-Lab/openpose.
+The system uses a CNN for initial anatomical detection and subsequently applies part affinity fields (PAFs) for part association, producing a series of body part candidates.
+The candidates are then matched to a single individual and finally assembled into a pose; here, we only made use of outputs of the face and hand detection modules.
 
-Part 1: How well can we capture social information using computer vision?
-- Description of OpenPose (Figure 1) 
-- Description of annotation strategy (24K by Ketan, ~4K on turk, reliability)
-- Describe main P/R/F statistics for 24K for faces and hands; interpret. Relatively higher precision vs. recall.
+### Manual annotation strategy
+To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from the videos of two children (S and A); Frames were jointly annotated for the presence of faces and hands.
+These randomly sampled frames covered XX of the videos present in the dataset.
+A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated XX frames; agreement with the primary coder was XX%.
+
+### Describe main PRF statistics for 24K for faces and hands; interpret.
+Relatively higher precision vs. recall.
 - P/R/F variation across child/age for faces
@@
     - Faces: weird viewpoints, occluded/side viewpoint, faces in books
-    - Hands: children’s own hands, hands in books, side viewpoints
+    - Hands: children's own hands, hands in books, side viewpoints
 - Describe additional child vs. hand annotation; P/R/F variation across child vs. adult hands (better for adult hands, still OK for child hands)
 
-Part 2: Access to social information across age
-Prevalence of hands vs faces across age (in goldset, full dataset) (Figure 2)
-Why so many hands? 
-More child hands as in gold set
-Cropped analysis
+## Part 2: Access to social information across age
 
-Variation across location contexts (goldset, full dataset)
+### Prevalence of hands vs faces across age (in goldset, full dataset) (Figure 2)
 
-# Method
+### Why so many hands?
 
-If the authors' names are
-included in the sentence, place only the year in parentheses, as in
-[-@Franchak2011], but otherwise place the entire reference in
-parentheses with the authors and year separated by a comma
-[@Fausey2016]. List multiple references alphabetically and
-separate them by semicolons [@Frank2012; @Smith2011]. 
-Use the et. al. construction only after listing all the authors to a
-publication in an earlier reference and for citations with four or
-more authors.
+### More child hands as in gold set
 
-You might want to display a wide figure across both columns.
-To do this, you change the `fig.env` chunk option to `figure*`.
-To align the image in the center of the page, set `fig.align` option to `center`.
-To format the width of your caption text, you set the `num.cols.cap` option to `2`.
+## Field-of-View Comparison
+The field of view (FOV) of the fisheye lens used in @SAYcam is much wider (109 degrees horizontal x 70 degrees vertical) than the FOV of the lens used in @Fausey2016 (69 deg. x 41 deg.). 
+Looks like child hands make up about ~34% of the hands detected in our gold set (in Fausey 2016, they are only 8% of the hands). 
+Furthermore, a lot of the lower proportions of hands come from the infants <6 months of age.
 
-## One-column images
+## Variability by Location
 
-Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.
+Next we examine variation in the presence of hands and faces across different locations.
+Of the 3,027 videos, the content of 1,829 `r length(unique(meta$File.Name))` have been manually manuallly annotated for filming location, activities taking place, and visible objects (see @SAYcam).
 
-```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
-img <- png::readPNG("figs/lab_logo_stanford.png")
-grid::grid.raster(img)
-```
+To give a sense of the contexts the children experienced, the most frequent filming locations were the living room (339 videos), bedroom (182), kitchen (150), outside on property (129), child's bedroom (81), deck/porch (73), hallway (70), and off property (57).
+Filming only took place twice in the dining room.
 
-## R Plots
+The most frequent activities were sitting (410), playing (375), being held (352), and standing (297). Eating was the 11th most-frequent activity (117 videos).
 
-You can use R chunks directly to plot graphs. And you can use latex floats in the
-fig.pos chunk option to have more control over the location of your plot on the page.
-For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**
-
-```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
-x <- 0:100
-y <- 2 * (x + rnorm(length(x), sd = 3) + 3)
-
-ggplot2::ggplot(data = data.frame(x, y), 
-                aes(x = x, y = y)) + 
-  geom_point() + 
-  geom_smooth(method = "lm")
-```
-
-## Tables
-
-You can use the xtable function in the xtable package.
-
-```{r xtable, results="asis"}
-n <- 100
-x <- rnorm(n)
-y <- 2*x + rnorm(n)
-out <- lm(y ~ x)
-
-tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
-                       caption = "This table prints across one column.")
-
-print(tab1, type="latex", comment = F, table.placement = "H")
-```
+(goldset, full dataset)
 
@@
 
+Demonstrate
+(1) Need to think about the child's viewpoint relative to actual FOV as well as attent
 Fausey 2016: 103,383 images; 

### 2020-01-14 src/get_all_openpose_bounding_boxes.R
scripts for getting bounding boxes and saving as RData

@@ -1,0 +1,31 @@
+
+# load bounding boxes from openpose detections from the entire dataset
+# (created in get_bounding_boxes_per_vid.py using numpy vectors in $GROUP_SCRATCH/openpose_flattened_whole)
+
+# 1,387 videos so far
+
+require(data.table)
+require(here)
+require(stringr)
+
+files <- list.files("../src/bounding_boxes") # 1632 vids
+# A_20140630_2117_04_bounding_boxes.csv had no detections
+
+df <- data.frame()
+
+#had to specify columns to get rid of the total column
+for (i in 1:length(files)) {
+  tmp <- fread(paste("../src/bounding_boxes", files[i], sep='/'), stringsAsFactors = F) 
+  if(ncol(tmp)==9) {
+    tmp$V1 = NULL
+    tmp$vid_name = str_remove(files[i], "_bounding_boxes.csv")
+    # remove any rows with all 0 bounding box + confidences (~50%)
+    tmp = subset(tmp, mean_confidence!=0)
+    #df <- rbindlist(list(df, tmp)) # , use.names = T
+    df = rbind(df, tmp)
+  } else {
+    print(paste("check file: ",files[i]))
+  }
+}
+
+save(df, file="all_bounding_boxes.RData")

### 2020-01-14 paper/cogsci/paper.Rmd
edits and updates from Google doc

@@
 ---
-title: "Quantifying social information in natural infant visual experience"
+title: "A longitudinal investigation of the social information in natural infant visual experience"
 bibliography: library.bib
@@
     Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants. 
-The present research aims to test the generality of these findings using the SAYcam dataset (Sullivan, Mei, Perfors, Wojcik, & Frank, under review), a longitudinal collection of over 1700 headcam videos collected from three children along a span of 6 to 32 months of age.
-To do so, we validate the use of a modern convolutional neural network for pose detection (OpenPose)  for the detection of people, faces, and hands for use with these naturalistic infant egocentric videos.
-We then apply this network to the entire dataset, analyzing the prevalence of faces across age, individuals, and activity contexts.
+    The present research aims to test the generality of these findings using the SAYcam dataset [@SAYcam], a longitudinal collection of over 1700 headcam videos collected from three children along a span of 6 to 32 months of age.
+    To do so, we validate the use of a modern convolutional neural network for pose detection (OpenPose) for the detection of people, faces, and hands to analyze these naturalistic infant egocentric videos.
+    We then apply this model to the entire dataset, analyzing the prevalence of faces across age, individuals, and activity contexts. 
     Overall, we find a higher prevalence of hands seen by infants than previously reported, considerably variability in the proportion of faces/hands seen across different locations (e.g., living room vs.
-kitchen), yet surprising consistency across our XX individuals.
+kitchen), yet surprising consistency across both individual children.
 
@@
 Yet infants do not embark on this learning process alone: infants are engaged in learning from their caregivers from early infancy. 
-From as early as 3 months of age, young infants follow overt gaze shifts (@Gredeback2010), and even newborns prefer to look at faces with direct vs.
-averted gaze [@Farroni2002; @Farroni2005], despite their limited acuity.
+From as early as 3 months of age, young infants follow overt gaze shifts [@Gredeback2010], and even newborns prefer to look at faces with direct vs.
+averted gaze [@Farroni2002], despite their limited acuity [CITE].
 Faces are thus likely to be an important conduit of social information that scaffolds infants cognitive development. 
-Given this importance, developmentalists have long hypothesized that faces are prevalent in the visual experience of young infants.
-However, as even the viewpoint of a walking child is not easily predicted by our own adult intuitions (Clerkin, Hart, Rehg, Yu, & Smith, 2017; Franchak et al., 2011; Yoshida & Smith, 2008), researchers have begun to record the egocentric views collected from infants and toddlers wearing head-mounted cameras to test theories about the infant perspective.
- A growing body of work now demonstrates that the viewpoints of very young infants—less than 4 months of age—are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @Sugden2014; @Jayaraman2018].
-However, as infants mature, their perspective starts to capture views of hands paired with the objects they are acting on [@fausey2016].
+Given this importance, developmentalists have long hypothesized [CITE] that faces are prevalent in the visual experience of young infants. 
+However, as even the viewpoint of a walking child is not easily predicted by our own adult intuitions (Clerkin, Hart, Rehg, Yu, & Smith, 2017; @Franchak2011; @Yoshida2008), researchers have begun to record the egocentric views collected from infants and toddlers wearing head-mounted cameras to test theories about the infant perspective.
+
+A growing body of work now demonstrates that the viewpoints of very young infants--less than 4 months of age--are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @Sugden2014; @Jayaraman2018].
+However, as infants mature, their perspective starts to capture views of hands paired with the objects they are acting on [@Fausey2016]. 
 As infants learn to use their own hands to act on the world, they may focus on manual actions taken by their social partners. 
 Furthermore, caregivers may start to use their hands more with communicative intent, directing infants attention with pointing and gestures to particular events or objects during play (Yu & Smith, 2013).
+
 The present research aims to test the generality of these findings using the SAYcam dataset [@SAYcam], a longitudinal collection of over 1700 headcam videos collected from three children along a span of 6 to 32 months of age.
-This In addition to its size and longitudinal nature, this dataset builds on those used in previous research in two key ways.
+In addition to its size and longitudinal nature, this dataset builds on those used in previous research in two key ways. 
 First, recordings were from a variety of many different naturalistic contexts, encompassing infants’ viewpoints during both activities outside and inside the home. 
 Second, the cameras used in this longitudinal study encompassed a much wider field of view than those typically used, allowing a more complete picture of the infant perspective.
-  However, with many hundreds of hours of footage (>100M frames), this large dataset truly necessitates a shift to an automated annotation strategy.
+
+However, with hundreds of hours of footage (>30M frames), this large dataset truly necessitates a shift to an automated annotation strategy. 
 Indeed, annotation of the frames extracted from egocentric videos has been to be prohibitively time-consuming, meaning that many of the frames are not inspected. 
-For example, in @fausey2016, collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand annotated (by four coders), totalling 103,383 frames (per coder)—an impressive number of annotations but nonetheless only 0.67% of the collected footage.
-To address this challenge, we  first validate the use modern computer vision model [@cao2017realtime] to automatically detect the presence of hands and faces from the infant egocentric viewpoint.
-In particular, we focus on OpenPose   [@cao2017realtime], a model optimized for jointly detecting human face, body, hand, and foot keypoints (135 in total) that operates well on scenes including multiple people even if they are partially-occluded (see Figure 1).
+For example, @Fausey2016, collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand annotated (by four coders), totalling 103,383 frames (per coder)--an impressive number of annotations but nonetheless only 0.67% of the collected footage.
+To address this challenge, we first validate the use of a modern computer vision model [@Cao2018openpose] to automatically detect the presence of hands and faces from the infant egocentric viewpoint. 
+In particular, we focus on OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints (135 in total) that operates well on scenes including multiple people even if they are partially-occluded (see Figure 1).
 We then apply these methods at scale to the larger dataset, allowing us to analyze the proportion of faces and hands observed by each child across age and activity context.
+
+In the following paper, we first describe the dataset and the pose model used in the following analyses and validate the use of this model for extracting our key descriptive variables by comparing to a human-annotated gold set of 24,000 frames.
+Next, we analyze key descriptive variables, including those that have been previously reported to vary across age, including the relative proportions of faces vs.
+hands and the sizes of the faces, over the entire dataset (30M frames), finding a greater prevalence of hands than has been previously reported.
+We then investigate sources of variability in our more naturalistic dataset that may explain these differences, including a diversity of activity contexts as well as a larger field of view captured by our cameras.
 
@@
 
-Videos captured by the headcam were 680x480 pixels, and a fisheye lens was attached to the camera to increase 109 degrees horizontal x 70 degrees vertical.
+Videos captured by the headcam were 640x480 pixels, and a fisheye lens was attached to the camera to increase 109 degrees horizontal x 70 degrees vertical. 
 Children wore headcams at least twice weekly, for approximately one hour per recording session. 
-One weekly session was on the same day each week at a roughly constant time of day, while the other(s) were chosen arbitrarily at the participating family’s discretion.
-At the time of the recording, all three children were only children.
-Videos with technical errors or that were not taken from the egocentric perspective were excluded from the dataset.
-All videos are available at https://nyu.databrary.org/volume/564.
-)
+One weekly session was on the same day each week at a roughly constant time of day, while the other(s) were chosen arbitrarily at the participating family's discretion. 
+At the time of the recording, all three children were in single-child households. 
+Videos[^1] with technical errors or that were not taken from the egocentric perspective were excluded from the dataset.
+We analyze 1,636 videos, with a total duration of XX hours (XX million frames).
+
+[^1]: All videos are available at https://nyu.databrary.org/volume/564
 
@@
 
-### Computer vision model (OpenPose)
+### Computer vision model
 To automatically annotate the millions of frames in SAYcam, we use OpenPose [@Cao2018openpose; @Simon2017hand], a computer vision model optimized for jointly detecting human face, body, hand, and foot keypoints (135 in total) that operates well on scenes including multiple people even if they are partially-occluded.
-This CNN-based pose detector (OpenPose; Cao et al., 2017; Simon, Joo, Matthews, & Sheikh, 2017; Wei, Ramakrishna, Kanade, & Sheikh, 2016) provided the locations of 18 body parts (ears, nose, wrists, etc.) and is available at https://github.com/ CMU-Perceptual-Computing-Lab/openpose.
+This convolutional neural network (CNN)-based pose detector[^2] provided the locations of 18 body parts (ears, nose, wrists, etc.). 
 The system uses a CNN for initial anatomical detection and subsequently applies part affinity fields (PAFs) for part association, producing a series of body part candidates. 
@@
 
+[^2]: https://github.com/CMU-Perceptual-Computing-Lab/openpose
+
 ### Manual annotation strategy
-To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from the videos of two children (S and A); Frames were jointly annotated for the presence of faces and hands.
+To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from the 1,636 videos of two children (S and A).
+Frames were jointly annotated for the presence of faces and hands. 
 These randomly sampled frames covered XX of the videos present in the dataset.  
@@
 
-### Describe main PRF statistics for 24K for faces and hands; interpret.
-Relatively higher precision vs. recall.
-- P/R/F variation across child/age for faces
-- Describe possible sources of variation that decrease scores for:
-    - Faces: weird viewpoints, occluded/side viewpoint, faces in books
-    - Hands: children's own hands, hands in books, side viewpoints
-- Describe additional child vs. hand annotation; P/R/F variation across child vs. adult hands (better for adult hands, still OK for child hands)
+### Detection accuracy for faces and hands
+Overall, we found that face detections were slightly more accurate than hand detections,
+
+Precision and recall (F-score) variation across child/age for faces
+
+Describe possible sources of variation that decrease scores for:
+-Faces: weird viewpoints, occluded/side viewpoint, faces in books
+-Hands: children's own hands, hands in books, side viewpoints
+
+Describe additional child vs. hand annotation; P/R/F variation across child vs. adult hands (better for adult hands, still OK for child hands)
 
@@
 
-### Prevalence of hands vs faces across age (in goldset, full dataset) (Figure 2)
+Next, we analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands that were in view for each child. 
+Data from videos were binned according to the age of the child (in weeks) (see Figure XX). 
+First, we saw that the proportion of faces in view showed a moderate decrease across this age range, both when analyzing the random 24K frames as well as the entire dataset. 
+While these trends appear somewhat different than those observed in @Fausey2016, note that @Fausey2016 included data from very young infants (starting at 2 months while), while here the youngest videos coming from S and A around 6 and 9 months of age, respectively.
+Similarly, our age range extends 8 months later than those infants in @Fausey2016, throughout a portion of third year of life.
 
-### Why so many hands?
+However, the most striking result from the dataset is a much greater proportion of hands in view than have previously been reported. 
+We found this to be true across all ages, in both children, and regardless of whether we analyzed human annotations (on the 24K random subset) or the entire dataset.   
+One reason this could be the case is the much larger field of view that was captured by the cameras used in this study: unlike previous studies, our cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible.
+Thus, the field of view (FOV) of the fisheye lens used in @SAYcam was much wider (109 degrees horizontal x 70 degrees vertical) than the FOV of the lens used in @Fausey2016 (69 x 41 degrees).
+This larger field of view may have allowed the SAYcam cameras to capture not only the presence of a social partner’s hands interacting with objects, but also the children’s own hands, leading to more frequent hand detections.
 
-### More child hands as in gold set
+To assess this possibility, we obtained annotations for a subsample of XX frames in which a hand was detected in the random gold set; participants (recruited via AMT) were asked to draw bounding boxes around children’s hands and adult hands.
+Overall, we found that 34% of the hands detected by OpenPose in the random 24K sample were of children’s own hands (compared to 8% reported in @Fausey2016) suggesting that this difference in field of view did contribute substantially to the higher rate of detections in the frames.
+Heatmaps of the bounding boxes obtained from these annotations can be seen in Figure XX, showing that children’s hands tended to appear in the lower half of the frames.
 
-## Field-of-View Comparison
-The field of view (FOV) of the fisheye lens used in @SAYcam is much wider (109 degrees horizontal x 70 degrees vertical) than the FOV of the lens used in @Fausey2016 (69 deg. x 41 deg.). 
-Looks like child hands make up about ~34% of the hands detected in our gold set (in Fausey 2016, they are only 8% of the hands). 
-Furthermore, a lot of the lower proportions of hands come from the infants <6 months of age.
+We thus re-analyzed the entire dataset while restricting our analysis to a smaller, middle portion of the frame comparable to the field of view used in @Fausey2016 (XX vs XX degrees).
+To do so, we excluded hand detections that occurred in the bottom 40% of the frame, while retaining all detections that occurred in the top of the frame.  
+Overall, we found X, suggesting Y.
 
-## Variability by Location
+Intriguingly, we observed an unexpected trend in which the relative proportion of faces vs. hands increased during the third year of life; in particular, this seemed...(save for discussion?)
 
+### Variability by Location 
 Next we examine variation in the presence of hands and faces across different locations. 
-Of the 3,027 videos, the content of 1,829 `r length(unique(meta$File.Name))` have been manually manuallly annotated for filming location, activities taking place, and visible objects (see @SAYcam).
+Of the XX videos, the content of 1,829 have been manually annotated for filming location, activites taking place, and visible objects (see @SAYcam).
+XX of the videos were filmed in a single location, representing XX% of the dataset and roughly XX million frames (see @SAYcam). 
+To give a sense of the contexts the children experienced, the most frequent filming locations were the living room (339 videos), bedroom (182), kitchen (150), outside on property (129), child's bedroom (81), deck/porch (73), hallway (70), and off property (57).
+Filming only took place twice in the dining room (see Figure XX). 
+Activities varied predictability by these locations: for example, eating and XX occured in the kitchen, whereas playtime was the dominant activity in the living room (see Figure XX). 
+Bria: analyze activity
 
-To give a sense of the contexts the children experienced, the most frequent filming locations were the living room (339 videos), bedroom (182), kitchen (150), outside on property (129), child's bedroom (81), deck/porch (73), hallway (70), and off property (57).
-Filming only took place twice in the dining room.
-
-The most frequent activities were sitting (410), playing (375), being held (352), and standing (297). Eating was the 11th most-frequent activity (117 videos).
+Not this, but point out that eating was not frequent:
+The most frequent activities were sitting (410), playing (375), being held (352), and standing (297). 
+Eating was the 11th most-frequent activity (117 videos).
 
@@
 
-Demonstrate
-(1) Need to think about the child's viewpoint relative to actual FOV as well as attent
+We demonstrate the feasibility of using modern computer vision models to vastly increase the efficiency of processing egocentric headcam footage, allowing us to annotate 100% of even very large datasets for the presence and size of people, hands, and faces.
+We validate the use of this model by comparing to a human-annotated gold set, and find X.
+
+Analyzing this dataset has yielded a better understanding of infants' evolving access and attention to social information.
+
+Need to think about the child's viewpoint relative to actual FOV as well as attention
+
 Fausey 2016: 103,383 images; 

### 2020-01-14 analysis/analysis_fulldataset.Rmd
add code for cropped analysis

--- 2020-01-11 analysis/analysis_fulldataset.Rmd
@@
   rename(vid_name = video)
-
 ```
@@
 
-### Load in detections from preprocessed Rdata file; 
+### Load in detections & bounding boxes from preprocessed Rdata file; 
 ```{r eval=FALSE}
@@
 load('../data/openpose_detections.RData')
+
 ```
 
-### Preprocess data (doesn't exceute; loads processed data below)
+### Preprocess data (doesn't execute in markdown; loads processed data below)
 ```{r eval=FALSE}
@@
 
-# reset levels of vid_name in big detections array (very slow rowwise)
+# reset levels of vid_name in big detections array for detections & bb (very slow rowwise)
 levels(detections$vid_name) <- all_video_names$vid_name
 
-# join with metadata and flip the videos
+# join with metadata and exclude bad videos
 d_all <- detections %>%
@@
   filter(!vid_name %in% flipped_videos$vid_name) 
+remove(detections)
+```
 
+### Now do the same for bounding box data
+```{r}
+load('../data/vid_info.RData')
+load("../data/all_bounding_boxes.Rdata")
+
+bb_all <- df
+bb_all$vid_name = as.factor(bb_all$vid_name)
+levels(bb_all$vid_name) <- all_video_names$vid_name
+
+bb_all <- bb_all %>%
+  filter(!vid_name %in% flipped_videos$vid_name) 
+  left_join(vid_info, by='vid_name') 
+  #
+
+```
+
+```{r}
 # check that we actually excluded the videos
@@
 
+bb_all <- bb_all %>%
+  filter(!vid_name %in% exclude_bad_quality$vid_name)
+
 ### Make detections into logical vectors and compute "person" as either face/hand
@@
 
+## save this data so this doesn't have to be redone again
+save(d_all, file = '../data/openpose_detections_filtered.RData')
+```
+
 ### Look at any suspicious videos with very high face detections (candidate missed allocentric videos)
+```{r}
 vid_check <- d_all %>%
@@
   filter(prop_faces>.8)
-
-## save this data so this doesn't have to be redone again
-save(d_all, file = '../data/openpose_detections_filtered.RData')
 
@@
 
+## Cropped analysis
+```{r}
+## Import bounding boxes data
+height_px = 480; width_px = 640
+
+# make etra DVs & age variable
+bb_all = bb_all %>%
+  mutate(height_y = height*height_px, width_x = width*width_px, area = (height_y*width_x)/(height_px*width_px)) %>%
+  mutate(x_pos = left*width_px, y_pos = top*height_px) %>%
+  mutate(center_x = x_pos + width_x/2, center_y = y_pos - height_y/2)  %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(x/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))
+
+detections_cropped <- bb_all %>%
+  filter(height <.6) %>%  ## cut off bottom part of frame
+  filter(mean_conf > 0) %>% ## look at detections
+  group_by(vid_name, frame, age_days, child_id) %>%
+  summarize(hand_detected = (length(label=="hand")>0), face_detected = (length(label=="face")>0)) %>%
+  distinct(vid_name, frame, age_days, child_id, face_detected, hand_detected)
+```
+
+### Now plot faces-hands for the cropped analysis
+```{r}
+summary_by_age_cropped <- detections_cropped %>%
+  group_by(age_day_bin, child_id) %>%
+  summarize(num_detect = length(face_detected), prop_faces = sum(face_detected) / num_detect,  prop_hands = sum(hand_detected) / num_detect)
+
+ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.8) +
+  geom_smooth(span=10) + 
+  theme_few(base_size=18) +
+  ylab('Proportion Faces - Hands (CROPPED)') + 
+  xlab('Age (months)')
+
+```
+
 ```{r}

### 2020-01-15 paper/cogsci/paper.Rmd
add code for cropped analysis
writing PRF section

@@
 The candidates are then matched to a single individual and finally assembled into a pose; here, we only made use of outputs of the face and hand detection modules. 
+Specifically, we tagged frames with detected nose keypoints as having a face, and frames with a wrist keypoint were tagged as having a hand present.
 
@@
 To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from the 1,636 videos of two children (S and A).
-Frames were jointly annotated for the presence of faces and hands. 
+Frames were jointly annotated for the presence of faces and hands: raters were asked to indicate presence if at least 30% (CHECK) of one of these body parts was visible.
 These randomly sampled frames covered XX of the videos present in the dataset.
-A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated XX frames; agreement with the primary coder was XX%.
+A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated ~4000 (CHECK) frames; agreement with the primary coder was 95%.
 
 ### Detection accuracy for faces and hands
-Overall, we found that face detections were slightly more accurate than hand detections,
 
-Precision and recall (F-score) variation across child/age for faces
+To evaluate OpenPose's performance, we compared its detections to the the manually-annotated gold set of 24,000 frames, calculating Precision (hits / hits + false alarms), Recall (hits / hits + misses), and F-score (the harmonic mean of precision and recall) were calculated.
+For faces, the F-score was 0.64, with a precision of 0.70 and recall of 0.58. 
+For hands, the F-score was 0.51, with a precision of 0.73 and recall of 0.40.
+Both faces and hands thus have moderately good precision, and face detections were slightly more accurate than hand detections, which suffer from fairly low recall, meaning that we are likely underestimating the proportion of hands in the dataset when using the automated detections.
+We also examined whether precision, recall, and F-score for hands and faces varied per child as a function of age to see if there was any bias in the OpenPose detections related to age.
+The scores for faces were steady across age and similar for both children, but the scores for hands declined somewhat for the last few months.
 
-Describe possible sources of variation that decrease scores for:
--Faces: weird viewpoints, occluded/side viewpoint, faces in books
--Hands: children's own hands, hands in books, side viewpoints
+What sources of variation might be causing trouble for OpenPose?
+For faces, we observed that children often have non-canonical viewpoints (e.g., looking up at a caregiver's chin) as well as partially-occluded or oblique viewpoints. 
+Finally, we noted that human annotators and OpenPose alike were sometimes unreliable about labeling faces seen in books that children were looking at.
+Hands in books may have also proved unreliable for hand detections, as would oblique or non-canonical viewpoints of real hands, but most notably in many frames children's own hands may have been visible, due to both the wide FOV and the downward tilt of the camera.
 
-Describe additional child vs. hand annotation; P/R/F variation across child vs. adult hands (better for adult hands, still OK for child hands)
+Describe additional child vs. hand annotation (move from Part 2?); P/R/F variation across child vs. adult hands (better for adult hands, still OK for child hands)
 
@@
 Thus, the field of view (FOV) of the fisheye lens used in @SAYcam was much wider (109 degrees horizontal x 70 degrees vertical) than the FOV of the lens used in @Fausey2016 (69 x 41 degrees).
-This larger field of view may have allowed the SAYcam cameras to capture not only the presence of a social partner’s hands interacting with objects, but also the children’s own hands, leading to more frequent hand detections.
+This larger field of view may have allowed the SAYcam cameras to capture not only the presence of a social partner's hands interacting with objects, but also the children’s own hands, leading to more frequent hand detections.
 
-To assess this possibility, we obtained annotations for a subsample of XX frames in which a hand was detected in the random gold set; participants (recruited via AMT) were asked to draw bounding boxes around children’s hands and adult hands.
-Overall, we found that 34% of the hands detected by OpenPose in the random 24K sample were of children’s own hands (compared to 8% reported in @Fausey2016) suggesting that this difference in field of view did contribute substantially to the higher rate of detections in the frames.
+To assess this possibility, we obtained annotations for a subsample of XX frames in which a hand was detected in the random gold set; participants (recruited via AMT) were asked to draw bounding boxes around children's hands and adult hands.
+Overall, we found that 34% of the hands detected by OpenPose in the random 24K sample were of children's own hands (compared to 8% reported in @Fausey2016) suggesting that this difference in field of view did contribute substantially to the higher rate of detections in the frames.
 Heatmaps of the bounding boxes obtained from these annotations can be seen in Figure XX, showing that children’s hands tended to appear in the lower half of the frames.

### 2020-01-15 src/get_all_openpose_bounding_boxes.R

@@ -2,14 +2,15 @@
 # load bounding boxes from openpose detections from the entire dataset
 # (created in get_bounding_boxes_per_vid.py using numpy vectors in $GROUP_SCRATCH/openpose_flattened_whole)
 
-# 1,387 videos so far
-
 require(data.table)
 require(here)
 require(stringr)
 
 files <- list.files("../src/bounding_boxes") # 1632 vids
 # A_20140630_2117_04_bounding_boxes.csv had no detections
+
+load("../src/data/vid_info.RData") # vid_info
+downup = fread("../src/data/video_right-side-up.csv", stringsAsFactors = F)
 
 df <- data.frame()
 
@@ -18,7 +19,11 @@ for (i in 1:length(files)) {
   tmp <- fread(paste("../src/bounding_boxes", files[i], sep='/'), stringsAsFactors = F) 
   if(ncol(tmp)==9) {
     tmp$V1 = NULL
-    tmp$vid_name = str_remove(files[i], "_bounding_boxes.csv")
+    this_vid = str_remove(files[i], "_bounding_boxes.csv")
+    tmp$child_id = strsplit(files[i], '_')[[1]][1]
+    tmp$vid_name = this_vid
+    tmp$age_days = vid_info[which(vid_info$vid_name == this_vid)[1],]$age_days
+    tmp$right_side_up = downup[which(downup$video == this_vid),]$right_side_up
     # remove any rows with all 0 bounding box + confidences (~50%)
     tmp = subset(tmp, mean_confidence!=0)
     #df <- rbindlist(list(df, tmp)) # , use.names = T

### 2020-01-15 paper/cogsci/paper.tex

--- 2020-01-11 paper/cogsci/paper.tex
@@
 
-\title{Quantifying social information in natural infant visual experience}
+\title{A longitudinal investigation of the social information in natural infant
+visual experience}
 
@@
 \begin{abstract}
-Faces are a critical part of infants' visual experience, as they convey
-social and linguistic information.
+The faces and hands of infants' caregivers and other social partners
+offer a rich source of social and causal information that may be
+critical for infants' cognitive and linguistic development. Previous
+work using manual annotation strategies and cross-sectional data has
+found systematic changes in the proportion of faces and hands in the
+egocentric perspective of young infants. The present research aims to
+test the generality of these findings using the SAYcam dataset
+(Sullivan, Mei, Perfors, Wojcik, \& Frank, n.d.), a longitudinal
+collection of over 1700 headcam videos collected from three children
+along a span of 6 to 32 months of age. To do so, we validate the use of
+a modern convolutional neural network for pose detection (OpenPose) for
+the detection of people, faces, and hands to analyze these naturalistic
+infant egocentric videos. We then apply this model to the entire
+dataset, analyzing the prevalence of faces across age, individuals, and
+activity contexts. Overall, we find a higher prevalence of hands seen by
+infants than previously reported, considerably variability in the
+proportion of faces/hands seen across different locations (e.g., living
+room vs.~kitchen), yet surprising consistency across both individual
+children.
 
 \textbf{Keywords:}
-Add your choice of indexing terms or keywords; kindly use a semi-colon;
-between each term.
+social cognition; face perception; infancy; head cameras; deep learning
 \end{abstract}
@@
 
-Previous work has suggested: - Relative changes in prevalence of faces
-vs.~hands (Fausey 2016), though perhaps this is driven by infants
-younger than 4 months of age (e.g., Jayaraman, Fausey, \& Smith, 2015;
-Sugden, Mohamed-Ali, \& Moulson, 2014) who see both more frequent and
-more persistent faces (Jayaraman \& Smith, 2018)
+Infants are confronted by a blooming, buzzing onslaught of stimuli
+(James, 1891) which they must learn to parse to make sense of the world
+around them. Yet infants do not embark on this learning process alone:
+infants are engaged in learning from their caregivers from early
+infancy. From as early as 3 months of age, young infants follow overt
+gaze shifts (Gredeback, Fikke, \& Melinder, 2010), and even newborns
+prefer to look at faces with direct vs.~averted gaze (Farroni, Csibra,
+Simion, \& Johnson, 2002), despite their limited acuity {[}CITE{]}.\\
+Faces are thus likely to be an important conduit of social information
+that scaffolds infants cognitive development. Given this importance,
+developmentalists have long hypothesized {[}CITE{]} that faces are
+prevalent in the visual experience of young infants. However, as even
+the viewpoint of a walking child is not easily predicted by our own
+adult intuitions (Clerkin, Hart, Rehg, Yu, \& Smith, 2017; Franchak,
+Kretch, Soska, \& Adolph (2011); Yoshida \& Smith (2008)), researchers
+have begun to record the egocentric views collected from infants and
+toddlers wearing head-mounted cameras to test theories about the infant
+perspective.
 
-\begin{itemize}
-\item
-  Surprising attention to hand movements and their interactions with
-  objects (Yu \& Smith, 2013), particularly in older infants
-\item
-  Differences in the availability of social information depending on
-  motor abilities (Sanchez, Long et al., 2018 CogSci; Franchack papers)
-\end{itemize}
+A growing body of work now demonstrates that the viewpoints of very
+young infants--less than 4 months of age--are indeed dominated by
+frequent, persistent views of the faces of their caregivers (Jayaraman,
+Fausey, \& Smith, 2015; Jayaraman \& Smith, 2018; Sugden, Mohamed-Ali,
+\& Moulson, n.d.). However, as infants mature, their perspective starts
+to capture views of hands paired with the objects they are acting on
+(Fausey, Jayaraman, \& Smith, 2016). As infants learn to use their own
+hands to act on the world, they may focus on manual actions taken by
+their social partners. Furthermore, caregivers may start to use their
+hands more with communicative intent, directing infants attention with
+pointing and gestures to particular events or objects during play (Yu \&
+Smith, 2013).
 
-One limitation of past work is that it has relied on cross-sectional
-data, and thus cannot speak to whether these trajectories are present in
-individual children.
+The present research aims to test the generality of these findings using
+the SAYcam dataset (Sullivan et al., n.d.), a longitudinal collection of
+over 1700 headcam videos collected from three children along a span of 6
+to 32 months of age. In addition to its size and longitudinal nature,
+this dataset builds on those used in previous research in two key ways.
+First, recordings were from a variety of many different naturalistic
+contexts, encompassing infants' viewpoints during both activities
+outside and inside the home. Second, the cameras used in this
+longitudinal study encompassed a much wider field of view than those
+typically used, allowing a more complete picture of the infant
+perspective.
 
-Here, we analyze a longitudinal corpus of head-mounted camera data,
-leveraging over XX hours of videos from XX children, totaling more than
-XX frames. \{briefly describe dataset; sampling strategy: location of
-two households, number of hours of video, variability in location, etc;
-reference published paper on what this dataset is, large field of view
-(fisheye lens))
+However, with hundreds of hours of footage (\textgreater{}30M frames),
+this large dataset truly necessitates a shift to an automated annotation
+strategy. Indeed, annotation of the frames extracted from egocentric
+videos has been to be prohibitively time-consuming, meaning that many of
+the frames are not inspected. For example, Fausey et al. (2016),
+collected a total of 143 hours of head-mounted camera footage (15.5
+million frames), of which one frame every five seconds was hand
+annotated (by four coders), totalling 103,383 frames (per coder)--an
+impressive number of annotations but nonetheless only 0.67\% of the
+collected footage. To address this challenge, we first validate the use
+of a modern computer vision model (Cao, Hidalgo, Simon, Wei, \& Sheikh,
+2018) to automatically detect the presence of hands and faces from the
+infant egocentric viewpoint. In particular, we focus on OpenPose (Cao et
+al., 2018), a model optimized for jointly detecting human face, body,
+hand, and foot keypoints (135 in total) that operates well on scenes
+including multiple people even if they are partially-occluded (see
+Figure 1).\\
+We then apply these methods at scale to the larger dataset, allowing us
+to analyze the proportion of faces and hands observed by each child
+across age and activity context.
 
-To do so, we first test and validate novel computer vision methods for
-extracting social information from these egocentric viewpoints on a
-small subset of randomly selected frames from the dataset. We then apply
-these methods at scale to the larger dataset, allowing us to extract key
-descriptive variables hypothesized to vary across development.
-
-Part 1: How well can we capture social information using computer
-vision? - Description of OpenPose (Figure 1) - Description of annotation
-strategy (24K by Ketan, \textasciitilde{}4K on turk, reliability) -
-Describe main P/R/F statistics for 24K for faces and hands; interpret.
-Relatively higher precision vs.~recall. - P/R/F variation across
-child/age for faces - Describe possible sources of variation that
-decrease scores for: - Faces: weird viewpoints, occluded/side viewpoint,
-faces in books - Hands: children's own hands, hands in books, side
-viewpoints - Describe additional child vs.~hand annotation; P/R/F
-variation across child vs.~adult hands (better for adult hands, still OK
-for child hands)
-
-Part 2: Access to social information across age Prevalence of hands vs
-faces across age (in goldset, full dataset) (Figure 2) Why so many
-hands? More child hands as in gold set Cropped analysis
-
-Variation across location contexts (goldset, full dataset)
+In the following paper, we first describe the dataset and the pose model
+used in the following analyses and validate the use of this model for
+extracting our key descriptive variables by comparing to a
+human-annotated gold set of 24,000 frames. Next, we analyze key
+descriptive variables, including those that have been previously
+reported to vary across age, including the relative proportions of faces
+vs.~hands and the sizes of the faces, over the entire dataset (30M
+frames), finding a greater prevalence of hands than has been previously
+reported.\\
+We then investigate sources of variability in our more naturalistic
+dataset that may explain these differences, including a diversity of
+activity contexts as well as a larger field of view captured by our
+cameras.
 
@@
 
-If the authors' names are included in the sentence, place only the year
-in parentheses, as in (2011), but otherwise place the entire reference
-in parentheses with the authors and year separated by a comma (Fausey,
-Jayaraman, \& Smith, 2016). List multiple references alphabetically and
-separate them by semicolons (Frank, 2012; Smith, Yu, \& Pereira, 2011).
-Use the et. al.~construction only after listing all the authors to a
-publication in an earlier reference and for citations with four or more
-authors.
+\hypertarget{dataset}{%
+\subsection{Dataset}\label{dataset}}
 
-You might want to display a wide figure across both columns. To do this,
-you change the \texttt{fig.env} chunk option to \texttt{figure*}. To
-align the image in the center of the page, set \texttt{fig.align} option
-to \texttt{center}. To format the width of your caption text, you set
-the \texttt{num.cols.cap} option to \texttt{2}.
+Videos captured by the headcam were 640x480 pixels, and a fisheye lens
+was attached to the camera to increase 109 degrees horizontal x 70
+degrees vertical. Children wore headcams at least twice weekly, for
+approximately one hour per recording session. One weekly session was on
+the same day each week at a roughly constant time of day, while the
+other(s) were chosen arbitrarily at the participating family's
+discretion. At the time of the recording, all three children were in
+single-child households. Videos\footnote{All videos are available at
+  \url{https://nyu.databrary.org/volume/564}} with technical errors or
+that were not taken from the egocentric perspective were excluded from
+the dataset. We analyze 1,636 videos, with a total duration of XX hours
+(XX million frames).
 
-\hypertarget{one-column-images}{%
-\subsection{One-column images}\label{one-column-images}}
+\hypertarget{part-1-how-well-can-we-capture-social-information-using-computer-vision}{%
+\subsection{Part 1: How well can we capture social information using
+computer
+vision?}\label{part-1-how-well-can-we-capture-social-information-using-computer-vision}}
 
-Single column is the default option, but if you want set it explicitly,
-set \texttt{fig.env} to \texttt{figure}. Notice that the
-\texttt{num.cols} option for the caption width is set to \texttt{1}.
+\hypertarget{computer-vision-model}{%
+\subsubsection{Computer vision model}\label{computer-vision-model}}
 
-\begin{CodeChunk}
-\begin{figure}[H]
+To automatically annotate the millions of frames in SAYcam, we use
+OpenPose (Cao et al., 2018; Simon, Joo, Matthews, \& Sheikh, 2017), a
+computer vision model optimized for jointly detecting human face, body,
+hand, and foot keypoints (135 in total) that operates well on scenes
+including multiple people even if they are partially-occluded. This
+convolutional neural network (CNN)-based pose detector\footnote{\url{https://github.com/CMU-Perceptual-Computing-Lab/openpose}}
+provided the locations of 18 body parts (ears, nose, wrists, etc.). The
+system uses a CNN for initial anatomical detection and subsequently
+applies part affinity fields (PAFs) for part association, producing a
+series of body part candidates. The candidates are then matched to a
+single individual and finally assembled into a pose; here, we only made
+use of outputs of the face and hand detection modules.
 
-{\centering \includegraphics{figs/image-1}
+\hypertarget{manual-annotation-strategy}{%
+\subsubsection{Manual annotation
+strategy}\label{manual-annotation-strategy}}
 
-}
+To test the validity of OpenPose's hand and face detections, we compared
+the accuracy of these detections relative to human annotations of 24,000
+frames selected uniformly at random from the 1,636 videos of two
+children (S and A). Frames were jointly annotated for the presence of
+faces and hands. These randomly sampled frames covered XX of the videos
+present in the dataset.\\
+A second set of coders recruited via AMT (Amazon Mechanical Turk)
+additionally annotated XX frames; agreement with the primary coder was
+XX\%.
 
-\caption[One column image]{One column image.}\label{fig:image}
-\end{figure}
-\end{CodeChunk}
+\hypertarget{detection-accuracy-for-faces-and-hands}{%
+\subsubsection{Detection accuracy for faces and
+hands}\label{detection-accuracy-for-faces-and-hands}}
 
-\hypertarget{r-plots}{%
-\subsection{R Plots}\label{r-plots}}
+Overall, we found that face detections were slightly more accurate than
+hand detections,
 
-You can use R chunks directly to plot graphs. And you can use latex
-floats in the fig.pos chunk option to have more control over the
-location of your plot on the page. For more information on latex
-placement specifiers see
-\textbf{\href{https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions}{here}}
+Precision and recall (F-score) variation across child/age for faces
 
-\begin{CodeChunk}
-\begin{figure}[H]
+Describe possible sources of variation that decrease scores for: -Faces:
+weird viewpoints, occluded/side viewpoint, faces in books -Hands:
+children's own hands, hands in books, side viewpoints
 
-{\centering \includegraphics{figs/plot-1}
+Describe additional child vs.~hand annotation; P/R/F variation across
+child vs.~adult hands (better for adult hands, still OK for child hands)
 
-}
+\hypertarget{part-2-access-to-social-information-across-age}{%
+\subsection{Part 2: Access to social information across
+age}\label{part-2-access-to-social-information-across-age}}
 
-\caption[R plot]{R plot}\label{fig:plot}
-\end{figure}
-\end{CodeChunk}
+Next, we analyzed the social information in view across the entire
+dataset, looking specifically at the proportions of faces and hands that
+were in view for each child. Data from videos were binned according to
+the age of the child (in weeks) (see Figure XX). First, we saw that the
+proportion of faces in view showed a moderate decrease across this age
+range, both when analyzing the random 24K frames as well as the entire
+dataset. While these trends appear somewhat different than those
+observed in Fausey et al. (2016), note that Fausey et al. (2016)
+included data from very young infants (starting at 2 months while),
+while here the youngest videos coming from S and A around 6 and 9 months
+of age, respectively. Similarly, our age range extends 8 months later
+than those infants in Fausey et al. (2016), throughout a portion of
+third year of life.
 
-\hypertarget{tables}{%
-\subsection{Tables}\label{tables}}
+However, the most striking result from the dataset is a much greater
+proportion of hands in view than have previously been reported. We found
+this to be true across all ages, in both children, and regardless of
+whether we analyzed human annotations (on the 24K random subset) or the
+entire dataset.\\
+One reason this could be the case is the much larger field of view that
+was captured by the cameras used in this study: unlike previous studies,
+our cameras were outfitted with a fish-eye lens in an attempt to capture
+as much of the children's field of view as possible.\\
+Thus, the field of view (FOV) of the fisheye lens used in Sullivan et
+al. (n.d.) was much wider (109 degrees horizontal x 70 degrees vertical)
+than the FOV of the lens used in Fausey et al. (2016) (69 x 41 degrees).
+This larger field of view may have allowed the SAYcam cameras to capture
+not only the presence of a social partner's hands interacting with
+objects, but also the children's own hands, leading to more frequent
+hand detections.
 
-You can use the xtable function in the xtable package.
+To assess this possibility, we obtained annotations for a subsample of
+XX frames in which a hand was detected in the random gold set;
+participants (recruited via AMT) were asked to draw bounding boxes
+around children's hands and adult hands. Overall, we found that 34\% of
+the hands detected by OpenPose in the random 24K sample were of
+children's own hands (compared to 8\% reported in Fausey et al. (2016))
+suggesting that this difference in field of view did contribute
+substantially to the higher rate of detections in the frames. Heatmaps
+of the bounding boxes obtained from these annotations can be seen in
+Figure XX, showing that children's hands tended to appear in the lower
+half of the frames.
 
-\begin{table}[H]
-\centering
-\begin{tabular}{rrrrr}
-  \hline
- & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
-  \hline
-(Intercept) & 0.00 & 0.10 & 0.0 & 0.98 \\ 
-  x & 1.90 & 0.09 & 20.1 & 0.00 \\ 
-   \hline
-\end{tabular}
-\caption{This table prints across one column.} 
-\end{table}
+We thus re-analyzed the entire dataset while restricting our analysis to
+a smaller, middle portion of the frame comparable to the field of view
+used in Fausey et al. (2016) (XX vs XX degrees). To do so, we excluded
+hand detections that occurred in the bottom 40\% of the frame, while
+retaining all detections that occurred in the top of the frame.\\
+Overall, we found X, suggesting Y.
+
+Intriguingly, we observed an unexpected trend in which the relative
+proportion of faces vs.~hands increased during the third year of life;
+in particular, this seemed\ldots{}(save for discussion?)
+
+\hypertarget{variability-by-location}{%
+\subsubsection{Variability by Location}\label{variability-by-location}}
+
+Next we examine variation in the presence of hands and faces across
+different locations. Of the XX videos, the content of 1,829 have been
+manually annotated for filming location, activites taking place, and
+visible objects (see Sullivan et al. (n.d.)). XX of the videos were
+filmed in a single location, representing XX\% of the dataset and
+roughly XX million frames (see Sullivan et al. (n.d.)). To give a sense
+of the contexts the children experienced, the most frequent filming
+locations were the living room (339 videos), bedroom (182), kitchen
+(150), outside on property (129), child's bedroom (81), deck/porch (73),
+hallway (70), and off property (57). Filming only took place twice in
+the dining room (see Figure XX). Activities varied predictability by
+these locations: for example, eating and XX occured in the kitchen,
+whereas playtime was the dominant activity in the living room (see
+Figure XX). Bria: analyze activity
+
+Not this, but point out that eating was not frequent: The most frequent
+activities were sitting (410), playing (375), being held (352), and
+standing (297). Eating was the 11th most-frequent activity (117 videos).
+
+(goldset, full dataset)
 
@@
 \section{Discussion}\label{discussion}}
+
+We demonstrate the feasibility of using modern computer vision models to
+vastly increase the efficiency of processing egocentric headcam footage,
+allowing us to annotate 100\% of even very large datasets for the
+presence and size of people, hands, and faces. We validate the use of
+this model by comparing to a human-annotated gold set, and find X.
+
+Analyzing this dataset has yielded a better understanding of infants'
+evolving access and attention to social information.
+
+Need to think about the child's viewpoint relative to actual FOV as well
+as attention
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-Cao2018openpose}{}%
+Cao, Z., Hidalgo, G., Simon, T., Wei, S.-E., \& Sheikh, Y. (2018).
+OpenPose: Realtime multi-person 2D pose estimation using Part Affinity
+Fields. In \emph{ArXiv preprint arXiv:1812.08008}.
+
+\leavevmode\hypertarget{ref-Farroni2002}{}%
+Farroni, T., Csibra, G., Simion, F., \& Johnson, M. H. (2002). Eye
+contact detection in humans from birth. \emph{Proceedings of the
+National Academy of Sciences}, \emph{99}(14), 9602--9605.
+
 \leavevmode\hypertarget{ref-Fausey2016}{}%
@@
 
-\leavevmode\hypertarget{ref-Frank2012}{}%
-Frank, M. C. (2012). Measuring children's visual access to social
-information using face detection. In \emph{Proceedings of the nth annual
-conference of the cognitive science society} (pp. XXX--XXX). Hillsdale,
-NJ: Cognitive Science Society.
+\leavevmode\hypertarget{ref-Gredeback2010}{}%
+Gredeback, G., Fikke, L., \& Melinder, A. (2010). The development of
+joint visual attention: A longitudinal study of gaze following during
+interactions with mothers and strangers. \emph{Developmental Science},
+\emph{13}(6), 839--848.
 
-\leavevmode\hypertarget{ref-Smith2011}{}%
-Smith, L. B., Yu, C., \& Pereira, A. (2011). Not your mother's view: The
-dynamics of toddler visual experience. \emph{Developmental Science},
-\emph{14}(1), 9--17.
+\leavevmode\hypertarget{ref-Jayaraman2015}{}%
+Jayaraman, S., Fausey, C. M., \& Smith, L. B. (2015). The faces in
+infant-perspective scenes change over the first year of life. \emph{PLoS
+One}. \url{http://doi.org/10.1371/journal.pone.0123780}
+
+\leavevmode\hypertarget{ref-Jayaraman2018}{}%
+Jayaraman, S., \& Smith, L. B. (2018). Faces in early visual
+environments are persistent not just frequent. \emph{Vision Research}.
+
+\leavevmode\hypertarget{ref-Simon2017hand}{}%
+Simon, T., Joo, H., Matthews, I., \& Sheikh, Y. (2017). Hand keypoint
+detection in single images using multiview bootstrapping. In
+\emph{CVPR}.
+
+\leavevmode\hypertarget{ref-Sugden2014}{}%
+Sugden, N. A., Mohamed-Ali, M. I., \& Moulson, M. C. (n.d.). I spy with
+my little eye: Typical, daily exposure to faces documented from a
+first-person infant perspective. \emph{Developmental Psychobiology},
+\emph{56}(2), 249--261.
+
+\leavevmode\hypertarget{ref-SAYcam}{}%
+Sullivan, J., Mei, M., Perfors, A., Wojcik, E., \& Frank, M. (n.d.).
+Head cameras on children aged 6 months through 31 months.
+
+\leavevmode\hypertarget{ref-Yoshida2008}{}%
+Yoshida, H., \& Smith, L. (2008). What's in view for toddlers? Using a
+head camera to study visual experience. \emph{Infancy}, \emph{13}(3),
+229--248.
 

### 2020-01-15 analysis/analysis_fulldataset.Rmd
separate out preprocessing of main datasets

--- 2020-01-11 analysis/analysis_fulldataset.Rmd
@@
 ## Read in data 
-
-### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
+### Load preprocessed and filtered detections
 ```{r}
-right_side_up_file = "../data/video_right-side-up.csv"
-right_side_up =read.csv(right_side_up_file)
-
-# get INCORRECT videos 
-flipped_videos <- right_side_up %>%
-  filter(right_side_up==1) %>%
-  rename(vid_name = video)
-
-```
-
-### Load SAYCAM metadata from csv file; get metadata from detections .csv
-```{r}
-metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"
-
-meta=read.csv(metadata_file) %>%
-  rowwise() %>%
-  mutate(vid_name = str_split(File.Name,"[.]")[[1]][1]) %>%
-  mutate(count_locations = length(str_split(Location,',')[[1]]))
-
-# collapse duplicate labels
-meta$Location[meta$Location=='Bedroom Alice/Sam'] = 'Bedroom'
-
-```
-
-### Load in detections from preprocessed Rdata file; 
-```{r eval=FALSE}
- # Could do list of detections  from csv (takes forever, skipping)
-# data_file = "../data/all_frames.csv"
-# detections=read.csv(data_file)
-
-## rdata is faster
-load('../data/openpose_detections.RData')
-```
-
-### Preprocess data (doesn't exceute; loads processed data below)
-```{r eval=FALSE}
-# get shortened video names so they match across all files
-all_video_names = as.tibble(unique(detections$vid_name))
-all_video_names <- all_video_names %>%
-  rowwise() %>%
-  mutate(vid_name = str_split(value,"[.]")[[1]][1])
-
-# reset levels of vid_name in big detections array (very slow rowwise)
-levels(detections$vid_name) <- all_video_names$vid_name
-
-# join with metadata and flip the videos
-d_all <- detections %>%
-  left_join(meta, by='vid_name') %>%
-  filter(!vid_name %in% flipped_videos$vid_name)
-
-# check that we actually excluded the videos
-num_orig_videos = length(unique(detections$vid_name))
-num_videos_retained = length(unique(d_all$vid_name))
-assert_that(num_videos_retained < num_orig_videos)
-
-## All 6 of the video that were not in this file (but were in the detections file) happened to be 6 very bad quality videos; excluding from detections
-exclude_bad_quality <- d_all %>%
-  filter(!vid_name %in% right_side_up$video)
-
-d_all <- d_all %>%
-  filter(!vid_name %in% exclude_bad_quality$vid_name)
-
-### Make detections into logical vectors and compute "person" as either face/hand
-d_all$face_openpose = as.logical(d_all$face_openpose)
-d_all$hand_openpose = as.logical(d_all$hand_openpose)
-d_all$person_openpose = (as.logical(d_all$face_openpose) | as.logical(d_all$hand_openpose))
-d_all$both_openpose = (as.logical(d_all$face_openpose) & as.logical(d_all$hand_openpose))
-
-### Look at any suspicious videos with very high face detections (candidate missed allocentric videos)
-vid_check <- d_all %>%
-  filter(child_id == "S") %>%
-  group_by(vid_name,vid_name, Databrary.Link) %>%
-  summarize(prop_faces =mean(face_openpose))
-
-high_faces <- vid_check %>%
-  filter(prop_faces>.8)
-
-## save this data so this doesn't have to be redone again
-save(d_all, file = '../data/openpose_detections_filtered.RData')
-
-```
-
-### Instead, load preprocess and filtered detections
-```{r}
-load('../data/openpose_detections_filtered.RData')
+load('../data/openpose_detections_filtered.RData') #d_all
+load('../data/openpose_detections_filtered_cropped.RData') # d_cropped
 ```
@@
 bins = c(bin_starts, max_age)
+
 d_all <- d_all %>%
   mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
-
 d_all$age_day_bin = as.numeric(as.character(d_all$age_day_bin))
-
 ```
 
+# Full dataset; all detection
 ## How do face/hand detection vary by age? 
@@
 
+# under 24 months
+summary_by_age_limited <- summary_by_age %>%
+  filter(age_day_bin < 24.1)
+
 ```
@@
 ```{r}
-ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
+(faces <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
   geom_point(alpha=.8) +
@@
   xlab('Age bin (months)') +
-  ylim(0,.5)
+  ylim(0,.5))
 ```
@@
 ```{r}
-ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
+(hands <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
   geom_point(alpha=.8) +
@@
 ## faces - hands
-ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
+(face_v_hand <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
   geom_point(alpha=.8) +
@@
   ylab('Proportion Faces - Hands') + 
-  xlab('Age (months)')
-
+  xlab('Age (months)'))
 ```
@@
 
-## Look at trends in full dataset by location
+## By location
+### Summarize faces vs hands by location
 ```{r}
@@
 (plot_faces_loc = ggplot(faces_by_location_to_plot, aes(x = Location, y = mean, col=child_id)) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_nudge(x = .4, y = 0)) +
-  geom_point(aes(x=Location, y=prop_faces, size=num_detect, alpha=.01)) +
-  geom_point() +
-  ylim(0,1) +
+  geom_point(aes(x=Location, y=prop_faces, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
+  # ylim(0,.6) +
   coord_flip() + 
-  ylab('Proportion Faces') +
-  facet_grid(~child_id) )
+  ylab('Proportion Faces')+
+   theme(legend.position = "none"))
 
-(plot_hand_loc = ggplot(hands_by_location_to_plot, aes(x = Location, y = mean, col=age_day_bin)) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_nudge(x = .2, y = 0)) +
-  geom_point(aes(x=Location, y=prop_hands, size=num_detect, alpha=.01)) +
-  geom_point() +
-  ylim(0,1) +
+(plot_hand_loc = ggplot(hands_by_location_to_plot, aes(x = Location, y = mean, col=child_id)) + 
+  geom_point(aes(x=Location, y=prop_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
+  # ylim(0,.6) +
   coord_flip() + 
   ylab('Proportion Hands') +
-  facet_grid(~child_id) +
   theme(legend.position = "none"))
 
-(plot_hands_vs_faces = ggplot(faces_vs_hands_to_plot, aes(x = Location, y = mean, col=age_day_bin)) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_nudge(x = .2, y = 0)) +
-  geom_point(aes(x=Location, y=faces_vs_hands, size=num_detect, alpha=.01)) +
-  geom_point() +
-  # ylim(0,1) +
+(plot_hands_vs_faces = ggplot(faces_vs_hands_to_plot, aes(x = Location, y = mean, col=child_id)) + 
+  geom_point(aes(x=Location, y=faces_vs_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
+  # ylim(-.4,.4) +
   coord_flip() + 
-  ylab('Proportion Faces - Hands') +
-  facet_grid(~child_id) +  theme(legend.position = "none"))
+  ylab('Proportion Faces - Hands'))
 
-# ggarrange(plot_faces_loc, plot_hand_loc,plot_hands_vs_faces)
+ggarrange(plot_faces_loc, plot_hand_loc,plot_hands_vs_faces, nrow=1)
 ```
-## what percentage of the dataset is this? 
+
+### what percentage of the dataset is this? 
 ```{r}
@@
 
+# Cropped analysis
+## Faces vs hands
+### Summary statistics
 ```{r}
+summary_by_age_cropped <- d_cropped %>%
+  group_by(age_day_bin,child_id) %>%
+  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_detected_cropped) / num_detect)
 
-# faces_by_location <- d_all %>%
-#   filter(!is.na(Location)) %>%
-#   filter(count_locations==1) %>%
-#   group_by(Location,child_id,age_day_bin) %>%
-#   summarize(prop_face = mean(face_openpose))  
-# 
-# ggplot(faces_by_location, aes(x = Location, y = prop_face, col=child_id)) + 
-#   # geom_flat_violin() +
-#   geom_boxplot() +
-#   # geom_point() +
-#   ylim(0,.8) +
-#   ylab('Proportion Faces') +
-#   coord_flip()
+summary_by_age_cropped_limited <- summary_by_age_cropped %>%
+  filter(age_day_bin < 24.1)
+```
+
+### Plot hands x age x child
+```{r}
+(hands_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.8) +
+  geom_smooth(span=10) + 
+  ylab('Proportion Hands (Cropped)') + 
+  xlab('Age bin (months)') +
+  ylim(0,.5))
+```
+
+### Plot faces vs. hands for cropped frames
+```{r}
+(face_v_hand_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.4) +
+  geom_smooth(span=10) + 
+  theme_few(base_size=18) +
+  ylab('Proportion Faces - Hands') + 
+  xlab('Age (months)') +
+  ylim(-.3, .3) +
+  ggtitle('(B). Upper 60% of FOV'))
+
+(face_v_hand <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.4) +
+  geom_smooth(span=10) + 
+  theme_few(base_size=18) +
+  ylab('Proportion Faces - Hands') + 
+  xlab('Age (months)') +
+  ylim(-.3, .3) +
+  theme(legend.position = "none") +
+  ggtitle('(A). Entire FOV'))
+
+ggarrange(face_v_hand, face_v_hand_cropped, nrow=1)
 
@@
 ```{r}
-# face_vs_hands_location_all <- d_all %>%
-#   filter(count_locations==1) %>%
-#   filter(!Location=='NA') %>%
-#   group_by(child_id,Location, age_day_bin) %>%
-#   summarize(prop_faces = sum(face_openpose) / length(face_openpose), prop_hands = sum(hand_openpose) / length(hand_openpose), num_detect = length(face_openpose)) %>%
-#   mutate(faces_vs_hands = prop_faces - prop_hands)
-# 
-# ggplot(face_vs_hands_location_all, aes(x=age_day_bin, y=prop_faces, col=child_id, size=num_detect)) +
-#   geom_point() +
-#   # geom_smooth() +
-#   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-#   ylab("Faces") +
-#   facet_grid(~Location)
-# 
-# ggplot(face_vs_hands_location_all, aes(x=age_day_bin, y=prop_hands, col=child_id, size=num_detect)) +
-#   geom_point() +
-#   # geom_smooth() +
-#   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-#   ylab("Hands") +
-#   facet_grid(~Location)
-# 
-# ggplot(face_vs_hands_location_all, aes(x=age_day_bin, y=faces_vs_hands, col=child_id, size=num_detect)) +
-#   geom_point() +
-#   # geom_smooth() +
-#   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-#   ylab("Faces vs Hands") +
-#   facet_grid(~Location)
+ggplot(summary_by_age_cropped_limited, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.8) +
+  geom_smooth(span=10, method='lm') + 
+  theme_few(base_size=18) +
+  ylab('Proportion Faces - Hands (CROPPED)') + 
+  xlab('Age (months)')
+
+ggarrange(face_v_hand, face_v_hand_cropped, nrow=1)
 
@@
 
-# Render out images based on annotations if desired
-## True positives on faces?
-```{r eval=FALSE}
-faces_only_op_cor <- m %>%
-  filter(faces == TRUE) %>%
-  filter(face_openpose == TRUE)
-
-# how about images where open pose got it? these should be most obvious
-dir.create(paste0('faces_tp/'))
-for (i in seq(1,length(faces_only_op_cor$full_image_path),1)){
-  image_read(as.character(faces_only_op_cor$full_image_path[i])) %>%
-  image_append(stack = FALSE) %>%
-  image_write(file.path(paste0("faces_tp/", faces_only_op_cor$short_image_path[i])))
-}
+### Side by side plots for cropped comparison
+```{r}
+ggarrange(hands, hands_cropped, nrow=1)
+ggarrange(face_v_hand, face_v_hand_cropped, nrow=1)
 
@@
 
-## False positives on facs?
-```{r eval=FALSE}
-to_write <- m %>%
-  filter(faces == FALSE) %>%
-  filter(face_openpose == TRUE)
+## By location
+### Summarize
 
-# how about images where open pose got it? these should be most obvious
-dir.create(paste0('faces_fp/'))
-for (i in seq(1,length(to_write$full_image_path),1)){
-  image_read(as.character(to_write$full_image_path[i])) %>%
-  image_append(stack = FALSE) %>%
-  image_write(file.path(paste0("faces_fp/", to_write$short_image_path[i])))
-}
+### Load SAYCAM metadata from csv file
+```{r}
+metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"
+
+meta=read.csv(metadata_file) %>%
+  rowwise() %>%
+  mutate(vid_name = str_split(File.Name,"[.]")[[1]][1]) %>%
+  mutate(count_locations = length(str_split(Location,',')[[1]]))
+
+# collapse duplicate labels
+meta$Location[meta$Location=='Bedroom Alice/Sam'] = 'Bedroom'
 
@@
 
-## False negatives on faces?
-```{r eval=FALSE}
-to_write <- m %>%
-  filter(faces == TRUE) %>%
-  filter(face_openpose == FALSE)
+### Join with cropped datasets and summarize
+```{r}
+face_hand_by_location_cropped <- d_cropped %>%
+  left_join(meta) %>%
+  filter(!is.na(Location)) %>%
+  filter(count_locations==1) %>%
+  group_by(Location,child_id,age_day_bin) %>%
+  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_detected_cropped), num_detect = length(hand_detected_cropped))  %>%
+  filter(num_detect > 9000) %>% ## 9000 frames = 5 minutes of video at 30 fps %>%
+  mutate(faces_vs_hands = prop_faces - prop_hands)
 
-# how about images where open pose got it? these should be most obvious
-dir.create(paste0('faces_fn/'))
-for (i in seq(1,length(to_write$full_image_path),1)){
-  image_read(as.character(to_write$full_image_path[i])) %>%
-  image_append(stack = FALSE) %>%
-  image_write(file.path(paste0("faces_fn/", to_write$short_image_path[i])))
-}
+hands_by_location_to_plot_cropped <- face_hand_by_location_cropped %>%
+  multi_boot_standard(col="prop_hands") %>%
+  ungroup %>%
+  left_join(face_hand_by_location_cropped) %>%
+  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
+  mutate(Location = fct_reorder(Location, mean))
+
+faces_by_location_to_plot_cropped <- face_hand_by_location_cropped %>%
+  multi_boot_standard(col="prop_faces") %>%
+  ungroup %>%
+  left_join(face_hand_by_location_cropped) %>%
+  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
+  mutate(Location = fct_reorder(Location, mean))
+
+faces_vs_hands_to_plot_cropped <- face_hand_by_location_cropped %>%
+  multi_boot_standard(col="faces_vs_hands") %>%
+  ungroup %>%
+  left_join(face_hand_by_location_cropped) %>%
+  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
+  mutate(Location = fct_reorder(Location, mean))
 
 ```
+
+### Plot cropped detections by location
+```{r}
+(plot_faces_loc_cropped = ggplot(faces_by_location_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
+  geom_point(aes(x=Location, y=prop_faces, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
+  # ylim(0,.6) +
+  coord_flip() + 
+  ylab('Proportion Faces')+
+   theme(legend.position = "none"))
+
+(plot_hand_loc_cropped = ggplot(hands_by_location_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
+  geom_point(aes(x=Location, y=prop_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
+  # ylim(0,.6) +
+  coord_flip() + 
+  ylab('Proportion Hands') +
+  theme(legend.position = "none"))
+
+(plot_hands_vs_faces_cropped = ggplot(faces_vs_hands_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
+  geom_point(aes(x=Location, y=faces_vs_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
+  # ylim(-.4,.4) +
+  coord_flip() + 
+  ylab('Proportion Faces - Hands'))
+
+# ggarrange(plot_faces_loc, plot_hand_loc,plot_hands_vs_faces)
+ggarrange(plot_faces_loc_cropped, plot_hand_loc_cropped,plot_hands_vs_faces_cropped, nrow=1)
+# ggarrange(plot_hands_vs_faces,plot_hands_vs_faces_cropped, nrow=1)
+
+```
+
+# Inferential statistics
+### Entire age range
+```{r}
+summary_by_age_cropped$num_detect <- scale(summary_by_age_cropped$num_detect)
+
+model_cropped <- glmer(prop_faces - prop_hands ~ age_day_bin + (1 | child_id), data = summary_by_age_cropped_limited)
+summary(model_cropped)
+```
+
+### Full dataset
+```{r}
+summary_by_age_cropped_limited$num_detect <- scale(summary_by_age_cropped_limited$num_detect)
+
+model_limited_cropped <- glmer(prop_faces - prop_hands ~ age_day_bin + num_detect + (1 | child_id), data = summary_by_age_cropped_limited)
+summary(model_limited_cropped)
+
+```
+
+# Analyze most frequent activities by location
+```{r}
+frames_by_video <- d_all %>%
+  group_by(vid_name) %>%
+  summarize(num_frames = n())
+
+activity_by_location <- meta %>%
+  filter(!is.na(Location)) %>%
+  filter(!Activity=='N/A') %>%
+  filter(!is.na(Activity)) %>%
+  filter(!Location=='N/A') %>%
+  filter(count_locations==1) %>%
+  select(vid_name, Location, Activity) %>%
+  mutate(Activity = strsplit(as.character(Activity), ",")) %>% 
+  unnest(Activity)
+
+# fix typo in annotations
+activity_by_location$Activity[activity_by_location$Activity=='Talking Walk']='Taking Walk'
+```
+
+### Plot activities by context
+```{r}
+activity_contexts <-  activity_by_location %>%
+  left_join(frames_by_video) %>%
+  filter(!Activity=='N/A') %>%
+  group_by(Location,Activity) %>%
+  summarize(count_frames = sum(num_frames)) %>%
+  filter(count_frames > 9000)
+
+ggplot(activity_contexts, aes(Location, y=Activity)) +
+  geom_tile(aes(fill = count_frames)) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+  coord_flip()
+
+```

### 2020-01-15 analysis/detector_validation.Rmd
separate out preprocessing of main datasets

@@
 prf_by_location_faces$age_day_bin  = as.numeric(as.character(prf_by_location_faces$age_day_bin))
-ggplot(prf_by_location_faces, aes(x=age_day_bin, y=f, col=Location, size=num_detect)) +
+ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=age_day_bin)) +
   geom_point(alpha=.5) +
-  facet_grid(~Location)
-  geom_smooth()  +
-  ylab('F-score - Face detection')
+  ylab('F-score - Face detection') +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
 ```

### 2020-01-15 analysis/preprocess_datasets.Rmd
separate out preprocessing of main datasets

---
title: "saycam full dataset -- preprocessing"
author: "Bria Long"
date: "1/9/2020"
output: html_document
---

# Basic data loading and setup
## Packages
```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(egg)
theme_set(theme_few())
```

## Read in data

### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
```{r}
right_side_up_file = "../data/video_right-side-up.csv"
right_side_up =read.csv(right_side_up_file)

# get INCORRECT videos 
flipped_videos <- right_side_up %>%
  filter(right_side_up==1) %>%
  rename(vid_name = video)
```

### Load SAYCAM metadata from csv file; get metadata from detections .csv
```{r}
metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"

meta=read.csv(metadata_file) %>%
  rowwise() %>%
  mutate(vid_name = str_split(File.Name,"[.]")[[1]][1]) %>%
  mutate(count_locations = length(str_split(Location,',')[[1]]))

# collapse duplicate labels
meta$Location[meta$Location=='Bedroom Alice/Sam'] = 'Bedroom'

```

### Load in detections & bounding boxes from preprocessed Rdata file; 
```{r eval=FALSE}
 # Could do list of detections  from csv (takes forever, skipping)
# data_file = "../data/all_frames.csv"
# detections=read.csv(data_file)

## rdata is faster
load('../data/openpose_detections.RData')

```

### Preprocess data (doesn't execute in markdown; loads processed data below)
```{r eval=FALSE}
# get shortened video names so they match across all files
all_video_names = as_tibble(unique(detections$vid_name))
all_video_names <- all_video_names %>%
  rowwise() %>%
  mutate(vid_name = str_split(value,"[.]")[[1]][1])

# reset levels of vid_name in big detections array for detections & bb (very slow rowwise)
levels(detections$vid_name) <- all_video_names$vid_name

# join with metadata and exclude bad videos
d_all <- detections %>%
  left_join(meta, by='vid_name') %>%
  filter(!vid_name %in% flipped_videos$vid_name)

## All 6 of the video that were not in this file (but were in the detections file) happened to be 6 very bad quality videos; excluding from detections
exclude_bad_quality <- d_all %>%
  filter(!vid_name %in% right_side_up$video)

d_all <- d_all %>%
  filter(!vid_name %in% exclude_bad_quality$vid_name)

# check that we actually excluded the videos
num_orig_videos = length(unique(detections$vid_name))
num_videos_retained = length(unique(d_all$vid_name))
assert_that(num_videos_retained < num_orig_videos)

# get rid of big data structure
remove(detections)
```

### Make detections into logical vectors and compute "person" as either face/hand
```{r}
d_all$face_openpose = as.logical(d_all$face_openpose)
d_all$hand_openpose = as.logical(d_all$hand_openpose)
d_all$person_openpose = (as.logical(d_all$face_openpose) | as.logical(d_all$hand_openpose))
d_all$both_openpose = (as.logical(d_all$face_openpose) & as.logical(d_all$hand_openpose))
```

### Look at any suspicious videos with very high face detections (candidate missed allocentric videos)
```{r}
vid_check <- d_all %>%
  filter(child_id == "S") %>%
  group_by(vid_name,vid_name, Databrary.Link) %>%
  summarize(prop_faces =mean(face_openpose))

high_faces <- vid_check %>%
  filter(prop_faces>.8)
```

### Make bins across which to analyze data
```{r}
bin_size = 7
min_age = min(d_all$age_days)
max_age = max(d_all$age_days)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)
```

### And save out into dataframe
```{r}
d_all <- d_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
d_all$age_day_bin = as.numeric(as.character(d_all$age_day_bin))
```

### Save this data so this doesn't have to be redone again
```{r}
save(d_all, file = '../data/openpose_detections_filtered.RData')
```

## Load bounding boxes to get cropped detections
```{r}
## import bounding boxes
load('../data/all_bounding_boxes.RData')

## frame
height_px = 480; width_px = 640

bb_all <- df %>%
  filter(right_side_up==0) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))

## get rid of extra dataframe
remove(df)
```

## Make cropped detections in top 60% of frame
```{R}
detections_cropped <- bb_all %>%
  filter(height <.6) %>%  ## cut off bottom part of frame
  group_by(vid_name, frame, child_id, age_day_bin) %>%
  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0)) %>% # if any faces or hands
  distinct(vid_name, frame, age_day_bin,face_detected, hand_detected)

## clean up so that we can join with original dataframe
detections_cropped <- detections_cropped %>%
  ungroup() %>%
  rename(hand_detected_cropped = hand_detected, face_detected_cropped = face_detected) %>%
  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id))

## now join with big dataframe
d_cropped <- d_all %>%
  as_tibble() %>%
  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id),face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
  select(vid_name, frame, child_id, age_day_bin, face_openpose, hand_openpose) %>%
  left_join(detections_cropped, by=c("vid_name","frame","age_day_bin","child_id"))

d_cropped <- d_cropped %>%
  replace_na(list(hand_detected_cropped = FALSE, face_detected_cropped = FALSE))  ## replace NAs from cropped anlaysis

# and save it out
save(d_cropped, file = '../data/openpose_detections_filtered_cropped.RData')
```

# Render out images based on annotations if desired
## True positives on faces?
```{r eval=FALSE}
faces_only_op_cor <- m %>%
  filter(faces == TRUE) %>%
  filter(face_openpose == TRUE)

# how about images where open pose got it? these should be most obvious
dir.create(paste0('faces_tp/'))
for (i in seq(1,length(faces_only_op_cor$full_image_path),1)){
  image_read(as.character(faces_only_op_cor$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_tp/", faces_only_op_cor$short_image_path[i])))
}

```

## False positives on facs?
```{r eval=FALSE}
to_write <- m %>%
  filter(faces == FALSE) %>%
  filter(face_openpose == TRUE)

# how about images where open pose got it? these should be most obvious
dir.create(paste0('faces_fp/'))
for (i in seq(1,length(to_write$full_image_path),1)){
  image_read(as.character(to_write$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_fp/", to_write$short_image_path[i])))
}

```

## False negatives on faces?
```{r eval=FALSE}
to_write <- m %>%
  filter(faces == TRUE) %>%
  filter(face_openpose == FALSE)

# how about images where open pose got it? these should be most obvious
dir.create(paste0('faces_fn/'))
for (i in seq(1,length(to_write$full_image_path),1)){
  image_read(as.character(to_write$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_fn/", to_write$short_image_path[i])))
}

```

### 2020-01-16 analysis/analysis_fulldataset.Rmd
updates to main analysis; first pass at integrating in paper.rmd

@@
 ```{r}
+
+check <- d_all %>%
+  filter(!is.na(Location)) %>%
+  filter(count_locations==1) %>%
+  group_by(Location,child_id,age_day_bin) %>%
+  summarize(num_frames = n())
+
 face_hand_by_location <- d_all %>%

### 2020-01-16 paper/cogsci/paper.Rmd
updates to main analysis; first pass at integrating in paper.rmd

--- 2020-01-14 paper/cogsci/paper.Rmd
@@
     Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants. 
-    The present research aims to test the generality of these findings using the SAYcam dataset [@SAYcam], a longitudinal collection of over 1700 headcam videos collected from three children along a span of 6 to 32 months of age.
+    The present research aims to test the generality of these findings using the SAYcam dataset [@SAYcam], a longitudinal collection of over 270 hours of headcam videos collected from three children along a span of 6 to 32 months of age.
     To do so, we validate the use of a modern convolutional neural network for pose detection (OpenPose) for the detection of people, faces, and hands to analyze these naturalistic infant egocentric videos.
     We then apply this model to the entire dataset, analyzing the prevalence of faces across age, individuals, and activity contexts. 
-    Overall, we find a higher prevalence of hands seen by infants than previously reported, considerably variability in the proportion of faces/hands seen across different locations (e.g., living room vs.
-kitchen), yet surprising consistency across both individual children.
+    Overall, we replicate a decrease the proportion of faces vs.
+hands across age and find considerably variability in the proportion of faces/hands seen across different locations (e.g., living room vs.
+kitchen).
 
@@
 ---
+\newcommand{\wrapmf}[1]{#1}
 
@@
 From as early as 3 months of age, young infants follow overt gaze shifts [@Gredeback2010], and even newborns prefer to look at faces with direct vs.
-averted gaze [@Farroni2002], despite their limited acuity [CITE].
+averted gaze [@Farroni2002], despite their limited acuity.
 Faces are thus likely to be an important conduit of social information that scaffolds infants cognitive development.
-Given this importance, developmentalists have long hypothesized [CITE] that faces are prevalent in the visual experience of young infants. 
-However, as even the viewpoint of a walking child is not easily predicted by our own adult intuitions (Clerkin, Hart, Rehg, Yu, & Smith, 2017; @Franchak2011; @Yoshida2008), researchers have begun to record the egocentric views collected from infants and toddlers wearing head-mounted cameras to test theories about the infant perspective.
+Given this importance, cognitive scientists have long hypothesized that faces are prevalent in the visual experience of young infants.
+However, as even the viewpoint of a walking child is not easily predicted by our own adult intuitions (Clerkin, Hart, Rehg, Yu, & Smith, 2017; Franchak et al., 2011; Yoshida & Smith, 2008), researchers have begun to record the egocentric views collected from infants and toddlers wearing head-mounted cameras to test theories about the infant perspective.
 
-A growing body of work now demonstrates that the viewpoints of very young infants--less than 4 months of age--are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @Sugden2014; @Jayaraman2018].
+A growing body of work now demonstrates that the viewpoints of very young infants—less than 4 months of age—are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @Sugden2014; @Jayaraman2018].
 However, as infants mature, their perspective starts to capture views of hands paired with the objects they are acting on [@Fausey2016].
@@
 The present research aims to test the generality of these findings using the SAYcam dataset [@SAYcam], a longitudinal collection of over 1700 headcam videos collected from three children along a span of 6 to 32 months of age.
-In addition to its size and longitudinal nature, this dataset builds on those used in previous research in two key ways. 
-First, recordings were from a variety of many different naturalistic contexts, encompassing infants’ viewpoints during both activities outside and inside the home. 
-Second, the cameras used in this longitudinal study encompassed a much wider field of view than those typically used, allowing a more complete picture of the infant perspective.
+In addition to its size and longitudinal nature, this dataset is more naturalistic on those used in previous research in two key ways.
+First, recordings were from a variety of many contexts, encompassing infants’ viewpoints during both activities outside and inside the home.
+Even in other naturalistic datasets,  the incredible variety in a typical infant’s experience has been largely underrepresented; here, we analyze scenes from a large variety of activity contexts that evolve as children get older (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth).
+Second, the head-mounted cameras used in this longitudinal study captured a much wider field of view than those typically used, allowing a more complete picture of the infant perspective.
 
@@
 Indeed, annotation of the frames extracted from egocentric videos has been to be prohibitively time-consuming, meaning that many of the frames are not inspected.
-For example, @Fausey2016, collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand annotated (by four coders), totalling 103,383 frames (per coder)--an impressive number of annotations but nonetheless only 0.67% of the collected footage.
-To address this challenge, we first validate the use of a modern computer vision model [@Cao2018openpose] to automatically detect the presence of hands and faces from the infant egocentric viewpoint. 
-In particular, we focus on OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints (135 in total) that operates well on scenes including multiple people even if they are partially-occluded (see Figure 1).
-We then apply these methods at scale to the larger dataset, allowing us to analyze the proportion of faces and hands observed by each child across age and activity context.
+For example, @Fausey2016, collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand annotated (by four coders), totalling 103,383 frames (per coder)—an impressive number of annotations but nonetheless only 0.67% of the collected footage.
+To address this challenge, we use a modern computer vision model of pose detection [@Cao2018openpose] to automatically detect the presence of hands and faces from the infant egocentric viewpoint.
+Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints that operates well on scenes including multiple people even if they are partially-occluded (see Figure 1).
+We then apply this method at scale in the larger dataset, allowing us to analyze the proportion of faces and hands observed by each child across age and activity context.
 
-In the following paper, we first describe the dataset and the pose model used in the following analyses and validate the use of this model for extracting our key descriptive variables by comparing to a human-annotated gold set of 24,000 frames.
-Next, we analyze key descriptive variables, including those that have been previously reported to vary across age, including the relative proportions of faces vs.
-hands and the sizes of the faces, over the entire dataset (30M frames), finding a greater prevalence of hands than has been previously reported.
-We then investigate sources of variability in our more naturalistic dataset that may explain these differences, including a diversity of activity contexts as well as a larger field of view captured by our cameras.
+In the following paper, we first describe the dataset and validate the use of this model by comparing face and hand detections to a human-annotated set of 24,000 frames.
+Next, we report how the proportion of faces and hands changes across age (30M frames), finding a greater prevalence of hands than has been previously reported.
+We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including a diversity of locations and activities during which the infant perspective was recorded.
+
+```{r}
+## Read in data 
+### Load preprocessed and filtered detections
+load('../../data/openpose_detections_filtered.RData') #d_all
+load('../../data/openpose_detections_filtered_cropped.RData') # d_cropped
+```
+
+```{r}
+### Make bins across which to analyze data
+bin_size = 7
+min_age = min(d_all$age_days)
+max_age = max(d_all$age_days)
+bin_starts = seq(min_age-1, max_age+1,bin_size)
+bins = c(bin_starts, max_age)
+
+d_all <- d_all %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
+d_all$age_day_bin = as.numeric(as.character(d_all$age_day_bin))
+```
+
+```{r}
+## Make summary stats
+summary_by_age <- d_all %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+  group_by(age_day_bin, child_id) %>%
+  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect, face_or_hand = sum(person_openpose)/ num_detect, face_and_hand = sum(both_openpose)/ num_detect)
+
+summary_by_age_cropped <- d_cropped %>%
+  group_by(age_day_bin,child_id) %>%
+  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_detected_cropped) / num_detect) 
+```
+
+```{r} 
+### How large is the dataset we're analyzing?
+num_frames = length(d_all$frame)
+
+fps=30
+num_seconds = length(d_all$frame)/fps
+num_videos = length(unique(d_all$vid_name))
+num_minutes = num_seconds/60
+num_hours = num_minutes/60
+num_days = num_hours / 24 
+```
 
@@
 
-Videos captured by the headcam were 640x480 pixels, and a fisheye lens was attached to the camera to increase 109 degrees horizontal x 70 degrees vertical. 
 Children wore headcams at least twice weekly, for approximately one hour per recording session.  
-One weekly session was on the same day each week at a roughly constant time of day, while the other(s) were chosen arbitrarily at the participating family's discretion. 
+One weekly session was on the same day each week at a roughly constant time of day, while the other(s) were chosen arbitrarily at the participating family’s discretion. 
 At the time of the recording, all three children were in single-child households. 
+Videos captured by the headcam were 640x480 pixels, and a fisheye lens was attached to the camera to increase the field of view to 109 degrees horizontal x 70 degrees vertical. 
 Videos[^1] with technical errors or that were not taken from the egocentric perspective were excluded from the dataset.
-We analyze 1,636 videos, with a total duration of XX hours (XX million frames).
+While data collection for the third child (Y) is still ongoing, here we analyze `r num_videos` videos, with a total duration of `r num_hours` hours (>29 million frames).
 
@@
 This convolutional neural network (CNN)-based pose detector[^2] provided the locations of 18 body parts (ears, nose, wrists, etc.).
-The system uses a CNN for initial anatomical detection and subsequently applies part affinity fields (PAFs) for part association, producing a series of body part candidates. 
-The candidates are then matched to a single individual and finally assembled into a pose; here, we only made use of outputs of the face and hand detection modules.
+The system uses a convolutional neural network for initial anatomical detection and subsequently applies part affinity fields for part association, producing a series of body part candidates. 
+The candidates are then matched to a single individual and finally assembled into a pose.
+Thus, while we only make use of the outputs of the face and hand detections, the pose information from an individual is used to determine the presence of a face/hand.
+Specifically, we tagged frames with detected nose keypoints as having a face, and frames with a wrist keypoint were tagged as having a hand present.
 
@@
 ### Manual annotation strategy
-To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from the 1,636 videos of two children (S and A).
-Frames were jointly annotated for the presence of faces and hands. 
-These randomly sampled frames covered XX of the videos present in the dataset.  
-A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated XX frames; agreement with the primary coder was XX%.
+```{r}
+# load('../../data/ketan_gold_sample.RData')
+```
+To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A).
+Frames were jointly annotated for the presence of faces and hands: raters were asked to indicate presence if at least 20% of one of these body parts was visible.
+A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated 3150 frames; agreement with the primary coder was 95.04%.
 
 ### Detection accuracy for faces and hands
-Overall, we found that face detections were slightly more accurate than hand detections,
 
-Precision and recall (F-score) variation across child/age for faces
-
-Describe possible sources of variation that decrease scores for:
--Faces: weird viewpoints, occluded/side viewpoint, faces in books
--Hands: children's own hands, hands in books, side viewpoints
-
-Describe additional child vs. hand annotation; P/R/F variation across child vs. adult hands (better for adult hands, still OK for child hands)
+To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of 24K frames, calculating Precision (hits / hits + false alarms), Recall (hits / hits + misses), and F-score (the harmonic mean of precision and recall).
+For faces, the F-score was 0.64, with a precision of 0.70 and recall of 0.58. 
+For hands, the F-score was 0.51, with a precision of 0.73 and recall of 0.40.
+While faces and hands have moderately good precision, face detections were overall slightly more accurate than hand detections.
+Hand detections suffered from fairly low recall, indicating that OpenPose likely underestimates the proportion of hands in the dataset.
+We also examined whether precision, recall, and F-score for hands and faces varied per child as a function of age to see if there was any bias in the OpenPose detections related to age.
+The scores for faces were steady across age and similar for both children, but the scores for hands declined somewhat for the last few months.
 
@@
 Next, we analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands that were in view for each child. 
-Data from videos were binned according to the age of the child (in weeks) (see Figure XX). 
+Data from videos were binned according to the age of the child (in weeks) (see Figure 2). 
 First, we saw that the proportion of faces in view showed a moderate decrease across this age range, both when analyzing the random 24K frames as well as the entire dataset. 
-While these trends appear somewhat different than those observed in @Fausey2016, note that @Fausey2016 included data from very young infants (starting at 2 months while), while here the youngest videos coming from S and A around 6 and 9 months of age, respectively.
+Note that while these trends appear somewhat different than those observed in @Fausey2016, note that @Fausey2016 included data from very young infants (from 1-4 months of age), while here the youngest videos coming from S and A around 6 and 9 months of age, respectively.
 Similarly, our age range extends 8 months later than those infants in @Fausey2016, throughout a portion of third year of life.
+
+```{r FaceVsHands, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=6, fig.height=3, fig.cap = "Proportion of faces vs.
+hands in the entire dataset (A) and when hand detections are restricted to the upper 60% of the field of view (B).
+Data from each child (A, S) are plotted separately and binned by each week that the videos were filmed; data is scaled by the number of frames in that age range."}
+
+(face_v_hand_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.4) +
+  geom_smooth(span=10) + 
+  theme_few(base_size=18) +
+  ylab('Proportion Faces - Hands') + 
+  xlab('Age (months)') +
+  ylim(-.3, .3) +
+  ggtitle('(B). Upper 60% of FOV'))
+
+(face_v_hand <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.4) +
+  geom_smooth(span=10) + 
+  theme_few(base_size=18) +
+  ylab('Proportion Faces - Hands') + 
+  xlab('Age (months)') +
+  ylim(-.3, .3) +
+  theme(legend.position = "none") +
+  ggtitle('(A). Entire FOV'))
+
+ggarrange(face_v_hand, face_v_hand_cropped, nrow=1)
+```
 
@@
 One reason this could be the case is the much larger field of view that was captured by the cameras used in this study: unlike previous studies, our cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible.
-Thus, the field of view (FOV) of the fisheye lens used in @SAYcam was much wider (109 degrees horizontal x 70 degrees vertical) than the FOV of the lens used in @Fausey2016 (69 x 41 degrees).
+Thus, the field of view (FOV) of the fisheye lens used in @SAYcam was much wider (109 degrees horizontal x 70 degrees vertical) than the FOV of the lens used in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees.
 This larger field of view may have allowed the SAYcam cameras to capture not only the presence of a social partner’s hands interacting with objects, but also the children’s own hands, leading to more frequent hand detections.
 
-To assess this possibility, we obtained annotations for a subsample of XX frames in which a hand was detected in the random gold set; participants (recruited via AMT) were asked to draw bounding boxes around children’s hands and adult hands.
-Overall, we found that 34% of the hands detected by OpenPose in the random 24K sample were of children’s own hands (compared to 8% reported in @Fausey2016) suggesting that this difference in field of view did contribute substantially to the higher rate of detections in the frames.
-Heatmaps of the bounding boxes obtained from these annotations can be seen in Figure XX, showing that children’s hands tended to appear in the lower half of the frames.
+```{r}
+load('../../data/child_adult_hand_annotations.RData')
+```
 
-We thus re-analyzed the entire dataset while restricting our analysis to a smaller, middle portion of the frame comparable to the field of view used in @Fausey2016 (XX vs XX degrees).
-To do so, we excluded hand detections that occurred in the bottom 40% of the frame, while retaining all detections that occurred in the top of the frame.  
-Overall, we found X, suggesting Y.
+To assess this possibility, we obtained annotations for a subsample of `r length(child_adult_hand_annotations$frame)` frames in which a hand was detected in the random gold set; participants (recruited via AMT) were asked to draw bounding boxes around children’s hands and adult hands.
+Overall, we found that `r mean(child_adult_hand_annotations$child_hand_seg)` percent of the hands detected by OpenPose in the random 24K sample were of children’s own hands (compared to 8 percent reported in @Fausey2016) suggesting that this difference in field of view did contribute substantially to the higher rate of hand detections in the frames.
+<!-- Heatmaps of the bounding boxes obtained from these annotations can be seen in Figure 3, showing that children’s hands tended to appear in the lower half of the frames. -->
 
-Intriguingly, we observed an unexpected trend in which the relative proportion of faces vs. hands increased during the third year of life; in particular, this seemed...(save for discussion?)
+We thus re-analyzed the entire dataset while restricting our analysis to a smaller, upper portion of the frame comparable to the field of view used in @Fausey2016.
+To do so, we excluded hand detections that occurred in the bottom 40 percent of the frame, while retaining all hand detections that occurred in the top 60% of the frame.
+This coarse cropping of decreased the proportion of hand detections from `r mean(d_all$hand_openpose)`percent to `r mean(d_cropped$hand_detected_cropped)` percent.
+
+With this modified field of view, we now observed a more substantive decrease in the proportions of faces relative to hands.
+To quantify this trend, we fit a generalized linear mixed model to the binned detection rates from this smaller field of field to estimate changes in the proportion of faces vs.
+hands over age.
+To better approximate @Fausey2016, we also restricted our analysis to the age range seen in @Fausey2016, excluding videos when children were over 24 months of age, and indeed found that the proportion of faces vs.
+hands declined modestly with age (see Table 1).
+
+However, when we considered the entire age range, we also observed an unexpected trend in which the relative proportion of faces vs.
+hands increased during the third year of life; this trend was present in both the full dataset and when only considering detections in the upper portion of the frames.
+We discuss possible factors that could cause this trend in the Discussion
 
 ### Variability by Location 
-Next we examine variation in the presence of hands and faces across different locations. 
-Of the XX videos, the content of 1,829 have been manually annotated for filming location, activites taking place, and visible objects (see @SAYcam).
-XX of the videos were filmed in a single location, representing XX% of the dataset and roughly XX million frames (see @SAYcam). 
-To give a sense of the contexts the children experienced, the most frequent filming locations were the living room (339 videos), bedroom (182), kitchen (150), outside on property (129), child's bedroom (81), deck/porch (73), hallway (70), and off property (57).
-Filming only took place twice in the dining room (see Figure XX). 
-Activities varied predictability by these locations: for example, eating and XX occured in the kitchen, whereas playtime was the dominant activity in the living room (see Figure XX). 
-Bria: analyze activity
+```{r}
+load('../../data/child_adult_hand_annotations.RData')
+load('../../data/saycam_metadata.RData')
 
-Not this, but point out that eating was not frequent:
-The most frequent activities were sitting (410), playing (375), being held (352), and standing (297). 
-Eating was the 11th most-frequent activity (117 videos).
+num_videos_annotated = sum(!is.na(meta$Location))
+videos_included = sum(!is.na(meta$Location) & meta$count_locations==1)
 
-(goldset, full dataset)
+# percentage_of_dataset = sum(faces_vs_hands_to_plot$num_detect)/length(d_all$frame)
+# num_frames = sum(faces_by_location_to_plot$num_detect)
+```
+How does variability across different contexts influence the social information in the infant view? 
+HIntuitively, some activities in different contexts may be characterized by a much higher proportion of faces (e.g., diaper changes in bedrooms) than others (e.g., playtime in the living room). 
+We thus next examined variation in presence of hands and faces across different locations. 
+Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location o videos were filmed in.
+`r videos_included` were filmed in single location, representing 17% of the dataset and over 5 million frames (see @SAYcam).
+
+<!-- Not sure video count is the rgiht metric here @George -- eliminating for now... -->
+<!-- To give a sense of the contexts the children experienced, the most frequent filming locations were the living room (339 videos), bedroom (182), kitchen (150), outside on property (129), child's bedroom (81), deck/porch (73), hallway (70), and off property (57).
+The most frequent activities were sitting (410), playing (375), being held (352), and standing (297); eating was the 11th most-frequent activity (117 videos).
+-->
+
+Activities varied somewhat predictability by these contexts: for example, eating occured in the kitchen, whereas playtime was the dominant activity in the living room.
+Overall, we found that the proportion of faces vs.
+hands varied across filming locations, and, to some extent, across children (Figure 3).For example, while both children saw a relatively similar proportion of faces vs.
+hands in the bedroom, they saw quite different amounts of faces vs.
+hands in kitchen.
+
+```{r}
+face_hand_by_location_cropped <- d_cropped %>%
+  left_join(meta) %>%
+  filter(!is.na(Location)) %>%
+  filter(count_locations==1) %>%
+  group_by(Location,child_id,age_day_bin) %>%
+  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_detected_cropped), num_detect = length(hand_detected_cropped))  %>%
+  filter(num_detect > 9000) %>% ## 9000 frames = 5 minutes of video at 30 fps %>%
+  mutate(faces_vs_hands = prop_faces - prop_hands)
+
+faces_vs_hands_to_plot_cropped <- face_hand_by_location_cropped %>%
+  multi_boot_standard(col="faces_vs_hands") %>%
+  ungroup %>%
+  left_join(face_hand_by_location_cropped) %>%
+  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
+  mutate(Location = fct_reorder(Location, mean)) 
+```
+
+```{r DetByLocation, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Proportion of face vs hand detections around in different activity contexts.
+Error bars represent non-parametric bootstrapped 95 \\% confidence intervals across weekly age bins; each datapoint is scaled by the number of frames included."}
+
+ggplot(faces_vs_hands_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
+  geom_point(aes(x=Location, y=faces_vs_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
+  # ylim(-.4,.4) +
+  coord_flip() + 
+  ylab('Proportion Faces - Hands')
+
+```
 
@@
 
-We demonstrate the feasibility of using modern computer vision models to vastly increase the efficiency of processing egocentric headcam footage, allowing us to annotate 100% of even very large datasets for the presence and size of people, hands, and faces.
-We validate the use of this model by comparing to a human-annotated gold set, and find X.
+Broadly, analyzing this dataset has yielded a better understanding of infants' evolving access and attention to social information.
+Despite the considerable variability across different types of activity contexts and age ranges, we still found a moderate decrease in the relative proportion of faces and hands across age, documenting this longitudinal trajectories in individual children.
+This is particularly notable given that this effect seems to be most strongly driven by infants younger than 4 months of age (e.g., Jayaraman, Fausey, & Smith, 2015; Sugden, Mohamed-Ali, & Moulson, 2014) who see both more frequent and more persistent faces (Jayaraman & Smith, 2018).
+Nonetheless, infant’s emerging abilities to act on the world and locomote independently continues to evolve across the first few years of life, and these advances in motoric abilities may be a driving factor that influences infants’ access to social information (Sanchez, Long et al., 2018).
 
-Analyzing this dataset has yielded a better understanding of infants' evolving access and attention to social information.
+Furthermore, we demonstrate the feasibility of using a modern, off-the-shelf computer vision models to vastly increase the efficiency of processing egocentric headcam footage, allowing us to annotate the entirety of very large datasets (here, >30 million frames) for the presence and size of people, hands, and faces, representing a 300-fold increase in data relative to prior work (@Fausey2016).
+To do so, we validate the use of this model by comparing to a human-annotated gold set, finding moderate precision and accuracy.
+While OpenPose was trained on photographs and videos taken by adults, this model still generalized relatively well to the egocentric infant viewpoint with no fine-tuning or post-processing of the detections.
 
-Need to think about the child's viewpoint relative to actual FOV as well as attention
-
-Fausey 2016: 103,383 images; 
-Here: 30,000,000 frames; 300 fold increase in data
+Indeed, as these detections were imperfect compared to human annotators, fine-tuning these models to better optimize them detecting social information from the infant viewpoint remains an open avenue for future work.
+For example, infant perspective often contains non-canonical viewpoints of faces (e.g., looking up at a caregiver's chin) as well as partially-occluded or oblique viewpoint.
+Finally, we noted that human annotators and OpenPose alike were sometimes unreliable about labeling faces seen in books that children were looking at—arguably a common part of many children’s visual experience with hands and faces.
+As standard computer vision models are rarely exposed on these naturalistic, egocentric viewpoints, we suspect that training these models on more naturalistic data may also lead to more robust, generalizable detectors.
 

### 2020-01-16 src/get_all_openpose_bounding_boxes.R
fixed bounding box bug

@@ -34,3 +34,10 @@ for (i in 1:length(files)) {
 }
 
 save(df, file="all_bounding_boxes.RData")
+
+
+df$area = df$height * df$width
+require(ggplot2)
+df %>% filter(area>0) %>%
+  ggplot(aes(x=area, color=label, fill=label)) + 
+  geom_histogram(alpha=.5) 

### 2020-01-16 src/get_bounding_boxes_per_vid.py

@@ -6,7 +6,7 @@ import pandas as pd
 # per frame, and saves as long format CSV (one row per bounding box, maximum 9 per frame)
 
 VID_PATH = "/scratch/groups/mcfrank/Home_Headcam_new/openpose_flattened_whole" # /scratch/groups/mcfrank/Home_Headcam_new/openpose_flattened_whole
-OUT_PATH = "bounding_boxes/"
+OUT_PATH = "/scratch/groups/mcfrank/Home_Headcam_new/bounding_boxes/"
 #VID_PATH = "openpose_flattened"
 #f = "A_20130531_0818_01.npy" # for testing
 
@@ -30,13 +30,13 @@ def get_face_hand_bounding_boxes(detection):
 	Y = detection[1]
 	conf = detection[2]
 	pose_x = X[:18]
-	pose_y = X[:18]
+	pose_y = Y[:18]
 	face_x = X[18:88]
 	face_y = Y[18:88]
 	Lhand_x = X[88:109]
 	Lhand_y = Y[88:109]
 	Rhand_x = X[109:]
-	Rhand_y = X[109:]
+	Rhand_y = Y[109:]
 	bbs = [get_bounding_box(pose_x, pose_y) + [np.mean(conf[:18])], 
 		get_bounding_box(face_x, face_y) + [np.mean(conf[18:88])], 
 		get_bounding_box(Lhand_x, Lhand_y) + [np.mean(conf[88:109])], 
@@ -59,8 +59,10 @@ for f in files:
 		try:
 			v = np.load(os.path.join(VID_PATH, f)) # frames x people (3) x keypoint (X, Y, confidence) x 130
 			for i in range(v.shape[0]): # frame i
+				detection = False # save a blank row if there are no detections for this frame
 				for p in range(3): # person p
 					if np.sum(v[i][p][2])>0: # 0 confidence = no detection
+						detection = True
 						bbs = get_face_hand_bounding_boxes(v[i][p]) # [face, Lhand, Rhand]
 						#for bb in bbs:
 						df.append([i, p, "pose"] + bbs[0])
@@ -68,7 +70,8 @@ for f in files:
 						df.append([i, p, "hand"] + bbs[2])
 						df.append([i, p, "hand"] + bbs[3])
 				# add a row indicating no detection for that frame (makes the file much larger)
-				# df.append([vid_name, i, -1,-1,  -1,-1,-1,-1])
+				if not detection:
[…]

### 2020-01-24 analysis/analysis_fulldataset.Rmd
separate out analysis scripts for efficiency

@@
 ### Load preprocessed and filtered detections
+
 ```{r}
-load('../data/openpose_detections_filtered.RData') #d_all
-load('../data/openpose_detections_filtered_cropped.RData') # d_cropped
+load('../data/openpose_detections_filtered_threekids.RData') #d_all
+
+##
+load('../data/openpose_detections_filtered_cropped_allthreekids.RData') # d_cropped
 ```
@@
 d_all$age_day_bin = as.numeric(as.character(d_all$age_day_bin))
+
+d_all$face_openpose = as.logical(d_all$face_openpose)
+d_all$hand_openpose = as.logical(d_all$hand_openpose)
+d_all$person_openpose = (as.logical(d_all$face_openpose) | as.logical(d_all$hand_openpose))
+d_all$both_openpose = (as.logical(d_all$face_openpose) & as.logical(d_all$hand_openpose))
 ```
@@
 (faces <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
-  geom_point(alpha=.8) +
+  geom_point(alpha=.5) +
   theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
@@
   ylab('Proportion Faces') + 
+     theme_few(base_size=16) +
   xlab('Age bin (months)') +
-  ylim(0,.5))
+  ylim(0,.5) +
+  theme(legend.position="none"))
 ```
@@
 (hands <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
-  geom_point(alpha=.8) +
+  geom_point(alpha=.5) +
   geom_smooth(span=10) + 
+     theme_few(base_size=16) +
   ylab('Proportion Hands') + 
   xlab('Age bin (months)') +
-  ylim(0,.5))
+  ylim(0,.5)+
+  theme(legend.position="none"))
 ```
@@
 (face_v_hand <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
-  geom_point(alpha=.8) +
+  geom_point(alpha=.5) +
   geom_smooth(span=10) + 
-  theme_few(base_size=18) +
+  theme_few(base_size=16) +
   ylab('Proportion Faces - Hands') + 
-  xlab('Age (months)'))
+  xlab('Age (months)')+
+  theme(legend.position="right"))
+```
+
+### Compiled plot
+```{r}
+
+ggarrange(faces,hands,face_v_hand, nrow=1)
 ```
@@
 ```
-
 ## By location
 ### Summarize faces vs hands by location
+
 ```{r}
@@
 # Cropped analysis
+
+### Make bins across which to analyze data
+```{r}
+bin_size = 7
+min_age = min(d_cropped$age_days)
+max_age = max(d_cropped$age_days)
+bin_starts = seq(min_age-1, max_age+1,bin_size)
+bins = c(bin_starts, max_age)
+
+d_cropped <- d_cropped %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
+d_cropped$age_day_bin = as.numeric(as.character(d_cropped$age_day_bin))
+
+d_cropped$face_openpose = as.logical(d_cropped$face_openpose)
+# d_cropped$hand_openpose = as.logical(d_cropped$hand_openpose)
+
+```
+
 ## Faces vs hands
@@
   summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_detected_cropped) / num_detect) 
-
-summary_by_age_cropped_limited <- summary_by_age_cropped %>%
-  filter(age_day_bin < 24.1)
+# 
+# summary_by_age_cropped_limited <- summary_by_age_cropped %>%
+#   filter(age_day_bin < 24.1)
 ```

### 2020-01-24 analysis/analysis_goldset.Rmd
separate out analysis scripts for efficiency

@@
     select(child_hand_seg, adult_hand_seg, full_image_path, vid_name, frame)
+
+# save(child_adult_hand_annotations, file="../data/child_adult_hand_annotations.RData")
 ```
@@
 ```{r}
-face_vs_hands_goldset <- d %>%
+d_with_child_hands <- d %>%
   full_join(child_adult_hand_annotations, by=c("vid_name", "frame")) %>%
   mutate(frame_id = paste0(vid_name, '-', frame)) %>%
-  replace_na(list(adult_hand_seg = FALSE, child_hand_seg = FALSE)) %>% ## replace NAs from segmentation with false for hands since all we got annotations for all frames with hands 
+  replace_na(list(adult_hand_seg = FALSE, child_hand_seg = FALSE)) ## replace NAs from segmentation with false for hands since all we got annotations for all frames with hands
+
+face_vs_hands_goldset <- d_with_child_hands
   group_by(child_id, age_day_bin) %>%
@@
   filter(!is.na(child_id))
+
+```
+
+```{r}
+ return_prf = function(eval){
+  tp=sum(eval == "TP")
+  fp=sum(eval == "FP")
+  fn=sum(eval == "FN")
+  p = tp / (tp + fp)
+  r = tp / (tp + fn)
+  f=( 2 * p * r )/ (p + r)
+  num_detect = length(eval)
+  out <- data.frame(p,r,f,num_detect)
+  return(out)
+ }
+
+evaluate_detector <- function(truth, detection) {
+  if (truth == TRUE) {
+    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
+    else return("FN") # was face/wrist, missed face/wrist
+  }
+  else {
+    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
+    else return("FP") # was not face/wrist, detected face/wrist
+  }
+}
+
+bin_size = 30
+min_age = min(d_with_child_hands$age_days, na.rm=TRUE)
+max_age = max(d_with_child_hands$age_days,na.rm=TRUE)
+bin_starts = seq(min_age-1, max_age+1,bin_size)
+bins = c(bin_starts, max_age)
+d_with_child_hands <- d_with_child_hands %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
+
+prf_by_age_child_hands <- d_with_child_hands %>%
+  filter(!is.na(hand_openpose)) %>%
+  mutate(child_hand_eval = evaluate_detector(child_hand_seg, hand_openpose)) %>%
+  mutate(adult_hand_eval = evaluate_detector(adult_hand_seg, hand_openpose)) %>%
+  group_by(age_day_bin, child_id) %>%
+  do(return_prf(.$child_hand_eval))
+
+prf_by_age_adult_hands <- d_with_child_hands %>%
+  filter(!is.na(hand_openpose)) %>%
+  mutate(adult_hand_eval = evaluate_detector(adult_hand_seg, hand_openpose)) %>%
+  group_by(age_day_bin, child_id) %>%
+  do(return_prf(.$adult_hand_eval))
+
+prf_by_age_child_hands$age_day_bin = as.numeric(prf_by_age_child_hands$age_day_bin)
+prf_by_age_adult_hands$age_day_bin = as.numeric(prf_by_age_adult_hands$age_day_bin)
+
+child_hand_scores  = ggplot(prf_by_age_child_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth(span=10)  +
+  ylim(0,.6) +
+  ylab('F-score - Child hand detection')
+
+adult_hand_scores = ggplot(prf_by_age_adult_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth(span=10)  +
+  ylab('F-score - Adult hand detection')
+  ylim(0,.6) +
+ggarrange(child_hand_scores,adult_hand_scores, nrow=1)
+
+  child_hand_scores  = ggplot(prf_by_age_child_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth(span=10)  +
+  ylim(0,.6) +
+  ylab('F-score - Child hand detection')
+
+adult_hand_scores = ggplot(prf_by_age_adult_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth(span=10)  +
+  ylab('F-score - Adult hand detection')
+  ylim(0,.6) +
+ggarrange(child_hand_scores,adult_hand_scores, nrow=1)
+
+  child_hand_scores_r  = ggplot(prf_by_age_child_hands, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth(span=10)  +
+  ylim(0,.6) +
+  ylab('Recall - Child hand detection')
+
+adult_hand_scores_r = ggplot(prf_by_age_adult_hands, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth(span=10)  +
+  ylab('Recall - Adult hand detection')
+  ylim(0,.6) +
+ggarrange(child_hand_scores_r,adult_hand_scores_r, nrow=1)
+
+    child_hand_scores_r  = ggplot(prf_by_age_child_hands, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth(span=10)  +
+  ylim(0,.6) +
+  ylab('Precision - Child hand detection')
+
+adult_hand_scores_r = ggplot(prf_by_age_adult_hands, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth(span=10)  +
+  ylab('Precision - Adult hand detection')
+  ylim(0,.6) +
+ggarrange(child_hand_scores_r,adult_hand_scores_r, nrow=1)
 
@@
 ggarrange(faces_vs_adult_hands, faces_vs_all_hands, nrow=1)
+```
+
+```{r}
+ return_prf = function(eval){
+  tp=sum(eval == "TP")
+  fp=sum(eval == "FP")
+  fn=sum(eval == "FN")
+  p = tp / (tp + fp)
+  r = tp / (tp + fn)
+  f=( 2 * p * r )/ (p + r)
+  num_detect = length(eval)
+  out <- data.frame(p,r,f,num_detect)
+  return(out)
+ }
+
 ```
@@
 ```{r}
-# g_seg_info <- g_seg %>%
-#   distinct(full_image_path, vid_name_short, frame_ind)
+# # g_seg_info <- g_seg %>%
+# #   distinct(full_image_path, vid_name_short, frame_ind)
+# #   
+# # bb_check <- bb %>%
+# #   mutate(frame_ind = frame, vid_name_short = vid_name) %>%
+# #   left_join(g_seg_info, by=c("vid_name_short","frame_ind")) %>%
+# #   filter(!is.na(full_image_path)) %>%
+# #   filter(mean_conf > 0)
 # 
-# bb_check <- bb %>%
-#   mutate(frame_ind = frame, vid_name_short = vid_name) %>%
-#   left_join(g_seg_info, by=c("vid_name_short","frame_ind")) %>%
-#   filter(!is.na(full_image_path)) %>%
-#   filter(mean_conf > 0)
-
-# # dir.create(paste0('bbcheck/'))
-# unique_images <- bb_check$full_image_path[101:200]
-# 
-# for (image in unique_images){
-#   this_image_rgb <- image_read(image)
-#   img <- image_draw(this_image_rgb)
-#   a <- bb_check %>%
-#     filter(full_image_path %in% image) 
-#   
-#   # rect(a$x_pos, a$y_pos-a$height_y, a$x_pos+a$width_x, a$y_pos)
-#   text(a$center_x, a$center_y, a$center_y)
-#   
-#   annotated_file = paste0('bbcheck/',unique(a$vid_name_short), unique(a$frame_ind), 'OP-center.jpg')
-#   image_write(img, annotated_file)
-#   dev.off()
-# }
+# # # dir.create(paste0('bbcheck/'))
+# # unique_images <- bb_check$full_image_path[101:200]
+# # 
+# # for (image in unique_images){
+# #   this_image_rgb <- image_read(image)
+# #   img <- image_draw(this_image_rgb)
+# #   a <- bb_check %>%
+# #     filter(full_image_path %in% image) 
+# #   
+# #   # rect(a$x_pos, a$y_pos-a$height_y, a$x_pos+a$width_x, a$y_pos)
+# #   text(a$center_x, a$center_y, a$center_y)
+# #   
+# #   annotated_file = paste0('bbcheck/',unique(a$vid_name_short), unique(a$frame_ind), 'OP-center.jpg')
+# #   image_write(img, annotated_file)
+# #   dev.off()
+# # }
 ```
@@
 
+turk_annotations_seg = "../data/turk_segmentations_hands_only_processed.csv" 
+g_seg = read.csv(turk_annotations_seg) %>%
+  select(-HITID, -HITTypeId, -WorkerID) %>%
+  mutate(center_x = left + width/2, center_y = top + height/2)
+
 child_hands <- g_seg %>%
@@
   filter(label=="Adult hand")
+
 ##
-ggplot(child_hands, aes(x=left, y=top)) +
+child_hand_plot <- ggplot(child_hands, aes(x=center_x, y=center_y)) +
   geom_point() + 
@@
   coord_fixed(ratio=1) +
-  ggtitle('Child hands (mturk)') +
-  ylim(0,height_px) +
+  ggtitle('(A). Child hand density') +
+  ylim(0,480) +
+  xlim(0,640) +
+  theme(legend.position="none") +
   scale_y_reverse()
 ##
-ggplot(adult_hands, aes(x=left, y=top)) +
+adult_hand_plot <- ggplot(adult_hands, aes(x=center_x, y=center_y)) +
   geom_point() + 
@@
   coord_fixed(ratio=1) +
-  ylim(0,height_px) +
+  ylim(0,480) +
+  xlim(0,640) +
   scale_y_reverse() +
-  ggtitle('Adult hands (mturk)')
+  theme(legend.position="none") +
+  ggtitle('(B). Adult hand density')
+
+ggarrange(child_hand_plot, adult_hand_plot, nrow=1)
 

### 2020-01-24 analysis/preprocess_datasets.Rmd
updates to main analysis; first pass at integrating in paper.rmd
separate out analysis scripts for efficiency

@@
 
+save(meta, file = '../data/saycam_metadata.RData')
+
 ```
@@
 # join with metadata and exclude bad videos
-d_all <- detections %>%
+d_SA <- detections %>%
   left_join(meta, by='vid_name') %>%
@@
 ## All 6 of the video that were not in this file (but were in the detections file) happened to be 6 very bad quality videos; excluding from detections
-exclude_bad_quality <- d_all %>%
+exclude_bad_quality <- d_SA %>%
   filter(!vid_name %in% right_side_up$video)
 
-d_all <- d_all %>%
+d_SA <- d_SA %>%
   filter(!vid_name %in% exclude_bad_quality$vid_name)
@@
 num_orig_videos = length(unique(detections$vid_name))
-num_videos_retained = length(unique(d_all$vid_name))
+num_videos_retained = length(unique(d_SA$vid_name))
 assert_that(num_videos_retained < num_orig_videos)
@@
 
-### Make detections into logical vectors and compute "person" as either face/hand
+## Load, process, merge Y's data
+### Now load in bounding box data from Y, which has detection rates built in
 ```{r}
-d_all$face_openpose = as.logical(d_all$face_openpose)
-d_all$hand_openpose = as.logical(d_all$hand_openpose)
-d_all$person_openpose = (as.logical(d_all$face_openpose) | as.logical(d_all$hand_openpose))
-d_all$both_openpose = (as.logical(d_all$face_openpose) & as.logical(d_all$hand_openpose))
+load('../data/Y_bounding_boxes.RData') #df again
+y_data <- df %>%
+  rowwise() %>%
+  mutate(age = str_split_fixed(vid_name, '_',4)[,3])
+
+remove(df)
+
+### wrangle age data for Y
+d_y <- y_data %>%
+  mutate(age_months = as.numeric(substr(age, 0,2)), days_to_add = as.numeric(substr(age, 3,4))) %>%
+  mutate(age_days = age_months*30 + days_to_add)
+
+save(y_data, file = '../data/Y_bounding_boxes_cleaned.RData')
 ```
 
-### Look at any suspicious videos with very high face detections (candidate missed allocentric videos)
+### Do basic preprocessing on Y detection's
 ```{r}
-vid_check <- d_all %>%
-  filter(child_id == "S") %>%
-  group_by(vid_name,vid_name, Databrary.Link) %>%
-  summarize(prop_faces =mean(face_openpose))
 
-high_faces <- vid_check %>%
-  filter(prop_faces>.8)
+### count hands/faces from bounding box outputs for Y -- for d_all
+y_detections <- d_y %>%
+  group_by(vid_name, frame,age_days) %>%
+  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0))
+
+y_detections <- y_detections %>%
+  # rename(hand_openpose = hand_detected, face_openpose = face_detected) %>%
+  mutate(child_id = "Y") %>%
+  left_join(meta)
+
+save(y_detections, file='../data/y_detections_preprocessed.RData')
 ```
 
-### Make bins across which to analyze data
+### Merge detections from Y with other kids
 ```{r}
-bin_size = 7
-min_age = min(d_all$age_days)
-max_age = max(d_all$age_days)
-bin_starts = seq(min_age-1, max_age+1,bin_size)
-bins = c(bin_starts, max_age)
-```
-
-### And save out into dataframe
-```{r}
-d_all <- d_all %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
-d_all$age_day_bin = as.numeric(as.character(d_all$age_day_bin))
+d_all <- d_SA %>%
+  mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
+  full_join(y_detections)
 ```
@@
 ```{r}
-save(d_all, file = '../data/openpose_detections_filtered.RData')
+save(d_all, file = '../data/openpose_detections_filtered_threekids.RData')
+```
+## Save out vid info for use with joining stuff later
+```{r}
+# vid_info_all <- d_all %>%
+#   select(vid_name, frame, age_days, child_id)
+# 
+# save(vid_info_all, '../data/vid_info_all.RData')
+```
+### Look at any suspicious Sam videos with very high face detections (candidate missed allocentric videos)
+```{r eval=FALSE}
+# vid_check <- d_all %>%
+#   filter(child_id == "S") %>%
+#   group_by(vid_name,vid_name, Databrary.Link) %>%
+#   summarize(prop_faces =mean(face_openpose))
+# 
+# high_faces <- vid_check %>%
+#   filter(prop_faces>.8)
 ```
 
-## Load bounding boxes to get cropped detections
+# Cropped detections
+## Load bounding boxes from S/A to get cropped detections
 ```{r}
@@
 bb_all <- df %>%
-  filter(right_side_up==0) %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))
+  filter(right_side_up==0)
 
@@
 
-## Make cropped detections in top 60% of frame
-```{R}
-detections_cropped <- bb_all %>%
-  filter(height <.6) %>%  ## cut off bottom part of frame
-  group_by(vid_name, frame, child_id, age_day_bin) %>%
-  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0)) %>% # if any faces or hands
-  distinct(vid_name, frame, age_day_bin,face_detected, hand_detected)
+## Make cropped detections in top 60% of frame for Y
+```{r}
+load(file = '../data/Y_bounding_boxes_cleaned.RData')
+d_y <- y_data %>%
+  mutate(age_months = as.numeric(substr(age, 0,2)), days_to_add = as.numeric(substr(age, 3,4))) %>%
+  mutate(age_days = age_months*30 + days_to_add)
 
-## clean up so that we can join with original dataframe
-detections_cropped <- detections_cropped %>%
+detections_cropped_Y <- d_y %>%
+  filter(person==0) %>% #only get frames where detections
+  filter(height <(.6*480)) %>%  ## cut off bottom part of frame
+  group_by(vid_name, frame, child_id, age_days) %>%
+  summarize(hand_detected_cropped = (sum(label=="hand")>0), face_detected_cropped = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))
+
+detections_cropped_Y <- detections_cropped_Y %>%
  ungroup() %>%
-  rename(hand_detected_cropped = hand_detected, face_detected_cropped = face_detected) %>%
  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id))
-
-## now join with big dataframe
-d_cropped <- d_all %>%
-  as_tibble() %>%
-  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id),face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
-  select(vid_name, frame, child_id, age_day_bin, face_openpose, hand_openpose) %>%
-  left_join(detections_cropped, by=c("vid_name","frame","age_day_bin","child_id"))
-
-d_cropped <- d_cropped %>%
-  replace_na(list(hand_detected_cropped = FALSE, face_detected_cropped = FALSE))  ## replace NAs from cropped anlaysis
-
-# and save it out
-save(d_cropped, file = '../data/openpose_detections_filtered_cropped.RData')
-```
-
-# Render out images based on annotations if desired
-## True positives on faces?
-```{r eval=FALSE}
-faces_only_op_cor <- m %>%
-  filter(faces == TRUE) %>%
-  filter(face_openpose == TRUE)
-
-# how about images where open pose got it? these should be most obvious
-dir.create(paste0('faces_tp/'))
-for (i in seq(1,length(faces_only_op_cor$full_image_path),1)){
-  image_read(as.character(faces_only_op_cor$full_image_path[i])) %>%
-  image_append(stack = FALSE) %>%
-  image_write(file.path(paste0("faces_tp/", faces_only_op_cor$short_image_path[i])))
-}
 
@@
 
-## False positives on facs?
-```{r eval=FALSE}
-to_write <- m %>%
-  filter(faces == FALSE) %>%
-  filter(face_openpose == TRUE)
+## Make cropped detections in top 60% of frame for S,A
+```{R}
+detections_cropped_SA <- bb_all %>%
+  filter(height <.6) %>%  ## cut off bottom part of frame
+  group_by(vid_name, frame, child_id, age_days) %>%
+  summarize(hand_detected_cropped = (sum(label=="hand")>0), face_detected_cropped = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))
 
-# how about images where open pose got it? these should be most obvious
-dir.create(paste0('faces_fp/'))
-for (i in seq(1,length(to_write$full_image_path),1)){
-  image_read(as.character(to_write$full_image_path[i])) %>%
-  image_append(stack = FALSE) %>%
-  image_write(file.path(paste0("faces_fp/", to_write$short_image_path[i])))
-}
+all_cropped_detections <- detections_cropped_SA %>%
+  ungroup() %>%
+  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id)) %>%
+  full_join(detections_cropped_Y)
 
@@
 
-## False negatives on faces?
-```{r eval=FALSE}
-to_write <- m %>%
-  filter(faces == TRUE) %>%
-  filter(face_openpose == FALSE)
+## need to get "FALSE" on frames where we didn't have info to be able to compute proportions; uses d_all from earlier and fills it all back in
+```{r}
+# load('../data/openpose_detections_filtered_threekids.RData') # d_all
 
-# how about images where open pose got it? these should be most obvious
-dir.create(paste0('faces_fn/'))
-for (i in seq(1,length(to_write$full_image_path),1)){
-  image_read(as.character(to_write$full_image_path[i])) %>%
-  image_append(stack = FALSE) %>%
-  image_write(file.path(paste0("faces_fn/", to_write$short_image_path[i])))
-}
+d_cropped <- d_all %>% ## needs to be loaded
+  as_tibble() %>%
+  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id)) %>%
+  select(vid_name, frame, child_id, age_days, face_openpose) %>%
+  left_join(all_cropped_detections, by=c("vid_name","frame","age_days","child_id")) %>%
+  replace_na(list(hand_detected_cropped = FALSE, face_detected_cropped = FALSE ))
+```
+
+### now save
+```{r}
+save(d_cropped, file = '../data/openpose_detections_filtered_cropped_allthreekids.RData')
 
 ```
+
+# Make bb detections only
+```{r}
+## import bounding boxes
+load('../data/all_bounding_boxes.RData')
+load('../data/Y_bounding_boxes_cleaned.RData')
+
+right_side_up_file = "../data/video_right-side-up.csv"
+right_side_up =read.csv(right_side_up_file)
+
+# get INCORRECT videos 
+flipped_videos <- right_side_up %>%
+  filter(right_side_up==1) %>%
+  rename(vid_name = video)
+
+```
+
+```{r}
+## frame
+height_px = 480; width_px = 640
+bb_all <- y_data %>%
+  filter(person==0) %>% # only rows with detections for now
+  filter(!is.na(child_id)) %>%
+  mutate(left = left*width_px, top = top*height_px, height = height*height_px, width = width*width_px) %>% #unnormalize data...
+  full_join(df) %>% # join with S/A
+  filter(right_side_up==0) %>% # get rid of allocentric
+  mutate(center_x = left + width/2, center_y = top - height/2, area = width*height)
+
+save(bb_all, file = '../data/all_bounding_boxes_three_kids_preprocessed.RData')
+
+```
+
+```

### 2020-01-24 analysis/render_annotations.R

@@ -1,0 +1,49 @@
+
+# Render out images based on annotations if desired
+## True positives on faces?
+```{r eval=FALSE}
+faces_only_op_cor <- m %>%
+  filter(faces == TRUE) %>%
+  filter(face_openpose == TRUE)
+
+# how about images where open pose got it? these should be most obvious
+dir.create(paste0('faces_tp/'))
+for (i in seq(1,length(faces_only_op_cor$full_image_path),1)){
+  image_read(as.character(faces_only_op_cor$full_image_path[i])) %>%
+    image_append(stack = FALSE) %>%
+    image_write(file.path(paste0("faces_tp/", faces_only_op_cor$short_image_path[i])))
+}
+
+```
+
+## False positives on facs?
+```{r eval=FALSE}
+to_write <- m %>%
+  filter(faces == FALSE) %>%
+  filter(face_openpose == TRUE)
+
+# how about images where open pose got it? these should be most obvious
+dir.create(paste0('faces_fp/'))
+for (i in seq(1,length(to_write$full_image_path),1)){
+  image_read(as.character(to_write$full_image_path[i])) %>%
+    image_append(stack = FALSE) %>%
+    image_write(file.path(paste0("faces_fp/", to_write$short_image_path[i])))
+}
+
+```
+
+## False negatives on faces?
+```{r eval=FALSE}
+to_write <- m %>%
+  filter(faces == TRUE) %>%
+  filter(face_openpose == FALSE)
+
+# how about images where open pose got it? these should be most obvious
+dir.create(paste0('faces_fn/'))
+for (i in seq(1,length(to_write$full_image_path),1)){
+  image_read(as.character(to_write$full_image_path[i])) %>%
+    image_append(stack = FALSE) %>%
+    image_write(file.path(paste0("faces_fn/", to_write$short_image_path[i])))
+}
+
+```

### 2020-01-24 paper/cogsci/paper.Rmd
cogsci paper draft with analysis integrated

--- 2020-01-14 paper/cogsci/paper.Rmd
@@
 ---
-title: "A longitudinal investigation of the social information in natural infant visual experience"
+title: "Detecting social information in a dense dataset of infants’ natural visual experience"
 bibliography: library.bib
@@
 Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants.
-    The present research aims to test the generality of these findings using the SAYcam dataset [@SAYcam], a longitudinal collection of over 1700 headcam videos collected from three children along a span of 6 to 32 months of age.
-    To do so, we validate the use of a modern convolutional neural network for pose detection (OpenPose) for the detection of people, faces, and hands to analyze these naturalistic infant egocentric videos.
-    We then apply this model to the entire dataset, analyzing the prevalence of faces across age, individuals, and activity contexts. 
-    Overall, we find a higher prevalence of hands seen by infants than previously reported, considerably variability in the proportion of faces/hands seen across different locations (e.g., living room vs.
-kitchen), yet surprising consistency across both individual children.
+Here, we examine the prevalence of faces and hands in a longitudinal collection of over 1400 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam].
+To analyze these naturalistic infant egocentric videos, we first validate the use of a modern convolutional neural network for pose detection (OpenPose) for the detection of faces and hands.
+We then apply this model to the entire dataset, finding a decrease in the proportion of faces vs.
+hands across age up to the end of the second year of life [@Fausey2016].
+In addition, we find considerable variability in the proportion of faces/hands viewed by children in different locations (e.g., living room vs.
+kitchen), demonstrating that variability across activity contexts may be a driving factor in the amount of social information that infants’ experience.
 
@@
                       message=F, sanitize = T)
+
 ```
@@
 # Introduction
+Infants are confronted by a blooming, buzzing onslaught of stimuli [@James1981] which they must learn to parse to make sense of the world around them.
+Yet they do not embark on this learning process alone: From as early as 3 months of age, young infants follow overt gaze shifts [@Gredeback2010], and even newborns prefer to look at faces with direct vs.
+averted gaze [@Farroni2002], despite their limited acuity.
+As faces are likely to be an important conduit of social information that scaffolds cognitive development, cognitive scientists have long hypothesized that faces are prevalent in the visual experience of young infants.
 
-Infants are confronted by a blooming, buzzing onslaught of stimuli (James, 1891) which they must learn to parse to make sense of the world around them. 
-Yet infants do not embark on this learning process alone: infants are engaged in learning from their caregivers from early infancy. 
-From as early as 3 months of age, young infants follow overt gaze shifts [@Gredeback2010], and even newborns prefer to look at faces with direct vs.
-averted gaze [@Farroni2002], despite their limited acuity [CITE].
-Faces are thus likely to be an important conduit of social information that scaffolds infants cognitive development. 
-Given this importance, developmentalists have long hypothesized [CITE] that faces are prevalent in the visual experience of young infants. 
-However, as even the viewpoint of a walking child is not easily predicted by our own adult intuitions (Clerkin, Hart, Rehg, Yu, & Smith, 2017; @Franchak2011; @Yoshida2008), researchers have begun to record the egocentric views collected from infants and toddlers wearing head-mounted cameras to test theories about the infant perspective.
+Yet until recently most hypotheses about infants’ visual experience have gone untested.
+Though parents and scientists alike have strong intuitions about what infant’s see, even the viewpoint of a walking child is not easily predicted by these intuitions (Clerkin, Hart, Rehg, Yu, & Smith, 2017; Franchak et al., 2011; Yoshida & Smith, 2008).
+By equipping infants and toddlers with head-mounted cameras, researchers have begun to document the infant egocentric perspective on the world.
+Using these methods, a growing body of work now demonstrates that the viewpoints of very young infants (less than 4 months of age) are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @Sugden2014; @Jayaraman2018].
 
-A growing body of work now demonstrates that the viewpoints of very young infants--less than 4 months of age--are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @Sugden2014; @Jayaraman2018].
-However, as infants mature, their perspective starts to capture views of hands paired with the objects they are acting on [@Fausey2016]. 
-As infants learn to use their own hands to act on the world, they may focus on manual actions taken by their social partners. 
-Furthermore, caregivers may start to use their hands more with communicative intent, directing infants attention with pointing and gestures to particular events or objects during play (Yu & Smith, 2013).
+As infants motor and cognitive abilities mature beyond these early months, their perspective on the world becomes even more varied.
+Crawlers see fewer faces and hands than do walking children [@Sanchez2018; @Franchak papers] as well as different view of objects [@Soska2010].
+Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, as their perspective starts to capture views of hands paired with the objects they are acting on [@Fausey2016].
+In turn, caregivers may start to use their hands with more communicative intent, directing infants attention with pointing and gestures to different events or objects during play [@YuSmith2013].
 
-The present research aims to test the generality of these findings using the SAYcam dataset [@SAYcam], a longitudinal collection of over 1700 headcam videos collected from three children along a span of 6 to 32 months of age.
-In addition to its size and longitudinal nature, this dataset builds on those used in previous research in two key ways. 
-First, recordings were from a variety of many different naturalistic contexts, encompassing infants’ viewpoints during both activities outside and inside the home. 
-Second, the cameras used in this longitudinal study encompassed a much wider field of view than those typically used, allowing a more complete picture of the infant perspective.
+Here, we analyze the social information present in the infant visual perspective by analyzing a longitudinal collection of over 1400 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam].
+In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways.
+First, recordings were taken under a large variety of contexts, encompassing infants’ viewpoints during both activities outside and inside the home.
+Even in other naturalistic datasets, the incredible variety in a typical infant’s experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth).
+Second, the head-mounted cameras used in the SAYcam dataset captured a substantially larger field of view than those typically used, allowing a more complete picture of the infant perspective.
+Head-mounted cameras with a more restricted field of view do still capture where infants are foveating most of the time [@YoshidaSmith2008, @SmithFausey-Review] but may still fail to capture short saccades to either faces or hands in the periphery, as the timescale of head movements is much longer.
 
-However, with hundreds of hours of footage (>30M frames), this large dataset truly necessitates a shift to an automated annotation strategy. 
-Indeed, annotation of the frames extracted from egocentric videos has been to be prohibitively time-consuming, meaning that many of the frames are not inspected. 
-For example, @Fausey2016, collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand annotated (by four coders), totalling 103,383 frames (per coder)--an impressive number of annotations but nonetheless only 0.67% of the collected footage.
-To address this challenge, we first validate the use of a modern computer vision model [@Cao2018openpose] to automatically detect the presence of hands and faces from the infant egocentric viewpoint. 
-In particular, we focus on OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints (135 in total) that operates well on scenes including multiple people even if they are partially-occluded (see Figure 1).
-We then apply these methods at scale to the larger dataset, allowing us to analyze the proportion of faces and hands observed by each child across age and activity context.
+With hundreds of hours of footage (>29M frames), this large dataset necessitates a shift to an automated annotation strategy.
+Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that many frames are typically not inspected, even in the most comprehensive studies.
+For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand annotated (by four coders), totalling 103,383 frames (per coder)—an impressive number of annotations but nonetheless only 0.67% of the collected footage.
+To address this challenge, we use a modern computer vision model of pose detection to automatically detect the presence of hands and faces from the infant egocentric viewpoint.
+Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints that operates well on scenes including multiple people, even if they are partially-occluded (see Figure 1).
 
-In the following paper, we first describe the dataset and the pose model used in the following analyses and validate the use of this model for extracting our key descriptive variables by comparing to a human-annotated gold set of 24,000 frames.
-Next, we analyze key descriptive variables, including those that have been previously reported to vary across age, including the relative proportions of faces vs.
-hands and the sizes of the faces, over the entire dataset (30M frames), finding a greater prevalence of hands than has been previously reported.
-We then investigate sources of variability in our more naturalistic dataset that may explain these differences, including a diversity of activity contexts as well as a larger field of view captured by our cameras.
+In the following paper, we first describe the dataset and validate the use of this model by comparing face and hand detections to a human-annotated set of 24,000 frames.
+Next, we report how the proportion of faces and hands changes across age.
+We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the present cameras as well as a diversity of locations during which videos were recorded.
+
+```{r}
+## Read in data 
+### Load preprocessed and filtered detections
+load('../../data/openpose_detections_filtered_threekids.RData') #d_all
+load('../../data/openpose_detections_filtered_cropped_allthreekids.RData') # d_cropped
+```
+
+```{r}
+### Choose bins across which to analyze data
+bin_size = 7 # days
+min_age = min(d_all$age_days)
+max_age = max(d_all$age_days)
+bin_starts = seq(min_age-1, max_age+1,bin_size)
+bins = c(bin_starts, max_age)
+```
+
+```{r}
+## Make summary stats for cropped and uncropped detedctions
+summary_by_age <- d_all %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+  group_by(age_day_bin, child_id) %>%
+  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect)
+
+summary_by_age_cropped <- d_cropped %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+  group_by(age_day_bin,child_id) %>%
+  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_detected_cropped) / num_detect) 
+```
+
+```{r} 
+### How large is the dataset we're analyzing?
+num_frames = length(d_all$frame)
+
+fps=30
+num_seconds = length(d_all$frame)/fps
+num_videos = length(unique(d_all$vid_name))
+num_minutes = num_seconds/60
+num_hours = num_minutes/60
+num_days = num_hours/24 
+```
 
@@
 ## Dataset
-
-Videos captured by the headcam were 640x480 pixels, and a fisheye lens was attached to the camera to increase 109 degrees horizontal x 70 degrees vertical. 
-Children wore headcams at least twice weekly, for approximately one hour per recording session. 
-One weekly session was on the same day each week at a roughly constant time of day, while the other(s) were chosen arbitrarily at the participating family's discretion. 
+The dataset is described in detail in @SAYcam; we summarize these details here.
+Children wore Veho Muvi miniature cameras mounted on a custom camping headlamp harness (“headcams”) at least twice weekly, for approximately one hour per recording session.
+One weekly session was on the same day each week at a roughly constant time of day, while the other(s) were chosen arbitrarily at the participating family’s discretion.
 At the time of the recording, all three children were in single-child households.
+Videos captured by the headcam were 640x480 pixels, and a fisheye lens was attached to the camera to increase the field of view to approximately 109 degrees horizontal x 70 degrees vertical.
 Videos[^1] with technical errors or that were not taken from the egocentric perspective were excluded from the dataset.
-We analyze 1,636 videos, with a total duration of XX hours (XX million frames).
-
+While data collection for the third child (Y) is still ongoing, here we analyze `r num_videos` videos, with a total duration of `r num_hours` hours (>29 million frames).
 [^1]: All videos are available at https://nyu.databrary.org/volume/564
 
-## Part 1: How well can we capture social information using computer vision?
+```{r examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=3.5, set.cap.width=T, num.cols.cap=2, fig.align = "center", fig.cap = "Example frames taken from the dataset, illustrating variability in the infant perspective across different locations.
+OpenPose detections are shown overlaid on these images."}
+examples <- png::readPNG("figs/modifiedOPfigure_v3.png")
+grid::grid.raster(examples)
+
+```
+
+## Assessing automated social annotations
 
 ### Computer vision model
-To automatically annotate the millions of frames in SAYcam, we use OpenPose [@Cao2018openpose; @Simon2017hand], a computer vision model optimized for jointly detecting human face, body, hand, and foot keypoints (135 in total) that operates well on scenes including multiple people even if they are partially-occluded.
-This convolutional neural network (CNN)-based pose detector[^2] provided the locations of 18 body parts (ears, nose, wrists, etc.). 
-The system uses a CNN for initial anatomical detection and subsequently applies part affinity fields (PAFs) for part association, producing a series of body part candidates. 
-The candidates are then matched to a single individual and finally assembled into a pose; here, we only made use of outputs of the face and hand detection modules.
+To automatically annotate the millions of frames in SAYcam, we use OpenPose [@Cao2018openpose; @Simon2017hand].
+This pose detector[^2] provided the locations of 18 body parts (ears, nose, wrists, etc.).
+The system uses a convolutional neural network for initial anatomical detection and subsequently applies part affinity fields for part association, producing a series of body part candidates.
+The candidates are then matched to a single individual and finally assembled into a pose.
+Thus, while we only make use of the outputs of the face and hand detections, the entire set of pose information from an individual is used to determine the presence of a face/hand, making the process much more robust to occlusion than methods optimized to detect only faces or hands.
+Specifically, we tagged frames with detected nose keypoints as having a face, and frames with a wrist keypoint were tagged as having a hand.
 
@@
 ### Manual annotation strategy
-To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from the 1,636 videos of two children (S and A).
+To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A).
 Frames were jointly annotated for the presence of faces and hands.
-These randomly sampled frames covered XX of the videos present in the dataset.  
-A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated XX frames; agreement with the primary coder was XX%.
+A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated 3150 frames; agreement with the primary coder was >95%.
 
 ### Detection accuracy for faces and hands
-Overall, we found that face detections were slightly more accurate than hand detections,
 
-Precision and recall (F-score) variation across child/age for faces
+```{r}
+### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
+right_side_up_file = "../../data/video_right-side-up.csv"
+right_side_up =read.csv(right_side_up_file)
 
-Describe possible sources of variation that decrease scores for:
--Faces: weird viewpoints, occluded/side viewpoint, faces in books
--Hands: children's own hands, hands in books, side viewpoints
+# get INCORRECT videos
+flipped_videos <- right_side_up %>%
+  filter(right_side_up==1)
 
-Describe additional child vs. hand annotation; P/R/F variation across child vs. adult hands (better for adult hands, still OK for child hands)
+## load goal sample annotations
+load('../../data/ketan_gold_sample.RData')
 
-## Part 2: Access to social information across age
+## preprocess them
+ ketan_gold_out <- ketan_gold %>%
+   rowwise() %>%
+   mutate(vid_name = str_split_fixed(vid_name,".mp4",2)[,1])%>%
+   mutate(vid_name_short = str_split(vid_name,"[.]")[[1]][1]) %>%
+   filter(!vid_name_short %in% flipped_videos$video) %>%
+   mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
+   rename(face_present_ketan = face_present, hand_present_ketan = hand_present)
 
-Next, we analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands that were in view for each child. 
-Data from videos were binned according to the age of the child (in weeks) (see Figure XX). 
-First, we saw that the proportion of faces in view showed a moderate decrease across this age range, both when analyzing the random 24K frames as well as the entire dataset. 
-While these trends appear somewhat different than those observed in @Fausey2016, note that @Fausey2016 included data from very young infants (starting at 2 months while), while here the youngest videos coming from S and A around 6 and 9 months of age, respectively.
+# Function to evaluate detectors
+evaluate_detector <- function(truth, detection) {
+  if (truth == TRUE) {
+    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
+    else return("FN") # was face/wrist, missed face/wrist
+  }
+  else {
+    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
+    else return("FP") # was not face/wrist, detected face/wrist
+  }
+}
+
+# function to return prfs
+ return_prf_short = function(eval){
+  tp=sum(eval == "TP")
+  fp=sum(eval == "FP")
+  fn=sum(eval == "FN")
+  p = tp / (tp + fp)
+  r = tp / (tp + fn)
+  f=( 2 * p * r )/ (p + r)
+  return(c(p,r,f))
+ }
+
+ ## evaluate detectors
+ gold_sample <- ketan_gold_out %>%
+   mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose))
+
+ ## output prfs
+ face_performance = return_prf_short(gold_sample$face_eval_ketan)
+ hand_performance = return_prf_short(gold_sample$hand_eval_ketan)
+
+```
+As has been observed in other studies on automated annotation of headcam data [e.g.
+@frank2013, @REF-chenyu-hand-paper], detection tasks that are easy in third-person video can be quite challenging in egocentric videos, due to difficult angles and sizes as well as substantial occlusion.
+For example, the infant perspective often contains non-canonical viewpoints of faces (e.g., looking up at a caregiver's chin) as well as partially-occluded or oblique viewpoints of both faces and hands.
+
+To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / hits + false alarms), recall (hits / hits + misses), and f-score (the harmonic mean of precision and recall).
+In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`.
+For hands, the F-score was `r round(hand_performance[3],2)`, with a precision of `r round(hand_performance[1],2)` and recall of `r round(hand_performance[2],2)`.
+While face and hand detections showed moderately good precision, face detections were overall slightly more accurate than hand detections.
+Hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.
+We suspect that this is in part because children’s own hands were often in view of the camera and unconnected to a pose; this factor is explored in detail in the following analysis section.
+
+We also examined whether the precision, recall, and F-score for hands and faces varied per child as a function of age to see if there was any bias in the OpenPose detections related to age, and did not find substantial variation.
+Nonetheless, while OpenPose was trained on photographs from the adult perspective, this model still generalized relatively well to the egocentric infant viewpoint with no fine-tuning or post-processing of the detections.
+
+## Access to social information 
+### Changes across age
+
+We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands that were in view for each child.
+Data from videos were binned according to the age of the child (in weeks) (see Figure 2).
+First, when examining the younger age ranges (< 24 months) we saw that the proportion of faces in view showed a moderate decrease across this age range, both when analyzing the random 24K frames as well as the entire dataset (see Figure 2A).
+
+While these trends appear somewhat different than those observed in @Fausey2016, note that @Fausey2016 included data from very young infants (from 1-4 months of age), while here the youngest videos coming from S and A around 6 and 9 months of age, respectively.
 Similarly, our age range extends 8 months later than those infants in @Fausey2016, throughout a portion of third year of life.
 
-However, the most striking result from the dataset is a much greater proportion of hands in view than have previously been reported. 
-We found this to be true across all ages, in both children, and regardless of whether we analyzed human annotations (on the 24K random subset) or the entire dataset.   
+```{r FaceVsHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces vs.
+hands in the entire dataset (A) and when hand detections are restricted to the upper 60 percent of the field of view (B).
+Data from each child (A, S) are plotted separately and binned by each week that the videos were filmed; data is scaled by the number of frames in that age range."}
+
+faces <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
+  geom_point(alpha=.2) +
+  geom_smooth(span=10) + 
+  ylab('Proportion Faces') + 
+  # theme_few(base_size=16) +
+  xlab('Age (months)') +
+  ylim(0,.5) +
+  theme(legend.position="none") +
+  ggtitle('(A).') +
+  scale_colour_brewer(palette = "Dark2")
+
+hands <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.2) +
+  geom_smooth(span=10) + 
+  # theme_few(base_size=16) +
+  ylab('Proportion Hands') + 
+  xlab('Age (months)') +
+  ylim(0,.5)+
+  theme(legend.position="none") +
+  ggtitle('(B).') +
+  scale_colour_brewer(palette = "Dark2")
+
+face_v_hand <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.2) +
+  geom_smooth(span=10) + 
+  # theme_few(base_size=16) +
+  ylab('Proportion Faces - Hands') + 
+  xlab('Age (months)') +
+  ylim(-.3, .3) +
+  theme(legend.position = "none") +
+  ggtitle('(C).') +
+  scale_colour_brewer(palette = "Dark2")
+
+face_v_hand_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.2) +
+  geom_smooth(span=10) + 
+  # theme_few(base_size=16) +
+  ylab('Proportion Faces - Hands') + 
+  xlab('Age (months)') +
+  ylim(-.3, .3) +
+  theme(legend.position = "none") +
+  ggtitle('(D).')  +
+  scale_colour_brewer(palette = "Dark2")
+
+ggarrange(faces, hands, face_v_hand, face_v_hand_cropped, nrow=1)
+```
+
+However, the most striking result is a much greater proportion of hands in view than have previously been reported [@Fausey2016].
+We found this to be true across all ages, in both children, and regardless of whether we analyzed human annotations (on the 24K random subset) or OpenPose annotations on entire dataset.
+This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this is still an underestimate of the proportion of hands in view.
 One reason this could be the case is the much larger field of view that was captured by the cameras used in this study: unlike previous studies, our cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible.
-Thus, the field of view (FOV) of the fisheye lens used in @SAYcam was much wider (109 degrees horizontal x 70 degrees vertical) than the FOV of the lens used in @Fausey2016 (69 x 41 degrees).
+Thus, the field of view (FOV) of the fisheye lens used was larger (109 degrees horizontal x 70 degrees vertical) than the FOV of the lens used in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees.
 This larger field of view may have allowed the SAYcam cameras to capture not only the presence of a social partner’s hands interacting with objects, but also the children’s own hands, leading to more frequent hand detections.
 
-To assess this possibility, we obtained annotations for a subsample of XX frames in which a hand was detected in the random gold set; participants (recruited via AMT) were asked to draw bounding boxes around children’s hands and adult hands.
-Overall, we found that 34% of the hands detected by OpenPose in the random 24K sample were of children’s own hands (compared to 8% reported in @Fausey2016) suggesting that this difference in field of view did contribute substantially to the higher rate of detections in the frames.
-Heatmaps of the bounding boxes obtained from these annotations can be seen in Figure XX, showing that children’s hands tended to appear in the lower half of the frames.
+```{r}
+turk_annotations_seg = "../../data/turk_segmentations_hands_only_processed.csv" 
+g_seg = read.csv(turk_annotations_seg) %>%
+  select(-HITID, -HITTypeId, -WorkerID) %>%
+  mutate(center_x = left + width/2, center_y = top + height/2)
 
-We thus re-analyzed the entire dataset while restricting our analysis to a smaller, middle portion of the frame comparable to the field of view used in @Fausey2016 (XX vs XX degrees).
-To do so, we excluded hand detections that occurred in the bottom 40% of the frame, while retaining all detections that occurred in the top of the frame.  
-Overall, we found X, suggesting Y.
+child_hands <- g_seg %>%
+  filter(label=="Child hand")
 
-Intriguingly, we observed an unexpected trend in which the relative proportion of faces vs. hands increased during the third year of life; in particular, this seemed...(save for discussion?)
+adult_hands <- g_seg %>%
+  filter(label=="Adult hand")
+
+##
+child_hand_plot <- ggplot(child_hands, aes(x=center_x, y=center_y)) +
+  geom_point() + 
+  stat_density_2d(aes(fill = ..level..), geom="polygon") +
+  coord_fixed(ratio=1) +
+  # ggtitle('(A). Child hand density') +
+  ylim(0,480) +
+  xlim(0,640) +
+  ylab('') +
+  xlab('') +
+  theme_few(base_size=12) +
+  theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
+  scale_y_reverse()
+##
+adult_hand_plot <- ggplot(adult_hands, aes(x=center_x, y=center_y)) +
+  geom_point() + 
+  stat_density_2d(aes(fill = ..level..), geom="polygon") +
+  coord_fixed(ratio=1) +
+  ylim(0,480) +
+  xlim(0,640) +
+  scale_y_reverse() +
+  ylab('') +
+  xlab('') +
+  theme_few(base_size=12) +
+    theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) 
+  # ggtitle('(B). Adult hand density') 
+```
+
+```{r density, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=4, fig.height=2, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in teh 24K random gold set; each dot represents the center of a bounding box made by an adult participant."}
+ggarrange(child_hand_plot, adult_hand_plot, nrow=1)
+```
+
+To assess this possibility, we obtained human annotations for a subsample of 9051 frames in which a hand was detected in the random gold set; participants (recruited via AMT) were asked to draw bounding boxes around children’s hands and adult’s hands.
+Overall, we found that 34% of the hands in the random 24K sample were of children’s own hands (compared to 8% reported in @Fausey2016) suggesting that this difference in field of view did contribute substantially to the higher rate of hand detections in the frames.
+Heatmaps of the bounding boxes obtained from these annotations can be seen in Figure 3, showing that children’s hands tended to appear in the lower half of the frames.
+
+We thus re-analyzed the entire dataset while restricting our analysis to a smaller, upper portion of the frame comparable to the field of view used in @Fausey2016.
+To do so, we excluded hand detections that occurred in the bottom 40% of the frame, while retaining all hand detections that occurred in the top 60% of the frame.
+This coarse cropping of decreased the proportion of hand detections from `r mean(d_all$hand_openpose)`percent to `r mean(d_cropped$hand_detected_cropped)` percent.
+
+With this modified field of view, we now observed a more substantive decrease across age in the proportions of faces relative to hands.
+To quantify this trend, we fit a generalized linear mixed model to the binned detection rates from this smaller field of field to estimate changes in the proportion of faces vs.
+hands over age.
+To better approximate @Fausey2016, we also restricted our analysis to the age range seen in @Fausey2016, excluding videos when children were over 24 months of age, and indeed found that the proportion of faces vs.
+hands declined modestly with age (see Table 1).
+
+However, when we considered the entire age range, we also observed an unexpected trend in which the relative proportion of faces vs.
+hands increased again after 24 months of life; this trend was stronger in the full dataset.
+While we did not have any a priori hypotheses about this age range, we suspect that this could have to do with an increase in children’s independence from their caregiver as they master walking around and interacting with objects in the world on their own.
 
 ### Variability by Location 
-Next we examine variation in the presence of hands and faces across different locations. 
-Of the XX videos, the content of 1,829 have been manually annotated for filming location, activites taking place, and visible objects (see @SAYcam).
-XX of the videos were filmed in a single location, representing XX% of the dataset and roughly XX million frames (see @SAYcam). 
-To give a sense of the contexts the children experienced, the most frequent filming locations were the living room (339 videos), bedroom (182), kitchen (150), outside on property (129), child's bedroom (81), deck/porch (73), hallway (70), and off property (57).
-Filming only took place twice in the dining room (see Figure XX). 
-Activities varied predictability by these locations: for example, eating and XX occured in the kitchen, whereas playtime was the dominant activity in the living room (see Figure XX). 
-Bria: analyze activity
+```{r}
+load('../../data/child_adult_hand_annotations.RData')
+load('../../data/saycam_metadata.RData')
 
-Not this, but point out that eating was not frequent:
-The most frequent activities were sitting (410), playing (375), being held (352), and standing (297). 
-Eating was the 11th most-frequent activity (117 videos).
+num_videos_annotated = sum(!is.na(meta$Location))
+videos_included = sum(!is.na(meta$Location) & meta$count_locations==1)
 
-(goldset, full dataset)
+# percentage_of_dataset = sum(faces_vs_hands_to_plot$num_detect)/length(d_all$frame)
+# num_frames = sum(faces_by_location_to_plot$num_detect)
+```
 
-# Discussion
+How does variability across different contexts influence the social information in the infant view? 
+Intuitively, some activities in different contexts may be characterized by a much higher proportion of faces (e.g., diaper changes in bedrooms) than others (e.g., playtime in the living room).
+We thus next examined variation in presence of hands and faces across different locations.
+Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location o videos were filmed in.
+`r videos_included` were filmed in single location, representing 17 percent of the dataset and over 5 million frames (see @SAYcam).
+Activities varied somewhat predictability by these contexts: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.
+Overall, we found that the proportion of faces vs.
+hands varied across filming locations, and, to some extent, across children.
+For example, while both A and S saw a relatively similar proportion of faces vs.
+hands in the bedroom, they saw quite different amounts of faces vs.
+hands in kitchen.
 
-We demonstrate the feasibility of using modern computer vision models to vastly increase the efficiency of processing egocentric headcam footage, allowing us to annotate 100% of even very large datasets for the presence and size of people, hands, and faces.
-We validate the use of this model by comparing to a human-annotated gold set, and find X.
+```{r}
+d_by_location_cropped <- d_cropped %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+  left_join(meta) %>%
+  filter(!is.na(Location)) %>%
+  filter(count_locations==1) 
+# 
+# d_by_location_cropped$Location = droplevels(d_by_location_cropped$Location)
+# levels(d_by_location_cropped$Location)
 
-Analyzing this dataset has yielded a better understanding of infants' evolving access and attention to social information.
+face_hand_by_location_cropped <- d_by_location_cropped %>%
+  group_by(Location,child_id,age_day_bin) %>%
+  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_detected_cropped), num_detect = length(hand_detected_cropped))  %>%
+  filter(num_detect > 12000) %>% ## 18000 frames = 10 minutes of video at 30 fps %>%
+  mutate(faces_vs_hands = prop_faces - prop_hands)
 
-Need to think about the child's viewpoint relative to actual FOV as well as attention
+hands_to_plot_cropped <- face_hand_by_location_cropped %>%
+  multi_boot_standard(col="prop_hands") %>%
+  ungroup %>%
+  left_join(face_hand_by_location_cropped) %>%
+  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
+  mutate(Location = fct_reorder(Location, mean))
 
-Fausey 2016: 103,383 images; 
-Here: 30,000,000 frames; 300 fold increase in data
+faces_to_plot_cropped <- face_hand_by_location_cropped %>%
+  multi_boot_standard(col="prop_faces") %>%
+  ungroup %>%
+  left_join(face_hand_by_location_cropped) %>%
+  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
+  mutate(Location = fct_reorder(Location, mean)) 
+```
+
+```{r DetByLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3, fig.height=4, fig.cap = "Proportion of faces (A),  hands (B), and faces vs.
+hands  (C) by location in which egocentric videos were filmed; data from individual children are plotted separately (location annotations were not available for Y).
+Data are only taken from the top 60 percent of the frames so as to minimize the contribution of children’s own hands.
+Each dot represents data from a week in which videos were filmed and are scaled by the number of frames (i.e., amount of video) in that datapoint."}
+
+faces_loc = ggplot(faces_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
+  geom_point(aes(x=Location, y=prop_faces, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
+  # ylim(-.4,.4) +
+  coord_flip() + 
+  ylab('Proportion Faces')+
+  xlab('')+
+  scale_colour_brewer(palette = "Dark2") +
+  theme(legend.position = "none")
+
+hands_loc = ggplot(hands_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
+  geom_point(aes(x=Location, y=prop_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
+  # ylim(-.4,.4) +
+  coord_flip() + 
+  xlab('')+
+  ylab('Proportion Hands') +
+  scale_colour_brewer(palette = "Dark2") +
+  theme(legend.position = "none")
+
+ggarrange(faces_loc, hands_loc, nrow=2)
+```
+# General Discussion
+
+Broadly, the present analysis of this dense, longitudinal dataset has yielded a better understanding of infants' evolving access to social information.
+First, we found a relatively high proportion of faces in view in the videos from the youngest age ranges in each child, confirming previous findings [@Fausey2016].
+This is particularly notable given that, in cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age (e.g., Fausey 2016; Jayaraman, Fausey, & Smith, 2015; Sugden, Mohamed-Ali, & Moulson, 2014) who see both more frequent and more persistent faces (Jayaraman & Smith, 2018).
+
+Second, we found considerable variability in the social information in view depending on the activity context in which children were present.
+Even within a given, well-defined context---mealtime---we found variability across individual children.
+Intuitively, there are at least three ways to feed a young child in a kitchen (i.e., forward facing the child in a high chair, holding the child outward, or sitting side by side with them) and these regularities in a child’s life may hold a larger influence over the amount of social information in view than previously considered.
+
+Finally, we demonstrate the feasibility of using a modern, off-the-shelf computer vision model to vastly increase the efficiency of processing egocentric headcam footage, allowing us to annotate the entirety of very large datasets (here, >30 million frames) for the presence and size of people, hands, and faces, representing a 300-fold increase in data relative to prior work [@Fausey2016].
+As these detections were imperfect compared to human annotators, fine-tuning these models to better optimize for the infant viewpoint remains an open avenue for future work.
+Standard computer vision models are rarely exposed on these naturalistic, egocentric viewpoints, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors.
+
+These analyses have highlighted the importance of considering the infants field-of-view when analyzing egocentric videos.
+In many frames children's own hands were likely visible, due to the wide field of view—capturing valuable information about what these children were interacting with in different contexts across the first few years of their life.
+Furthermore, though this choice more closely approximates children’s actual perspective, these viewpoints are still a proxy as we do not know where in the frames children are allocating their attention.
+
+Indeed, the questions of how, when, from whom, and what data we sample become critically important when we attempt to construct naturalistic datasets, and we would be remiss if we did not acknowledge the limitations of the present dataset.
+While these data are longitudinal, they are only sampled from representative of few children, all growing up in relatively privileged households in western societies.
+Any idiosyncrasies in how and when these particular families chose to film these videos undoubtedly influences the variability seen here.
+Nonetheless, we believe that these advances in methodologies and datasets are a step in the right direction.
+The large-scale analysis of dense datasets—collected with different fields of view, cameras and from many different laboratories—has the potential to create generalizable conclusions about the regularities of infant experience that scaffold learning.
 

### 2020-01-24 paper/cogsci/paper.tex
cogsci paper draft with analysis integrated

--- 2020-01-11 paper/cogsci/paper.tex
@@
 
-\title{Quantifying social information in natural infant visual experience}
+\title{Detecting social information in a dense dataset of infants' natural
+visual experience}
 
@@
 \begin{abstract}
-Faces are a critical part of infants' visual experience, as they convey
-social and linguistic information.
+The faces and hands of infants' caregivers and other social partners
+offer a rich source of social and causal information that may be
+critical for infants' cognitive and linguistic development. Previous
+work using manual annotation strategies and cross-sectional data has
+found systematic changes in the proportion of faces and hands in the
+egocentric perspective of young infants. Here, we examine the prevalence
+of faces and hands in a longitudinal collection of over 1400 headcam
+videos collected from three children along a span of 6 to 32 months of
+age---the SAYcam dataset (Sullivan, Mei, Perfors, Wojcik, \& Frank,
+under review). To analyze these naturalistic infant egocentric videos,
+we first validate the use of a modern convolutional neural network for
+pose detection (OpenPose) for the detection of faces and hands. We then
+apply this model to the entire dataset, finding a decrease in the
+proportion of faces vs.~hands across age up to the end of the second
+year of life (Fausey, Jayaraman, \& Smith, 2016). In addition, we find
+considerable variability in the proportion of faces/hands viewed by
+children in different locations (e.g., living room vs.~kitchen),
+demonstrating that variability across activity contexts may be a driving
+factor in the amount of social information that infants' experience.
 
 \textbf{Keywords:}
-Add your choice of indexing terms or keywords; kindly use a semi-colon;
-between each term.
+social cognition; face perception; infancy; head cameras; deep learning
 \end{abstract}
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\newcommand{\wrapmf}[1]{#1}
 
-Previous work has suggested: - Relative changes in prevalence of faces
-vs.~hands (Fausey 2016), though perhaps this is driven by infants
-younger than 4 months of age (e.g., Jayaraman, Fausey, \& Smith, 2015;
-Sugden, Mohamed-Ali, \& Moulson, 2014) who see both more frequent and
-more persistent faces (Jayaraman \& Smith, 2018)
+\section{Introduction}\label{introduction}
 
-\begin{itemize}
-\item
-  Surprising attention to hand movements and their interactions with
-  objects (Yu \& Smith, 2013), particularly in older infants
-\item
-  Differences in the availability of social information depending on
-  motor abilities (Sanchez, Long et al., 2018 CogSci; Franchack papers)
-\end{itemize}
+Infants are confronted by a blooming, buzzing onslaught of stimuli
+({\textbf{???}}) which they must learn to parse to make sense of the
+world around them. Yet they do not embark on this learning process
+alone: From as early as 3 months of age, young infants follow overt gaze
+shifts (Gredeback, Fikke, \& Melinder, 2010), and even newborns prefer
+to look at faces with direct vs.~averted gaze (Farroni, Csibra, Simion,
+\& Johnson, 2002), despite their limited acuity. As faces are likely to
+be an important conduit of social information that scaffolds cognitive
+development, cognitive scientists have long hypothesized that faces are
+prevalent in the visual experience of young infants.
 
-One limitation of past work is that it has relied on cross-sectional
-data, and thus cannot speak to whether these trajectories are present in
-individual children.
+Yet until recently most hypotheses about infants' visual experience have
+gone untested. Though parents and scientists alike have strong
+intuitions about what infant's see, even the viewpoint of a walking
+child is not easily predicted by these intuitions (Clerkin, Hart, Rehg,
+Yu, \& Smith, 2017; Franchak et al., 2011; Yoshida \& Smith, 2008). By
+equipping infants and toddlers with head-mounted cameras, researchers
+have begun to document the infant egocentric perspective on the world.
+Using these methods, a growing body of work now demonstrates that the
+viewpoints of very young infants (less than 4 months of age) are indeed
+dominated by frequent, persistent views of the faces of their caregivers
+(Jayaraman \& Smith, 2018; Jayaraman, Fausey, \& Smith, 2015; Sugden,
+Mohamed-Ali, \& Moulson, n.d.).
 
-Here, we analyze a longitudinal corpus of head-mounted camera data,
-leveraging over XX hours of videos from XX children, totaling more than
-XX frames. \{briefly describe dataset; sampling strategy: location of
-two households, number of hours of video, variability in location, etc;
-reference published paper on what this dataset is, large field of view
-(fisheye lens))
+As infants motor and cognitive abilities mature beyond these early
+months, their perspective on the world becomes even more varied.
+Crawlers see fewer faces and hands than do walking children
+({\textbf{???}} papers; Sanchez, Long, Kraus, \& Frank, 2018) as well as
+different view of objects ({\textbf{???}}). Further, as infants learn to
+use their own hands to act on the world, they seem to focus on manual
+actions taken by their social partners, as their perspective starts to
+capture views of hands paired with the objects they are acting on
+(Fausey et al., 2016). In turn, caregivers may start to use their hands
+with more communicative intent, directing infants attention with
+pointing and gestures to different events or objects during play
+({\textbf{???}}).
 
-To do so, we first test and validate novel computer vision methods for
-extracting social information from these egocentric viewpoints on a
-small subset of randomly selected frames from the dataset. We then apply
-these methods at scale to the larger dataset, allowing us to extract key
-descriptive variables hypothesized to vary across development.
+Here, we analyze the social information present in the infant visual
+perspective by analyzing a longitudinal collection of over 1400 headcam
+videos collected from three children along a span of 6 to 32 months of
+age---the SAYcam dataset (Sullivan et al., under review). In addition to
+its size and longitudinal nature, this dataset is more naturalistic than
+those previously used in two key ways. First, recordings were taken
+under a large variety of contexts, encompassing infants' viewpoints
+during both activities outside and inside the home. Even in other
+naturalistic datasets, the incredible variety in a typical infant's
+experience has been largely underrepresented (see examples in Figure 1;
+e.g., riding in the car, gardening, watching chickens during a walk,
+browsing magazines, nursing, brushing teeth). Second, the head-mounted
+cameras used in the SAYcam dataset captured a substantially larger field
+of view than those typically used, allowing a more complete picture of
+the infant perspective. Head-mounted cameras with a more restricted
+field of view do still capture where infants are foveating most of the
+time ({\textbf{???}}, ({\textbf{???}})) but may still fail to capture
+short saccades to either faces or hands in the periphery, as the
+timescale of head movements is much longer.
 
-Part 1: How well can we capture social information using computer
-vision? - Description of OpenPose (Figure 1) - Description of annotation
-strategy (24K by Ketan, \textasciitilde{}4K on turk, reliability) -
-Describe main P/R/F statistics for 24K for faces and hands; interpret.
-Relatively higher precision vs.~recall. - P/R/F variation across
-child/age for faces - Describe possible sources of variation that
-decrease scores for: - Faces: weird viewpoints, occluded/side viewpoint,
-faces in books - Hands: children's own hands, hands in books, side
-viewpoints - Describe additional child vs.~hand annotation; P/R/F
-variation across child vs.~adult hands (better for adult hands, still OK
-for child hands)
+With hundreds of hours of footage (\textgreater{}29M frames), this large
+dataset necessitates a shift to an automated annotation strategy.
+Indeed, annotation of the frames extracted from egocentric videos has
+been prohibitively time-consuming, meaning that many frames are
+typically not inspected, even in the most comprehensive studies. For
+example, Fausey et al. (2016) collected a total of 143 hours of
+head-mounted camera footage (15.5 million frames), of which one frame
+every five seconds was hand annotated (by four coders), totalling
+103,383 frames (per coder)---an impressive number of annotations but
+nonetheless only 0.67\% of the collected footage. To address this
+challenge, we use a modern computer vision model of pose detection to
+automatically detect the presence of hands and faces from the infant
+egocentric viewpoint. Specifically, we use OpenPose (Cao, Hidalgo,
+Simon, Wei, \& Sheikh, 2018), a model optimized for jointly detecting
+human face, body, hand, and foot keypoints that operates well on scenes
+including multiple people, even if they are partially-occluded (see
+Figure 1).
 
-Part 2: Access to social information across age Prevalence of hands vs
-faces across age (in goldset, full dataset) (Figure 2) Why so many
-hands? More child hands as in gold set Cropped analysis
+In the following paper, we first describe the dataset and validate the
+use of this model by comparing face and hand detections to a
+human-annotated set of 24,000 frames. Next, we report how the proportion
+of faces and hands changes across age. We then investigate sources of
+variability in our more naturalistic dataset that may explain
+differences from prior work, including both the field-of-view of the
+present cameras as well as a diversity of locations during which videos
+were recorded.
 
-Variation across location contexts (goldset, full dataset)
+\section{Method}\label{method}
 
-\hypertarget{method}{%
-\section{Method}\label{method}}
+\subsection{Dataset}\label{dataset}
 
-If the authors' names are included in the sentence, place only the year
-in parentheses, as in (2011), but otherwise place the entire reference
-in parentheses with the authors and year separated by a comma (Fausey,
-Jayaraman, \& Smith, 2016). List multiple references alphabetically and
-separate them by semicolons (Frank, 2012; Smith, Yu, \& Pereira, 2011).
-Use the et. al.~construction only after listing all the authors to a
-publication in an earlier reference and for citations with four or more
-authors.
-
-You might want to display a wide figure across both columns. To do this,
-you change the \texttt{fig.env} chunk option to \texttt{figure*}. To
-align the image in the center of the page, set \texttt{fig.align} option
-to \texttt{center}. To format the width of your caption text, you set
-the \texttt{num.cols.cap} option to \texttt{2}.
-
-\hypertarget{one-column-images}{%
-\subsection{One-column images}\label{one-column-images}}
-
-Single column is the default option, but if you want set it explicitly,
-set \texttt{fig.env} to \texttt{figure}. Notice that the
-\texttt{num.cols} option for the caption width is set to \texttt{1}.
+The dataset is described in detail in Sullivan et al. (under review); we
+summarize these details here. Children wore Veho Muvi miniature cameras
+mounted on a custom camping headlamp harness (``headcams'') at least
+twice weekly, for approximately one hour per recording session. One
+weekly session was on the same day each week at a roughly constant time
+of day, while the other(s) were chosen arbitrarily at the participating
+family's discretion. At the time of the recording, all three children
+were in single-child households. Videos captured by the headcam were
+640x480 pixels, and a fisheye lens was attached to the camera to
+increase the field of view to approximately 109 degrees horizontal x 70
+degrees vertical. Videos{[}\^{}1{]} with technical errors or that were
+not taken from the egocentric perspective were excluded from the
+dataset. While data collection for the third child (Y) is still ongoing,
+here we analyze 1622 videos, with a total duration of 347.81225 hours
+(\textgreater{}29 million frames). {[}\^{}1{]}: All videos are available
+at \url{https://nyu.databrary.org/volume/564}
 
 \begin{CodeChunk}
-\begin{figure}[H]
+\begin{figure*}[h]
 
-{\centering \includegraphics{figs/image-1}
+{\centering \includegraphics{figs/examples-1}
 
@@
 
-\caption[One column image]{One column image.}\label{fig:image}
+\caption[Example frames taken from the dataset, illustrating variability in the infant perspective across different locations]{Example frames taken from the dataset, illustrating variability in the infant perspective across different locations.
+OpenPose detections are shown overlaid on these images.}\label{fig:examples}
+\end{figure*}
+\end{CodeChunk}
+
+\subsection{Assessing automated social
+annotations}\label{assessing-automated-social-annotations}
+
+\subsubsection{Computer vision model}\label{computer-vision-model}
+
+To automatically annotate the millions of frames in SAYcam, we use
+OpenPose (Cao et al., 2018; Simon, Joo, Matthews, \& Sheikh, 2017). This
+pose detector\footnote{\url{https://github.com/CMU-Perceptual-Computing-Lab/openpose}}
+provided the locations of 18 body parts (ears, nose, wrists, etc.). The
+system uses a convolutional neural network for initial anatomical
+detection and subsequently applies part affinity fields for part
+association, producing a series of body part candidates. The candidates
+are then matched to a single individual and finally assembled into a
+pose. Thus, while we only make use of the outputs of the face and hand
+detections, the entire set of pose information from an individual is
+used to determine the presence of a face/hand, making the process much
+more robust to occlusion than methods optimized to detect only faces or
+hands. Specifically, we tagged frames with detected nose keypoints as
+having a face, and frames with a wrist keypoint were tagged as having a
+hand.
+
+\subsubsection{Manual annotation
+strategy}\label{manual-annotation-strategy}
+
+To test the validity of OpenPose's hand and face detections, we compared
+the accuracy of these detections relative to human annotations of 24,000
+frames selected uniformly at random from videos of two children (S and
+A). Frames were jointly annotated for the presence of faces and hands. A
+second set of coders recruited via AMT (Amazon Mechanical Turk)
+additionally annotated 3150 frames; agreement with the primary coder was
+\textgreater{}95\%.
+
+\subsubsection{Detection accuracy for faces and
+hands}\label{detection-accuracy-for-faces-and-hands}
+
+As has been observed in other studies on automated annotation of headcam
+data (e.g. {\textbf{???}}, ({\textbf{???}})), detection tasks that are
+easy in third-person video can be quite challenging in egocentric
+videos, due to difficult angles and sizes as well as substantial
+occlusion. For example, the infant perspective often contains
+non-canonical viewpoints of faces (e.g., looking up at a caregiver's
+chin) as well as partially-occluded or oblique viewpoints of both faces
+and hands.
+
+To evaluate OpenPose's performance, we compared its detections to the
+manually-annotated gold set of frames, calculating precision (hits /
+hits + false alarms), recall (hits / hits + misses), and f-score (the
+harmonic mean of precision and recall). In our data, for faces, the
+F-score was 0.64, with a precision of 0.7 and recall of 0.58. For hands,
+the F-score was 0.51, with a precision of 0.73 and recall of 0.4. While
+face and hand detections showed moderately good precision, face
+detections were overall slightly more accurate than hand detections.
+Hand detections suffered from fairly low recall, indicating that
+OpenPose likely underestimated the proportion of hands in the dataset.
+We suspect that this is in part because children's own hands were often
+in view of the camera and unconnected to a pose; this factor is explored
+in detail in the following analysis section.
+
+We also examined whether the precision, recall, and F-score for hands
+and faces varied per child as a function of age to see if there was any
+bias in the OpenPose detections related to age, and did not find
+substantial variation. Nonetheless, while OpenPose was trained on
+photographs from the adult perspective, this model still generalized
+relatively well to the egocentric infant viewpoint with no fine-tuning
+or post-processing of the detections.
+
+\subsection{Access to social
+information}\label{access-to-social-information}
+
+\subsubsection{Changes across age}\label{changes-across-age}
+
+We analyzed the social information in view across the entire dataset,
+looking specifically at the proportions of faces and hands that were in
+view for each child. Data from videos were binned according to the age
+of the child (in weeks) (see Figure 2). First, when examining the
+younger age ranges (\textless{} 24 months) we saw that the proportion of
+faces in view showed a moderate decrease across this age range, both
+when analyzing the random 24K frames as well as the entire dataset (see
+Figure 2A).
+
+While these trends appear somewhat different than those observed in
+Fausey et al. (2016), note that Fausey et al. (2016) included data from
+very young infants (from 1-4 months of age), while here the youngest
+videos coming from S and A around 6 and 9 months of age, respectively.
+Similarly, our age range extends 8 months later than those infants in
+Fausey et al. (2016), throughout a portion of third year of life.
+
+\begin{CodeChunk}
+\begin{figure*}[h]
+
+{\centering \includegraphics{figs/FaceVsHands-1}
+
+}
+
+\caption[Proportion of faces vs]{Proportion of faces vs.
+hands in the entire dataset (A) and when hand detections are restricted to the upper 60 percent of the field of view (B).
+Data from each child (A, S) are plotted separately and binned by each week that the videos were filmed; data is scaled by the number of frames in that age range.}\label{fig:FaceVsHands}
+\end{figure*}
+\end{CodeChunk}
+
+However, the most striking result is a much greater proportion of hands
+in view than have previously been reported (Fausey et al., 2016). We
+found this to be true across all ages, in both children, and regardless
+of whether we analyzed human annotations (on the 24K random subset) or
+OpenPose annotations on entire dataset. This is notable especially given
+that OpenPose showed relatively low recall for hands, indicating that
+this is still an underestimate of the proportion of hands in view. One
+reason this could be the case is the much larger field of view that was
+captured by the cameras used in this study: unlike previous studies, our
+cameras were outfitted with a fish-eye lens in an attempt to capture as
+much of the children's field of view as possible. Thus, the field of
+view (FOV) of the fisheye lens used was larger (109 degrees horizontal x
+70 degrees vertical) than the FOV of the lens used in many previous
+studies; for example, in Fausey et al. (2016) the FOV was 69 x 41
+degrees. This larger field of view may have allowed the SAYcam cameras
+to capture not only the presence of a social partner's hands interacting
+with objects, but also the children's own hands, leading to more
+frequent hand detections.
+
+\begin{CodeChunk}
+\begin{figure}[h]
+
+{\centering \includegraphics{figs/density-1}
+
+}
+
+\caption[Density estimates for the child (left) and adult (right) hands that were detected int eh 24K random gold set]{Density estimates for the child (left) and adult (right) hands that were detected int eh 24K random gold set; each dot represents the center of a bounding box made by an adult participant.}\label{fig:density}
 \end{figure}
@@
 
-\hypertarget{r-plots}{%
-\subsection{R Plots}\label{r-plots}}
+To assess this possibility, we obtained human annotations for a
+subsample of 9051 frames in which a hand was detected in the random gold
+set; participants (recruited via AMT) were asked to draw bounding boxes
+around children's hands and adult's hands. Overall, we found that 34\%
+of the hands in the random 24K sample were of children's own hands
+(compared to 8\% reported in Fausey et al. (2016)) suggesting that this
+difference in field of view did contribute substantially to the higher
+rate of hand detections in the frames. Heatmaps of the bounding boxes
+obtained from these annotations can be seen in Figure 3, showing that
+children's hands tended to appear in the lower half of the frames.
 
-You can use R chunks directly to plot graphs. And you can use latex
-floats in the fig.pos chunk option to have more control over the
-location of your plot on the page. For more information on latex
-placement specifiers see
-\textbf{\href{https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions}{here}}
+We thus re-analyzed the entire dataset while restricting our analysis to
+a smaller, upper portion of the frame comparable to the field of view
+used in Fausey et al. (2016). To do so, we excluded hand detections that
+occurred in the bottom 40\% of the frame, while retaining all hand
+detections that occurred in the top 60\% of the frame. This coarse
+cropping of decreased the proportion of hand detections from
+0.3263743percent to 0.2156618 percent.
+
+With this modified field of view, we now observed a more substantive
+decrease across age in the proportions of faces relative to hands. To
+quantify this trend, we fit a generalized linear mixed model to the
+binned detection rates from this smaller field of field to estimate
+changes in the proportion of faces vs.~hands over age. To better
+approximate Fausey et al. (2016), we also restricted our analysis to the
+age range seen in Fausey et al. (2016), excluding videos when children
+were over 24 months of age, and indeed found that the proportion of
+faces vs.~hands declined modestly with age (see Table 1).
+
+However, when we considered the entire age range, we also observed an
+unexpected trend in which the relative proportion of faces vs.~hands
+increased again after 24 months of life; this trend was stronger in the
+full dataset. While we did not have any a priori hypotheses about this
+age range, we suspect that this could have to do with an increase in
+children's independence from their caregiver as they master walking
+around and interacting with objects in the world on their own.
+
+\subsubsection{Variability by Location}\label{variability-by-location}
+
+How does variability across different contexts influence the social
+information in the infant view? Intuitively, some activities in
+different contexts may be characterized by a much higher proportion of
+faces (e.g., diaper changes in bedrooms) than others (e.g., playtime in
+the living room). We thus next examined variation in presence of hands
+and faces across different locations. Of the 1622 videos, 639 were
+annotated (Sullivan et al., under review) for the location o videos were
+filmed in. 296 were filmed in single location, representing 17 percent
+of the dataset and over 5 million frames (see Sullivan et al. (under
+review)). Activities varied somewhat predictability by these contexts:
+for example, eating tended to occur in the kitchen, whereas playtime was
+the dominant activity in the living room. Overall, we found that the
+proportion of faces vs.~hands varied across filming locations, and, to
+some extent, across children. For example, while both A and S saw a
+relatively similar proportion of faces vs.~hands in the bedroom, they
+saw quite different amounts of faces vs.~hands in kitchen.
 
 \begin{CodeChunk}
-\begin{figure}[H]
+\begin{figure}[h]
 
-{\centering \includegraphics{figs/plot-1}
+{\centering \includegraphics{figs/DetByLocation-1}
 
@@
 
-\caption[R plot]{R plot}\label{fig:plot}
+\caption[Proportion of faces (A),  hands (B), and faces vs]{Proportion of faces (A),  hands (B), and faces vs.
+hands  (C) by location in which egocentric videos were filmed; data from individual children are plotted separately (location annotations were not available for Y).
+Data are only taken from the top 60 percent of the frames so as to minimize the contribution of children’s own hands.
+Each dot represents data from a week in which videos were filmed and are scaled by the number of frames (i.e., amount of video) in that datapoint.}\label{fig:DetByLocation}
 \end{figure}
@@
 
-\hypertarget{tables}{%
-\subsection{Tables}\label{tables}}
+\section{General Discussion}\label{general-discussion}
 
-You can use the xtable function in the xtable package.
+Broadly, the present analysis of this dense, longitudinal dataset has
+yielded a better understanding of infants' evolving access to social
+information. First, we found a relatively high proportion of faces in
+view in the videos from the youngest age ranges in each child,
+confirming previous findings (Fausey et al., 2016). This is particularly
+notable given that, in cross-sectional data, this effect seems to be
+most strongly driven by infants younger than 4 months of age (e.g.,
+Fausey 2016; Jayaraman, Fausey, \& Smith, 2015; Sugden, Mohamed-Ali, \&
+Moulson, 2014) who see both more frequent and more persistent faces
+(Jayaraman \& Smith, 2018).
 
-\begin{table}[H]
-\centering
-\begin{tabular}{rrrrr}
-  \hline
- & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
-  \hline
-(Intercept) & 0.00 & 0.10 & 0.0 & 0.98 \\ 
-  x & 1.90 & 0.09 & 20.1 & 0.00 \\ 
-   \hline
-\end{tabular}
-\caption{This table prints across one column.} 
-\end{table}
+Second, we found considerable variability in the social information in
+view depending on the activity context in which children were present.
+Even within a given, well-defined context---mealtime---we found
+variability across individual children. Intuitively, there are at least
+three ways to feed a young child in a kitchen (i.e., forward facing the
+child in a high chair, holding the child outward, or sitting side by
+side with them) and these regularities in a child's life may hold a
+larger influence over the amount of social information in view than
+previously considered.
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+Finally, we demonstrate the feasibility of using a modern, off-the-shelf
+computer vision model to vastly increase the efficiency of processing
+egocentric headcam footage, allowing us to annotate the entirety of very
+large datasets (here, \textgreater{}30 million frames) for the presence
+and size of people, hands, and faces, representing a 300-fold increase
+in data relative to prior work (Fausey et al., 2016). As these
+detections were imperfect compared to human annotators, fine-tuning
+these models to better optimize for the infant viewpoint remains an open
+avenue for future work. Standard computer vision models are rarely
+exposed on these naturalistic, egocentric viewpoints, and we suspect
+that training these models on more naturalistic data may lead to more
+robust, generalizable detectors.
 
-Fausey 2016: 103,383 images; Here: 30,000,000 frames; 300 fold increase
-in data
+These analyses have highlighted the importance of considering the
+infants field-of-view when analyzing egocentric videos. In many frames
+children's own hands were likely visible, due to the wide field of
+view---capturing valuable information about what these children were
+interacting with in different contexts across the first few years of
+their life. Furthermore, though this choice more closely approximates
+children's actual perspective, these viewpoints are still a proxy as we
+do not know where in the frames children are allocating their attention.
 
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
+Indeed, the questions of how, when, from whom, and what data we sample
+become critically important when we attempt to construct naturalistic
+datasets, and we would be remiss if we did not acknowledge the
+limitations of the present dataset. While these data are longitudinal,
+they are only sampled from representative of few children, all growing
+up in relatively privileged households in western societies. Any
+idiosyncrasies in how and when these particular families chose to film
+these videos undoubtedly influences the variability seen here.
+Nonetheless, we believe that these advances in methodologies and
+datasets are a step in the right direction. The large-scale analysis of
+dense datasets---collected with different fields of view, cameras and
+from many different laboratories---has the potential to create
+generalizable conclusions about the regularities of infant experience
+that scaffold learning.
+
+\section{Acknowledgements}\label{acknowledgements}
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\section{References}\label{references}
 
-\setlength{\parindent}{-0.1in} 
-\setlength{\leftskip}{0.125in}
-
-\noindent
+\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent
 
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-Fausey2016}{}%
+\hypertarget{ref-Cao2018openpose}{}
+Cao, Z., Hidalgo, G., Simon, T., Wei, S.-E., \& Sheikh, Y. (2018).
+OpenPose: Realtime multi-person 2D pose estimation using Part Affinity
+Fields. In \emph{ArXiv preprint arXiv:1812.08008}.
+
+\hypertarget{ref-Farroni2002}{}
+Farroni, T., Csibra, G., Simion, F., \& Johnson, M. H. (2002). Eye
+contact detection in humans from birth. \emph{Proceedings of the
+National Academy of Sciences}, \emph{99}(14), 9602--9605.
+
+\hypertarget{ref-Fausey2016}{}
 Fausey, C. M., Jayaraman, S., \& Smith, L. B. (2016). From faces to
@@
 
-\leavevmode\hypertarget{ref-Franchak2011}{}%
-Franchak, J. M., Kretch, K. S., Soska, K. C., \& Adolph, K. E. (2011).
-Head-mounted eye- tracking: A new method to describe infant looking.
-\emph{Child Development}, \emph{82}(6), 1738--1750.
+\hypertarget{ref-Gredeback2010}{}
+Gredeback, G., Fikke, L., \& Melinder, A. (2010). The development of
+joint visual attention: A longitudinal study of gaze following during
+interactions with mothers and strangers. \emph{Developmental Science},
+\emph{13}(6), 839--848.
 
-\leavevmode\hypertarget{ref-Frank2012}{}%
-Frank, M. C. (2012). Measuring children's visual access to social
-information using face detection. In \emph{Proceedings of the nth annual
-conference of the cognitive science society} (pp. XXX--XXX). Hillsdale,
-NJ: Cognitive Science Society.
+\hypertarget{ref-Jayaraman2018}{}
+Jayaraman, S., \& Smith, L. B. (2018). Faces in early visual
+environments are persistent not just frequent. \emph{Vision Research}.
 
-\leavevmode\hypertarget{ref-Smith2011}{}%
-Smith, L. B., Yu, C., \& Pereira, A. (2011). Not your mother's view: The
-dynamics of toddler visual experience. \emph{Developmental Science},
-\emph{14}(1), 9--17.
+\hypertarget{ref-Jayaraman2015}{}
+Jayaraman, S., Fausey, C. M., \& Smith, L. B. (2015). The faces in
+infant-perspective scenes change over the first year of life. \emph{PLoS
+One}. \url{http://doi.org/10.1371/journal.pone.0123780}
+
+\hypertarget{ref-Sanchez2018}{}
+Sanchez, A., Long, B., Kraus, A. M., \& Frank, M. C. (2018). Postural
+developments modulate children's visual access to social information. In
+\emph{Proceedings of the 40th annual conference of the cognitive science
+society}.
+
+\hypertarget{ref-Simon2017hand}{}
+Simon, T., Joo, H., Matthews, I., \& Sheikh, Y. (2017). Hand keypoint
+detection in single images using multiview bootstrapping. In
+\emph{CVPR}.
+
+\hypertarget{ref-Sugden2014}{}
+Sugden, N. A., Mohamed-Ali, M. I., \& Moulson, M. C. (n.d.). I spy with
+my little eye: Typical, daily exposure to faces documented from a
+first-person infant perspective. \emph{Developmental Psychobiology},
+\emph{56}(2), 249--261.
+
+\hypertarget{ref-SAYcam}{}
+Sullivan, J., Mei, M., Perfors, A., Wojcik, E., \& Frank, M. (under
+review). Head cameras on children aged 6 months through 31 months.
 

### 2020-01-24 paper/cogsci/paper.Rmd
fix references

@@
 # Introduction
-Infants are confronted by a blooming, buzzing onslaught of stimuli [@James1981] which they must learn to parse to make sense of the world around them.
-Yet they do not embark on this learning process alone: From as early as 3 months of age, young infants follow overt gaze shifts [@Gredeback2010], and even newborns prefer to look at faces with direct vs.
+Infants are confronted by a blooming, buzzing onslaught of stimuli [@james1890principles] which they must learn to parse to make sense of the world around them.
+Yet they do not embark on this learning process alone: From as early as 3 months of age, young infants follow overt gaze shifts [@gredeback2008microstructure], and even newborns prefer to look at faces with direct vs.
 averted gaze [@Farroni2002], despite their limited acuity.
@@
 Yet until recently most hypotheses about infants’ visual experience have gone untested.
-Though parents and scientists alike have strong intuitions about what infant’s see, even the viewpoint of a walking child is not easily predicted by these intuitions (Clerkin, Hart, Rehg, Yu, & Smith, 2017; Franchak et al., 2011; Yoshida & Smith, 2008).
+Though parents and scientists alike have strong intuitions about what infant’s see, even the viewpoint of a walking child is not easily predicted by these intuitions [@clerkin2017; @franchak2011].
 By equipping infants and toddlers with head-mounted cameras, researchers have begun to document the infant egocentric perspective on the world.
@@
 As infants motor and cognitive abilities mature beyond these early months, their perspective on the world becomes even more varied.
-Crawlers see fewer faces and hands than do walking children [@Sanchez2018; @Franchak papers] as well as different view of objects [@Soska2010].
+Crawlers see fewer faces and hands than do walking children [@Sanchez2018; @franchak2017see; @kretch2014] as well as different view of objects [@smith2011not].
 Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, as their perspective starts to capture views of hands paired with the objects they are acting on [@Fausey2016].
-In turn, caregivers may start to use their hands with more communicative intent, directing infants attention with pointing and gestures to different events or objects during play [@YuSmith2013].
+In turn, caregivers may start to use their hands with more communicative intent, directing infants attention with pointing and gestures to different events or objects during play [@yu2013joint].
 
@@
 Second, the head-mounted cameras used in the SAYcam dataset captured a substantially larger field of view than those typically used, allowing a more complete picture of the infant perspective.
-Head-mounted cameras with a more restricted field of view do still capture where infants are foveating most of the time [@YoshidaSmith2008, @SmithFausey-Review] but may still fail to capture short saccades to either faces or hands in the periphery, as the timescale of head movements is much longer.
+Head-mounted cameras with a more restricted field of view do still capture where infants are foveating most of the time [@yoshida2008, @smith2015contributions] but may still fail to capture short saccades to either faces or hands in the periphery, as the timescale of head movements is much longer.
 
@@
 As has been observed in other studies on automated annotation of headcam data [e.g.
-@frank2013, @REF-chenyu-hand-paper], detection tasks that are easy in third-person video can be quite challenging in egocentric videos, due to difficult angles and sizes as well as substantial occlusion.
+@frank2013, @sanchez2018postural, @bambach2015lending], detection tasks that are easy in third-person video can be quite challenging in egocentric videos, due to difficult angles and sizes as well as substantial occlusion.
 For example, the infant perspective often contains non-canonical viewpoints of faces (e.g., looking up at a caregiver's chin) as well as partially-occluded or oblique viewpoints of both faces and hands.
@@
 
-```{r FaceVsHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces vs.
-hands in the entire dataset (A) and when hand detections are restricted to the upper 60 percent of the field of view (B).
-Data from each child (A, S) are plotted separately and binned by each week that the videos were filmed; data is scaled by the number of frames in that age range."}
+```{r FaceVsHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces (A), hands (B), and faces vs.
+hands (C) in the entire dataset and (D).
+when hand detections are restricted to the upper 60 percent of the field of view (B).
+Data from each child are plotted separately and binned by each week that the videos were filmed; data pointsscaled by the number of frames in that age range."}
 

### 2020-01-24 paper/cogsci/paper.Rmd
most recent versions of markdown and pdf for cogsci paper

@@
 
+```{r eval=FALSE}
+summary_by_age_days_cropped_limited <- d_cropped %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+  group_by(age_day_bin,child_id) %>%
+  filter(age_day_bin < (24))  %>%
+  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected_cropped)) %>%
+  rename(age_months = age_day_bin)
+
+summary_by_age_days_cropped <- d_cropped %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+  group_by(age_day_bin,child_id) %>%
+  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected_cropped)) %>%
+  rename(age_months = age_day_bin)
+
+```
+
+```{r eval=FALSE}
+### Proportion faces vs. hands 
+face_vs_hands_model_limited <- glmer(cbind(num_faces,num_hands) ~ scale(age_months) + (1 | child_id), 
+             summary_by_age_days_cropped_limited, family = "binomial")
+# doesn't converge with random slopes for age | child_id
+face_vs_hands_model_limited_out = summary(face_vs_hands_model_limited)
+
+```
+
+```{r eval=FALSE}
+### Proportion faces vs. hands 
+face_vs_hands_model_full_age <- glmer(cbind(num_faces,num_hands) ~ scale(age_months) + (1 | child_id), 
+             summary_by_age_days_cropped, family = "binomial")
+# doesn't converge with random slopes for age | child_id
+face_vs_hands_model_full_age_out <- summary(face_vs_hands_model_full_age)
+
+# xtable(face_vs_hands_model_full_age_out$coefficients, digits=c(2,2,2,2,3),"Model coefficients from a generalized linear mixed model predicting the proportion of faces vs. hands seen by infants.") 
+```
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrrr}
+  \hline
+ & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
+  \hline
+(Intercept) & -0.26 & 0.09 & -2.83 & 0.005 \\ 
+  scale(age\_months) & -0.15 & 0.00 & -225.40 & 0.000 \\ 
+   \hline
+\end{tabular}
+\caption{Model coefficients from a generalized linear mixed model predicting the proportion of faces vs. hands seen by infants.} 
+\end{table}
+
 However, when we considered the entire age range, we also observed an unexpected trend in which the relative proportion of faces vs.
@@
 #
+
 # d_by_location_cropped$Location = droplevels(d_by_location_cropped$Location)

### 2020-01-28 analysis/preprocess_datasets.Rmd
fix merging datasets bug in preprocessing pipelined

@@
 ```{r}
-metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"
-
-meta=read.csv(metadata_file) %>%
-  rowwise() %>%
-  mutate(vid_name = str_split(File.Name,"[.]")[[1]][1]) %>%
-  mutate(count_locations = length(str_split(Location,',')[[1]]))
-
-# collapse duplicate labels
-meta$Location[meta$Location=='Bedroom Alice/Sam'] = 'Bedroom'
-
-save(meta, file = '../data/saycam_metadata.RData')
-
+# metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"
+# meta=read.csv(metadata_file) %>%
+#   rowwise() %>%
+#   mutate(vid_name = str_split(File.Name,"[.]")[[1]][1]) %>%
+#   mutate(count_locations = length(str_split(Location,',')[[1]]))
+# 
+# # collapse duplicate labels
+# meta$Location[meta$Location=='Bedroom Alice/Sam'] = 'Bedroom'
+# save(meta, file = '../data/saycam_metadata.RData')
+load(file = '../data/saycam_metadata.RData')
 ```
@@
 ### Load in detections & bounding boxes from preprocessed Rdata file; 
-```{r eval=FALSE}
+```{r}
  # Could do list of detections  from csv (takes forever, skipping)
@@
 load('../data/openpose_detections.RData')
-
 ```
@@
 ### Preprocess data (doesn't execute in markdown; loads processed data below)
-```{r eval=FALSE}
+```{r}
 # get shortened video names so they match across all files
@@
 ```{r}
-load('../data/Y_bounding_boxes.RData') #df again
-y_data <- df %>%
-  rowwise() %>%
-  mutate(age = str_split_fixed(vid_name, '_',4)[,3])
-
-remove(df)
-
-### wrangle age data for Y
+# load('../data/Y_bounding_boxes.RData') #df again
+# y_data <- df %>%
+#   rowwise() %>%
+#   mutate(age = str_split_fixed(vid_name, '_',4)[,3])
+# remove(df)
+# 
+# ### wrangle age data for Y
 d_y <- y_data %>%
@@
   mutate(age_days = age_months*30 + days_to_add)
-
-save(y_data, file = '../data/Y_bounding_boxes_cleaned.RData')
+## 
+save(d_y, file = '../data/Y_bounding_boxes_cleaned_jan27.RData')
 ```
@@
 ```{r}
-
 ### count hands/faces from bounding box outputs for Y -- for d_all
-y_detections <- d_y %>%
-  group_by(vid_name, frame,age_days) %>%
-  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0))
-
-y_detections <- y_detections %>%
-  # rename(hand_openpose = hand_detected, face_openpose = face_detected) %>%
-  mutate(child_id = "Y") %>%
-  left_join(meta)
-
-save(y_detections, file='../data/y_detections_preprocessed.RData')
+# y_detections <- d_y %>%
+#   group_by(vid_name, frame,age_days) %>%
+#   summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0))
+# 
+# y_detections <- y_detections %>%
+#   mutate(child_id = "Y") %>%
+#   left_join(meta)
+#   
+# save(y_detections, file='../data/y_detections_preprocessed.RData')
 ```
@@
 ```{r}
+load(file='../data/y_detections_preprocessed.RData')
+y_detections <-  y_detections %>%
+  rename(hand_openpose = hand_detected, face_openpose = face_detected) # standardize
+
 d_all <- d_SA %>%
@@
   full_join(y_detections)
+
+# check
+length(unique(d_all$vid_name)) == (length(unique(y_detections$vid_name)) +  length(unique(d_SA$vid_name)))
+
+# clean up
+remove(d_SA)
+remove(d_y)
+
+# save
+save(d_all, file = '../data/openpose_detections_filtered_threekids_jan27.RData')
 ```
 
-### Save this data so this doesn't have to be redone again
-```{r}
-save(d_all, file = '../data/openpose_detections_filtered_threekids.RData')
-```
 ## Save out vid info for use with joining stuff later
@@
 load('../data/all_bounding_boxes.RData')
+bb_all <- df
+remove(df)
 
@@
 
-bb_all <- df %>%
-  filter(right_side_up==0)
+# get shortened video names so they match across all files
+all_video_names_bb = as_tibble(unique(bb_all$vid_name))
+all_video_names_bb <- all_video_names_bb %>%
+  rowwise() %>%
+  mutate(vid_name = str_split(value,"[.]")[[1]][1])
 
-## get rid of extra dataframe
-remove(df)
+# reset levels of vid_name in big detections array for detections & bb (very slow rowwise)
+bb_all$vid_name <- as.factor(bb_all$vid_name)
+levels(bb_all$vid_name) <- all_video_names_bb$vid_name
+
+bb_all <- bb_all %>%
+  filter(!vid_name %in% flipped_videos$video)
+
+save(bb_all, file = "../data/SA_bounding_boxes_cleaned.RData")
+
+# length(unique(bb_all_2$vid_name[bb_all_2$child_id=='S']))
+# length(unique(bb_all_2$vid_name[bb_all_2$child_id=='A']))
+# 
+# length(unique(d_all$vid_name[d_all$child_id=='S']))
+# length(unique(d_all$vid_name[d_all$child_id=='A']))
 ```
 
-## Make cropped detections in top 60% of frame for Y
+## Join detections for both and save out for later
 ```{r}
-load(file = '../data/Y_bounding_boxes_cleaned.RData')
-d_y <- y_data %>%
-  mutate(age_months = as.numeric(substr(age, 0,2)), days_to_add = as.numeric(substr(age, 3,4))) %>%
-  mutate(age_days = age_months*30 + days_to_add)
+# load(file = '../data/Y_bounding_boxes_cleaned.RData') #  d_y from earlier if not loaded
 
+## frame
+# height_px = 480; width_px = 640
+# bb_all_three <- d_y %>%
+#   filter(person==0) %>% # only rows with detections for now so comparable to bb_all
+#   mutate(left = left*width_px, top = top*height_px, height = height*height_px, width = width*width_px) %>% #unnormalize data so comparable
+#   full_join(bb_all) %>% # join with SA bounding boxes
+#   mutate(center_x = left + width/2, center_y = top - height/2, area = width*height) 
+# 
+# save(bb_all_three, file = '../data/all_bounding_boxes_three_kids_preprocessed.RData')
+# remove(bb_all_three)
+```
+
+```{r}
+load(file='../data/openpose_detections_filtered_threekids_jan27.RData')
+load(file='../data/SA_bounding_boxes_cleaned.RData')
+load(file='../Y_bounding_boxes_cleaned_jan27.RData')
+```
+
+### Make cropped detections for Y/SA, join, make cropped large data
+```{r}
 detections_cropped_Y <- d_y %>%
-  filter(person==0) %>% #only get frames where detections
-  filter(height <(.6*480)) %>%  ## cut off bottom part of frame
+  filter(person==0) %>% #only get frames where detections so comparable
+  filter((height<(.6*480))) %>%  ## 
   group_by(vid_name, frame, child_id, age_days) %>%
-  summarize(hand_detected_cropped = (sum(label=="hand")>0), face_detected_cropped = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))
+  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))
 
@@
 
-```
-
 ## Make cropped detections in top 60% of frame for S,A
-```{R}
 detections_cropped_SA <- bb_all %>%
-  filter(height <.6) %>%  ## cut off bottom part of frame
+  filter(height<(.6)) %>%  ## 
   group_by(vid_name, frame, child_id, age_days) %>%
-  summarize(hand_detected_cropped = (sum(label=="hand")>0), face_detected_cropped = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))
-
+  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))  
+# join all together
 all_cropped_detections <- detections_cropped_SA %>%
@@
 
-```
+## clean up workspace or else we run into memory limits
+# cropped detections
+remove(detections_cropped_Y)
+remove(detections_cropped_SA)
+
+# bb data
+remove(y_data)
+remove(bb_all)
 
 ## need to get "FALSE" on frames where we didn't have info to be able to compute proportions; uses d_all from earlier and fills it all back in
-```{r}
-# load('../data/openpose_detections_filtered_threekids.RData') # d_all
 
-d_cropped <- d_all %>% ## needs to be loaded
+all_cropped_detections <- all_cropped_detections %>%
+  select(-age_days, -child_id)
+
+d_cropped <- d_all %>% ## needs to be loaded!
   as_tibble() %>%
   mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id)) %>%
-  select(vid_name, frame, child_id, age_days, face_openpose) %>%
-  left_join(all_cropped_detections, by=c("vid_name","frame","age_days","child_id")) %>%
-  replace_na(list(hand_detected_cropped = FALSE, face_detected_cropped = FALSE ))
-```
+  select(vid_name, frame, child_id, age_days, face_openpose, hand_openpose) %>%
+  left_join(all_cropped_detections, by=c("vid_name","frame"))
 
-### now save
-```{r}
-save(d_cropped, file = '../data/openpose_detections_filtered_cropped_allthreekids.RData')
-
-```
-
-# Make bb detections only
-```{r}
-## import bounding boxes
-load('../data/all_bounding_boxes.RData')
-load('../data/Y_bounding_boxes_cleaned.RData')
-
-right_side_up_file = "../data/video_right-side-up.csv"
-right_side_up =read.csv(right_side_up_file)
-
-# get INCORRECT videos 
-flipped_videos <- right_side_up %>%
-  filter(right_side_up==1) %>%
-  rename(vid_name = video)
+save(d_cropped, file = '../data/openpose_detections_filtered_cropped_allthreekids_jan27.RData')
 
@@
 ```{r}
-## frame
-height_px = 480; width_px = 640
-bb_all <- y_data %>%
-  filter(person==0) %>% # only rows with detections for now
-  filter(!is.na(child_id)) %>%
-  mutate(left = left*width_px, top = top*height_px, height = height*height_px, width = width*width_px) %>% #unnormalize data...
-  full_join(df) %>% # join with S/A
-  filter(right_side_up==0) %>% # get rid of allocentric
-  mutate(center_x = left + width/2, center_y = top - height/2, area = width*height)
+what <- d_cropped %>%
+  filter(face_openpose == TRUE) %>%
+  filter(fa)
 
-save(bb_all, file = '../data/all_bounding_boxes_three_kids_preprocessed.RData')
+vid_summary <- d_cropped %>%
+  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
+  group_by(vid_name) %>%
+  summarize(prop_faces = mean(face_openpose), prop_faces_cropped = mean(face_detected), prop_hands_cropped = mean(hand_detected), diff = prop_faces - prop_faces_cropped) %>%
+  filter(diff>.2)
 
+weird_vids = unique(vid_summary$vid_name[vid_summary$prop_hands_cropped==0])
+
+weird_d_all <- d_all %>%
+  filter(vid_name %in% weird_vids)
+
+bb_all_check <- bb_all %>%
+  filter(vid_name %in% weird_vids)
 ```
-
-```

### 2020-01-28 src/config.py

@@ -7,20 +7,20 @@ from default_config import *
 # VIDEO_DIRS = ['/scratch/groups/mcfrank/Home_Headcam_new/']
 
 #Overall output directory.
-# OUTPUT = '/scratch/users/agrawalk/headcam-algo-output/'
+OUTPUT = '/Users/brialong/Documents/GitHub/headcam-algo/data'
 
 #Directory for raw Openpose output (warning: need inode space for millions of small JSON files)
-# OPENPOSE_OUTPUT = os.path.join(OUTPUT, 'openpose')
+OPENPOSE_OUTPUT = os.path.join(OUTPUT, 'openpose')
 
 #Directory for condensed Openpose output (one file per video) 
-# OPENPOSE_CONDENSED_OUTPUT = os.path.join(OUTPUT, 'openpose_condensed')
+OPENPOSE_CONDENSED_OUTPUT = os.path.join(OUTPUT, 'openpose_condensed')
 
 #File path for the video-level dataframe.
-# VID_DATAFRAME_PATH = os.path.join(OUTPUT, 'master_vid_info.json')
+VID_DATAFRAME_PATH = os.path.join(OUTPUT, 'master_vid_info.json')
 
 #FIle path for the frame-level dataframe 
 #(which will contain openpose outputs as well.)
-# FRAME_DATAFRAME_PATH = os.path.join(OUTPUT, 'master_frames_openpose.h5')
+FRAME_DATAFRAME_PATH = os.path.join(OUTPUT, 'master_frames_openpose.h5')
 
 #How much to rotate videos by (default 180, as most headcam videos are recorded upside down)
 # VID_ROTATE = 180

### 2020-01-28 src/default_config.py

@@ -4,7 +4,10 @@ import os
 VIDEO_DIRS = ['/scratch/groups/mcfrank/Home_Headcam_new/']
 
 #Overall output directory.
-OUTPUT = '/scratch/users/agrawalk/headcam-algo-output/'
+OUTPUT = '/Users/brialong/Documents/GitHub/headcam-algo/data'
+
+
+# OUTPUT = '/scratch/users/agrawalk/headcam-algo-output/'
 
 #Directory for raw Openpose output (warning: need inode space for millions of small JSON files)
 OPENPOSE_OUTPUT = os.path.join(OUTPUT, 'openpose')
@@ -27,7 +30,7 @@ VID_ROTATE = 180
 
 #Dict from child id => birthdate in (year, month, day) format.
 #NOTE: Actual birthdates not included for privacy reasons.
-BIRTHDATES = {'A': (YYYY, MM, DD), 'S': (YYYY, MM, DD)}
+BIRTHDATES = {'A': (1980, 1, 1), 'S': (1980, 1, 1)}
 
 #Number of frames to extract for gold sample.
 GOLD_SET_NUM_FRAMES = 24000

### 2020-01-28 paper/cogsci/paper_jan28.Rmd
add latest version of cogsci paper

--- 2020-01-24 paper/cogsci/paper.Rmd
@@
 
-As infants motor and cognitive abilities mature beyond these early months, their perspective on the world becomes even more varied.
-Crawlers see fewer faces and hands than do walking children [@Sanchez2018; @franchak2017see; @kretch2014] as well as different view of objects [@smith2011not].
-Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, as their perspective starts to capture views of hands paired with the objects they are acting on [@Fausey2016].
-In turn, caregivers may start to use their hands with more communicative intent, directing infants attention with pointing and gestures to different events or objects during play [@yu2013joint].
+Beyond these early months,infants motor and cognitive abilities mature, leading to a vastly different perspectives on the world.
+For example, crawlers see fewer faces and hands than do walking children [@Sanchez2018; @franchak2017see; @kretch2014] as well as different view of objects [@smith2011not].
+Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, and their perspective starts to capture views of hands paired with the objects they are acting on [@Fausey2016].
+In turn, caregivers may also start to use their hands with more communicative intent, directing infants attention by pointing and gesturing to different events and objects during play [@yu2013joint].
 
-Here, we analyze the social information present in the infant visual perspective by analyzing a longitudinal collection of over 1400 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam].
+Here, we examine the social information present in the infant visual perspective--the presence of faces and hands--by analyzing a longitudinal collection of over 1400 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam].
 In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways.
-First, recordings were taken under a large variety of contexts, encompassing infants’ viewpoints during both activities outside and inside the home.
+First, recordings were taken under a large variety of activity contexts [@roy2015predicting; @bruner1985role] encompassing infants’ viewpoints during both activities outside and inside the home.
 Even in other naturalistic datasets, the incredible variety in a typical infant’s experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth).
-Second, the head-mounted cameras used in the SAYcam dataset captured a substantially larger field of view than those typically used, allowing a more complete picture of the infant perspective.
-Head-mounted cameras with a more restricted field of view do still capture where infants are foveating most of the time [@yoshida2008, @smith2015contributions] but may still fail to capture short saccades to either faces or hands in the periphery, as the timescale of head movements is much longer.
+Second, the head-mounted cameras used in the SAYcam dataset captured a larger field of view than those typically used, allowing a more complete picture of the infant perspective.
+While head-mounted cameras with a more restricted field of view do  represent where infants are foveating most of the time [@yoshida2008, @smith2015contributions], they may fail to capture short saccades to either faces or hands in the periphery, as the timescale of head movements is much longer.
 
-With hundreds of hours of footage (>29M frames), this large dataset necessitates a shift to an automated annotation strategy.
+With hundreds of hours of footage (>29M frames), however, this large dataset necessitates a shift to an automated annotation strategy.
 Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that many frames are typically not inspected, even in the most comprehensive studies.
@@
 In the following paper, we first describe the dataset and validate the use of this model by comparing face and hand detections to a human-annotated set of 24,000 frames.
-Next, we report how the proportion of faces and hands changes across age.
+Next, we report how the proportion of faces and hands changes across age in each of the three children in the dataset.
 We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the present cameras as well as a diversity of locations during which videos were recorded.
@@
 load('../../data/openpose_detections_filtered_threekids.RData') #d_all
-load('../../data/openpose_detections_filtered_cropped_allthreekids.RData') # d_cropped
+load('../../data/openpose_detections_filtered_cropped_allthreekids_jan28.RData') # d_cropped
 ```
@@
 bins = c(bin_starts, max_age)
-```
-
-```{r}
-## Make summary stats for cropped and uncropped detedctions
-summary_by_age <- d_all %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
-  group_by(age_day_bin, child_id) %>%
-  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect)
-
-summary_by_age_cropped <- d_cropped %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
-  group_by(age_day_bin,child_id) %>%
-  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_detected_cropped) / num_detect) 
 ```
@@
  gold_sample <- ketan_gold_out %>%
+  select(-vid_name) %>%
+  rename(vid_name = vid_name_short) %>% 
+  mutate(vid_name = as.factor(vid_name)) %>%
   mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose))
@@
  hand_performance = return_prf_short(gold_sample$hand_eval_ketan)
-
-```
-As has been observed in other studies on automated annotation of headcam data [e.g.
-@frank2013, @sanchez2018postural, @bambach2015lending], detection tasks that are easy in third-person video can be quite challenging in egocentric videos, due to difficult angles and sizes as well as substantial occlusion.
-For example, the infant perspective often contains non-canonical viewpoints of faces (e.g., looking up at a caregiver's chin) as well as partially-occluded or oblique viewpoints of both faces and hands.
-
-To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / hits + false alarms), recall (hits / hits + misses), and f-score (the harmonic mean of precision and recall).
-In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`.
-For hands, the F-score was `r round(hand_performance[3],2)`, with a precision of `r round(hand_performance[1],2)` and recall of `r round(hand_performance[2],2)`.
-While face and hand detections showed moderately good precision, face detections were overall slightly more accurate than hand detections.
-Hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.
-We suspect that this is in part because children’s own hands were often in view of the camera and unconnected to a pose; this factor is explored in detail in the following analysis section.
-
-We also examined whether the precision, recall, and F-score for hands and faces varied per child as a function of age to see if there was any bias in the OpenPose detections related to age, and did not find substantial variation.
-Nonetheless, while OpenPose was trained on photographs from the adult perspective, this model still generalized relatively well to the egocentric infant viewpoint with no fine-tuning or post-processing of the detections.
-
-## Access to social information 
-### Changes across age
-
-We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands that were in view for each child.
-Data from videos were binned according to the age of the child (in weeks) (see Figure 2).
-First, when examining the younger age ranges (< 24 months) we saw that the proportion of faces in view showed a moderate decrease across this age range, both when analyzing the random 24K frames as well as the entire dataset (see Figure 2A).
-
-While these trends appear somewhat different than those observed in @Fausey2016, note that @Fausey2016 included data from very young infants (from 1-4 months of age), while here the youngest videos coming from S and A around 6 and 9 months of age, respectively.
-Similarly, our age range extends 8 months later than those infants in @Fausey2016, throughout a portion of third year of life.
-
-```{r FaceVsHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces (A), hands (B), and faces vs.
-hands (C) in the entire dataset and (D).
-when hand detections are restricted to the upper 60 percent of the field of view (B).
-Data from each child are plotted separately and binned by each week that the videos were filmed; data pointsscaled by the number of frames in that age range."}
-
-faces <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
-  geom_point(alpha=.2) +
-  geom_smooth(span=10) + 
-  ylab('Proportion Faces') + 
-  # theme_few(base_size=16) +
-  xlab('Age (months)') +
-  ylim(0,.5) +
-  theme(legend.position="none") +
-  ggtitle('(A).') +
-  scale_colour_brewer(palette = "Dark2")
-
-hands <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
-  geom_point(alpha=.2) +
-  geom_smooth(span=10) + 
-  # theme_few(base_size=16) +
-  ylab('Proportion Hands') + 
-  xlab('Age (months)') +
-  ylim(0,.5)+
-  theme(legend.position="none") +
-  ggtitle('(B).') +
-  scale_colour_brewer(palette = "Dark2")
-
-face_v_hand <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
-  geom_point(alpha=.2) +
-  geom_smooth(span=10) + 
-  # theme_few(base_size=16) +
-  ylab('Proportion Faces - Hands') + 
-  xlab('Age (months)') +
-  ylim(-.3, .3) +
-  theme(legend.position = "none") +
-  ggtitle('(C).') +
-  scale_colour_brewer(palette = "Dark2")
-
-face_v_hand_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
-  geom_point(alpha=.2) +
-  geom_smooth(span=10) + 
-  # theme_few(base_size=16) +
-  ylab('Proportion Faces - Hands') + 
-  xlab('Age (months)') +
-  ylim(-.3, .3) +
-  theme(legend.position = "none") +
-  ggtitle('(D).')  +
-  scale_colour_brewer(palette = "Dark2")
-
-ggarrange(faces, hands, face_v_hand, face_v_hand_cropped, nrow=1)
 ```
 
-However, the most striking result is a much greater proportion of hands in view than have previously been reported [@Fausey2016].
-We found this to be true across all ages, in both children, and regardless of whether we analyzed human annotations (on the 24K random subset) or OpenPose annotations on entire dataset.
-This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this is still an underestimate of the proportion of hands in view.
-One reason this could be the case is the much larger field of view that was captured by the cameras used in this study: unlike previous studies, our cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible.
-Thus, the field of view (FOV) of the fisheye lens used was larger (109 degrees horizontal x 70 degrees vertical) than the FOV of the lens used in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees.
-This larger field of view may have allowed the SAYcam cameras to capture not only the presence of a social partner’s hands interacting with objects, but also the children’s own hands, leading to more frequent hand detections.
-
 ```{r} 
+### Load turk hand annotations wtih all bounding boxes (multiple dets per frame)
 turk_annotations_seg = "../../data/turk_segmentations_hands_only_processed.csv" 
@@
   filter(label=="Adult hand")
+```
 
+```{r eval=FALSE}
+hands_missed <- gold_sample %>%
+  select(-vid_name) %>%
+  rename(vid_name = vid_name_short) %>% 
+  mutate(vid_name = as.factor(vid_name)) %>%
+  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
+  filter(!is.na(full_image_path)) %>%
+  filter(hand_eval_ketan == 'FN')
+
+# render examples of missed hands
+# dir.create(paste0('det_examples/missed_hand'), recursive=TRUE)
+# for (i in seq(1,length(hands_missed$full_image_path),1)){
+#   image_read(as.character(hands_missed$full_image_path[i])) %>%
+#     image_append(stack = FALSE) %>%
+#     image_write(file.path(paste0("det_examples/missed_hand/", hands_missed$vid_name[i],hands_missed$frame[i],'.jpg')))
+# }
+
+```
+
+```{r}
 ##
@@
 
-To assess this possibility, we obtained human annotations for a subsample of 9051 frames in which a hand was detected in the random gold set; participants (recruited via AMT) were asked to draw bounding boxes around children’s hands and adult’s hands.
-Overall, we found that 34% of the hands in the random 24K sample were of children’s own hands (compared to 8% reported in @Fausey2016) suggesting that this difference in field of view did contribute substantially to the higher rate of hand detections in the frames.
-Heatmaps of the bounding boxes obtained from these annotations can be seen in Figure 3, showing that children’s hands tended to appear in the lower half of the frames.
+```{r} 
+gold_sample_no_child_hands <- gold_sample %>%
+  left_join(child_adult_hand_annotations) %>%
+  replace_na(list(child_hand_seg = FALSE)) %>% # replace NAs so they are counted
+  filter(child_hand_seg==FALSE) %>%
+  mutate(hand_eval_adults = evaluate_detector(hand_present_ketan, hand_openpose))
+
+hand_performance_adults = return_prf_short(gold_sample_no_child_hands$hand_eval_adults)
+```
+
+As has been observed in other studies on automated annotation of headcam data [e.g.
+@frank2013, @sanchez2018postural, @bambach2015lending], detection tasks that are easy in third-person video can be quite challenging in egocentric videos, due to difficult angles and sizes as well as substantial occlusion.
+For example, the infant perspective often contains non-canonical viewpoints of faces (e.g., looking up at a caregiver's chin) as well as partially-occluded or oblique viewpoints of both faces and hands.
+Furthermore, hand detection tends to be a somewhat harder problem than face detection [@simon2017hand; @bambach2015lending], and certainly one that has received less attention than face detection.
+We thus expected overall performance to be lower in these naturalistic videos than on either photos taken from the adult perspective or in egocentric videos in controlled, laboratory settings [@.g., @sanchez2018postural].
+
+To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / hits + false alarms), recall (hits / hits + misses), and f-score (the harmonic mean of precision and recall).
+In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`.
+For hands, the F-score was `r round(hand_performance[3],2)`, with a precision of `r round(hand_performance[1],2)` and recall of `r round(hand_performance[2],2)`.
+While face and hand detections showed moderately good precision, face detections were overall slightly more accurate than hand detections.
+In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.
+
+We suspected that this is in part because children’s own hands were often in view of the camera and unconnected to a pose—a notoriously challenging detection problem [@bambach2015lending].
+To assess this possibility, we obtained human annotations for a subsample of 9051 frames in which a hand was detected; participants (recruited via AMT) were asked to draw bounding boxes around children’s hands and adult’s hands.
+Overall, we found that almost half `r mean(hands_missed$child_hand_seg)` of missed hand detections were of child hands.
+When frames with children's hands were removed from the gold set, recall did improve to `r hand_performance_adults[3]` somewhat.
+We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Figure 3.
+
+Finally, we examined whether the precision, recall, and F-score for hands and faces varied with age or child, and did not find substantial variation.
+Thus, while OpenPose was trained on photographs from the adult perspective, this model still generalized relatively well to the egocentric infant viewpoint with no fine-tuning or post-processing of the detections.
+
+## Access to social information 
+### Changes across age
+
+```{r}
+## Make summary stats for cropped and uncropped detedctions
+summary_by_age <- d_all %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+  group_by(age_day_bin, child_id) %>%
+  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect)
+
+summary_by_age_cropped <- d_cropped %>%
+  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+  group_by(age_day_bin,child_id) %>%
+  summarize(num_detect = length(face_openpose), prop_faces = sum(face_detected) / num_detect,  prop_hands = sum(hand_detected) / num_detect) 
+```
+
+```{r FaceVsHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=4, fig.cap = "Proportion of faces (A), hands (B), and faces vs.
+hands (C) in the entire dataset and (D).
+when hand detections are restricted to the upper 60 percent of the field of view (B).
+Data from each child are plotted separately and binned by each week that the videos were filmed; data pointsscaled by the number of frames in that age range."}
+
+faces <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
+  geom_point(alpha=.2) +
+  geom_smooth(span=10) + 
+  ylab('Prop. Faces') + 
+  # theme_few(base_size=16) +
+  xlab('Age (months)') +
+  ylim(0,.5) +
+  theme(legend.position="none") +
+  ggtitle('A.') +
+  scale_colour_brewer(palette = "Dark2")
+
+hands <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.2) +
+  geom_smooth(span=10) + 
+  # theme_few(base_size=16) +
+  ylab('Prop. Hands') + 
+  xlab('Age (months)') +
+  ylim(0,.5)+
+  theme(legend.position="none") +
+  ggtitle('B.') +
+  scale_colour_brewer(palette = "Dark2")
+
+face_v_hand <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.2) +
+  geom_smooth(span=10) + 
+  # theme_few(base_size=16) +
+  ylab('Prop. Faces - Hands') + 
+  xlab('Age (months)') +
+  ylim(-.3, .3) +
+  theme(legend.position = "none") +
+  ggtitle('C.') +
+  scale_colour_brewer(palette = "Dark2")
+###
+
+faces_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
+  geom_point(alpha=.2) +
+  geom_smooth(span=10) + 
+  ylab('Prop. Faces (Upper FOV)') + 
+  # theme_few(base_size=16) +
+  xlab('Age (months)') +
+  ylim(0,.5) +
+  theme(legend.position="none") +
+  ggtitle('D.') +
+  scale_colour_brewer(palette = "Dark2")
+
+hands_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.2) +
+  geom_smooth(span=10) + 
+  # theme_few(base_size=16) +
+  ylab('Prop. Hands (Upper FOV)') + 
+  xlab('Age (months)') +
+  ylim(0,.5)+
+  theme(legend.position="none") +
+  ggtitle('E.') +
+  scale_colour_brewer(palette = "Dark2")
+
+face_v_hand_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
+  geom_point(alpha=.2) +
+  geom_smooth(span=10) + 
+  # theme_few(base_size=16) +
+  ylab('Prop. Faces - Hands (Upper FOV)') + 
+  xlab('Age (months)') +
+  ylim(-.3, .3) +
+  theme(legend.position = "none") +
+  ggtitle('F.')  +
+  scale_colour_brewer(palette = "Dark2")
+
+ggarrange(faces, hands, face_v_hand, faces_cropped, hands_cropped, face_v_hand_cropped, nrow=2)
+```
+
+We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands that were in view for each child.
+Data from videos were binned according to the age of the child (in weeks) (see Figure 2).
+First, when examining the younger age ranges (< 24 months), as in @Fausey2016, we saw that the proportion of faces vs.
+hands in view showed a moderate decrease across this age range, both when analyzing the random 24K frames as well as the entire dataset (see Figure 2A).
+
+However, the most striking result is a much greater proportion of hands in view than have previously been reported [@Fausey2016].
+We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset) or OpenPose annotations on the entire dataset.
+This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this is still an underestimate of the proportion of hands in view.
+Nonetheless, one reason this could be the case is the much larger field of view that was captured by the cameras used in this study: unlike previous studies, our cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible.
+Thus, the field of view (FOV) of the fisheye lens used was larger (109 degrees horizontal x 70 degrees vertical) than the FOV of the lens used in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees.
+This larger field of view may have allowed the SAYcam cameras to capture not only the presence of a social partner’s hands interacting with objects, but also the children’s own hands, leading to these more frequent hand detections.
 
@@
 To do so, we excluded hand detections that occurred in the bottom 40% of the frame, while retaining all hand detections that occurred in the top 60% of the frame.
-This coarse cropping of decreased the proportion of hand detections from `r mean(d_all$hand_openpose)`percent to `r mean(d_cropped$hand_detected_cropped)` percent.
+This coarse cropping of decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)`percent to `r round(mean(d_cropped$hand_detected_cropped),2)` percent, but only decreased face detections from `r round(mean(d_all$face_openpose),2)` to `r round(mean(d_cropped$face_detected_cropped,2)`.
+Within this modified field of view, we still observed, on average, more hand detections than face detections.
 
-With this modified field of view, we now observed a more substantive decrease across age in the proportions of faces relative to hands.
+However, we also still observed a moderate decrease in the proportion of faces vs.
+hands in view across age.
 To quantify this trend, we fit a generalized linear mixed model to the binned detection rates from this smaller field of field to estimate changes in the proportion of faces vs.
 hands over age.
-To better approximate @Fausey2016, we also restricted our analysis to the age range seen in @Fausey2016, excluding videos when children were over 24 months of age, and indeed found that the proportion of faces vs.
+To better approximate @Fausey2016, we  restricted our analysis to the age range seen in @Fausey2016, excluding videos when children were over 24 months of age, and indeed found that the proportion of faces vs.
 hands declined modestly with age (see Table 1).
+Note that @Fausey2016 also included data from very young infants (from 1-4 months of age), while here the youngest videos coming from S and A around 6 and 9 months of age, respectively.
 
 ```{r eval=FALSE}
-summary_by_age_days_cropped_limited <- d_cropped %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
-  group_by(age_day_bin,child_id) %>%
-  filter(age_day_bin < (24))  %>%
-  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected_cropped)) %>%
-  rename(age_months = age_day_bin)
+summary_by_age_days_cropped_younger <- d_cropped %>%
+  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
+  filter(age_days < 730) %>% ## less than 24 months
+  group_by(age_days,child_id) %>%
+  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected), num_detect = length(face_openpose)) %>%
+  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect)
 
 summary_by_age_days_cropped <- d_cropped %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
-  group_by(age_day_bin,child_id) %>%
-  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected_cropped)) %>%
-  rename(age_months = age_day_bin)
+  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
+  group_by(age_days,child_id) %>%
+  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected), num_detect = length(face_openpose)) %>%
+  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect)
 
@@
 ### Proportion faces vs. hands 
-face_vs_hands_model_limited <- glmer(cbind(num_faces,num_hands) ~ scale(age_months) + (1 | child_id), 
-             summary_by_age_days_cropped_limited, family = "binomial")
-# doesn't converge with random slopes for age | child_id
-face_vs_hands_model_limited_out = summary(face_vs_hands_model_limited)
+face_vs_hands_model_full_age <- lmer(prop_faces - prop_hands ~ scale(age_days) + scale(num_detect) + (age_days | child_id),  summary_by_age_days_cropped)
 
-```
+face_vs_hands_model_younger <- lmer(prop_faces - prop_hands ~ scale(age_days) + scale(num_detect) + (age_days | child_id),  summary_by_age_days_cropped_younger)
 
-```{r eval=FALSE}
-### Proportion faces vs. hands 
-face_vs_hands_model_full_age <- glmer(cbind(num_faces,num_hands) ~ scale(age_months) + (1 | child_id), 
+face_vs_hands_model_full_age <- glmer(cbind(num_faces,num_hands) ~ scale(age_days) + (1 | child_id), 
              summary_by_age_days_cropped, family = "binomial")
-# doesn't converge with random slopes for age | child_id
 face_vs_hands_model_full_age_out <- summary(face_vs_hands_model_full_age)

### 2020-01-28 analysis/analysis_goldset.Rmd
update goldset code to check OP bounding boxes

@@
 ```{r}
-# # g_seg_info <- g_seg %>%
-# #   distinct(full_image_path, vid_name_short, frame_ind)
-# #   
-# # bb_check <- bb %>%
-# #   mutate(frame_ind = frame, vid_name_short = vid_name) %>%
-# #   left_join(g_seg_info, by=c("vid_name_short","frame_ind")) %>%
-# #   filter(!is.na(full_image_path)) %>%
-# #   filter(mean_conf > 0)
-# 
-# # # dir.create(paste0('bbcheck/'))
-# # unique_images <- bb_check$full_image_path[101:200]
-# # 
-# # for (image in unique_images){
-# #   this_image_rgb <- image_read(image)
-# #   img <- image_draw(this_image_rgb)
-# #   a <- bb_check %>%
-# #     filter(full_image_path %in% image) 
-# #   
-# #   # rect(a$x_pos, a$y_pos-a$height_y, a$x_pos+a$width_x, a$y_pos)
-# #   text(a$center_x, a$center_y, a$center_y)
-# #   
-# #   annotated_file = paste0('bbcheck/',unique(a$vid_name_short), unique(a$frame_ind), 'OP-center.jpg')
-# #   image_write(img, annotated_file)
-# #   dev.off()
-# # }
+g_seg_info <- g_seg %>%
+  distinct(full_image_path, vid_name_short, frame_ind)
+
+bb_check <- bb_all %>%
+  mutate(frame_ind = frame, vid_name_short = vid_name) %>%
+  left_join(g_seg_info, by=c("vid_name_short","frame_ind")) %>%
+  filter(!is.na(full_image_path)) %>%
+  filter(mean_confidence > 0)
+
+# dir.create(paste0('bbcheck/'))
+unique_images <- bb_check$full_image_path[300:350]
+
+bb_check_face_tall <- bb_check_face %>%
+  filter(top>.7) %>%
+  filter(label=='face')
+
+bb_check_weird_vids <- bb_check %>%
+  filter(vid_name %in% weird_vids)
+
+unique_images = unique(bb_check_weird_vids$full_image_path)
+for (image in unique_images){
+  this_image_rgb <- image_read(image)
+  img <- image_draw(this_image_rgb)
+  a <- bb_check %>%
+    filter(full_image_path %in% image)
+
+  # rect(a$x_pos, a$y_pos-a$height_y, a$x_pos+a$width_x, a$y_pos)
+
+  text(a$left*680, a$top*480, a$top)
+
+  annotated_file = paste0('bbcheck_sanity/',unique(a$vid_name_short), unique(a$frame_ind), 'OP-center.jpg')
+  image_write(img, annotated_file)
+  dev.off()
+}
+
+face_check <- bb_check_weird_vids %>%
+  filter(label=="face")
+
 ```

### 2020-01-28 paper/cogsci/paper_jan28.Rmd
change datapaths in .Rmd to data_cogsci

@@
 library(egg)
+library(xtable)
 theme_set(theme_few())
@@
 ### Load preprocessed and filtered detections
-load('../../data/openpose_detections_filtered_threekids.RData') #d_all
-load('../../data/openpose_detections_filtered_cropped_allthreekids_jan28.RData') # d_cropped
+load('../../data_cogsci/openpose_detections_filtered_threekids_jan28.RData') #d_all
+load('../../data_cogsci/openpose_detections_filtered_cropped_allthreekids_jan28.RData') # d_cropped
 ```
@@
 ### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
-right_side_up_file = "../../data/video_right-side-up.csv"
+right_side_up_file = "../../data_cogsci/video_right-side-up.csv"
 right_side_up =read.csv(right_side_up_file)
@@
 ## load goal sample annotations
-load('../../data/ketan_gold_sample.RData')
+load('../../data_cogsci/ketan_gold_sample.RData')
 
@@
 ### Load turk hand annotations wtih all bounding boxes (multiple dets per frame)
-turk_annotations_seg = "../../data/turk_segmentations_hands_only_processed.csv" 
+turk_annotations_seg = "../../data_cogsci/turk_segmentations_hands_only_processed.csv" 
 g_seg = read.csv(turk_annotations_seg) %>%
@@
 
-```{r eval=FALSE}
-hands_missed <- gold_sample %>%
-  select(-vid_name) %>%
-  rename(vid_name = vid_name_short) %>% 
-  mutate(vid_name = as.factor(vid_name)) %>%
-  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
-  filter(!is.na(full_image_path)) %>%
-  filter(hand_eval_ketan == 'FN')
+```{r}
+load('../../data_cogsci/child_adult_hand_annotations.RData')
+# 
+# hands_missed <- gold_sample %>%
+#   select(-vid_name) %>%
+#   rename(vid_name = vid_name_short) %>% 
+#   mutate(vid_name = as.factor(vid_name)) %>%
+#   left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
+#   filter(!is.na(full_image_path)) %>%
+#   filter(hand_eval_ketan == 'FN')
 
@@
 ```{r} 
+load('../../data_cogsci/child_adult_hand_annotations.RData')
+
 gold_sample_no_child_hands <- gold_sample %>%
@@
 To assess this possibility, we obtained human annotations for a subsample of 9051 frames in which a hand was detected; participants (recruited via AMT) were asked to draw bounding boxes around children’s hands and adult’s hands.
-Overall, we found that almost half `r mean(hands_missed$child_hand_seg)` of missed hand detections were of child hands.
+Overall, we found that almost half  of missed hand detections were of child hands.
 When frames with children's hands were removed from the gold set, recall did improve to `r hand_performance_adults[3]` somewhat.
@@
 To do so, we excluded hand detections that occurred in the bottom 40% of the frame, while retaining all hand detections that occurred in the top 60% of the frame.
-This coarse cropping of decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)`percent to `r round(mean(d_cropped$hand_detected_cropped),2)` percent, but only decreased face detections from `r round(mean(d_all$face_openpose),2)` to `r round(mean(d_cropped$face_detected_cropped,2)`.
+This coarse cropping of decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)`percent to `r round(mean(d_cropped$hand_detected_cropped),2)` percent, but only decreased face detections from `r round(mean(d_all$face_openpose),2)` to `r round(mean(d_cropped$face_detected_cropped),2)`.
 Within this modified field of view, we still observed, on average, more hand detections than face detections.
@@
   summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected), num_detect = length(face_openpose)) %>%
-  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect)
+  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect) %>%
+  mutate(num_no_detect_faces = num_detect - num_faces, num_no_detect_hands = num_detect - num_hands)
 
@@
   summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected), num_detect = length(face_openpose)) %>%
-  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect)
+  mutate(num_no_detect_faces = num_detect - num_faces, num_no_detect_hands = num_detect - num_hands)
 
@@
 ### Proportion faces vs. hands 
-face_vs_hands_model_full_age <- lmer(prop_faces - prop_hands ~ scale(age_days) + scale(num_detect) + (age_days | child_id),  summary_by_age_days_cropped)
+faces_model_full_age <- glmer(cbind(num_faces,num_no_detect_faces) ~ scale(age_days) + (1 | child_id),  summary_by_age_days_cropped, family = "binomial")
+# summary(faces_model_full_age)
 
-face_vs_hands_model_younger <- lmer(prop_faces - prop_hands ~ scale(age_days) + scale(num_detect) + (age_days | child_id),  summary_by_age_days_cropped_younger)
+hands_model_full_age <- glmer(cbind(num_hands,num_no_detect_hands) ~ scale((age_days)) + (1 | child_id),  summary_by_age_days_cropped, family = "binomial", control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
+# summary(hands_model_full_age)
 
-face_vs_hands_model_full_age <- glmer(cbind(num_faces,num_hands) ~ scale(age_days) + (1 | child_id), 
-             summary_by_age_days_cropped, family = "binomial")
-face_vs_hands_model_full_age_out <- summary(face_vs_hands_model_full_age)
+##
+faces_model_younger <- glmer(cbind(num_faces,num_no_detect_faces) ~ scale((age_days)) + (1 | child_id),  summary_by_age_days_cropped_younger, family = "binomial",  control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
 
-# xtable(face_vs_hands_model_full_age_out$coefficients, digits=c(2,2,2,2,3),"Model coefficients from a generalized linear mixed model predicting the proportion of faces vs. hands seen by infants.") 
+hands_model_younger <- glmer(cbind(num_hands,num_no_detect_hands) ~ scale((age_days)) + (1 | child_id),  summary_by_age_days_cropped, family = "binomial", ,  control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
+
+# faces_model_full_age_out <- summary(faces_model_full_age)
+# xtable(faces_model_full_age_out$coefficients, digits=c(2,2,2,2,3),"Model coefficients from a generalized linear mixed model predicting the proportion of faces seen by infants.") 
 ```
@@
   \hline
-(Intercept) & -0.26 & 0.09 & -2.83 & 0.005 \\ 
-  scale(age\_months) & -0.15 & 0.00 & -225.40 & 0.000 \\ 
+(Intercept) & -1.55 & 0.03 & -52.47 & 0.000 \\ 
+  scale(age\_days) & -0.13 & 0.00 & -261.57 & 0.000 \\ 
    \hline
 \end{tabular}
-\caption{Model coefficients from a generalized linear mixed model predicting the proportion of faces vs. hands seen by infants.} 
+\caption{Model coefficients from a generalized linear mixed model predicting the proportion of faces seen by infants.} 
 \end{table}
@@
 ```{r}
-load('../../data/child_adult_hand_annotations.RData')
-load('../../data/saycam_metadata.RData')
+load('../../data_cogsci/saycam_metadata.RData')
 

### 2020-01-28 paper/cogsci/paper_jan28.Rmd
last edits to .rmd

@@
 To do so, we excluded hand detections that occurred in the bottom 40% of the frame, while retaining all hand detections that occurred in the top 60% of the frame.
-This coarse cropping of decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)`percent to `r round(mean(d_cropped$hand_detected_cropped),2)` percent, but only decreased face detections from `r round(mean(d_all$face_openpose),2)` to `r round(mean(d_cropped$face_detected_cropped),2)`.
+This coarse cropping of decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)`percent to `r round(mean(d_cropped$hand_detected),2)` percent, but only decreased face detections from `r round(mean(d_all$face_openpose),2)` to `r round(mean(d_cropped$face_detected),2)`.
 Within this modified field of view, we still observed, on average, more hand detections than face detections.
@@
 d_by_location_cropped <- d_cropped %>%
+  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
   mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
@@
   group_by(Location,child_id,age_day_bin) %>%
-  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_detected_cropped), num_detect = length(hand_detected_cropped))  %>%
+  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_detected), num_detect = length(hand_detected))  %>%
   filter(num_detect > 12000) %>% ## 18000 frames = 10 minutes of video at 30 fps %>%

### 2020-01-29 paper/cogsci/paper.Rmd
small edits

@@
 In addition, we find considerable variability in the proportion of faces/hands viewed by children in different locations (e.g., living room vs.
-kitchen), demonstrating that variability across activity contexts may be a driving factor in the amount of social information that infants’ experience.
+kitchen), demonstrating that variability across activity contexts may be a driving factor in the amount of social information that infants experience.
 
@@
 averted gaze [@Farroni2002], despite their limited acuity.
-As faces are likely to be an important conduit of social information that scaffolds cognitive development, cognitive scientists have long hypothesized that faces are prevalent in the visual experience of young infants.
+As faces are likely to be an important conduit of social information that scaffolds cognitive development, psychologists have long hypothesized that faces are prevalent in the visual experience of young infants.
 
-Yet until recently most hypotheses about infants’ visual experience have gone untested.
-Though parents and scientists alike have strong intuitions about what infant’s see, even the viewpoint of a walking child is not easily predicted by these intuitions [@clerkin2017; @franchak2011].
-By equipping infants and toddlers with head-mounted cameras, researchers have begun to document the infant egocentric perspective on the world.
+Yet until recently most hypotheses about infants' visual experience have gone untested.
+Though parents and scientists alike have strong intuitions about what infants see, even the viewpoint of a walking child is not easily predicted by these intuitions [@clerkin2017; @franchak2011].
+By equipping infants and toddlers with head-mounted cameras, researchers have begun to document the infant's egocentric perspective on the world.
 Using these methods, a growing body of work now demonstrates that the viewpoints of very young infants (less than 4 months of age) are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @Sugden2014; @Jayaraman2018].
 
-As infants motor and cognitive abilities mature beyond these early months, their perspective on the world becomes even more varied.
-Crawlers see fewer faces and hands than do walking children [@Sanchez2018; @franchak2017see; @kretch2014] as well as different view of objects [@smith2011not].
-Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, as their perspective starts to capture views of hands paired with the objects they are acting on [@Fausey2016].
-In turn, caregivers may start to use their hands with more communicative intent, directing infants attention with pointing and gestures to different events or objects during play [@yu2013joint].
+Beyond these early months,infants motor and cognitive abilities mature, leading to a vastly different perspectives on the world.
+For example, crawlers see fewer faces and hands than do walking children [@Sanchez2018; @franchak2017see; @kretch2014] as well as different views of objects [@smith2011not].
+Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, and their perspective starts to capture views of hands manipulating objects [@Fausey2016].
+In turn, caregivers may also start to use their hands with more communicative intent, directing infants attention by pointing and gesturing to different events and objects during play [@yu2013joint].
 
-Here, we analyze the social information present in the infant visual perspective by analyzing a longitudinal collection of over 1400 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam].
+Here, we examine the social information present in the infant visual perspective--the presence of faces and hands--by analyzing a longitudinal collection of over 1400 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam].
 In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways.
-First, recordings were taken under a large variety of contexts, encompassing infants’ viewpoints during both activities outside and inside the home.
-Even in other naturalistic datasets, the incredible variety in a typical infant’s experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth).
-Second, the head-mounted cameras used in the SAYcam dataset captured a substantially larger field of view than those typically used, allowing a more complete picture of the infant perspective.
-Head-mounted cameras with a more restricted field of view do still capture where infants are foveating most of the time [@yoshida2008, @smith2015contributions] but may still fail to capture short saccades to either faces or hands in the periphery, as the timescale of head movements is much longer.
+First, recordings were taken under a large variety of activity contexts [@roy2015predicting; @bruner1985role] encompassing infants' viewpoints during both activities outside and inside the home.
+Even in other naturalistic datasets, the incredible variety in a typical infan's experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth).
+Second, the head-mounted cameras used in the SAYcam dataset captured a larger field of view than those typically used, allowing a more complete picture of the infant perspective.
+While head-mounted cameras with a more restricted field of view do represent where infants are foveating most of the time [@yoshida2008, @smith2015contributions], they may fail to capture short saccades to either faces or hands in the periphery, as the timescale of head movements is much longer.
 
-With hundreds of hours of footage (>29M frames), this large dataset necessitates a shift to an automated annotation strategy.
+With hundreds of hours of footage (>37.5M frames), however, this large dataset necessitates a shift to an automated annotation strategy.
 Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that many frames are typically not inspected, even in the most comprehensive studies.
-For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand annotated (by four coders), totalling 103,383 frames (per coder)—an impressive number of annotations but nonetheless only 0.67% of the collected footage.
+For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand-annotated (by four coders), totalling 103,383 frames (per coder)—an impressive number of annotations but nonetheless only 0.67% of the collected footage.
 To address this challenge, we use a modern computer vision model of pose detection to automatically detect the presence of hands and faces from the infant egocentric viewpoint.
@@
 In the following paper, we first describe the dataset and validate the use of this model by comparing face and hand detections to a human-annotated set of 24,000 frames.
-Next, we report how the proportion of faces and hands changes across age.
+Next, we report how the proportion of faces and hands changes with age in each of the three children in the dataset.
 We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the present cameras as well as a diversity of locations during which videos were recorded.
@@
 The dataset is described in detail in @SAYcam; we summarize these details here.
-Children wore Veho Muvi miniature cameras mounted on a custom camping headlamp harness (“headcams”) at least twice weekly, for approximately one hour per recording session.
+Children wore Veho Muvi miniature cameras mounted on a custom camping headlamp harness ("headcams") at least twice weekly, for approximately one hour per recording session.
 One weekly session was on the same day each week at a roughly constant time of day, while the other(s) were chosen arbitrarily at the participating family’s discretion.
@@
 Videos[^1] with technical errors or that were not taken from the egocentric perspective were excluded from the dataset.
-While data collection for the third child (Y) is still ongoing, here we analyze `r num_videos` videos, with a total duration of `r num_hours` hours (>29 million frames).
+While data collection for the third child (Y) is still ongoing, here we analyze `r num_videos` videos, with a total duration of `r round(num_hours,2)` hours (>37.5 million frames).
 [^1]: All videos are available at https://nyu.databrary.org/volume/564
@@
 ```{r examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=3.5, set.cap.width=T, num.cols.cap=2, fig.align = "center", fig.cap = "Example frames taken from the dataset, illustrating variability in the infant perspective across different locations.
-OpenPose detections are shown overlaid on these images."}
+OpenPose detections are shown overlaid on these images (green dots = face, red dots = hands, orange dots = pose)."}
 examples <- png::readPNG("figs/modifiedOPfigure_v3.png")
@@
 
-```{r density, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=4, fig.height=2, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in teh 24K random gold set; each dot represents the center of a bounding box made by an adult participant."}
+```{r density, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=4, fig.height=2, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant."}
 ggarrange(child_hand_plot, adult_hand_plot, nrow=1)
@@
 We thus next examined variation in presence of hands and faces across different locations.
-Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location o videos were filmed in.
+Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location that the videos were filmed in.
 `r videos_included` were filmed in single location, representing 17 percent of the dataset and over 5 million frames (see @SAYcam).
@@
 First, we found a relatively high proportion of faces in view in the videos from the youngest age ranges in each child, confirming previous findings [@Fausey2016].
-This is particularly notable given that, in cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age (e.g., Fausey 2016; Jayaraman, Fausey, & Smith, 2015; Sugden, Mohamed-Ali, & Moulson, 2014) who see both more frequent and more persistent faces (Jayaraman & Smith, 2018).
+This is particularly notable given that, in cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018].
 
 Second, we found considerable variability in the social information in view depending on the activity context in which children were present.
-Even within a given, well-defined context---mealtime---we found variability across individual children.
-Intuitively, there are at least three ways to feed a young child in a kitchen (i.e., forward facing the child in a high chair, holding the child outward, or sitting side by side with them) and these regularities in a child’s life may hold a larger influence over the amount of social information in view than previously considered.
+Even within a given, well-defined context---e.g., mealtime---we found variability across individual children.
+Intuitively, there are at least three ways to feed a young child in a kitchen: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side with the child.
+Each of these positions might offer the child significantly differing degrees of visual access to face and hands.
+For example, consider the constant access to a caregiver's face afforded by sitting across from them (1) as compared to sitting behind the child (2), where the child may rarely glimpse the caregiver's face.
+Regularities such as these in daily parent-child interactions may hold a larger influence over the amount of social information in children's view than previously considered.
 
-Finally, we demonstrate the feasibility of using a modern, off-the-shelf computer vision model to vastly increase the efficiency of processing egocentric headcam footage, allowing us to annotate the entirety of very large datasets (here, >30 million frames) for the presence and size of people, hands, and faces, representing a 300-fold increase in data relative to prior work [@Fausey2016].
+Finally, we demonstrate the feasibility of using a modern, off-the-shelf computer vision model to vastly increase the efficiency of processing egocentric headcam footage, allowing us to annotate the entirety of very large datasets (here, >37.5 million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to prior work [e.g., @Fausey2016].
 As these detections were imperfect compared to human annotators, fine-tuning these models to better optimize for the infant viewpoint remains an open avenue for future work.
-Standard computer vision models are rarely exposed on these naturalistic, egocentric viewpoints, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors.
+Standard computer vision models are rarely exposed to these naturalistic, egocentric viewpoints, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors.
 
 These analyses have highlighted the importance of considering the infants field-of-view when analyzing egocentric videos.
-In many frames children's own hands were likely visible, due to the wide field of view—capturing valuable information about what these children were interacting with in different contexts across the first few years of their life.
+In many frames children's own hands were likely visible, due to the wide field-of-view—capturing valuable information about what these children were interacting with in different contexts across the first few years of their life.
 Furthermore, though this choice more closely approximates children’s actual perspective, these viewpoints are still a proxy as we do not know where in the frames children are allocating their attention.
@@
 Indeed, the questions of how, when, from whom, and what data we sample become critically important when we attempt to construct naturalistic datasets, and we would be remiss if we did not acknowledge the limitations of the present dataset.
-While these data are longitudinal, they are only sampled from representative of few children, all growing up in relatively privileged households in western societies.
+While these data are longitudinal, they are only sampled from only a few children, all of whom are growing up in relatively privileged households in western societies and thus are not representative of the global population.
 Any idiosyncrasies in how and when these particular families chose to film these videos undoubtedly influences the variability seen here.

### 2020-01-29 paper/cogsci/paper_jan28.Rmd
redo data sources, figures for paper

@@
 theme_set(theme_few())
+
+# renv::init()
+# https://rstudio.github.io/renv/articles/renv.html
 ```
@@
 ### Load preprocessed and filtered detections
-load('../../data_cogsci/openpose_detections_filtered_threekids_jan28.RData') #d_all
-load('../../data_cogsci/openpose_detections_filtered_cropped_allthreekids_jan28.RData') # d_cropped
+load('../../data_cogsci/openpose_detections_filtered_2020-01-29.RData') # d_all
+load('../../data_cogsci/openpose_detections_filtered_cropped_2020-01-29.RData') # d_cropped
 ```
@@
 ```{r}
-### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
-right_side_up_file = "../../data_cogsci/video_right-side-up.csv"
-right_side_up =read.csv(right_side_up_file)
-
-# get INCORRECT videos
-flipped_videos <- right_side_up %>%
-  filter(right_side_up==1)
-
-## load goal sample annotations
-load('../../data_cogsci/ketan_gold_sample.RData')
-
-## preprocess them
- ketan_gold_out <- ketan_gold %>%
-   rowwise() %>%
-   mutate(vid_name = str_split_fixed(vid_name,".mp4",2)[,1])%>%
-   mutate(vid_name_short = str_split(vid_name,"[.]")[[1]][1]) %>%
-   filter(!vid_name_short %in% flipped_videos$video) %>%
-   mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
-   rename(face_present_ketan = face_present, hand_present_ketan = hand_present)
-
 # Function to evaluate detectors
@@
 
+ ## load gold sample annotations
+ load('../../data_cogsci/gold_sample_annotations_2020-01-29.RData') #d_all
+
  ## evaluate detectors
- gold_sample <- ketan_gold_out %>%
-  select(-vid_name) %>%
-  rename(vid_name = vid_name_short) %>% 
-  mutate(vid_name = as.factor(vid_name)) %>%
+ gold_sample <- gold_sample %>%
   mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose))
@@
 ```{r}
-### Load turk hand annotations wtih all bounding boxes (multiple dets per frame)
-turk_annotations_seg = "../../data_cogsci/turk_segmentations_hands_only_processed.csv" 
-g_seg = read.csv(turk_annotations_seg) %>%
-  select(-HITID, -HITTypeId, -WorkerID) %>%
-  mutate(center_x = left + width/2, center_y = top + height/2)
+### Examine gold sample performance by child hands
+load('../../data_cogsci/child_adult_hand_annotations_by_frame.RData')
+# 
+hands_missed <- gold_sample %>%
+  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
+  filter(!is.na(full_image_path)) %>%
+  filter(hand_eval_ketan == 'FN')
 
-child_hands <- g_seg %>%
-  filter(label=="Child hand")
+gold_sample_no_child_hands <- gold_sample %>%
+  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
+  replace_na(list(child_hand_seg = FALSE)) %>% # replace NAs with false (frames not in annotations (NAs) did not have hands) 
+  filter(child_hand_seg==FALSE) %>% # now these are counted as frames where OP didn't need to detect something
+  mutate(hand_eval_adults = evaluate_detector(hand_present_ketan, hand_openpose))
 
-adult_hands <- g_seg %>%
-  filter(label=="Adult hand")
-```
-
-```{r}
-load('../../data_cogsci/child_adult_hand_annotations.RData')
-# 
-# hands_missed <- gold_sample %>%
-#   select(-vid_name) %>%
-#   rename(vid_name = vid_name_short) %>% 
-#   mutate(vid_name = as.factor(vid_name)) %>%
-#   left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
-#   filter(!is.na(full_image_path)) %>%
-#   filter(hand_eval_ketan == 'FN')
+hand_performance_adults = return_prf_short(gold_sample_no_child_hands$hand_eval_adults)
 
@@
 ```{r} 
-##
+### Load turk hand annotations with all bounding boxes (multiple dets per frame)
+load("../../data_cogsci/hand_annotations_2020-01-29.RData")
+
+child_hands <- hand_annotations %>%
+  filter(label=="Child hand")
+
+adult_hands <- hand_annotations %>%
+  filter(label=="Adult hand")
+
+## plot centers of the bounding boxes made for child and adult hands
 child_hand_plot <- ggplot(child_hands, aes(x=center_x, y=center_y)) +
-  geom_point() + 
-  stat_density_2d(aes(fill = ..level..), geom="polygon") +
+  geom_point(alpha=.1) + 
+  stat_density_2d(aes(fill = ..level..), geom="polygon", alpha=.8) +
   coord_fixed(ratio=1) +
@@
 adult_hand_plot <- ggplot(adult_hands, aes(x=center_x, y=center_y)) +
-  geom_point() + 
-  stat_density_2d(aes(fill = ..level..), geom="polygon") +
+  geom_point(alpha=.1) + 
+  stat_density_2d(aes(fill = ..level..), geom="polygon", alpha=.8) +
   coord_fixed(ratio=1) +
@@
 ggarrange(child_hand_plot, adult_hand_plot, nrow=1)
-```
-
-```{r} 
-load('../../data_cogsci/child_adult_hand_annotations.RData')
-
-gold_sample_no_child_hands <- gold_sample %>%
-  left_join(child_adult_hand_annotations) %>%
-  replace_na(list(child_hand_seg = FALSE)) %>% # replace NAs so they are counted
-  filter(child_hand_seg==FALSE) %>%
-  mutate(hand_eval_adults = evaluate_detector(hand_present_ketan, hand_openpose))
-
-hand_performance_adults = return_prf_short(gold_sample_no_child_hands$hand_eval_adults)
 ```
@@
   summarize(num_detect = length(face_openpose), prop_faces = sum(face_detected) / num_detect,  prop_hands = sum(hand_detected) / num_detect)
+
 ```
 
-```{r FaceVsHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=4, fig.cap = "Proportion of faces (A), hands (B), and faces vs.
-hands (C) in the entire dataset and (D).
-when hand detections are restricted to the upper 60 percent of the field of view (B).
-Data from each child are plotted separately and binned by each week that the videos were filmed; data pointsscaled by the number of frames in that age range."}
+```{r}
+wide_cropped <- summary_by_age_cropped %>%
+  gather(region, prop, prop_faces, prop_hands) %>%
+  mutate(approach = "cropped",
+         region = ifelse(region == "prop_faces","Face","Hands"))
 
-faces <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
+wide_uncropped <- summary_by_age %>%
+  gather(region, prop, prop_faces, prop_hands) %>%
+  mutate(approach = "uncropped",
+         region = ifelse(region == "prop_faces","Face","Hands"))
+
+ggplot(wide_uncropped, 
+       aes(x=age_day_bin, y=prop, 
+           size=log10(num_detect),
+           col=region)) +
   geom_point(alpha=.2) +
-  geom_smooth(span=10) + 
-  ylab('Prop. Faces') + 
-  # theme_few(base_size=16) +
-  xlab('Age (months)') +
+  geom_smooth(span=10, aes(weight = num_detect)) + 
+  geom_smooth(data = wide_cropped, aes(weight = num_detect),
+              lty = 2, span=10, se = FALSE) +
+  ylab('Proportion Detections') + 
+  xlab('Age (Months)') +
   ylim(0,.5) +
-  theme(legend.position="none") +
-  ggtitle('A.') +
-  scale_colour_brewer(palette = "Dark2")
-
-hands <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
-  geom_point(alpha=.2) +
-  geom_smooth(span=10) + 
-  # theme_few(base_size=16) +
-  ylab('Prop. Hands') + 
-  xlab('Age (months)') +
-  ylim(0,.5)+
-  theme(legend.position="none") +
-  ggtitle('B.') +
-  scale_colour_brewer(palette = "Dark2")
-
-face_v_hand <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
-  geom_point(alpha=.2) +
-  geom_smooth(span=10) + 
-  # theme_few(base_size=16) +
-  ylab('Prop. Faces - Hands') + 
-  xlab('Age (months)') +
-  ylim(-.3, .3) +
-  theme(legend.position = "none") +
-  ggtitle('C.') +
-  scale_colour_brewer(palette = "Dark2")
-###
-
-faces_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
-  geom_point(alpha=.2) +
-  geom_smooth(span=10) + 
-  ylab('Prop. Faces (Upper FOV)') + 
-  # theme_few(base_size=16) +
-  xlab('Age (months)') +
-  ylim(0,.5) +
-  theme(legend.position="none") +
-  ggtitle('D.') +
-  scale_colour_brewer(palette = "Dark2")
-
-hands_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
-  geom_point(alpha=.2) +
-  geom_smooth(span=10) + 
-  # theme_few(base_size=16) +
-  ylab('Prop. Hands (Upper FOV)') + 
-  xlab('Age (months)') +
-  ylim(0,.5)+
-  theme(legend.position="none") +
-  ggtitle('E.') +
-  scale_colour_brewer(palette = "Dark2")
-
-face_v_hand_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
-  geom_point(alpha=.2) +
-  geom_smooth(span=10) + 
-  # theme_few(base_size=16) +
-  ylab('Prop. Faces - Hands (Upper FOV)') + 
-  xlab('Age (months)') +
-  ylim(-.3, .3) +
-  theme(legend.position = "none") +
-  ggtitle('F.')  +
-  scale_colour_brewer(palette = "Dark2")
-
-ggarrange(faces, hands, face_v_hand, faces_cropped, hands_cropped, face_v_hand_cropped, nrow=2)
+  theme(legend.position="bottom") +
+  facet_grid(.~child_id) + 
+  ggthemes::scale_color_solarized(name = "Detection") + 
+  scale_size_continuous(name = "Detections (Log 10)")
 ```
@@
 This coarse cropping of decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)`percent to `r round(mean(d_cropped$hand_detected),2)` percent, but only decreased face detections from `r round(mean(d_all$face_openpose),2)` to `r round(mean(d_cropped$face_detected),2)`.
-Within this modified field of view, we still observed, on average, more hand detections than face detections.
+Within this modified field of view, we still observed, on average, more hand detections than face detections'.
 
@@
 hands in view across age.
-To quantify this trend, we fit a generalized linear mixed model to the binned detection rates from this smaller field of field to estimate changes in the proportion of faces vs.
-hands over age.
-To better approximate @Fausey2016, we  restricted our analysis to the age range seen in @Fausey2016, excluding videos when children were over 24 months of age, and indeed found that the proportion of faces vs.
+To quantify this trend, we fit a linear mixed model to the proportion of hands/faces observed, binned across the days in which the videos were filmed.
+T
+
+ e foungain found that the proportion of faces vs.
 hands declined modestly with age (see Table 1).
@@
 ```{r eval=FALSE}
-summary_by_age_days_cropped_younger <- d_cropped %>%
-  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
-  filter(age_days < 730) %>% ## less than 24 months
-  group_by(age_days,child_id) %>%
-  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected), num_detect = length(face_openpose)) %>%
-  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect) %>%
-  mutate(num_no_detect_faces = num_detect - num_faces, num_no_detect_hands = num_detect - num_hands)
-
 summary_by_age_days_cropped <- d_cropped %>%
@@
   summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected), num_detect = length(face_openpose)) %>%
-  mutate(num_no_detect_faces = num_detect - num_faces, num_no_detect_hands = num_detect - num_hands)
+  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect)
 
+summary_by_age_days_cropped_younger <- summary_by_age_days_cropped %>%
+  filter(age_days < 730) ## less than 24 months
+```
+###
+```{r}
+library(lmerTest)
+summary_by_age_days_cropped$age_scale <- scale(summary_by_age_days_cropped$age_days, scale = FALSE)[,1] / 30.3
+# summary_by_age_days_cropped_younger$age_scale <- scale(summary_by_age_days_cropped_younger$age_days, scale = FALSE)[,1] / 30.3
+
+faces_model_full_age_out = summary(lmer(prop_faces ~ age_scale + (1 | child_id), data = summary_by_age_days_cropped))
+hands_model_full_age_out = summary(lmer(prop_hands ~ age_scale + (1 | child_id), data = summary_by_age_days_cropped))
 ```
 
-```{r eval=FALSE}
-### Proportion faces vs. hands 
-faces_model_full_age <- glmer(cbind(num_faces,num_no_detect_faces) ~ scale(age_days) + (1 | child_id),  summary_by_age_days_cropped, family = "binomial")
-# summary(faces_model_full_age)
+```{r}
+xtable(faces_model_full_age_out$coefficients, digits=c(2,2,2,2,3,3),"Model coefficients from a generalized linear mixed model predicting the proportion of faces seen by infants.")
 
-hands_model_full_age <- glmer(cbind(num_hands,num_no_detect_hands) ~ scale((age_days)) + (1 | child_id),  summary_by_age_days_cropped, family = "binomial", control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
-# summary(hands_model_full_age)
-
-##
-faces_model_younger <- glmer(cbind(num_faces,num_no_detect_faces) ~ scale((age_days)) + (1 | child_id),  summary_by_age_days_cropped_younger, family = "binomial",  control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
-
-hands_model_younger <- glmer(cbind(num_hands,num_no_detect_hands) ~ scale((age_days)) + (1 | child_id),  summary_by_age_days_cropped, family = "binomial", ,  control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
-
-# faces_model_full_age_out <- summary(faces_model_full_age)
-# xtable(faces_model_full_age_out$coefficients, digits=c(2,2,2,2,3),"Model coefficients from a generalized linear mixed model predicting the proportion of faces seen by infants.") 
+xtable(hands_model_full_age_out$coefficients, digits=c(2,2,2,2,3,3),"Model coefficients from a generalized linear mixed model predicting the proportion of hands seen by infants.")
 ```
-
-\begin{table}[ht]
-\centering
-\begin{tabular}{rrrrr}
-  \hline
- & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
-  \hline
-(Intercept) & -1.55 & 0.03 & -52.47 & 0.000 \\ 
-  scale(age\_days) & -0.13 & 0.00 & -261.57 & 0.000 \\ 
-   \hline
-\end{tabular}
-\caption{Model coefficients from a generalized linear mixed model predicting the proportion of faces seen by infants.} 
-\end{table}
 
@@
 # 
-
-# d_by_location_cropped$Location = droplevels(d_by_location_cropped$Location)
-# levels(d_by_location_cropped$Location)
+d_by_location_cropped$Location = droplevels(d_by_location_cropped$Location) # get rid of unused levels (more than 1 location)
+# merge locations that seem similar
+levels_to_modify = levels(d_by_location_cropped$Location)
+levels_to_modify[10] = 'Outside' # Outside on property
+levels_to_modify[12] = 'Outside' # Off Property
+levels(d_by_location_cropped$Location) <- levels_to_modify
 
@@
   summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_detected), num_detect = length(hand_detected))  %>%
+  group_by(Location) %>%
   filter(num_detect > 12000) %>% ## 18000 frames = 10 minutes of video at 30 fps %>%
@@
 hands_to_plot_cropped <- face_hand_by_location_cropped %>%
+  group_by(Location, child_id) %>%
   multi_boot_standard(col="prop_hands") %>%
+  mutate(region = "Hand") %>%
   ungroup %>%
   left_join(face_hand_by_location_cropped) %>%
-  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
-  mutate(Location = fct_reorder(Location, mean))
+  mutate(prop = prop_hands) %>%
+  select(-prop_faces, -prop_hands) %>%
+  filter(!is.na(ci_lower))
 
 faces_to_plot_cropped <- face_hand_by_location_cropped %>%
+  group_by(Location, child_id) %>%
   multi_boot_standard(col="prop_faces") %>%
+  mutate(region = "Face") %>%
   ungroup %>%
   left_join(face_hand_by_location_cropped) %>%
-  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
-  mutate(Location = fct_reorder(Location, mean)) 
+  mutate(prop = prop_faces) %>%
+  select(-prop_faces, -prop_hands) %>%
+  filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter
+
+both_to_plot <- faces_to_plot_cropped %>%
+  full_join(hands_to_plot_cropped) %>%
+  group_by(Location) %>%
+  mutate(num_detect_location = sum(num_detect)) %>%
+  ungroup() %>%
+  mutate(Location = fct_reorder(Location, num_detect_location))
 ```
 
-```{r DetByLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3, fig.height=4, fig.cap = "Proportion of faces (A),  hands (B), and faces vs.
-hands  (C) by location in which egocentric videos were filmed; data from individual children are plotted separately (location annotations were not available for Y).
+```{r DetByLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3, fig.height=4, fig.cap = "Proportion of faces and hands by location in which egocentric videos were filmed; data from individual children are plotted separately (location annotations were not available for Y).
 Data are only taken from the top 60 percent of the frames so as to minimize the contribution of children’s own hands.
-Each dot represents data from a week in which videos were filmed and are scaled by the number of frames (i.e., amount of video) in that datapoint."}
+Each dot represents data from a week in which videos were filmed and are scaled by the number of frames in that datapoint."}
 
-faces_loc = ggplot(faces_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
-  geom_point(aes(x=Location, y=prop_faces, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
+ggplot(both_to_plot, aes(x = Location, y = mean, col=region)) + 
+  geom_point(aes(x=Location, y=prop, size=log10(num_detect)), alpha=.1, position = position_dodge(width=.3)) +
   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
-  # ylim(-.4,.4) +
   coord_flip() + 
-  ylab('Proportion Faces')+
+  ylab('Proportion Detected')+
   xlab('')+
-  scale_colour_brewer(palette = "Dark2") +
-  theme(legend.position = "none")
+  ggthemes::scale_color_solarized(name = "Detection") + 
+  theme(legend.position = "bottom") +
+  facet_grid(.~child_id)  +
+  scale_size_continuous(name = "Detections (Log 10)")
+```
 
-hands_loc = ggplot(hands_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
-  geom_point(aes(x=Location, y=prop_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
-  # ylim(-.4,.4) +
-  coord_flip() + 
-  xlab('')+
-  ylab('Proportion Hands') +
-  scale_colour_brewer(palette = "Dark2") +
-  theme(legend.position = "none")
-
-ggarrange(faces_loc, hands_loc, nrow=2)
-```
 # General Discussion

### 2020-01-29 src/get_all_openpose_bounding_boxes.R
reorg and rename src folder

@@ -1,43 +1,0 @@
-
-# load bounding boxes from openpose detections from the entire dataset
-# (created in get_bounding_boxes_per_vid.py using numpy vectors in $GROUP_SCRATCH/openpose_flattened_whole)
-
-require(data.table)
-require(here)
-require(stringr)
-
-files <- list.files("../src/bounding_boxes") # 1632 vids
-# A_20140630_2117_04_bounding_boxes.csv had no detections
-
-load("../src/data/vid_info.RData") # vid_info
-downup = fread("../src/data/video_right-side-up.csv", stringsAsFactors = F)
-
-df <- data.frame()
-
-#had to specify columns to get rid of the total column
-for (i in 1:length(files)) {
-  tmp <- fread(paste("../src/bounding_boxes", files[i], sep='/'), stringsAsFactors = F) 
-  if(ncol(tmp)==9) {
-    tmp$V1 = NULL
-    this_vid = str_remove(files[i], "_bounding_boxes.csv")
-    tmp$child_id = strsplit(files[i], '_')[[1]][1]
-    tmp$vid_name = this_vid
-    tmp$age_days = vid_info[which(vid_info$vid_name == this_vid)[1],]$age_days
-    tmp$right_side_up = downup[which(downup$video == this_vid),]$right_side_up
-    # remove any rows with all 0 bounding box + confidences (~50%)
-    tmp = subset(tmp, mean_confidence!=0)
-    #df <- rbindlist(list(df, tmp)) # , use.names = T
-    df = rbind(df, tmp)
-  } else {
-    print(paste("check file: ",files[i]))
-  }
-}
-
-save(df, file="all_bounding_boxes.RData")
-
-
-df$area = df$height * df$width
-require(ggplot2)
-df %>% filter(area>0) %>%
-  ggplot(aes(x=area, color=label, fill=label)) + 
-  geom_histogram(alpha=.5) 

### 2020-01-29 src/get_bounding_boxes_per_vid.py

@@ -1,79 +1,0 @@
-import os
-import numpy as np
-import pandas as pd
-
-# load flattened numpy arrays per video, extracts bounding boxes for hands and faces
-# per frame, and saves as long format CSV (one row per bounding box, maximum 9 per frame)
-
-VID_PATH = "/scratch/groups/mcfrank/Home_Headcam_new/openpose_flattened_whole" # /scratch/groups/mcfrank/Home_Headcam_new/openpose_flattened_whole
-OUT_PATH = "/scratch/groups/mcfrank/Home_Headcam_new/bounding_boxes/"
-#VID_PATH = "openpose_flattened"
-#f = "A_20130531_0818_01.npy" # for testing
-
-frame_size = {'x':640, 'y':480} # pixels; keypoint x,y coords are normalized 0-1, but go out of frame occasionall
-# min=-.22, max=1.16
-
-files = os.listdir(VID_PATH)
-
-# 130 for pose (18), face (70), L hand (21), and R hand (21) keypoints, in that order
-
-def get_bounding_box(X, Y):
-	left = np.min(X)
-	top = np.max(Y) # is (0,0) top or bottom left? assume bottom left for now -- check python
-	height = top - np.min(Y)
-	width = np.max(X) - left
-	return([height, width, left, top])
-
-def get_face_hand_bounding_boxes(detection):
-	# (X, Y, confidence) x 130 keypoints
-	X = detection[0]
-	Y = detection[1]
-	conf = detection[2]
-	pose_x = X[:18]
-	pose_y = Y[:18]
-	face_x = X[18:88]
-	face_y = Y[18:88]
-	Lhand_x = X[88:109]
-	Lhand_y = Y[88:109]
-	Rhand_x = X[109:]
-	Rhand_y = Y[109:]
-	bbs = [get_bounding_box(pose_x, pose_y) + [np.mean(conf[:18])], 
-		get_bounding_box(face_x, face_y) + [np.mean(conf[18:88])], 
-		get_bounding_box(Lhand_x, Lhand_y) + [np.mean(conf[88:109])], 
-		get_bounding_box(Rhand_x, Rhand_y) + [np.mean(conf[109:])]]
-	return bbs # could add mean confidences for face and each hand
-	# return height, width, left, top
-
-col_names = ["frame", "person", "label", "height", "width", "left", "top", "mean_confidence"]
-
-processed = os.listdir(OUT_PATH) # skip these
-
-# look into these:
-#  Problem processing A_20140609_2027_02
[…]

### 2020-01-30 analysis/get_all_openpose_bounding_boxes.R
reorg analysis scripts

@@ -1,0 +1,43 @@
+
+# load bounding boxes from openpose detections from the entire dataset
+# (created in get_bounding_boxes_per_vid.py using numpy vectors in $GROUP_SCRATCH/openpose_flattened_whole)
+
+require(data.table)
+require(here)
+require(stringr)
+
+files <- list.files("../src/bounding_boxes") # 1632 vids
+# A_20140630_2117_04_bounding_boxes.csv had no detections
+
+load("../src/data/vid_info.RData") # vid_info
+downup = fread("../src/data/video_right-side-up.csv", stringsAsFactors = F)
+
+df <- data.frame()
+
+#had to specify columns to get rid of the total column
+for (i in 1:length(files)) {
+  tmp <- fread(paste("../src/bounding_boxes", files[i], sep='/'), stringsAsFactors = F) 
+  if(ncol(tmp)==9) {
+    tmp$V1 = NULL
+    this_vid = str_remove(files[i], "_bounding_boxes.csv")
+    tmp$child_id = strsplit(files[i], '_')[[1]][1]
+    tmp$vid_name = this_vid
+    tmp$age_days = vid_info[which(vid_info$vid_name == this_vid)[1],]$age_days
+    tmp$right_side_up = downup[which(downup$video == this_vid),]$right_side_up
+    # remove any rows with all 0 bounding box + confidences (~50%)
+    tmp = subset(tmp, mean_confidence!=0)
+    #df <- rbindlist(list(df, tmp)) # , use.names = T
+    df = rbind(df, tmp)
+  } else {
+    print(paste("check file: ",files[i]))
+  }
+}
+
+save(df, file="all_bounding_boxes.RData")
+
+
+df$area = df$height * df$width
+require(ggplot2)
+df %>% filter(area>0) %>%
+  ggplot(aes(x=area, color=label, fill=label)) + 
+  geom_histogram(alpha=.5) 

### 2020-01-30 analysis/get_bounding_boxes_per_vid.py

@@ -1,0 +1,79 @@
+import os
+import numpy as np
+import pandas as pd
+
+# load flattened numpy arrays per video, extracts bounding boxes for hands and faces
+# per frame, and saves as long format CSV (one row per bounding box, maximum 9 per frame)
+
+VID_PATH = "/scratch/groups/mcfrank/Home_Headcam_new/openpose_flattened_whole" # /scratch/groups/mcfrank/Home_Headcam_new/openpose_flattened_whole
+OUT_PATH = "/scratch/groups/mcfrank/Home_Headcam_new/bounding_boxes/"
+#VID_PATH = "openpose_flattened"
+#f = "A_20130531_0818_01.npy" # for testing
+
+frame_size = {'x':640, 'y':480} # pixels; keypoint x,y coords are normalized 0-1, but go out of frame occasionall
+# min=-.22, max=1.16
+
+files = os.listdir(VID_PATH)
+
+# 130 for pose (18), face (70), L hand (21), and R hand (21) keypoints, in that order
+
+def get_bounding_box(X, Y):
+	left = np.min(X)
+	top = np.max(Y) # is (0,0) top or bottom left? assume bottom left for now -- check python
+	height = top - np.min(Y)
+	width = np.max(X) - left
+	return([height, width, left, top])
+
+def get_face_hand_bounding_boxes(detection):
+	# (X, Y, confidence) x 130 keypoints
+	X = detection[0]
+	Y = detection[1]
+	conf = detection[2]
+	pose_x = X[:18]
+	pose_y = Y[:18]
+	face_x = X[18:88]
+	face_y = Y[18:88]
+	Lhand_x = X[88:109]
+	Lhand_y = Y[88:109]
+	Rhand_x = X[109:]
+	Rhand_y = Y[109:]
+	bbs = [get_bounding_box(pose_x, pose_y) + [np.mean(conf[:18])], 
+		get_bounding_box(face_x, face_y) + [np.mean(conf[18:88])], 
+		get_bounding_box(Lhand_x, Lhand_y) + [np.mean(conf[88:109])], 
+		get_bounding_box(Rhand_x, Rhand_y) + [np.mean(conf[109:])]]
+	return bbs # could add mean confidences for face and each hand
+	# return height, width, left, top
+
+col_names = ["frame", "person", "label", "height", "width", "left", "top", "mean_confidence"]
+
+processed = os.listdir(OUT_PATH) # skip these
+
+# look into these:
+#  Problem processing A_20140609_2027_02
[…]

### 2020-01-30 analysis/analysis_bb_fulldataset.Rmd
scripts to start full bounding box analyses

---
title: "analyze_bb_fullset"
author: "Bria Long"
date: "1/23/2020"
output: html_document
---

# Basic data loading and setup
## Packages
```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(egg)
theme_set(theme_few())
```

### Load preprocessed bb's for all kids
```{r}
load(file = '../data/all_bounding_boxes_three_kids_preprocessed.RData')

```

### Make bins across which to analyze data
```{r}
bin_size = 7
min_age = min(bb_all$age_days)
max_age = max(bb_all$age_days)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

bb_all <- bb_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(d$age_day_bin)))
```

```{r}

bin_size = 6
min_age = 6
max_age = 30
bin_starts = seq(min_age, max_age+1,bin_size)
bins = c(bin_starts)

```

```{r}
hands_by_size_by_frame <- bb_all %>%
  filter(label=="hand") %>%
  group_by(vid_name, frame, age_days, child_id) %>%
  summarize(num_hands = sum(label=="hand"), avg_area = mean(area), avg_x = mean(center_x), avg_y = mean(center_y))

faces_by_size_by_frame <- bb_all %>%
  filter(label=="face") %>%
  group_by(vid_name, frame, age_days, child_id) %>%
  summarize(num_faces = sum(label=="face"), avg_area = mean(area), avg_x = mean(center_x), avg_y = mean(center_y))

poses_by_size_by_frame <- bb_all %>%
  filter(label=="pose") %>%
  group_by(vid_name, frame, age_days, child_id) %>%
  summarize(num_poses = sum(label=="pose"), avg_area = mean(area), avg_x = mean(center_x), avg_y = mean(center_y))
# 
# save(hands_by_size_by_frame, file="../data/hands_by_size_by_frame.RData")
# save(faces_by_size_by_frame, file="../data/faces_by_size_by_frame.RData")
# save(poses_by_size_by_frame, file="../data/poses_by_size_by_frame.RData")
```

```{r}

to_plot_poses <- poses_by_size_by_frame %>%
  mutate(age_months = age_days/30) %>%
  mutate(months_binned = cut(age_months, bins, labels=c("6m-12m","12m-18m","18m-24m","24m-32m")))

```

```{r}
bin_size = 7
min_age = min(bb_all$age_days)
max_age = max(bb_all$age_days)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

bb_all <- bb_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))

poses_by_size_by_frame <- poses_by_size_by_frame %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))

```

```{r}
ggplot(to_plot_poses, aes(x=num_poses, y=log(avg_area), col=child_id)) +
  geom_jitter(alpha=.2) +
  ggtitle('Pose size by #') +
  geom_grid(~months_binned)

ggplot(to_plot_hands, aes(x=num_hands, y=log(avg_area), col=child_id)) +
  geom_jitter(alpha=.2) +
  ggtitle('Hand size by #') +
  geom_grid(~months_binned)

ggplot(to_plot_faces, aes(x=num_faces, y=log(avg_area), col=child_id)) +
  geom_jitter(alpha=.2) +
  ggtitle('Face size by #') +
  geom_grid(~months_binned)

```

```{r}
subset_A <- poses_by_size_by_frame %>%
  filter(child_id == "A") %>%
  filter(age_days < 400)

subset_A <- subset_A %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))
```

```{r}
pose_summary_by_age_days <- poses_by_size_by_frame %>%
  group_by(age_days, child_id) %>%
  summarize(num_detect = length(frame), avg_area_age = mean(avg_area), avg_people = mean(num_poses)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))

face_summary_by_age_days <- faces_by_size_by_frame %>%
  group_by(age_days, child_id) %>%
  summarize(num_detect = length(frame), avg_area_age = mean(avg_area), avg_faces = mean(num_faces))

hand_summary_by_age_days <- hands_by_size_by_frame %>%
  group_by(age_days, child_id) %>%
  summarize(num_detect = length(frame), avg_area_age = mean(avg_area), avg_faces = mean(num_hands))

ggplot(pose_summary_by_age_days, aes(x=age_days, y=log(avg_area_age), col=child_id, size=num_detect)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10)

ggplot(face_summary_by_age_days, aes(x=age_days, y=log(avg_area_age), col=child_id, size=num_detect)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10)

ggplot(hand_summary_by_age_days, aes(x=age_days, y=log(avg_area_age), col=child_id, size=num_detect)) +
  geom_point(alpha=.2) +
  geom_smooth() 
```

### 2020-01-30 preprocessing/preprocess_datasets.Rmd
sort analyses by pre/post processing

---
title: "saycam full dataset -- preprocessing"
author: "Bria Long"
date: "1/9/2020"
output: html_document
---

# Basic data loading and setup
## Packages
```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(lubridate)
library(egg)
theme_set(theme_few())
## are we saving outputs
saveFiles = TRUE
```

## Read in data

### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
```{r}
allocentric_file = "../data/raw_data/SAYCAM_allocentric_videos.csv"
to_exclude =read.csv(allocentric_file)

# get INCORRECT videos 
to_exclude <- to_exclude %>%
  filter(allocentric==1) %>%
  rename(vid_name = video)
```

### Load SAYCAM metadata from csv file; get metadata from detections .csv
```{r}
metadata_file = "../data/raw_data/Metadata_SAYcam-2019-12-0922_54_28.csv"
meta=read.csv(metadata_file) %>%
  rowwise() %>%
  mutate(vid_name = str_split(File.Name,"[.]")[[1]][1]) %>%
  mutate(count_locations = length(str_split(Location,',')[[1]]))

# collapse duplicate labels
meta$Location[meta$Location=='Bedroom Alice/Sam'] = 'Bedroom'

# only select relevant columnts
meta <- meta %>%
  select(vid_name, count_locations, Location, Databrary.Link)
```

### Load in detections & bounding boxes from preprocessed Rdata file; 
```{r}
 # Could do list of detections  from csv (takes forever, skipping)
# data_file = "../data/raw_data/all_frames.csv"
# detections=read.csv(data_file)

## rdata is faster
load('../data/raw_data/openpose_detections_SA.RData') #SA = for Sam and Alice
# unselect unused columns
detections <- detections %>%
  select(-unix_time, -X, -vid_path, -nose_conf, -wrist_conf)
```

### Preprocess detections 
```{r}
# get shortened video names so they match across all files
all_video_names = as_tibble(unique(detections$vid_name))
all_video_names <- all_video_names %>%
  rowwise() %>%
  mutate(vid_name = str_split(value,"[.]")[[1]][1])

# reset levels of vid_name in big detections array for detections & bb (very slow rowwise)
levels(detections$vid_name) <- all_video_names$vid_name

# join with metadata and exclude bad videos
d_SA <- detections %>%
  left_join(meta, by='vid_name') %>%
  filter(!vid_name %in% to_exclude$vid_name)

## All 6 of the video that were not in this file (but were in the detections file) happened to be 6 very bad quality videos; excluding from detections
exclude_bad_quality <- d_SA %>%
  filter(!vid_name %in% right_side_up$video) %>%
  distinct(vid_name)

d_SA <- d_SA %>%
  filter(!vid_name %in% exclude_bad_quality$vid_name)

# make new list for later
vids_to_exclude <- to_exclude %>%
  select(vid_name) %>%
  full_join(exclude_bad_quality) %>%
  select(vid_name) %>%
  distinct(vid_name)

# check that we actually excluded the videos
num_orig_videos = length(unique(detections$vid_name))
num_videos_retained = length(unique(d_SA$vid_name))
assert_that(num_videos_retained < num_orig_videos)

# get rid of big data structure
remove(detections)
```

## Load, process, merge Y's data
### Now load in bounding box data from Y, which has detection rates built in
```{r}
load('../data/Y_bounding_boxes.RData') #df again as import
y_data <- df %>%
  rowwise() %>%
  mutate(age = str_split_fixed(vid_name, '_',4)[,3])
remove(df)

# ### wrangle age data for Y
d_y <- y_data %>%
  mutate(age_months = as.numeric(substr(age, 0,2)), days_to_add = as.numeric(substr(age, 3,4))) %>%
  mutate(age_days = age_months*30.42 + days_to_add)
##
if (saveFiles){
save(d_y, file = paste0('../data/temp_data/Y_bounding_boxes_cleaned_',today(),'.RData'))
}
```

### Do basic preprocessing on Y detection's
```{r}
### count hands/faces from bounding box outputs for Y -- for d_all
y_detections <- d_y %>%
  group_by(vid_name, frame,age_days) %>%
  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0))

y_detections <- y_detections %>%
  mutate(child_id = "Y") %>%
  left_join(meta)

if (saveFiles){
save(y_detections, file = paste0('../data/temp_data/Y_detections_preprocessed_',today(),'.RData'))
}
```

### Merge detections from Y with other kids
```{r}
# load(file='../data/temp_data/y_detections_preprocessed.RData')
y_detections <-  y_detections %>%
  rename(hand_openpose = hand_detected, face_openpose = face_detected) # standardize

d_all <- d_SA %>%
  mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
  full_join(y_detections)

# check
length(unique(d_all$vid_name)) == (length(unique(y_detections$vid_name)) +  length(unique(d_SA$vid_name)))

# clean up
remove(d_SA)
remove(d_y)

# save
if (saveFiles){
save(d_all, file = paste0('../data/preprocessed_data/openpose_detections_filtered_',today(),'.RData'))
}
```

### Look at any suspicious Sam videos with very high face detections (candidate missed allocentric videos)
```{r eval=FALSE}
# vid_check <- d_all %>%
#   filter(child_id == "S") %>%
#   group_by(vid_name, Databrary.Link) %>%
#   summarize(prop_faces=mean(face_openpose))
# 
# high_faces <- vid_check %>%
#   filter(prop_faces>.8)
```

# Cropped detections
## Load bounding boxes from S/A to get cropped detections
```{r}
## import bounding boxes
load('../data/raw_data/SA_bounding_boxes.RData')
bb_SA <- df
remove(df)

# get shortened video names so they match across all files
all_video_names_bb = as_tibble(unique(bb_SA$vid_name))
all_video_names_bb <- all_video_names_bb %>%
  rowwise() %>%
  mutate(vid_name = str_split(value,"[.]")[[1]][1])

# reset levels of vid_name in big detections array for detections & bb (very slow rowwise)
bb_SA$vid_name <- as.factor(bb_SA$vid_name)
levels(bb_SA$vid_name) <- all_video_names_bb$vid_name

# filter out flipped videos & get rid of bad variables
bb_SA <- bb_SA %>%
  filter(!vid_name %in% vids_to_exclude$vid_name) %>%
  select(-right_side_up, -age_days) # these variables were computed on the video names in other code and have NAs for some weird vids, excluding

# check that we excluded the wrong videos here 
vids_bb_S = length(unique(bb_SA$vid_name[bb_SA$child_id=='S']))
vids_bb_A = length(unique(bb_SA$vid_name[bb_SA$child_id=='A']))
vids_dets_S = length(unique(d_all$vid_name[d_all$child_id=='S']))
vids_dets_A = length(unique(d_all$vid_name[d_all$child_id=='A']))

## these are two videos in which A is just staring at the ceiling, no no bb's to be had in the entire vids
## can look at Databrary.link
vids_no_bb <- all_video_names %>%
  filter(!vid_name %in% all_video_names_bb$vid_name) %>%
  left_join(meta)

#
assert_that(vids_bb_S == vids_dets_S)

# if we meet checks, save
if (saveFiles){
save(bb_SA, file = paste0('../data/temp_data/SA_bounding_boxes_cleaned_', today(), '.RData'))
}
```

## Join detections for both and save out for later
```{r}
# load(file = '../data/Y_bounding_boxes_cleaned.RData') #  d_y from earlier if not loaded

## frame
# height_px = 480; width_px = 640
# bb_all_three <- d_y %>%
#   filter(person==0) %>% # only rows with detections for now so comparable to bb_all
#   mutate(left = left*width_px, top = top*height_px, height = height*height_px, width = width*width_px) %>% #unnormalize data so comparable
#   full_join(bb_all) %>% # join with SA bounding boxes
#   mutate(center_x = left + width/2, center_y = top - height/2, area = width*height) 
# 
# save(bb_all_three, file = '../data/all_bounding_boxes_three_kids_preprocessed.RData')
# remove(bb_all_three)
```

## Load temp files if we are skipping steps above run if we are skipping steps above
```{r eval=FALSE}
## For cropped detections, need..
# 1. full set of detections (d_all from above)
load(file='../data/preprocessed_data/openpose_detections_filtered_2020-01-29.RData')

# 2. bounding boxes from S and A (bb_SA)
load(file='../data/temp_data/SA_bounding_boxes_cleaned_2020-01-29.RData')

# 3. bounding boxes from Y (d_y) -- has different format than bb_SA, so diff name..
load(file='../data/temp_data/Y_bounding_boxes_cleaned_2020-01-29.RData')
```

### Make cropped detections for Y/SA, join, make cropped large data
```{r}
detections_cropped_Y <- d_y %>%
  filter(person==0) %>% #only get frames where detections so comparable
  filter((height<(.6*480))) %>%  ## 
  group_by(vid_name, frame, child_id, age_days) %>%
  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))

detections_cropped_Y <- detections_cropped_Y %>%
 ungroup() %>%
 mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id))

## Make cropped detections in top 60% of frame for S,A
detections_cropped_SA <- bb_SA %>%
  filter(height<(.6)) %>%  ## 
  group_by(vid_name, frame, child_id) %>%
  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))  
# join all together
all_cropped_detections <- detections_cropped_SA %>%
  ungroup() %>%
  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id)) %>%
  full_join(detections_cropped_Y)

## clean up workspace or else we run into memory limits
# cropped detections
remove(detections_cropped_Y)
remove(detections_cropped_SA)

# bb data
remove(y_data)
remove(bb_all)

## need to get "FALSE" on frames where we didn't have info to be able to compute proportions; uses d_all from earlier and fills it all back in

all_cropped_detections <- all_cropped_detections %>%
  select(-age_days, -child_id)

d_cropped <- d_all %>% ## needs to be loaded!
  as_tibble() %>%
  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id)) %>%
  select(vid_name, frame, child_id, age_days, face_openpose, hand_openpose) %>%
  left_join(all_cropped_detections, by=c("vid_name","frame"))

if (saveFiles){
save(d_cropped, file = paste0('../data/preprocessed_data/openpose_detections_filtered_cropped', today(), '.RData'))
}
```

# Other data files that get cleaned up for cogsci
### Gold sample annotations
```{r}
## load goal sample annotations
load('../data/raw_data/ketan_gold_sample.RData')

## preprocess them
 ketan_gold_out <- ketan_gold %>%
   rowwise() %>%
   mutate(vid_name = str_split_fixed(vid_name,".mp4",2)[,1])%>%
   mutate(vid_name_short = str_split(vid_name,"[.]")[[1]][1]) %>%
   filter(!vid_name_short %in% flipped_videos$video) %>%
   mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
   rename(face_present_ketan = face_present, hand_present_ketan = hand_present)

gold_sample <- ketan_gold_out %>%
  select(-vid_name) %>%
  rename(vid_name = vid_name_short) %>% 
  mutate(vid_name = as.factor(vid_name))

if (saveFiles){
save(gold_sample, file = paste0('../data/preprocessed_data/gold_sample_annotations', today(), '.RData'))
}
```

### Turk annotations (get rid of identifying info)
```{r}
turk_annotations_seg = "../data/raw_data/turk_segmentations_hands_only_processed.csv" 
hand_annotations = read.csv(turk_annotations_seg) %>%
  select(-HITID, -HITTypeId, -WorkerID) %>%
  mutate(center_x = left + width/2, center_y = top + height/2)

if (saveFiles){
save(hand_annotations, file = paste0('../data/preprocessed_data/hand_annotations_', today(), '.RData'))
}

```

```{r}
# what <- d_cropped %>%
#   filter(face_openpose == TRUE) %>%
#   filter(fa)
# 
child_hands_cropping <- d_cropped %>%
  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
  group_by(vid_name) %>%
  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_openpose), prop_faces_cropped = mean(face_detected), prop_hands_cropped = mean(hand_detected), diff = prop_hands - prop_hands_cropped) %>%
  filter(diff>.3) %>%
  left_join(meta)

vid_summary <- vid_summary %>%
  left_join(meta)
# weird_vids = unique(vid_summary$vid_name[vid_summary$prop_hands_cropped==0])
# 
# weird_d_all <- d_all %>%
#   filter(vid_name %in% weird_vids)
# 
# bb_all_check <- bb_all %>%
#   filter(vid_name %in% weird_vids)
```

### 2020-01-30 paper/cogsci/paper.tex
updates to cogsci paper

@@
 proportion of faces vs.~hands across age up to the end of the second
-year of life (Fausey, Jayaraman, \& Smith, 2016). In addition, we find
-considerable variability in the proportion of faces/hands viewed by
+year of life (C. M. Fausey, Jayaraman, \& Smith, 2016). In addition, we
+find considerable variability in the proportion of faces/hands viewed by
 children in different locations (e.g., living room vs.~kitchen),
@@
 Infants are confronted by a blooming, buzzing onslaught of stimuli
-({\textbf{???}}) which they must learn to parse to make sense of the
-world around them. Yet they do not embark on this learning process
-alone: From as early as 3 months of age, young infants follow overt gaze
-shifts (Gredeback, Fikke, \& Melinder, 2010), and even newborns prefer
-to look at faces with direct vs.~averted gaze (Farroni, Csibra, Simion,
-\& Johnson, 2002), despite their limited acuity. As faces are likely to
-be an important conduit of social information that scaffolds cognitive
-development, cognitive scientists have long hypothesized that faces are
-prevalent in the visual experience of young infants.
+(James, Burkhardt, Bowers, \& Skrupskelis, 1890) which they must learn
+to parse to make sense of the world around them. Yet they do not embark
+on this learning process alone: From as early as 3 months of age, young
+infants follow overt gaze shifts (Gredeb\wrapmf{\"{a}}ck, Theuring,
+Hauf, \& Kenward, 2008), and even newborns prefer to look at faces with
+direct vs.~averted gaze (Farroni, Csibra, Simion, \& Johnson, 2002),
+despite their limited acuity. As faces are likely to be an important
+conduit of social information that scaffolds cognitive development,
+cognitive scientists have long hypothesized that faces are prevalent in
+the visual experience of young infants.
 
@@
 child is not easily predicted by these intuitions (Clerkin, Hart, Rehg,
-Yu, \& Smith, 2017; Franchak et al., 2011; Yoshida \& Smith, 2008). By
+Yu, \& Smith, 2017; Franchak, Kretch, Soska, \& Adolph, 2011). By
 equipping infants and toddlers with head-mounted cameras, researchers
@@
 (Jayaraman \& Smith, 2018; Jayaraman, Fausey, \& Smith, 2015; Sugden,
-Mohamed-Ali, \& Moulson, n.d.).
+Mohamed-Ali, \& Moulson, 2014).
 
@@
 months, their perspective on the world becomes even more varied.
-Crawlers see fewer faces and hands than do walking children
-({\textbf{???}} papers; Sanchez, Long, Kraus, \& Frank, 2018) as well as
-different view of objects ({\textbf{???}}). Further, as infants learn to
-use their own hands to act on the world, they seem to focus on manual
-actions taken by their social partners, as their perspective starts to
-capture views of hands paired with the objects they are acting on
-(Fausey et al., 2016). In turn, caregivers may start to use their hands
-with more communicative intent, directing infants attention with
-pointing and gestures to different events or objects during play
-({\textbf{???}}).
+Crawlers see fewer faces and hands than do walking children (Franchak,
+Kretch, \& Adolph, 2017; Kretch, Franchak, \& Adolph, 2014; A. Sanchez,
+Long, Kraus, \& Frank, 2018) as well as different view of objects
+(Smith, Yu, \& Pereira, 2011). Further, as infants learn to use their
+own hands to act on the world, they seem to focus on manual actions
+taken by their social partners, as their perspective starts to capture
+views of hands paired with the objects they are acting on (C. M. Fausey
+et al., 2016). In turn, caregivers may start to use their hands with
+more communicative intent, directing infants attention with pointing and
+gestures to different events or objects during play (Yu \& Smith, 2013).
 
@@
 field of view do still capture where infants are foveating most of the
-time ({\textbf{???}}, ({\textbf{???}})) but may still fail to capture
-short saccades to either faces or hands in the periphery, as the
-timescale of head movements is much longer.
+time (H. Yoshida \& Smith, 2008, Smith, Yu, Yoshida, \& Fausey (2015))
+but may still fail to capture short saccades to either faces or hands in
+the periphery, as the timescale of head movements is much longer.
 
@@
 typically not inspected, even in the most comprehensive studies. For
-example, Fausey et al. (2016) collected a total of 143 hours of
+example, C. M. Fausey et al. (2016) collected a total of 143 hours of
 head-mounted camera footage (15.5 million frames), of which one frame
@@
 As has been observed in other studies on automated annotation of headcam
-data (e.g. {\textbf{???}}, ({\textbf{???}})), detection tasks that are
-easy in third-person video can be quite challenging in egocentric
-videos, due to difficult angles and sizes as well as substantial
-occlusion. For example, the infant perspective often contains
-non-canonical viewpoints of faces (e.g., looking up at a caregiver's
-chin) as well as partially-occluded or oblique viewpoints of both faces
-and hands.
+data (e.g. M. C. Frank, Simmons, Yurovsky, \& Pusiol, 2013, Alessandro
+Sanchez, Long, Kraus, \& Frank (2018), Bambach, Lee, Crandall, \& Yu
+(2015)), detection tasks that are easy in third-person video can be
+quite challenging in egocentric videos, due to difficult angles and
+sizes as well as substantial occlusion. For example, the infant
+perspective often contains non-canonical viewpoints of faces (e.g.,
+looking up at a caregiver's chin) as well as partially-occluded or
+oblique viewpoints of both faces and hands.
 
@@
 
-While these trends appear somewhat different than those observed in
-Fausey et al. (2016), note that Fausey et al. (2016) included data from
-very young infants (from 1-4 months of age), while here the youngest
-videos coming from S and A around 6 and 9 months of age, respectively.
-Similarly, our age range extends 8 months later than those infants in
-Fausey et al. (2016), throughout a portion of third year of life.
+While these trends appear somewhat different than those observed in C.
+M. Fausey et al. (2016), note that C. M. Fausey et al. (2016) included
+data from very young infants (from 1-4 months of age), while here the
+youngest videos coming from S and A around 6 and 9 months of age,
+respectively. Similarly, our age range extends 8 months later than those
+infants in C. M. Fausey et al. (2016), throughout a portion of third
+year of life.
 
@@
 
-\caption[Proportion of faces vs]{Proportion of faces vs.
-hands in the entire dataset (A) and when hand detections are restricted to the upper 60 percent of the field of view (B).
-Data from each child (A, S) are plotted separately and binned by each week that the videos were filmed; data is scaled by the number of frames in that age range.}\label{fig:FaceVsHands}
+\caption[Proportion of faces (A), hands (B), and faces vs]{Proportion of faces (A), hands (B), and faces vs.
+hands (C) in the entire dataset and (D).
+when hand detections are restricted to the upper 60 percent of the field of view (B).
+Data from each child are plotted separately and binned by each week that the videos were filmed; data pointsscaled by the number of frames in that age range.}\label{fig:FaceVsHands}
 \end{figure*}
@@
 However, the most striking result is a much greater proportion of hands
-in view than have previously been reported (Fausey et al., 2016). We
-found this to be true across all ages, in both children, and regardless
-of whether we analyzed human annotations (on the 24K random subset) or
-OpenPose annotations on entire dataset. This is notable especially given
-that OpenPose showed relatively low recall for hands, indicating that
-this is still an underestimate of the proportion of hands in view. One
-reason this could be the case is the much larger field of view that was
-captured by the cameras used in this study: unlike previous studies, our
-cameras were outfitted with a fish-eye lens in an attempt to capture as
-much of the children's field of view as possible. Thus, the field of
-view (FOV) of the fisheye lens used was larger (109 degrees horizontal x
-70 degrees vertical) than the FOV of the lens used in many previous
-studies; for example, in Fausey et al. (2016) the FOV was 69 x 41
-degrees. This larger field of view may have allowed the SAYcam cameras
-to capture not only the presence of a social partner's hands interacting
-with objects, but also the children's own hands, leading to more
-frequent hand detections.
+in view than have previously been reported (C. M. Fausey et al., 2016).
+We found this to be true across all ages, in both children, and
+regardless of whether we analyzed human annotations (on the 24K random
+subset) or OpenPose annotations on entire dataset. This is notable
+especially given that OpenPose showed relatively low recall for hands,
+indicating that this is still an underestimate of the proportion of
+hands in view. One reason this could be the case is the much larger
+field of view that was captured by the cameras used in this study:
+unlike previous studies, our cameras were outfitted with a fish-eye lens
+in an attempt to capture as much of the children's field of view as
+possible. Thus, the field of view (FOV) of the fisheye lens used was
+larger (109 degrees horizontal x 70 degrees vertical) than the FOV of
+the lens used in many previous studies; for example, in C. M. Fausey et
+al. (2016) the FOV was 69 x 41 degrees. This larger field of view may
+have allowed the SAYcam cameras to capture not only the presence of a
+social partner's hands interacting with objects, but also the children's
+own hands, leading to more frequent hand detections.
 
@@
 
-\caption[Density estimates for the child (left) and adult (right) hands that were detected int eh 24K random gold set]{Density estimates for the child (left) and adult (right) hands that were detected int eh 24K random gold set; each dot represents the center of a bounding box made by an adult participant.}\label{fig:density}
+\caption[Density estimates for the child (left) and adult (right) hands that were detected in teh 24K random gold set]{Density estimates for the child (left) and adult (right) hands that were detected in teh 24K random gold set; each dot represents the center of a bounding box made by an adult participant.}\label{fig:density}
 \end{figure}
@@
 of the hands in the random 24K sample were of children's own hands
-(compared to 8\% reported in Fausey et al. (2016)) suggesting that this
-difference in field of view did contribute substantially to the higher
-rate of hand detections in the frames. Heatmaps of the bounding boxes
-obtained from these annotations can be seen in Figure 3, showing that
-children's hands tended to appear in the lower half of the frames.
+(compared to 8\% reported in C. M. Fausey et al. (2016)) suggesting that
+this difference in field of view did contribute substantially to the
+higher rate of hand detections in the frames. Heatmaps of the bounding
+boxes obtained from these annotations can be seen in Figure 3, showing
+that children's hands tended to appear in the lower half of the frames.
 
@@
 a smaller, upper portion of the frame comparable to the field of view
-used in Fausey et al. (2016). To do so, we excluded hand detections that
-occurred in the bottom 40\% of the frame, while retaining all hand
-detections that occurred in the top 60\% of the frame. This coarse
-cropping of decreased the proportion of hand detections from
-0.3263743percent to 0.2156618 percent.
+used in C. M. Fausey et al. (2016). To do so, we excluded hand
+detections that occurred in the bottom 40\% of the frame, while
+retaining all hand detections that occurred in the top 60\% of the
+frame. This coarse cropping of decreased the proportion of hand
+detections from 0.3263743percent to 0.2156618 percent.
 
@@
 changes in the proportion of faces vs.~hands over age. To better
-approximate Fausey et al. (2016), we also restricted our analysis to the
-age range seen in Fausey et al. (2016), excluding videos when children
-were over 24 months of age, and indeed found that the proportion of
-faces vs.~hands declined modestly with age (see Table 1).
+approximate C. M. Fausey et al. (2016), we also restricted our analysis
+to the age range seen in C. M. Fausey et al. (2016), excluding videos
+when children were over 24 months of age, and indeed found that the
+proportion of faces vs.~hands declined modestly with age (see Table 1).
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrrr}
+  \hline
+ & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
+  \hline
+(Intercept) & -0.26 & 0.09 & -2.83 & 0.005 \\ 
+  scale(age\_months) & -0.15 & 0.00 & -225.40 & 0.000 \\ 
+   \hline
+\end{tabular}
+\caption{Model coefficients from a generalized linear mixed model predicting the proportion of faces vs. hands seen by infants.} 
+\end{table}
 
@@
 view in the videos from the youngest age ranges in each child,
-confirming previous findings (Fausey et al., 2016). This is particularly
-notable given that, in cross-sectional data, this effect seems to be
-most strongly driven by infants younger than 4 months of age (e.g.,
-Fausey 2016; Jayaraman, Fausey, \& Smith, 2015; Sugden, Mohamed-Ali, \&
-Moulson, 2014) who see both more frequent and more persistent faces
-(Jayaraman \& Smith, 2018).
+confirming previous findings (C. M. Fausey et al., 2016). This is
+particularly notable given that, in cross-sectional data, this effect
+seems to be most strongly driven by infants younger than 4 months of age
+(e.g., Fausey 2016; Jayaraman, Fausey, \& Smith, 2015; Sugden,
+Mohamed-Ali, \& Moulson, 2014) who see both more frequent and more
+persistent faces (Jayaraman \& Smith, 2018).
 
@@
 and size of people, hands, and faces, representing a 300-fold increase
-in data relative to prior work (Fausey et al., 2016). As these
+in data relative to prior work (C. M. Fausey et al., 2016). As these
 detections were imperfect compared to human annotators, fine-tuning
@@
 \hypertarget{refs}{}
+\hypertarget{ref-bambach2015lending}{}
+Bambach, S., Lee, S., Crandall, D. J., \& Yu, C. (2015). Lending a hand:
+Detecting hands and recognizing activities in complex egocentric
+interactions. In \emph{Proceedings of the ieee international conference
+on computer vision} (pp. 1949--1957).
+
 \hypertarget{ref-Cao2018openpose}{}
@@
 Fields. In \emph{ArXiv preprint arXiv:1812.08008}.
+
+\hypertarget{ref-clerkin2017}{}
+Clerkin, E. M., Hart, E., Rehg, J. M., Yu, C., \& Smith, L. B. (2017).
+Real-world visual statistics and infants' first-learned object names.
+\emph{Phil. Trans. R. Soc. B}, \emph{372}(1711), 20160055.
 
@@
 
-\hypertarget{ref-Gredeback2010}{}
-Gredeback, G., Fikke, L., \& Melinder, A. (2010). The development of
-joint visual attention: A longitudinal study of gaze following during
-interactions with mothers and strangers. \emph{Developmental Science},
-\emph{13}(6), 839--848.
+\hypertarget{ref-franchak2017see}{}
+Franchak, J. M., Kretch, K. S., \& Adolph, K. E. (2017). See and be
+seen: Infant--caregiver social looking during locomotor free play.
+\emph{Developmental Science}.
+
+\hypertarget{ref-franchak2011}{}
+Franchak, J. M., Kretch, K. S., Soska, K. C., \& Adolph, K. E. (2011).
+Head-mounted eye tracking: A new method to describe infant looking.
+\emph{Child Development}, \emph{82}(6), 1738--1750.
+
+\hypertarget{ref-frank2013}{}
+Frank, M. C., Simmons, K., Yurovsky, D., \& Pusiol, G. (2013).
+Developmental and postural changes in childrens visual access to faces.
+In \emph{Proceedings of the 35th annual meeting of the cognitive science
+society} (pp. 454--459).
+
+\hypertarget{ref-gredeback2008microstructure}{}
+Gredeb\wrapmf{\"{a}}ck, G., Theuring, C., Hauf, P., \& Kenward, B.
+(2008). The microstructure of infants' gaze as they view adult shifts in
+overt attention. \emph{Infancy}, \emph{13}(5), 533--543.
+
+\hypertarget{ref-james1890principles}{}
+James, W., Burkhardt, F., Bowers, F., \& Skrupskelis, I. K. (1890).
+\emph{The principles of psychology} (Vol. 1). Macmillan London.
 
@@
 
+\hypertarget{ref-kretch2014}{}
+Kretch, K. S., Franchak, J. M., \& Adolph, K. E. (2014). Crawling and
+walking infants see the world differently. \emph{Child Development},
+\emph{85}(4), 1503--1518.
+
 \hypertarget{ref-Sanchez2018}{}
@@
 
+\hypertarget{ref-sanchez2018postural}{}
+Sanchez, A., Long, B., Kraus, A. M., \& Frank, M. C. (2018). Postural
+developments modulate children's visual access to social information.
+
 \hypertarget{ref-Simon2017hand}{}
@@
 
+\hypertarget{ref-smith2011not}{}
+Smith, L. B., Yu, C., \& Pereira, A. F. (2011). Not your mother?s view:
+The dynamics of toddler visual experience. \emph{Developmental Science},
+\emph{14}(1), 9--17.
+
+\hypertarget{ref-smith2015contributions}{}
+Smith, L. B., Yu, C., Yoshida, H., \& Fausey, C. M. (2015).
+Contributions of head-mounted cameras to studying the visual
+environments of infants and young children. \emph{Journal of Cognition
+and Development}, \emph{16}(3), 407--419.
+
 \hypertarget{ref-Sugden2014}{}
-Sugden, N. A., Mohamed-Ali, M. I., \& Moulson, M. C. (n.d.). I spy with
+Sugden, N. A., Mohamed-Ali, M. I., \& Moulson, M. C. (2014). I spy with
 my little eye: Typical, daily exposure to faces documented from a
@@
 
+\hypertarget{ref-yoshida2008}{}
+Yoshida, H., \& Smith, L. (2008). What's in view for toddlers? Using a
+head camera to study visual experience. \emph{Infancy}, \emph{13},
+229--248.
+
+\hypertarget{ref-yu2013joint}{}
+Yu, C., \& Smith, L. B. (2013). Joint attention without gaze following:
+Human infants and their parents coordinate visual attention to objects
+through eye-hand coordination. \emph{PloS One}, \emph{8}(11).
+
 \bibliographystyle{apacite}

### 2020-01-30 paper/cogsci/paper_jan28.Rmd
updates to cogsci paper

@@
 Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants.
-Here, we examine the prevalence of faces and hands in a longitudinal collection of over 1400 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam].
-To analyze these naturalistic infant egocentric videos, we first validate the use of a modern convolutional neural network for pose detection (OpenPose) for the detection of faces and hands.
-We then apply this model to the entire dataset, finding a decrease in the proportion of faces vs.
-hands across age up to the end of the second year of life [@Fausey2016].
-In addition, we find considerable variability in the proportion of faces/hands viewed by children in different locations (e.g., living room vs.
-kitchen), demonstrating that variability across activity contexts may be a driving factor in the amount of social information that infants’ experience.
+Here, we examine the prevalence of faces and hands in a longitudinal collection of nearly 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam].
+To analyze these naturalistic infant egocentric videos, we first validated the use of a modern convolutional neural network for pose detection (OpenPose) for the detection of faces and hands.
+We then applied this model to the entire dataset, and found a higher proportion of hands in view than previous reported and a moderate decrease the proportion of faces in children's view across age.
+In addition, we found variability in the proportion of faces/hands viewed by different children in different locations (e.g., living room vs.
+kitchen), suggesting that individual activity contexts may shape the social information that infants experience.
 
@@
 library(xtable)
+library(lmerTest)
+
 theme_set(theme_few())
@@
 averted gaze [@Farroni2002], despite their limited acuity.
-As faces are likely to be an important conduit of social information that scaffolds cognitive development, cognitive scientists have long hypothesized that faces are prevalent in the visual experience of young infants.
+As faces are likely to be an important conduit of social information that scaffolds cognitive development, psychologists have long hypothesized that faces are prevalent in the visual experience of young infants.
 
-Yet until recently most hypotheses about infants’ visual experience have gone untested.
-Though parents and scientists alike have strong intuitions about what infant’s see, even the viewpoint of a walking child is not easily predicted by these intuitions [@clerkin2017; @franchak2011].
-By equipping infants and toddlers with head-mounted cameras, researchers have begun to document the infant egocentric perspective on the world.
+Yet until recently most hypotheses about infants' visual experience have gone untested.
+Though parents and scientists alike have strong intuitions about what infants see, even the viewpoint of a walking child is not easily predicted by these intuitions [@clerkin2017; @franchak2011].
+By equipping infants and toddlers with head-mounted cameras, researchers have begun to document the infant's egocentric perspective on the world.
 Using these methods, a growing body of work now demonstrates that the viewpoints of very young infants (less than 4 months of age) are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @Sugden2014; @Jayaraman2018].
 
-Beyond these early months,infants motor and cognitive abilities mature, leading to a vastly different perspectives on the world.
-For example, crawlers see fewer faces and hands than do walking children [@Sanchez2018; @franchak2017see; @kretch2014] as well as different view of objects [@smith2011not].
-Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, and their perspective starts to capture views of hands paired with the objects they are acting on [@Fausey2016].
+Beyond these early months, infants motor and cognitive abilities mature, leading to a vastly different perspectives on the world.
+For example, crawlers see fewer faces and hands than do walking children [@Sanchez2018; @franchak2017see; @kretch2014] as well as different views of objects [@smith2011not].
+Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, and their perspective starts to capture views of hands manipulating objects [@Fausey2016].
 In turn, caregivers may also start to use their hands with more communicative intent, directing infants attention by pointing and gesturing to different events and objects during play [@yu2013joint].
@@
 In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways.
-First, recordings were taken under a large variety of activity contexts [@roy2015predicting; @bruner1985role] encompassing infants’ viewpoints during both activities outside and inside the home.
-Even in other naturalistic datasets, the incredible variety in a typical infant’s experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth).
+First, recordings were taken under a large variety of activity contexts [@roy2015predicting; @bruner1985role] encompassing infants' viewpoints during both activities outside and inside the home.
+Even in other naturalistic datasets, the incredible variety in a typical infant's experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth).
 Second, the head-mounted cameras used in the SAYcam dataset captured a larger field of view than those typically used, allowing a more complete picture of the infant perspective.
@@
 
-With hundreds of hours of footage (>29M frames), however, this large dataset necessitates a shift to an automated annotation strategy.
+With hundreds of hours of footage (>40M frames), however, this large dataset necessitates a shift to an automated annotation strategy.
 Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that many frames are typically not inspected, even in the most comprehensive studies.
-For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand annotated (by four coders), totalling 103,383 frames (per coder)—an impressive number of annotations but nonetheless only 0.67% of the collected footage.
+For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand-annotated (by four coders), totalling 103,383 frames (per coder)—an impressive number of annotations but nonetheless only 0.67% of the collected footage.
 To address this challenge, we use a modern computer vision model of pose detection to automatically detect the presence of hands and faces from the infant egocentric viewpoint.
 Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints that operates well on scenes including multiple people, even if they are partially-occluded (see Figure 1).
+In prior work with egocentric videos, [@sanchez2018postural]  OpenPose performed comparably to other detectors specified for detecting only faces (MTCNN, @zhang2016).
 
 In the following paper, we first describe the dataset and validate the use of this model by comparing face and hand detections to a human-annotated set of 24,000 frames.
-Next, we report how the proportion of faces and hands changes across age in each of the three children in the dataset.
+Next, we report how the proportion of faces and hands changes with age in each of the three children in the dataset.
 We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the present cameras as well as a diversity of locations during which videos were recorded.
@@
 Videos[^1] with technical errors or that were not taken from the egocentric perspective were excluded from the dataset.
-While data collection for the third child (Y) is still ongoing, here we analyze `r num_videos` videos, with a total duration of `r num_hours` hours (>29 million frames).
+While data collection for the third child (Y) is still ongoing, here we analyze `r num_videos` videos, with a total duration of `r round(num_hours,2)` hours (>40 million frames).
 [^1]: All videos are available at https://nyu.databrary.org/volume/564
@@
 ```{r examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=3.5, set.cap.width=T, num.cols.cap=2, fig.align = "center", fig.cap = "Example frames taken from the dataset, illustrating variability in the infant perspective across different locations.
-OpenPose detections are shown overlaid on these images."}
+OpenPose detections are shown overlaid on these images (green dots = face, red dots = hands, orange dots = pose)."}
 examples <- png::readPNG("figs/modifiedOPfigure_v3.png")
 grid::grid.raster(examples)
-
 ```
@@
 This pose detector[^2] provided the locations of 18 body parts (ears, nose, wrists, etc.).
-The system uses a convolutional neural network for initial anatomical detection and subsequently applies part affinity fields for part association, producing a series of body part candidates.
-The candidates are then matched to a single individual and finally assembled into a pose.
+A convolutional neural network is used for initial anatomical detection, and part affinity fields are subsequently applied for part association to produce a series of body part candidates.
+Once these body part candidates are matched to a single individual in the frame, they are finally assembled into a pose.
 Thus, while we only make use of the outputs of the face and hand detections, the entire set of pose information from an individual is used to determine the presence of a face/hand, making the process much more robust to occlusion than methods optimized to detect only faces or hands.
-Specifically, we tagged frames with detected nose keypoints as having a face, and frames with a wrist keypoint were tagged as having a hand.
-
 [^2]: https://github.com/CMU-Perceptual-Computing-Lab/openpose
@@
   filter(label=="Adult hand")
+```
+
+```{r}
 
@@
   coord_fixed(ratio=1) +
-  # ggtitle('(A). Child hand density') +
+  ggtitle('A. Child hand density') +
   ylim(0,480) +
@@
   xlab('') +
-  theme_few(base_size=12) +
+  # theme_few(base_size=12) +
   theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
@@
   xlab('') +
-  theme_few(base_size=12) +
-    theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) 
-  # ggtitle('(B). Adult hand density') 
+  # theme_few(base_size=12) +
+    theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
+  ggtitle('B. Adult hand density')
 ```
 
-```{r density, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=4, fig.height=2, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in teh 24K random gold set; each dot represents the center of a bounding box made by an adult participant."}
-ggarrange(child_hand_plot, adult_hand_plot, nrow=1)
+```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3.5, fig.height=2, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant."}
+cowplot::plot_grid(child_hand_plot, adult_hand_plot, nrow=1)
 ```
@@
 For example, the infant perspective often contains non-canonical viewpoints of faces (e.g., looking up at a caregiver's chin) as well as partially-occluded or oblique viewpoints of both faces and hands.
-Furthermore, hand detection tends to be a somewhat harder problem than face detection [@simon2017hand; @bambach2015lending], and certainly one that has received less attention than face detection.
-We thus expected overall performance to be lower in these naturalistic videos than on either photos taken from the adult perspective or in egocentric videos in controlled, laboratory settings [@.g., @sanchez2018postural].
+Furthermore, hand detection tends to be a harder problem than face detection [@simon2017hand; @bambach2015lending], and has certainyl received less attention.
+We thus expected overall performance to be lower in these naturalistic videos than on either photos taken from the adult perspective or in egocentric videos in controlled, laboratory settings [e.g., @sanchez2018postural].
 
@@
 
-We suspected that this is in part because children’s own hands were often in view of the camera and unconnected to a pose—a notoriously challenging detection problem [@bambach2015lending].
-To assess this possibility, we obtained human annotations for a subsample of 9051 frames in which a hand was detected; participants (recruited via AMT) were asked to draw bounding boxes around children’s hands and adult’s hands.
-Overall, we found that almost half  of missed hand detections were of child hands.
+We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose—-a notoriously challenging detection problem [@bambach2015lending].
+To assess this possibility, we obtained human annotations for a subsample of 9051 frames in which a hand was detected; participants (recruited via AMT) were asked to draw bounding boxes around children’s and adult’s hands.
+Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)` percent of missed hand detections were of child hands.
 When frames with children's hands were removed from the gold set, recall did improve to `r hand_performance_adults[3]` somewhat.
-We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Figure 3.
+We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in (see Figure \ref{fig:handLocation}).
 
@@
 Thus, while OpenPose was trained on photographs from the adult perspective, this model still generalized relatively well to the egocentric infant viewpoint with no fine-tuning or post-processing of the detections.
+As these detections were imperfect compared to human annotators, fine-tuning these models to better optimize for the infant viewpoint remains an open avenue for future work.
+Standard computer vision models are rarely exposed to these naturalistic, egocentric viewpoints, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors.
 
@@
 
-```
-
-```{r}
 wide_cropped <- summary_by_age_cropped %>%
@@
          region = ifelse(region == "prop_faces","Face","Hands"))
+
+```
+
+```{r FacesAndHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3.5, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset.
+Data are binned by each week that the videos were filme and scaled by the number of frames in that age range.
+Dashed lines show the proportion of faces/hands in view when detections are restricted to the upper 60 percent of the FOV, reducing the contribution of children's own hands."}
 
@@
 We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands that were in view for each child.
-Data from videos were binned according to the age of the child (in weeks) (see Figure 2).
-First, when examining the younger age ranges (< 24 months), as in @Fausey2016, we saw that the proportion of faces vs.
-hands in view showed a moderate decrease across this age range, both when analyzing the random 24K frames as well as the entire dataset (see Figure 2A).
+Data from videos were binned according to the age of the child (in weeks).
+First, consistent with @Fausey2016, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:FacesAndHands}); we did not observe an increase in the proportion of hands in view, but rather a slight decrease (as quantified with two linear mixed-models, see Tables 1 & 2).
 
-However, the most striking result is a much greater proportion of hands in view than have previously been reported [@Fausey2016].
+However, the most striking result from these analyses is a much overall greater proportion of hands in view than have previously been reported [@Fausey2016].
 We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset) or OpenPose annotations on the entire dataset.
-This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this is still an underestimate of the proportion of hands in view.
-Nonetheless, one reason this could be the case is the much larger field of view that was captured by the cameras used in this study: unlike previous studies, our cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible.
-Thus, the field of view (FOV) of the fisheye lens used was larger (109 degrees horizontal x 70 degrees vertical) than the FOV of the lens used in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees.
-This larger field of view may have allowed the SAYcam cameras to capture not only the presence of a social partner’s hands interacting with objects, but also the children’s own hands, leading to these more frequent hand detections.
+This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may still be an underestimate of the proportion of hands in view.
+Nonetheless, one reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view of 109 degrees horizontal x 70 degrees verticall than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees.
+This larger FOV may have allowed the SAYcam cameras to capture not only the presence of a social partner’s hands interacting with objects, but also the children’s own hands, leading to more frequent hand detections.
 
-We thus re-analyzed the entire dataset while restricting our analysis to a smaller, upper portion of the frame comparable to the field of view used in @Fausey2016.
-To do so, we excluded hand detections that occurred in the bottom 40% of the frame, while retaining all hand detections that occurred in the top 60% of the frame.
-This coarse cropping of decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)`percent to `r round(mean(d_cropped$hand_detected),2)` percent, but only decreased face detections from `r round(mean(d_all$face_openpose),2)` to `r round(mean(d_cropped$face_detected),2)`.
-Within this modified field of view, we still observed, on average, more hand detections than face detections'.
-
-However, we also still observed a moderate decrease in the proportion of faces vs.
-hands in view across age.
-To quantify this trend, we fit a linear mixed model to the proportion of hands/faces observed, binned across the days in which the videos were filmed.
-T
-
- e foungain found that the proportion of faces vs.
-hands declined modestly with age (see Table 1).
-Note that @Fausey2016 also included data from very young infants (from 1-4 months of age), while here the youngest videos coming from S and A around 6 and 9 months of age, respectively.
+As children's hands tended to occur in the lower visual field (see Figure 2), we thus re-analyzed the entire dataset while restricting our analysis to the upper 60 percent of the field of view.
+When we excluded detections that occurred in the bottom 40% of the frame, this decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)`percent to `r round(mean(d_cropped$hand_detected),2)` percent, but only decreased face detections from `r round(mean(d_all$face_openpose),2)` to `r round(mean(d_cropped$face_detected),2)`.
+Nonetheless, within this modified field of view, we still observed, on average, more hand detections than face detections.
 
@@
   mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect) 
+summary_by_age_days_cropped$age_scale <- scale(summary_by_age_days_cropped$age_days, scale = FALSE)[,1] / 30.3
+
+summary_by_age_days <- d_all %>%
+  group_by(age_days,child_id) %>%
+  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_openpose), num_detect = length(face_openpose)) %>%
+  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect) 
+summary_by_age_days$age_scale <- scale(summary_by_age_days$age_days, scale = FALSE)[,1] / 30.3
 
@@
   filter(age_days < 730) ## less than 24 months
+summary_by_age_days_cropped_younger$age_scale <- scale(summary_by_age_days_cropped_younger$age_days, scale = FALSE)[,1] / 30.3
 ```
-###
-```{r}
-library(lmerTest)
-summary_by_age_days_cropped$age_scale <- scale(summary_by_age_days_cropped$age_days, scale = FALSE)[,1] / 30.3
-# summary_by_age_days_cropped_younger$age_scale <- scale(summary_by_age_days_cropped_younger$age_days, scale = FALSE)[,1] / 30.3
 
+```{r eval=FALSE}
+# run lmer models
 faces_model_full_age_out = summary(lmer(prop_faces ~ age_scale + (1 | child_id), data = summary_by_age_days_cropped))
+
 hands_model_full_age_out = summary(lmer(prop_hands ~ age_scale + (1 | child_id), data = summary_by_age_days_cropped))
@@
 
-```{r}
-xtable(faces_model_full_age_out$coefficients, digits=c(2,2,2,2,3,3),"Model coefficients from a generalized linear mixed model predicting the proportion of faces seen by infants.")
+```{r eval=FALSE}
+xtable(faces_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of faces seen by infants.")
 
-xtable(hands_model_full_age_out$coefficients, digits=c(2,2,2,2,3,3),"Model coefficients from a generalized linear mixed model predicting the proportion of hands seen by infants.")
+xtable(hands_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of hands seen by infants.")
 ```
 
-However, when we considered the entire age range, we also observed an unexpected trend in which the relative proportion of faces vs.
-hands increased again after 24 months of life; this trend was stronger in the full dataset.
-While we did not have any a priori hypotheses about this age range, we suspect that this could have to do with an increase in children’s independence from their caregiver as they master walking around and interacting with objects in the world on their own.
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrrrr}
+  \hline
+ & Estimate & Std. Err. & df & t value & Pr($>$$|$t$|$) \\ 
+  \hline
+(Int.) & 0.179 & 0.008 & 2.180 & 22.736 & 0.001 \\ 
+  Age & -0.002 & 0.001 & 402.024 & -3.138 & 0.002 \\ 
+   \hline
+\end{tabular}
+\caption{Model coefficients from a linear mixed model predicting the proportion of faces seen by infants.} 
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrrrr}
+  \hline
+ & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
+  \hline
+(Int.) & 0.238 & 0.011 & 1.913 & 22.359 & 0.002 \\ 
+  Age & -0.002 & 0.001 & 409.966 & -2.286 & 0.023 \\ 
+   \hline
+\end{tabular}
+\caption{Model coefficients from a linear mixed model predicting the proportion of hands seen by infants.} 
+\end{table}
 
@@
 
-```{r DetByLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3, fig.height=4, fig.cap = "Proportion of faces and hands by location in which egocentric videos were filmed; data from individual children are plotted separately (location annotations were not available for Y).
+```{r DetByLocation, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3.5, fig.cap = "Proportion of faces and hands by location in which egocentric videos were filmed; data from individual children are plotted separately (location annotations were not available for Y).
 Data are only taken from the top 60 percent of the frames so as to minimize the contribution of children’s own hands.
@@
   facet_grid(.~child_id)  +
-  scale_size_continuous(name = "Detections (Log 10)")
+  scale_size_continuous(name = "Detections (Log 10)") +
+  guides(scale=guide_legend(nrow=2,byrow=TRUE))
 ```
@@
 
-Broadly, the present analysis of this dense, longitudinal dataset has yielded a better understanding of infants' evolving access to social information.
-First, we found a relatively high proportion of faces in view in the videos from the youngest age ranges in each child, confirming previous findings [@Fausey2016].
-This is particularly notable given that, in cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age (e.g., Fausey 2016; Jayaraman, Fausey, & Smith, 2015; Sugden, Mohamed-Ali, & Moulson, 2014) who see both more frequent and more persistent faces (Jayaraman & Smith, 2018).
+The present analysis of this dense, longitudinal dataset has yielded a better understanding of infants' evolving access to social information.
+Confirming previous findings, we found a moderate decrease across age in the proportion of faces in view in the videos [@Fausey2016].
+This is particularly notable given that, in cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018].
 
-Second, we found considerable variability in the social information in view depending on the activity context in which children were present.
-Even within a given, well-defined context---mealtime---we found variability across individual children.
-Intuitively, there are at least three ways to feed a young child in a kitchen (i.e., forward facing the child in a high chair, holding the child outward, or sitting side by side with them) and these regularities in a child’s life may hold a larger influence over the amount of social information in view than previously considered.
+We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field of view to the upper visual field of the frames.
+One possibility is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be simply observing the actions of caregivers and other people in their environment.
+Further work that examines the variability in the social information in view across different activity contexts may help elucidate this new finding.
 
-Finally, we demonstrate the feasibility of using a modern, off-the-shelf computer vision model to vastly increase the efficiency of processing egocentric headcam footage, allowing us to annotate the entirety of very large datasets (here, >30 million frames) for the presence and size of people, hands, and faces, representing a 300-fold increase in data relative to prior work [@Fausey2016].
-As these detections were imperfect compared to human annotators, fine-tuning these models to better optimize for the infant viewpoint remains an open avenue for future work.
-Standard computer vision models are rarely exposed on these naturalistic, egocentric viewpoints, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors.
+Indeed, a coarse analysis based the location the videos were filmed in already highlights the variability of the the social information in view, both across locations and between individual children.
+Even within a given, well-defined context---e.g., mealtime in kitchens---there was considerable variability.
+Indeed, there are at least three ways to feed a young child in a kitchen: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side.
+Each of these positions offer the child differing degrees of visual access to face and hands, and likely tend to vary across individuals
 
-These analyses have highlighted the importance of considering the infants field-of-view when analyzing egocentric videos.
-In many frames children's own hands were likely visible, due to the wide field of view—capturing valuable information about what these children were interacting with in different contexts across the first few years of their life.
-Furthermore, though this choice more closely approximates children’s actual perspective, these viewpoints are still a proxy as we do not know where in the frames children are allocating their attention.
+Thus, these analyses underscore how the questions of how, when, from whom, and what data we sample become critically important when we attempt to draw conclusions about the regularities of experience.
+Further, while unprecedented in size, this dataset still has many limitations.
+These videos only represent a small portion of the everyday experience of these three children, all of whom come from relatively privileged households in western societies and thus are not representative of the global population.
+Any idiosyncrasies in how and when these particular families chose to film these videos undoubtedly influences the variability seen here.
+Finally, without eye-tracking data, we still do not know if children are attending to the social information in their visual field.
 
-Indeed, the questions of how, when, from whom, and what data we sample become critically important when we attempt to construct naturalistic datasets, and we would be remiss if we did not acknowledge the limitations of the present dataset.
-While these data are longitudinal, they are only sampled from representative of few children, all growing up in relatively privileged households in western societies.
-Any idiosyncrasies in how and when these particular families chose to film these videos undoubtedly influences the variability seen here.
 Nonetheless, we believe that these advances in methodologies and datasets are a step in the right direction.
-The large-scale analysis of dense datasets—collected with different fields of view, cameras and from many different laboratories—has the potential to create generalizable conclusions about the regularities of infant experience that scaffold learning.
+The present paper demonstrates the feasibility of using a modern, off-the-shelf computer vision model to annotate the entirety of a very large dataset (here, >40M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to prior work [e.g., @Fausey2016].
+We propose that the large-scale analysis of these kinds of dense datasets—-collected with different fields of view, cameras and from many different laboratories—-have the potential to create generalizable conclusions about the regularities of infant experience that scaffold learning.
 
 # Acknowledgements
-
-We would like to thank X and Y for helpful comments, and...
+Blinded.
 
 # References 
-
 ```{r}

### 2020-01-30 analysis/analysis_bb_fulldataset_2.Rmd
code to start bb analyses in full data, part2

--- 2020-01-30 analysis/analysis_bb_fulldataset.Rmd
@@
   mutate(age_day_bin = as.numeric(as.character(d$age_day_bin)))
-```
-
-```{r}
-
-bin_size = 6
-min_age = 6
-max_age = 30
-bin_starts = seq(min_age, max_age+1,bin_size)
-bins = c(bin_starts)
-
+# 
+# bin_size = 6
+# min_age = 6
+# max_age = 30
+# bin_starts = seq(min_age, max_age+1,bin_size)
+# bins = c(bin_starts)
 ```
@@
   summarize(num_poses = sum(label=="pose"), avg_area = mean(area), avg_x = mean(center_x), avg_y = mean(center_y))
-# 
-# save(hands_by_size_by_frame, file="../data/hands_by_size_by_frame.RData")
-# save(faces_by_size_by_frame, file="../data/faces_by_size_by_frame.RData")
-# save(poses_by_size_by_frame, file="../data/poses_by_size_by_frame.RData")
 ```
@@
   mutate(months_binned = cut(age_months, bins, labels=c("6m-12m","12m-18m","18m-24m","24m-32m")))
+
+save(hands_by_size_by_frame, file="../data/hands_by_size_by_frame.RData")
+save(faces_by_size_by_frame, file="../data/faces_by_size_by_frame.RData")
+save(poses_by_size_by_frame, file="../data/poses_by_size_by_frame.RData")
 
@@
 bb_all <- bb_all %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(d$age_day_bin)))
 
@@
   mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))
+  mutate(age_day_bin = as.numeric(as.character(d$age_day_bin)))
 
@@
 ```{r}
-subset_A <- poses_by_size_by_frame %>%
-  filter(child_id == "A") %>%
-  filter(age_days < 400)
+summary_by_age <- bb_all %>%
+  group_by(age_day_bin, child_id) %>%
+  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect, face_or_hand = sum(person_openpose)/ num_detect, face_and_hand = sum(both_openpose)/ num_detect)
 
-subset_A <- subset_A %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))
 ```
-
-```{r}
-pose_summary_by_age_days <- poses_by_size_by_frame %>%
-  group_by(age_days, child_id) %>%
-  summarize(num_detect = length(frame), avg_area_age = mean(avg_area), avg_people = mean(num_poses)) %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
-
-face_summary_by_age_days <- faces_by_size_by_frame %>%
-  group_by(age_days, child_id) %>%
-  summarize(num_detect = length(frame), avg_area_age = mean(avg_area), avg_faces = mean(num_faces))
-
-hand_summary_by_age_days <- hands_by_size_by_frame %>%
-  group_by(age_days, child_id) %>%
-  summarize(num_detect = length(frame), avg_area_age = mean(avg_area), avg_faces = mean(num_hands))
-
-ggplot(pose_summary_by_age_days, aes(x=age_days, y=log(avg_area_age), col=child_id, size=num_detect)) +
-  geom_point(alpha=.2) +
-  geom_smooth(span=10)
-
-ggplot(face_summary_by_age_days, aes(x=age_days, y=log(avg_area_age), col=child_id, size=num_detect)) +
-  geom_point(alpha=.2) +
-  geom_smooth(span=10)
-
-ggplot(hand_summary_by_age_days, aes(x=age_days, y=log(avg_area_age), col=child_id, size=num_detect)) +
-  geom_point(alpha=.2) +
-  geom_smooth() 
-```

### 2020-01-30 paper/cogsci/paper_jan28.Rmd
latest updates to cogsci 2020

@@
 ---
-title: "Detecting social information in a dense dataset of infants’ natural visual experience"
+title: "Detecting social information in a dense dataset \\ of infants’ natural visual experience"
 bibliography: library.bib
@@
 Second, the head-mounted cameras used in the SAYcam dataset captured a larger field of view than those typically used, allowing a more complete picture of the infant perspective.
-While head-mounted cameras with a more restricted field of view do represent where infants are foveating most of the time [@yoshida2008, @smith2015contributions], they may fail to capture short saccades to either faces or hands in the periphery, as the timescale of head movements is much longer.
+While head-mounted cameras with a more restricted field of view do represent where infants are foveating most of the time [@yoshida2008; @smith2015contributions], they may fail to capture short saccades to either faces or hands in the periphery, as the timescale of head movements is much longer.
 
@@
   xlab('') +
-  # theme_few(base_size=12) +
+  theme_few(base_size=8) +
   theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
@@
   xlab('') +
-  # theme_few(base_size=12) +
+  theme_few(base_size=8) +
     theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
   ggtitle('B. Adult hand density')
-```
-
-```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3.5, fig.height=2, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant."}
-cowplot::plot_grid(child_hand_plot, adult_hand_plot, nrow=1)
 ```
@@
 To assess this possibility, we obtained human annotations for a subsample of 9051 frames in which a hand was detected; participants (recruited via AMT) were asked to draw bounding boxes around children’s and adult’s hands.
-Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)` percent of missed hand detections were of child hands.
-When frames with children's hands were removed from the gold set, recall did improve to `r hand_performance_adults[3]` somewhat.
+Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100` percent of missed hand detections were of child hands.
+When frames with children's hands were removed from the gold set, recall did improve somewhat to`r round(hand_performance_adults[3],2)`.
 We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in (see Figure \ref{fig:handLocation}).
@@
 Standard computer vision models are rarely exposed to these naturalistic, egocentric viewpoints, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors.
+
+```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3.5, fig.height=2, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant."}
+cowplot::plot_grid(child_hand_plot, adult_hand_plot, nrow=1)
+```
 
@@
 
+```{r}
+## replace NAs for computing prop hands in cropped anlaysis
+d_cropped <- d_cropped %>%
+  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) 
+```
+
 As children's hands tended to occur in the lower visual field (see Figure 2), we thus re-analyzed the entire dataset while restricting our analysis to the upper 60 percent of the field of view.
-When we excluded detections that occurred in the bottom 40% of the frame, this decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)`percent to `r round(mean(d_cropped$hand_detected),2)` percent, but only decreased face detections from `r round(mean(d_all$face_openpose),2)` to `r round(mean(d_cropped$face_detected),2)`.
-Nonetheless, within this modified field of view, we still observed, on average, more hand detections than face detections.
+When we excluded detections that occurred in the bottom 40% of the frame, this decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)*100`% to `r round(mean(d_cropped$hand_detected),2)*100`%, but only decreased face detections from `r round(mean(d_all$face_openpose),2)*100`% to `r round(mean(d_cropped$face_detected),3)*100` % Nonetheless, within this modified field of view, we still observed, on average, more hand detections than face detections (see Figure \ref{fig:FacesAndHands}).
 
@@
 
-```{r DetByLocation, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3.5, fig.cap = "Proportion of faces and hands by location in which egocentric videos were filmed; data from individual children are plotted separately (location annotations were not available for Y).
+```{r DetByLocation, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands by location in which egocentric videos were filmed; data from individual children are plotted separately (location annotations were not available for Y).
 Data are only taken from the top 60 percent of the frames so as to minimize the contribution of children’s own hands.
@@
 Indeed, there are at least three ways to feed a young child in a kitchen: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side.
-Each of these positions offer the child differing degrees of visual access to face and hands, and likely tend to vary across individuals
+Each of these positions offer the child differing degrees of visual access to face and hands.
+Thus, even while the social information in view could be variable across children in different activitiy contexts, they could be stable within children's typical experience.
 
-Thus, these analyses underscore how the questions of how, when, from whom, and what data we sample become critically important when we attempt to draw conclusions about the regularities of experience.
+Thus, these analyses underscore the questions of how, when, from whom, and what data we sample; these choices become critically important when we attempt to draw conclusions about the regularities of experience.
 Further, while unprecedented in size, this dataset still has many limitations.
@@
 Any idiosyncrasies in how and when these particular families chose to film these videos undoubtedly influences the variability seen here.
-Finally, without eye-tracking data, we still do not know if children are attending to the social information in their visual field.
+Finally, without eye-tracking data, we do not know if children are attending to the social information in their visual field.
 
@@
 The present paper demonstrates the feasibility of using a modern, off-the-shelf computer vision model to annotate the entirety of a very large dataset (here, >40M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to prior work [e.g., @Fausey2016].
-We propose that the large-scale analysis of these kinds of dense datasets—-collected with different fields of view, cameras and from many different laboratories—-have the potential to create generalizable conclusions about the regularities of infant experience that scaffold learning.
+We propose that the large-scale analysis of these kinds of dense datasets, collected with different fields of view, cameras and from many different laboratories, have the potential to create generalizable conclusions about the regularities of infant experience that scaffold learning.
 

### 2020-01-30 paper/cogsci/paper_jan28.Rmd
minor edits

@@
 
-Beyond these early months, infants motor and cognitive abilities mature, leading to a vastly different perspectives on the world.
+Beyond these early months, infants' motor and cognitive abilities mature, leading to a vastly different perspectives on the world.
 For example, crawlers see fewer faces and hands than do walking children [@Sanchez2018; @franchak2017see; @kretch2014] as well as different views of objects [@smith2011not].
@@
 
-Here, we examine the social information present in the infant visual perspective--the presence of faces and hands--by analyzing a longitudinal collection of over 1400 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam].
+Here, we examine the social information present in the infant visual perspective--the presence of faces and hands--by analyzing a longitudinal collection of 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam].
 In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways.
@@
 Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints that operates well on scenes including multiple people, even if they are partially-occluded (see Figure 1).
-In prior work with egocentric videos, [@sanchez2018postural]  OpenPose performed comparably to other detectors specified for detecting only faces (MTCNN, @zhang2016).
+In prior work with egocentric videos, [@sanchez2018postural]  OpenPose performed comparably to other detectors specified for detecting only faces [MTCNN, @zhang2016].
 
@@
 We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the present cameras as well as a diversity of locations during which videos were recorded.
+<!-- could preview the results in this paragraph if space permits -->
 
@@
 
-To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / hits + false alarms), recall (hits / hits + misses), and f-score (the harmonic mean of precision and recall).
+To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (the harmonic mean of precision and recall).
 In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`.

### 2020-01-30 paper/cogsci/paper_jan28.Rmd
Smoothing edits to text, revising Figure 4 to include cropped hands (same filenames)

@@
 ---
-title: "Detecting social information in a dense dataset \\ of infants’ natural visual experience"
+title:  |
+  | Detecting social information in a dense database
+  | of infants’ natural visual experience
 bibliography: library.bib
@@
                       message=F, sanitize = T)
-
 ```
@@
 library(langcog)
-library(viridis)
-library(magick)
 library(stringr)
-library(egg)
-library(xtable)
 library(lmerTest)
@@
 theme_set(theme_few())
-
 # renv::init()
@@
 Videos captured by the headcam were 640x480 pixels, and a fisheye lens was attached to the camera to increase the field of view to approximately 109 degrees horizontal x 70 degrees vertical.
-Videos[^1] with technical errors or that were not taken from the egocentric perspective were excluded from the dataset.
+Videos ^[All videos are available at https://nyu.databrary.org/volume/564 ] with technical errors or that were not taken from the egocentric perspective were excluded from the dataset.
 While data collection for the third child (Y) is still ongoing, here we analyze `r num_videos` videos, with a total duration of `r round(num_hours,2)` hours (>40 million frames).
-[^1]: All videos are available at https://nyu.databrary.org/volume/564
 
@@
 To automatically annotate the millions of frames in SAYcam, we use OpenPose [@Cao2018openpose; @Simon2017hand].
-This pose detector[^2] provided the locations of 18 body parts (ears, nose, wrists, etc.).
-A convolutional neural network is used for initial anatomical detection, and part affinity fields are subsequently applied for part association to produce a series of body part candidates.
-Once these body part candidates are matched to a single individual in the frame, they are finally assembled into a pose.
+This pose detector ^[https://github.com/CMU-Perceptual-Computing-Lab/openpose] provided the locations of 18 body parts (ears, nose, wrists, etc.).
+A convolutional neural network was used for initial anatomical detection, and part affinity fields were subsequently applied for part association to produce a series of body part candidates.
+Once these body part candidates were matched to a single individual in the frame, they were finally assembled into a pose.
 Thus, while we only make use of the outputs of the face and hand detections, the entire set of pose information from an individual is used to determine the presence of a face/hand, making the process much more robust to occlusion than methods optimized to detect only faces or hands.
-[^2]: https://github.com/CMU-Perceptual-Computing-Lab/openpose
 
@@
  ## load gold sample annotations
- load('../../data_cogsci/gold_sample_annotations_2020-01-29.RData') #d_all
+ load('../../data_cogsci/gold_sample_annotations_2020-01-29.RData') # gold_sample
 
@@
 
-# render examples of missed hands
+# can render examples of missed hands if desired
+# library(magick)
 # dir.create(paste0('det_examples/missed_hand'), recursive=TRUE)
@@
 ```{r}
-
-## plot centers of the bounding boxes made for child and adult hands
+### plot centers of the bounding boxes made for child and adult hands
 child_hand_plot <- ggplot(child_hands, aes(x=center_x, y=center_y)) +
@@
 As has been observed in other studies on automated annotation of headcam data [e.g.
-@frank2013, @sanchez2018postural, @bambach2015lending], detection tasks that are easy in third-person video can be quite challenging in egocentric videos, due to difficult angles and sizes as well as substantial occlusion.
+@frank2013; @sanchez2018postural; @bambach2015lending], detection tasks that are easy in third-person video can be quite challenging in egocentric videos, due to difficult angles and sizes as well as substantial occlusion.
 For example, the infant perspective often contains non-canonical viewpoints of faces (e.g., looking up at a caregiver's chin) as well as partially-occluded or oblique viewpoints of both faces and hands.
-Furthermore, hand detection tends to be a harder problem than face detection [@simon2017hand; @bambach2015lending], and has certainyl received less attention.
+Furthermore, hand detection tends to be a harder problem than face detection [@simon2017hand; @bambach2015lending], and has certainly received less attention.
 We thus expected overall performance to be lower in these naturalistic videos than on either photos taken from the adult perspective or in egocentric videos in controlled, laboratory settings [e.g., @sanchez2018postural].
@@
 To assess this possibility, we obtained human annotations for a subsample of 9051 frames in which a hand was detected; participants (recruited via AMT) were asked to draw bounding boxes around children’s and adult’s hands.
-Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100` percent of missed hand detections were of child hands.
-When frames with children's hands were removed from the gold set, recall did improve somewhat to`r round(hand_performance_adults[3],2)`.
-We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in (see Figure \ref{fig:handLocation}).
+Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100` % of missed hand detections were of child hands.
+When frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`.
+We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Figure \ref{fig:handLocation}.
 
@@
   mutate(approach = "cropped",
-         region = ifelse(region == "prop_faces","Face","Hands"))
+         region = ifelse(region == "prop_faces","Face","Hands"))  %>%
+  filter(num_detect > 5000) # eliminate one data point that skews scaling
 
@@
   mutate(approach = "uncropped",
-         region = ifelse(region == "prop_faces","Face","Hands"))
+         region = ifelse(region == "prop_faces","Face","Hands"))  %>%
+  filter(num_detect > 5000) # eliminate one data point that skews scaling
 
@@
 Data are binned by each week that the videos were filme and scaled by the number of frames in that age range.
-Dashed lines show the proportion of faces/hands in view when detections are restricted to the upper 60 percent of the FOV, reducing the contribution of children's own hands."}
+Dashed lines show the proportion of faces/hands in view when detections are restricted to the upper 60 percent of the FOV, reducing the contribution of children's own hands.
+Bins with less"}
 
@@
   facet_grid(.~child_id) + 
-  ggthemes::scale_color_solarized(name = "Detection") + 
-  scale_size_continuous(name = "Detections (Log 10)")
+  ggthemes::scale_color_solarized(name = "") + 
+  scale_size_continuous(name = "Detections (Log 10)") +
+  theme(legend.text=element_text(size=8))
 ```
@@
 Data from videos were binned according to the age of the child (in weeks).
-First, consistent with @Fausey2016, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:FacesAndHands}); we did not observe an increase in the proportion of hands in view, but rather a slight decrease (as quantified with two linear mixed-models, see Tables 1 & 2).
+First, consistent with @Fausey2016, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:FacesAndHands}); in contrast, we did not observe an increase in the proportion of hands in view, but rather a slight decrease.
+These effects were quantified with two separate linear mixed-models (see Tables 1 & 2).^[Face/hand detections were binned across each week of filming.
+Participant's age was converted into months and centered for these analyses.
+Random slopes for the effect of age by child led to a singular fit and were removed from both analyses; see full model specification in accompanying codebase.]
 
@@
 This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may still be an underestimate of the proportion of hands in view.
-Nonetheless, one reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view of 109 degrees horizontal x 70 degrees verticall than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees.
+Nonetheless, one reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees.
 This larger FOV may have allowed the SAYcam cameras to capture not only the presence of a social partner’s hands interacting with objects, but also the children’s own hands, leading to more frequent hand detections.
@@
 
-As children's hands tended to occur in the lower visual field (see Figure 2), we thus re-analyzed the entire dataset while restricting our analysis to the upper 60 percent of the field of view.
-When we excluded detections that occurred in the bottom 40% of the frame, this decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)*100`% to `r round(mean(d_cropped$hand_detected),2)*100`%, but only decreased face detections from `r round(mean(d_all$face_openpose),2)*100`% to `r round(mean(d_cropped$face_detected),3)*100` % Nonetheless, within this modified field of view, we still observed, on average, more hand detections than face detections (see Figure \ref{fig:FacesAndHands}).
+As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the upper 60% of the field of view.
+This decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)*100`% to `r round(mean(d_cropped$hand_detected),2)*100`%, but only decreased face detections from `r round(mean(d_all$face_openpose),2)*100`% to `r round(mean(d_cropped$face_detected),3)*100` %.
+Note that this cropping likely removes both the majority of detections of children's own hands but does also remove some detections of adult hands(see Figure \ref{fig:handLocation}).
+Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see Figure \ref{fig:FacesAndHands}).
 
@@
 
-summary_by_age_days_cropped_younger <- summary_by_age_days_cropped %>%
-  filter(age_days < 730) ## less than 24 months
-summary_by_age_days_cropped_younger$age_scale <- scale(summary_by_age_days_cropped_younger$age_days, scale = FALSE)[,1] / 30.3
 ```
@@
 ```{r eval=FALSE}
-# run lmer models
+# run lmer models -- faces over age
 faces_model_full_age_out = summary(lmer(prop_faces ~ age_scale + (1 | child_id), data = summary_by_age_days_cropped))
 
+# hands over age
 hands_model_full_age_out = summary(lmer(prop_hands ~ age_scale + (1 | child_id), data = summary_by_age_days_cropped))
+
+# explicit modeling of faces vs. hands and interaction with age
+# main effect of ages and regions; no interaction.
+wide_cropped_age_days <- summary_by_age_days_cropped %>%
+  gather(region, prop, prop_faces, prop_hands) %>%
+  mutate(approach = "cropped",
+         region = ifelse(region == "prop_faces","Face","Hands"))
+
+diff_model_full_age_out = summary(lmer(prop ~ region*age_scale + (1 | child_id), data = wide_cropped_age_days))
 ```
@@
 ```{r}
-load('../../data_cogsci/saycam_metadata.RData')
+load('../../data_cogsci/saycam_metadata.RData') # meta
 
@@
 ```
-
-How does variability across different contexts influence the social information in the infant view? 
-Intuitively, some activities in different contexts may be characterized by a much higher proportion of faces (e.g., diaper changes in bedrooms) than others (e.g., playtime in the living room).
-We thus next examined variation in presence of hands and faces across different locations.
-Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location that the videos were filmed in.
-`r videos_included` were filmed in single location, representing 17 percent of the dataset and over 5 million frames (see @SAYcam).
-Activities varied somewhat predictability by these contexts: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.
-Overall, we found that the proportion of faces vs.
-hands varied across filming locations, and, to some extent, across children.
-For example, while both A and S saw a relatively similar proportion of faces vs.
-hands in the bedroom, they saw quite different amounts of faces vs.
-hands in kitchen.
 
@@
 levels_to_modify[12] = 'Outside' # Off Property
+# reset levels for both cropped/uncropped
 levels(d_by_location_cropped$Location) <- levels_to_modify
@@
   group_by(Location,child_id,age_day_bin) %>%
-  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_detected), num_detect = length(hand_detected))  %>%
+  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_openpose), prop_hands_cropped = mean(hand_detected), num_detect = length(hand_detected))  %>%
   group_by(Location) %>%
-  filter(num_detect > 12000) %>% ## 18000 frames = 10 minutes of video at 30 fps %>%
-  mutate(faces_vs_hands = prop_faces - prop_hands)
+  filter(num_detect > 12000)  ## 18000 frames = 10 minutes of video at 30 fps %>%
 
+## Compute CIs for faces/hands by each location, and then merge back raw data so they can be plotted together
+## Get rid of any locations where we didn't have enough data to make a CI (not more than 1 age_bin)
 hands_to_plot_cropped <- face_hand_by_location_cropped %>%
   group_by(Location, child_id) %>%
+  multi_boot_standard(col="prop_hands_cropped") %>%
+  mutate(region = "Hands (Cropped)") %>%
+  ungroup %>%
+  left_join(face_hand_by_location_cropped) %>%
+  mutate(prop = prop_hands_cropped) %>%
+  select(-prop_faces, -prop_hands, -prop_hands_cropped) %>%
+  filter(!is.na(ci_lower))
+
+hands_to_plot <- face_hand_by_location_cropped %>%
+  group_by(Location, child_id) %>%
   multi_boot_standard(col="prop_hands") %>%
-  mutate(region = "Hand") %>%
+  mutate(region = "Hands") %>%
   ungroup %>%
@@
   mutate(prop = prop_hands) %>%
-  select(-prop_faces, -prop_hands) %>%
+  select(-prop_faces, -prop_hands, -prop_hands_cropped) %>%
   filter(!is.na(ci_lower))
@@
   mutate(prop = prop_faces) %>%
-  select(-prop_faces, -prop_hands) %>%
+  select(-prop_faces, -prop_hands, -prop_hands_cropped) %>%
   filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter
 
-both_to_plot <- faces_to_plot_cropped %>%
+all_to_plot <- faces_to_plot_cropped %>%
   full_join(hands_to_plot_cropped) %>%
+  full_join(hands_to_plot) %>%
   group_by(Location) %>%
@@
 
-```{r DetByLocation, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands by location in which egocentric videos were filmed; data from individual children are plotted separately (location annotations were not available for Y).
-Data are only taken from the top 60 percent of the frames so as to minimize the contribution of children’s own hands.
-Each dot represents data from a week in which videos were filmed and are scaled by the number of frames in that datapoint."}
+```{r DetByLocation, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands by location in which egocentric videos were filmed; each panel represents data from an individual child (location annotations were not yet available for Y).
+Each dot represents data from a week in which videos were filmed and are scaled by the number of frames."}
 
-ggplot(both_to_plot, aes(x = Location, y = mean, col=region)) + 
-  geom_point(aes(x=Location, y=prop, size=log10(num_detect)), alpha=.1, position = position_dodge(width=.3)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
+ggplot(all_to_plot, aes(x = Location, y = mean, col=region)) + 
+  geom_point(aes(x=Location, y=prop, size=log10(num_detect)), alpha=.1, position = position_dodge(width=.6)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper, linetype=region),position = position_dodge(width=.6)) +
   coord_flip() + 
@@
   xlab('')+
-  ggthemes::scale_color_solarized(name = "Detection") + 
+  theme_few(base_size=9) +
   theme(legend.position = "bottom") +
@@
   scale_size_continuous(name = "Detections (Log 10)") +
-  guides(scale=guide_legend(nrow=2,byrow=TRUE))
+  scale_linetype_manual(values=c("solid", "solid","dashed"), name = "") +
+  scale_color_manual(values = c("#268bd2", "#dc322f","#DC7977"), name = "") +
+  theme(legend.text=element_text(size=8))
+
 ```
+
+How does variability across different contexts influence the social information in the infant view? 
+Intuitively, some activities in different contexts may be characterized by a much higher proportion of faces (e.g., diaper changes in bedrooms) than others (e.g., playtime in the living room).
+We thus next examined variation in presence of hands and faces across different locations.
+Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location that the videos were filmed in.
+`r videos_included` were filmed in single location, representing 17 percent of the dataset and over 5 million frames (see @SAYcam).
+Activities varied somewhat predictability by these contexts: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.
+Overall, we found that the proportion of faces vs.
+hands varied across filming locations, and, to some extent, across children.
+For example, while both A and S saw a relatively similar proportion of faces vs.
+hands in the bedroom, they saw quite different amounts of faces vs.
+hands in kitchen (see Figure \ref{fig:DetByLocation}).
 
@@
 
-We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field of view to the upper visual field of the frames.
+We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field of view to the upper 60% of the visual field of the videos.
 One possibility is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be simply observing the actions of caregivers and other people in their environment.
@@
 Indeed, a coarse analysis based the location the videos were filmed in already highlights the variability of the the social information in view, both across locations and between individual children.
-Even within a given, well-defined context---e.g., mealtime in kitchens---there was considerable variability.
-Indeed, there are at least three ways to feed a young child in a kitchen: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side.
+Even within a given, well-defined context---e.g., mealtime in kitchens---there was considerable variability: S saw more faces than A in the kitchen, and more faces in the kitchen than in other locations.
+This is likely because there are at least three ways to feed a young child in a kitchen: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side.
 Each of these positions offer the child differing degrees of visual access to face and hands.
-Thus, even while the social information in view could be variable across children in different activitiy contexts, they could be stable within children's typical experience.
+Thus, even while the social information in view may be variable across children in different activitiy contexts, these analyses suggest they could be stable within children's typical experience.
 
-Thus, these analyses underscore the questions of how, when, from whom, and what data we sample; these choices become critically important when we attempt to draw conclusions about the regularities of experience.
-Further, while unprecedented in size, this dataset still has many limitations.
+Overall, these analyses underscore the importance of how, when, from whom, and what data we sample; these choices become central when we attempt to draw conclusions about the regularities of experience.
+Indeed, while unprecedented in size, this dataset still has many limitations.
 These videos only represent a small portion of the everyday experience of these three children, all of whom come from relatively privileged households in western societies and thus are not representative of the global population.
-Any idiosyncrasies in how and when these particular families chose to film these videos undoubtedly influences the variability seen here.
-Finally, without eye-tracking data, we do not know if children are attending to the social information in their visual field.
+Any idiosyncrasies in how and when these particular families chose to film these videos also undoubtedly influences the variability seen here.
+And without eye-tracking data, we do not know if children are attending to the social information in their visual field.
 
-Nonetheless, we believe that these advances in methodologies and datasets are a step in the right direction.
+Nonetheless, we believe that these advances in datasets and methodologies represent a step in the right direction.
 The present paper demonstrates the feasibility of using a modern, off-the-shelf computer vision model to annotate the entirety of a very large dataset (here, >40M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to prior work [e.g., @Fausey2016].

### 2020-01-31 paper/cogsci/paper_jan28.Rmd
figure edit + GD edits; same filenames

@@
 Beyond these early months, infants' motor and cognitive abilities mature, leading to a vastly different perspectives on the world.
-For example, crawlers see fewer faces and hands than do walking children [@Sanchez2018; @franchak2017see; @kretch2014] as well as different views of objects [@smith2011not].
+For example, crawlers see fewer faces and hands than do walking children [@sanchez2018postural; @franchak2017see; @kretch2014] as well as different views of objects [@smith2011not].
 Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, and their perspective starts to capture views of hands manipulating objects [@Fausey2016].
@@
 OpenPose detections are shown overlaid on these images (green dots = face, red dots = hands, orange dots = pose)."}
-examples <- png::readPNG("figs/modifiedOPfigure_v3.png")
+examples <- png::readPNG("figs/modifiedOPfigure_v4.png")
 grid::grid.raster(examples)
@@
 We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field of view to the upper 60% of the visual field of the videos.
-One possibility is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be simply observing the actions of caregivers and other people in their environment.
-Further work that examines the variability in the social information in view across different activity contexts may help elucidate this new finding.
+Why might this be the case?
+One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment.
+During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly--leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1).
+Indeed, using the same pose detector on videos from in-lab play sessions, @sanchez2018postural found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age.
+Work that directly examines the variability in the social information in view across more vs.
+less structured activity contexts could further test this idea.
 
-Indeed, a coarse analysis based the location the videos were filmed in already highlights the variability of the the social information in view, both across locations and between individual children.
-Even within a given, well-defined context---e.g., mealtime in kitchens---there was considerable variability: S saw more faces than A in the kitchen, and more faces in the kitchen than in other locations.
-This is likely because there are at least three ways to feed a young child in a kitchen: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side.
+A coarse analysis based the location the videos were filmed in further highlights the variability of the social information in view during different activites, showing differences across locations and between individual children.
+Within a given, well-defined context---e.g., mealtime in kitchens---S saw more faces than A, and S  more faces in the kitchen than in other locations.
+This variability likely stems from the fact that thereare at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side.
 Each of these positions offer the child differing degrees of visual access to face and hands.
-Thus, even while the social information in view may be variable across children in different activitiy contexts, these analyses suggest they could be stable within children's typical experience.
+While the social information in view may be variable across children in different activitiy contexts, these analyses suggest they could be stable within a given child's day-to-day experience.
 
@@
 Nonetheless, we believe that these advances in datasets and methodologies represent a step in the right direction.
-The present paper demonstrates the feasibility of using a modern, off-the-shelf computer vision model to annotate the entirety of a very large dataset (here, >40M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to prior work [e.g., @Fausey2016].
+The present paper demonstrates the feasibility of using a modern, off-the-shelf computer vision model to annotate the entirety of a very large dataset (here, >40M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to prior work.
 We propose that the large-scale analysis of these kinds of dense datasets, collected with different fields of view, cameras and from many different laboratories, have the potential to create generalizable conclusions about the regularities of infant experience that scaffold learning.

### 2020-01-31 preprocessing/preprocess_datasets.Rmd
figure edit + GD edits; same filenames

@@
 
+```{r}
+### Code to start to see if it maatters how many people are in the frame
+age_info <- d_cropped %>%
+  select(vid_name, frame, child_id, age_days)
+
+one_person <- detections_cropped_SA %>%
+  filter(num_people < 2) %>%
+  left_join(d_cropped) %>%
+  group_by(age_days, child_id) %>%
+  summarize(prop_hands = mean(hand_detected), prop_faces = mean(face_detected))
+
+wide_one_person <- one_person %>%
+  gather(region, prop, prop_hands, prop_faces)
+
+ggplot(wide_one_person, aes(x=age_days, y=prop, col=region)) +
+  geom_point() +
+  geom_smooth() +
+  facet_grid(.~child_id) +
+  ggtitle('hands vs faces (cropped) -- frames with only 1 person')
+```
+
 # Other data files that get cleaned up for cogsci

### 2020-01-31 paper/cogsci/paper_jan28.Rmd
Incorporating GK's edits

@@
 
-Here, we examine the social information present in the infant visual perspective--the presence of faces and hands--by analyzing a longitudinal collection of 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam].
+Here, we examine the social information present in the infant visual perspective--the presence of faces and hands--by analyzing a longitudinal collection of nearly 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam].
 In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways.
@@
 With hundreds of hours of footage (>40M frames), however, this large dataset necessitates a shift to an automated annotation strategy.
-Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that many frames are typically not inspected, even in the most comprehensive studies.
+Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that most frames are typically not inspected, even in the most comprehensive studies.
 For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand-annotated (by four coders), totalling 103,383 frames (per coder)—an impressive number of annotations but nonetheless only 0.67% of the collected footage.
@@
 We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose—-a notoriously challenging detection problem [@bambach2015lending].
-To assess this possibility, we obtained human annotations for a subsample of 9051 frames in which a hand was detected; participants (recruited via AMT) were asked to draw bounding boxes around children’s and adult’s hands.
+To assess this possibility, we obtained human annotations for the entire subsample of 9051 frames in which a hand was detected; participants (recruited via AMT) were asked to draw bounding boxes around children’s and adult’s hands.
 Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100` % of missed hand detections were of child hands.
@@
 
-```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3.5, fig.height=2, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant."}
+```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3.5, fig.height=2, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant.
+Brighter values indicate more detections."}
 cowplot::plot_grid(child_hand_plot, adult_hand_plot, nrow=1)
@@
 ```{r FacesAndHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3.5, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset.
-Data are binned by each week that the videos were filme and scaled by the number of frames in that age range.
+Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range.
 Dashed lines show the proportion of faces/hands in view when detections are restricted to the upper 60 percent of the FOV, reducing the contribution of children's own hands.
@@
 Nonetheless, one reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees.
-This larger FOV may have allowed the SAYcam cameras to capture not only the presence of a social partner’s hands interacting with objects, but also the children’s own hands, leading to more frequent hand detections.
+This larger FOV may have allowed the SAYcam cameras to capture not only the presence of a social partner’s hands interacting with objects or gestures, but also the children’s own hands, leading to more frequent hand detections.
 
@@
 As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the upper 60% of the field of view.
-This decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)*100`% to `r round(mean(d_cropped$hand_detected),2)*100`%, but only decreased face detections from `r round(mean(d_all$face_openpose),2)*100`% to `r round(mean(d_cropped$face_detected),3)*100` %.
-Note that this cropping likely removes both the majority of detections of children's own hands but does also remove some detections of adult hands(see Figure \ref{fig:handLocation}).
+This decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)*100`% to `r round(mean(d_cropped$hand_detected),2)*100`%, but only decreased face detections from `r round(mean(d_all$face_openpose),2)*100`% to `r round(mean(d_cropped$face_detected),3)*100`%.
+Note that this cropping likely removes both the majority of detections of children's own hands but does also remove some detections of adult hands (see Figure \ref{fig:handLocation}), as especially as OpenPose was biased to miss children's hands when they were in view.
 Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see Figure \ref{fig:FacesAndHands}).
@@
 Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location that the videos were filmed in.
-`r videos_included` were filmed in single location, representing 17 percent of the dataset and over 5 million frames (see @SAYcam).
-Activities varied somewhat predictability by these contexts: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.
+`r videos_included` were filmed in single location, representing 17 percent of the dataset and over 5 million frames [@SAYcam].
+Activities varied somewhat predictably by these contexts: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.
 Overall, we found that the proportion of faces vs.
@@
 
-We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field of view to the upper 60% of the visual field of the videos.
+We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field of view to the upper 60% of the visual field of the videos to make the analyses more comparable to previous work [@Fausey2016].
 Why might this be the case?
@@
 
-A coarse analysis based the location the videos were filmed in further highlights the variability of the social information in view during different activites, showing differences across locations and between individual children.
+A coarse analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activites, showing differences across locations and between individual children.
 Within a given, well-defined context---e.g., mealtime in kitchens---S saw more faces than A, and S  more faces in the kitchen than in other locations.

### 2020-02-01 paper/cogsci/paper_jan28.Rmd
incoporate edits from MCF; add chi2 analyses code for locations

@@
 abstract: >
-        The faces and hands of infants' caregivers and other social partners offer a rich source of social and causal information that may be critical for infants' cognitive and linguistic development.
+        The faces and hands of caregivers and other social partners offer a rich source of social and causal information that may be critical for infants' cognitive and linguistic development.
 Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants.
@@
 library(langcog)
+library(lsr) 
 library(stringr)
@@
 Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, and their perspective starts to capture views of hands manipulating objects [@Fausey2016].
-In turn, caregivers may also start to use their hands with more communicative intent, directing infants attention by pointing and gesturing to different events and objects during play [@yu2013joint].
+In turn, caregivers may also start to use their hands with more communicative intent, directing infants' attention by pointing and gesturing to different events and objects during play [@yu2013joint].
 
-Here, we examine the social information present in the infant visual perspective--the presence of faces and hands--by analyzing a longitudinal collection of nearly 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam].
+Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of nearly 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYCAM dataset [@SAYcam].
 In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways.
@@
 Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints that operates well on scenes including multiple people, even if they are partially-occluded (see Figure 1).
-In prior work with egocentric videos, [@sanchez2018postural]  OpenPose performed comparably to other detectors specified for detecting only faces [MTCNN, @zhang2016].
+In prior work with egocentric videos, [@sanchez2018postural] OpenPose performed comparably to other detectors specified for detecting only faces.
 
-In the following paper, we first describe the dataset and validate the use of this model by comparing face and hand detections to a human-annotated set of 24,000 frames.
+In this paper, we first describe the dataset and validate the use of this model by comparing face and hand detections to a human-annotated set of 24,000 frames.
 Next, we report how the proportion of faces and hands changes with age in each of the three children in the dataset.
-We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the present cameras as well as a diversity of locations during which videos were recorded.
-<!-- could preview the results in this paragraph if space permits -->
+We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the head cameras as well as a diversity of locations in which videos were recorded.
 
@@
 
-## Assessing automated social annotations
-
-### Computer vision model
-To automatically annotate the millions of frames in SAYcam, we use OpenPose [@Cao2018openpose; @Simon2017hand].
+## Detection Method
+To automatically annotate the millions of frames in SAYcam, we used OpenPose [@Cao2018openpose; @Simon2017hand].
 This pose detector ^[https://github.com/CMU-Perceptual-Computing-Lab/openpose] provided the locations of 18 body parts (ears, nose, wrists, etc.).
@@
 Once these body part candidates were matched to a single individual in the frame, they were finally assembled into a pose.
-Thus, while we only make use of the outputs of the face and hand detections, the entire set of pose information from an individual is used to determine the presence of a face/hand, making the process much more robust to occlusion than methods optimized to detect only faces or hands.
+Thus, while we only made use of the outputs of the face and hand detections, the entire set of pose information from an individual was used to determine the presence of a face/hand, making the process much more robust to occlusion than methods optimized to detect only faces or hands.
+Note, however, that these face/hand detections are reliant on the detection of at least a partial pose, so some very up-close views of faces/hands may go undetected.
 
-### Manual annotation strategy
-To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A).
-Frames were jointly annotated for the presence of faces and hands.
-A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated 3150 frames; agreement with the primary coder was >95%.
-
-### Detection accuracy for faces and hands
+## Detection Validation
 
@@
  ## load gold sample annotations
- load('../../data_cogsci/gold_sample_annotations_2020-01-29.RData') # gold_sample
+ load('../../data_cogsci/gold_sample_annotations2020-01-31.RData') # gold_sample, pre-filtered
 
@@
   xlab('') +
-  theme_few(base_size=8) +
+  theme_few(base_size=6) +
   theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
@@
   xlab('') +
-  theme_few(base_size=8) +
+  theme_few(base_size=6) +
     theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
@@
 
+To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A).
+Frames were jointly annotated for the presence of faces and hands by one author.
+A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated 3150 frames; agreement with the primary coder was >95%.
+
 As has been observed in other studies on automated annotation of headcam data [e.g.
@@
 For example, the infant perspective often contains non-canonical viewpoints of faces (e.g., looking up at a caregiver's chin) as well as partially-occluded or oblique viewpoints of both faces and hands.
-Furthermore, hand detection tends to be a harder problem than face detection [@simon2017hand; @bambach2015lending], and has certainly received less attention.
+Furthermore, hand detection tends to be a harder problem than face detection [@Simon2017hand; @bambach2015lending].
 We thus expected overall performance to be lower in these naturalistic videos than on either photos taken from the adult perspective or in egocentric videos in controlled, laboratory settings [e.g., @sanchez2018postural].
@@
 To assess this possibility, we obtained human annotations for the entire subsample of 9051 frames in which a hand was detected; participants (recruited via AMT) were asked to draw bounding boxes around children’s and adult’s hands.
-Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100` % of missed hand detections were of child hands.
+Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100`% of missed hand detections were of child hands.
 When frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`.
@@
 As these detections were imperfect compared to human annotators, fine-tuning these models to better optimize for the infant viewpoint remains an open avenue for future work.
-Standard computer vision models are rarely exposed to these naturalistic, egocentric viewpoints, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors.
+Standard computer vision models are rarely trained on the egocentric viewpoint, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors.
 
@@
 
-## Access to social information 
-### Changes across age
+# Results
+## Access to social information across age
 
 ```{r}
+vid_info <- d_all %>%
+  select(vid_name, frame, age_days, child_id)
+
+## summary stats for gold sample detections
+summary_by_age_gold <- gold_sample %>%
+  left_join(vid_info) %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+  group_by(age_day_bin, child_id) %>%
+  summarize(num_detect = length(face_present_ketan), prop_faces = sum(face_present_ketan) / num_detect,  prop_hands = sum(hand_present_ketan) / num_detect)
+
 ## Make summary stats for cropped and uncropped detedctions
@@
   summarize(num_detect = length(face_openpose), prop_faces = sum(face_detected) / num_detect,  prop_hands = sum(hand_detected) / num_detect)
+
+##
+wide_gold <- summary_by_age_gold %>%
+  gather(region, prop, prop_faces, prop_hands) %>%
+  mutate(approach = "gold", region = ifelse(region == "prop_faces","Face","Hands"))  %>%
+  filter(!is.na(child_id)) # weird video
 
@@
 Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range.
-Dashed lines show the proportion of faces/hands in view when detections are restricted to the upper 60 percent of the FOV, reducing the contribution of children's own hands.
-Bins with less"}
+Dashed lines show estimated trend lines from proportion of faces/hands in view when detections are restricted to the upper 60 percent of the FOV, reducing the contribution of children's own hands; dotted lines show estimated trend lines for human annotations on the 24K gold set."}
 
@@
               lty = 2, span=10, se = FALSE) +
+  geom_smooth(data = wide_gold, aes(weight = num_detect),
+              lty = 3, span=10, se = FALSE) +
   ylab('Proportion Detections') + 
@@
   ylim(0,.5) +
-  theme(legend.position="bottom") +
   facet_grid(.~child_id) + 
+  theme_few(base_size=9) +
   ggthemes::scale_color_solarized(name = "") + 
   scale_size_continuous(name = "Detections (Log 10)") +
-  theme(legend.text=element_text(size=8))
+  theme(legend.text=element_text(size=8)) +
+  theme(legend.position="bottom")
+
 ```
@@
 Data from videos were binned according to the age of the child (in weeks).
-First, consistent with @Fausey2016, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:FacesAndHands}); in contrast, we did not observe an increase in the proportion of hands in view, but rather a slight decrease.
+First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:FacesAndHands}); in contrast, we did not observe an increase in the proportion of hands in view, but rather a slight decrease.
 These effects were quantified with two separate linear mixed-models (see Tables 1 & 2).^[Face/hand detections were binned across each week of filming.
@@
 However, the most striking result from these analyses is a much overall greater proportion of hands in view than have previously been reported [@Fausey2016].
-We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset) or OpenPose annotations on the entire dataset.
-This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may still be an underestimate of the proportion of hands in view.
+We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Figure \ref{fig:FacesAndHands}) or OpenPose annotations on the entire dataset (see solid lines in Figure \ref{fig:FacesAndHands}).
+This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may be an underestimate of the proportion of hands in view.
 Nonetheless, one reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees.
@@
 
-As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the upper 60% of the field of view.
-This decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)*100`% to `r round(mean(d_cropped$hand_detected),2)*100`%, but only decreased face detections from `r round(mean(d_all$face_openpose),2)*100`% to `r round(mean(d_cropped$face_detected),3)*100`%.
-Note that this cropping likely removes both the majority of detections of children's own hands but does also remove some detections of adult hands (see Figure \ref{fig:handLocation}), as especially as OpenPose was biased to miss children's hands when they were in view.
-Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see Figure \ref{fig:FacesAndHands}).
+As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the upper 60% of the field of view, decreasing the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)*100`% to `r round(mean(d_cropped$hand_detected),2)*100`%, but only decreased face detections from `r round(mean(d_all$face_openpose),2)*100`% to `r round(mean(d_cropped$face_detected),3)*100`%.
+This cropping likely removed both the majority of detections of children's own hands but does also remove some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
+Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:FacesAndHands}).
 
@@
 
-### Variability by Location 
+## Access to social information in different locations
 ```{r}
@@
   group_by(Location) %>%
-  filter(num_detect > 12000)  ## 18000 frames = 10 minutes of video at 30 fps %>%
+  filter(num_detect > 12000)  ##
 
@@
 
+```{r}
+### Chi-squared tests for location variability
+d_by_location_cropped_mini_S <- d_by_location_cropped %>%
+  group_by(Location) %>%
+  mutate(num_detect = length(hand_detected))  %>%
+  filter(num_detect > 0)  %>%
+  filter(child_id == "S") %>%
+  select(Location, face_openpose,hand_detected) # using cropped hands here
+
+d_by_location_cropped_mini_A <- d_by_location_cropped %>%
+  group_by(Location) %>%
+  mutate(num_detect = length(hand_detected))  %>%
+  filter(num_detect > 0)  %>% #
+  filter(child_id == "A") %>%
+  select(Location, face_openpose, hand_detected)
+
+## drop levels
+d_by_location_cropped_mini_S$Location = droplevels(d_by_location_cropped_mini_S$Location)
+d_by_location_cropped_mini_A$Location = droplevels(d_by_location_cropped_mini_A$Location)
+
+## make smaller dataframes for just faces/hands
+d_by_location_cropped_mini_S_face <- d_by_location_cropped_mini_S %>%
+  select(Location, face_openpose)
+
+d_by_location_cropped_mini_S_hand <- d_by_location_cropped_mini_S %>%
+  select(Location, hand_detected)
+
+d_by_location_cropped_mini_A_face <- d_by_location_cropped_mini_A %>%
+  select(Location, face_openpose)
+
+d_by_location_cropped_mini_A_hand <- d_by_location_cropped_mini_A %>%
+  select(Location, hand_detected)
+
+# output (runs chi-squared tests in summary)
+faces_S_loc = summary(table(d_by_location_cropped_mini_S_face))
+hands_S_loc = summary(table(d_by_location_cropped_mini_S_hand))
+faces_A_loc = summary(table(d_by_location_cropped_mini_A_face))
+hands_A_loc = summary(table(d_by_location_cropped_mini_A_hand))
+
+# effect size estimates
+# cramersV(table(d_by_location_cropped_mini_S_face))
+# cramersV(table(d_by_location_cropped_mini_S_hand))
+# cramersV(table(d_by_location_cropped_mini_A_face))
+# cramersV(table(d_by_location_cropped_mini_A_hand))
+
+```
+
 ```{r DetByLocation, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands by location in which egocentric videos were filmed; each panel represents data from an individual child (location annotations were not yet available for Y).
@@
 We thus next examined variation in presence of hands and faces across different locations.
-Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location that the videos were filmed in.
-`r videos_included` were filmed in single location, representing 17 percent of the dataset and over 5 million frames [@SAYcam].
+Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location they were filmed in.
+Of these, `r videos_included` videos were filmed in single location, representing 17 percent of the dataset and over 5 million frames.
 Activities varied somewhat predictably by these contexts: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.
 Overall, we found that the proportion of faces vs.
-hands varied across filming locations, and, to some extent, across children.
+hands varied across filming locations, and, to some extent, across children; separate chi-squared tests for each child and detection type revealed significant variability in detections by location in each case ^[all p<.001, see accompanying codebase].
 For example, while both A and S saw a relatively similar proportion of faces vs.
 hands in the bedroom, they saw quite different amounts of faces vs.
-hands in kitchen (see Figure \ref{fig:DetByLocation}).
+hands in kitchens (see Figure \ref{fig:DetByLocation}).
 
@@
 
-The present analysis of this dense, longitudinal dataset has yielded a better understanding of infants' evolving access to social information.
-Confirming previous findings, we found a moderate decrease across age in the proportion of faces in view in the videos [@Fausey2016].
-This is particularly notable given that, in cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018].
+Here, we analyzed the social information in view in a dense, longitudinal dataset, applying computer-vision models to quantify the proportion of hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.
+This analysis has yielded a better understanding of infants' evolving access to social information.
+We found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016].
+However, this finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018].
 
-We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field of view to the upper 60% of the visual field of the videos to make the analyses more comparable to previous work [@Fausey2016].
+We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field-of-view to the upper 60% of the visual field of the videos to make the viewpoints comparable to those of headcams used in previous work [@Fausey2016].
 Why might this be the case?
 One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment.
-During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly--leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1).
+During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly---leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1).
 Indeed, using the same pose detector on videos from in-lab play sessions, @sanchez2018postural found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age.
@@
 A coarse analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activites, showing differences across locations and between individual children.
-Within a given, well-defined context---e.g., mealtime in kitchens---S saw more faces than A, and S  more faces in the kitchen than in other locations.
-This variability likely stems from the fact that thereare at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side.
+Within a given, well-defined context---e.g., mealtime in kitchens---S saw more faces than A, and S saw more faces in the kitchen than in other locations.
+This variability likely stems from the fact that there are at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side.
 Each of these positions offer the child differing degrees of visual access to face and hands.
@@
 Nonetheless, we believe that these advances in datasets and methodologies represent a step in the right direction.
-The present paper demonstrates the feasibility of using a modern, off-the-shelf computer vision model to annotate the entirety of a very large dataset (here, >40M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to prior work.
-We propose that the large-scale analysis of these kinds of dense datasets, collected with different fields of view, cameras and from many different laboratories, have the potential to create generalizable conclusions about the regularities of infant experience that scaffold learning.
+The present paper demonstrates the feasibility of using a modern computer vision model to annotate the entirety of a very large dataset (here, >40M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to prior work.
+We propose that the large-scale analysis of dense datasets, collected with different fields of view, cameras and from many different laboratories, will lead to generalizable conclusions about the regularities of infant experience that scaffold learning.
 

### 2020-02-01 analysis/one_person_frames_check.R

@@ -1,0 +1,44 @@
+
+summary_by_age_cropped <- d_cropped %>%
+  replace_na(list(hand_detected = FALSE, face_detected = FALSE, num_people = 0)) %>%
+  # filter(num_people < 2) %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+  group_by(age_day_bin,child_id) %>%
+  summarize(num_detect = length(face_openpose), num_people = mean(num_people), Face = sum(face_detected) / num_detect,  Hands_Cropped = sum(hand_detected) / num_detect, Hands = sum(hand_openpose) / num_detect)
+
+wide <- summary_by_age_cropped_one_person %>%
+  gather(region, prop, Face, Hands_Cropped, Hands)
+
+
+ggplot(summary_by_age_cropped, 
+       aes(x=age_day_bin, y=num_people, 
+           size=log10(num_detect))) +
+  geom_point(alpha=.2) +
+  geom_smooth(span=10, aes(weight = num_detect)) + 
+  ylab('Proportion People Detected') + 
+  xlab('Age (Months)') +
+  ylim(0,.5) +
+  theme(legend.position="bottom") +
+  facet_grid(.~child_id) + 
+  ggthemes::scale_color_solarized(name = "") + 
+  scale_size_continuous(name = "Detections (Log 10)") +
+  theme(legend.text=element_text(size=8))
+
+
+ggplot(wide, 
+       aes(x=age_day_bin, y=prop, 
+           size=log10(num_detect),
+           col=region)) +
+  geom_point(alpha=.2) +
+  geom_smooth(span=10, aes(weight = num_detect)) + 
+  # geom_smooth(data = wide_cropped, aes(weight = num_detect),
+  # lty = 2, span=10, se = FALSE) +
+  ylab('Proportion Detections') + 
+  xlab('Age (Months)') +
+  ylim(0,.5) +
+  theme(legend.position="bottom") +
+  facet_grid(.~child_id) + 
+  ggthemes::scale_color_solarized(name = "") + 
+  scale_size_continuous(name = "Detections (Log 10)") +
+  theme(legend.text=element_text(size=8))

### 2020-02-02 paper/cogsci/paper_jan28.Rmd
changed Fig 3 figure legend, minor edits, condensed refs

@@
 Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints that operates well on scenes including multiple people, even if they are partially-occluded (see Figure 1).
-In prior work with egocentric videos, [@sanchez2018postural] OpenPose performed comparably to other detectors specified for detecting only faces.
+In prior work examining egocentric videos, OpenPose performed comparably to other modern face detection models [@sanchez2018postural].
 
@@
   geom_point(alpha=.2) +
-  geom_smooth(span=10, aes(weight = num_detect)) + 
-  geom_smooth(data = wide_cropped, aes(weight = num_detect),
+  geom_smooth(span=10, aes(weight = num_detect), show.legend = FALSE) + # geom_smooth(show.legend = FALSE) or move these below legend?
+  geom_smooth(data = wide_cropped, aes(weight = num_detect), show.legend = FALSE, 
               lty = 2, span=10, se = FALSE) +
-  geom_smooth(data = wide_gold, aes(weight = num_detect),
+  geom_smooth(data = wide_gold, aes(weight = num_detect), show.legend = FALSE,
               lty = 3, span=10, se = FALSE) +
@@
 Overall, we found that the proportion of faces vs.
-hands varied across filming locations, and, to some extent, across children; separate chi-squared tests for each child and detection type revealed significant variability in detections by location in each case ^[all p<.001, see accompanying codebase].
+hands varied across filming locations, and, to some extent, across children; separate chi-squared tests for each child and detection type revealed significant variability in detections by location in each case ^[all *p*<.001, see accompanying codebase].
 For example, while both A and S saw a relatively similar proportion of faces vs.
@@
 
-Here, we analyzed the social information in view in a dense, longitudinal dataset, applying computer-vision models to quantify the proportion of hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.
+Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the proportion of hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.
 This analysis has yielded a better understanding of infants' evolving access to social information.

### 2020-02-03 paper/cogsci/paper_initial_submission_blinded.Rmd
cleaned paper repo, added data links, last typos, rendered pdfs

--- 2020-02-02 paper/cogsci/paper_jan28.Rmd
@@
 author-information: >
-    \author{{\large \bf Bria Long (bria@stanford.edu)} 
-    \AND {\large \bf George Kachergis (kachergis@stanford.edu)} 
-    \AND {\large \bf Ketan Jay Agarwal (agrawalk@stanford.edu)} 
-    \AND {\large \bf Michael C. Frank (mcfrank@stanford.edu)} \\ 
-    Department of Psychology, Street Address \\ Stanford, CA 91305 USA}
 
@@
 Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants.
-Here, we examine the prevalence of faces and hands in a longitudinal collection of nearly 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam].
-To analyze these naturalistic infant egocentric videos, we first validated the use of a modern convolutional neural network for pose detection (OpenPose) for the detection of faces and hands.
+Here, we examine the prevalence of faces and hands in a longitudinal collection of nearly 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYCam dataset [@SAYcam].
+To analyze these naturalistic infant egocentric videos, we first validated the use of a modern convolutional neural network of pose detection (OpenPose) for the detection of faces and hands.
 We then applied this model to the entire dataset, and found a higher proportion of hands in view than previous reported and a moderate decrease the proportion of faces in children's view across age.
@@
 
-Beyond these early months, infants' motor and cognitive abilities mature, leading to a vastly different perspectives on the world.
+Beyond these early months, infants' motor and cognitive abilities mature, leading to vastly different perspectives on the world.
 For example, crawlers see fewer faces and hands than do walking children [@sanchez2018postural; @franchak2017see; @kretch2014] as well as different views of objects [@smith2011not].
@@
 
-Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of nearly 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYCAM dataset [@SAYcam].
+Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of nearly 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYCam dataset [@SAYcam].
 In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways.
@@
 Even in other naturalistic datasets, the incredible variety in a typical infant's experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth).
-Second, the head-mounted cameras used in the SAYcam dataset captured a larger field of view than those typically used, allowing a more complete picture of the infant perspective.
+Second, the head-mounted cameras used in the SAYCam dataset captured a larger field of view than those typically used, allowing a more complete picture of the infant perspective.
 While head-mounted cameras with a more restricted field of view do represent where infants are foveating most of the time [@yoshida2008; @smith2015contributions], they may fail to capture short saccades to either faces or hands in the periphery, as the timescale of head movements is much longer.
@@
 ## Detection Method
-To automatically annotate the millions of frames in SAYcam, we used OpenPose [@Cao2018openpose; @Simon2017hand].
-This pose detector ^[https://github.com/CMU-Perceptual-Computing-Lab/openpose] provided the locations of 18 body parts (ears, nose, wrists, etc.).
-A convolutional neural network was used for initial anatomical detection, and part affinity fields were subsequently applied for part association to produce a series of body part candidates.
+To automatically annotate the millions of frames in SAYCam, we used a pose detector, OpenPose ^[https://github.com/CMU-Perceptual-Computing-Lab/openpose]  [@Cao2018openpose; @Simon2017hand], which provided the locations of 18 body parts (ears, nose, wrists, etc.).
+To do so, a convolutional neural network was used for initial anatomical detection, and part affinity fields were subsequently applied for part association to produce a series of body part candidates.
 Once these body part candidates were matched to a single individual in the frame, they were finally assembled into a pose.
-Thus, while we only made use of the outputs of the face and hand detections, the entire set of pose information from an individual was used to determine the presence of a face/hand, making the process much more robust to occlusion than methods optimized to detect only faces or hands.
+Thus, while we only made use of the outputs of the face and hand detections, the entire set of pose information from an individual was used to determine the presence of a face/hand, making the process more robust to occlusion than methods optimized to detect only faces or hands.
 Note, however, that these face/hand detections are reliant on the detection of at least a partial pose, so some very up-close views of faces/hands may go undetected.
@@
 For example, the infant perspective often contains non-canonical viewpoints of faces (e.g., looking up at a caregiver's chin) as well as partially-occluded or oblique viewpoints of both faces and hands.
-Furthermore, hand detection tends to be a harder problem than face detection [@Simon2017hand; @bambach2015lending].
+Further, hand detection tends to be a harder computational problem than face detection [@Simon2017hand; @bambach2015lending].
 We thus expected overall performance to be lower in these naturalistic videos than on either photos taken from the adult perspective or in egocentric videos in controlled, laboratory settings [e.g., @sanchez2018postural].
@@
 In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.
+
+```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3.5, fig.height=2, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant.
+Brighter values indicate more detections."}
+cowplot::plot_grid(child_hand_plot, adult_hand_plot, nrow=1)
+```
 
@@
 Standard computer vision models are rarely trained on the egocentric viewpoint, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors.
-
-```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3.5, fig.height=2, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant.
-Brighter values indicate more detections."}
-cowplot::plot_grid(child_hand_plot, adult_hand_plot, nrow=1)
-```
 
@@
 
-```{r FacesAndHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3.5, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset.
+```{r FacesAndHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset.
 Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range.
@@
 
-We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands that were in view for each child.
-Data from videos were binned according to the age of the child (in weeks).
+We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands that were in view for each child.^[All analyses and preprocessed data files for this paper are avaliable at https://tinyurl.com/detecting-social-info] Data from videos were binned according to the age of the child (in weeks).
 First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:FacesAndHands}); in contrast, we did not observe an increase in the proportion of hands in view, but rather a slight decrease.
@@
 Nonetheless, one reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees.
-This larger FOV may have allowed the SAYcam cameras to capture not only the presence of a social partner’s hands interacting with objects or gestures, but also the children’s own hands, leading to more frequent hand detections.
+This larger FOV may have allowed the SAYCam cameras to capture not only the presence of a social partner’s hands interacting with objects or gestures, but also the children’s own hands, leading to more frequent hand detections.
 
 ```{r}
-## replace NAs for computing prop hands in cropped anlaysis
+# replace NAs with FALSE to compare proportion hands detected
 d_cropped <- d_cropped %>%
@@
 As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the upper 60% of the field of view, decreasing the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)*100`% to `r round(mean(d_cropped$hand_detected),2)*100`%, but only decreased face detections from `r round(mean(d_all$face_openpose),2)*100`% to `r round(mean(d_cropped$face_detected),3)*100`%.
-This cropping likely removed both the majority of detections of children's own hands but does also remove some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
+This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
 Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:FacesAndHands}).
@@
 We found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016].
-However, this finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018].
+This finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018].
 
@@
 This variability likely stems from the fact that there are at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side.
-Each of these positions offer the child differing degrees of visual access to face and hands.
+Each of these positions offer the child differing degrees of visual access to faces and hands.
 While the social information in view may be variable across children in different activitiy contexts, these analyses suggest they could be stable within a given child's day-to-day experience.

### 2020-04-17 get_bounding_boxes_per_vid.py
run on sherlock to save bounding boxes for each video from numpy arrays

@@ -1,0 +1,80 @@
+import os
+import numpy as np
+import pandas as pd
+
+# load flattened numpy arrays per video, extracts bounding boxes for hands and faces
+# per frame, and saves as long format CSV (one row per bounding box, maximum 9 per frame)
+
+VID_PATH = "/scratch/groups/mcfrank/Home_Headcam_new/openpose_flattened_whole" # /scratch/groups/mcfrank/Home_Headcam_new/openpose_flattened_whole
+OUT_PATH = "/scratch/groups/mcfrank/Home_Headcam_new/bounding_boxes/"
+#VID_PATH = "openpose_flattened"
+#f = "A_20130531_0818_01.npy" # for testing
+
+frame_size = {'x':640, 'y':480} # pixels; keypoint x,y coords are normalized 0-1, but go out of frame occasionall
+# min=-.22, max=1.16
+
+files = os.listdir(VID_PATH)
+
+# 130 for pose (18), face (70), L hand (21), and R hand (21) keypoints, in that order
+
+def get_bounding_box(X, Y):
+	left = np.min(X)
+	top = np.max(Y) # is (0,0) top or bottom left? assume bottom left for now -- check python
+	height = top - np.min(Y)
+	width = np.max(X) - left
+	return([height, width, left, top])
+
+def get_face_hand_bounding_boxes(detection):
+	# (X, Y, confidence) x 130 keypoints
+	X = detection[0]
+	Y = detection[1]
+	conf = detection[2]
+	pose_x = X[:18]
+	pose_y = Y[:18]
+	face_x = X[18:88]
+	face_y = Y[18:88]
+	Lhand_x = X[88:109]
+	Lhand_y = Y[88:109]
+	Rhand_x = X[109:]
+	Rhand_y = Y[109:]
+	bbs = [get_bounding_box(pose_x, pose_y) + [np.mean(conf[:18])], 
+		get_bounding_box(face_x, face_y) + [np.mean(conf[18:88])], 
+		get_bounding_box(Lhand_x, Lhand_y) + [np.mean(conf[88:109])], 
+		get_bounding_box(Rhand_x, Rhand_y) + [np.mean(conf[109:])]]
+	return bbs # could add mean confidences for face and each hand
+	# return height, width, left, top
+
+col_names = ["frame", "person", "label", "height", "width", "left", "top", "mean_confidence"]
+
+processed = os.listdir(OUT_PATH) # skip these
+
+# look into these:
+#  Problem processing A_20140609_2027_02
[…]

### 2020-04-20 analysis/bounding_box_G.Rmd
re-exported bounding boxes from numpy arrays to create all_bounding_boxes.RData - still need frame numbers for Y vids

---
title: "Bounding Box Analysis"
author: "George"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)

require(tidyverse)
require(data.table)
require(here)
require(stringr)
```

## Load Data

Detections by type:

```{r load-data}
load(here("data/all_bounding_boxes.RData"))
#summary(df)
table(df$label)
```

## Filter Weird Data

We'll also get rid of detections in videos that were not named with the standard format (and therefore we could not extract age from; e.g. 161384-Baby_Scene videos).
We may also want to get rid of detections below some level of mean confidence (a skewed distro: most <.1): we'll start with $\geq 0.1$.

```{r filter-data, echo=FALSE}
# normalize Y vids height=480, width=640

sdf <- df %>% filter(!is.na(age_days),
                     area>.0001, # keep detections larger than .01*.01
                     mean_confidence > .3)

sdf <- sdf %>% mutate(age_months = round(age_days / 30.42))
```

Keeping `r round(nrow(sdf)/nrow(df),3)*100`% of the detections.

## Detection size by type

Detected people are generally much larger than faces, or hands (which are quite small) -- all very reasonable.

```{r}
sdf %>% ggplot(aes(x=area, fill=label)) + 
  geom_histogram(alpha=.5) + theme_bw() #+ facet_wrap(~age_months)
```

```{r}
hands_by_age <- sdf %>%
  filter(label=="hand") %>%
  group_by(vid_name, age_months, child_id) %>% # do per frame ?
  summarize(N = n(), avg_area = mean(area))

faces_by_age <- sdf %>%
  filter(label=="face") %>%
  group_by(vid_name, age_months, child_id) %>%
  summarize(N = n(), avg_area = mean(area))

poses_by_age <- sdf %>%
  filter(label=="pose") %>%
  group_by(vid_name, age_months, child_id) %>%
  summarize(N = n(), avg_area = mean(area))
```

```{r}
ggplot(hands_by_age, aes(x=N, y=avg_area, col=child_id)) +
  geom_jitter(alpha=.2) +
  ggtitle('Hand size by #') +
  facet_wrap(~age_months) + theme_bw()

ggplot(faces_by_age, aes(x=N, y=avg_area, col=child_id)) +
  geom_jitter(alpha=.2) +
  ggtitle('Hand size by #') +
  facet_wrap(~age_months) + theme_bw()

ggplot(poses_by_age, aes(x=N, y=avg_area, col=child_id)) +
  geom_jitter(alpha=.2) +
  ggtitle('Pose size by #') +
  facet_wrap(~age_months) + theme_bw()
```

### 2020-04-20 preprocessing/get_all_openpose_bounding_boxes.R

@@ -6,23 +6,29 @@ require(data.table)
 require(here)
 require(stringr)
 
-files <- list.files("../src/bounding_boxes") # 1632 vids
+files <- list.files(here("bounding_boxes")) # 1927 vids
 # A_20140630_2117_04_bounding_boxes.csv had no detections
 
-load("../src/data/vid_info.RData") # vid_info
-downup = fread("../src/data/video_right-side-up.csv", stringsAsFactors = F)
+load(here("src/data/vid_info.RData")) # vid_info
+downup = fread(here("src/data/video_right-side-up.csv"), stringsAsFactors = F)
 
 df <- data.frame()
 
+Yb <- as.Date("20180214", "%Y%m%d")
+
 #had to specify columns to get rid of the total column
 for (i in 1:length(files)) {
-  tmp <- fread(paste("../src/bounding_boxes", files[i], sep='/'), stringsAsFactors = F) 
+  tmp <- fread(paste(here("bounding_boxes"), files[i], sep='/'), stringsAsFactors = F) 
   if(ncol(tmp)==9) {
     tmp$V1 = NULL
     this_vid = str_remove(files[i], "_bounding_boxes.csv")
     tmp$child_id = strsplit(files[i], '_')[[1]][1]
     tmp$vid_name = this_vid
     tmp$age_days = vid_info[which(vid_info$vid_name == this_vid)[1],]$age_days
+    if(is.na(tmp$age_days) & tmp$child_id=="Y") {
+      cur_age = as.Date(strsplit(files[i], '_')[[1]][2], "%Y%m%d")
+      tmp$age_days = as.numeric(cur_age - Yb)
+    }
     tmp$right_side_up = downup[which(downup$video == this_vid),]$right_side_up
     # remove any rows with all 0 bounding box + confidences (~50%)
     tmp = subset(tmp, mean_confidence!=0)
@@ -33,11 +39,9 @@ for (i in 1:length(files)) {
   }
 }
 
-save(df, file="all_bounding_boxes.RData")
-
+df <- df %>% mutate(height = ifelse(child_id=="Y", height/480, height),
+                    width = ifelse(child_id=="Y", width/640, width))
 
 df$area = df$height * df$width
-require(ggplot2)
-df %>% filter(area>0) %>%
-  ggplot(aes(x=area, color=label, fill=label)) + 
-  geom_histogram(alpha=.5) 
+save(df, file="data/all_bounding_boxes.RData")
+

### 2020-05-06 get_bounding_boxes_per_vid.py
get_bounding_boxes_per_vid.py -- corrected origin: (0,0) is top left

@@ -19,8 +19,8 @@ files = os.listdir(VID_PATH)
 
 def get_bounding_box(X, Y):
 	left = np.min(X)
-	top = np.max(Y) # is (0,0) top or bottom left? assume bottom left for now -- check python
-	height = top - np.min(Y)
+	top = np.min(Y) # (0,0) is top left
+	height = np.max(Y) - top
 	width = np.max(X) - left
 	return([height, width, left, top])
 

### 2020-05-06 preprocessing/4_preprocess_datasets.Rmd
organizing repo: ordering steps more clearly

--- 2020-01-31 preprocessing/preprocess_datasets.Rmd
@@
   rename(vid_name = vid_name_short) %>% 
-  mutate(vid_name = as.factor(vid_name))
+  mutate(vid_name = as.factor(vid_name)) %<%
+  filter(!vid_name %in% to_exclude$vid_name)
 

### 2020-05-06 preprocessing/human_annotations/face_hands/analysis/preprocess_turk_detections.Rmd
move human_annotations to cleaned up folder in preprocessing pipeline

--- 2019-12-16 annotations/face_hands/analysis/preprocess_turk_detections.Rmd
@@
 # Preprocessing
+## Not finished cleaning this up yet...
+```{r}
+jf <- paste0(here::here(), '/data/turk_data/raw/face_hand_detections/Batch_3858789_batch_results.csv')
 
-```{r}
-f <- dir("turk_annotations_single/")
-jf <- paste("turk_annotations_single/",f,sep="")
 jd <- read_csv(jf)
@@
 jd$response = jd$`Answer.trial-1.label`
-
 agreement <- jd %>%
@@
 trial_indexes = seq(1,252,1)
-files <- dir("turk_annotations/")
 num_workers=20
-
-for (f in files) {
-  jf <- paste("turk_annotations/",f,sep="")
-  jd <- read_csv(jf)
+d <- read_csv(jf)
 
@@
     d.raw <- bind_rows(d.raw, trial_data)
-  }
 }

### 2020-05-06 preprocessing/human_annotations/face_hands/analysis/preprocess_turk_segmentations.Rmd
move human_annotations to cleaned up folder in preprocessing pipeline

--- 2020-01-11 annotations/face_hands/analysis/preprocess_turk_segmentations.Rmd
@@
 library(magick)
-library(egg)
 library(jsonlite)
+library(here)
+library(lubridate)
 theme_set(theme_few())
@@
 ```{r}
-# f <- dir("turk_annotations_segmentation/")
-# jf <- paste("turk_annotations_segmentation/",f,sep="")
-# jd <- read_csv(jf)
-
 f = "turk_segmentations_hands_only.csv"
-jf <- paste("../../../data/",f,sep="")
+jf <- paste0(here::here(), '/data/turk_data/',f)
 jd <- read_csv(jf)
@@
 # dir.create(paste0('child_face/'))
-# for (i in seq(1,length(child_face_frames$full_image_path),1)){
-#   image_read(as.character(child_face_frames$full_image_path[i])) %>%
-#   image_append(stack = FALSE) %>%
-#   image_write(file.path(paste0("child_face/", child_face_frames$short_image_path[i])))
-# }
+for (i in seq(1,length(child_face_frames$full_image_path),1)){
+  image_read(as.character(child_face_frames$full_image_path[i])) %>%
+  image_append(stack = FALSE) %>%
+  image_write(file.path(paste0("child_face/", child_face_frames$short_image_path[i])))
+}
 
@@
 ```{r}
-write_csv(d,'turk_segmentations_hands_only_processed.csv')
+write_csv(d, paste0(here::here(), '/data/turk_data/turk_segmentations_hands_only_processed', today(), '.csv'))
 ```
 
+## Write out some images
 ```{r}
@@
 ```{r eval=FALSE}
-
 unique_images = d$full_image_path

### 2020-06-02 openpose_detections/run_openpose.py
small updates to run on only flipped A/S videos

@@ -35,10 +35,11 @@ def run_openpose(vid_path, op_output_dir, face=True, hand=True,
     vid_output_dir = os.path.join(op_output_dir, f'{vid_name}')
 
     if os.path.exists(vid_output_dir):
-        if not overwrite and input(f'overwrite existing directory {vid_output_dir}? (yes/no)') != 'yes':
-            print(f'aborting on video {vid_path}.')
+        if not overwrite:
+            print(f'Outputs already exist for video {vid_path}- continuing...')
             return
-        print(f'NOTE: overwriting data in {vid_output_dir}')
+        else:
+            print(f'NOTE: overwriting data in {vid_output_dir}')
 
     # this could also be openpose_latest.sif, instead of openpose-latest.img.
     cmd = 'singularity exec --nv $SINGULARITY_CACHEDIR/openpose-latest.img bash -c \''

### 2020-06-02 openpose_detections/run_openpose.py
-

@@ -36,7 +36,7 @@ def run_openpose(vid_path, op_output_dir, face=True, hand=True,
 
     if os.path.exists(vid_output_dir):
         if not overwrite:
-            print(f'Outputs already exist for video {vid_path}- continuing...')
+            print(f'Outputs already exist for video {vid_path} -- continuing...')
             return
         else:
             print(f'NOTE: overwriting data in {vid_output_dir}')

### 2020-06-02 preprocessing/compile_bb_outputs.Rmd
updated to sanity check 1st main analyses

---
title: "saycam bb outputs compile"
author: "Bria Long"
date: "1/9/2020"
output: html_document
---

# Basic data loading and setup
## Packages
```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(lubridate)
library(egg)
library(here)
theme_set(theme_few())
## are we saving outputs
saveFiles = TRUE
```

```{r}
op_file_dir = "../data/op_outputs_per_vid/"
op_files = dir(op_file_dir)
```

```{r}
vid_index = 0
for (vid_file in op_files) {
  vid_index = vid_index + 1
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
   this_vid_data <- readRDS(vid_file_path)
   summary_vid_data <- this_vid_data %>%
     group_by(frame, child_id, vid_name, right_side_up, age_days) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)  %>%
     group_by(child_id, vid_name, right_side_up, age_days) %>%
     summarize(prop_hands = mean(hand_detected), prop_faces = mean(face_detected), num_detect = length(hand_detected))

   if (vid_index == 1 ){
     all_vid_data <- summary_vid_data
   }
   else if (vid_index > 1) {
   all_vid_data <- all_vid_data %>%
     full_join(summary_vid_data)
   }
}
```

```{r}
### Choose bins across which to analyze data
bin_size = 7 # days
min_age = min(all_vid_data$age_days, na.rm=TRUE)
max_age = max(all_vid_data$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)
```

## regualrize vid names
```{r}
all_vid_data <- all_vid_data %>%
  rowwise() %>%
  mutate(vid_name_cleaned = str_split(vid_name,"[.]")[[1]][1])
```

## filter allocentric videos
```{r}
allocentric_file = "../data/raw_data/SAYCAM_allocentric_videos.csv"
to_exclude =read.csv(allocentric_file)

# get INCORRECT videos 
to_exclude <- to_exclude %>%
  filter(allocentric==1) %>%
  rename(vid_name = video)
```

## get rid of vids to exclude
```{r}
all_vid_data <- all_vid_data %>%
  mutate(vid_name_old = vid_name) %>%
  select(-vid_name) %>%
  filter(!vid_name_cleaned %in% to_exclude$vid_name)
```

```{r}
missing_age <-all_vid_data %>%
  filter(is.na(age_days))
```

## summarize by age
```{r}
summary_by_age <- all_vid_data %>%
  filter(!is.na(age_days)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_detect), num_faces = sum(prop_faces*num_detect), num_hands = sum(prop_hands*num_detect), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)

```

```{R}
wide_uncropped <- summary_by_age %>%
  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
  mutate(approach = "uncropped",
         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
  filter(num_frames_total > 5000) # eliminate one data point that skews scaling 
```

```{r}
ggplot(wide_uncropped,
       aes(x=age_day_bin, y=prop,
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + # geom_smooth(show.legend = FALSE) or move these below legend?
  # geom_smooth(data = wide_center, aes(weight = num_detect), show.legend = FALSE,
  #             lty = 2, span=10, se = FALSE) +
  # # geom_smooth(data = wide_gold, aes(weight = num_detect), show.legend = FALSE,
  #             lty = 3, span=10, se = FALSE) +
  ylab('Proportion Detections') +
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(.~child_id) +
  theme_few(base_size=18) +
  ggthemes::scale_color_solarized(name = "") +
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=8)) +
  theme(legend.position="bottom")
```

```{r}
faces_model_out= summary(lmer(prop_faces_summary ~ scale(age_day_bin) + (1 | child_id), data = summary_by_age))

hands_model_out= summary(lmer(prop_hands_summary ~ scale(age_day_bin) + (1 | child_id), data = summary_by_age))

```

```{r}
load(here('data_cogsci/saycam_metadata.RData'))

num_videos_annotated = sum(!is.na(meta$Location))
videos_included = sum(!is.na(meta$Location) & meta$count_locations==1)

# percentage_of_dataset = sum(faces_vs_hands_to_plot$num_detect)/length(d_all$frame)
# num_frames = sum(faces_by_location_to_plot$num_detect)
```

### 2020-06-02 analysis/analyses_fullset_redo_from_bb_outputs.Rmd
code to redo main anlayses from cogsci paper from bb outputs

---
title: "SAYCAM Main analyses from bounding box outputs"
author: "Bria Long"
date: "6/2020"
output:
  pdf_document: default
  html_document: default
---

# Basic data loading and setup
## Packages

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(stringr)
library(here)
theme_set(theme_few())
```

## OP bounding box outputs
```{r}
op_file_dir = here::here("data/op_outputs_per_vid/")
op_files = dir(op_file_dir)
```

## Read in bounding box outputs from each vid, summarize and compile.
```{r}
reload_data=FALSE
# instead of loading each vid, load summary...
load(here::here('data/preprocessed_data/all_vid_data_from_bbs_may2020.RData'))

if (reload_data){
vid_index = 0
for (vid_file in op_files) {
  vid_index = vid_index + 1
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
   this_vid_data <- readRDS(vid_file_path)
   summary_vid_data <- this_vid_data %>%
     group_by(frame, child_id, vid_name, right_side_up, age_days) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)  %>%
     group_by(child_id, vid_name, right_side_up, age_days) %>%
     summarize(prop_hands = mean(hand_detected), prop_faces = mean(face_detected), num_detect = length(hand_detected))

   if (vid_index == 1 ){
     all_vid_data <- summary_vid_data
   }
   else if (vid_index > 1) {
   all_vid_data <- all_vid_data %>%
     full_join(summary_vid_data)
   }
}
}
```

## Data cleaning
### Choose bins across which to analyze data
```{r}
bin_size = 7 # days
min_age = min(all_vid_data$age_days, na.rm=TRUE)
max_age = max(all_vid_data$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)
```

### Regualrize vid names
```{r}
all_vid_data <- all_vid_data %>%
  rowwise() %>%
  mutate(vid_name_cleaned = str_split(vid_name,"[.]")[[1]][1])
```

### Load list of videos we should exclude -- allocentric videos
```{r}
allocentric_file = here::here("data/raw_data/SAYCAM_allocentric_videos.csv")
to_exclude =read.csv(allocentric_file)

# get INCORRECT videos where allocentric videopoint 
to_exclude <- to_exclude %>%
  filter(allocentric==1) %>%
  rename(vid_name = video)
```

### Get rid of vids to exclude from allocentric file
```{r}
all_vid_data <- all_vid_data %>%
  mutate(vid_name_old = vid_name) %>%
  select(-vid_name) %>%
  filter(!vid_name_cleaned %in% to_exclude$vid_name)
```

### Some videos still need metadata (!)
```{r}
missing_age <-all_vid_data %>%
  filter(is.na(age_days))
```

# Basic analysis #1: face/hand by age x child
### Summarize by age x child
```{r}
summary_by_age <- all_vid_data %>%
  filter(!is.na(age_days)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_detect), num_faces = sum(prop_faces*num_detect), num_hands = sum(prop_hands*num_detect), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
```

#### Make wide format for plotting
```{R}
wide_uncropped <- summary_by_age %>%
  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
  mutate(approach = "uncropped",
         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
  filter(num_frames_total > 5000) # eliminate small data point that skews scaling 
```

### Plot face/hand detections by age by child
```{r}
ggplot(wide_uncropped,
       aes(x=age_day_bin, y=prop,
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + # geom_smooth(show.legend =
  ylab('Proportion Detections') +
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(.~child_id) +
  theme_few(base_size=18) +
  ggthemes::scale_color_solarized(name = "") +
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=8)) +
  theme(legend.position="bottom")
```

### Quick lmers
```{r}
faces_model_out= summary(lmer(prop_faces_summary ~ scale(age_day_bin) + (1 | child_id), data = summary_by_age))

hands_model_out= summary(lmer(prop_hands_summary ~ scale(age_day_bin) + (1 | child_id), data = summary_by_age))
```

# Basic analysis #2: Location variability

## Preprocessing
### Load metadata 
```{r}
# meta
load(here::here('data/preprocessed_data/saycam_metadata.RData'))
```

### Join face/hand detections with metadata and restrict to videos with a single location.
```{r}
vid_by_location <- all_vid_data %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  mutate(vid_name = vid_name_cleaned) %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) 
```

### Restrict to videos with age data for now
```{r}
# until we get all metadata
vid_by_location <- vid_by_location %>%
  filter(!is.na(age_days)) 
```

## Summarize by location / child / age_bin 
```{r}
face_hand_by_location<- vid_by_location %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(num_frames_total = sum(num_detect), num_faces = sum(prop_faces*num_detect), num_hands = sum(prop_hands*num_detect), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)

# get CIs for hands; join with summary data points 
hands_to_plot <- vid_by_location %>%
  filter(!is.na(age_day_bin)) %>%
  group_by(Location, child_id, age_day_bin) %>%
  summarize(num_frames_total = sum(num_detect), num_faces = sum(prop_faces*num_detect), num_hands = sum(prop_hands*num_detect), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total) %>%
  multi_boot_standard(col="prop_hands_summary") %>%
  mutate(region = "Hands") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(prop = prop_hands_summary) %>%
  filter(!is.na(ci_lower))  # filter if only one point per location/child

# get CIs for faces; join with summary data points 
faces_to_plot <- vid_by_location %>%
  filter(!is.na(age_day_bin)) %>%
  group_by(Location, child_id, age_day_bin) %>%
  summarize(num_frames_total = sum(num_detect), num_faces = sum(prop_faces*num_detect), num_hands = sum(prop_hands*num_detect), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total) %>%
  multi_boot_standard(col="prop_faces_summary") %>%
  mutate(region = "Faces") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(prop = prop_faces_summary) %>%
  filter(!is.na(ci_lower))  # filter if only one point per location/child
```

### compile and reorder by num detections in a location for plotting
```{r}
all_to_plot <- hands_to_plot %>%
  full_join(faces_to_plot) %>%
  group_by(Location) %>%
  mutate(num_detect_location = sum(num_frames_total)) %>%
  ungroup() %>%
  mutate(Location = fct_reorder(Location, num_detect_location))
```

## Plot location variability for each child separately
```{r}
ggplot(all_to_plot, aes(x = Location, y = mean, col=region)) + 
  geom_point(aes(x=Location, y=prop, size=log10(num_frames_total)), alpha=.1, position = position_dodge(width=.6)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper, linetype=region),position = position_dodge(width=.6)) +
  coord_flip() + 
  ylab('Proportion Detected')+
  xlab('')+
  theme_few(base_size=9) +
  theme(legend.position = "bottom") +
  facet_grid(.~child_id)  +
  scale_size_continuous(name = "Detections (Log 10)") +
  scale_linetype_manual(values=c("solid", "solid","dashed"), name = "") +
  scale_color_manual(values = c("#268bd2", "#dc322f","#DC7977"), name = "") +
  theme(legend.text=element_text(size=8))
```

### 2020-06-02 preprocessing/compile_bb_outputs.Rmd
code to redo main anlayses from cogsci paper from bb outputs

@@
 ---
-title: "saycam bb outputs compile"
+title: "SAYCAM Main analyses from bounding box outputs"
 author: "Bria Long"
-date: "1/9/2020"
+date: "6/2020"
 output: html_document
@@
 library(viridis)
-library(magick)
 library(stringr)
-library(lubridate)
-library(egg)
 library(here)
 theme_set(theme_few())
-## are we saving outputs
-saveFiles = TRUE
 ```
-
+## OP bounding box outputs
 ```{r}
-op_file_dir = "../data/op_outputs_per_vid/"
+op_file_dir = here("/data/op_outputs_per_vid/")
 op_files = dir(op_file_dir)
@@
 
+## Read in bounding box outputs from each vid, summarize and compile.
 ```{r}
@@
 
+## Data cleaning
+### Choose bins across which to analyze data
 ```{r}
-### Choose bins across which to analyze data
 bin_size = 7 # days
@@
 
-## regualrize vid names
+### Regualrize vid names
 ```{r}
@@
 
-## filter allocentric videos
+### Load list of videos we should exclude -- allocentric videos
 ```{r}
-allocentric_file = "../data/raw_data/SAYCAM_allocentric_videos.csv"
+allocentric_file = here("data/raw_data/SAYCAM_allocentric_videos.csv")
 to_exclude =read.csv(allocentric_file)
 
-# get INCORRECT videos 
+# get INCORRECT videos where allocentric videopoint 
 to_exclude <- to_exclude %>%
@@
 
-## get rid of vids to exclude
+### Get rid of vids to exclude from allocentric file
 ```{r}
@@
 
+### Some videos still need metadata (!)
 ```{r}
@@
 ```
-
-## summarize by age
-```{r}
-summary_by_age <- all_vid_data %>%
-  filter(!is.na(age_days)) %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
-  group_by(age_day_bin, child_id) %>%
-  summarize(num_frames_total = sum(num_detect), num_faces = sum(prop_faces*num_detect), num_hands = sum(prop_hands*num_detect), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
-
-```
-
-```{R}
-wide_uncropped <- summary_by_age %>%
-  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
-  mutate(approach = "uncropped",
-         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
-  filter(num_frames_total > 5000) # eliminate one data point that skews scaling 
-```
-
-```{r}
-ggplot(wide_uncropped,
-       aes(x=age_day_bin, y=prop,
-           size=log10(num_frames_total),
-           col=region)) +
-  geom_point(alpha=.2) +
-  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + # geom_smooth(show.legend = FALSE) or move these below legend?
-  # geom_smooth(data = wide_center, aes(weight = num_detect), show.legend = FALSE,
-  #             lty = 2, span=10, se = FALSE) +
-  # # geom_smooth(data = wide_gold, aes(weight = num_detect), show.legend = FALSE,
-  #             lty = 3, span=10, se = FALSE) +
-  ylab('Proportion Detections') +
-  xlab('Age (Months)') +
-  ylim(0,.5) +
-  facet_grid(.~child_id) +
-  theme_few(base_size=18) +
-  ggthemes::scale_color_solarized(name = "") +
-  scale_size_continuous(name = "Detections (Log 10)") +
-  theme(legend.text=element_text(size=8)) +
-  theme(legend.position="bottom")
-```
-
-```{r}
-faces_model_out= summary(lmer(prop_faces_summary ~ scale(age_day_bin) + (1 | child_id), data = summary_by_age))
-
-hands_model_out= summary(lmer(prop_hands_summary ~ scale(age_day_bin) + (1 | child_id), data = summary_by_age))
-
-```
-
-```{r}
-load(here('data_cogsci/saycam_metadata.RData'))
-
-num_videos_annotated = sum(!is.na(meta$Location))
-videos_included = sum(!is.na(meta$Location) & meta$count_locations==1)
-
-# percentage_of_dataset = sum(faces_vs_hands_to_plot$num_detect)/length(d_all$frame)
-# num_frames = sum(faces_by_location_to_plot$num_detect)
-```

### 2020-06-03 setup.sh
improved setup script + documentation

@@ -1,15 +1,21 @@
-#!/bin/bash
+#!/usr/bin/env bash
+# Sets up conda environment and pulls Openpose Singularity container into specified directory.
+# If no install directory is provided, Openpose will be installed in $HOME
+# (WARNING: takes up 2GB)
+# This script should be run from a development node, not a login node.
+# Example usage: chmod +x setup.sh; ./setup.sh /path/to/desired/openpose_install_dir
 
-#Create Conda env
+# #Create Conda env
+echo "Initializing conda for bash shell..."
+conda init
+
 echo "Creating conda env..."
 conda env create -f headcam.yml
-source activate headcam
+conda activate headcam
+echo "Installing ipython kernel..."
 python -m ipykernel install --user --name headcam --display-name "Python (headcam)"
 
-#Pull Openpose Docker
-#TODO: change this to wherever is convenient, i.e. /path/to/.singularity.
-echo "Pulling Openpose Docker..."
-mkdir $SCRATCH/.singularity
-#One can create $SINGULARITY_CACHEDIR wherever it's convenient on your system.
-export SINGULARITY_CACHEDIR=$SCRATCH/.singularity
+echo "Installing Openpose Singularity container in ${1:-$HOME}/.singularity ..."
+export SINGULARITY_CACHEDIR=${1:-$HOME}/.singularity
+mkdir $SINGULARITY_CACHEDIR
 singularity pull docker://amsan7/openpose

### 2020-06-17 analysis/analyses_fullset_redo_from_bb_outputs.Rmd
add code to redo center cropping from bb outputs

@@
 op_files = dir(op_file_dir)
+# op_files = op_files [1] # for testing
+```
+
+### Load list of videos we should exclude -- allocentric videos
+```{r}
+allocentric_file = here::here("data/raw_data/SAYCAM_allocentric_videos.csv")
+to_exclude =read.csv(allocentric_file)
+
+# get INCORRECT videos where allocentric videopoint 
+to_exclude <- to_exclude %>%
+  filter(allocentric==1) %>%
+  rename(vid_name = video)
 ```
@@
 
+## Crop out detections from outer edges of frames; do so at video level.
+```{r}
+# cropping paramts
+limit_lower =.2
+limit_upper =.8
+# vid params
+y_max = 480
+x_max = 640
+
+reload_data=TRUE
+if (reload_data){
+vid_index = 0
+for (vid_file in op_files) {
+
+   # to check progress
+   vid_index = vid_index + 1
+   if ((vid_index %% 100)==0) { print (vid_file) }
+
+   # get vid level data
+   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
+   this_vid_data <- readRDS(vid_file_path)
+
+    # don't bother for these files
+   if (!this_vid_data$vid_name[1] %in% to_exclude$vid_name){
+
+    # for renormalizing y's vids which were run differently this time
+   if (this_vid_data$child_id[1]=='Y'){
+     this_vid_data <- this_vid_data %>%
+      mutate(top = top/y_max, height = height/y_max, left = left/x_max, width = width/x_max)
+   }
+
+   # now get vid level data
+   summary_vid_data_center <- this_vid_data %>%
+     mutate(num_frames = length(unique(frame))) %>% # count frames
+     mutate(center_y = top + height/2, center_x = left + width/2) %>% # get center_x and y
+     filter(center_y<(limit_upper) & center_x<(limit_upper) & center_y>(limit_lower) & center_x>(limit_lower)) %>%   # filter within parameters
+     group_by(frame, child_id, vid_name, num_frames, age_days) %>% # group at frame level first
+     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0) %>%
+     group_by(child_id, vid_name, age_days, num_frames) %>% # now at the video level
+     summarize(num_hands = sum(hand_detected), num_faces = sum(face_detected)) # count how many faces/hands
+
+   # compile vid-level summaries 
+   if (vid_index == 1){
+     all_vid_data_center <- summary_vid_data_center
+   }
+   else if (vid_index > 1) {
+   all_vid_data_center <- all_vid_data_center %>%
+     full_join(summary_vid_data_center)
+   }
+}
+}
+}
+
+```
+
 ## Data cleaning
@@
 
-### Regualrize vid names
+### Regualrize vid names & get rid of vids to exclude from allocentric file
 ```{r}
@@
   mutate(vid_name_cleaned = str_split(vid_name,"[.]")[[1]][1])
-```
 
-### Load list of videos we should exclude -- allocentric videos
-```{r}
-allocentric_file = here::here("data/raw_data/SAYCAM_allocentric_videos.csv")
-to_exclude =read.csv(allocentric_file)
-
-# get INCORRECT videos where allocentric videopoint 
-to_exclude <- to_exclude %>%
-  filter(allocentric==1) %>%
-  rename(vid_name = video)
-```
-
-### Get rid of vids to exclude from allocentric file
-```{r}
 all_vid_data <- all_vid_data %>%
@@
   filter(!vid_name_cleaned %in% to_exclude$vid_name)
+```
+
+```{r}
+# Function to evaluate detectors
+evaluate_detector <- function(truth, detection) {
+  if (truth == TRUE) {
+    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
+    else return("FN") # was face/wrist, missed face/wrist
+  }
+  else {
+    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
+    else return("FP") # was not face/wrist, detected face/wrist
+  }
+}
+
+# function to return prfs
+ return_prf_short = function(eval){
+  tp=sum(eval == "TP")
+  fp=sum(eval == "FP")
+  fn=sum(eval == "FN")
+  p = tp / (tp + fp)
+  r = tp / (tp + fn)
+  f=( 2 * p * r )/ (p + r)
+  return(c(p,r,f))
+ }
+
+```
+
+```{R}
+ ## load gold sample annotations
+ load(here('data/data_cogsci/gold_sample_annotations2020-01-31.RData')) # gold_sample, pre-filtered
+
+gold_sample_frames <- gold_sample %>%
+  select(vid_name, frame)
+
+gold_sample_vids <- unique(gold_sample_frames$vid_name)
+```
+
+```{r}
+# redo gold sample 
+if (reload_data){
+vid_index = 0
+for (vid_file in op_files) {
+
+   # to check progress
+   vid_index = vid_index + 1
+   if ((vid_index %% 100)==0) { print (vid_file) }
+
+   # get vid level data
+   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
+   this_vid_data <- readRDS(vid_file_path)
+   this_vid_name <- this_vid_data$vid_name[1]
+
+   # if it's one of the vids from gold sample
+   if (this_vid_name %in% unique(gold_sample_frames$vid_name)){
+   # and not excluded
+   if (!this_vid_name %in% to_exclude$vid_name){
+
+   frames_to_get <- gold_sample_frames %>%
+     filter(vid_name == this_vid_name)
+
+   # now get vid level data
+   gold_sample_op <- this_vid_data %>%
+     filter(frame %in% frames_to_get$frame) %>%
+     group_by(frame, vid_name) %>%
+     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)
+
+   # compile vid-level summaries 
+   if (vid_index == 1){
+     all_gold_sample_frames_op <- gold_sample_op
+   }
+   else if (vid_index > 1) {
+   all_gold_sample_frames_op <- all_gold_sample_frames_op %>%
+     full_join(gold_sample_op)
+   }
+}
+}
+}
+}
+```
+
+```{r}
+
+ ## evaluate detectors
+ gold_sample <- gold_sample %>%
+  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
+  right_join(all_gold_sample_frames_op) %>%
+  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))
+
+ ## output prfs
+ face_performance = return_prf_short(gold_sample$face_eval_ketan)
+ hand_performance = return_prf_short(gold_sample$hand_eval_ketan)
 ```
@@
 
+```{r}
+summary_by_age_center <- all_vid_data_center %>%
+  filter(!is.na(age_days)) %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+  group_by(age_day_bin, child_id) %>%
+  summarize(num_frames_total = sum(num_frames), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
+
+```
+
 #### Make wide format for plotting
@@
   mutate(approach = "uncropped",
+         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
+  filter(num_frames_total > 5000) # eliminate small data point that skews scaling 
+```
+
+```{r}
+wide_center <- summary_by_age_center %>%
+  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
+  mutate(approach = "centered",
          region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
@@
   geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + # geom_smooth(show.legend =
+  geom_smooth(data = wide_center, aes(weight = num_frames_total), show.legend = FALSE, 
+              lty = 2, span=10, se = FALSE) +
   ylab('Proportion Detections') +
@@
 # Basic analysis #2: Location variability
-
 ## Preprocessing

### 2020-06-17 openpose_detections/openpose_helpers.py
bug fix (edge case, only affected a few vids)

@@ -91,7 +91,7 @@ def load_json_list(json_filepaths, part_size=10000, num_chunks=16):
         print(f'{i}/{num_frames}')
         fps_cut = json_filepaths[i:i+part_size]
         p = mp.Pool()
-        chunk_size = len(fps_cut) // num_chunks
+        chunk_size = max(len(fps_cut) // num_chunks, 1)
         chunk_list = chunks(fps_cut, chunk_size)
         json_list += p.map(load_json_chunk, chunk_list)
     json_list = [frame for chunk in json_list for frame in chunk]

### 2020-06-30 paper/preprint/paper_revised_submission_june2020_apa.Rmd
code for rendering preprint

--- 2020-02-03 paper/cogsci/paper_initial_submission_blinded.Rmd
@@
 ---
-title:  |
-  | Detecting social information in a dense database
-  | of infants’ natural visual experience
-bibliography: library.bib
-csl: apa6.csl
-document-params: "10pt, letterpaper"
+title             : "Detecting social information in a dense database of infants’ natural visual experience"
+shorttitle        : "Detecting social information"
 
-author-information: >
+author: 
+  - name          : "Bria L. Long"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "450 Serra Mall, Stanford CA 94305"
+    email         : "bria@stanford.edu"
+  - name          : "George Kachergis"
+    affiliation   : "1"
+  - name          : "Ketan Agrawal"
+    affiliation   : "1"
+  - name          : "Michael C. Frank"
+    affiliation   : "1"
 
-abstract: >
+affiliation:
+  - id            : "1"
+    institution   : "Department of Psychology, Stanford University"
+
+# authornote: |
+#   Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+# 
+#   Enter author note here.
+
+abstract: |
           The faces and hands of caregivers and other social partners offer a rich source of social and causal information that may be critical for infants' cognitive and linguistic development.
@@
 
-keywords: >
-    social cognition; face perception; infancy; head cameras; deep learning
+keywords          : "social cognition; face perception; infancy; head cameras; deep learning"
+wordcount         : "3444"
 
-output: cogsci2016::cogsci_paper
-#final-submission: \cogscifinalcopy
+bibliography      : ["library.bib"]
+
+floatsintext      : no
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+mask              : no
+draft             : no
+
+documentclass     : "apa6"
+classoption       : "man"
+output            : papaja::apa6_pdf
 ---
-\newcommand{\wrapmf}[1]{#1}
+
+```{r setup, include = FALSE}
+library("papaja")
+```
 
@@
 library(lmerTest)
-
+library(here)
 theme_set(theme_few())
-# renv::init()
-# https://rstudio.github.io/renv/articles/renv.html
 ```
@@
 ## Read in data 
-### Load preprocessed and filtered detections
-load('../../data_cogsci/openpose_detections_filtered_2020-01-29.RData') # d_all
-load('../../data_cogsci/openpose_detections_filtered_cropped_2020-01-29.RData') # d_cropped
+load(here::here('data/data_preprint/all_vid_data_from_bbs_june2020.RData')) # all detections
+load(here::here('data/data_preprint/all_centered_vid_data_from_bbs_june2020.RData')) # centered cropped
 ```
@@
 ```{r}
-### Choose bins across which to analyze data
-bin_size = 7 # days
-min_age = min(d_all$age_days)
-max_age = max(d_all$age_days)
-bin_starts = seq(min_age-1, max_age+1,bin_size)
-bins = c(bin_starts, max_age)
+load(here::here('data/data_preprint/gold_sample_from_bbs_june2020.RData')) # gold sample detections
+load(here::here('data/data_preprint/gold_sample_annotations2020-01-31.RData')) # human annotations
 ```
@@
 ### How large is the dataset we're analyzing?
-num_frames = length(d_all$frame)
+num_frames = sum(all_vid_data$num_detect)
 
 fps=30
-num_seconds = length(d_all$frame)/fps
-num_videos = length(unique(d_all$vid_name))
+num_seconds = sum(all_vid_data$num_detect)/fps
+num_videos = length(unique(all_vid_data$vid_name))
 num_minutes = num_seconds/60
@@
 num_days = num_hours/24
+
+bin_size = 7 # days
+min_age = min(all_vid_data$age_days, na.rm=TRUE)
+max_age = max(all_vid_data$age_days, na.rm=TRUE)
+bin_starts = seq(min_age-1, max_age+1,bin_size)
+bins = c(bin_starts, max_age)
 ```
@@
 
- ## load gold sample annotations
- load('../../data_cogsci/gold_sample_annotations2020-01-31.RData') # gold_sample, pre-filtered
+#
 
- ## evaluate detectors
+# join human and OP detections
 gold_sample <- gold_sample %>%
-  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose))
+  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
+  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
+  right_join(all_gold_sample_frames_op) %>%
+  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))
 
@@
 ### Examine gold sample performance by child hands
-load('../../data_cogsci/child_adult_hand_annotations_by_frame.RData')
+load(here::here('data/data_preprint/child_adult_hand_annotations_by_frame.RData'))
 # 
@@
   filter(child_hand_seg==FALSE) %>% # now these are counted as frames where OP didn't need to detect something
-  mutate(hand_eval_adults = evaluate_detector(hand_present_ketan, hand_openpose))
+  mutate(hand_eval_adults = evaluate_detector(hand_present_ketan, hand_detected))
 
@@
 ### Load turk hand annotations with all bounding boxes (multiple dets per frame)
-load("../../data_cogsci/hand_annotations_2020-01-29.RData")
+load(here::here('data/data_preprint/hand_annotations_2020-01-29.RData'))
 
@@
 ```{r}
-vid_info <- d_all %>%
-  select(vid_name, frame, age_days, child_id)
-
-## summary stats for gold sample detections
-summary_by_age_gold <- gold_sample %>%
-  left_join(vid_info) %>%
+## summary for all detections
+summary_by_age <- all_vid_data %>%
+  filter(!is.na(age_days)) %>%
   mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
@@
   group_by(age_day_bin, child_id) %>%
-  summarize(num_detect = length(face_present_ketan), prop_faces = sum(face_present_ketan) / num_detect,  prop_hands = sum(hand_present_ketan) / num_detect)
+  summarize(num_frames_total = sum(num_detect), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
+```
 
-## Make summary stats for cropped and uncropped detedctions
-summary_by_age <- d_all %>%
+```{r}
+## summary for centered detections
+summary_by_age_center <- all_vid_data_center %>%
+  filter(!is.na(age_days)) %>%
   mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
@@
   group_by(age_day_bin, child_id) %>%
-  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect)
+  summarize(num_frames_total = sum(num_frames), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
+```
 
-summary_by_age_cropped <- d_cropped %>%
-  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
-  group_by(age_day_bin,child_id) %>%
-  summarize(num_detect = length(face_openpose), prop_faces = sum(face_detected) / num_detect,  prop_hands = sum(hand_detected) / num_detect)
+```{R}
+#### Make wide format for plotting
+wide_uncropped <- summary_by_age %>%
+  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
+  mutate(approach = "uncropped",
+         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
+  filter(num_frames_total > 5000) # eliminate small data point that skews scaling
 
-##
-wide_gold <- summary_by_age_gold %>%
-  gather(region, prop, prop_faces, prop_hands) %>%
-  mutate(approach = "gold", region = ifelse(region == "prop_faces","Face","Hands"))  %>%
-  filter(!is.na(child_id)) # weird video
-
-wide_cropped <- summary_by_age_cropped %>%
-  gather(region, prop, prop_faces, prop_hands) %>%
-  mutate(approach = "cropped",
-         region = ifelse(region == "prop_faces","Face","Hands"))  %>%
-  filter(num_detect > 5000) # eliminate one data point that skews scaling
-
-wide_uncropped <- summary_by_age %>%
-  gather(region, prop, prop_faces, prop_hands) %>%
-  mutate(approach = "uncropped",
-         region = ifelse(region == "prop_faces","Face","Hands"))  %>%
-  filter(num_detect > 5000) # eliminate one data point that skews scaling
-
+wide_center <- summary_by_age_center %>%
+  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
+  mutate(approach = "centered",
+         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
+  filter(num_frames_total > 5000) # eliminate small data point that skews scaling 
 ```
@@
 Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range.
-Dashed lines show estimated trend lines from proportion of faces/hands in view when detections are restricted to the upper 60 percent of the FOV, reducing the contribution of children's own hands; dotted lines show estimated trend lines for human annotations on the 24K gold set."}
+Dashed lines show estimated trend lines from proportion of faces/hands in view when detections are restricted to the center FOV, reducing the contribution of children's own hands."}
 
@@
        aes(x=age_day_bin, y=prop, 
-           size=log10(num_detect),
+           size=log10(num_frames_total),
            col=region)) +
   geom_point(alpha=.2) +
-  geom_smooth(span=10, aes(weight = num_detect), show.legend = FALSE) + # geom_smooth(show.legend = FALSE) or move these below legend?
-  geom_smooth(data = wide_cropped, aes(weight = num_detect), show.legend = FALSE, 
+  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + # geom_smooth(show.legend = FALSE) or move these below legend?
+  geom_smooth(data = wide_center, span=10, aes(weight = num_frames_total), show.legend = FALSE, 
               lty = 2, span=10, se = FALSE) +
-  geom_smooth(data = wide_gold, aes(weight = num_detect), show.legend = FALSE,
-              lty = 3, span=10, se = FALSE) +
   ylab('Proportion Detections') + 
@@
 
-We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands that were in view for each child.^[All analyses and preprocessed data files for this paper are avaliable at https://tinyurl.com/detecting-social-info] Data from videos were binned according to the age of the child (in weeks).
+We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands that were in view for each child.^[All analyses and preprocessed data files for this paper are available at https://tinyurl.com/detecting-social-info] Data from videos were binned according to the age of the child (in weeks).
 First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:FacesAndHands}); in contrast, we did not observe an increase in the proportion of hands in view, but rather a slight decrease.
@@
 
-```{r}
-# replace NAs with FALSE to compare proportion hands detected
-d_cropped <- d_cropped %>%
-  replace_na(list(hand_detected = FALSE, face_detected = FALSE))
-```
-
-As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the upper 60% of the field of view, decreasing the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)*100`% to `r round(mean(d_cropped$hand_detected),2)*100`%, but only decreased face detections from `r round(mean(d_all$face_openpose),2)*100`% to `r round(mean(d_cropped$face_detected),3)*100`%.
+As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_detect),2)*100`% to `r round(sum(all_vid_data_center$num_hands)/sum(all_vid_data_center$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_detect),2)*100`% to `r round(sum(all_vid_data_center$num_faces)/sum(all_vid_data_center$num_frames),3)*100`%.
 This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
@@
 ```{r eval=FALSE}
-summary_by_age_days_cropped <- d_cropped %>%
-  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
+summary_by_age_days_centered <- all_vid_data_center %>%
   group_by(age_days,child_id) %>%
-  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected), num_detect = length(face_openpose)) %>%
+  summarize(num_faces = sum(num_faces), num_hands = sum(num_hands), num_detect = sum(num_frames)) %>%
   mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect) 
-summary_by_age_days_cropped$age_scale <- scale(summary_by_age_days_cropped$age_days, scale = FALSE)[,1] / 30.3
+summary_by_age_days_centered$age_scale <- scale(summary_by_age_days_centered$age_days, scale = FALSE)[,1] / 30.3
 
-summary_by_age_days <- d_all %>%
+summary_by_age_days <- all_vid_data %>%
   group_by(age_days,child_id) %>%
-  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_openpose), num_detect = length(face_openpose)) %>%
+  summarize(num_faces = sum(num_faces), num_hands = sum(num_hands), num_detect = sum(num_frames)) %>%
   mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect) 
@@
 # run lmer models -- faces over age
-faces_model_full_age_out = summary(lmer(prop_faces ~ age_scale + (1 | child_id), data = summary_by_age_days_cropped))
+faces_model_full_age_out = summary(lmer(prop_faces ~ age_scale + (1 | child_id), data = summary_by_age_days_centered))
 
 # hands over age
-hands_model_full_age_out = summary(lmer(prop_hands ~ age_scale + (1 | child_id), data = summary_by_age_days_cropped))
+hands_model_full_age_out = summary(lmer(prop_hands ~ age_scale + (1 | child_id), data = summary_by_age_days_centered))
 
@@
 # main effect of ages and regions; no interaction.
-wide_cropped_age_days <- summary_by_age_days_cropped %>%
+wide_centered_age_days <- summary_by_age_days_centered %>%
   gather(region, prop, prop_faces, prop_hands) %>%
@@
 
-diff_model_full_age_out = summary(lmer(prop ~ region*age_scale + (1 | child_id), data = wide_cropped_age_days))
+diff_model_full_age_out = summary(lmer(prop ~ region*age_scale + (1 | child_id), data = wide_centered_age_days))
 ```
@@
 ```{r eval=FALSE}
-xtable(faces_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of faces seen by infants.")
+xtable(faces_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of faces seen by infants in the center FOV.")
 
-xtable(hands_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of hands seen by infants.")
+xtable(hands_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of hands seen by infants n the center FOV.")
 ```
@@
   \hline
- & Estimate & Std. Err. & df & t value & Pr($>$$|$t$|$) \\ 
+ & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
   \hline
-(Int.) & 0.179 & 0.008 & 2.180 & 22.736 & 0.001 \\ 
-  Age & -0.002 & 0.001 & 402.024 & -3.138 & 0.002 \\ 
+(Intercept) & 0.100 & 0.014 & 1.955 & 7.049 & 0.021 \\ 
+  Age  & -0.002 & 0.001 & 386.972 & -4.461 & 0.000 \\ 
    \hline
 \end{tabular}
-\caption{Model coefficients from a linear mixed model predicting the proportion of faces seen by infants.} 
+\caption{Model coefficients from a linear mixed model predicting the proportion of faces seen by infants in the center FOV.} 
 \end{table}
@@
   \hline
-(Int.) & 0.238 & 0.011 & 1.913 & 22.359 & 0.002 \\ 
-  Age & -0.002 & 0.001 & 409.966 & -2.286 & 0.023 \\ 
+(Intercept) & 0.166 & 0.011 & 2.082 & 15.340 & 0.004 \\ 
+  Age & -0.002 & 0.001 & 380.308 & -3.114 & 0.002 \\ 
    \hline
 \end{tabular}
-\caption{Model coefficients from a linear mixed model predicting the proportion of hands seen by infants.} 
+\caption{Model coefficients from a linear mixed model predicting the proportion of hands seen by infants in the center FOV.} 
 \end{table}
@@
 ```{r}
-load('../../data_cogsci/saycam_metadata.RData') # meta
+load(here::here('data/data_preprint/saycam_metadata.RData')) # meta
 
@@
 ```{r}
-d_by_location_cropped <- d_cropped %>%
-  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
+vid_data_by_location <- all_vid_data %>%
+  mutate(num_frames = num_detect) %>%
   mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
@@
   filter(count_locations==1)
+
+vid_data_centered_by_location <- all_vid_data_center %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+  left_join(meta) %>%
+  filter(!is.na(Location)) %>%
+  filter(count_locations==1)
+
 # 
-d_by_location_cropped$Location = droplevels(d_by_location_cropped$Location) # get rid of unused levels (more than 1 location)
+vid_data_by_location$Location = droplevels(vid_data_by_location$Location) 
+vid_data_centered_by_location$Location = droplevels(vid_data_centered_by_location$Location) # get rid of unused levels (more than 1 location)
+
 # merge locations that seem similar
-levels_to_modify = levels(d_by_location_cropped$Location)
+levels_to_modify = levels(vid_data_by_location$Location)
+levels_to_modify = levels(vid_data_centered_by_location$Location)
 levels_to_modify[10] = 'Outside' # Outside on property
 levels_to_modify[12] = 'Outside' # Off Property
+
 # reset levels for both cropped/uncropped
-levels(d_by_location_cropped$Location) <- levels_to_modify
+levels(vid_data_centered_by_location$Location) <- levels_to_modify
+levels(vid_data_by_location$Location) <- levels_to_modify
 
-face_hand_by_location_cropped <- d_by_location_cropped %>%
+```
+
+```{r}
+face_hand_by_location_centered<- vid_data_centered_by_location %>%
   group_by(Location,child_id,age_day_bin) %>%
-  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_openpose), prop_hands_cropped = mean(hand_detected), num_detect = length(hand_detected))  %>%
+  summarize(prop_faces = sum(num_faces)/sum(num_frames), prop_hands = sum(num_hands)/sum(num_frames), num_detect = sum(num_frames))  %>%
   group_by(Location) %>%
-  filter(num_detect > 12000)  ##
+  filter(num_detect >12000)
+
+face_hand_by_location <- vid_data_by_location %>%
+  group_by(Location,child_id,age_day_bin) %>%
+  summarize(prop_faces = sum(num_faces)/sum(num_frames), prop_hands = sum(num_hands)/sum(num_frames), num_detect = sum(num_frames))  %>%
+  group_by(Location) %>%
+  filter(num_detect >12000)
 
@@
 ## Get rid of any locations where we didn't have enough data to make a CI (not more than 1 age_bin)
-hands_to_plot_cropped <- face_hand_by_location_cropped %>%
+hands_to_plot_centered <- face_hand_by_location_centered %>%
   group_by(Location, child_id) %>%
-  multi_boot_standard(col="prop_hands_cropped") %>%
-  mutate(region = "Hands (Cropped)") %>%
+  multi_boot_standard(col="prop_hands") %>%
+  mutate(region = "Hands (Center)") %>%
   ungroup %>%
-  left_join(face_hand_by_location_cropped) %>%
-  mutate(prop = prop_hands_cropped) %>%
-  select(-prop_faces, -prop_hands, -prop_hands_cropped) %>%
+  left_join(face_hand_by_location_centered) %>%
+  mutate(prop = prop_hands) %>%
+  select(-prop_faces, -prop_hands) %>%
   filter(!is.na(ci_lower))
 
-hands_to_plot <- face_hand_by_location_cropped %>%
+faces_to_plot_centered <- face_hand_by_location_centered %>%
+  group_by(Location, child_id) %>%
+  multi_boot_standard(col="prop_faces") %>%
+  mutate(region = "Face (Center)") %>%
+  ungroup %>%
+  left_join(face_hand_by_location_centered) %>%
+  mutate(prop = prop_faces) %>%
+  select(-prop_faces, -prop_hands) %>%
+  filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter
+
+faces_to_plot_all <- face_hand_by_location %>%
+  group_by(Location, child_id) %>%
+  multi_boot_standard(col="prop_faces") %>%
+  mutate(region = "Faces (All)") %>%
+  ungroup %>%
+  left_join(face_hand_by_location) %>%
+  mutate(prop = prop_faces) %>%
+  select(-prop_faces, -prop_hands) %>%
+  filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter
+
+hands_to_plot_all <- face_hand_by_location %>%
   group_by(Location, child_id) %>%
   multi_boot_standard(col="prop_hands") %>%
-  mutate(region = "Hands") %>%
+  mutate(region = "Hands (All)") %>%
   ungroup %>%
-  left_join(face_hand_by_location_cropped) %>%
+  left_join(face_hand_by_location) %>%
   mutate(prop = prop_hands) %>%
-  select(-prop_faces, -prop_hands, -prop_hands_cropped) %>%
-  filter(!is.na(ci_lower))
-
-faces_to_plot_cropped <- face_hand_by_location_cropped %>%
-  group_by(Location, child_id) %>%
-  multi_boot_standard(col="prop_faces") %>%
-  mutate(region = "Face") %>%
-  ungroup %>%
-  left_join(face_hand_by_location_cropped) %>%
-  mutate(prop = prop_faces) %>%
-  select(-prop_faces, -prop_hands, -prop_hands_cropped) %>%
+  select(-prop_faces, -prop_hands) %>%
   filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter
 
-all_to_plot <- faces_to_plot_cropped %>%
-  full_join(hands_to_plot_cropped) %>%
-  full_join(hands_to_plot) %>%
+all_to_plot <- faces_to_plot_centered %>%
+  full_join(hands_to_plot_centered) %>%
+  full_join(hands_to_plot_all) %>%
+  full_join(faces_to_plot_all) %>%
   group_by(Location) %>%
@@
 
-```{r}
-### Chi-squared tests for location variability
-d_by_location_cropped_mini_S <- d_by_location_cropped %>%
-  group_by(Location) %>%
-  mutate(num_detect = length(hand_detected))  %>%
-  filter(num_detect > 0)  %>%
-  filter(child_id == "S") %>%
-  select(Location, face_openpose,hand_detected) # using cropped hands here
-
-d_by_location_cropped_mini_A <- d_by_location_cropped %>%
-  group_by(Location) %>%
-  mutate(num_detect = length(hand_detected))  %>%
-  filter(num_detect > 0)  %>% #
-  filter(child_id == "A") %>%
-  select(Location, face_openpose, hand_detected)
-
-## drop levels
-d_by_location_cropped_mini_S$Location = droplevels(d_by_location_cropped_mini_S$Location)
-d_by_location_cropped_mini_A$Location = droplevels(d_by_location_cropped_mini_A$Location)
-
-## make smaller dataframes for just faces/hands
-d_by_location_cropped_mini_S_face <- d_by_location_cropped_mini_S %>%
-  select(Location, face_openpose)
-
-d_by_location_cropped_mini_S_hand <- d_by_location_cropped_mini_S %>%
-  select(Location, hand_detected)
-
-d_by_location_cropped_mini_A_face <- d_by_location_cropped_mini_A %>%
-  select(Location, face_openpose)
-
-d_by_location_cropped_mini_A_hand <- d_by_location_cropped_mini_A %>%
-  select(Location, hand_detected)
-
-# output (runs chi-squared tests in summary)
-faces_S_loc = summary(table(d_by_location_cropped_mini_S_face))
-hands_S_loc = summary(table(d_by_location_cropped_mini_S_hand))
-faces_A_loc = summary(table(d_by_location_cropped_mini_A_face))
-hands_A_loc = summary(table(d_by_location_cropped_mini_A_hand))
-
-# effect size estimates
-# cramersV(table(d_by_location_cropped_mini_S_face))
-# cramersV(table(d_by_location_cropped_mini_S_hand))
-# cramersV(table(d_by_location_cropped_mini_A_face))
-# cramersV(table(d_by_location_cropped_mini_A_hand))
-
-```
-
 ```{r DetByLocation, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands by location in which egocentric videos were filmed; each panel represents data from an individual child (location annotations were not yet available for Y).
 Each dot represents data from a week in which videos were filmed and are scaled by the number of frames."}
+
+all_to_plot$region <- as.factor(all_to_plot$region)
+all_to_plot$region <- relevel(all_to_plot$region, ref ="Faces (All)")
 
@@
   xlab('')+
-  theme_few(base_size=9) +
+  theme_few(base_size=8) +
   theme(legend.position = "bottom") +
@@
   scale_size_continuous(name = "Detections (Log 10)") +
-  scale_linetype_manual(values=c("solid", "solid","dashed"), name = "") +
-  scale_color_manual(values = c("#268bd2", "#dc322f","#DC7977"), name = "") +
+  scale_linetype_manual(values=c("solid", "dashed","solid","dashed"), name = "") +
+  scale_color_manual(values = c("#268bd2", "#51acec", "#dc322f","#ea5e5c"), name = "") +
   theme(legend.text=element_text(size=8))
 
+```
+
+```{r include=FALSE}
+### Chi-squared tests for location variability
+vid_data_by_location_A <- vid_data_by_location %>%
+  filter(child_id == "A") %>%
+  group_by(Location) %>%
+  summarize(num_faces_by_loc = sum(num_faces), num_no_faces_by_loc = sum(num_detect)-num_faces_by_loc,
+            num_hands_by_loc = sum(num_hands),  num_no_hands_by_loc = sum(num_detect)-num_hands_by_loc)
+
+vid_data_by_location_S <- vid_data_by_location %>%
+  filter(child_id == "S") %>%
+  group_by(Location) %>%
+  summarize(num_faces_by_loc = sum(num_faces), num_no_faces_by_loc = sum(num_detect)-num_faces_by_loc,
+            num_hands_by_loc = sum(num_hands),  num_no_hands_by_loc = sum(num_detect)-num_hands_by_loc)
+
+Faces_A <- cbind(vid_data_by_location_A$num_faces_by_loc, vid_data_by_location_A$num_no_faces_by_loc)
+Faces_S <- cbind(vid_data_by_location_S$num_faces_by_loc, vid_data_by_location_S$num_no_faces_by_loc)
+Hands_A <- cbind(vid_data_by_location_A$num_faces_by_loc, vid_data_by_location_A$num_no_faces_by_loc)
+Hands_S <- cbind(vid_data_by_location_S$num_hands_by_loc, vid_data_by_location_S$num_no_hands_by_loc)
+
+chisq.test(Faces_A)
+chisq.test(Faces_S)
+chisq.test(Hands_A)
+chisq.test(Hands_S)
 ```
@@
 # General Discussion
-
 Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the proportion of hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.
@@
 
-We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field-of-view to the upper 60% of the visual field of the videos to make the viewpoints comparable to those of headcams used in previous work [@Fausey2016].
+We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field-of-view to the center field of view the videos to make the viewpoints comparable to those of headcams used in previous work [@Fausey2016].
 Why might this be the case?
@@
 
-A coarse analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activites, showing differences across locations and between individual children.
+A coarse analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations and between individual children.
 Within a given, well-defined context---e.g., mealtime in kitchens---S saw more faces than A, and S saw more faces in the kitchen than in other locations.
@@
 Each of these positions offer the child differing degrees of visual access to faces and hands.
-While the social information in view may be variable across children in different activitiy contexts, these analyses suggest they could be stable within a given child's day-to-day experience.
+While the social information in view may be variable across children in different activity contexts, these analyses suggest they could be stable within a given child's day-to-day experience.
 
@@
 # Acknowledgements
-Blinded.
+Thanks to the creators of the SAYCam dataset who made this work possible and to Alessandro Sanchez for his contributions to the codebase.
+This work was funded by a Jacobs Foundation Fellowship to MCF, a John Merck Scholars award to MCF, and NSF #1714726 to BLL.
+
+\newpage
 
 # References
-```{r}
-# References will be generated automatically by Pandoc and included here.
-# The following code is some latex to format the bibliography. Do not remove it.
+```{r create_r-references}
+r_refs(file = "library.bib")
 ```
 
-\setlength{\parindent}{-0.1in} 
-\setlength{\leftskip}{0.125in}
-\noindent
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup

### 2020-07-03 openpose_detections/openpose_helpers.py
edge case bug for videos with no people detected

@@ -137,6 +137,8 @@ def json_list_to_npy(json_list):
         return frame_keypts
 
     max_num_people = max(len(frame['people']) for frame in json_list)
+    if max_num_people == 0:
+        max_num_people = 1
     flattened = np.array([frame_to_npy(frame_json, max_num_people)
                           for frame_json in json_list])
     return flattened

### 2021-04-16 analysis/_old_analysis/analysis_bb_fulldataset.Rmd
reorg analysis scripts -- port outdated/draft scripts to "old" folder

--- 2020-01-30 analysis/analysis_bb_fulldataset.Rmd
@@
 ```{r}
-load(file = '../data/all_bounding_boxes_three_kids_preprocessed.RData')
+load(file = '../data/preprocessed_data/all_bounding_boxes_three_kids_preprocessed.RData')
+```
+
+### Randomly sample some subset of the data
+```{r}
+num_to_sample = .1*length(bb_all_three$frame)
+bb_all_three_sample <- bb_all_three %>%
+  sample_frac(.1)
+```
+
+```{r}
+save(file = '../data/preprocessed_data/all_bounding_boxes_three_kids_preprocessed_small_sample.RData', bb_all_three_sample)
+```
+
+```{r}
+
+bb_all <- bb_all_three_sample
+```
+
+```{R}
+ggplot(bb_all_three_sample) +
+  geom_histogram(aes(x=height)) +
+  facet_wrap(~child_id)
 
@@
 ```{r}
-hands_by_size_by_frame <- bb_all %>%
-  filter(label=="hand") %>%
+hands <- bb_all %>%
+  filter(label=='hand')
+
+```
+
+```{r}
+hands_by_size_by_frame <- hands %>%
   group_by(vid_name, frame, age_days, child_id) %>%
-  summarize(num_hands = sum(label=="hand"), avg_area = mean(area), avg_x = mean(center_x), avg_y = mean(center_y))
+  summarize(num_hands = n(), avg_area = mean(height*width), avg_x = mean(center_x), avg_y = mean(center_y))
 

### 2021-04-16 analysis/_old_analysis/analysis_bb_fulldataset_2.Rmd
reorg analysis scripts -- port outdated/draft scripts to "old" folder

--- 2020-01-30 analysis/analysis_bb_fulldataset_2.Rmd
@@
 library(egg)
+library(here)
 theme_set(theme_few())
@@
 ```{r}
-load(file = '../data/all_bounding_boxes_three_kids_preprocessed.RData')
 

### 2021-04-16 analysis/_old_analysis/bb_check.Rmd
reorg analysis scripts -- port outdated/draft scripts to "old" folder

---
title: "BB_CHeck"
author: "Bria Long"
date: "5/2/2020"
output: html_document
---

# Load temp files if we are skipping steps above run if we are skipping steps above
```{r eval=FALSE}
## For cropped detections, need..
# 1. full set of detections (d_all from above)
# load(file='../data/preprocessed_data/openpose_detections_filtered_2020-01-29.RData')

# 2. bounding boxes from S and A (bb_SA)
load(file='../data/temp_data/SA_bounding_boxes_cleaned_2020-01-29.RData')

# 3. bounding boxes from Y (d_y) -- has different format than bb_SA, so diff name..
# load(file='../data/temp_data/Y_bounding_boxes_cleaned_2020-01-29.RData')
```

```{r}
load(file='../data/preprocessed_data/openpose_detections_filtered_2020-01-29.RData')
d_SA <- d_all %>%
  filter(child_id %in% c('S','A'))
```

```{r}
detections_cropped_SA <- bb_SA %>%
  filter(height<(.6)) %>%  ## 
  group_by(vid_name, frame, child_id) %>%
  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"), mean_height = mean(height), mean_top = mean(top))

detections_SA <- bb_SA %>%
  group_by(vid_name, frame, child_id) %>%
  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"), mean_height = mean(height), mean_top = mean(top))

```

```{r}
hands_bb <- detections_SA %>%
  filter(hand_detected==TRUE)

hands_dets <- d_SA %>%
  filter(hand_openpose==TRUE)

hands_compare <- hands_dets %>%
  left_join(hands_bb)

lacking_bb <- hands_compare %>%
  filter(is.na(hand_detected))

compare_one_vid_BB <- detections_SA %>%
  filter(vid_name=="A_20130531_0818_01")

compare_one_vid_dets <- d_SA %>%
  filter(vid_name=="A_20130531_0818_01")

joined_SA <- d_SA %>%
  left_join(detections_SA) %>%

no_bb <-  joined_SA %>%
  filter(hand_openpose==TRUE & hand_detected==FALSE)

```

## Look at height (i.e., vertical size) of hands
```{r}
bb_hands_y <- d_y %>%
   filter(label=='hand')

bb_hands <- bb_SA %>%
  filter(label=='hand')

bb_faces<- bb_SA %>%
  filter(label=='face')

```

```{r}
what <- bb_hands %>%
  filter(height>.6)
```

### 2021-04-16 analysis/_old_analysis/detector_validation 2.Rmd
reorg analysis scripts -- port outdated/draft scripts to "old" folder

--- 2020-01-15 analysis/detector_validation.Rmd
@@
 ```{r}
-load('../data/openpose_detections.RData')
+# load('../data/openpose_detections.RData')
 load('../data/ketan_gold_sample.RData')
@@
   mutate(count_locations = length(str_split(Location,',')[[1]]))
-
-# location_data <- meta %>%
-#   filter(count_locations==1) %>%
-
 ```
@@
 return_prf_short(m_seg$adult_hand_eval)
-
-# weird_gs_frames <- m_seg %>%
-#   mutate(weird = (label=='Child face')) %>%
-#   filter(weird==TRUE)
 

### 2021-04-16 analysis/_old_analysis/detector_validation.Rmd
reorg analysis scripts -- port outdated/draft scripts to "old" folder

--- 2021-04-16 analysis/_old_analysis/detector_validation 2.Rmd
@@
 ```{r}
-# load('../data/openpose_detections.RData')
-load('../data/ketan_gold_sample.RData')
+## 25K annotations are only on S/A
+load('../data/raw_data/openpose_detections_SA.RData')
+load('../data/raw_data/ketan_gold_sample.RData')
 ```
@@
 ```{r}
-right_side_up_file = "../data/video_right-side-up.csv"
+right_side_up_file = "../data/raw_data/SAYCAM_allocentric_videos.csv"
 right_side_up =read.csv(right_side_up_file)
@@
 flipped_videos <- right_side_up %>%
-  filter(right_side_up==1)
+  filter(allocentric==1)
 ```
@@
 ```{r}
-metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"
+metadata_file = "../data/raw_data/Metadata_SAYcam-2019-12-0922_54_28.csv"
 
@@
 ```{r}
-turk_annotations = "../data/turk_annotations_dec5.csv" # 20 turkers who did ~250 frames each
+turk_annotations = "../data/turk_data/turk_annotations_dec5.csv" # 20 turkers who did ~250 frames each
 gold_set = read.csv(turk_annotations)
@@
 ```{r eval=FALSE}
-turk_annotations_seg = "../data/turk_segmentations_hands_only_processed.csv" 
+turk_annotations_seg = "../data/turk_data/turk_segmentations_hands_only_processed.csv" 
 g_seg = read.csv(turk_annotations_seg)
@@
   do(return_prf(.$hand_eval_ketan))
+
+##
+prf_by_age_hands_both_kids <- d %>%
+  mutate(hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose)) %>%
+  group_by(age_day_bin) %>%
+  do(return_prf(.$hand_eval_ketan))
+```
+
+```{r}
+prf_by_child_hands <- d %>%
+  mutate(hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose)) %>%
+  group_by(vid_name_short) %>%
+  do(return_prf(.$hand_eval_ketan))
+
+prf_by_child_faces <- d %>%
+  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose)) %>%
+  group_by(child_id) %>%
+  do(return_prf(.$face_eval_ketan))
+
+```
+
+```{r}
+
+# not that useful since vids are so long for A
+
+# face_prf_by_vid <- d %>%
+#   mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose)) %>%
+#   group_by(vid_name_short, Databrary.Link) %>%
+#   do(return_prf(.$face_eval_ketan)) 
+# 
+# low_p_vids <-  face_prf_by_vid %>%
+#   filter(p<.2) %>%
+#   filter(num_detect > 40)
+```
+
+```{r}
+ggplot(prf_by_age_hands_both_kids, aes(x=age_day_bin, y=p, col=age_day_bin, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth()  +
+  ylab('F-score - Face detection')
+
 ```

### 2021-04-16 analysis/_old_analysis/vid_check.Rmd
reorg analysis scripts -- port outdated/draft scripts to "old" folder

---
title: "Untitled"
author: "Bria Long"
date: "7/18/2020"
output: html_document
---

```{r}
library(tidyverse)
library(here)
load(paste0(here::here(), '/data/raw_data/SA_bounding_boxes.RData'))
```

## calculate problems
```{r}
reload_data=TRUE

if (reload_data){
vid_index = 0

for (vid_file in op_files[1700:1710]) {
  vid_index = vid_index + 1

  vid_file_path_new= paste0(here::here(), '/data/op_outputs_per_vid_full_set/', vid_file)
  this_vid_data_new <- readRDS(vid_file_path_new)

   vid_file_path_old = paste0(here::here(), '/data/_old_op_outputs_per_vid/', vid_file)
   this_vid_data_old <- readRDS(vid_file_path_old)

   # check vid name to see if excluded vid
   this_vid_name_temp <- this_vid_data_new$vid_name[1]
   this_vid_name <- str_split(this_vid_name_temp,"[.]")[[1]][1]

   # only run if not excluded
   if (!this_vid_name %in% to_exclude$vid_name){

    assert_that(this_vid_data_new$vid_name[1] == this_vid_data_old$vid_name[1])
    # summarize hands/faces in each video
   summary_vid_data_new <- this_vid_data_new %>%
     group_by(frame, child_id, vid_name) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)  %>%
     group_by(child_id, vid_name) %>%
     summarize(num_hands = sum(hand_detected), num_faces = sum(face_detected), num_frames = length(hand_detected))

      summary_vid_data_old <- this_vid_data_old %>%
     group_by(frame, child_id, vid_name) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)  %>%
     group_by(child_id, vid_name) %>%
     summarize(num_hands = sum(hand_detected), num_faces = sum(face_detected), num_frames = length(hand_detected))

      video_diff <- summary_vid_data_new %>%
        mutate(diff_hands = num_hands - summary_vid_data_old$num_hands,
               diff_faces = num_faces - summary_vid_data_old$num_faces) %>%
        mutate(vid_name = vid_file)

  print(video_diff)

  # join it: 1 row = 1 video
   if (vid_index == 1 ){
     all_vid_diffs <- video_diff 
   }
   else if (vid_index > 1) {
   all_vid_diffs <- all_vid_diffs %>%
     full_join(video_diff)
   }
}
}
}
```

```{r}
old_no_na <- this_vid_data_old %>%
  filter(person<3) %>%
  filter(!is.na(mean_confidence))

new_no_na <- this_vid_data_new %>%
  filter(person<3) %>%
  filter(!is.na(mean_confidence))
```

```{r}
files_to_check = op_files[1:100]

all_vid_diffs <- all_vid_diffs %>%
  mutate(vid_name = str_split_fixed(vid_name, '_BBs.Rds',2)[,1])

orig_dectections_check <- d_all %>%
  filter(vid_name %in% all_vid_diffs$vid_name)

orig_dectections_check_by_vid <- orig_dectections_check %>%
  group_by(vid_name) %>%
  summarize(num_faces_orig_det = sum(face_openpose))

all_vid_diffs <- all_vid_diffs %>%
  left_join(orig_dectections_check_by_vid)
```

```{r}
first_vid_faces <- orig_dectections_check %>%
  filter(face_openpose==TRUE) %>%
  filter(vid_name == 'A_20130531_0818_01')

first_vid_faces_new_bb <- this_vid_data_new %>%
  filter(label=='face')

first_vid_faces_old_bb <- this_vid_data_old %>%
  filter(label=='face') %>%
  filter(!is.na(mean_confidence))

first_vid_faces_old_bb_all_NAs <- this_vid_data_old %>%
  filter(label=='face')

```

```{r}

face_frames <- summary_vid_data %>%
  filter(face_detected==TRUE)

frame_level_faces <- this_vid_data %>%
  right_join(face_frames) %>%
  filter(label=='face') %>%
  filter(!is.na(mean_confidence))

```

```{r}

old_faces <- this_vid_data_old %>%
  filter(label=='face') %>%
  filter(!is.na(mean_confidence)) %>%
  filter(person==0)

new_faces <- this_vid_data_new %>%
  filter(label=='face') %>%
  filter(!is.na(mean_confidence)) %>%
  filter(person==0)

```

```{r}
this_vid_name = 'A_20130531_0818_01'

test_vid <- df %>%
  filter(vid_name == this_vid_name)

summary_old_bbs_data <- test_vid %>%
  group_by(frame) %>%
    summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)  %>%
     summarize(num_hands = sum(hand_detected), num_faces = sum(face_detected))

new_file_path = paste0(here::here(), '/data/op_outputs_per_vid_full_set/', this_vid_name, '_BBs.Rds')
this_vid_data_new <- readRDS(new_file_path)

summary_new_bbs_data <- this_vid_data_new %>%
  group_by(frame) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)  %>%
     summarize(num_hands = sum(hand_detected), num_faces = sum(face_detected))

summary_new_bbs_data - summary_old_bbs_data
```

```{r}

> s = read_csv('sherlock.csv', col_names=FALSE)

s <- s %>%

```

### 2021-04-16 preprocessing/4_create_bounding_box_summaries.Rmd
reorganize preprocessing folder -- port old scripts to old folder

---
title: "bounding_box_preprocesing"
author: "Bria Long"
date: "7/16/2020"
output: html_document
---

# Basic data loading and setup
## Packages
```{r}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(lubridate)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(stringr)
library(here)
theme_set(theme_few())
```

## Info to compute ages
```{r}
bday_s_approx = lubridate::ymd(20121017)
bday_a_approx = lubridate::ymd(20120913)
bday_y_approx = lubridate::ymd(20180214)

bday = c(bday_s_approx,bday_a_approx, bday_y_approx)
child_id  = c('S','A','Y')
age_info = tibble(bday,child_id)
```

## Paths to raw outputs & datafiles
```{r}
op_file_dir = here::here("data/op_outputs_per_vid_full_set/")
op_files = dir(op_file_dir)
# op_files = op_files [1] # for testing

allocentric_file = here::here("data/raw_data/SAYCAM_allocentric_videos.csv")
to_exclude =read.csv(allocentric_file)

# get INCORRECT videos where allocentric videopoint 
to_exclude <- to_exclude %>%
  filter(allocentric==1) %>%
  rename(vid_name = video)
```

## Main detections: read in bounding box outputs from each vid, summarize and compile.
```{r}
reload_data=TRUE
# instead of loading each vid, load summary...
# load(here::here('data/preprocessed_data/all_vid_data_from_bbs_may2020.RData'))

# vid params
y_max = 480
x_max = 640

if (reload_data){
vid_index = 0
for (vid_file in op_files) {
  vid_index = vid_index + 1
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid_full_set/', vid_file)
   this_vid_data <- readRDS(vid_file_path)

   # if data wasn't normalized -- some (but not all!) Y videos
   if (this_vid_data$child_id[1]=='Y' &  max(this_vid_data$height, na.rm=TRUE)>1) {
     this_vid_data <- this_vid_data %>% 
        mutate(top = top/y_max, height = height/y_max, left = left/x_max, width = width/x_max)
   }

   this_vid <- this_vid_data %>%
      filter(!is.na(height)) %>%
      mutate(area = height * width) %>%
      filter(mean_confidence >.1 ) %>%
      group_by(label, child_id, vid_name) %>%
      summarize(num_detect = length(height), avg_area = median(area), avg_height = median(height), avg_width = median(width), avg_left = median(left), avg_top = median(top))

   empty_vid = (length(this_vid$num_detect)==0)
   if (empty_vid) {
     print(vid_file)
    }

   if (vid_index == 1 ){
     all_vid_bbs <- this_vid
   }
   else if (vid_index > 1 && empty_vid==FALSE) {
   all_vid_bbs <- all_vid_bbs %>%
     full_join(this_vid)
   }
}
}
```

```{r}
all_vid_bbs <- all_vid_bbs %>%
  left_join(age_info) %>%
  rowwise() %>%
  mutate(date_filmed = lubridate::ymd(str_split_fixed(vid_name,"_",4)[[2]])) %>%
  mutate(age_days = as.numeric(difftime(date_filmed,bday)) )

save(all_vid_bbs,file=here::here('data/preprocessed_data_2021/bounding_box_summaries.RData'))

```

### 2021-04-16 preprocessing/_old/4_preprocess_datasets.Rmd
reorganize preprocessing folder -- port old scripts to old folder

--- 2020-05-06 preprocessing/4_preprocess_datasets.Rmd
@@
 ```{r}
-load('../data/Y_bounding_boxes.RData') #df again as import
+load('../data/raw_data/Y_bounding_boxes.RData') #df again as import
 y_data <- df %>%
@@
 ## frame
-# height_px = 480; width_px = 640
-# bb_all_three <- d_y %>%
-#   filter(person==0) %>% # only rows with detections for now so comparable to bb_all
+height_px = 480; width_px = 640
+bb_all_three <- d_y %>%
+  filter(person==0) %>% # only rows with detections for now so comparable to bb_all
   # mutate(left = left*width_px, top = top*height_px, height = height*height_px, width = width*width_px) %>% #unnormalize data so comparable
-#   full_join(bb_all) %>% # join with SA bounding boxes
-#   mutate(center_x = left + width/2, center_y = top - height/2, area = width*height) 
-# 
-# save(bb_all_three, file = '../data/all_bounding_boxes_three_kids_preprocessed.RData')
-# remove(bb_all_three)
+  full_join(bb_SA) %>% # join with SA bounding boxes
+  mutate(center_x = left + width/2, center_y = top - height/2, area = width*height)
+
+save(bb_all_three, file = '../data/all_bounding_boxes_three_kids_preprocessed.RData')
+remove(bb_all_three)
 ```
 
-## Load temp files if we are skipping steps above run if we are skipping steps above
+# Load temp files if we are skipping steps above run if we are skipping steps above
 ```{r eval=FALSE}
@@
 detections_cropped_Y <- d_y %>%
-  filter(person==0) %>% #only get frames where detections so comparable
-  filter((height<(.6*480))) %>%  ## 
+  filter(person>0) %>% #only get frames where detections so comparable
+  mutate(top_real = top - height) %>% ## TOP IS ACTULALY BOTTOM AND 0,0 IS in the "TOP/LEFT" ! OMG.
+  mutate(center_y = top_real + height/2, center_x = left + width/2) %>%
+  filter(center_y<(.6*480)) %>%  ## 
   group_by(vid_name, frame, child_id, age_days) %>%
@@
 detections_cropped_SA <- bb_SA %>%
-  filter(height<(.6)) %>%  ## 
+  mutate(top_real = top - height) %>% ## TOP IS ACTULALY BOTTOM AND 0,0 IS TOP
+  mutate(center_y = top_real + height/2, center_x = left + width/2) %>%
+  filter(center_y<(.6)) %>%  ## 
   group_by(vid_name, frame, child_id) %>%
   summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))
+
 # join all together
@@
 save(d_cropped, file = paste0('../data/preprocessed_data/openpose_detections_filtered_cropped', today(), '.RData'))
+}
+```
+
+### Make center detections for Y/SA, join, make centered large data
+```{r}
+limit_lower =.2
+limit_upper =.8
+y_max = 480
+x_max = 640
+
+detections_center_Y <- d_y %>%
+  filter(person>0) %>% #only get frames where detections so comparable
+  mutate(top_real = top - height) %>%
+  mutate(center_y = top_real + height/2, center_x = left + width/2) %>%
+  filter(center_y<(limit_upper*y_max) & center_x<(limit_upper*x_max) & center_y>(limit_lower*y_max) & center_x>(limit_lower*x_max)) %>%  ## 
+  group_by(vid_name, frame, child_id, age_days) %>%
+  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))
+
+detections_center_Y <- detections_center_Y %>%
+ ungroup() %>%
+ mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id))
+
+## Make center detections in top 60% of frame for S,A
+detections_center_SA <- bb_SA %>%
+  mutate(top_real = top - height) %>%
+  mutate(center_y = top_real + height/2, center_x = left + width/2) %>%
+  filter(center_y<(limit_upper) & center_x<(limit_upper) & center_y>(limit_lower) & center_x>(limit_lower)) %>%  ## 
+  group_by(vid_name, frame, child_id) %>%
+  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))  
+# join all together
+all_center_detections <- detections_center_SA %>%
+  ungroup() %>%
+  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id)) %>%
+  full_join(detections_center_Y)
+```
+
+## Join back with big data structure
+```{r}
+## clean up workspace or else we run into memory limits
+# center detections
+remove(detections_center_Y)
+remove(detections_center_SA)
+
+# # bb data
+# remove(y_data)
+# remove(bb_all)
+
+## need to get "FALSE" on frames where we didn't have info to be able to compute proportions; uses d_all from earlier and fills it all back in
+all_center_detections <- all_center_detections %>%
+  select(-age_days, -child_id) %>%
+  mutate(face_openpose_center = face_detected, hand_openpose_center = hand_detected)
+
+d_center <- d_all %>% ## needs to be loaded!
+  as_tibble() %>%
+  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id)) %>%
+  select(vid_name, frame, child_id, age_days, face_openpose, hand_openpose) %>%
+  left_join(all_center_detections, by=c("vid_name","frame"))
+
+if (saveFiles){
+save(d_center, file = paste0('../data/preprocessed_data/openpose_detections_filtered_center2', today(), '.RData'))
 }

### 2021-04-16 preprocessing/_old/4_preprocess_datasets_per_vid.Rmd
reorganize preprocessing folder -- port old scripts to old folder

--- 2021-04-16 preprocessing/_old/4_preprocess_datasets.Rmd
@@
 saveFiles = TRUE
+```
+
+```{r}
+op_file_dir = "../data/op_outputs_per_vid/"
+op_files = dir(op_file_dir)
+
+```
+
+```{r}
+vid_index = 0
+for (vid_file in op_files) {
+  vid_index = vid_index + 1
+   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
+   this_vid_data <- readRDS(vid_file_path)
+   summary_vid_data <- this_vid_data %>%
+     group_by(frame, child_id, vid_name) %>%
+     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)
+
+   if (vid_index == 1 ){
+     all_vid_data <- summary_vid_data
+   }
+   else if (vid_index > 1) {
+   all_vid_data <- all_vid_data %>%
+     full_join(summary_vid_data)
+   }
+}
+```
+
+```{r}
+
 ```

### 2021-04-16 preprocessing/_old/4_preprocess_datasets_per_vid_2.Rmd
reorganize preprocessing folder -- port old scripts to old folder

--- 2020-06-02 preprocessing/compile_bb_outputs.Rmd
@@
 ---
-title: "SAYCAM Main analyses from bounding box outputs"
+title: "saycam bb outputs compile"
 author: "Bria Long"
-date: "6/2020"
+date: "1/9/2020"
 output: html_document
@@
 library(viridis)
+library(magick)
 library(stringr)
+library(lubridate)
+library(egg)
 library(here)
 theme_set(theme_few())
-```
-## OP bounding box outputs
-```{r}
-op_file_dir = here("/data/op_outputs_per_vid/")
-op_files = dir(op_file_dir)
+## are we saving outputs
+saveFiles = TRUE
 ```
 
-## Read in bounding box outputs from each vid, summarize and compile.
+```{r}
+op_file_dir = "../data/op_outputs_per_vid/"
+op_files = dir(op_file_dir)
+
+```
+
 ```{r}
@@
 ```
-
-## Data cleaning
-### Choose bins across which to analyze data
-```{r}
-bin_size = 7 # days
-min_age = min(all_vid_data$age_days, na.rm=TRUE)
-max_age = max(all_vid_data$age_days, na.rm=TRUE)
-bin_starts = seq(min_age-1, max_age+1,bin_size)
-bins = c(bin_starts, max_age)
-```
-
-### Regualrize vid names
-```{r}
-all_vid_data <- all_vid_data %>%
-  rowwise() %>%
-  mutate(vid_name_cleaned = str_split(vid_name,"[.]")[[1]][1])
-```
-
-### Load list of videos we should exclude -- allocentric videos
-```{r}
-allocentric_file = here("data/raw_data/SAYCAM_allocentric_videos.csv")
-to_exclude =read.csv(allocentric_file)
-
-# get INCORRECT videos where allocentric videopoint 
-to_exclude <- to_exclude %>%
-  filter(allocentric==1) %>%
-  rename(vid_name = video)
-```
-
-### Get rid of vids to exclude from allocentric file
-```{r}
-all_vid_data <- all_vid_data %>%
-  mutate(vid_name_old = vid_name) %>%
-  select(-vid_name) %>%
-  filter(!vid_name_cleaned %in% to_exclude$vid_name)
-```
-
-### Some videos still need metadata (!)
-```{r}
-missing_age <-all_vid_data %>%
-  filter(is.na(age_days))
-```

### 2021-04-16 preprocessing/_old/5_render_annotations.Rmd.R

@@ -1,0 +1,48 @@
+
+# Render out images based on annotations if desired
+## True positives on faces?
+```{r eval=FALSE}
+faces_only_op_cor <- m %>%
+  filter(faces == TRUE) %>%
+  filter(face_openpose == TRUE)
+
+# how about images where open pose got it? these should be most obvious
+dir.create(paste0('faces_tp/'))
+for (i in seq(1,length(faces_only_op_cor$full_image_path),1)){
+  image_read(as.character(faces_only_op_cor$full_image_path[i])) %>%
+    image_append(stack = FALSE) %>%
+    image_write(file.path(paste0("faces_tp/", faces_only_op_cor$short_image_path[i])))
+}
+```
+
+## False positives on facs?
+```{r eval=FALSE}
+to_write <- m %>%
+  filter(faces == FALSE) %>%
+  filter(face_openpose == TRUE)
+
+# how about images where open pose got it? these should be most obvious
+dir.create(paste0('faces_fp/'))
+for (i in seq(1,length(to_write$full_image_path),1)){
+  image_read(as.character(to_write$full_image_path[i])) %>%
+    image_append(stack = FALSE) %>%
+    image_write(file.path(paste0("faces_fp/", to_write$short_image_path[i])))
+}
+
+```
+
+## False negatives on faces?
+```{r eval=FALSE}
+to_write <- m %>%
+  filter(faces == TRUE) %>%
+  filter(face_openpose == FALSE)
+
+# how about images where open pose got it? these should be most obvious
+dir.create(paste0('faces_fn/'))
+for (i in seq(1,length(to_write$full_image_path),1)){
+  image_read(as.character(to_write$full_image_path[i])) %>%
+    image_append(stack = FALSE) %>%
+    image_write(file.path(paste0("faces_fn/", to_write$short_image_path[i])))
+}
+
+```

### 2021-04-16 analysis/bounding_boxes_april2021.Rmd
initial bounding box analyses script

---
title: "bounding_box_analyses_2021"
author: "Bria Long"
date: "4/15/2021"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(stringr)
library(here)
theme_set(theme_few())
```

```{r}
load(file=here::here('data/preprocessed_data_2021/bounding_box_summaries.RData'))
```

## construct age bins for plotting
```{r}
bin_size=90
min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
max_age = max(all_vid_bbs$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

all_vid_bbs <- all_vid_bbs %>%
  mutate(age_months = age_days/30.4) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) 
```

## restrict to face/hands for now
```{r}
face_hands <- all_vid_bbs %>%
  filter(!label=='pose') %>%
  mutate(avg_center_y = avg_top + avg_height/2, avg_center_x = avg_left + avg_width/2)
```

```{r}
ggplot(face_hands, aes(x=age_days/30.4, y=log(avg_area), col=label, size=num_detect)) +
  geom_point(alpha=.1) +
  facet_grid(~child_id) +
  geom_smooth(span=10000000) + # lol what
  ylab('Log (average area)') +
  xlab('Age in days')
```

```{r}
ggplot(face_hands, aes(x=age_days, y=log(avg_height), col=label, size=num_detect)) +
  geom_point(alpha=.1) +
  facet_grid(~child_id) +
  geom_smooth(span=10000000) + # lol what
  ylab('Log (average height)') +
  xlab('Age in days')
```

```{R}
ggplot(faces, aes(x=log(avg_area))) +
  geom_histogram(bin=100) +
  facet_grid(~child_id) +
  ggtitle('Log (average area) of faces') 
```

```{r}
ggplot(face_hands %>% filter(log(avg_area)>-10), aes(x=log(avg_area), col=label, fill=label)) +
  geom_histogram(alpha=.1, bins=100) +
  facet_wrap(~age_day_bin) +
  ggtitle('Average sizes of faces/hands') 
```

## Face hand density by age
```{r}
ggplot(face_hands, aes(x=avg_center_x , y = avg_center_y, size=num_detect, color=label)) +
  geom_point(alpha=.3) + 
  stat_density2d(aes(fill = label, color=label), geom="polygon", alpha=.6) +
  coord_fixed(ratio=.76) +
  ggtitle('Face/hand density') +
  ylab('') +
  xlab('') +
  theme_few(base_size=14) +
  theme(legend.position="right", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  scale_y_reverse() +
  facet_wrap(~age_day_bin)

```

### 2021-04-16 analysis/analysis_goldset.Rmd
update goldset exploratory script --> new filenames

@@
 
-### Get video/frame info from full cleaned dataset (saved)
-# load('../data/openpose_detections_filtered.RData')
+## Get video/frame info from full cleaned dataset (saved)
+# load('../data/preprocessed_data/openpose_detections_filtered_2020-01-29.RData')
 # vid_info <- d_all %>%
   # select(vid_name, frame, age_days, child_id)
-# save(vid_info, file = '../data/vid_info.RData')
+# save(vid_info, file = '../data/preprocessed_data/vid_info.RData')
+load('../data/preprocessed_data/vid_info.RData')
 
-load('../data/vid_info.RData')
-load('../data/ketan_gold_sample.RData')
+# load('../data/raw_data/vid_info.RData')
+load('../data/raw_data/ketan_gold_sample.RData')
 ```
@@
 flipped_videos <- right_side_up %>%
-  filter(right_side_up==1) %>%
+  filter(allocentric==1) %>%
   rename(vid_name = video)
@@
 ```{r}
-metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"
+metadata_file = "../data/raw_data/Metadata_SAYcam-2019-12-0922_54_28.csv"
 meta=read.csv(metadata_file) %>%
@@
 ```{r}
-bounding_boxes = "../data/gold_sample_bounding_boxes.csv" 
+bounding_boxes = "../data/raw_data/gold_sample_bounding_boxes.csv" 
 height_px = 480; width_px = 640
@@
 ```{r}
-turk_annotations_seg = "../data/turk_segmentations_hands_only_processed.csv" 
+turk_annotations_seg = "../data/turk_data/turk_segmentations_hands_only_processed.csv" 
 g_seg = read.csv(turk_annotations_seg) %>%
@@
   mutate(x_pos = left*width_px, y_pos = top*height_px) %>%
-  mutate(center_x = x_pos + width_x/2, center_y = y_pos - height_y/2) %>%
+  mutate(center_x = x_pos + width_x/2, center_y = y_pos - height_y/2) 
   filter(!is.na(child_id))
 
-bb_forheatmap <- bb %>%
-  filter(height>0)
+# bb_forheatmap <- bb %>%
+  # filter(height>0)
 ```
@@
 
-bb_check <- bb_all %>%
+bb_check <- bb %>%
   mutate(frame_ind = frame, vid_name_short = vid_name) %>%
@@
   filter(!is.na(full_image_path)) %>%
-  filter(mean_confidence > 0)
+  filter(mean_conf > 0)
 
-# dir.create(paste0('bbcheck/'))
-unique_images <- bb_check$full_image_path[300:350]
+dir.create(paste0('bbcheck_height/'))
+# unique_images <- bb_check$full_image_path[300:350]
 
-bb_check_face_tall <- bb_check_face %>%
-  filter(top>.7) %>%
-  filter(label=='face')
+bb_check_subset <- bb_check %>%
+  filter(height>.8) %>%
+  filter(label=='hand')
 
-bb_check_weird_vids <- bb_check %>%
-  filter(vid_name %in% weird_vids)
-
-unique_images = unique(bb_check_weird_vids$full_image_path)
+unique_images = unique(bb_check_subset$full_image_path)
 for (image in unique_images){
@@
 
-  # rect(a$x_pos, a$y_pos-a$height_y, a$x_pos+a$width_x, a$y_pos)
-
-  text(a$left*680, a$top*480, a$top)
-
-  annotated_file = paste0('bbcheck_sanity/',unique(a$vid_name_short), unique(a$frame_ind), 'OP-center.jpg')
+  rect(a$x_pos, a$y_pos, a$x_pos+a$width_x, a$y_pos - a$height)
+  # text(a$x_pos*680, a$y_pos*480, a$top)
+  # text(a$x_pos*680, a$y_pos*480, a$y_pos)
+  annotated_file = paste0('bbcheck_height/',unique(a$vid_name_short), unique(a$frame_ind), 'OP-big-hands.jpg')
   image_write(img, annotated_file)
@@
   filter(label=="face")
+
+```
+
+```{r}
+bb_hand_only <- bb_SA %>%
+  filter(label=='hand') 
+  # filter(height<.6)
+
+bb_face_only <- bb_SA %>%
+  filter(label=='face')
+
+# ggplot(bb_hand_only, aes(x=left, y=top)) +
+#   geom_point() + 
+#   stat_density_2d(aes(fill = ..level..), geom="polygon") +
+#   coord_fixed(ratio=1) +
+#   ggtitle('Hands')
 

### 2021-04-16 openpose_detections/run_openpose_per_user.py
reorg of openpose_detections files into subfolders

@@ -1,0 +1,51 @@
+# In[1]:
+import os
+import time
+import pickle
+import pandas as pd
+from config import *
+from run_openpose import run_openpose
+from openpose_helpers import extract_face_hand_presence
+# # Step 1: Run Openpose on videos
+# In[2]:
+#Edit these parameters in config.py
+print('VID_ROTATE: ', VID_ROTATE)
+print('OPENPOSE_OUTPUT: ', OPENPOSE_OUTPUT)
+print('OPENPOSE_CONDENSED_OUTPUT: ', OPENPOSE_CONDENSED_OUTPUT)
+"""Should be:
+VID_ROTATE:  180
+OPENPOSE_OUTPUT:  $GROUP_SCRATCH/Home_Headcam_new/outputs/openpose_raw_json
+OPENPOSE_CONDENSED_OUTPUT:  $GROUP_SCRATCH/Home_Headcam_new/outputs/openpose_condensed
+"""
+# In[3]:
+def run_openpose_on_vid_dir(vid_dir, op_output_dir=OPENPOSE_OUTPUT, condensed_output_dir=OPENPOSE_CONDENSED_OUTPUT, flipped_df_path=None):
+    vid_files = os.listdir(vid_dir)
+    vid_paths = [os.path.join(vid_dir, vid_name) for vid_name in vid_files]
+    run_openpose_on_vid_list(vid_paths, op_output_dir, condensed_output_dir, flipped_df_path)
+
+def run_openpose_on_vid_list(vid_list,  op_output_dir=OPENPOSE_OUTPUT, condensed_output_dir=OPENPOSE_CONDENSED_OUTPUT, flipped_df_path=None):
+    for i, vid_path in enumerate(vid_list):
+        print(f'{i+1}/{len(vid_list)}: {vid_path}')
+        wait_for_space(15)
+        run_openpose(vid_path, op_output_dir, 
+                     frame_rotate=VID_ROTATE,
+                     condensed_output_dir=condensed_output_dir,
+                     keypoint_scale=3)
+
+def wait_for_space(max_jobs):
+    time.sleep(5) #Allow for squeue to refresh properly
+    if queue_size() >= max_jobs:
+        print('Waiting for space in queue...')
+    while queue_size() >= max_jobs:
+        time.sleep(600)
+
+def queue_size():
+    size = get_ipython().getoutput('squeue -u $USER')
+    return len(size) - 1
[…]

### 2021-05-03 paper/preprint/paper_revised_submission_april2021_apa.Rmd
new .rmd integrating analyses and revamped data frames

--- 2020-06-30 paper/preprint/paper_revised_submission_june2020_apa.Rmd
@@
 output            : papaja::apa6_pdf
+                      include:
+                        after_body: appendix.tex
 ---
@@
 ## Read in data 
-load(here::here('data/data_preprint/all_vid_data_from_bbs_june2020.RData')) # all detections
-load(here::here('data/data_preprint/all_centered_vid_data_from_bbs_june2020.RData')) # centered cropped
+load(here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
 ```
@@
 ```{r}
-load(here::here('data/data_preprint/gold_sample_from_bbs_june2020.RData')) # gold sample detections
-load(here::here('data/data_preprint/gold_sample_annotations2020-01-31.RData')) # human annotations
+# load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021.RData')) # gold sample detections
+load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
+
+load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_all_detections.RData'))
+
+# all_gold_sample_frames_op_hc = load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_high_conf_detections.RData')) 
 ```
@@
 ### How large is the dataset we're analyzing?
-num_frames = sum(all_vid_data$num_detect)
+num_frames = sum(all_vid_data$num_frames)
 
 fps=30
-num_seconds = sum(all_vid_data$num_detect)/fps
+num_seconds = sum(all_vid_data$num_frames)/fps
 num_videos = length(unique(all_vid_data$vid_name))
@@
 Videos ^[All videos are available at https://nyu.databrary.org/volume/564 ] with technical errors or that were not taken from the egocentric perspective were excluded from the dataset.
-While data collection for the third child (Y) is still ongoing, here we analyze `r num_videos` videos, with a total duration of `r round(num_hours,2)` hours (>40 million frames).
+We analyze `r num_videos` videos, with a total duration of `r round(num_hours,2)` hours (>50 million frames).
 
-```{r examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=3.5, set.cap.width=T, num.cols.cap=2, fig.align = "center", fig.cap = "Example frames taken from the dataset, illustrating variability in the infant perspective across different locations.
+```{r examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=3.5, set.cap.width=T, num.cols.cap=2,  fig.fullwidth = TRUE, fig.align = "center", fig.cap = "Example frames taken from the dataset, illustrating variability in the infant perspective across different locations.
 OpenPose detections are shown overlaid on these images (green dots = face, red dots = hands, orange dots = pose)."}
@@
  hand_performance = return_prf_short(gold_sample$hand_eval_ketan)
+
+```
+
+```{r}
+## for high confidence detections
+gold_sample_hc <- gold_sample %>%
+  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
+  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
+  right_join(all_gold_sample_frames_op_hc) %>% # HIGH CONF DF
+  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))
+
+face_performance_hc = return_prf_short(gold_sample_hc$face_eval_ketan)
+hand_performance_hc = return_prf_short(gold_sample_hc$hand_eval_ketan)
 ```
@@
 ### Examine gold sample performance by child hands
-load(here::here('data/data_preprint/child_adult_hand_annotations_by_frame.RData'))
+load(here::here('data/preprocessed_data_2021/child_adult_hand_annotations_by_frame.RData'))
 # 
@@
 ### Load turk hand annotations with all bounding boxes (multiple dets per frame)
-load(here::here('data/data_preprint/hand_annotations_2020-01-29.RData'))
+load(here::here('data/preprocessed_data_2021/hand_annotations_2020-01-29.RData'))
 
@@
 
-To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A).
+To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A); XX frames with allocentric videos were excluded, as were these videos from the rest of analyses.
 Frames were jointly annotated for the presence of faces and hands by one author.
@@
 In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.
+We also evaluated OpenPose's performance while restricting detections to high-confidence detections (>.5 confidence, default threshold for visualization).
+For faces, we found that the F-score was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`.
+For hands, the F-score for high confidence detections `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
+Thus, as in prior work [@long2020automated], while precision was much highe for both faces and hands, the lower recall for high-confidence detection indicates that these lower-confidence detections still index the presence of social information in the infant view.
 
@@
 ## summary for all detections
-summary_by_age <- all_vid_data %>%
-  filter(!is.na(age_days)) %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+face_hand_by_age <- all_vid_data %>%
+  ungroup() %>%
+  tidyr::replace_na(list(faces_and_hands=0)) %>%
   group_by(age_day_bin, child_id) %>%
-  summarize(num_frames_total = sum(num_detect), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
-```
+  summarize(num_frames_total = sum(num_frames), 
+            # prop faces overall
+            num_faces = sum(num_faces), 
+            num_hands = sum(num_hands), 
+            prop_faces = num_faces / num_frames_total, 
+            prop_hands = num_hands / num_frames_total,
+            # in center FOV
+            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
+            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
+            prop_faces_center = num_faces_center / num_frames_total, 
+            prop_hands_center = num_hands_center / num_frames_total,
+            # detailed face info
+            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
+            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
+            # face/hand contingency
+            prop_faces_with_hands = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
+            prop_hands_with_faces = sum(faces_and_hands, na.rm=TRUE)/num_hands 
+            )
 
-```{r}
-## summary for centered detections
-summary_by_age_center <- all_vid_data_center %>%
-  filter(!is.na(age_days)) %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
-  group_by(age_day_bin, child_id) %>%
-  summarize(num_frames_total = sum(num_frames), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
 ```
@@
 ```{R}
-#### Make wide format for plotting
-wide_uncropped <- summary_by_age %>%
-  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
+#### Make longer format for plotting
+all_detections <- face_hand_by_age %>%
+  filter(num_frames_total > 2000) %>% # eliminate small data point that skews scaling
+  select(prop_faces, prop_hands, num_frames_total, age_day_bin, child_id) %>%
+  pivot_longer(cols = c(prop_faces, prop_hands), names_to = "region", values_to = "prop") %>%
   mutate(approach = "uncropped",
-         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
-  filter(num_frames_total > 5000) # eliminate small data point that skews scaling
+         region = ifelse(region == "prop_faces","Faces","Hands"))
 
-wide_center <- summary_by_age_center %>%
-  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
+centered <- face_hand_by_age %>%
+  filter(num_frames_total > 2000) %>% # eliminate small data point that skews scaling
+  select(prop_faces_center, prop_hands_center, num_frames_total, age_day_bin, child_id) %>%
+  gather(region, prop, prop_faces_center, prop_hands_center) %>%
   mutate(approach = "centered",
-         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
-  filter(num_frames_total > 5000) # eliminate small data point that skews scaling 
+         region = ifelse(region == "prop_faces_center","Faces","Hands"))
 ```
@@
 Dashed lines show estimated trend lines from proportion of faces/hands in view when detections are restricted to the center FOV, reducing the contribution of children's own hands."}
-
-ggplot(wide_uncropped, 
+ggplot(all_detections, 
        aes(x=age_day_bin, y=prop, 
@@
   geom_point(alpha=.2) +
-  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + # geom_smooth(show.legend = FALSE) or move these below legend?
-  geom_smooth(data = wide_center, span=10, aes(weight = num_frames_total), show.legend = FALSE, 
+  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
+  geom_smooth(data = centered, span=10, aes(weight = num_frames_total), show.legend = TRUE,
               lty = 2, span=10, se = FALSE) +
@@
   ggthemes::scale_color_solarized(name = "") + 
-  scale_size_continuous(name = "Detections (Log 10)") +
   theme(legend.text=element_text(size=8)) +
+  guides(size = FALSE) +
   theme(legend.position="bottom") 
-
 ```
@@
 However, the most striking result from these analyses is a much overall greater proportion of hands in view than have previously been reported [@Fausey2016].
-We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Figure \ref{fig:FacesAndHands}) or OpenPose annotations on the entire dataset (see solid lines in Figure \ref{fig:FacesAndHands}).
+We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Appendix Figure \ref{fig:goldSetSanity}) or OpenPose annotations on the entire dataset (see solid lines in Figure \ref{fig:FacesAndHands}).
 This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may be an underestimate of the proportion of hands in view.
@@
 
-As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_detect),2)*100`% to `r round(sum(all_vid_data_center$num_hands)/sum(all_vid_data_center$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_detect),2)*100`% to `r round(sum(all_vid_data_center$num_faces)/sum(all_vid_data_center$num_frames),3)*100`%.
+As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center)/sum(all_vid_data$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center)/sum(all_vid_data$num_frames),3)*100`%.
 This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
@@
 
+In a second set of analysis, we explored finer-grained changes in the ways in which infants’ experienced this social information across development, capitalizing on the fact that OpenPose provides not only face and hand detections but also positional keypoints.
+In particular, we explored this dataset with the idea that younger children may tend to see larger, complete faces towards the center of their visual field—that is, that have both eyes, nose, and a mouth in view—while older children may experience more incomplete views of faces.
+
+First, we explored the proportion of faces that were detected that tended to be “complete” faces—that is, faces where the eyes, mouth, and nose were all detected by OpenPose.
+Figure \ref{eye_distance} shows that roughly half of the faces detected by OpenPose were full-view faces, suggesting that infants’ are often seeing partial views of their caregiver’s faces.
+More generally, we found that the proportion of full faces in view roughly followed the proportion of faces in view, again converging with the findings of Fausey et al., 2016 showing a decrease in the proportion of faces in the infant view across early development.
+
+```{r}
+face_hand_detailed_plot <- face_hand_by_age %>%
+  gather(region, prop, prop_full_faces, prop_faces, prop_hands, prop_faces_and_hands) %>%
+  mutate(approach = "uncropped",
+         region = case_when(region == "prop_faces" ~"All faces",
+                            region == "prop_full_faces" ~ "Full faces (eyes, nose, mouth visible)",
+                            region == "prop_hands" ~ "All hands",
+                            region == "prop_faces_and_hands" ~ "Both hands and faces visible"),
+         child_name = case_when(child_id =='A' ~ "Child A",
+                      child_id == "S" ~ "Child S",
+                      child_id == "Y" ~ "Child Y")) %>%
+  filter(num_frames_total > 5000) # skews scaling of detections to have this 1 sparse age bin
+
+```
+
+```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of face, hand, 'full' face (i.e.
+nose, mouth, and nose visilbe), and joint face/hand detections as a function of age for each child in the dataset.
+Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range.
+}
+ggplot(face_hand_detailed_plot, 
+       aes(x=age_day_bin, y=prop, 
+           col=region)) +
+  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
+  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
+  ylab('Proportion Detections') + 
+  xlab('Age (Months)') +
+  ylim(0,.5) +
+  facet_grid(.~child_name) + 
+  theme_few(base_size=12) +
+  scale_color_manual(values = c( "#2048d6","#d62020","#751098","#142c83"), name = "") +
+  scale_size_continuous(name = "") +
+  guides(size = FALSE) +
+  theme(legend.text=element_text(size=8)) +
+  theme(legend.position="bottom") 
+```
+
+```{r}
+# eye distance... ugh
+eye_dist <- all_vid_data %>%
+  group_by(child_id, age_day_bin) %>%
+  summarize(eye_distance = mean(avg_eye_distance, na.rm=TRUE), num_frames_total = sum(num_frames)) %>%
+  filter(num_frames>2000)
+```
+
+```{r avgEyeDistance, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Average distance between eyes in faces detected as a function of age for each child in the dataset (each color = different child).
+Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range.
+}
+ggplot(eye_dist, 
+       aes(x=age_day_bin, y=eye_distance, 
+           col=child_id)) +
+  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
+  geom_smooth(method='lm', aes(weight = num_frames_total), show.legend = TRUE) + 
+  ylab('Average distance between eyes') + 
+  xlab('Age (Months)') +
+  theme_few(base_size=12) +
+  scale_color_brewer(palette="Dark2") +
+  guides(size = FALSE) +
+  theme(legend.text=element_text(size=12)) +
+  theme(legend.position="none", aspect.ratio=.75) 
+```
+
+```{r}
+# eye distance... ugh
+face_hand_contingency <- face_hand_by_age %>%
+  pivot_longer(c(prop_faces_with_hands, prop_hands_with_faces), values_to="prop", names_to = "region") %>%
+  mutate(region = case_when(
+    region == "prop_faces_with_hands" ~ "Proportion hands (given face detection)",
+    region == "prop_hands_with_faces" ~ "Proportion faces (given hand detection)"))
+```
+
+```{r faceHandContingency, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=5, fig.height=3, fig.cap = "Face hand contingnecy }
+ggplot(face_hand_contingency, 
+       aes(x=age_day_bin, y=prop, 
+           col=child_id)) +
+  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
+  geom_smooth(method='lm', aes(weight = num_frames_total), show.legend = TRUE) + 
+  ylab('Average distance between eyes') + 
+  xlab('Age (Months)') +
+  theme_few(base_size=12) +
+  facet_grid(~region) +
+  scale_color_brewer(palette="Dark2") +
+  guides(size = FALSE) +
+  theme(legend.text=element_text(size=12)) +
+  theme(legend.position="none", aspect.ratio=.75) 
+```
+
+In addition, we found faces tended to be farther away from children across age (restricting our analysis to faces where both eyes were detected).
+Figure X shows the average interpupillary distance on faces as a function of each child’s age at the time of recording, showing a trend from larger, closer faces (with a larger interpupillary distance) to smaller faces that were farther away (with a smaller interpupillary distance).
+We saw relatively similar trends across all three children in the dataset, and a linear mixed-effect model confirmed a main effect of age (STATS; see repository for full model specification).
+However, when we examined the size of all faces and hands in the infant view, we found consistency across development (see Appendix, Figure X): while faces (and full body poses) were of course bigger than hands on average, these properties were relatively stable across development and children (see Appendix, Figure X).
+
+Next, we explored where in the visual field children tended to see faces and hands, suspecting, perhaps, that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank, 2012.
+As expected, faces tended to appear in the upper visual field vs.
+hands, which tended to be more centrally located.
+Figure XX shows the average position of faces and hands in the visual field; each dot represents the average position from one video within a given age range.
+However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ -- and likely adults’ -- visual environment from 6 months of age.
+
 ```{r eval=FALSE}
-summary_by_age_days_centered <- all_vid_data_center %>%
-  group_by(age_days,child_id) %>%
-  summarize(num_faces = sum(num_faces), num_hands = sum(num_hands), num_detect = sum(num_frames)) %>%
-  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect) 
-summary_by_age_days_centered$age_scale <- scale(summary_by_age_days_centered$age_days, scale = FALSE)[,1] / 30.3
-
 summary_by_age_days <- all_vid_data %>%
   group_by(age_days,child_id) %>%
-  summarize(num_faces = sum(num_faces), num_hands = sum(num_hands), num_detect = sum(num_frames)) %>%
-  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect) 
+  summarize(num_faces = sum(num_faces), 
+            num_faces_center = sum(num_faces_center), 
+            num_hands = sum(num_hands), 
+            num_hands_center = sum(num_hands_center), 
+            num_detect = sum(num_frames)) %>%
+  mutate(prop_faces = num_faces / num_detect, 
+         prop_hands = num_hands / num_detect,
+         prop_faces_center = num_faces_center / num_detect, 
+          prop_hands_center = num_hands_center / num_detect)
+
+long_summary_by_age_days <- summary_by_age_days %>%
+  select(prop_faces, prop_hands, age_days, child_id) %>%
+  pivot_longer(col = c(prop_faces, prop_hands), names_to="region", values_to = "prop")
+
 summary_by_age_days$age_scale <- scale(summary_by_age_days$age_days, scale = FALSE)[,1] / 30.3
+long_summary_by_age_days$age_scale <- scale(long_summary_by_age_days$age_days, scale = FALSE)[,1] / 30.3
 
@@
 # run lmer models -- faces over age
-faces_model_full_age_out = summary(lmer(prop_faces ~ age_scale + (1 | child_id), data = summary_by_age_days_centered))
+faces_model_full_age_out = summary(lmer(prop_faces_center ~ age_scale + (1 | child_id), data = summary_by_age_days))
 
 # hands over age
-hands_model_full_age_out = summary(lmer(prop_hands ~ age_scale + (1 | child_id), data = summary_by_age_days_centered))
+hands_model_full_age_out = summary(lmer(prop_hands_center ~ age_scale + (1 | child_id), data = summary_by_age_days))
 
@@
 # main effect of ages and regions; no interaction.
-wide_centered_age_days <- summary_by_age_days_centered %>%
-  gather(region, prop, prop_faces, prop_hands) %>%
-  mutate(approach = "cropped",
-         region = ifelse(region == "prop_faces","Face","Hands"))
-
-diff_model_full_age_out = summary(lmer(prop ~ region*age_scale + (1 | child_id), data = wide_centered_age_days))
+diff_model_full_age_out = summary(lmer(prop ~ region*age_scale + (1 | child_id), data = long_summary_by_age_days))
 ```
@@
   \hline
-(Intercept) & 0.100 & 0.014 & 1.955 & 7.049 & 0.021 \\ 
-  Age  & -0.002 & 0.001 & 386.972 & -4.461 & 0.000 \\ 
+(Intercept)  9.845e-02  1.049e-02  1.956e+00   9.386  0.01198 * 
+Age   -1.418e-03  4.503e-04  4.310e+02  -3.150  0.00175 **
    \hline
@@
   \hline
-(Intercept) & 0.166 & 0.011 & 2.082 & 15.340 & 0.004 \\ 
-  Age & -0.002 & 0.001 & 380.308 & -3.114 & 0.002 \\ 
+(Intercept)  1.612e-01  8.930e-03  1.881e+00   18.05   0.0040 **
+Age   -9.987e-04  5.945e-04  4.287e+02   -1.68   0.0937 
    \hline
@@
 videos_included = sum(!is.na(meta$Location) & meta$count_locations==1)
-
-# percentage_of_dataset = sum(faces_vs_hands_to_plot$num_detect)/length(d_all$frame)
-# num_frames = sum(faces_by_location_to_plot$num_detect)
 ```
@@
 vid_data_by_location <- all_vid_data %>%
-  mutate(num_frames = num_detect) %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
   left_join(meta) %>%
@@
   filter(count_locations==1) 
-
-vid_data_centered_by_location <- all_vid_data_center %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
-  left_join(meta) %>%
-  filter(!is.na(Location)) %>%
-  filter(count_locations==1)
-
 # 
 vid_data_by_location$Location = droplevels(vid_data_by_location$Location)
-vid_data_centered_by_location$Location = droplevels(vid_data_centered_by_location$Location) # get rid of unused levels (more than 1 location)
 
@@
 levels_to_modify = levels(vid_data_by_location$Location)
-levels_to_modify = levels(vid_data_centered_by_location$Location)
 levels_to_modify[10] = 'Outside' # Outside on property
@@
 # reset levels for both cropped/uncropped
-levels(vid_data_centered_by_location$Location) <- levels_to_modify
 levels(vid_data_by_location$Location) <- levels_to_modify
+
+percentage_of_dataset = sum(vid_data_by_location$num_frames)/sum(all_vid_data$num_frames)
+num_frames = sum(vid_data_by_location$num_frames)
 
@@
 ```{r}
-face_hand_by_location_centered<- vid_data_centered_by_location %>%
-  group_by(Location,child_id,age_day_bin) %>%
-  summarize(prop_faces = sum(num_faces)/sum(num_frames), prop_hands = sum(num_hands)/sum(num_frames), num_detect = sum(num_frames))  %>%
-  group_by(Location) %>%
-  filter(num_detect >12000)
-
 face_hand_by_location <- vid_data_by_location %>%
   group_by(Location,child_id,age_day_bin) %>%
-  summarize(prop_faces = sum(num_faces)/sum(num_frames), prop_hands = sum(num_hands)/sum(num_frames), num_detect = sum(num_frames))  %>%
+  summarize(num_detect = sum(num_frames),prop_faces = sum(num_faces)/num_detect, prop_hands = sum(num_hands)/num_detect,  prop_hands_center =  sum(num_hands_center, na.rm=TRUE)/num_detect, prop_faces_center = sum(num_faces_center, na.rm=TRUE)/num_detect)  %>%
   group_by(Location) %>%
-  filter(num_detect >12000)
+  filter(num_detect > 2000)
 
@@
 ## Get rid of any locations where we didn't have enough data to make a CI (not more than 1 age_bin)
-hands_to_plot_centered <- face_hand_by_location_centered %>%
+hands_to_plot_centered <- face_hand_by_location %>%
   group_by(Location, child_id) %>%
-  multi_boot_standard(col="prop_hands") %>%
+  multi_boot_standard(col="prop_hands_center") %>%
   mutate(region = "Hands (Center)") %>%
   ungroup %>%
-  left_join(face_hand_by_location_centered) %>%
-  mutate(prop = prop_hands) %>%
-  select(-prop_faces, -prop_hands) %>%
+  left_join(face_hand_by_location) %>%
+  mutate(prop = prop_hands_center) %>%
   filter(!is.na(ci_lower))
 
-faces_to_plot_centered <- face_hand_by_location_centered %>%
+faces_to_plot_centered <- face_hand_by_location %>%
   group_by(Location, child_id) %>%
-  multi_boot_standard(col="prop_faces") %>%
+  multi_boot_standard(col="prop_faces_center") %>%
   mutate(region = "Face (Center)") %>%
   ungroup %>%
-  left_join(face_hand_by_location_centered) %>%
-  mutate(prop = prop_faces) %>%
-  select(-prop_faces, -prop_hands) %>%
+  left_join(face_hand_by_location) %>%
+  mutate(prop = prop_faces_center) %>%
   filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter
@@
   mutate(prop = prop_faces) %>%
-  select(-prop_faces, -prop_hands) %>%
   filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter
@@
   mutate(prop = prop_hands) %>%
-  select(-prop_faces, -prop_hands) %>%
   filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter
@@
   xlab('')+
-  theme_few(base_size=8) +
+  theme_few(base_size=18) +
   theme(legend.position = "bottom") +
@@
   group_by(Location) %>%
-  summarize(num_faces_by_loc = sum(num_faces), num_no_faces_by_loc = sum(num_detect)-num_faces_by_loc,
-            num_hands_by_loc = sum(num_hands),  num_no_hands_by_loc = sum(num_detect)-num_hands_by_loc)
+  summarize(num_faces_by_loc = sum(num_faces), num_no_faces_by_loc = sum(num_frames)-num_faces_by_loc,
+            num_hands_by_loc = sum(num_hands),  num_no_hands_by_loc = sum(num_frames)-num_hands_by_loc)
 
@@
 Faces_S <- cbind(vid_data_by_location_S$num_faces_by_loc, vid_data_by_location_S$num_no_faces_by_loc)
-Hands_A <- cbind(vid_data_by_location_A$num_faces_by_loc, vid_data_by_location_A$num_no_faces_by_loc)
+
+Hands_A <- cbind(vid_data_by_location_A$num_hands_by_loc, vid_data_by_location_A$num_no_hands_by_loc)
 Hands_S <- cbind(vid_data_by_location_S$num_hands_by_loc, vid_data_by_location_S$num_no_hands_by_loc)

### 2021-05-04 analysis/bounding_boxes_april2021.Rmd
exploratory script for bb analysis

@@
 ```{r}
-load(file=here::here('data/preprocessed_data_2021/bounding_box_summaries.RData'))
+load(file=here::here('data/preprocessed_data_2021/bounding_box_summaries_all.RData'))
 ```
@@
 ```{r}
-bin_size=90
+bin_size=7
 min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
@@
   mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) 
-```
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))  %>%
+ mutate(avg_center_y = avg_top + avg_height/2, avg_center_x = avg_left + avg_width/2) %>%
+  filter(!avg_area==0) # a very few bounding boxes with zero areas (all keypoints on one plane as faces)
 
-## restrict to face/hands for now
-```{r}
-face_hands <- all_vid_bbs %>%
-  filter(!label=='pose') %>%
-  mutate(avg_center_y = avg_top + avg_height/2, avg_center_x = avg_left + avg_width/2)
 ```
@@
 ```{r}
-ggplot(face_hands, aes(x=age_days/30.4, y=log(avg_area), col=label, size=num_detect)) +
+avg_area_by_age <- all_vid_bbs %>%
+  group_by(age_day_bin, child_id, label) %>%
+  summarize(avg_area = mean(avg_area), num_detect = sum(num_detect)) %>%
+  mutate(label = factor(label, levels = c('pose','face','hand'), labels = c('Full pose','Faces','Hands'))) %>%
+  mutate(child_id = as.factor(child_id))
+
+ggplot(avg_area_by_age, aes(x=age_day_bin, y=log(avg_area), col=child_id, size=num_detect)) +
   geom_point(alpha=.1) +
-  facet_grid(~child_id) +
-  geom_smooth(span=10000000) + # lol what
+  facet_grid(~label) +
+  geom_smooth(method='lm') + 
   ylab('Log (average area)') +
-  xlab('Age in days')
+  xlab('Age in days') +
+  scale_color_brewer(palette="Dark2", name = "Child") +
+  guides(size = FALSE)
+
 ```
@@
 ```{r}
-ggplot(face_hands, aes(x=age_days, y=log(avg_height), col=label, size=num_detect)) +
+summary(lmer(log(avg_area) ~ age_days + (1|child_id), data=all_vid_bbs %>% filter(label=='hand')))
+
+summary(lmer(log(avg_area) ~ age_days + (1|child_id), data=all_vid_bbs %>% filter(label=='face')))
+
+summary(lmer(log(avg_area) ~ age_days + (1|child_id), data=all_vid_bbs %>% filter(label=='pose')))
+
+```
+
+```{r}
+ggplot(face_hands , aes(x=age_days, y=log(avg_area), col=label, size=num_detect)) +
   geom_point(alpha=.1) +
   facet_grid(~child_id) +
-  geom_smooth(span=10000000) + # lol what
+  geom_smooth(method='lm') + 
   ylab('Log (average height)') +
   xlab('Age in days')
+
+summary(lmer(log(avg_area) ~ age_days + label + (1|child_id), data  = face_hands %>% filter(!avg_area==0) %>% filter(label=='hand'))
 ```

### 2021-05-04 paper/preprint/appendix.Rmd
start appendix rmd

---
title: "Appendix"
author: "Bria Long"
date: "5/3/2021"
output: html_document
---

```{r}
library(tidyverse)
library(ggplot2)
library(ggthemes)
```

```{r}
## Read in preprocessed data 
load(here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections

## all bounding boxes
load(file=here::here('data/preprocessed_data_2021/bounding_box_summaries.RData'))

```

```{r}
## Load in gold sample detections
load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_all_detections.RData'))

# all_gold_sample_frames_op_hc = load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_high_conf_detections.RData')) 
```

```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_faces_with_hands = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_hands_with_faces = sum(faces_and_hands, na.rm=TRUE)/num_hands 
            )

all_detections <- face_hand_by_age %>%
  filter(num_frames_total > 2000) %>% # eliminate small data point that skews scaling
  select(prop_faces, prop_hands, num_frames_total, age_day_bin, child_id) %>%
  pivot_longer(cols = c(prop_faces, prop_hands), names_to = "region", values_to = "prop") %>%
  mutate(approach = "uncropped",
         region = ifelse(region == "prop_faces","Faces","Hands"))

```

```{r}
# Function to evaluate detectors
evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

# function to return prfs
 return_prf_short = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  return(c(p,r,f))
 }

#

# join human and OP detections
gold_sample <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))

 ## output prfs
 face_performance = return_prf_short(gold_sample$face_eval_ketan)
 hand_performance = return_prf_short(gold_sample$hand_eval_ketan)

```

```{r}
## Move to appendix
## get out summary by age for goldset hand-labeled frames
vid_info <- all_vid_data  %>%
  select(child_id, vid_name, age_days, age_day_bin)

summary_by_age_gold <- gold_sample %>%
  left_join(vid_info) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = n(), num_faces = sum(face_present_ketan), num_hands = sum(hand_present_ketan), prop_faces= num_faces / num_frames_total, prop_hands = num_hands / num_frames_total)
```

```{r}
### Examine gold sample performance by child hands
load(here::here('data/preprocessed_data_2021/child_adult_hand_annotations_by_frame.RData'))

gold_sample_no_child_hands <- gold_sample %>%
  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
  replace_na(list(child_hand_seg = FALSE)) %>% # replace NAs with false (frames not in annotations (NAs) did not have hands) 
  filter(child_hand_seg==FALSE) %>% # now these are counted as frames where OP didn't need to detect something
  mutate(hand_eval_adults = evaluate_detector(hand_present_ketan, hand_detected))

summary_by_age_adult_hands_gold <- gold_sample_no_child_hands %>%
  left_join(vid_info) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = n(), num_faces = sum(face_present_ketan), num_hands = sum(hand_present_ketan), prop_faces = num_faces / num_frames_total, prop_hands = num_hands / num_frames_total)
```

```{r}
goldset <- summary_by_age_gold %>%
  gather(region, prop, prop_faces, prop_hands) %>%
  mutate(approach = "goldset",
         region = ifelse(region == "prop_faces","Faces","Hands"))

goldset_adult_hands <- summary_by_age_adult_hands_gold %>%
  gather(region, prop, prop_faces, prop_hands) %>%
  mutate(approach = "goldset",
         region = ifelse(region == "prop_faces","Faces","Hands"))

```

# Face/hand detections relative to human annotations
```{r goldSetSanity, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset. Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range. Dashed lines show estimated trend lines from proportion of faces/hands in view when analyzing the gold set of frames made by human annotators. Dotted lines show trend lines from the goldset when frames when children's own hand were detected." }

ggplot(all_detections %>% filter(child_id %in% c('S','A')), 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
  geom_smooth(data = goldset_adult_hands, span=10, aes(weight = num_frames_total), show.legend = FALSE,
              lty = 2, span=10, se = FALSE) +
  geom_smooth(data = goldset, span=10, aes(weight = num_frames_total), show.legend = FALSE,
              lty = 3, span=10, se = FALSE) +
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.6) +
  facet_grid(.~child_id) + 
  theme_few(base_size=9) +
  ggthemes::scale_color_solarized(name = "") + 
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=8)) +
  theme(legend.position="bottom")

```

# Distribution of faces and hands in the visual field
We explored where in the visual field children tended to see faces and hands, suspecting, perhaps, that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank, 2012.  As expected, faces tended to appear in the upper visual field vs. hands, which tended to be more centrally located.  However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ -- and likely adults’ -- visual environment from 6 months of age.

```{r}
bin_size=30
min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
max_age = max(all_vid_bbs$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

all_vid_bbs <- all_vid_bbs %>%
  mutate(age_months = age_days/30.4) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=paste0(as.character(round(bin_starts/30,1)), ' m.o.'))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  mutate(avg_center_y = avg_top + avg_height/2, avg_center_x = avg_left + avg_width/2) %>%
  filter(num_detect > 100)

```

```{r}

Caption="Each panel shows the average position of faces and hands in the visual field; each dot represents the average position from one video within a given age range."

ggplot(all_vid_bbs %>% filter(label %in% c('face','hand')), aes(x=avg_center_x , y = avg_center_y, size=num_detect, color=label)) +
  geom_point(alpha=.3) + 
  stat_density2d(aes(fill = label, color=label), geom="polygon", alpha=.6) +
  coord_fixed(ratio=.76) +
  # ggtitle('Face/hand density') +
  ylab('') +
  xlab('') +
  theme_few(base_size=14) +
  theme(legend.position="right", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  scale_y_reverse() +
  facet_wrap(~age_day_bin) +
  guides(size = FALSE) +
  ggthemes::scale_color_solarized(name = "")  +
  ggthemes::scale_fill_solarized(name = "") 
```

### 2021-05-04 paper/preprint/appendix.Rmd
start appendix

@@
 
+<!-- We also evaluated OpenPose's performance while restricting detections to high-confidence detections (>.5 confidence, default threshold for visualization).
+For faces, we found that the F-score was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`.
+For hands, the F-score for high confidence detections `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
+Thus, as in prior work [@long2020automated], while precision was much highe for both faces and hands, the lower recall for high-confidence detection indicates that these lower-confidence detections still index the presence of social information in the infant view.
+-->
+
 ```{r}

### 2021-05-04 preprocessing/step0_get_human_annotations/face_hands/analysis/preprocess_turk_detections.Rmd
restructure preprocessing folder

--- 2020-05-06 preprocessing/human_annotations/face_hands/analysis/preprocess_turk_detections.Rmd
@@
 library(magick)
+library(here)
+library(lubridate)
 library(egg)
@@
 # Preprocessing
-## Not finished cleaning this up yet...
 ```{r}
@@
   group_by(WorkerId) %>%
-  summarize(count_images = n(), avg_time = mean(WorkTimeInSeconds))
+  summarize(avg_time = mean(WorkTimeInSeconds))
 
-jd$response = jd$`Answer.trial-1.label`
-agreement <- jd %>%
-  group_by(Input.img_src1) %>%
-  summarize(agree = response[1] == response[2])
 ```
@@
 ## Would like to get rando responses in .label field here:
-
 ### Sometimes we get NAs and they end up in ".label fields", but not every trial has them (so it throws errors in a loop).
@@
 Starter code is below.
-
 # empty_labels = as.character(array(matrix(data=NA, nrow=1, ncol=num_workers)))
@@
 ```{r}
-write_csv(d.filtered,'turk_annotations_dec5.csv')
+write_csv(d.filtered,paste0(here::here, '/data/turk_data/face_hand_detections', today(), '.csv'))
 ```

### 2021-05-04 preprocessing/step0_get_human_annotations/face_hands/experiment_segmentation/generate_annotation_frames_face_only.Rmd
restructure preprocessing folder

---
title: "Generate annotation frames"
author: "Bria Long"
date: "1/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(egg)
theme_set(theme_few())
```

### Instead load in detections and ketan's gold set annotations from preprocessed Rdata files
```{r}
load('../data/raw_data/ketan_gold_sample.RData')
```

### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
```{r}
right_side_up_file = "../data/video_right-side-up.csv"
right_side_up =read.csv(right_side_up_file)

# get INCORRECT videos
flipped_videos <- right_side_up %>%
  filter(right_side_up==1)
```

### Get out frame urls for frames where ketan annotated hands
```{r}
## preprocess all frame urls
frame_urls = "../data/frame_urls.csv"
gold_frame_urls =read.csv(frame_urls) %>%
    as_tibble() %>%
    mutate(short_image_path = str_split_fixed(img_src1,'/',7)[,7]) %>%
    mutate(sample_ind = str_split_fixed(short_image_path,"-",3)[,1], frame_ind_temp = str_split_fixed(short_image_path,"-",3)[,3], vid_name = str_split_fixed(short_image_path,"-",3)[,2]) %>%
  mutate(sample_ind = as.numeric(sample_ind), frame_ind = as.numeric(str_split_fixed(frame_ind_temp,".jpg",3)[,1])) %>%
  mutate(vid_name_short = str_split_fixed(vid_name,".mp4",2)[,1]) %>%
  select(vid_name, frame_ind, short_image_path, img_src1) %>%
  rename(frame=frame_ind) %>%
  mutate(vid_name = as.character(vid_name))

## grab frames were hands were present
hand_present_frames <- ketan_gold %>%
  filter(hand_present==1) %>%
  select(vid_name,frame) %>%
  rowwise() %>%
  mutate(vid_name_short = str_split(vid_name,"[.]")[[1]][1]) %>%
  filter(!vid_name_short %in% flipped_videos$video) %>%
  mutate(vid_name = as.character(vid_name)) %>%
  left_join(gold_frame_urls)

## write out to csv
hand_present_filepaths <- hand_present_frames %>%
  select(img_src1)

write_csv(hand_present_filepaths,'../data/hands_present_goldset.csv')

# render out some of these...
# dir.create(paste0('hands_present/'))
# for (i in seq(1,length(hand_present_frames$img_src1),1)){
#   image_read(as.character(hand_present_frames$img_src1[i])) %>%
#   image_append(stack = FALSE) %>%
#   image_write(file.path(paste0("hands_present/", hand_present_frames$short_image_path[i])))
# }

```

### 2021-05-04 preprocessing/step4_create_bounding_box_summaries.Rmd
restructure preprocessing folder

--- 2021-04-16 preprocessing/4_create_bounding_box_summaries.Rmd
@@
 ```{r}
-op_file_dir = here::here("data/op_outputs_per_vid_full_set/")
+op_file_dir = here::here("data/op_outputs_per_vid_rds/")
 op_files = dir(op_file_dir)
@@
 # instead of loading each vid, load summary...
-# load(here::here('data/preprocessed_data/all_vid_data_from_bbs_may2020.RData'))
 
@@
   vid_index = vid_index + 1
-   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid_full_set/', vid_file)
+   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid_rds/', vid_file)
    this_vid_data <- readRDS(vid_file_path)
@@
       filter(!is.na(height)) %>%
+      filter(mean_confidence > 0) %>% # sanity
       mutate(area = height * width) %>%
-      filter(mean_confidence >.1 ) %>%
       group_by(label, child_id, vid_name) %>%
@@
 
-save(all_vid_bbs,file=here::here('data/preprocessed_data_2021/bounding_box_summaries.RData'))
+save(all_vid_bbs,file=here::here('data/preprocessed_data_2021/bounding_box_summaries_all.RData'))
 

### 2021-05-04 preprocessing/step5_preprocess_fullset_from_bb_outputs.Rmd
restructure preprocessing folder

 ---
title: "SAYCAM preprocessing analyses from bounding box outputs"
author: "Bria Long"
date: "6/2020, updated 4/2021"
output:
  pdf_document: default
  html_document: default
---

# Basic data loading and setup
## Packages
```{r}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(stringr)
library(here)
theme_set(theme_few())
```

## Info to compute ages
```{r}
bday_s_approx = lubridate::ymd(20121017)
bday_a_approx = lubridate::ymd(20120913)
bday_y_approx = lubridate::ymd(20180214)

bday = c(bday_s_approx,bday_a_approx, bday_y_approx)
child_id  = c('S','A','Y')
age_info = tibble(bday,child_id)
```

## Paths to raw outputs & datafiles
```{r}
# toggle between each of these folders / dataset types
dataset_dir = "/data/op_outputs_per_vid_rds/"; dataset_type = "all_detections"
# dataset_dir = "/data/op_outputs_per_vid_rds_high_conf/"; dataset_type = "high_conf_detections"

op_file_dir = here::here(dataset_dir)
op_files = dir(op_file_dir)
# op_files = op_files [1] # for testing

allocentric_file = here::here("data/raw_data/SAYCAM_allocentric_videos.csv")
to_exclude =read.csv(allocentric_file)

# get INCORRECT videos where allocentric videopoint 
to_exclude <- to_exclude %>%
  filter(allocentric==1) %>%
  rename(vid_name = video)
```

## Main detections: read in bounding box outputs from each vid, summarize and compile.
```{r}
reload_data=TRUE

# cropping paramts
limit_lower =.2
limit_upper =.8
# vid params
y_max = 480
x_max = 640

if (reload_data){
vid_index = 0

for (vid_file in op_files) {
  vid_index = vid_index + 1

  vid_file_path = paste0(here::here(), dataset_dir, vid_file)
  this_vid_data <- readRDS(vid_file_path)
   #
  assert_that(this_vid_data$frame[1]==0) # make sure we have all frames in this rds

   # check vid name to see if excluded vid
   this_vid_name_temp <- this_vid_data$vid_name[1]
   this_vid_name <- str_split(this_vid_name_temp,"[.]")[[1]][1]

   # only run if not excluded
   if (!this_vid_name %in% to_exclude$vid_name){

   # replace negative eye distances with NAs
   this_vid_data <- this_vid_data %>%
      mutate(eye_distance = replace(eye_distance, eye_distance<0,NA))

   # make sure we only have high conf detectino
   if (dataset_type=='high_conf_detections'){
      this_vid_data <- this_vid_data %>%
         filter(conf_thres==.5)
      assert_that(length(this_vid_data$frame)>0)
   }

    # summarize hands/faces in each video
   summary_vid_data <- this_vid_data %>%
     group_by(frame, child_id, vid_name, full_face, eye_distance) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)  %>%
     group_by(child_id, vid_name) %>%
     summarize(num_hands = sum(hand_detected), num_faces = sum(face_detected), num_full_faces = sum(full_face, na.rm=TRUE), avg_eye_distance = mean(eye_distance, na.rm=TRUE))

   # full_face_data <- this_vid_data %>%
   #    filter(label=='face') %>%
   #    group_by(full_face) %>%
   #    summarize(eye_dist = mean(eye_distance,na.rm=TRUE))

   # get face/hand detections that occured together
   faces_and_hands <- this_vid_data %>%
      group_by(frame, child_id, vid_name) %>% # group at frame level first
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0) %>%
      filter(hand_detected==TRUE) %>%
      group_by(child_id, vid_name) %>% # now at the video level
     summarize(faces_and_hands = sum(face_detected)) # count how many faces/hands

   # crop detections to center and get hands/faces
  this_vid_data_center <- this_vid_data %>%
     mutate(center_y = top + height/2, center_x = left + width/2) %>% # get center_x and y
     filter(center_y<(limit_upper) & center_x<(limit_upper) & center_y>(limit_lower) & center_x>(limit_lower)) %>%   # filter within parameters
     group_by(frame, child_id, vid_name) %>% # group at frame level first
     summarize(hand_detected_center = sum(!is.na(mean_confidence[label=='hand']))>0, face_detected_center = sum(!is.na(mean_confidence[label=='face']))>0)

   faces_and_hands_center <- this_vid_data_center %>%
      filter(hand_detected_center==TRUE) %>%
      group_by(child_id, vid_name) %>% # now at the video level
     summarize(face_and_hands_center = sum(face_detected_center)) # count how many faces/hands  together

    # join datasets for center cropped
    summary_vid_data_center <- this_vid_data_center %>%
       group_by(child_id, vid_name) %>% # now at the video level
       summarize(num_hands_center = sum(hand_detected_center), num_faces_center = sum(face_detected_center)) %>%  # count how many faces/hands
      left_join(faces_and_hands_center)

   #  save conf thres & num franes
   this_conf_thres = mean(this_vid_data$conf_thres,na.rm=TRUE)
   num_frames = length(unique(this_vid_data$frame)) # count frames before doing anything

  # create summary from both normal and cropped, clean vid_name, get age info
  joined_summary <- summary_vid_data %>%
    left_join(faces_and_hands) %>%
    left_join(summary_vid_data_center) %>%
    rowwise %>%
    mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>% 
    left_join(age_info) %>%
    mutate(date_filmed = lubridate::ymd(str_split_fixed(vid_name,"_",4)[[2]])) %>%
    mutate(age_days = as.numeric(difftime(date_filmed,bday)) ) %>%
    select(-bday, -date_filmed) %>%
    mutate(conf_thres = this_conf_thres) %>%
    mutate(num_frames = num_frames)

  # join it: 1 row = 1 video
   if (vid_index == 1 ){
     all_vid_data <- joined_summary 
   }
   else if (vid_index > 1) {
   all_vid_data <- all_vid_data %>%
     full_join(joined_summary)
   }

    # assert that we have actual center face/hands data 
  # check that length of videos without face/hands in center is not equal to the num of videos in dataframe, 
  assert_that(!sum(is.na(all_vid_data$face_and_hands_center))==length(all_vid_data$vid_name))
}
}
}
```

### Choose bins across which to aggregate data & save out
```{r}
bin_size = 7 # days
min_age = min(all_vid_data$age_days, na.rm=TRUE)
max_age = max(all_vid_data$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

all_vid_data <- all_vid_data %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) 
```

```{r}
save(all_vid_data, file = here::here(paste0('data/preprocessed_data_2021/all_vid_data_from_bbs_', dataset_type, '.RData')))

```

## Gold sample detections only -- specific frame

### Get detections from gold sample videos only -- have to do this to get the SPECIFIC FRAMES (not videos) from which things were sampled....
```{r}
reload_data=TRUE
# redo gold sample 
if (reload_data){
vid_index = 0
## load gold sample annotations

load(here('data/data_cogsci/gold_sample_annotations2020-01-31.RData')) # gold_sample
gold_sample_frames <- gold_sample %>%
  select(-X, -level_0) %>%
  select(vid_name, frame) %>%
  mutate(vid_name = str_split(vid_name,"[.]")[[1]][1])

gold_sample_vids <- unique(gold_sample_frames$vid_name)

for (vid_file in op_files) {

   # to check progress
   vid_index = vid_index + 1
   if ((vid_index %% 100)==0) { print (vid_file) }

   # get vid level data
   vid_file_path = paste0(here::here(), dataset_dir, vid_file)
   this_vid_data <- readRDS(vid_file_path)
   this_vid_name_temp <- this_vid_data$vid_name[1]
   this_vid_name <- str_split(this_vid_name_temp,"[.]")[[1]][1]

   # if it's one of the vids from gold sample
   if (this_vid_name %in% gold_sample_vids){
   # and not excluded
   if (!this_vid_name %in% to_exclude$vid_name){

   frames_to_get <- gold_sample_frames %>%
     filter(vid_name == this_vid_name)

   # now get vid level data
   gold_sample_op <- this_vid_data %>%
     filter(frame %in% frames_to_get$frame) %>%
     mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
     group_by(frame, vid_name, child_id) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)

   # compile vid-level summaries 
   if (vid_index == 1){
     all_gold_sample_frames_op <- gold_sample_op
   }
   else if (vid_index > 1) {
   all_gold_sample_frames_op <- all_gold_sample_frames_op %>%
     full_join(gold_sample_op)
   }
}
}
}
}

## Add in age data
all_gold_sample_frames_op <-all_gold_sample_frames_op %>%
  left_join(age_info) %>%
  mutate(date_filmed = lubridate::ymd(str_split_fixed(vid_name,"_",4)[[2]])) %>%
  mutate(age_days = as.numeric(difftime(date_filmed,bday)) )

save(all_gold_sample_frames_op, file = here::here('data/preprocessed_data_2021/',paste0('gold_sample_from_bbs_2021_',dataset_type,'.RData')))
```

### 2021-05-04 preprocessing/extra_bounding_box_dev.py

@@ -1,133 +1,0 @@
-import numpy as np
-import pandas as pd
-from openpose_helpers import recover_npy
-import os
-​
-test_file =  '/Users/brialong/Documents/GitHub/headcam-algo/data/test_data/A_20130609_0827_04.json'
-vid_df = pd.read_json(open(test_file, 'r'))
-v = recover_npy(vid_df)
-​
-def get_bounding_box(X, Y, conf):
-	if np.sum(conf)==0:
-		return [np.nan, np.nan, np.nan, np.nan]
-	left = np.min(X)
-	top = np.min(Y) # (0,0) is top left
-	height = np.max(Y) - top
-	width = np.max(X) - left
-	return [height, width, left, top, conf]
-
-def get_eye_distance(face_x, face_y, face_conf):
-	pupil_left_X = face_x[68]
-	pupil_right_X = face_x[69]
-	pupil_dist = pupil_right_X - pupil_left_X # 0,0 is origin, so right-left
-	if sum(face_conf)==0:
-		pupil_dist=np.nan
-	return pupil_dist
-
-def is_full_face(face_x, face_y, face_conf, conf_thres):
-	mouth = range(48,59)
-	left_eye = range(36,40)
-	right_eye = range(42,47)
-	mouth_conf = np.mean(face_conf[mouth])
-	left_eye_conf = np.mean(face_conf[left_eye])
-	right_eye_conf = np.mean(face_conf[right_eye])
-	full_face = (mouth_conf>conf_thres) & (left_eye_conf>conf_thres) & (right_eye_conf>conf_thres)
-	return full_face
-
-def get_face_info(detection, conf_thres):
-	X = detection[0]
-	Y = detection[1]
-	conf = detection[2]
-	face_x = X[18:88]
-	face_y = Y[18:88]
-	face_conf = conf[18:88]
-	face_bb = get_bounding_box(face_x, face_y, np.mean(face_conf))
-	full_face = is_full_face(face_x, face_y, face_conf, conf_thres)
-	eye_distance = get_eye_distance(face_x, face_y, face_conf)
-	face_info = [face_bb, full_face, eye_distance]
-	return face_info
-
-def get_face_hand_bounding_boxes(detection):
-	# (X, Y, confidence) x 130 keypoints
-	X = detection[0]
-	Y = detection[1]
-	conf = detection[2]
-	pose_x = X[:18]
-	pose_y = Y[:18]
[…]

### 2021-05-04 preprocessing/step2_get_bounding_boxes_per_vid.py

@@ -1,0 +1,152 @@
+import os
+import numpy as np
+import pandas as pd
+
+# load flattened numpy arrays per video, extracts bounding boxes for hands and faces
+# per frame, and saves as long format CSV (one row per bounding box, maximum 9 per frame)
+
+VID_PATH = "/scratch/groups/mcfrank/Home_Headcam_new/outputs/openpose_flattened/" 
+OUT_PATH = "/scratch/groups/mcfrank/Home_Headcam_new/bounding_boxes_with_face_info/"
+#VID_PATH = "openpose_flattened"
+#f = "A_20130531_0818_01.npy" # for testing
+
+frame_size = {'x':640, 'y':480} # pixels; keypoint x,y coords are normalized 0-1, but go out of frame occasionall
+# min=-.22, max=1.16
+
+files = os.listdir(VID_PATH)
+
+# 130 for pose (18), face (70), L hand (21), and R hand (21) keypoints, in that order
+# https://github.com/CMU-Perceptual-Computing-Lab/openpose/blob/master/doc/02_output.md
+
+
+def get_eye_distance(face_x, face_y, face_conf):
+	pupil_left_X = face_x[68]
+	pupil_right_X = face_x[69]
+	pupil_dist = pupil_right_X - pupil_left_X # 0,0 is origin, so right-left
+	if sum(face_conf)==0:
+		pupil_dist=np.nan
+	return pupil_dist
+
+def is_full_face(face_x, face_y, face_conf, conf_thres):
+	mouth = range(48,60) # range = n:n-1
+	left_eye = range(36,42)
+	right_eye = range(42,48)
+	nose = range(27,36)
+	mouth_conf = np.mean(face_conf[mouth])
+	left_eye_conf = np.mean(face_conf[left_eye])
+	right_eye_conf = np.mean(face_conf[right_eye])
+	nose_conf = np.mean(face_conf[nose])
+	full_face = (mouth_conf>conf_thres) & (left_eye_conf>conf_thres) & (right_eye_conf>conf_thres) & (nose_conf>conf_thres)
+	return full_face
+
+def get_all_bounding_boxes(vid_name,detection,i,p,conf_thres=0):
+	# (X, Y, confidence) x 130 keypoints
+	X = detection[0]
+	Y = detection[1]
+	conf = detection[2]
+	# pose
+	pose_x = X[:18]
+	pose_y = Y[:18]
+	pose_conf  = conf[:18]
+	# face
[…]

### 2021-05-04 preprocessing/step3_merge_per_vid_bounding_boxes.R

@@ -1,0 +1,40 @@
+
+# load bounding boxes from openpose detections from the entire dataset
+# (created in 2_get_bounding_boxes_per_vid.py using numpy vectors in $GROUP_SCRATCH/Home_Headcam_new/openpose_saycam_flattened)
+
+require(data.table)
+require(here)
+require(stringr)
+
+INDIR = "/scratch/groups/mcfrank/Home_Headcam_new/bounding_boxes" # CSV files from the npy arrays
+OUTDIR = "/scratch/groups/mcfrank/Home_Headcam_new/bounding_boxes_Rds/"
+
+files <- list.files(INDIR) 
+# A_20140630_2117_04_bounding_boxes.csv had no detections
+print(length(files))
+
+df <- data.frame()
+
+#had to specify columns to get rid of the total column
+for (i in 1:length(files)) {
+  tmp <- fread(paste("/scratch/groups/mcfrank/Home_Headcam_new/bounding_boxes", files[i], sep='/'), stringsAsFactors = F) 
+  if(ncol(tmp)==9) {
+    tmp$V1 = NULL
+    this_vid = str_remove(files[i], "_bounding_boxes.csv")
+    tmp$child_id = strsplit(files[i], '_')[[1]][1]
+    tmp$vid_name = this_vid
+    tmp = subset(tmp, mean_confidence!=0)
+    #df <- rbindlist(list(df, tmp)) # , use.names = T
+    #df = rbind(df, tmp)
+    saveRDS(tmp, file=paste0(OUTDIR,this_vid,"_BBs.Rds"))
+  } else {
+    print(paste("check file: ",files[i])) # improper number of columns
+  }
+}
+
+#df <- df %>% mutate(height = ifelse(child_id=="Y", height/480, height),
+#                    width = ifelse(child_id=="Y", width/640, width))
+
+#df$area = df$height * df$width
+#save(df, file="all_bounding_boxes.RData")
+

### 2021-05-04 preprocessing/2_get_bounding_boxes_per_vid.py
fix minor typo
(low conf left hands were in high_conf files)

@@ -10,7 +10,7 @@ OUT_PATH = "/scratch/groups/mcfrank/Home_Headcam_new/bounding_boxes/"
 #VID_PATH = "openpose_flattened"
 #f = "A_20130531_0818_01.npy" # for testing
 
-frame_size = {'x':640, 'y':480} # pixels; keypoint x,y coords are normalized 0-1, but go out of frame occasionall
+frame_size = {'x':640, 'y':480} # pixels; keypoint x,y coords are normalized 0-1, but go out of frame occasionally
 # min=-.22, max=1.16
 
 files = os.listdir(VID_PATH)
@@ -145,7 +145,7 @@ for f in files:
 						if ~np.isnan(rhand_h[8]):
 							df_hc.append(rhand_h)
 						if ~np.isnan(lhand_h[8]):
-							df_hc.append(lhand)
+							df_hc.append(lhand_h)
 				# add a row indicating no detection for that frame (makes the file much larger)
 				if not detection:
 					df.append([vid_name, i, np.nan, 'none', np.nan,np.nan, np.nan,np.nan,np.nan,np.nan,np.nan, np.nan])

### 2021-05-04 preprocessing/2_get_bounding_boxes_per_vid.py
better error handling

@@ -129,7 +129,7 @@ for f in files:
 						detection = True
 						# Error: this_detection not defined, GK substituted v[i][p]
 						pose, face, rhand, lhand = get_all_bounding_boxes(vid_name,v[i][p],i,p,0)  # all detections
-						pose_h, face_h, rhand_h, lhand_h = get_all_bounding_boxes(vid_name,v[i][p],i,p,.5)  # high confidence detections
+						pose_h, face_h, rhand_h, lhand_h = get_all_bounding_boxes(vid_name,v[i][p],i,p, high_conf_thres)  # high confidence detections
 						# append all bbs
 						df.append(pose)
 						if ~np.isnan(face[8]): # 8th column = mean confidence (as outputted by get_all_bounding_boxes)
@@ -160,6 +160,7 @@ for f in files:
 			df_hc.columns = col_names
 			df_hc.fillna('') # replace NaNs with emptiness
 			df_hc.to_csv(os.path.join(OUT_PATH, vid_name+"_bounding_boxes_high_conf.csv"), index=False)
-		except:
+		except Exception as e:
 			print("Problem processing "+vid_name)
+			print(e)
 

### 2021-05-04 paper/preprint/appendix.Rmd
reworking sections to accomodate new bb analyses

@@
 ```{r}
-bin_size=30
+bin_size=7
 min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
@@
   mutate(age_months = age_days/30.4) %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=paste0(as.character(round(bin_starts/30,1)), ' m.o.'))) %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=floor(bin_starts/30.4))) %>%
   mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
@@
 -->
+
+```{r}
+CV_faces <- all_vid_bbs %>%
+  filter(label=='face') %>%
+  group_by(age_day_bin,child_id) %>%
+  summarize(cv_x_pos = sd(avg_center_x)/mean(avg_center_x)*100, cv_y_pos = sd(avg_center_y)/mean(avg_center_y)*100, num_detect = sum(num_detect), num_vids = n()) %>%
+  pivot_longer(cols = c(cv_y_pos, cv_x_pos), values_to = "CV", names_to = "position") %>%
+  mutate(position = factor(position, levels = c("cv_x_pos","cv_y_pos"), labels = c("X Position", "Y Position")))
+
+```
+
+```{r}
+ggplot(CV_faces, aes(x=age_day_bin , y = CV, size=num_detect, color=child_id)) +
+  geom_point(alpha=.3) + 
+  facet_wrap(~position)  +
+  geom_smooth(method='lm') +
+  scale_color_brewer(palette='Dark2') + 
+  ylab('Coefficient of variation for face position') +
+  xlab('Age (in months)') +
+  guides(size = FALSE)
+```
 

### 2021-05-04 paper/preprint/paper_revised_submission_april2021_apa.Rmd
minor intro edits
reworking sections to accomodate new bb analyses

@@
 output            : papaja::apa6_pdf
-                      include:
-                        after_body: appendix.tex
 ---
@@
 ```{r}
-## Read in data 
+# Read in data 
+## Face/hand detections by video
 load(here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
@@
 ```{r}
-# load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021.RData')) # gold sample detections
+# load bounding box summaries by video
+load(file=here::here('data/preprocessed_data_2021/bounding_box_summaries_all.RData'))
+```
+
+```{r}
+# gold sample annotatios and detedctinos for these specific frames
 load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
-
 load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_all_detections.RData'))
@@
 Videos ^[All videos are available at https://nyu.databrary.org/volume/564 ] with technical errors or that were not taken from the egocentric perspective were excluded from the dataset.
-We analyze `r num_videos` videos, with a total duration of `r round(num_hours,2)` hours (>50 million frames).
+We analyze `r num_videos` videos, with a total duration of `r round(num_hours,2)` hours (>40 million frames).
 
@@
 ## Detection Validation
-
 ```{r}
@@
  hand_performance = return_prf_short(gold_sample$hand_eval_ketan)
-
 ```
 
-```{r}
+```{r eval=FALSE,include=FALSE}
 ## for high confidence detections
-gold_sample_hc <- gold_sample %>%
-  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
-  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
-  right_join(all_gold_sample_frames_op_hc) %>% # HIGH CONF DF
-  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))
-
-face_performance_hc = return_prf_short(gold_sample_hc$face_eval_ketan)
-hand_performance_hc = return_prf_short(gold_sample_hc$hand_eval_ketan)
+# gold_sample_hc <- gold_sample %>%
+#   select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
+#   mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
+#   right_join(all_gold_sample_frames_op_hc) %>% # HIGH CONF DF
+#   mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))
+# 
+#  
+# face_performance_hc = return_prf_short(gold_sample_hc$face_eval_ketan)
+# hand_performance_hc = return_prf_short(gold_sample_hc$hand_eval_ketan)
 ```
@@
 
-To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A); XX frames with allocentric videos were excluded, as were these videos from the rest of analyses.
+To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A); `r  24000-length(gold_sample$face_openpose)` frames with allocentric videos were excluded, as were these videos from the rest of analyses.
 Frames were jointly annotated for the presence of faces and hands by one author.
@@
 In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.
-We also evaluated OpenPose's performance while restricting detections to high-confidence detections (>.5 confidence, default threshold for visualization).
-For faces, we found that the F-score was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`.
-For hands, the F-score for high confidence detections `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
-Thus, as in prior work [@long2020automated], while precision was much highe for both faces and hands, the lower recall for high-confidence detection indicates that these lower-confidence detections still index the presence of social information in the infant view.
 
@@
             # face/hand contingency
-            prop_faces_with_hands = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
-            prop_hands_with_faces = sum(faces_and_hands, na.rm=TRUE)/num_hands 
-            )
+            prop_joint_given_faces = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
+            prop_joint_given_hands = sum(faces_and_hands, na.rm=TRUE)/num_hands,
+            prop_joint_given_faces_center = sum(face_and_hands_center, na.rm=TRUE)/num_faces_center, 
+            prop_joint_given_hands_center = sum(face_and_hands_center, na.rm=TRUE)/num_hands_center)
 
@@
 
-We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands that were in view for each child.^[All analyses and preprocessed data files for this paper are available at https://tinyurl.com/detecting-social-info] Data from videos were binned according to the age of the child (in weeks).
-First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:FacesAndHands}); in contrast, we did not observe an increase in the proportion of hands in view, but rather a slight decrease.
+We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands detected for each child.^[All analyses and preprocessed data files for this paper are available at https://tinyurl.com/detecting-social-info] Data from videos were binned according to the age of the child (in weeks).
+First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:FacesAndHands}), in keeping with prior findings [@Fausey2016]; in contrast, we did not observe an increase in the proportion of hands in view.
 These effects were quantified with two separate linear mixed-models (see Tables 1 & 2).^[Face/hand detections were binned across each week of filming.
@@
 This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may be an underestimate of the proportion of hands in view.
-Nonetheless, one reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees.
+In fact, analysis the human annotations underscores revealed a much higher proportion of hands relative to faces than the automated annotations.
+
+One reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees.
 This larger FOV may have allowed the SAYCam cameras to capture not only the presence of a social partner’s hands interacting with objects or gestures, but also the children’s own hands, leading to more frequent hand detections.
 
-As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center)/sum(all_vid_data$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center)/sum(all_vid_data$num_frames),3)*100`%.
+As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%.
 This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
 Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:FacesAndHands}).
+We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure\ref{fig:goldSetSanity}).
 
-In a second set of analysis, we explored finer-grained changes in the ways in which infants’ experienced this social information across development, capitalizing on the fact that OpenPose provides not only face and hand detections but also positional keypoints.
-In particular, we explored this dataset with the idea that younger children may tend to see larger, complete faces towards the center of their visual field—that is, that have both eyes, nose, and a mouth in view—while older children may experience more incomplete views of faces.
-
-First, we explored the proportion of faces that were detected that tended to be “complete” faces—that is, faces where the eyes, mouth, and nose were all detected by OpenPose.
-Figure \ref{eye_distance} shows that roughly half of the faces detected by OpenPose were full-view faces, suggesting that infants’ are often seeing partial views of their caregiver’s faces.
-More generally, we found that the proportion of full faces in view roughly followed the proportion of faces in view, again converging with the findings of Fausey et al., 2016 showing a decrease in the proportion of faces in the infant view across early development.
-
-```{r}
-face_hand_detailed_plot <- face_hand_by_age %>%
-  gather(region, prop, prop_full_faces, prop_faces, prop_hands, prop_faces_and_hands) %>%
-  mutate(approach = "uncropped",
-         region = case_when(region == "prop_faces" ~"All faces",
-                            region == "prop_full_faces" ~ "Full faces (eyes, nose, mouth visible)",
-                            region == "prop_hands" ~ "All hands",
-                            region == "prop_faces_and_hands" ~ "Both hands and faces visible"),
-         child_name = case_when(child_id =='A' ~ "Child A",
-                      child_id == "S" ~ "Child S",
-                      child_id == "Y" ~ "Child Y")) %>%
-  filter(num_frames_total > 5000) # skews scaling of detections to have this 1 sparse age bin
-
-```
-
-```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of face, hand, 'full' face (i.e.
-nose, mouth, and nose visilbe), and joint face/hand detections as a function of age for each child in the dataset.
-Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range.
-}
-ggplot(face_hand_detailed_plot, 
-       aes(x=age_day_bin, y=prop, 
-           col=region)) +
-  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
-  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
-  ylab('Proportion Detections') + 
-  xlab('Age (Months)') +
-  ylim(0,.5) +
-  facet_grid(.~child_name) + 
-  theme_few(base_size=12) +
-  scale_color_manual(values = c( "#2048d6","#d62020","#751098","#142c83"), name = "") +
-  scale_size_continuous(name = "") +
-  guides(size = FALSE) +
-  theme(legend.text=element_text(size=8)) +
-  theme(legend.position="bottom") 
-```
-
-```{r}
-# eye distance... ugh
-eye_dist <- all_vid_data %>%
-  group_by(child_id, age_day_bin) %>%
-  summarize(eye_distance = mean(avg_eye_distance, na.rm=TRUE), num_frames_total = sum(num_frames)) %>%
-  filter(num_frames>2000)
-```
-
-```{r avgEyeDistance, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Average distance between eyes in faces detected as a function of age for each child in the dataset (each color = different child).
-Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range.
-}
-ggplot(eye_dist, 
-       aes(x=age_day_bin, y=eye_distance, 
-           col=child_id)) +
-  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
-  geom_smooth(method='lm', aes(weight = num_frames_total), show.legend = TRUE) + 
-  ylab('Average distance between eyes') + 
-  xlab('Age (Months)') +
-  theme_few(base_size=12) +
-  scale_color_brewer(palette="Dark2") +
-  guides(size = FALSE) +
-  theme(legend.text=element_text(size=12)) +
-  theme(legend.position="none", aspect.ratio=.75) 
-```
-
-```{r}
-# eye distance... ugh
-face_hand_contingency <- face_hand_by_age %>%
-  pivot_longer(c(prop_faces_with_hands, prop_hands_with_faces), values_to="prop", names_to = "region") %>%
-  mutate(region = case_when(
-    region == "prop_faces_with_hands" ~ "Proportion hands (given face detection)",
-    region == "prop_hands_with_faces" ~ "Proportion faces (given hand detection)"))
-```
-
-```{r faceHandContingency, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=5, fig.height=3, fig.cap = "Face hand contingnecy }
-ggplot(face_hand_contingency, 
-       aes(x=age_day_bin, y=prop, 
-           col=child_id)) +
-  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
-  geom_smooth(method='lm', aes(weight = num_frames_total), show.legend = TRUE) + 
-  ylab('Average distance between eyes') + 
-  xlab('Age (Months)') +
-  theme_few(base_size=12) +
-  facet_grid(~region) +
-  scale_color_brewer(palette="Dark2") +
-  guides(size = FALSE) +
-  theme(legend.text=element_text(size=12)) +
-  theme(legend.position="none", aspect.ratio=.75) 
-```
-
-In addition, we found faces tended to be farther away from children across age (restricting our analysis to faces where both eyes were detected).
-Figure X shows the average interpupillary distance on faces as a function of each child’s age at the time of recording, showing a trend from larger, closer faces (with a larger interpupillary distance) to smaller faces that were farther away (with a smaller interpupillary distance).
-We saw relatively similar trends across all three children in the dataset, and a linear mixed-effect model confirmed a main effect of age (STATS; see repository for full model specification).
-However, when we examined the size of all faces and hands in the infant view, we found consistency across development (see Appendix, Figure X): while faces (and full body poses) were of course bigger than hands on average, these properties were relatively stable across development and children (see Appendix, Figure X).
-
-Next, we explored where in the visual field children tended to see faces and hands, suspecting, perhaps, that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank, 2012.
-As expected, faces tended to appear in the upper visual field vs.
-hands, which tended to be more centrally located.
-Figure XX shows the average position of faces and hands in the visual field; each dot represents the average position from one video within a given age range.
-However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ -- and likely adults’ -- visual environment from 6 months of age.
+Finally, we analyzed how these two sources of social information co-occurred, finding  that faces/hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}).
+To do so, we  calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range.
+We found that all three infants than were more likely see hands independently -- without the presence of a face -- that they were likely to see faces independently.
+That is, generally speaking when a face was present, a hand also tended to be present.
 
@@
   \hline
-(Intercept)  9.845e-02  1.049e-02  1.956e+00   9.386  0.01198 * 
-Age   -1.418e-03  4.503e-04  4.310e+02  -3.150  0.00175 **
+(Intercept) & 0.098 & 0.010 & 1.956 & 9.386 & 0.012 \\ 
+  age\_scale & -0.001 & 0.000 & 430.976 & -3.150 & 0.002 \\ 
    \hline
@@
   \hline
-(Intercept)  1.612e-01  8.930e-03  1.881e+00   18.05   0.0040 **
-Age   -9.987e-04  5.945e-04  4.287e+02   -1.68   0.0937 
+(Intercept) & 0.161 & 0.009 & 1.881 & 18.046 & 0.004 \\ 
+  age\_scale & -0.001 & 0.001 & 428.651 & -1.680 & 0.094 \\ 
    \hline
 \end{tabular}
-\caption{Model coefficients from a linear mixed model predicting the proportion of hands seen by infants in the center FOV.} 
+\caption{Model coefficients from a linear mixed model predicting the proportion of hands seen by infants n the center FOV.} 
 \end{table}
 
-## Access to social information in different locations
+```{r}
+face_hand_detailed_plot <- face_hand_by_age %>%
+  gather(region, prop, prop_full_faces, prop_faces, prop_hands, prop_faces_and_hands) %>%
+  mutate(approach = "uncropped",
+         region = case_when(region == "prop_faces" ~"All faces",
+                            region == "prop_full_faces" ~ "Full faces (eyes, nose, mouth visible)",
+                            region == "prop_hands" ~ "All hands",
+                            region == "prop_faces_and_hands" ~ "Both hands and faces visible"),
+         child_name = case_when(child_id =='A' ~ "Child A",
+                      child_id == "S" ~ "Child S",
+                      child_id == "Y" ~ "Child Y")) %>%
+  filter(num_frames_total > 5000) # skews scaling of detections to have this 1 sparse age bin
+
+```
+
+```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of face, hand, 'full' face (i.e.
+nose, mouth, and nose visilbe), and joint face/hand detections as a function of age for each child in the dataset.
+Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range." }
+ggplot(face_hand_detailed_plot, 
+       aes(x=age_day_bin, y=prop, 
+           col=region)) +
+  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
+  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
+  ylab('Proportion Detections') + 
+  xlab('Age (Months)') +
+  ylim(0,.5) +
+  facet_grid(.~child_name) + 
+  theme_few(base_size=12) +
+  scale_color_manual(values = c( "#2048d6","#d62020","#751098","#142c83"), name = "") +
+  scale_size_continuous(name = "") +
+  guides(size = FALSE) +
+  theme(legend.text=element_text(size=8)) +
+  theme(legend.position="bottom") 
+```
+
+```{r}
+face_hand_contingency <- face_hand_by_age %>%
+  pivot_longer(c(prop_joint_given_hands, prop_joint_given_faces), values_to="prop", names_to = "region") %>%
+  mutate(region = case_when(
+    region == "prop_joint_given_faces" ~ "Prop. hands (given face det)",
+    region == "prop_joint_given_hands" ~ "Prop. faces (given hand det)"))
+
+    # region == "prop_joint_given_faces_center" ~ "Prop. center hands (given center face det)",
+    # region == "prop_joint_given_hands_center" ~ "Prop. center faces (given center hand det)"))
+```
+
+```{r faceHandContingency, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of joint face/hands detection within frames where frames/ were detected." }
+face_hand_contingency_plot <- ggplot(face_hand_contingency, 
+       aes(x=age_day_bin, y=prop, 
+           col=child_id)) +
+  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
+  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
+  ylab('Proportion joint hand/face detection') + 
+  xlab('Age (Months)') +
+  theme_few(base_size=12) +
+  facet_grid(~region) +
+  # scale_color_manual(values = c( "#DAA0EE","#710D93"), name="") +
+  scale_color_brewer(palette="Dark2") +
+  guides(size = FALSE) +
+  theme(legend.text=element_text(size=12)) 
+```
+
+## Variability in social information across learning contexts 
 ```{r}
@@
 
-```{r DetByLocation, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands by location in which egocentric videos were filmed; each panel represents data from an individual child (location annotations were not yet available for Y).
+```{r DetByLocation, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=5, fig.cap = "Proportion of faces and hands by location in which egocentric videos were filmed; each panel represents data from an individual child (location annotations were not yet available for Y).
 Each dot represents data from a week in which videos were filmed and are scaled by the number of frames."}
@@
 
-How does variability across different contexts influence the social information in the infant view?
+How does variability across different learning contexts influence the social information in the infant view?
 Intuitively, some activities in different contexts may be characterized by a much higher proportion of faces (e.g., diaper changes in bedrooms) than others (e.g., playtime in the living room).
@@
 
+## Fine-grained changes in the social information in view
+```{r}
+## construct age bins for plotting
+bin_size=7
+min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
+max_age = max(all_vid_bbs$age_days, na.rm=TRUE)
+bin_starts = seq(min_age-1, max_age+1,bin_size)
+bins = c(bin_starts, max_age)
+
+all_vid_bbs <- all_vid_bbs %>%
+  mutate(age_months = age_days/30.4) %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))  %>%
+ mutate(avg_center_y = avg_top + avg_height/2, avg_center_x = avg_left + avg_width/2) %>%
+  filter(!avg_area==0) # a very few bounding boxes with zero areas (all keypoints on one plane as faces
+```
+
+```{r}
+# Changes in full vs. all faces? --- not significant, inconsistent results across kids
+# diff_full_vs_all <- face_hand_by_age %>%
+#   mutate(diff = prop_faces - prop_full_faces)
+#
+# ggplot(diff_full_vs_all, aes(x=age_day_bin, y=diff, color=child_id, size=num_frames_total)) +
+#   geom_point(alpha=.2) +
+#   geom_smooth(method='lm')
+#
+# summary(lmer(data=diff_full_vs_all, diff ~ scale(age_day_bin) + scale(num_frames_total) + (1|child_id)))
+```
+
+```{r}
+# for plotting average area / age for each type 
+avg_area_by_age <- all_vid_bbs %>%
+  group_by(age_day_bin, child_id, label) %>%
+  summarize(avg_area = mean(avg_area), num_detect = sum(num_detect)) %>%
+  mutate(label = factor(label, levels = c('pose','face','hand'), labels = c('Full body pose','Faces','Hands'))) %>%
+  mutate(child_id = as.factor(child_id))
+```
+
+```{r avgSizes, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Average size of poses, faces, and hands detected in the dataset  between eyes in faces detected as a function of age for each child in the dataset (each color = different child).
+Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range."}
+
+ggplot(avg_area_by_age, aes(x=age_day_bin, y=log(avg_area), col=child_id, size=num_detect)) +
+  geom_point(alpha=.1) +
+  facet_grid(~label) +
+  geom_smooth(method='lm') + 
+  ylab('Log (average area)') +
+  xlab('Age in days') +
+  scale_color_brewer(palette="Dark2", name = "Child") +
+  guides(size = FALSE)
+```
+
+```{r}
+# eye distance dataframe
+eye_dist <- all_vid_data %>%
+  group_by(child_id, age_day_bin) %>%
+  summarize(eye_distance = mean(avg_eye_distance, na.rm=TRUE), num_faces = sum(num_faces)) %>%
+  filter(num_faces>2000) %>%
+  mutate(variable = 'Eye distance')
+```
+
+```{r}
+eye_dist_plot <- ggplot(eye_dist, 
+       aes(x=age_day_bin, y=eye_distance, 
+           col=child_id)) +
+  geom_point(alpha=.15, aes(size=num_faces), show.legend= FALSE) +
+  geom_smooth(method='lm', aes(weight = num_faces), show.legend = TRUE) + 
+  ylab('Avg. distance between eyes') + 
+  xlab('Age (in months)') +
+  theme_few(base_size=12) +
+  facet_grid(~variable) +
+  scale_color_brewer(palette="Dark2", name='Child') +
+  guides(size = FALSE) +
+  ggtitle('A.') +
+  theme(legend.text=element_text(size=12))  +
+  theme(legend.position="none")
+```
+
+```{r} 
+CV_faces <- all_vid_bbs %>%
+  filter(label=='face') %>%
+  group_by(age_day_bin,child_id) %>%
+  summarize(cv_x_pos = sd(avg_center_x)/mean(avg_center_x)*100, cv_y_pos = sd(avg_center_y)/mean(avg_center_y)*100, num_detect = sum(num_detect), avg_size = mean(avg_area), num_vids = n(), avg_x_pos = mean(avg_center_x), avg_y_pos = mean(avg_center_y)) %>%
+  pivot_longer(cols = c(cv_y_pos, cv_x_pos), values_to = "CV", names_to = "position") %>%
+  mutate(position = factor(position, levels = c("cv_x_pos","cv_y_pos"), labels = c("Face X Position", "Face Y Position")))
+
+```
+
+```{r}
+CV_faces_plot <- ggplot(CV_faces, aes(x=age_day_bin, y = CV, size=num_detect, color=child_id)) +
+  geom_point(alpha=.15) + 
+  facet_wrap(~position)  +
+  geom_smooth(method='lm') +
+  ggtitle('B.') +
+  scale_color_brewer(palette='Dark2', name='Child') + 
+  ylab('Coefficient of variation') +
+  xlab('Age (in months)') +
+  guides(size = FALSE) 
+```
+
+```{r}
+# ggplot(CV_faces, aes(x=avg_size, y = CV, size=num_detect, color=child_id)) +
+#   geom_point(alpha=.15) + 
+#   facet_wrap(~position)  +
+#   geom_smooth(method='lm') +
+#   ggtitle('B.') +
+#   scale_color_brewer(palette='Dark2', name='Child') + 
+#   ylab('Coefficient of variation') +
+#   xlab('Size of face') +
+#   guides(size = FALSE) 
+```
+
+```{r}
+# perip_faces <- all_vid_bbs %>%
+#   filter(label=='face') %>%
+#   group_by(age_day_bin,child_id) %>%
+#   dplyr::summarize(deviation_from_center_x = abs(mean(avg_center_x) - .5), deviation_from_center_y = abs(mean(avg_center_y) - .5), num_detect = sum(num_detect)) %>%
+#   pivot_longer(cols = c(deviation_from_center_x, deviation_from_center_y), values_to = "Deviation", names_to = "position") %>%
+#   mutate(position = factor(position, levels = c("deviation_from_center_x","deviation_from_center_y"), labels = c("Face X Deviation", "Face Y Deviation")))
+# 
+# 
+# ggplot(perip_faces, aes(x=age_day_bin, y = Deviation, size=num_detect, color=child_id)) +
+#   geom_point(alpha=.15) + 
+#   facet_wrap(~position)  +
+#   geom_smooth(method='lm', aes(weight = num_detect)) +
+#   scale_color_brewer(palette='Dark2', name='Child') + 
+#   ylab('Variation from center position') +
+#   xlab('Age (in months)') +
+#   guides(size = FALSE) 
+```
+
+```{r}
+x_pos_summary = summary(lmer(data=CV_faces %>% filter(position == 'Face X Position'), CV ~ scale(age_day_bin) + scale(num_detect) + (1|child_id)))
+
+y_pos_summary = summary(lmer(data=CV_faces %>% filter(position == 'Face Y Position'), CV ~ scale(age_day_bin) + scale(num_detect) +  (1|child_id)))
+```
+
+```{r faceDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "(A).Average distance between eyes and (B) average coefficient of variation for the x and y position of faces detected by OpenPose as a function of each child's age at the time of filming.
+Data in (A) are restricted to faces where both eyes were detected.
+Data are binned by each week that the videos were filmed and scaled by the number of face detections in that age range."}
+
+cowplot::plot_grid(eye_dist_plot, CV_faces_plot, rel_widths=c(1,2))
+```
+In a second set of analysis, we explored fine-grained changes in how these infants  experienced social information across development, capitalizing on the fact that OpenPose provides not only face and hand detections but also positional keypoints.
+In particular, we explored this dataset with the idea that younger, less mobile children may tend to see larger faces towards the center of their visual field while older, more mobile children may experience more smaller, more variable views of faces.
+
+<!-- Next, we examined detailed changes in how infants viewed faces across development. -->
+Supporting this idea, we found that the averages sizes of the people, faces, and hands in the infant view became smaller over development (Figure \ref{fig:avgSizes}).
+This effect was relatively consistent across the three children in the dataset, despite the fact that the three children showed sometimes disparate overall proportions of faces/hands in view.
+Thus, children may see closer, larger views of people, hands, and faces earlier in development.
+In keeping with this hypothesis, we also found evidence that faces tended to be become farther away from children across development (restricting our analysis to faces where both eyes were detected): Figure \ref{fig:faceDetailed}A shows the average interpupillary distance on faces as a function of each child’s age at the time of recording, showing a trend from larger, closer faces (with a larger interpupillary distance) to smaller faces that were farther away (with a smaller interpupillary distance).
+However, we found relatively equal proportions of complete, full-view faces across development (see Figure \ref{fig:faceHandDetailed}: in other words, these very close views of eyes experienced by younger infants were sometimes partial views.
+
+Finally, we also examined whether there were changes in where faces tended to appear in the infant view.
+As expected, faces tended to be located towards the upper field of view, while views of hands were more centrally distributed (see Appendix, Figure XX for average density distributions).
+However, we also found evidence that older children tended to see more faces in more variable positions than younger children.
+Specifically, we examined how variable the horizontal and vertical coordinates were of the faces in the infant view.
+To do so, we calculated the coefficient of variation of the x and vertical y positions of centers of the faces detected by OpenPose (see Figure \ref{fig:faceDetailed}B), and examined changes across age.
+First, we found that faces tended to be more variable in the vertical than their horizontal position (see Figure \ref{fig:faceDetailed}B); evidenced by a much higher coefficeints of variation in the y-direction.
+We also found that as children got older, they tended to see faces that varied more in their horizontal -- but not their vertical position -- suggesting that older children might be more likely to see more smaller faces in their periphery (see Figure \ref{fig:faceDetailed}B).
+
 # General Discussion
-Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the proportion of hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.
-This analysis has yielded a better understanding of infants' evolving access to social information.
-We found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016].
+Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.
+First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016].
 This finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018].
+We also found this to be true when restricting our analyses to full-field faces, suggesting this effect is not driven by a concurrent shift from more full-view to partial-views of faces.
 
@@
 
-Overall, these analyses underscore the importance of how, when, from whom, and what data we sample; these choices become central when we attempt to draw conclusions about the regularities of experience.
+We also found changes in how children experienced faces and hands over development: we found that the faces, hands, and people in the infant view tended to become smaller and that faces tended to be farther away and in more variable horizontal positions.
+Overall, these data support the idea that the social information in view changes across development as infants become increasingly mobile an independent.
+As children can navigate the world on their own, they may experience fewer close-up interactions with the caregivers and more bouts of play where they are exploring the objects and things in the environment around them.
+
+More broadly, however, these analyses underscore the importance of how, when, from whom, and what data we sample; these choices become central when we attempt to draw conclusions about the regularities of experience.
 Indeed, while unprecedented in size, this dataset still has many limitations.
-These videos only represent a small portion of the everyday experience of these three children, all of whom come from relatively privileged households in western societies and thus are not representative of the global population.
+These videos only represent a small portion of the everyday experience of these three children, all of whom come from relatively privileged households in western societies and thus are not representative in many ways of the global population.
 Any idiosyncrasies in how and when these particular families chose to film these videos also undoubtedly influences the variability seen here.
@@
 Thanks to the creators of the SAYCam dataset who made this work possible and to Alessandro Sanchez for his contributions to the codebase.
-This work was funded by a Jacobs Foundation Fellowship to MCF, a John Merck Scholars award to MCF, and NSF #1714726 to BLL.
+This work was funded by a Jacobs Foundation Fellowship to MCF, a John Mereck Scholars award to MCF, and NSF #1714726 to BLL.
 

### 2021-05-11 paper/preprint/preprint_version/paper_revised_submission_june2020_apa.Rmd
move june 2020 preprint files

--- 2020-06-30 paper/preprint/paper_revised_submission_june2020_apa.Rmd
@@
 ## Read in data 
+# load(here::here('data/preprocessed_data/all_vid_data_from_bbs_july192020_merged.RData')) # all detections
+# load(here::here('data/preprocessed_data/all_centered_vid_data_from_bbs_july2020.RData')) # centered cropped
+
 load(here::here('data/data_preprint/all_vid_data_from_bbs_june2020.RData')) # all detections
 load(here::here('data/data_preprint/all_centered_vid_data_from_bbs_june2020.RData')) # centered cropped
+
 ```
@@
 ```{r}
-load(here::here('data/data_preprint/gold_sample_from_bbs_june2020.RData')) # gold sample detections
+load(here::here('data/preprocessed_data/gold_sample_from_bbs_july192020.RData')) # gold sample detections
 load(here::here('data/data_preprint/gold_sample_annotations2020-01-31.RData')) # human annotations
@@
 
-```{r examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=3.5, set.cap.width=T, num.cols.cap=2, fig.align = "center", fig.cap = "Example frames taken from the dataset, illustrating variability in the infant perspective across different locations.
+```{r examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=3.5, set.cap.width=T, num.cols.cap=2,  fig.fullwidth = TRUE, fig.align = "center", fig.cap = "Example frames taken from the dataset, illustrating variability in the infant perspective across different locations.
 OpenPose detections are shown overlaid on these images (green dots = face, red dots = hands, orange dots = pose)."}
@@
 summary_by_age <- all_vid_data %>%
+  ungroup() %>%
   filter(!is.na(age_days)) %>%
@@
 ## summary for centered detections
-summary_by_age_center <- all_vid_data_center %>%
-  filter(!is.na(age_days)) %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+# summary_by_age_center <- all_vid_data_center %>%
+#   ungroup() %>%
+#   filter(!is.na(age_days)) %>%
+#   mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+#   mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+#   group_by(age_day_bin, child_id) %>%
+#   summarize(num_frames_total = sum(num_frames), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
+```
+
+```{r}
+## get out summary by age for goldset hand-labelled frames
+vid_info <- all_vid_data  %>%
+  select(child_id, vid_name, age_days, age_day_bin)
+
+summary_by_age_gold <- gold_sample %>%
+  left_join(vid_info) %>%
   group_by(age_day_bin, child_id) %>%
-  summarize(num_frames_total = sum(num_frames), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
+  summarize(num_frames_total = n(), num_faces = sum(face_present_ketan), num_hands = sum(hand_present_ketan), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
+
+summary_by_age_adult_hands_gold <- gold_sample_no_child_hands %>%
+  left_join(vid_info) %>%
+  group_by(age_day_bin, child_id) %>%
+  summarize(num_frames_total = n(), num_faces = sum(face_present_ketan), num_hands = sum(hand_present_ketan), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
+
+```
+
+```{r}
+# ## summary for centered detections
+# summary_by_age_center <- all_vid_data_center %>%
+#   filter(!is.na(age_days)) %>%
+#   mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+#   mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+#   group_by(age_day_bin, child_id) %>%
+#   summarize(num_frames_total = sum(num_frames), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
 ```
@@
   mutate(approach = "uncropped",
-         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
-  filter(num_frames_total > 5000) # eliminate small data point that skews scaling
+         region = ifelse(region == "prop_faces_summary","Face","Hands"))  
+  # filter(num_frames_total > 5000) # eliminate small data point that skews scaling
 
-wide_center <- summary_by_age_center %>%
+wide_gold <- summary_by_age_adult_hands_gold %>%
   gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
-  mutate(approach = "centered",
-         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
-  filter(num_frames_total > 5000) # eliminate small data point that skews scaling 
+  mutate(approach = "goldset",
+         region = ifelse(region == "prop_faces_summary","Face","Hands"))
+
+# wide_center <- summary_by_age_center %>%
+#   gather(region, prop, prop_faces_center_summary, prop_hands_center_summary) %>%
+#   mutate(approach = "centered",
+#          region = ifelse(region == "prop_faces_center_summary","Face","Hands")) 
+#   # filter(num_frames_total > 5000) # eliminate small data point that skews scaling 
 ```
@@
   geom_point(alpha=.2) +
-  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + # geom_smooth(show.legend = FALSE) or move these below legend?
-  geom_smooth(data = wide_center, span=10, aes(weight = num_frames_total), show.legend = FALSE, 
+  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
+  geom_smooth(data = wide_gold, span=10, aes(weight = num_frames_total), show.legend = FALSE,
               lty = 2, span=10, se = FALSE) +
@@
   theme(legend.position="bottom")
+
+```
+
+```{r}
+## Appendix figure --- same trends in gold set
+# ggplot(wide_gold, 
+#        aes(x=age_day_bin, y=prop, 
+#            size=log10(num_frames_total),
+#            col=region)) +
+#   geom_point(alpha=.2) +
+#   geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
+#   # geom_smooth(data = wide_gold, span=10, aes(weight = num_frames_total), show.legend = FALSE,
+#               # lty = 2, span=10, se = FALSE) +
+#   ylab('Proportion Detections') + 
+#   xlab('Age (Months)') +
+#   ylim(0,.5) +
+#   facet_grid(.~child_id) +
+#   theme_few(base_size=18) +
+#   ggthemes::scale_color_solarized(name = "") + 
+#   scale_size_continuous(name = "Detections (Log 10)") +
+#   theme(legend.text=element_text(size=8)) +
+#   theme(legend.position="bottom")
 
@@
 vid_data_by_location <- all_vid_data %>%
-  mutate(num_frames = num_detect) %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
-  left_join(meta) %>%
-  filter(!is.na(Location)) %>%
-  filter(count_locations==1)
-
-vid_data_centered_by_location <- all_vid_data_center %>%
   mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
@@
 vid_data_by_location$Location = droplevels(vid_data_by_location$Location)
-vid_data_centered_by_location$Location = droplevels(vid_data_centered_by_location$Location) # get rid of unused levels (more than 1 location)
 
@@
 # reset levels for both cropped/uncropped
-levels(vid_data_centered_by_location$Location) <- levels_to_modify
 levels(vid_data_by_location$Location) <- levels_to_modify
@@
 ```{r}
-face_hand_by_location_centered<- vid_data_centered_by_location %>%
-  group_by(Location,child_id,age_day_bin) %>%
-  summarize(prop_faces = sum(num_faces)/sum(num_frames), prop_hands = sum(num_hands)/sum(num_frames), num_detect = sum(num_frames))  %>%
-  group_by(Location) %>%
-  filter(num_detect >12000)
 
@@
   group_by(Location,child_id,age_day_bin) %>%
-  summarize(prop_faces = sum(num_faces)/sum(num_frames), prop_hands = sum(num_hands)/sum(num_frames), num_detect = sum(num_frames))  %>%
+  summarize(num_detect = sum(num_frames),prop_faces = sum(num_faces)/num_detect, prop_hands = sum(num_hands)/num_detect,  prop_hands_center =  sum(num_hands_center)/num_detect, prop_faces_center = sum(num_faces_center)/num_detect)  %>%
+  mutate(prop_faces_center = replace_na(prop_faces_center,0), prop_hands_center = replace_na(prop_hands_center,0)) %>%
   group_by(Location) %>%
-  filter(num_detect >12000)
+  filter(num_detect >3000)
 

### 2021-05-11 paper/preprint/paper_revised_submission_april2021_apa.Rmd
fix file paths to metadata, change plot base size, make contingnecy plot appear

@@
 We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the head cameras as well as a diversity of locations in which videos were recorded.
+Finally, making use of automated annotation of pose bounding boxes, we analyze the size, location, and variability of detected faces and poses across development.
 
@@
 ## Access to social information across age
-
 ```{r}
@@
 ```{r faceHandContingency, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of joint face/hands detection within frames where frames/ were detected." }
-face_hand_contingency_plot <- ggplot(face_hand_contingency, 
+ggplot(face_hand_contingency, 
        aes(x=age_day_bin, y=prop, 
@@
   geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
-  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
+  geom_smooth(method='lm', aes(weight = num_frames_total), show.legend = TRUE) + 
   ylab('Proportion joint hand/face detection') + 
@@
 ```{r}
-load(here::here('data/data_preprint/saycam_metadata.RData')) # meta
+load(here::here('data/preprocessed_data_2021/saycam_metadata.RData')) # meta
 
@@
   xlab('')+
-  theme_few(base_size=18) +
+  theme_few(base_size=12) +
   theme(legend.position = "bottom") +

### 2021-05-11 paper/preprint/paper_revised_submission_april2021_apa.Rmd
added more in variability section

--- 2021-05-04 paper/preprint/paper_revised_submission_april2021_apa.Rmd
@@
 
-# Results
+# Results and Discussion
+
 ## Access to social information across age
@@
 
+<!-- FIXME - references not rendering for -->
 As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%.
@@
 
-How does variability across different learning contexts influence the social information in the infant view?
-Intuitively, some activities in different contexts may be characterized by a much higher proportion of faces (e.g., diaper changes in bedrooms) than others (e.g., playtime in the living room).
-We thus next examined variation in presence of hands and faces across different locations.
-Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location they were filmed in.
-Of these, `r videos_included` videos were filmed in single location, representing 17 percent of the dataset and over 5 million frames.
-Activities varied somewhat predictably by these contexts: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.
-Overall, we found that the proportion of faces vs.
-hands varied across filming locations, and, to some extent, across children; separate chi-squared tests for each child and detection type revealed significant variability in detections by location in each case ^[all *p*<.001, see accompanying codebase].
-For example, while both A and S saw a relatively similar proportion of faces vs.
-hands in the bedroom, they saw quite different amounts of faces vs.
-hands in kitchens (see Figure \ref{fig:DetByLocation}).
+How does the child's context influence the social information in view? 
+@bruner1985role discussed the role of children's activities in shaping the information present for learning.
+Following this idea, we investigated whether there were differences in access to faces by the activity that the child was engaged in.
+This hypothesis seems intuitively appealing.  
+Some activities seem likely to be characterized by a much higher proportion of faces (e.g., diaper changes) than others (e.g., a car trip). 
+Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime).
+
+We did not have access to annotations of activity. 
+Thus, following @roy2015predicting, we used spatial location as a proxy for activity context, taking advantage of the presence of these annotations for a subset of the SAYCam videos. 
+Of the `r num_videos` videos in the dataset, `r num_videos_annotated` were annotated for the location or locations they were filmed in. 
+These location annotations were only available for two children, S and A.
+Annotated locations mostly consisted of rooms of the house (e.g., "living room") but also included some other locations (e.g., "car," "outside").
+Of this set, `r videos_included` videos were filmed in only a single location (e.g., the location label did not change within the video), representing 17 percent of the dataset and over 5 million frames.
+In our viewing of the SAYCam videos and in other annotations available with the dataset, activities varied somewhat predictably by location: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.
+
+Figure \ref{fig:DetByLocation} shows the proportion of faces vs. hands across locations. 
+We found substantial variation across locations and, to some extent, across children. 
+Separate chi-squared tests for each child and detection type revealed significant variability in detections by location in each case, with all $p$s $<.001$. 
+For example, while both A and S saw a relatively similar proportion of faces and hands in the bedroom, the two children saw quite different amounts of faces and hands from one another in the kitchen. 
+This difference is likely explained by differences in arrangement of the kitchen in the two children's households (Sullivan, personal communication), such that mealtimes in one kitchen resulted in a face-to-face orientation while it did not in the other).
+This example illustrates how specifics of the geometry of a particular context can play an outsize role in the child's access to social information during that context.
 
@@
 # General Discussion
+
 Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.

### 2021-05-11 paper/preprint/paper_revised_submission_april2021_apa.Rmd

@@
 ## Fine-grained changes in the social information in view
+
 ```{r}

### 2021-05-11 paper/preprint/paper_revised_submission_april2021_apa.Rmd
(render appendix)
tweaks to results 3

@@
 ```{r}
-# Changes in full vs. all faces? --- not significant, inconsistent results across kids
-# diff_full_vs_all <- face_hand_by_age %>%
-#   mutate(diff = prop_faces - prop_full_faces)
-#
-# ggplot(diff_full_vs_all, aes(x=age_day_bin, y=diff, color=child_id, size=num_frames_total)) +
-#   geom_point(alpha=.2) +
-#   geom_smooth(method='lm')
-#
-# summary(lmer(data=diff_full_vs_all, diff ~ scale(age_day_bin) + scale(num_frames_total) + (1|child_id)))
-```
-
-```{r}
 # for plotting average area / age for each type 
@@
 
-```{r faceDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "(A).Average distance between eyes and (B) average coefficient of variation for the x and y position of faces detected by OpenPose as a function of each child's age at the time of filming.
+```{r faceDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "(A) Average distance between eyes and (B) average coefficient of variation for the x and y position of faces detected by OpenPose as a function of each child's age at the time of filming.
 Data in (A) are restricted to faces where both eyes were detected.
@@
 ```
-In a second set of analysis, we explored fine-grained changes in how these infants  experienced social information across development, capitalizing on the fact that OpenPose provides not only face and hand detections but also positional keypoints.
-In particular, we explored this dataset with the idea that younger, less mobile children may tend to see larger faces towards the center of their visual field while older, more mobile children may experience more smaller, more variable views of faces.
+In a third set of analyses, we explored fine-grained changes in the SAYCam infants' access to social information across development.
+In these analyses, we capitalize on the fact that OpenPose provides not only face and hand detections but also positional keypoints. 
+In particular, we explored this keypoint dataset with the idea that greater mobility allows older children to be further from their caregivers on average. 
+Thus, younger, less mobile children may tend to see larger faces towards the center of their visual field while older, more mobile children may experience more smaller, more variable views of faces.
+The same dynamic would be predicted hold for hands as well, as it would be driven by overall differences in distance.
 
@@
 Thus, children may see closer, larger views of people, hands, and faces earlier in development.
-In keeping with this hypothesis, we also found evidence that faces tended to be become farther away from children across development (restricting our analysis to faces where both eyes were detected): Figure \ref{fig:faceDetailed}A shows the average interpupillary distance on faces as a function of each child’s age at the time of recording, showing a trend from larger, closer faces (with a larger interpupillary distance) to smaller faces that were farther away (with a smaller interpupillary distance).
-However, we found relatively equal proportions of complete, full-view faces across development (see Figure \ref{fig:faceHandDetailed}: in other words, these very close views of eyes experienced by younger infants were sometimes partial views.
 
-Finally, we also examined whether there were changes in where faces tended to appear in the infant view.
+In keeping with this hypothesis, we also found evidence that faces tended to be farther away from older children. 
+We restricted our analysis here to faces where both eyes were detected and computed interpupillary distance as a rough metric of distance, since eyes should be closer together on average when a face is further from the camera.
+Figure \ref{fig:faceDetailed}A shows the average interpupillary distance on faces as a function of each child’s age at the time of recording. 
+There is a trend from larger, closer faces (with a larger interpupillary distance) to smaller faces that were farther away (with a smaller interpupillary distance). 
+<!-- However, in our previous analysis we found relatively equal proportions of complete, full-view faces across development (see e.g., Figure \ref{fig:faceHandDetailed}, where full view faces stayed relatively constant as a proportion of all detected faces).
+-->
+
+```{r}
+# Changes in full vs. all faces? --- not significant, inconsistent results across kids
+# diff_full_vs_all <- face_hand_by_age %>%
+#   mutate(diff = prop_faces - prop_full_faces)
+#
+# ggplot(diff_full_vs_all, aes(x=age_day_bin, y=diff, color=child_id, size=num_frames_total)) +
+#   geom_point(alpha=.2) +
+#   geom_smooth(method='lm')
+#
+# summary(lmer(data=diff_full_vs_all, diff ~ scale(age_day_bin) + scale(num_frames_total) + (1|child_id)))
+```
+
+<!-- NEED TO LOOK AT PROPORTION OF FULL FACES IN ALL FACES -->
+<!-- : in other words, these very close views of eyes experienced by younger infants were sometimes partial views. -->
+
+Finally, we also examined whether there were changes in where faces tended to appear in the camera's (and hence, by proxy, the child's) field of view. 
 As expected, faces tended to be located towards the upper field of view, while views of hands were more centrally distributed (see Appendix, Figure XX for average density distributions). 
@@
 Specifically, we examined how variable the horizontal and vertical coordinates were of the faces in the infant view. 
-To do so, we calculated the coefficient of variation of the x and vertical y positions of centers of the faces detected by OpenPose (see Figure \ref{fig:faceDetailed}B), and examined changes across age.
-First, we found that faces tended to be more variable in the vertical than their horizontal position (see Figure \ref{fig:faceDetailed}B); evidenced by a much higher coefficeints of variation in the y-direction.
+To do so, we calculated the coefficient of variation of the horizontal (x) and vertical (y) positions of centers of the faces detected by OpenPose (see Figure \ref{fig:faceDetailed}B), and examined changes across age.
+Faces tended to be more variable in the vertical than their horizontal position (see Figure \ref{fig:faceDetailed}B). 
 We also found that as children got older, they tended to see faces that varied more in their horizontal -- but not their vertical position -- suggesting that older children might be more likely to see more smaller faces in their periphery (see Figure \ref{fig:faceDetailed}B).

### 2021-05-11 paper/preprint/paper_revised_submission_april2021_apa.Rmd
caption fix

@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : 
+  papaja::apa6_pdf:
+    includes:
+      after_body: "appendix.tex"
 ---
@@
 
-```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of face, hand, 'full' face (i.e.
-nose, mouth, and nose visilbe), and joint face/hand detections as a function of age for each child in the dataset.
+```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of face, hand, full face (i.e., nose, mouth, and nose visible), and joint face/hand detections as a function of age for each child in the dataset.
 Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range." }
@@
 
+```{r appendix, include = FALSE}
+render_appendix("appendix.Rmd")
+```
+
 # References

### 2021-05-11 paper/preprint/paper_revised_submission_april2021_apa.Rmd
discussion minor edits

--- 2021-05-11 paper/preprint/paper_revised_submission_april2021_apa.Rmd
@@
 
-# Results and Discussion
-
+# Results
 ## Access to social information across age
@@
 
-<!-- FIXME - references not rendering for -->
 As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%.
@@
 
-How does the child's context influence the social information in view? 
-@bruner1985role discussed the role of children's activities in shaping the information present for learning.
-Following this idea, we investigated whether there were differences in access to faces by the activity that the child was engaged in.
-This hypothesis seems intuitively appealing.  
-Some activities seem likely to be characterized by a much higher proportion of faces (e.g., diaper changes) than others (e.g., a car trip). 
-Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime).
-
-We did not have access to annotations of activity. 
-Thus, following @roy2015predicting, we used spatial location as a proxy for activity context, taking advantage of the presence of these annotations for a subset of the SAYCam videos. 
-Of the `r num_videos` videos in the dataset, `r num_videos_annotated` were annotated for the location or locations they were filmed in. 
-These location annotations were only available for two children, S and A.
-Annotated locations mostly consisted of rooms of the house (e.g., "living room") but also included some other locations (e.g., "car," "outside").
-Of this set, `r videos_included` videos were filmed in only a single location (e.g., the location label did not change within the video), representing 17 percent of the dataset and over 5 million frames.
-In our viewing of the SAYCam videos and in other annotations available with the dataset, activities varied somewhat predictably by location: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.
-
-Figure \ref{fig:DetByLocation} shows the proportion of faces vs. hands across locations. 
-We found substantial variation across locations and, to some extent, across children. 
-Separate chi-squared tests for each child and detection type revealed significant variability in detections by location in each case, with all $p$s $<.001$. 
-For example, while both A and S saw a relatively similar proportion of faces and hands in the bedroom, the two children saw quite different amounts of faces and hands from one another in the kitchen. 
-This difference is likely explained by differences in arrangement of the kitchen in the two children's households (Sullivan, personal communication), such that mealtimes in one kitchen resulted in a face-to-face orientation while it did not in the other).
-This example illustrates how specifics of the geometry of a particular context can play an outsize role in the child's access to social information during that context.
+How does variability across different learning contexts influence the social information in the infant view?
+Intuitively, some activities in different contexts may be characterized by a much higher proportion of faces (e.g., diaper changes in bedrooms) than others (e.g., playtime in the living room).
+We thus next examined variation in presence of hands and faces across different locations.
+Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location they were filmed in.
+Of these, `r videos_included` videos were filmed in single location, representing 17 percent of the dataset and over 5 million frames.
+Activities varied somewhat predictably by these contexts: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.
+Overall, we found that the proportion of faces vs.
+hands varied across filming locations, and, to some extent, across children; separate chi-squared tests for each child and detection type revealed significant variability in detections by location in each case ^[all *p*<.001, see accompanying codebase].
+For example, while both A and S saw a relatively similar proportion of faces vs.
+hands in the bedroom, they saw quite different amounts of faces vs.
+hands in kitchens (see Figure \ref{fig:DetByLocation}).
 
 ## Fine-grained changes in the social information in view
-
 ```{r}
@@
 # General Discussion
-
 Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.
@@
 
-We also found changes in how children experienced faces and hands over development: we found that the faces, hands, and people in the infant view tended to become smaller and that faces tended to be farther away and in more variable horizontal positions.
+We also used these detailed pose annotations to explore finer-grained changes in how children experience the faces and hands of their caregivers over development.
+We found that the faces, hands, and people in the infant view tended to become smaller and that faces tended to be farther away and in more variable horizontal positions.
 Overall, these data support the idea that the social information in view changes across development as infants become increasingly mobile an independent.

### 2021-05-11 paper/preprint/appendix.Rmd

@@
 ---
-title: "Appendix"
-author: "Bria Long"
-date: "5/3/2021"
-output: html_document
+title: Appendix to 'Detecting social information in a dense database of infants’ natural
+  visual experience'
+date: "`r Sys.Date()`"
+output:
+  pdf_document: default
 ---
@@
 # Distribution of faces and hands in the visual field
-We explored where in the visual field children tended to see faces and hands, suspecting, perhaps, that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank, 2012.
-As expected, faces tended to appear in the upper visual field vs.
-hands, which tended to be more centrally located.
-However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ -- and likely adults’ -- visual environment from 6 months of age.
+
+We explored where in the visual field children tended to see faces and hands, suspecting that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank (2012).
+As expected, faces tended to appear in the upper visual field in contrast to hands, which tended to be more centrally located.  
+However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ -- and perhaps adults’ -- visual environment from 6 months of age.
 
@@
 
-<!-- We also evaluated OpenPose's performance while restricting detections to high-confidence detections (>.5 confidence, default threshold for visualization).
-For faces, we found that the F-score was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`.
-For hands, the F-score for high confidence detections `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
-Thus, as in prior work [@long2020automated], while precision was much highe for both faces and hands, the lower recall for high-confidence detection indicates that these lower-confidence detections still index the presence of social information in the infant view.
--->
+```{r, eval=F, include=F}
+# add back to text when high-conf BBs are processed:
+# We also evaluated OpenPose's performance while restricting detections to high-confidence detections (>.5 confidence, default threshold for visualization). 
+#For faces, we found that the F-score was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`. 
+#For hands, the F-score for high-confidence detections was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
+#Thus, as in prior work [@long2020automated], while precision was much higher for both faces and hands, the lower recall for high-confidence detections indicates that these lower-confidence detections still index the presence of social information in the infant view.
+```
 
@@
 
-```{r}
+```{r, fig.width=6.5, fig.height=4, fig.cap="ToDo"}
 ggplot(CV_faces, aes(x=age_day_bin , y = CV, size=num_detect, color=child_id)) +
@@
   facet_wrap(~position) +
+  theme_few(base_size=14) +
   geom_smooth(method='lm') +
@@
 
-```{r}
-
-Caption="Each panel shows the average position of faces and hands in the visual field; each dot represents the average position from one video within a given age range."
+```{r, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field; each dot represents the average position from one video within a given age range."}
 
@@
   theme_few(base_size=14) +
-  theme(legend.position="right", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
+  theme(legend.position="top", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
   scale_y_reverse() +

### 2021-05-25 paper/preprint/paper_revised_submission_april2021_apa.Rmd
editing

@@
 Yet until recently most hypotheses about infants' visual experience have gone untested. 
-Though parents and scientists alike have strong intuitions about what infants see, even the viewpoint of a walking child is not easily predicted by these intuitions [@clerkin2017; @franchak2011].
+Though parents and scientists alike have strong intuitions about what infants see, even the viewpoint of a walking child is hard to intuit [@clerkin2017; @franchak2011]. 
 By equipping infants and toddlers with head-mounted cameras, researchers have begun to document the infant's egocentric perspective on the world. 
@@
 
-Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of nearly 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYCam dataset [@SAYcam].
+Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of more than 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYCam dataset [@SAYcam].
 In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways.
@@
 
-To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A); `r  24000-length(gold_sample$face_openpose)` frames with allocentric videos were excluded, as were these videos from the rest of analyses.
+To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A); `r  24000-length(gold_sample$face_openpose)` frames sampled from allocentric videos were excluded, and these videos were also excluded from the other analyses.
 Frames were jointly annotated for the presence of faces and hands by one author.
@@
 
-To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (the harmonic mean of precision and recall).
+To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / (hits + false alarms)), recall (hits / (hits + misses)), and F-score (the harmonic mean of precision and recall).
 In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`.
@@
 
-```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3.5, fig.height=2, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant.
+```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=5, fig.height=3, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant.
 Brighter values indicate more detections."}
@@
 
-```{R}
+```{r}
 #### Make longer format for plotting
@@
 
-```{r FacesAndHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset.
+```{r FacesAndHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands seen as a function of age for each child (A, S, and Y).
 Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range.
@@
   facet_grid(.~child_id) + 
-  theme_few(base_size=9) +
+  theme_few(base_size=10) +
   ggthemes::scale_color_solarized(name = "") + 
-  theme(legend.text=element_text(size=8)) +
+  theme(legend.text=element_text(size=10)) +
   guides(size = FALSE) +
@@
 To do so, we  calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range. 
-We found that all three infants than were more likely see hands independently -- without the presence of a face -- that they were likely to see faces independently.
+As shown in Figure \ref{fig:faceHandContingency}, we found that all three infants were more likely to see hands independently -- without the presence of a face -- than they were likely to see faces independently.
 That is, generally speaking when a face was present, a hand also tended to be present.
@@
 (Intercept) & 0.098 & 0.010 & 1.956 & 9.386 & 0.012 \\ 
-  age\_scale & -0.001 & 0.000 & 430.976 & -3.150 & 0.002 \\ 
+  Age & -0.001 & 0.000 & 430.976 & -3.150 & 0.002 \\ 
    \hline
@@
 (Intercept) & 0.161 & 0.009 & 1.881 & 18.046 & 0.004 \\ 
-  age\_scale & -0.001 & 0.001 & 428.651 & -1.680 & 0.094 \\ 
+  Age & -0.001 & 0.001 & 428.651 & -1.680 & 0.094 \\ 
    \hline
@@
 
-```{r faceHandContingency, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of joint face/hands detection within frames where frames/ were detected." }
+```{r faceHandContingency, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of joint face and hands detection within frames where hands (left) or faces (right) were detected." }
 ggplot(face_hand_contingency, 
@@
   guides(size = FALSE) +
-  theme(legend.text=element_text(size=12)) 
+  theme(legend.text=element_text(size=10)) 
 ```
@@
   xlab('')+
-  theme_few(base_size=12) +
+  theme_few(base_size=10) +
   theme(legend.position = "bottom") +
   facet_grid(.~child_id)  +
-  scale_size_continuous(name = "Detections (Log 10)") +
+  scale_size_continuous(name = "log(Detections)") +
   scale_linetype_manual(values=c("solid", "dashed","solid","dashed"), name = "") +

### 2021-05-25 paper/preprint/paper_revised_submission_april2021_apa.Rmd
fix minor typos

--- 2021-05-11 paper/preprint/paper_revised_submission_april2021_apa.Rmd
@@
 We found that the faces, hands, and people in the infant view tended to become smaller and that faces tended to be farther away and in more variable horizontal positions.
-Overall, these data support the idea that the social information in view changes across development as infants become increasingly mobile an independent.
+Overall, these data support the idea that the social information in view changes across development as infants become increasingly mobile and independent.
 As children can navigate the world on their own, they may experience fewer close-up interactions with the caregivers and more bouts of play where they are exploring the objects and things in the environment around them.

### 2021-05-25 paper/preprint/appendix.Rmd
get rid of duplicated graph

@@
 
-```{r}
-CV_faces <- all_vid_bbs %>%
-  filter(label=='face') %>%
-  group_by(age_day_bin,child_id) %>%
-  summarize(cv_x_pos = sd(avg_center_x)/mean(avg_center_x)*100, cv_y_pos = sd(avg_center_y)/mean(avg_center_y)*100, num_detect = sum(num_detect), num_vids = n()) %>%
-  pivot_longer(cols = c(cv_y_pos, cv_x_pos), values_to = "CV", names_to = "position") %>%
-  mutate(position = factor(position, levels = c("cv_x_pos","cv_y_pos"), labels = c("X Position", "Y Position")))
-
-```
-
-```{r, fig.width=6.5, fig.height=4, fig.cap="ToDo"}
-ggplot(CV_faces, aes(x=age_day_bin , y = CV, size=num_detect, color=child_id)) +
-  geom_point(alpha=.3) + 
-  facet_wrap(~position) +
-  theme_few(base_size=14) +
-  geom_smooth(method='lm') +
-  scale_color_brewer(palette='Dark2') + 
-  ylab('Coefficient of variation for face position') +
-  xlab('Age (in months)') +
-  guides(size = FALSE)
-```
-
 ```{r, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field; each dot represents the average position from one video within a given age range."}

### 2021-05-25 paper/preprint/paper_revised_submission_april2021_apa.Rmd
replaced linear regression tables with quadratic reg tables

--- 2021-05-25 paper/preprint/paper_revised_submission_april2021_apa.Rmd
@@
 library(here)
+library(papaja)
 theme_set(theme_few())
@@
 To do so, we  calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range. 
-As shown in Figure \ref{fig:faceHandContingency}, we found that all three infants were more likely to see hands independently -- without the presence of a face -- than they were likely to see faces independently.
-That is, generally speaking when a face was present, a hand also tended to be present.
+We found that all three infants were more likely to see hands independently -- without the presence of a face -- than they were likely to see faces independently. 
+That is, generally speaking when a face was present, a hand also tended to be present (see also Figure \ref{fig:faceHandContingency}).
 
-```{r eval=FALSE}
+```{r eval=T}
 summary_by_age_days <- all_vid_data %>%
@@
 
-```{r eval=FALSE}
+```{r eval=T, include=F, echo=F}
 # run lmer models -- faces over age
-faces_model_full_age_out = summary(lmer(prop_faces_center ~ age_scale + (1 | child_id), data = summary_by_age_days))
+faces_model1 <- lmer(prop_faces_center ~ age_scale + (1 | child_id), data = summary_by_age_days)
+faces_model_full_age_out = summary(faces_model1)
+# # singular:
+#faces_model2 = summary(lmer(prop_faces_center ~ poly(age_scale, 2) + (poly(age_scale, 2) | child_id), 
+#                            data = summary_by_age_days))
+faces_model2 <- lmer(prop_faces_center ~ poly(age_scale, 2) + (1 | child_id), 
+                            data = summary_by_age_days)
+faces_comparison <- anova(faces_model1, faces_model2) # chisq 7.17 p = 0.007407 ** - complex model preferred
+faces_out <- summary(faces_model2) # poly(age_scale, 2)1 -.20 **, poly(age_scale, 2)2 -.16**
 
 # hands over age
-hands_model_full_age_out = summary(lmer(prop_hands_center ~ age_scale + (1 | child_id), data = summary_by_age_days))
+hands_model1 <- lmer(prop_hands_center ~ age_scale + (1 | child_id), data = summary_by_age_days)
+hands_model_full_age_out = summary(hands_model1)
+hands_model2 <- lmer(prop_hands_center ~ poly(age_scale, 2) + (1 | child_id), 
+                            data = summary_by_age_days)
+hands_comparison <- anova(hands_model1, hands_model2) # chisq = 17.11, p<.001 - complex model preferred
+
+hands_out <- summary(hands_model2) # poly(age_scale, 2)1  -0.14, p=.06, poly(age_scale, 2)2  -0.32, p<.001
 
@@
 # main effect of ages and regions; no interaction.
-diff_model_full_age_out = summary(lmer(prop ~ region*age_scale + (1 | child_id), data = long_summary_by_age_days))
+diff_model1 <- lmer(prop ~ region*age_scale + (1 | child_id), data = long_summary_by_age_days)
+diff_model_full_age_out = summary(diff_model1)
+diff_model2 <- lmer(prop ~ region*poly(age_scale, 2) + (1 | child_id), data = long_summary_by_age_days)
+diff_comparison <- anova(diff_model1, diff_model2) # chisq = 23.66, p<.001 - complex model preferred
+
+diff_out <- summary(diff_model2) 
+# regionprop_hands .04***, poly(age_scale, 2)1 -.42**, poly(age_scale, 2)2 -.29*, marginal hand*poly(age_scale, 2)2
 ```
 
-```{r eval=FALSE}
+```{r faces-regression-table}
+faces_tab <- faces_out$coefficients
+rownames(faces_tab)[2] = "Age"
+rownames(faces_tab)[3] = "Age**2"
+apa_table(faces_tab, digits=3,
+           caption = "Coefficients from a mixed-effects regression predicting the proportion of faces seen by infants in the center FOV.")
+```
+
+```{r hands-regression-table}
+hands_tab <- round(hands_out$coefficients, 3)
+rownames(hands_tab)[2] = "Age"
+rownames(hands_tab)[3] = "Age**2"
+hands_tab[3,5] = "<.001"
+apa_table(hands_tab, 
+           caption = "Coefficients from a mixed-effects regression predicting the proportion of hands seen by infants in the center FOV.")
+```
+
+```{r linear-regression-tables, eval=FALSE, include=F}
+# old -- now want the above poly models
 xtable(faces_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of faces seen by infants in the center FOV.")
 
-xtable(hands_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of hands seen by infants n the center FOV.")
+xtable(hands_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of hands seen by infants in the center FOV.")
 ```
 
+<!-- old linear regression tables
 \begin{table}[ht]
@@
 \end{table}
+-->
 
@@
 
-```{r}
+```{r, include=F}
 x_pos_summary = summary(lmer(data=CV_faces %>% filter(position == 'Face X Position'), CV ~ scale(age_day_bin) + scale(num_detect) + (1|child_id)))

### 2021-05-25 paper/preprint/paper_revised_submission_april2021_apa.Rmd

--- 2021-05-25 paper/preprint/paper_revised_submission_april2021_apa.Rmd
@@
 ## Face/hand detections by video
-load(here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
+load(file=here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
 ```
@@
 ```{r}
-# gold sample annotatios and detedctinos for these specific frames
+# gold sample annotations for these specific frames
 load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
+```
+
+```{r}
+# load high confidence detections for gold sample frames
+load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_high_conf_detections.RData'))
+all_gold_sample_frames_op_hc = all_gold_sample_frames_op
+```
+
+```{r}
+# load all detections for gold sample frames
 load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_all_detections.RData')) 
-
-# all_gold_sample_frames_op_hc = load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_high_conf_detections.RData')) 
 ```
@@
 ## for high confidence detections
-# gold_sample_hc <- gold_sample %>%
-#   select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
-#   mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
-#   right_join(all_gold_sample_frames_op_hc) %>% # HIGH CONF DF
-#   mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))
-# 
-#  
-# face_performance_hc = return_prf_short(gold_sample_hc$face_eval_ketan)
-# hand_performance_hc = return_prf_short(gold_sample_hc$hand_eval_ketan)
+gold_sample_hc <- gold_sample %>%
+  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
+  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
+  right_join(all_gold_sample_frames_op_hc) %>% # HIGH CONF DF
+  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))
+
+face_performance_hc = return_prf_short(gold_sample_hc$face_eval_ketan)
+hand_performance_hc = return_prf_short(gold_sample_hc$hand_eval_ketan)
 ```
@@
 
-```{r} 
-### Load turk hand annotations with all bounding boxes (multiple dets per frame)
-load(here::here('data/preprocessed_data_2021/hand_annotations_2020-01-29.RData'))
-
-child_hands <- hand_annotations %>%
-  filter(label=="Child hand")
-
-adult_hands <- hand_annotations %>%
-  filter(label=="Adult hand")
-```
-
-```{r}
-### plot centers of the bounding boxes made for child and adult hands
-child_hand_plot <- ggplot(child_hands, aes(x=center_x, y=center_y)) +
-  geom_point(alpha=.1) + 
-  stat_density_2d(aes(fill = ..level..), geom="polygon", alpha=.8) +
-  coord_fixed(ratio=1) +
-  ggtitle('A. Child hand density') +
-  ylim(0,480) +
-  xlim(0,640) +
-  ylab('') +
-  xlab('') +
-  theme_few(base_size=6) +
-  theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
-  scale_y_reverse()
-##
-adult_hand_plot <- ggplot(adult_hands, aes(x=center_x, y=center_y)) +
-  geom_point(alpha=.1) + 
-  stat_density_2d(aes(fill = ..level..), geom="polygon", alpha=.8) +
-  coord_fixed(ratio=1) +
-  ylim(0,480) +
-  xlim(0,640) +
-  scale_y_reverse() +
-  ylab('') +
-  xlab('') +
-  theme_few(base_size=6) +
-    theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
-  ggtitle('B. Adult hand density')
-```
-
 To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A); `r  24000-length(gold_sample$face_openpose)` frames sampled from allocentric videos were excluded, and these videos were also excluded from the other analyses.
@@
 
-```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=5, fig.height=3, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant.
-Brighter values indicate more detections."}
-cowplot::plot_grid(child_hand_plot, adult_hand_plot, nrow=1)
-```
-
 We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose—-a notoriously challenging detection problem [@bambach2015lending].
@@
 When frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`.
-We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Figure \ref{fig:handLocation}.
+We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Appendix Figure \ref{fig:handLocation}.
 
@@
 all_detections <- face_hand_by_age %>%
-  filter(num_frames_total > 2000) %>% # eliminate small data point that skews scaling
+  filter(num_frames_total > 5000) %>% # eliminate small data point that skews scaling
   select(prop_faces, prop_hands, num_frames_total, age_day_bin, child_id) %>%
@@
   mutate(approach = "uncropped",
-         region = ifelse(region == "prop_faces","Faces","Hands"))
+         region = ifelse(region == "prop_faces","All faces","All hands"),
+         child_name = case_when(child_id =='A' ~ "Child A",
+                      child_id == "S" ~ "Child S",
+                      child_id == "Y" ~ "Child Y"))
 
 centered <- face_hand_by_age %>%
-  filter(num_frames_total > 2000) %>% # eliminate small data point that skews scaling
+  filter(num_frames_total > 5000) %>% # eliminate small data point that skews scaling
   select(prop_faces_center, prop_hands_center, num_frames_total, age_day_bin, child_id) %>%
@@
   mutate(approach = "centered",
-         region = ifelse(region == "prop_faces_center","Faces","Hands"))
+         region = ifelse(region == "prop_faces_center","Faces in center FOV","Hands in center FOV"),
+         child_name = case_when(child_id =='A' ~ "Child A",
+                      child_id == "S" ~ "Child S",
+                      child_id == "Y" ~ "Child Y"))
+
+detailed <- face_hand_by_age %>%
+  filter(num_frames_total > 5000) %>%
+  select(prop_full_faces, prop_faces_and_hands, num_frames_total, age_day_bin, child_id) %>%
+  gather(region, prop, prop_full_faces, prop_faces_and_hands) %>%
+  mutate(approach = "detailed",
+         region = case_when(region == "prop_full_faces" ~ "Full faces",
+                            region == "prop_faces_and_hands" ~ "Both hands & faces"),
+         child_name = case_when(child_id =='A' ~ "Child A",
+                      child_id == "S" ~ "Child S",
+                      child_id == "Y" ~ "Child Y")) 
 ```
 
-```{r FacesAndHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands seen as a function of age for each child (A, S, and Y).
-Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range.
-Dashed lines show estimated trend lines from proportion of faces/hands in view when detections are restricted to the center FOV, reducing the contribution of children's own hands."}
-ggplot(all_detections, 
+```{r}
+first_panel <- ggplot(all_detections, 
        aes(x=age_day_bin, y=prop, 
@@
            col=region)) +
-  geom_point(alpha=.2) +
-  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
-  geom_smooth(data = centered, span=10, aes(weight = num_frames_total), show.legend = TRUE,
-              lty = 2, span=10, se = FALSE) +
+  geom_point(alpha=.1) +
+  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
   ylab('Proportion Detections') + 
@@
   ylim(0,.5) +
-  facet_grid(.~child_id) + 
+  facet_grid(cols = vars(child_name)) + 
   theme_few(base_size=10) +
@@
   guides(size = FALSE) +
-  theme(legend.position="bottom") 
+  theme(legend.position="right")
+
+second_panel <- ggplot(centered, 
+       aes(x=age_day_bin, y=prop, 
+           size=log10(num_frames_total),
+           col=region)) +
+  geom_point(alpha=.1) +
+  geom_smooth(span=10, aes(weight = num_frames_total),linetype = 'dashed', show.legend = TRUE) + 
+  ylab('Proportion Detections') + 
+  xlab('Age (Months)') +
+  ylim(0,.5) +
+  facet_grid(cols = vars(child_name)) + 
+  theme_few(base_size=10) +
+  ggthemes::scale_color_solarized(name = "") + 
+  theme(legend.text=element_text(size=10)) +
+  guides(size = FALSE) +
+  theme(legend.position="right")
+
+third_panel <- ggplot(detailed, 
+       aes(x=age_day_bin, y=prop, 
+           size=log10(num_frames_total),
+           col=region)) +
+  geom_point(alpha=.1) +
+  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
+  ylab('Proportion Detections') + 
+  xlab('Age (Months)') +
+  ylim(0,.5) +
+  facet_grid(cols = vars(child_name)) + 
+  theme_few(base_size=10) +
+  scale_color_manual(values = c("#751098","#142c83"), name = "") +
+  theme(legend.text=element_text(size=10)) +
+  guides(size = FALSE) +
+  theme(legend.position="right")
+
+```
+
+```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=7, fig.cap = "Proportion of frames with (A).All face and hand detections,  B.Face/hand detections that fell within the center field-of-view (reducing the contribution of children's own hands) and (C) Face detections that were full faces (e.g., eyes, nose, and mouth all visible) and that co-occurred with hands, plotted as a function of age for each child (A, S, and Y).
+Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range."}
+
+cowplot::plot_grid(first_panel, second_panel, third_panel, labels='AUTO', nrow=3, align = "v", axis = "b")
 ```
@@
 We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands detected for each child.^[All analyses and preprocessed data files for this paper are available at https://tinyurl.com/detecting-social-info] Data from videos were binned according to the age of the child (in weeks).
-First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:FacesAndHands}), in keeping with prior findings [@Fausey2016]; in contrast, we did not observe an increase in the proportion of hands in view.
+First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:faceHandDetailed}), in keeping with prior findings [@Fausey2016]; in contrast, we did not observe an increase in the proportion of hands in view.
 These effects were quantified with two separate linear mixed-models (see Tables 1 & 2).^[Face/hand detections were binned across each week of filming.
@@
 However, the most striking result from these analyses is a much overall greater proportion of hands in view than have previously been reported [@Fausey2016].
-We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Appendix Figure \ref{fig:goldSetSanity}) or OpenPose annotations on the entire dataset (see solid lines in Figure \ref{fig:FacesAndHands}).
+We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Appendix Figure \ref{fig:goldSetSanity}) or OpenPose annotations on the entire dataset (see Figure \ref{fig:faceHandDetailed}A).
 This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may be an underestimate of the proportion of hands in view.
@@
 This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
-Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:FacesAndHands}). 
+Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}).
+We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure\ref{fig:goldSetSanity}).
+
+Finally, we analyzed how these two sources of social information co-occurred, finding that faces/hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}C).
+To do so, we  calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range.
+We found that all three infants than were more likely see hands independently -- without the presence of a face -- that they were likely to see faces independently \ref{fig:faceHandContingnecy}.
+That is, generally speaking when a face was present, a hand also tended to be present.
+
+As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%.
+This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
+Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}B). 
 We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure\ref{fig:goldSetSanity}).
@@
 \end{table}
-
-```{r}
-face_hand_detailed_plot <- face_hand_by_age %>%
-  gather(region, prop, prop_full_faces, prop_faces, prop_hands, prop_faces_and_hands) %>%
-  mutate(approach = "uncropped",
-         region = case_when(region == "prop_faces" ~"All faces",
-                            region == "prop_full_faces" ~ "Full faces (eyes, nose, mouth visible)",
-                            region == "prop_hands" ~ "All hands",
-                            region == "prop_faces_and_hands" ~ "Both hands and faces visible"),
-         child_name = case_when(child_id =='A' ~ "Child A",
-                      child_id == "S" ~ "Child S",
-                      child_id == "Y" ~ "Child Y")) %>%
-  filter(num_frames_total > 5000) # skews scaling of detections to have this 1 sparse age bin
-
-```
-
-```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of face, hand, full face (i.e., nose, mouth, and nose visible), and joint face/hand detections as a function of age for each child in the dataset.
-Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range." }
-ggplot(face_hand_detailed_plot, 
-       aes(x=age_day_bin, y=prop, 
-           col=region)) +
-  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
-  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
-  ylab('Proportion Detections') + 
-  xlab('Age (Months)') +
-  ylim(0,.5) +
-  facet_grid(.~child_name) + 
-  theme_few(base_size=12) +
-  scale_color_manual(values = c( "#2048d6","#d62020","#751098","#142c83"), name = "") +
-  scale_size_continuous(name = "") +
-  guides(size = FALSE) +
-  theme(legend.text=element_text(size=8)) +
-  theme(legend.position="bottom") 
-```
 
@@
 Finally, we also examined whether there were changes in where faces tended to appear in the camera's (and hence, by proxy, the child's) field of view. 
-As expected, faces tended to be located towards the upper field of view, while views of hands were more centrally distributed (see Appendix, Figure XX for average density distributions). 
+As expected, faces tended to be located towards the upper field of view, while views of hands were more centrally distributed (see Appendix, Figure \ref{fig:faceHandDensity} for average density distributions).
 However, we also found evidence that older children tended to see more faces in more variable positions than younger children. 

### 2021-05-25 paper/preprint/paper_revised_submission_april2021_apa.Rmd

@@
 
-```{r eval=FALSE}
+```{r eval=T}
 summary_by_age_days <- all_vid_data %>%

### 2021-05-25 preprocessing/step5_preprocess_fullset_from_bb_outputs.Rmd
update to help process high conf bbs

@@
 # toggle between each of these folders / dataset types
-dataset_dir = "/data/op_outputs_per_vid_rds/"; dataset_type = "all_detections"
-# dataset_dir = "/data/op_outputs_per_vid_rds_high_conf/"; dataset_type = "high_conf_detections"
+# dataset_dir = "/data/bounding_boxes/"; dataset_type = "all_detections"
+dataset_dir = "/data/high_conf_bounding_boxes/"; dataset_type = "high_conf_detections"
 
@@
          filter(conf_thres==.5)
-      assert_that(length(this_vid_data$frame)>0)
+      # assert_that(length(this_vid_data$frame)>0)
    }
 
+   if (length(this_vid_data$frame)>0){
     # summarize hands/faces in each video
@@
   assert_that(!sum(is.na(all_vid_data$face_and_hands_center))==length(all_vid_data$vid_name))
+   }
    }

### 2021-05-25 paper/preprint/appendix.Rmd
add child/adult hand density plot to appendix

@@
 
+# Density of child vs. adults hands in the visual field
+
+```{r} 
+### Load turk hand annotations with all bounding boxes (multiple dets per frame)
+load(here::here('data/preprocessed_data_2021/hand_annotations_2020-01-29.RData'))
+
+child_hands <- hand_annotations %>%
+  filter(label=="Child hand")
+
+adult_hands <- hand_annotations %>%
+  filter(label=="Adult hand")
+```
+
+```{r}
+### plot centers of the bounding boxes made for child and adult hands
+child_hand_plot <- ggplot(child_hands, aes(x=center_x, y=center_y)) +
+  geom_point(alpha=.1) + 
+  stat_density_2d(aes(fill = ..level..), geom="polygon", alpha=.8) +
+  coord_fixed(ratio=1) +
+  ggtitle('A. Child hand density') +
+  ylim(0,480) +
+  xlim(0,640) +
+  ylab('') +
+  xlab('') +
+  theme_few(base_size=6) +
+  theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
+  scale_y_reverse()
+##
+adult_hand_plot <- ggplot(adult_hands, aes(x=center_x, y=center_y)) +
+  geom_point(alpha=.1) + 
+  stat_density_2d(aes(fill = ..level..), geom="polygon", alpha=.8) +
+  coord_fixed(ratio=1) +
+  ylim(0,480) +
+  xlim(0,640) +
+  scale_y_reverse() +
+  ylab('') +
+  xlab('') +
+  theme_few(base_size=6) +
+    theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
+  ggtitle('B. Adult hand density')
+```
+
+```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=5, fig.height=3, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant.
+Brighter values indicate more detections."}
+cowplot::plot_grid(child_hand_plot, adult_hand_plot, nrow=1)
+```
+
 # Distribution of faces and hands in the visual field
-
 We explored where in the visual field children tended to see faces and hands, suspecting that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank (2012).
-As expected, faces tended to appear in the upper visual field in contrast to hands, which tended to be more centrally located.  
-However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ -- and perhaps adults’ -- visual environment from 6 months of age.
+As expected, faces tended to appear in the upper visual field in contrast to hands, which tended to be more centrally located.However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ visual environment from 6 months of age.
 
@@
 
-```{r, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field; each dot represents the average position from one video within a given age range."}
+```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field; each dot represents the average position from one video within a given age range."}
 

### 2021-05-25 preprocessing/step4_create_bounding_box_summaries.Rmd
minor updates to bounding box summaries csript

@@
 
-   # if data wasn't normalized -- some (but not all!) Y videos
-   if (this_vid_data$child_id[1]=='Y' &  max(this_vid_data$height, na.rm=TRUE)>1) {
-     this_vid_data <- this_vid_data %>% 
-        mutate(top = top/y_max, height = height/y_max, left = left/x_max, width = width/x_max)
-   }
+   # # if data wasn't normalized -- some (but not all!) Y videos
+   # if (this_vid_data$child_id[1]=='Y' &  max(this_vid_data$height, na.rm=TRUE)>1) {
+   #   this_vid_data <- this_vid_data %>% 
+   #      mutate(top = top/y_max, height = height/y_max, left = left/x_max, width = width/x_max)
+   # }
 
-   this_vid <- this_vid_data %>%
+   # this_vid <- this_vid_data %>%
+   #    filter(!is.na(height)) %>%
+   #    filter(mean_confidence > 0) %>% # sanity
+   #    mutate(area = height * width) %>%
+   #    group_by(label, child_id, vid_name) %>%
+   #    summarize(num_detect = length(height), avg_area = median(area), avg_height = median(height), avg_width = median(width), avg_left = median(left), avg_top = median(top))
+
+   this_vid_faces <- this_vid_data %>%
       filter(!is.na(height)) %>%
-      filter(mean_confidence > 0) %>% # sanity
-      mutate(area = height * width) %>%
-      group_by(label, child_id, vid_name) %>%
-      summarize(num_detect = length(height), avg_area = median(area), avg_height = median(height), avg_width = median(width), avg_left = median(left), avg_top = median(top))
+      filter(label=='face') %>%
+      filter(mean_confidence > 0)
 
-   empty_vid = (length(this_vid$num_detect)==0)
-   if (empty_vid) {
-     print(vid_file)
-    }
+   empty_vid=FALSE
+   # empty_vid = (length(this_vid_data$num_detect)==0)
+   # if (empty_vid) {
+   #   print(vid_file)
+   #  }
 
    if (vid_index == 1 ){
-     all_vid_bbs <- this_vid
+     # all_vid_bbs <- this_vid
+     all_faces <- this_vid_faces
    }
    else if (vid_index > 1 && empty_vid==FALSE) {
-   all_vid_bbs <- all_vid_bbs %>%
-     full_join(this_vid)
+   # all_vid_bbs <- all_vid_bbs %>%
+   #   full_join(this_vid)
+
+   all_faces <- all_faces %>%
+      full_join(this_vid_faces)
    }
@@
 ```{r}
-all_vid_bbs <- all_vid_bbs %>%
+# all_vid_bbs <- all_vid_bbs %>%
+#   left_join(age_info) %>%
+#   rowwise() %>%
+#   mutate(date_filmed = lubridate::ymd(str_split_fixed(vid_name,"_",4)[[2]])) %>%
+#   mutate(age_days = as.numeric(difftime(date_filmed,bday)) )
+# 
+# save(all_vid_bbs,file=here::here('data/preprocessed_data_2021/bounding_box_summaries_all.RData'))
+
+all_faces <- all_faces %>%
   left_join(age_info) %>%
@@
 
-save(all_vid_bbs,file=here::here('data/preprocessed_data_2021/bounding_box_summaries_all.RData'))
+ save(all_vid_bbs,file=here::here('data/preprocessed_data_2021/all_faces_summary.RData'))
 

### 2021-05-25 paper/preprint/paper_revised_submission_april2021_apa.Rmd
updates to figures, rmd, pdf following last round of edits

@@
 Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants.
-Here, we examine the prevalence of faces and hands in a longitudinal collection of nearly 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYCam dataset [@SAYcam].
-To analyze these naturalistic infant egocentric videos, we first validated the use of a modern convolutional neural network of pose detection (OpenPose) for the detection of faces and hands.
-We then applied this model to the entire dataset, and found a higher proportion of hands in view than previous reported and a moderate decrease the proportion of faces in children's view across age.
-In addition, we found variability in the proportion of faces/hands viewed by different children in different locations (e.g., living room vs.
+Here, we examine the prevalence of faces and hands in a longitudinal collection of more than 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYCam dataset [@SAYcam].
+To analyze these naturalistic infant egocentric videos, we first validated the use of a modern convolutional neural network of pose detection (OpenPose) for the detection of faces and hands and then applied this model to the entire dataset.
+First, we found a higher proportion of hands in view than previously reported and a moderate decrease in the proportion of faces in children's view across age.
+Second, we  found variability in the proportion of faces/hands viewed by different children in different locations (e.g., living room vs.
 kitchen), suggesting that individual activity contexts may shape the social information that infants experience.
+Third, we found evidence that children may see closer, larger views of people, hands, and faces earlier in development.
+These analyses provide new insight into the changes in the social information in view across early development and call for further work that examines their generalizability across populations and their relationship to learning outcomes.
 
 keywords          : "social cognition; face perception; infancy; head cameras; deep learning"
-wordcount         : "3444"
+wordcount         : "4392"
 
@@
 linenumbers       : yes
-mask              : no
+mask              : yes
 draft             : no
@@
 
-```{r eval=FALSE,include=FALSE}
+```{r}
 ## for high confidence detections
@@
   mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
-  right_join(all_gold_sample_frames_op_hc) %>% # HIGH CONF DF
+  left_join(all_gold_sample_frames_op_hc) %>% # HIGH CONF DF
   mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))
@@
 # }
-
 ```
 
-To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A); `r  24000-length(gold_sample$face_openpose)` frames sampled from allocentric videos were excluded, and these videos were also excluded from the other analyses.
+```{r}
+num_frames_excluded = 24000-length(gold_sample$face_openpose)
+```
+
+To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A); `r  num_frames_excluded` frames sampled from allocentric videos were excluded, and these videos were also excluded from the other analyses.
 Frames were jointly annotated for the presence of faces and hands by one author.
@@
 In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.
+We also found that restricing our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`)
 
-We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose—-a notoriously challenging detection problem [@bambach2015lending].
+We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose--a notoriously challenging detection problem [@bambach2015lending].
 To assess this possibility, we obtained human annotations for the entire subsample of 9051 frames in which a hand was detected; participants (recruited via AMT) were asked to draw bounding boxes around children’s and adult’s hands.
@@
 
-Finally, we examined whether the precision, recall, and F-score for hands and faces varied with age or child, and did not find substantial variation.
-Thus, while OpenPose was trained on photographs from the adult perspective, this model still generalized relatively well to the egocentric infant viewpoint with no fine-tuning or post-processing of the detections.
+Finally, we examined whether the precision, recall, and F-score for hands and faces varied with age or child, and did not find substantial variation.Thus, while OpenPose was trained on photographs from the adult perspective, this model still generalized relatively well to the egocentric infant viewpoint with no fine-tuning or post-processing of the detections.
 As these detections were imperfect compared to human annotators, fine-tuning these models to better optimize for the infant viewpoint remains an open avenue for future work.
@@
 
-```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=7, fig.cap = "Proportion of frames with (A).All face and hand detections,  B.Face/hand detections that fell within the center field-of-view (reducing the contribution of children's own hands) and (C) Face detections that were full faces (e.g., eyes, nose, and mouth all visible) and that co-occurred with hands, plotted as a function of age for each child (A, S, and Y).
+```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=6, fig.cap = "Proportion of frames with (A).All face and hand detections,  B.Face/hand detections that fell within the center field-of-view (reducing the contribution of children's own hands) and (C) Face detections that were full faces (e.g., eyes, nose, and mouth all visible) and that co-occurred with hands, plotted as a function of age for each child (A, S, and Y).
 Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range."}
@@
 
-Finally, we analyzed how these two sources of social information co-occurred, finding that faces/hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}C).
-To do so, we  calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range.
-We found that all three infants than were more likely see hands independently -- without the presence of a face -- that they were likely to see faces independently \ref{fig:faceHandContingnecy}.
-That is, generally speaking when a face was present, a hand also tended to be present.
-
 As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%.
@@
 Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}B). 
-We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure\ref{fig:goldSetSanity}).
+We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure \ref{fig:goldSetSanity}).
 
-Finally, we analyzed how these two sources of social information co-occurred, finding that faces/hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}).
+Finally, we analyzed how these two sources of social information co-occurred, finding that faces/hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}C).
 To do so, we  calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range.
@@
 # # singular:
-#faces_model2 = summary(lmer(prop_faces_center ~ poly(age_scale, 2) + (poly(age_scale, 2) | child_id), 
+# faces_model2 = summary(lmer(prop_faces_center ~ poly(age_scale, 2) + (poly(age_scale, 2) | child_id),
                            # data = summary_by_age_days))
+
 faces_model2 <- lmer(prop_faces_center ~ poly(age_scale, 2) + (1 | child_id), 
@@
 
-<!-- Next, we examined detailed changes in how infants viewed faces across development. -->
 Supporting this idea, we found that the averages sizes of the people, faces, and hands in the infant view became smaller over development (Figure \ref{fig:avgSizes}). 
@@
 There is a trend from larger, closer faces (with a larger interpupillary distance) to smaller faces that were farther away (with a smaller interpupillary distance).
-<!-- However, in our previous analysis we found relatively equal proportions of complete, full-view faces across development (see e.g., Figure \ref{fig:faceHandDetailed}, where full view faces stayed relatively constant as a proportion of all detected faces).
--->
 
@@
 #   geom_point(alpha=.2) +
-#   geom_smooth(method='lm')
+#   geom_smooth(method='lm') d
 #
@@
 ```
-
-<!-- NEED TO LOOK AT PROPORTION OF FULL FACES IN ALL FACES -->
-<!-- : in other words, these very close views of eyes experienced by younger infants were sometimes partial views. -->
 

### 2021-05-26 paper/preprint/paper_revised_submission_april2021_apa.Rmd
Intro/Discussion edits, quadratic results, added references

@@
 ---
-title             : "Detecting social information in a dense database of infants’ natural visual experience"
-shorttitle        : "Detecting social information"
+title             : "A longitudinal analysis of the social information in infants' naturalistic visual experience using automated detections"
+shorttitle        : "Longitudinal analysis of social information"
 
@@
 Here, we examine the prevalence of faces and hands in a longitudinal collection of more than 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYCam dataset [@SAYcam].
-To analyze these naturalistic infant egocentric videos, we first validated the use of a modern convolutional neural network of pose detection (OpenPose) for the detection of faces and hands and then applied this model to the entire dataset.
+To analyze these naturalistic infant egocentric videos, we validated the use of a modern convolutional neural network of pose detection (OpenPose) for the detection of faces and hands and then applied this model to the entire dataset.
 First, we found a higher proportion of hands in view than previously reported and a moderate decrease in the proportion of faces in children's view across age.
@@
 Third, we found evidence that children may see closer, larger views of people, hands, and faces earlier in development.
-These analyses provide new insight into the changes in the social information in view across early development and call for further work that examines their generalizability across populations and their relationship to learning outcomes.
+These analyses provide new insight into the changes in the social information in view across the first few years of life and call for further work that examines their generalizability across populations and their relationship to learning outcomes.
 
@@
 Though parents and scientists alike have strong intuitions about what infants see, even the viewpoint of a walking child is hard to intuit [@clerkin2017; @franchak2011]. 
-By equipping infants and toddlers with head-mounted cameras, researchers have begun to document the infant's egocentric perspective on the world. 
-Using these methods, a growing body of work now demonstrates that the viewpoints of very young infants (less than 4 months of age) are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @Sugden2014; @Jayaraman2018].
+By equipping infants and toddlers with head-mounted cameras, researchers have begun to document the infant's egocentric perspective on the world [@smith2015contributions; @smith2018developing; @franchak2011] and the consequences of this changing view for early learning.
+Using these methods, a growing body of work now demonstrates that the viewpoints of very young infants (less than 4 months of age) are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @jayaraman2013visual; @jayaraman2017faces; @Sugden2014; @Jayaraman2018].
 
-Beyond these early months, infants' motor and cognitive abilities mature, leading to vastly different perspectives on the world.
-For example, crawlers see fewer faces and hands than do walking children [@sanchez2018postural; @franchak2017see; @kretch2014] as well as different views of objects [@smith2011not].
+Beyond these early months, infants' motor and cognitive abilities mature, leading to vastly different perspectives on the world [@iverson2010].
+For example, children see fewer faces and hands when crawling than walking or sitting [@luo2020head; @sanchez2018postural; @franchak2017see; @kretch2014; @franchak2019changing; @yamamoto2020transition] as well as different views of objects [@smith2011not; @luo2020head].
 Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, and their perspective starts to capture views of hands manipulating objects [@Fausey2016].
@@
 Second, the head-mounted cameras used in the SAYCam dataset captured a larger field of view than those typically used, allowing a more complete picture of the infant perspective.
-While head-mounted cameras with a more restricted field of view do represent where infants are foveating most of the time [@yoshida2008; @smith2015contributions], they may fail to capture short saccades to either faces or hands in the periphery, as the timescale of head movements is much longer.
+While head-mounted cameras with a more restricted field of view do represent where infants are foveating most of the time [@yoshida2008; @smith2015contributions], they may fail when faces or hands appear in children's peripheral vision but are still part of a joint interaction.
 
@@
 In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.
-We also found that restricing our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`)
+We also found that restricting our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`)
 
 We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose--a notoriously challenging detection problem [@bambach2015lending].
-To assess this possibility, we obtained human annotations for the entire subsample of 9051 frames in which a hand was detected; participants (recruited via AMT) were asked to draw bounding boxes around children’s and adult’s hands.
+To assess this possibility, we obtained human annotations for the entire subsample of 9051 frames in which a hand was detected; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands.
 Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100`% of missed hand detections were of child hands.
@@
 First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:faceHandDetailed}), in keeping with prior findings [@Fausey2016]; in contrast, we did not observe an increase in the proportion of hands in view.
-These effects were quantified with two separate linear mixed-models (see Tables 1 & 2).^[Face/hand detections were binned across each week of filming.
+These effects were quantified with two separate linear mixed-effect models (see Tables 1 & 2)^[Face/hand detections were binned across each week of filming.
 Participant's age was converted into months and centered for these analyses.
-Random slopes for the effect of age by child led to a singular fit and were removed from both analyses; see full model specification in accompanying codebase.]
+Random slopes for the effect of age by child led to a singular fit and were removed from both analyses; see full model specification in accompanying codebase.] After visualizing the data (see Figure \ref{fig:faceHandDetailed}A), we examined whether linear vs.
+quadratic terms relating children's age to the proportion of faces/hands detected would provide better fits to the data, and found that this was true in both cases (see Tables 1 & 2), though linear terms also provided a significant fit for faces.
+Thus, these exploratory results point towards the idea that some children may experience overall more social information in view in the second year of life.
 
@@
 This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may be an underestimate of the proportion of hands in view.
-In fact, analysis the human annotations underscores revealed a much higher proportion of hands relative to faces than the automated annotations.
+In fact, analysis of the human annotations underscores revealed a much higher proportion of hands relative to faces than the automated annotations.
 
@@
 # General Discussion
-
 Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.
-First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016]. 
+First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016; @Jayaraman2015]. 
 This finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018].
@@
 
-We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field-of-view to the center field of view the videos to make the viewpoints comparable to those of headcams used in previous work [@Fausey2016].
+We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field-of-view to the center field-of-view to make the viewpoints comparable to those of headcams used in prior work.
 Why might this be the case?
@@
 We also used these detailed pose annotations to explore finer-grained changes in how children experience the faces and hands of their caregivers over development.
-We found that the faces, hands, and people in the infant view tended to become smaller and that faces tended to be farther away and in more variable horizontal positions.
-Overall, these data support the idea that the social information in view changes across development as infants become increasingly mobile and independent.
-As children can navigate the world on their own, they may experience fewer close-up interactions with the caregivers and more bouts of play where they are exploring the objects and things in the environment around them.
+We found that the faces, hands, and people in the infant view tended to become smaller and that faces tended to be farther away and in more variable horizontal positions, in keeping with prior work examining the sizes of faces in the infant view during the first year of life [@Jayaraman2015].
+Overall, these data support the idea that the social information in view changes across development as infants become increasingly mobile and independent [@franchak2018; @fausey2016].
+As children explore the world on their own [@xu2019towards], they may experience fewer close-up interactions with the caregivers and more bouts of play where they are exploring the objects and things in the environment around them.
 
@@
 Indeed, while unprecedented in size, this dataset still has many limitations.
-These videos only represent a small portion of the everyday experience of these three children, all of whom come from relatively privileged households in western societies and thus are not representative in many ways of the global population.
-Any idiosyncrasies in how and when these particular families chose to film these videos also undoubtedly influences the variability seen here.
+These videos only represent a small portion of the everyday experience of these three children, all of whom come from relatively privileged households in western societies and thus are not representative in many ways of the global population [@karasik2018ties; @henrich2010most].
+Any idiosyncrasies in how and when these particular families chose to film these videos also undoubtedly influences the variability seen here, and may contribute to the individual differences between the three children in this dataset.
 And without eye-tracking data, we do not know if children are attending to the social information in their visual field.
@@
 Nonetheless, we believe that these advances in datasets and methodologies represent a step in the right direction.
-The present paper demonstrates the feasibility of using a modern computer vision model to annotate the entirety of a very large dataset (here, >40M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to prior work.
-We propose that the large-scale analysis of dense datasets, collected with different fields of view, cameras and from many different laboratories, will lead to generalizable conclusions about the regularities of infant experience that scaffold learning.
+The present paper demonstrates the feasibility of using a modern computer vision model to annotate the entirety of a very large dataset (here, >40M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to human annotations in prior work.
+While OpenPose did not provide annotations that were as accurate as those provided by human annotators, we found relatively consistent results with prior literature, suggesting that the sheer scale and density of the annotations provided by this method may overcome some of it's limitations.
+
+In future work, the adaptation of deep neural networks for the infant egocentric view remains a promising avenue for collaboration between computer vision experts and developmental psychologists, and indeed has already yielded new insights about the learning mechanisms needed to build visual representations [@tsutsui2020computational; @zhuang2020unsupervised; @orhan2020self].
+We propose that the use of novel algorithms with large-scale analysis of dense datasets -- collected with different fields of view, cameras, and from many different laboratories -- will lead to generalizable conclusions about the regularities of infant experience that scaffold learning.
 

### 2021-05-26 paper/preprint/paper_revised_submission_april2021_apa.Rmd
minor edits and new pdf

@@
 keywords          : "social cognition; face perception; infancy; head cameras; deep learning"
-wordcount         : "4392"
+wordcount         : "4671"
 
@@
 In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.
-We also found that restricting our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`)
+We also found that restricting our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`).
 
@@
 Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}).
-We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure\ref{fig:goldSetSanity}).
+We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure \ref{fig:goldSetSanity}).
 
@@
 Following this idea, we investigated whether there were differences in access to faces by the activity that the child was engaged in.
-This hypothesis seems intuitively appealing.  
-Some activities seem likely to be characterized by a much higher proportion of faces (e.g., diaper changes) than others (e.g., a car trip). 
+This hypothesis seems intuitively appealing. Some activities seem likely to be characterized by a much higher proportion of faces (e.g., diaper changes) than others (e.g., a car trip). 
 Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime).
@@
 While OpenPose did not provide annotations that were as accurate as those provided by human annotators, we found relatively consistent results with prior literature, suggesting that the sheer scale and density of the annotations provided by this method may overcome some of it's limitations.
-
 In future work, the adaptation of deep neural networks for the infant egocentric view remains a promising avenue for collaboration between computer vision experts and developmental psychologists, and indeed has already yielded new insights about the learning mechanisms needed to build visual representations [@tsutsui2020computational; @zhuang2020unsupervised; @orhan2020self].

### 2021-05-28 paper/preprint/paper_revised_submission_april2021_apa.Rmd
minor wording

@@
 abstract: |
-           The faces and hands of caregivers and other social partners offer a rich source of social and causal information that may be critical for infants' cognitive and linguistic development.
+           The faces and hands of caregivers and other social partners offer a rich source of social and causal information that is likely critical for infants' cognitive and linguistic development.
 Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants.
-Here, we examine the prevalence of faces and hands in a longitudinal collection of more than 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYCam dataset [@SAYcam].
-To analyze these naturalistic infant egocentric videos, we validated the use of a modern convolutional neural network of pose detection (OpenPose) for the detection of faces and hands and then applied this model to the entire dataset.
+Here, we examine the prevalence of faces and hands in a longitudinal collection of more than 1700 headcam videos from three children ages 6 to 32 months.
+To analyze these naturalistic infant egocentric videos, we validated the use of a modern convolutional neural network (OpenPose) for the detection of faces and hands and then applied this model to the entire dataset.
 First, we found a higher proportion of hands in view than previously reported and a moderate decrease in the proportion of faces in children's view across age.
-Second, we found variability in the proportion of faces/hands viewed by different children in different locations (e.g., living room vs.
+Second, we found substantial variability in the proportion of faces and hands viewed by different children in different locations (e.g., living room vs.
 kitchen), suggesting that individual activity contexts may shape the social information that infants experience.
@@
 # Introduction
-Infants are confronted by a blooming, buzzing onslaught of stimuli [@james1890principles] which they must learn to parse to make sense of the world around them.
+Infants are confronted by a blooming, buzzing onslaught of stimuli [@james1890principles] that they must learn to parse to make sense of the world around them.
 Yet they do not embark on this learning process alone: From as early as 3 months of age, young infants follow overt gaze shifts [@gredeback2008microstructure], and even newborns prefer to look at faces with direct vs.
@@
 ## Detection Method
-To automatically annotate the millions of frames in SAYCam, we used a pose detector, OpenPose ^[https://github.com/CMU-Perceptual-Computing-Lab/openpose]  [@Cao2018openpose; @Simon2017hand], which provided the locations of 18 body parts (ears, nose, wrists, etc.).
-To do so, a convolutional neural network was used for initial anatomical detection, and part affinity fields were subsequently applied for part association to produce a series of body part candidates.
-Once these body part candidates were matched to a single individual in the frame, they were finally assembled into a pose.
-Thus, while we only made use of the outputs of the face and hand detections, the entire set of pose information from an individual was used to determine the presence of a face/hand, making the process more robust to occlusion than methods optimized to detect only faces or hands.
-Note, however, that these face/hand detections are reliant on the detection of at least a partial pose, so some very up-close views of faces/hands may go undetected.
+To  annotate the millions of frames in SAYCam automatically, we used a pose detector, OpenPose^[https://github.com/CMU-Perceptual-Computing-Lab/openpose]  [@Cao2018openpose; @Simon2017hand].
+The OpenPose system provides the locations of up to 18 body parts (ears, nose, wrists, etc.) from individual frames.
+OpenPose relies on a convolutional neural network for initial anatomical detection.
+It then uses part affinity fields for part association to produce a series of body part candidates.
+Once these body part candidates are matched to a single individual in the frame, they are finally assembled into a pose.
+While in this study we only measured face and hand presence, the entire set of pose information from an individual was used to determine the presence of a face/hand, making the process much more robust to occlusion than methods optimized to detect *only* faces or hands.
+Of course, these face/hand detections are nevertheless reliant on the detection of at least a partial pose, so some very up-close views of faces/hands may still go undetected.
 
@@
 
-We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose--a notoriously challenging detection problem [@bambach2015lending].
+We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose -- a notoriously challenging detection problem [@bambach2015lending].
 To assess this possibility, we obtained human annotations for the entire subsample of 9051 frames in which a hand was detected; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands.
@@
 
-Finally, we examined whether the precision, recall, and F-score for hands and faces varied with age or child, and did not find substantial variation.Thus, while OpenPose was trained on photographs from the adult perspective, this model still generalized relatively well to the egocentric infant viewpoint with no fine-tuning or post-processing of the detections.
+Finally, we examined whether the precision, recall, and F-score for hands and faces varied with age or child, and did not find substantial variation.
+Thus, while OpenPose was trained on photographs from the adult perspective, this model still generalized relatively well to the egocentric infant viewpoint with no fine-tuning or post-processing of the detections.
 As these detections were imperfect compared to human annotators, fine-tuning these models to better optimize for the infant viewpoint remains an open avenue for future work.
@@
 First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:faceHandDetailed}), in keeping with prior findings [@Fausey2016]; in contrast, we did not observe an increase in the proportion of hands in view.
-These effects were quantified with two separate linear mixed-effect models (see Tables 1 & 2)^[Face/hand detections were binned across each week of filming.
+These effects were quantified with two separate linear mixed-effect models (see Tables 1 & 2).^[Face/hand detections were binned across each week of filming.
 Participant's age was converted into months and centered for these analyses.
-Random slopes for the effect of age by child led to a singular fit and were removed from both analyses; see full model specification in accompanying codebase.] After visualizing the data (see Figure \ref{fig:faceHandDetailed}A), we examined whether linear vs.
-quadratic terms relating children's age to the proportion of faces/hands detected would provide better fits to the data, and found that this was true in both cases (see Tables 1 & 2), though linear terms also provided a significant fit for faces.
+Random slopes for the effect of age by child led to a singular fit and were removed from both analyses; see full model specification in accompanying codebase.] After visualizing the data (see Figure \ref{fig:faceHandDetailed}A), we examined whether the addition of quadratic terms relating children's age to the proportion of faces/hands detected would provide better fit to the data than linear terms alone, and found that this was true in both cases (see Tables 1 & 2), though the linear term was also significant for faces.
 Thus, these exploratory results point towards the idea that some children may experience overall more social information in view in the second year of life.
 
-However, the most striking result from these analyses is a much overall greater proportion of hands in view than have previously been reported [@Fausey2016].
-We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Appendix Figure \ref{fig:goldSetSanity}) or OpenPose annotations on the entire dataset (see Figure \ref{fig:faceHandDetailed}A).
-This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may be an underestimate of the proportion of hands in view.
-In fact, analysis of the human annotations underscores revealed a much higher proportion of hands relative to faces than the automated annotations.
+However, the most striking result from these analyses is a much greater overall proportion of hands in view than has previously been reported [@Fausey2016].
+We found this observation to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Appendix Figure \ref{fig:goldSetSanity}) or OpenPose annotations on the entire dataset (see Figure \ref{fig:faceHandDetailed}A).
+This finding is notable especially given that OpenPose showed relatively low recall for hands, indicating that our measurements may in fact be an underestimate of the proportion of hands in view.
+In fact, analysis of the human gold standard annotations revealed a much higher proportion of hands relative to faces than the automated annotations.
 
-One reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees.
+One reason we could have observed more hands in view than previous studies is the much larger field of view that was captured by the cameras used in this study.
+These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies.
+For example, in @Fausey2016 the FOV was 69 x 41 degrees.
 This larger FOV may have allowed the SAYCam cameras to capture not only the presence of a social partner’s hands interacting with objects or gestures, but also the children’s own hands, leading to more frequent hand detections.
@@
 
-As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%.
+As we found that children's hands tended to occur in the lower visual field (see Figure Appendix \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, and face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%.
 This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
@@
 
-Finally, we analyzed how these two sources of social information co-occurred, finding that faces/hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}C).
+Finally, we analyzed how these two sources of social information co-occurred.
 To do so, we  calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range.
-As shown in Figure \ref{fig:faceHandContingency}, we found that all three infants were more likely to see hands independently -- without the presence of a face -- than they were likely to see faces independently.
+Faces and hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}C).
+As shown in Figure \ref{fig:faceHandContingency}, all three infants were more likely to see hands independently -- without the presence of a face -- than they were likely to see faces independently.
 That is, generally speaking when a face was present, a hand also tended to be present.
@@
 Following this idea, we investigated whether there were differences in access to faces by the activity that the child was engaged in.
-This hypothesis seems intuitively appealing. Some activities seem likely to be characterized by a much higher proportion of faces (e.g., diaper changes) than others (e.g., a car trip). 
+This hypothesis seems intuitively appealing.
+Some activities seem likely to be characterized by a much higher proportion of faces (e.g., diaper changes) than others (e.g., a car trip).
 Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime).
@@
 For example, while both A and S saw a relatively similar proportion of faces and hands in the bedroom, the two children saw quite different amounts of faces and hands from one another in the kitchen. 
-This difference is likely explained by differences in arrangement of the kitchen in the two children's households (Sullivan, personal communication), such that mealtimes in one kitchen resulted in a face-to-face orientation while it did not in the other).
+This difference is likely explained by differences in arrangement of the kitchen in the two children's households (Sullivan, personal communication), such that mealtimes in one kitchen resulted in a face-to-face orientation while they did not in the other.
 This example illustrates how specifics of the geometry of a particular context can play an outsize role in the child's access to social information during that context.
@@
 Figure \ref{fig:faceDetailed}A shows the average interpupillary distance on faces as a function of each child’s age at the time of recording. 
-There is a trend from larger, closer faces (with a larger interpupillary distance) to smaller faces that were farther away (with a smaller interpupillary distance).
+There was a trend from larger, closer faces (with a larger interpupillary distance) to smaller faces that were farther away (with a smaller interpupillary distance).
 
@@
 Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.
+
 First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016; @Jayaraman2015].
@@
 One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment.
-During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly---leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1).
+During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1).
 Indeed, using the same pose detector on videos from in-lab play sessions, @sanchez2018postural found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age.
@@
 A coarse analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations and between individual children.
-Within a given, well-defined context---e.g., mealtime in kitchens---S saw more faces than A, and S saw more faces in the kitchen than in other locations.
+Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations.
 This variability likely stems from the fact that there are at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side.
@@
 While OpenPose did not provide annotations that were as accurate as those provided by human annotators, we found relatively consistent results with prior literature, suggesting that the sheer scale and density of the annotations provided by this method may overcome some of it's limitations.
-In future work, the adaptation of deep neural networks for the infant egocentric view remains a promising avenue for collaboration between computer vision experts and developmental psychologists, and indeed has already yielded new insights about the learning mechanisms needed to build visual representations [@tsutsui2020computational; @zhuang2020unsupervised; @orhan2020self].
+
+In future work, the adaptation of deep neural networks for the infant egocentric view remains a promising avenue for collaboration between computer vision experts and developmental psychologists.
+Indeed, this combination has already yielded new insights about the learning mechanisms needed to build visual representations [@tsutsui2020computational; @zhuang2020unsupervised; @orhan2020self].
 We propose that the use of novel algorithms with large-scale analysis of dense datasets -- collected with different fields of view, cameras, and from many different laboratories -- will lead to generalizable conclusions about the regularities of infant experience that scaffold learning.
@@
 # Acknowledgements
+
 Thanks to the creators of the SAYCam dataset who made this work possible and to Alessandro Sanchez for his contributions to the codebase.
-This work was funded by a Jacobs Foundation Fellowship to MCF, a John Mereck Scholars award to MCF, and NSF #1714726 to BLL.
+This work was funded by a Jacobs Foundation Fellowship to MCF, a John Merck Scholars award to MCF, and NSF #1714726 to BLL.
 

### 2021-06-09 paper/preprint/paper_revised_submission_april2021_apa.Rmd
Minor wording change

--- 2021-05-26 paper/preprint/paper_revised_submission_april2021_apa.Rmd
@@
 
-As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%.
+As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, and decreasing face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%.
 This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.

### 2021-06-09 paper/preprint/appendix.Rmd

@@
 # Face/hand detections relative to human annotations
-```{r goldSetSanity, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset.
+```{r goldSetSanity, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=4, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset.
 Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range.
@@
   facet_grid(.~child_id) + 
-  theme_few(base_size=9) +
+  theme_few(base_size=10) +
   ggthemes::scale_color_solarized(name = "") + 
   scale_size_continuous(name = "Detections (Log 10)") +
-  theme(legend.text=element_text(size=8)) +
+  theme(legend.text=element_text(size=10)) +
   theme(legend.position="bottom")
@@
   xlab('') +
-  theme_few(base_size=6) +
+  theme_few(base_size=10) +
   theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
@@
   xlab('') +
-  theme_few(base_size=6) +
+  theme_few(base_size=10) +
     theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
@@
 
-```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=5, fig.height=3, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant.
+```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=6.5, fig.height=3.5, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant.
 Brighter values indicate more detections."}
@@
 We explored where in the visual field children tended to see faces and hands, suspecting that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank (2012).
-As expected, faces tended to appear in the upper visual field in contrast to hands, which tended to be more centrally located.However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ visual environment from 6 months of age.
+As expected, faces tended to appear in the upper visual field in contrast to hands, which tended to be more centrally located (see Figure C1). 
+However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ visual environment from 6 months of age.
 

### 2021-06-09 paper/preprint/paper_revised_submission_april2021_apa.Rmd

--- 2021-05-28 paper/preprint/paper_revised_submission_april2021_apa.Rmd
@@
 keywords          : "social cognition; face perception; infancy; head cameras; deep learning"
-wordcount         : "4671"
+wordcount         : "4698"
 
@@
 
-With hundreds of hours of footage (>40M frames), however, this large dataset necessitates a shift to an automated annotation strategy.
+With hundreds of hours of footage (>42M frames), however, this large dataset necessitates a shift to an automated annotation strategy.
 Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that most frames are typically not inspected, even in the most comprehensive studies. 
@@
 Videos ^[All videos are available at https://nyu.databrary.org/volume/564 ] with technical errors or that were not taken from the egocentric perspective were excluded from the dataset.
-We analyze `r num_videos` videos, with a total duration of `r round(num_hours,2)` hours (>40 million frames).
+We analyze `r num_videos` videos, with a total duration of `r round(num_hours,2)` hours (>42 million frames).
 
@@
 
-```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=6, fig.cap = "Proportion of frames with (A).All face and hand detections,  B.Face/hand detections that fell within the center field-of-view (reducing the contribution of children's own hands) and (C) Face detections that were full faces (e.g., eyes, nose, and mouth all visible) and that co-occurred with hands, plotted as a function of age for each child (A, S, and Y).
+```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=6, fig.cap = "Proportion of frames with (A) All face and hand detections,  (B) Face/hand detections that fell within the center field-of-view (reducing the contribution of children's own hands) and (C) Face detections that were full faces (e.g., eyes, nose, and mouth all visible) and that co-occurred with hands, plotted as a function of age for each child (A, S, and Y).
 Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range."}
@@
 
-We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field-of-view to the center field-of-view to make the viewpoints comparable to those of headcams used in prior work.
+We also found an unexpectedly high proportion of hands in infants' view, even when restricting the field-of-view to the center field-of-view to make the viewpoints comparable to those of headcams used in prior work.
 Why might this be the case?
@@
 We found that the faces, hands, and people in the infant view tended to become smaller and that faces tended to be farther away and in more variable horizontal positions, in keeping with prior work examining the sizes of faces in the infant view during the first year of life [@Jayaraman2015].
-Overall, these data support the idea that the social information in view changes across development as infants become increasingly mobile and independent [@franchak2018; @fausey2016].
-As children explore the world on their own [@xu2019towards], they may experience fewer close-up interactions with the caregivers and more bouts of play where they are exploring the objects and things in the environment around them.
+Overall, these data support the idea that the social information in view changes across development as infants become increasingly mobile and independent [@franchak2017see; @fausey2016]. 
+As children explore the world on their own [@xu2019towards], they may experience fewer close-up interactions with their caregivers and more bouts of play where they are exploring the objects in their environment.
 
@@
 These videos only represent a small portion of the everyday experience of these three children, all of whom come from relatively privileged households in western societies and thus are not representative in many ways of the global population [@karasik2018ties; @henrich2010most].
-Any idiosyncrasies in how and when these particular families chose to film these videos also undoubtedly influences the variability seen here, and may contribute to the individual differences between the three children in this dataset.
-And without eye-tracking data, we do not know if children are attending to the social information in their visual field.
+Any idiosyncrasies in how and when these particular families chose to film these videos also undoubtedly influenced the variability seen here, and may contribute to the individual differences between the three children in this dataset.
+And without eye-tracking data, we do not know the extent to which children are attending to the social information in view.
 
 Nonetheless, we believe that these advances in datasets and methodologies represent a step in the right direction. 
-The present paper demonstrates the feasibility of using a modern computer vision model to annotate the entirety of a very large dataset (here, >40M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to human annotations in prior work.
-While OpenPose did not provide annotations that were as accurate as those provided by human annotators, we found relatively consistent results with prior literature, suggesting that the sheer scale and density of the annotations provided by this method may overcome some of it's limitations.
+The present paper demonstrates the feasibility of using a modern computer vision model to annotate the entirety of a very large dataset (here, >42M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to human annotations in prior work.
+While OpenPose did not provide annotations that were as accurate as those provided by human annotators, we found relatively consistent results with prior literature, suggesting that the sheer scale and density of the annotations provided by this method may overcome some of its limitations.
 

### 2021-06-10 paper/preprint/manuscript_june2021_apa.Rmd
Update latest version of paper and add blinded version to repo

--- 2021-06-09 paper/preprint/paper_revised_submission_april2021_apa.Rmd
@@
 
-# authornote: |
-#   Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-# 
-#   Enter author note here.
+authornote: |
+  The data and code that support the findings of this study are available at https://osf.io/cdhw4/.
 
@@
 keywords          : "social cognition; face perception; infancy; head cameras; deep learning"
-wordcount         : "4698"
+wordcount         : "4681"
 
@@
 footnotelist      : no
-linenumbers       : yes
-mask              : yes
+linenumbers       : no
+mask              : no
 draft             : no
@@
 # 
+```
 
+```{r}
 # join human and OP detections
@@
 ```{r}
-num_frames_excluded = 24000-length(gold_sample$face_openpose)
+num_frames_excluded = 24000-length(gold_sample$face_detected)
 ```
 
-To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A); `r  num_frames_excluded` frames sampled from allocentric videos were excluded, and these videos were also excluded from the other analyses.
+To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A).
 Frames were jointly annotated for the presence of faces and hands by one author.
 A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated 3150 frames; agreement with the primary coder was >95%.
+Upon manually inspecting these frames, we noticed that `r  num_frames_excluded` were sampled from videos taken from the allocentric perspective (i.e., not from the infant viewpoint); these frames and videos containing these frames were subsequently excluded from all other analyses.
 
 As has been observed in other studies on automated annotation of headcam data [e.g.
-@frank2013; @sanchez2018postural; @bambach2015lending], detection tasks that are easy in third-person video can be quite challenging in egocentric videos, due to difficult angles and sizes as well as substantial occlusion.
+@frank2013; @long2021automated; @sanchez2018postural; @bambach2015lending], detection tasks that are easy in third-person video can be quite challenging in egocentric videos, due to difficult angles and sizes as well as substantial occlusion.
 For example, the infant perspective often contains non-canonical viewpoints of faces (e.g., looking up at a caregiver's chin) as well as partially-occluded or oblique viewpoints of both faces and hands.
 Further, hand detection tends to be a harder computational problem than face detection [@Simon2017hand; @bambach2015lending].
-We thus expected overall performance to be lower in these naturalistic videos than on either photos taken from the adult perspective or in egocentric videos in controlled, laboratory settings [e.g., @sanchez2018postural].
+We thus expected overall performance to be lower in these naturalistic videos than on either photos taken from the adult perspective or in egocentric videos in controlled, laboratory settings [e.g., @long2021automated].
 
@@
 In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.
-We also found that restricting our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`).
+We also found that restricting our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
 
 We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose -- a notoriously challenging detection problem [@bambach2015lending].
-To assess this possibility, we obtained human annotations for the entire subsample of 9051 frames in which a hand was detected; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands.
+To assess this possibility, we obtained additional human annotations for the subsample of 9051 frames in the gold set frames where a hand was present; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands.
 Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100`% of missed hand detections were of child hands.
@@
 
-We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands detected for each child.^[All analyses and preprocessed data files for this paper are available at https://tinyurl.com/detecting-social-info] Data from videos were binned according to the age of the child (in weeks).
+We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands detected for each child.
+All analyses and preprocessed data files for this paper are available at tinyurl.com/longitudinal-social-info.
+Data from videos were binned according to the age of the child (in weeks).
 First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:faceHandDetailed}), in keeping with prior findings [@Fausey2016]; in contrast, we did not observe an increase in the proportion of hands in view.
@@
 As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, and decreasing face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%.
-This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
+This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure Appendix \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
 Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}).
@@
 @bruner1985role discussed the role of children's activities in shaping the information present for learning.
-Following this idea, we investigated whether there were differences in access to faces by the activity that the child was engaged in.
+Following this idea, we investigated whether there were differences in access to faces and hands by the activity that the child was engaged in.
 This hypothesis seems intuitively appealing.
@@
 Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime).
-
 We did not have access to annotations of activity. 
@@
 
-```{r avgSizes, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Average size of poses, faces, and hands detected in the dataset  between eyes in faces detected as a function of age for each child in the dataset (each color = different child).
+```{r avgSizes, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Average size of poses, faces, and hands detected in the dataset as a function of age for each child in the dataset (each color = different child).
 Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range."}
@@
 Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.
-
 First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016; @Jayaraman2015].
@@
 During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1).
-Indeed, using the same pose detector on videos from in-lab play sessions, @sanchez2018postural found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age.
+Indeed, using the same pose detector on videos from in-lab play sessions, @long2021automated found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age.
 Work that directly examines the variability in the social information in view across more vs.
@@
 # Acknowledgements
-
 Thanks to the creators of the SAYCam dataset who made this work possible and to Alessandro Sanchez for his contributions to the codebase.
@@
 
-<div id="refs" custom-style="Bibliography"></div>
 \endgroup

### 2021-06-10 paper/preprint/manuscript_june2021_apa_blinded.Rmd
Update latest version of paper and add blinded version to repo

--- 2021-06-10 paper/preprint/manuscript_june2021_apa.Rmd
@@
 author: 
-  - name          : "Bria L. Long"
+  - name          : "Blinded"
     affiliation   : "1"
     corresponding : yes    # Define only one corresponding author
-    address       : "450 Serra Mall, Stanford CA 94305"
-    email         : "bria@stanford.edu"
-  - name          : "George Kachergis"
-    affiliation   : "1"
-  - name          : "Ketan Agrawal"
-    affiliation   : "1"
-  - name          : "Michael C. Frank"
+    address       : ""
+    email         : " "
+  - name          : " "
     affiliation   : "1"
@@
   - id            : "1"
-    institution   : "Department of Psychology, Stanford University"
+    institution   : "Blinded"
 
@@
 # Acknowledgements
-Thanks to the creators of the SAYCam dataset who made this work possible and to Alessandro Sanchez for his contributions to the codebase.
-This work was funded by a Jacobs Foundation Fellowship to MCF, a John Merck Scholars award to MCF, and NSF #1714726 to BLL.
+Blinded.
 

### 2021-12-21 paper/preprint/initial_submission/manuscript_june2021_apa.Rmd
reorganize paper folder

--- 2021-06-10 paper/preprint/manuscript_june2021_apa.Rmd
@@
 Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}).
-We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure \ref{fig:goldSetSanity}).
-
-As we found that children's hands tended to occur in the lower visual field (see Figure Appendix \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, and face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%.
-This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
-Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}B). 
 We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure \ref{fig:goldSetSanity}).
@@
 Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.
-First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016; @Jayaraman2015].
+gurerst, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016; @Jayaraman2015].
 This finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018].

### 2021-12-21 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
reorganize paper folder

--- 2021-06-10 paper/preprint/manuscript_june2021_apa_blinded.Rmd
@@
 output            : 
-  papaja::apa6_pdf:
+  papaja::apa6_docx:
     includes:
@@
 Beyond these early months, infants' motor and cognitive abilities mature, leading to vastly different perspectives on the world [@iverson2010].
-For example, children see fewer faces and hands when crawling than walking or sitting [@luo2020head; @sanchez2018postural; @franchak2017see; @kretch2014; @franchak2019changing; @yamamoto2020transition] as well as different views of objects [@smith2011not; @luo2020head].
+For example, children see fewer faces and hands when crawling than walking or sitting [@luo2020head; @sanchez2018postural; @franchak2017see; @kretch2014; @franchak2019changing; @yamamoto2020transition; @long2021automated] as well as different views of objects [@smith2011not; @luo2020head].
 Further, as infants learn to use their own hands to act on the world, they seem to focus on manual actions taken by their social partners, and their perspective starts to capture views of hands manipulating objects [@Fausey2016].
@@
 
-Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of more than 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYCam dataset [@SAYcam].
+Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of more than 1700 headcam videos collected from three children along a span of 6 to 32 months of age—--the SAYCam dataset [@SAYcam].
 In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways.
@@
 Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints that operates well on scenes including multiple people, even if they are partially-occluded (see Figure 1).
-In prior work examining egocentric videos, OpenPose performed comparably to other modern face detection models [@sanchez2018postural].
+In prior work examining egocentric videos taken from the infant perspective, OpenPose performed comparably to other modern face detection models [@long2021automated].
 
@@
 
+# Variation with motor development
+```{r}
+motor = read_csv(file=here::here('data/raw_data/saycam_walking_asq.csv'))
+
+```
+
 # General Discussion

### 2021-12-21 paper/preprint_version/paper_revised_submission_june2020_apa_orig_version.Rmd
reorganize paper folder

--- 2020-06-30 paper/preprint/paper_revised_submission_june2020_apa.Rmd
@@
 summary_by_age_center <- all_vid_data_center %>%
+  ungroup() %>%
   filter(!is.na(age_days)) %>%
@@
   summarize(num_frames_total = sum(num_frames), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
+```
+
+```{r}
+## get out summary by age for goldset hand-labelled frames
+vid_info <- all_vid_data  %>%
+  select(child_id, vid_name, age_days, age_day_bin)
+
+summary_by_age_gold <- gold_sample %>%
+  left_join(vid_info) %>%
+  group_by(age_day_bin, child_id) %>%
+  summarize(num_frames_total = n(), num_faces = sum(face_present_ketan), num_hands = sum(hand_present_ketan), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
+
 ```
@@
   filter(num_frames_total > 5000) # eliminate small data point that skews scaling
+
+wide_gold <- summary_by_age_gold %>%
+  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
+  mutate(approach = "goldset",
+         region = ifelse(region == "prop_faces_summary","Face","Hands"))
 
@@
   geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + # geom_smooth(show.legend = FALSE) or move these below legend?
-  geom_smooth(data = wide_center, span=10, aes(weight = num_frames_total), show.legend = FALSE, 
+  geom_smooth(data = wide_gold, span=10, aes(weight = num_frames_total), show.legend = FALSE,
               lty = 2, span=10, se = FALSE) +
@@
   facet_grid(.~child_id) +
-  theme_few(base_size=9) +
+  theme_few(base_size=18) +
   ggthemes::scale_color_solarized(name = "") + 

### 2021-12-21 paper/preprint_version/preprocess_fullset_from_bb_outputs.Rmd
reorganize paper folder

---
title: "SAYCAM preprocessing analyses from bounding box outputs"
author: "Bria Long"
date: "6/2020"
output:
  pdf_document: default
  html_document: default
---

# Basic data loading and setup
## Packages
```{r}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(stringr)
library(here)
theme_set(theme_few())
```

## Paths to raw outputs & datafiles
```{r}
op_file_dir = here::here("data/op_outputs_per_vid/")
op_files = dir(op_file_dir)
# op_files = op_files [1] # for testing

allocentric_file = here::here("data/raw_data/SAYCAM_allocentric_videos.csv")
to_exclude =read.csv(allocentric_file)

# get INCORRECT videos where allocentric videopoint 
to_exclude <- to_exclude %>%
  filter(allocentric==1) %>%
  rename(vid_name = video)
```

## Main detections: read in bounding box outputs from each vid, summarize and compile.
```{r}
reload_data=TRUE
# instead of loading each vid, load summary...
load(here::here('data/preprocessed_data/all_vid_data_from_bbs_may2020.RData'))

if (reload_data){
vid_index = 0
for (vid_file in op_files) {
  vid_index = vid_index + 1
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
   this_vid_data <- readRDS(vid_file_path)

   summary_vid_data <- this_vid_data %>%
     group_by(frame, child_id, vid_name, right_side_up, age_days) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)  %>%
     group_by(child_id, vid_name, right_side_up, age_days) %>%
     summarize(num_hands = sum(hand_detected), num_faces = sum(face_detected), num_detect = length(hand_detected))

   if (vid_index == 1 ){
     all_vid_data <- summary_vid_data
   }
   else if (vid_index > 1) {
   all_vid_data <- all_vid_data %>%
     full_join(summary_vid_data)
   }
}
}
```

## Cropped detections: crop out detections from outer edges of frames; do so at video level.
```{r}
# cropping paramts
limit_lower =.2
limit_upper =.8
# vid params
y_max = 480
x_max = 640

load(here::here('data/preprocessed_data/all_vid_data_from_bbs_may2020.RData'))

reload_data=TRUE

if (reload_data){
vid_index = 0
for (vid_file in op_files) {

   # to check progress
   vid_index = vid_index + 1
   if ((vid_index %% 100)==0) { print (vid_file) }

   # get vid level data
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
   this_vid_data <- readRDS(vid_file_path)

    # don't bother for these files
   if (!this_vid_data$vid_name[1] %in% to_exclude$vid_name){

    # for renormalizing y's vids which were run differently this time
   if (this_vid_data$child_id[1]=='Y'){
     this_vid_data <- this_vid_data %>%
      mutate(top = top/y_max, height = height/y_max, left = left/x_max, width = width/x_max)
   }

   # now get vid level data
   summary_vid_data_center <- this_vid_data %>%
     mutate(num_frames = length(unique(frame))) %>% # count frames
     mutate(center_y = top + height/2, center_x = left + width/2) %>% # get center_x and y
     filter(center_y<(limit_upper) & center_x<(limit_upper) & center_y>(limit_lower) & center_x>(limit_lower)) %>%   # filter within parameters
     group_by(frame, child_id, vid_name, num_frames, age_days) %>% # group at frame level first
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0) %>%
     group_by(child_id, vid_name, age_days, num_frames) %>% # now at the video level
     summarize(num_hands = sum(hand_detected), num_faces = sum(face_detected)) # count how many faces/hands

   # compile vid-level summaries 
   if (vid_index == 1){
     all_vid_data_center <- summary_vid_data_center
   }
   else if (vid_index > 1) {
   all_vid_data_center <- all_vid_data_center %>%
     full_join(summary_vid_data_center)
   }
}
}
}

```

## Gold sample detections only
### Load gold sample annotations
```{R}
## load gold sample annotations
load(here('data/data_cogsci/gold_sample_annotations2020-01-31.RData')) # gold_sample

gold_sample_frames <- gold_sample %>%
  select(vid_name, frame) %>%
  mutate(vid_name = str_split(vid_name,"[.]")[[1]][1])

gold_sample_vids <- unique(gold_sample_frames$vid_name)
```

### Get detections from gold sample videos only
```{r}
reload_data=TRUE
# redo gold sample 
if (reload_data){
vid_index = 0
for (vid_file in op_files) {

   # to check progress
   vid_index = vid_index + 1
   if ((vid_index %% 100)==0) { print (vid_file) }

   # get vid level data
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
   this_vid_data <- readRDS(vid_file_path)
   this_vid_name_temp <- this_vid_data$vid_name[1]

   this_vid_name <- str_split(this_vid_name_temp,"[.]")[[1]][1]

   # if it's one of the vids from gold sample
   if (this_vid_name %in% gold_sample_vids){
   # and not excluded
   if (!this_vid_name %in% to_exclude$vid_name){

   frames_to_get <- gold_sample_frames %>%
     filter(vid_name == this_vid_name)

   # now get vid level data
   gold_sample_op <- this_vid_data %>%
     filter(frame %in% frames_to_get$frame) %>%
     mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
     group_by(frame, vid_name) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)

   # compile vid-level summaries 
   if (vid_index == 1){
     all_gold_sample_frames_op <- gold_sample_op
   }
   else if (vid_index > 1) {
   all_gold_sample_frames_op <- all_gold_sample_frames_op %>%
     full_join(gold_sample_op)
   }
}
}
}
}
```

## Data cleaning
### Choose bins across which to aggregate data
```{r}
bin_size = 7 # days
min_age = min(all_vid_data$age_days, na.rm=TRUE)
max_age = max(all_vid_data$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

vid_info <- all_vid_data %>%
  select(vid_name, age_days, child_id)
```

### Regualrize vid names & get rid of vids to exclude from allocentric file
```{r}
all_vid_data <- all_vid_data %>%
  rowwise() %>%
  mutate(vid_name_cleaned = str_split(vid_name,"[.]")[[1]][1])
```

```{r}
all_vid_data <- all_vid_data %>%
  mutate(vid_name_old = vid_name) %>%
  filter(!vid_name_cleaned %in% to_exclude$vid_name) %>%
  mutate(vid_name = vid_name_cleaned) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))

all_vid_data <- all_vid_data %>%
  mutate(vid_name = vid_name_cleaned)

save(all_vid_data, file = here::here('data/preprocessed_data/all_vid_data_from_bbs_june2020.RData'))
```

```{r}
## repeat for center cropped data
all_vid_data_center <- all_vid_data_center %>%
  rowwise() %>%
  mutate(vid_name_cleaned = str_split(vid_name,"[.]")[[1]][1])

all_vid_data_center <- all_vid_data_center %>%
  mutate(vid_name_old = vid_name) %>%
  select(-vid_name) %>%
  filter(!vid_name_cleaned %in% to_exclude$vid_name) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))

all_vid_data_center <- all_vid_data_center %>%
  mutate(vid_name = vid_name_cleaned)

save(all_vid_data_center, file = here::here('data/preprocessed_data/all_centered_vid_data_from_bbs_june2020.RData'))

```

```{r}
all_gold_sample_frames_op <- all_gold_sample_frames_op %>%
  left_join(vid_info) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))
save(all_gold_sample_frames_op, file = here::here('data/preprocessed_data/gold_sample_from_bbs_june2020.RData'))
```

### A few videos still need metadata...
```{r}
missing_age <-all_vid_data %>%
  filter(is.na(age_days))
```

### 2021-12-21 preprocessing/step5_preprocess_fullset_from_bb_outputs.Rmd

@@
 # toggle between each of these folders / dataset types
-# dataset_dir = "/data/bounding_boxes/"; dataset_type = "all_detections"
-dataset_dir = "/data/high_conf_bounding_boxes/"; dataset_type = "high_conf_detections"
+dataset_dir = "/data/bounding_boxes/"; dataset_type = "all_detections"
+# dataset_dir = "/data/high_conf_bounding_boxes/"; dataset_type = "high_conf_detections"
 
@@
   mutate(age_day_bin = as.numeric(as.character(age_day_bin)))
+
 ```
@@
 ```
+
+### Get gold sample detections by sweeping across detection thresholds
+```{r}
+reload_data=TRUE
+# redo gold sample 
+if (reload_data){
+vid_index = 0
+## load gold sample annotations
+
+load(here('data/data_cogsci/gold_sample_annotations2020-01-31.RData')) # gold_sample
+gold_sample_frames <- gold_sample %>%
+  select(-X, -level_0) %>%
+  select(vid_name, frame) %>%
+  mutate(vid_name = str_split(vid_name,"[.]")[[1]][1])
+
+gold_sample_vids <- unique(gold_sample_frames$vid_name)
+
+all_thresholds = seq(0,.9,.1)
+
+for (vid_file in op_files) {
+
+   # to check progress
+   vid_index = vid_index + 1
+   if ((vid_index %% 100)==0) { print (vid_file) }
+
+   # get vid level data
+   vid_file_path = paste0(here::here(), dataset_dir, vid_file)
+   this_vid_data <- readRDS(vid_file_path)
+   this_vid_name_temp <- this_vid_data$vid_name[1]
+   this_vid_name <- str_split(this_vid_name_temp,"[.]")[[1]][1]
+
+   # if it's one of the vids from gold sample
+   if (this_vid_name %in% gold_sample_vids){
+   # and not excluded
+   if (!this_vid_name %in% to_exclude$vid_name){
+
+   frames_to_get <- gold_sample_frames %>%
+     filter(vid_name == this_vid_name)
+
+   # now get vid level data
+
+   for (detection_thres in all_thresholds){
+
+      gold_sample_op_this_thres <- this_vid_data %>%
+        filter(frame %in% frames_to_get$frame) %>%
+        mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
+        group_by(frame, vid_name, child_id) %>%
+        summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>detection_thres) %>%
+        mutate(detection_threshold = detection_thres)
+
+      if (detection_thres==0){
+         gold_sample_op<-gold_sample_op_this_thres
+      }
+      else if (detection_thres>0){
+      gold_sample_op <- gold_sample_op %>%
+        full_join(gold_sample_op_this_thres)
+      }
+   }
+
+   # compile vid-level summaries 
+   if (vid_index == 1){
+     all_gold_sample_frames_op <- gold_sample_op
+   }
+   else if (vid_index > 1) {
+   all_gold_sample_frames_op <- all_gold_sample_frames_op %>%
+     full_join(gold_sample_op)
+   }
+}
+}
+}
+}
+
+## Add in age data
+all_gold_sample_frames_op <-all_gold_sample_frames_op %>%
+  mutate(date_filmed = lubridate::ymd(str_split_fixed(vid_name,"_",4)[[2]])) %>%
+  left_join(age_info) %>%
+  rowwise() %>%
+  mutate(age_days = as.numeric(difftime(date_filmed,bday)))
+
+save(all_gold_sample_frames_op, file = here::here('data/preprocessed_data_2021/',paste0('gold_sample_from_bbs_2021_',dataset_type,'all_thresholds.RData')))
+
+```

### 2021-12-21 paper/preprint/appendix.Rmd

@@
 Dashed lines show estimated trend lines from proportion of faces/hands in view when analyzing the gold set of frames made by human annotators.
-Dotted lines show trend lines from the goldset when frames when children's own hand were detected." }
+Dotted lines show trend lines from the goldset when frames containing children's own hands were excluded." }
 
@@
 
-```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field; each dot represents the average position from one video within a given age range."}
+```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 6-31 month-old.
+Each dot represents the average position from one video within a given age range."}
 
@@
 ```
+
+# ROC Curve
+
+Not done!
+
+```{r}
+#load(here("data/preprocessed_data/saycam_metadata.RData"))
+load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detectionsall_thresholds.RData"))
+# where's ground truth? these columns just refer to detections, not gold sample human ratings..
+
+#roc <- all_gold_sample_frames_op %>% group_by(detection_threshold) %>%
+#  summarise(hand_pos = sum(hand_detected) / n(),
+#            face_pos = sum(face_detected) / n()) 
+# hmm shouldn't we have varying numbers of detection at different thresholds?
+
+# can extract human ratings from hand_eval_ketan / face_eval_ketan:
+load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
+
+# x-axis = False positive rate
+# y-axis = True positive rate
+
+```

### 2021-12-21 preprocessing/step5_preprocess_fullset_from_bb_outputs.Rmd
fix parentheses

@@
         group_by(frame, vid_name, child_id) %>%
-        summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>detection_thres) %>%
+        summarize(hand_detected =sum(mean_confidence[label=='hand']>detection_thres),face_detected = sum(mean_confidence[label=='face']>detection_thres)) %>%
         mutate(detection_threshold = detection_thres)
@@
 
-## Add in age data
-all_gold_sample_frames_op <-all_gold_sample_frames_op %>%
-  mutate(date_filmed = lubridate::ymd(str_split_fixed(vid_name,"_",4)[[2]])) %>%
-  left_join(age_info) %>%
-  rowwise() %>%
-  mutate(age_days = as.numeric(difftime(date_filmed,bday)))
-
-save(all_gold_sample_frames_op, file = here::here('data/preprocessed_data_2021/',paste0('gold_sample_from_bbs_2021_',dataset_type,'all_thresholds.RData')))
+save(all_gold_sample_frames_op, file = here::here('data/preprocessed_data_2021/',paste0('gold_sample_from_bbs_2021_',dataset_type,'_all_thresholds.RData')))
 

### 2021-12-21 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
minor edits

@@
 A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated 3150 frames; agreement with the primary coder was >95%.
-Upon manually inspecting these frames, we noticed that `r  num_frames_excluded` were sampled from videos taken from the allocentric perspective (i.e., not from the infant viewpoint); these frames and videos containing these frames were subsequently excluded from all other analyses.
+Upon manually inspecting these 24K frames, we noticed that `r  num_frames_excluded` were sampled from videos taken from the allocentric perspective (i.e., not from the infant viewpoint); these frames and videos containing these frames were subsequently excluded from all other analyses.
 

### 2021-12-21 paper/preprint/appendix.Rmd
add roc curve starts

@@
 
-Not done!
+```{r}
+load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections_all_thresholds.RData"))
+
+load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
+
+evaluate_detector <- function(truth, detection) {
+  if (truth == TRUE) {
+    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
+    else return("FN") # was face/wrist, missed face/wrist
+  }
+  else {
+    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
+    else return("FP") # was not face/wrist, detected face/wrist
+  }
+}
+
+ return_tpr = function(eval){
+  tp=sum(eval == "TP")
+  fp=sum(eval == "FP")
+  fn=sum(eval == "FN")
+  tn=sum(eval == "TN")
+  tpr = tp / (tp + fn)
+  return(tpr)
+ }
+
+return_fpr = function(eval){
+  tp=sum(eval == "TP")
+  fp=sum(eval == "FP")
+  fn=sum(eval == "FN")
+  tn=sum(eval == "TN")
+  fpr = fp / (fp + tn)
+  return(fpr)
+ }
+
+```
 
 ```{r}
-#load(here("data/preprocessed_data/saycam_metadata.RData"))
-load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detectionsall_thresholds.RData"))
-# where's ground truth? these columns just refer to detections, not gold sample human ratings..
+roc_data <- gold_sample %>%
+  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
+  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
+  right_join(all_gold_sample_frames_op) %>%
+   mutate(hand_detected = hand_detected>0, face_detected = face_detected > 0) %>%
+  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) %>%
+  group_by(detection_threshold) %>%
+  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan))
+```
 
-#roc <- all_gold_sample_frames_op %>% group_by(detection_threshold) %>%
-#  summarise(hand_pos = sum(hand_detected) / n(),
-#            face_pos = sum(face_detected) / n()) 
-# hmm shouldn't we have varying numbers of detection at different thresholds?
+```{r}
+ggplot(data=roc_data, aes(x=fpr_faces, y=tpr_faces, color=detection_threshold)) +
+  geom_point() +
+  geom_line() +
+  ylim(0,1) +
+  xlim(0,1) +
+  geom_abline(color = 'grey') +
+  xlab('False Positive Rate') +
+  ylab('True Positive Rate')
 
-# can extract human ratings from hand_eval_ketan / face_eval_ketan:
-load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
+ggplot(data=roc_data, aes(x=fpr_hands, y=tpr_hands, color=detection_threshold)) +
+  geom_point() +
+  geom_line() +
+  ylim(0,1) +
+  xlim(0,1) +
+  geom_abline(color = 'grey') +
+  xlab('False Positive Rate') +
+  ylab('True Positive Rate')
+
+```
 

### 2021-12-22 paper/preprint/appendix.Rmd
add code for roc curves, prf x age and location to appendix

@@
 library(ggthemes)
+library(egg)
 ```
@@
 
-# ROC Curve
+# Detection threshold estimations
 
@@
 load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
+```
 
+```{r}
 evaluate_detector <- function(truth, detection) {
@@
   right_join(all_gold_sample_frames_op) %>%
-   mutate(hand_detected = hand_detected>0, face_detected = face_detected > 0) %>%
+   mutate(hand_detected = hand_detected>0, face_detected = face_detected > 0) %>% # number = number of faces/hands detected
   mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) %>%
@@
 ```
+# OpenPose Error Analyses
+```{r}
+# join human and OP detections
+gold_sample <- gold_sample %>%
+  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
+  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
+  right_join(all_gold_sample_frames_op) %>%
+  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) 
+```
 
-# x-axis = False positive rate
-# y-axis = True positive rate
+```{r}
+# add age day bins to gold_sample
+load(file=here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
+bin_size = 7 # days
+min_age = min(all_vid_data$age_days, na.rm=TRUE) # 182
+max_age = max(all_vid_data$age_days, na.rm=TRUE) # 966
+bin_starts = seq(min_age-1, max_age+1,bin_size)
+bins = c(bin_starts, max_age)
+
+gold_sample <- gold_sample %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) 
+```
+
+```{r}
+ return_prf = function(eval){
+  tp=sum(eval == "TP")
+  fp=sum(eval == "FP")
+  fn=sum(eval == "FN")
+  p = tp / (tp + fp)
+  r = tp / (tp + fn)
+  f=( 2 * p * r )/ (p + r)
+  num_detect = length(eval)
+  out <- data.frame(p,r,f,num_detect)
+  return(out)
+ }
 
 ```
+
+```{r}
+prf_by_age_faces <-  gold_sample %>%
+  group_by(child_id, age_day_bin) %>%
+  do(return_prf(.$face_eval_ketan)) %>%
+  filter(num_detect > 50)
+
+prf_by_age_hands <-  gold_sample %>%
+  group_by(child_id, age_day_bin) %>%
+  do(return_prf(.$hand_eval_ketan)) %>%
+  filter(num_detect > 50)
+```
+
+```{r}
+
+prf_by_age_faces$age_day_bin = as.numeric(prf_by_age_faces$age_day_bin)
+
+prf_by_age_hands$age_day_bin = as.numeric(prf_by_age_hands$age_day_bin)
+
+ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth(span=20, alpha=.1)  +
+  ylim(0,1) +
+  ylab('F-score - Face detection') +
+  xlab('Age (months)') +
+  theme(legend.position= 'none')
+
+ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
+  geom_point(alpha=.5) +
+  geom_smooth(span=20, alpha=.1)  +
+  ylim(0,1) +
+  ylab('F-score - Hand detection') +
+  xlab('Age (months)') +
+  theme(legend.position= 'none')
+
+# p2 = ggplot(prf_by_age_faces, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
+#   geom_point(alpha=.5) +
+#   geom_smooth(span=10, alpha=.1)  +
+#   ylim(0,1) +
+#   ylab('Precision - Face detection')+
+#   xlab('Age (months)') +
+#   theme(legend.position= 'none')
+# 
+# p3 =ggplot(prf_by_age_faces, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
+#   geom_point(alpha=.5) +
+#   geom_smooth(span=10, alpha=.1)  +
+#   ylim(0,1) +
+#   ylab('Recall - Face detection')+
+#   xlab('Age (months)') +
+#   theme(legend.position= 'none')
+# #
+# ggarrange(p1,p2,p3)
+
+```
+
+```{r}
+
+```
+
+```{r}
+load(here::here('data/preprocessed_data_2021/saycam_metadata.RData')) # meta
+
+num_videos_annotated = sum(!is.na(meta$Location))
+videos_included = sum(!is.na(meta$Location) & meta$count_locations==1)
+```
+
+```{r}
+gold_sample_by_location <- gold_sample %>%
+  left_join(meta) %>%
+  filter(!is.na(Location)) %>%
+  filter(count_locations==1)
+
+```
+
+```{r}
+prf_by_location_faces <-  gold_sample_by_location %>%
+  group_by(Location) %>%
+  do(return_prf(.$face_eval_ketan)) %>%
+  filter(num_detect > 50)
+
+prf_by_location_hands <-  gold_sample_by_location %>%
+  group_by(Location) %>%
+  do(return_prf(.$hand_eval_ketan)) %>%
+  filter(num_detect > 50)
+```
+
+```{r}
+
+ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=num_detect)) +
+  geom_point(alpha=.5) +
+  ylab('F-score - Face detection') +
+  theme(legend.position = 'none') +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+  ylim(0,1)
+```
+
+```{r}
+ggplot(prf_by_location_hands, aes(x=Location, y=f, col=Location, size=num_detect)) +
+  geom_point(alpha=.5) +
+  ylab('F-score - Hand detection') +
+  theme(legend.position = 'none') +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+  ylim(0,1)
+```

### 2021-12-22 paper/preprint/appendix.Rmd
activity by location

@@
 # function to return prfs
- return_prf_short = function(eval){
+ return_prf_short <- function(eval){
   tp=sum(eval == "TP")
@@
  }
-
-#
 
@@
 ```
+
 # OpenPose Error Analyses
+
 ```{r}
@@
 
-```{r}
+```{r, fig.width=6.5, fig.height=3.2}
 
@@
 
-ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
+p1 <- ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
   geom_point(alpha=.5) +
@@
   ylim(0,1) +
-  ylab('F-score - Face detection') +
-  xlab('Age (months)') +
+  ylab('F-score') + xlab('Age (months)') +
+  ggtitle("Face detections") + 
   theme(legend.position= 'none')
 
-ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
+p2 <- ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
   geom_point(alpha=.5) +
@@
   ylim(0,1) +
-  ylab('F-score - Hand detection') +
-  xlab('Age (months)') +
+  ylab('F-score') + xlab('Age (months)') +
+  ggtitle("Hand detections") + 
   theme(legend.position= 'none')
+
+ggarrange(p1, p2, nrow=1)
 
@@
 ```{r}
-
-```
-
-```{r}
 load(here::here('data/preprocessed_data_2021/saycam_metadata.RData')) # meta
@@
   filter(count_locations==1) 
-
 ```
@@
 
-```{r}
+```{r, fig.width=6.5, fig.height=3.0, fig.cap="F-score of OpenPose hand and face detections in the gold sample by location.
+Size indicates number of detections per location: minimum = 55 (car); maximum = 1753 (living room)."}
+p1 <- ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=num_detect)) +
+  geom_point(alpha=.5) +
+  ylab('F-score') + ggtitle("Face detections") +
+  theme(legend.position = 'none') +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  ylim(0,1)
 
-ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=num_detect)) +
+p2 <- ggplot(prf_by_location_hands, aes(x=Location, y=f, col=Location, size=num_detect)) +
   geom_point(alpha=.5) +
-  ylab('F-score - Face detection') +
+  ylab('F-score') + ggtitle("Hand detections") +
   theme(legend.position = 'none') +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
   ylim(0,1)
+
+ggarrange(p1, p2, nrow=1)
 ```
 
+# Activity by Location
+
 ```{r}
-ggplot(prf_by_location_hands, aes(x=Location, y=f, col=Location, size=num_detect)) +
-  geom_point(alpha=.5) +
-  ylab('F-score - Hand detection') +
-  theme(legend.position = 'none') +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-  ylim(0,1)
+meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))
+
+meta_wide <- meta2 %>% filter(Activity!="N/A", !is.na(Location)) %>%
+  select(Child, `File Name`, Activity, Location) %>%
+  separate(Activity, c("Act.1","Act.2","Act.3","Act.4","Act.5","Act.6","Act.7","Act.8","Act.9","Act.10","Act.11","Act.12"), sep=',') %>%
+  separate(Location, c("Loc.1","Loc.2","Loc.3","Loc.4","Loc.5","Loc.6"), sep=',')
+
+meta_long <- meta_wide %>% pivot_longer(cols = starts_with("Act."), 
+                                        names_to = "activity_index",
+                                        names_prefix = "Act.",
+                                        values_to = "Activity",
+                                        values_drop_na = T) %>%
+  pivot_longer(cols = starts_with("Loc."),
+               names_to = "location_index",
+               names_prefix = "Loc.",
+               values_to = "Location",
+               values_drop_na = T)
+
+# what is "California Room" ?
+meta_long <- meta_long %>% mutate(Location = ifelse(Location=="Bedroom Alice/Sam", "Bedroom", Location))
+
+meta_long %>% filter(Activity!="N/A") %>%
+  group_by(Activity, Location) %>%
+  summarise(n = n()) %>% 
+  ggplot(aes(x=Location, y=Activity, fill=n)) +
+  geom_tile() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+#ggsave("activity_by_location.pdf", width=6, height=10)
 ```

### 2021-12-22 paper/preprint/appendix.Rmd
activity x location using only single-location videos

@@
   select(Child, `File Name`, Activity, Location) %>%
-  separate(Activity, c("Act.1","Act.2","Act.3","Act.4","Act.5","Act.6","Act.7","Act.8","Act.9","Act.10","Act.11","Act.12"), sep=',') %>%
+  separate(Activity, c("Act.1","Act.2","Act.3","Act.4","Act.5","Act.6","Act.7","Act.8","Act.9","Act.10","Act.11","Act.12"), sep=',')
+
+# include videos with multiple locations
+meta_long <- meta_wide %>% 
   separate(Location, c("Loc.1","Loc.2","Loc.3","Loc.4","Loc.5","Loc.6"), sep=',')
-
-meta_long <- meta_wide %>% pivot_longer(cols = starts_with("Act."), 
+  pivot_longer(cols = starts_with("Act."), 
                                         names_to = "activity_index",
@@
 
+single_locations = c("Bedroom","Car","Deck/Porch","Kitchen","Living Room","Off Property","Office","Outside on Property")
+
+# single-location videos
+meta_long_1loc <- meta_wide %>%
+  filter(is.element(Location, single_locations)) %>%
+  pivot_longer(cols = starts_with("Act."), 
+               names_to = "activity_index",
+               names_prefix = "Act.",
+               values_to = "Activity",
+               values_drop_na = T)
+
 # what is "California Room" ?
@@
 
-meta_long %>% filter(Activity!="N/A") %>%
+# use meta_long for multi-location videos
+meta_long_1loc %>% filter(Activity!="N/A") %>%
   group_by(Activity, Location) %>%
@@
 #ggsave("activity_by_location.pdf", width=6, height=10)
+
+# Talking Walk -> Taking Walk ?
+# Taking Walk -> Walking?
 ```

### 2021-12-22 paper/preprint/appendix.Rmd
cleaned up activities, plotting both single-location and multi-location videos, and pr(activity|location)

--- 2021-12-22 paper/preprint/appendix.Rmd
@@
 
-```{r}
+```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos.}
 meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))
@@
   separate(Activity, c("Act.1","Act.2","Act.3","Act.4","Act.5","Act.6","Act.7","Act.8","Act.9","Act.10","Act.11","Act.12"), sep=',') %>%
-  separate(Location, c("Loc.1","Loc.2","Loc.3","Loc.4","Loc.5","Loc.6"), sep=',')
-
-meta_long <- meta_wide %>% pivot_longer(cols = starts_with("Act."), 
+  pivot_longer(cols = starts_with("Act."), 
                                         names_to = "activity_index",
@@
                                         values_drop_na = T) %>%
+  mutate(Activity = case_when(Activity=="Waving" ~ "Gesturing",
+                              Activity=="Imitation" ~ "Imitating",
+                              Activity=="Talking Walk" ~ "Walking",
+                              Activity=="Tidying" ~ "Cleaning",
+                              Activity=="Preparing for Outing" ~ "Getting Changed/Dressed",
+                              Activity=="Play Pretend" ~ "Playing",
+                              TRUE ~ Activity))
+
+# include videos with multiple locations
+meta_long <- meta_wide %>% 
+  separate(Location, c("Loc.1","Loc.2","Loc.3","Loc.4","Loc.5","Loc.6"), sep=',') %>%
   pivot_longer(cols = starts_with("Loc."),
@@
 
+single_locations = c("Bedroom","Car","Deck/Porch","Kitchen","Living Room","Off Property","Office","Outside on Property")
+
+# single-location videos
+meta_long_1loc <- meta_wide %>%
+  filter(is.element(Location, single_locations)) %>%
+  filter(Activity!="N/A", Activity!="Consequence", Activity!="Gesturing")
+
 # what is "California Room" ?
@@
 
-meta_long %>% filter(Activity!="N/A") %>%
+loc_freq = sort(table(meta_long_1loc$Location))
+
+# multi-location videos
+meta_long %>% filter(Activity!="N/A", Activity!="Consequence", Activity!="Kicking",
+                     Activity!="Gesturing", Activity!="Look and Listen", 
+                     Location!="N/A", Location!="California Room",
+                     Location!="Rapidly Moving Between Locations", Location!="Piano Room") %>%
+  mutate(Location = ifelse(Location=="Dog Park/Park/Field", "Off Property", Location)) %>%
   group_by(Activity, Location) %>%
   summarise(n = n()) %>% 
-  ggplot(aes(x=Location, y=Activity, fill=n)) +
+  ggplot(aes(x=Activity, y=Location, fill=n)) +
   geom_tile() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
-#ggsave("activity_by_location.pdf", width=6, height=10)
 ```
+
+```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location in videos taking place in only a single location.}
+# single location videos
+meta_long_1loc %>% 
+  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
+  group_by(Activity, Location) %>%
+  summarise(n = n()) %>% 
+  ggplot(aes(x=Activity, y=Location, fill=n)) +
+  geom_tile() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+#ggsave("activity_by_location.pdf", width=6.5, height=3.5)
+```
+
+```{r, fig.width=6.5, fig.height=3.0, fig.cap="Probability of different activities, given location (in single-location videos).}
+# normalize by location
+meta_long_1loc %>% 
+  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
+  left_join(meta_long_1loc %>% group_by(Location) %>% summarise(loc_freq = n())) %>%
+  group_by(Activity, Location) %>%
+  summarise(n = n(),
+            prop_loc = n / loc_freq) %>% 
+  ggplot(aes(x=Activity, y=Location, fill=prop_loc)) +
+  geom_tile() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```

### 2021-12-23 paper/preprint/appendix.Rmd
add appendix code for rendering examples / new figure

@@
   group_by(child_id, age_day_bin) %>%
-  do(return_prf(.$face_eval_ketan)) %>%
-  filter(num_detect > 50)
+  do(return_prf(.$face_eval_ketan))
 
@@
   group_by(child_id, age_day_bin) %>%
-  do(return_prf(.$hand_eval_ketan)) %>%
-  filter(num_detect > 50)
+  do(return_prf(.$hand_eval_ketan)) 
 ```
 
-```{r, fig.width=6.5, fig.height=3.2}
+```{r, fig.width=6.5, fig.height=3.2, fig.cap="F-score of OpenPose hand and face detections in the gold sample by child and age. Size indicates number of detections age bin/child."}
 
@@
   theme(legend.position= 'none')
+```
 
+```{r}
 ggarrange(p1, p2, nrow=1)
+```
 
+```{r}
 # p2 = ggplot(prf_by_age_faces, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
@@
 
+# OpenPose Annotation Examples
+```{r include=FALSE}
+load(file = here::here('data/preprocessed_data_2021/goldset_category_annotations.RData'))
+
+fp_face_examples <- d %>%
+  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+  filter(face_eval_ketan == 'FP')
+
+fp_hand_examples <- d %>%
+  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+  filter(hand_eval_ketan == 'FP')
+
+fn_face_examples <- d %>%
+  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+  filter(face_eval_ketan == 'FN')
+
+fn_hand_examples <- d %>%
+  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+  filter(face_eval_ketan == 'FN')
+
+images_to_render =  fp_hand_examples
+which_images = 'fp_hand_examples'
+
+public_urls = unique(images_to_render$public_url)
+img_names_short = unique(images_to_render$img_name)
+
+dir.create(here::here("data/annotation_examples/", which_images),recursive = TRUE)
+
+  for (i in 1:length(public_urls)){
+    this_image = image_read(public_urls[i])
+    image_write(this_image,here::here("data/annotation_examples/",which_images, img_names_short[i]))
+  }
+
+```
+
+```{r}
+det_types = c('FP','FN')
+
+render_examples = FALSE
+if (render_examples == TRUE) {
+for (det_type in det_types) {
+  to_render_hands <- d %>%
+    distinct(vid_name, frame, public_url) %>%
+    left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+    filter(hand_eval_ketan == det_type) %>%
+    ungroup() %>%
+    dplyr::sample_n(7)
+
+  image_read(to_render_hands$public_url) %>%
+    image_append(stack = FALSE) %>%
+    image_write(paste0(here::here("data/annotation_examples/"), 'example_hands_', det_type,".png"))
+
+  ###
+    to_render_faces <- d %>%
+    distinct(vid_name, frame, public_url) %>%
+    left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+    filter(face_eval_ketan == det_type) %>%
+    ungroup() %>%
+    dplyr::sample_n(7)
+
+  image_read(to_render_faces$public_url) %>%
+    image_append(stack = FALSE) %>%
+    image_write(paste0(here::here("data/annotation_examples/"), 'example_faces_', det_type,".png"))
+
+}
+}
+
+```
+
+```{r error_examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=6, set.cap.width=T, num.cols.cap=2,  fig.fullwidth = TRUE, fig.align = "center", fig.cap = "Example false alarms/misses for faces/hands randomly sampled from the larger set of manual annotations."}
+error_examples <- png::readPNG("figs/OP_errors.png")
+grid::grid.raster(error_examples)
+```
+
 # Activity by Location
 
-```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos.}
+```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos."}
 meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))
@@
 
-```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location in videos taking place in only a single location.}
+```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location in videos taking place in only a single location."}
 # single location videos
@@
 
-```{r, fig.width=6.5, fig.height=3.0, fig.cap="Probability of different activities, given location (in single-location videos).}
+```{r, fig.width=6.5, fig.height=3.0, fig.cap="Probability of different activities, given location (in single-location videos)."}
 # normalize by location

### 2021-12-23 preprocessing/step5_preprocess_fullset_from_bb_outputs.Rmd
add modifications to goldset outputs to includde center detectinos

@@
 
+   gold_sample_op_center <- this_vid_data %>%
+     filter(frame %in% frames_to_get$frame) %>%
+     mutate(center_y = top + height/2, center_x = left + width/2) %>% # get center_x and y
+     filter(center_y<(limit_upper) & center_x<(limit_upper) & center_y>(limit_lower) & center_x>(limit_lower)) %>%   # filter within parameters
+     group_by(frame, child_id, vid_name) %>% # group at frame level first
+     summarize(hand_detected_center = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected_center = sum(!is.na(mean_confidence[label=='face']))>0)
+
+   gold_sample_op<- gold_sample_op %>%
+      right_join(gold_sample_op_center)[1:]
+
    # compile vid-level summaries 
@@
 
-save(all_gold_sample_frames_op, file = here::here('data/preprocessed_data_2021/',paste0('gold_sample_from_bbs_2021_',dataset_type,'.RData')))
+save(all_gold_sample_frames_op, file = here::here('data/preprocessed_data_2021/',paste0('gold_sample_from_bbs_2021_with_center',dataset_type,'.RData')))
 ```

### 2022-01-04 paper/preprint/appendix.Rmd
adding motor milestone regressions

--- 2021-12-22 paper/preprint/appendix.Rmd
@@
 ```
+
+# Discontinuity Analysis
+
+We next examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the amount of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
+[table with each child's age of onset per milestone?]
+
+```{r, get-milestones, echo=F}
+motor <- read_csv(here::here("data","raw_data", "saycam_walking_asq.csv"))
+# A and S are sitting at 6mos
+face_hand_by_age_milestones <- face_hand_by_age %>%
+  mutate(sit = ifelse(child_id=="S" | child_id=="A", 1, 
+                      ifelse(child_id=="Y" & age_day_bin > 8, 1, 0))) %>%
+  mutate(cruise = ifelse((child_id=="S" & age_day_bin >= 9) | 
+                      (child_id=="A" & age_day_bin >= 10) | 
+                      (child_id=="Y" & age_day_bin > 9), 1, 0)) %>%
+  mutate(walk = ifelse((child_id=="S" & age_day_bin > 10) |
+                       (child_id=="A" & age_day_bin > 13) |
+                       (child_id=="Y" & age_day_bin > 16), 1, 0)) %>%
+  mutate(age = age_day_bin)
+
+library(lmerTest)
+library(sjPlot)
+library(sjmisc)
+# https://rpsychologist.com/r-guide-longitudinal-lme-lmer
+# with random slopes and intercepts ((age_day_bin | child_id): is singular / not converging
+# so we drop random slopes
+```
+
+## Sitting
+
+Children's age at which they began sitting did not significantly predict changes in either the amount of faces or hands that they saw.
+
+```{r}
+face_sit <- lmer(prop_faces ~ age * sit + (1 | child_id), 
+     data=face_hand_by_age_milestones) 
+#summary(face_sit) # ns
+tab_model(face_sit, show.re.var=F, dv.labels = "Proportion of Faces")
+```
+
+```{r}
+hand_sit <- lmer(prop_hands ~ age * sit + (1 | child_id), 
+     data=face_hand_by_age_milestones) 
+#summary(hand_sit) # ns
+tab_model(hand_sit, show.re.var=F, dv.labels = "Proportion of Hands")
+```
+
+## Cruising
+
+As children became able to cruise, they saw significantly more faces ($\beta = 0.27$) and hands ($\beta = 0.26$. 
+For faces, there was a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$).
+
+```{r}
+face_cruise <- lmer(prop_faces ~ age * cruise + (1 | child_id), 
+     data=face_hand_by_age_milestones)
+summary(face_cruise) 
+# age+., cruise+*, age*cruise-*
+tab_model(face_cruise, show.re.var=F, dv.labels = "Proportion of Faces")
+```
+
+```{r, include=F}
+# need to also include main effect terms ("age" and "cruise")?
+face_cruise_eff <- effects::effect(term="age:cruise", mod=face_cruise)
+fc_dat <- data.frame(face_cruise_eff) %>% filter(cruise==0 | cruise==1)
+fc_dat %>% ggplot(aes(x=age, y=fit, group=cruise, color=cruise)) +
+  geom_line() +
+  geom_ribbon(aes(x=age, ymin=lower, ymax=upper, fill=cruise), alpha= 0.3) +
+  geom_point(data=face_hand_by_age_milestones, aes(x=age, y=prop_faces))
+```
+
+```{r}
+hand_cruise <- lmer(prop_hands ~ age * cruise + (1 | child_id), 
+     data=face_hand_by_age_milestones)
+summary(hand_cruise) 
+# cruise+*, age*cruise-.
+tab_model(hand_cruise, show.re.var=F, dv.labels = "Proportion of Hands")
+```
+
+## Walking
+
+Walking - only a marginal positive effect on the proportion of hands ($\beta = 0.09$, $p=0.052$).
+
+```{r}
+face_walk <- lmer(prop_faces ~ age * walk + (1 | child_id), 
+     data=face_hand_by_age_milestones)
+#summary(face_walk) # ns
+tab_model(face_walk, show.re.var=F, dv.labels = "Proportion of Faces")
+```
+
+```{r}
+hand_walk <- lmer(prop_hands ~ age * walk + (1 | child_id), 
+     data=face_hand_by_age_milestones)
+#summary(hand_walk) # walk+.
+tab_model(hand_walk, show.re.var=F, dv.labels = "Proportion of Hands")
+```

### 2022-01-04 paper/preprint/appendix.Rmd
minor edits to appendix
(but missing the thresholded detections data file!)

@@
 ```{r}
+# file not found - name changed?
 load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections_all_thresholds.RData"))
@@
 
-```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos.}
+```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos."}
 meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))
@@
 # cruise+*, age*cruise-.
-tab_model(hand_cruise, show.re.var=F, dv.labels = "Proportion of Hands")
+tab_model(hand_cruise, show.re.var=F, dv.labels = "Proportion of Hands") # show.obs=F
 ```
@@
 
-Walking - only a marginal positive effect on the proportion of hands ($\beta = 0.09$, $p=0.052$).
+As children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$).
 

### 2022-01-04 paper/preprint/appendix.Rmd
add commented code for prf on center detections

--- 2021-12-23 paper/preprint/appendix.Rmd
@@
 load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
-load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_all_detections.RData'))
+load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_with_centerall_detections.RData'))
 
@@
   mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))
+
+    # mutate(face_eval_ketan_center = evaluate_detector(face_present_ketan, face_detected_center), hand_eval_ketan_center = evaluate_detector(hand_present_ketan, hand_detected_center)) 
 ```
@@
 
+# function to return prfs
+ return_prf_short = function(eval){
+  tp=sum(eval == "TP")
+  fp=sum(eval == "FP")
+  fn=sum(eval == "FN")
+  p = tp / (tp + fp)
+  r = tp / (tp + fn)
+  f=( 2 * p * r )/ (p + r)
+  return(c(p,r,f))
+ }
+
 ```
@@
   do(return_prf(.$hand_eval_ketan)) 
+```
+
+```{r}
+# Evaluating prfs in center detections is challenging because we ONLY have ground truth on the full image -- so it's not that informative.
+
+# return_prf_short(gold_sample$hand_eval_ketan_center)
+# return_prf_short(gold_sample$face_eval_ketan_center)
 ```

### 2022-01-04 paper/preprint/appendix.Rmd

@@
 ```
+
+# Discontinuity Analysis
+
+We next examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the amount of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
+[table with each child's age of onset per milestone?]
+
+```{r, get-milestones, echo=F}
+motor <- read_csv(here::here("data","raw_data", "saycam_walking_asq.csv"))
+# A and S are sitting at 6mos
+face_hand_by_age_milestones <- face_hand_by_age %>%
+  mutate(sit = ifelse(child_id=="S" | child_id=="A", 1, 
+                      ifelse(child_id=="Y" & age_day_bin > 8, 1, 0))) %>%
+  mutate(cruise = ifelse((child_id=="S" & age_day_bin >= 9) | 
+                      (child_id=="A" & age_day_bin >= 10) | 
+                      (child_id=="Y" & age_day_bin > 9), 1, 0)) %>%
+  mutate(walk = ifelse((child_id=="S" & age_day_bin > 10) |
+                       (child_id=="A" & age_day_bin > 13) |
+                       (child_id=="Y" & age_day_bin > 16), 1, 0)) %>%
+  mutate(age = age_day_bin)
+
+library(lmerTest)
+library(sjPlot)
+library(sjmisc)
+# https://rpsychologist.com/r-guide-longitudinal-lme-lmer
+# with random slopes and intercepts ((age_day_bin | child_id): is singular / not converging
+# so we drop random slopes
+```
+
+## Sitting
+
+Children's age at which they began sitting did not significantly predict changes in either the amount of faces or hands that they saw.
+
+```{r}
+face_sit <- lmer(prop_faces ~ age * sit + (1 | child_id), 
+     data=face_hand_by_age_milestones) 
+#summary(face_sit) # ns
+tab_model(face_sit, show.re.var=F, dv.labels = "Proportion of Faces")
+```
+
+```{r}
+hand_sit <- lmer(prop_hands ~ age * sit + (1 | child_id), 
+     data=face_hand_by_age_milestones) 
+#summary(hand_sit) # ns
+tab_model(hand_sit, show.re.var=F, dv.labels = "Proportion of Hands")
+```
+
+## Cruising
+
+As children became able to cruise, they saw significantly more faces ($\beta = 0.27$) and hands ($\beta = 0.26$. 
+For faces, there was a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$).
+
+```{r}
+face_cruise <- lmer(prop_faces ~ age * cruise + (1 | child_id), 
+     data=face_hand_by_age_milestones)
+summary(face_cruise) 
+# age+., cruise+*, age*cruise-*
+tab_model(face_cruise, show.re.var=F, dv.labels = "Proportion of Faces")
+```
+
+```{r, include=F}
+# need to also include main effect terms ("age" and "cruise")?
+face_cruise_eff <- effects::effect(term="age:cruise", mod=face_cruise)
+fc_dat <- data.frame(face_cruise_eff) %>% filter(cruise==0 | cruise==1)
+fc_dat %>% ggplot(aes(x=age, y=fit, group=cruise, color=cruise)) +
+  geom_line() +
+  geom_ribbon(aes(x=age, ymin=lower, ymax=upper, fill=cruise), alpha= 0.3) +
+  geom_point(data=face_hand_by_age_milestones, aes(x=age, y=prop_faces))
+```
+
+```{r}
+hand_cruise <- lmer(prop_hands ~ age * cruise + (1 | child_id), 
+     data=face_hand_by_age_milestones)
+summary(hand_cruise) 
+# cruise+*, age*cruise-.
+tab_model(hand_cruise, show.re.var=F, dv.labels = "Proportion of Hands") # show.obs=F
+```
+
+## Walking
+
+As children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$).
+
+```{r}
+face_walk <- lmer(prop_faces ~ age * walk + (1 | child_id), 
+     data=face_hand_by_age_milestones)
+#summary(face_walk) # ns
+tab_model(face_walk, show.re.var=F, dv.labels = "Proportion of Faces")
+```
+
+```{r}
+hand_walk <- lmer(prop_hands ~ age * walk + (1 | child_id), 
+     data=face_hand_by_age_milestones)
+#summary(hand_walk) # walk+.
+tab_model(hand_walk, show.re.var=F, dv.labels = "Proportion of Hands")
+```

### 2022-01-04 analysis/analysis_bb_fulldataset.Rmd
backup script

@@
 ```{r}
-load(file = '../data/all_bounding_boxes_three_kids_preprocessed.RData')
+load(file = '../data/old_data/SA_bounding_boxes_cleaned.RData')
 

### 2022-01-04 openpose_detections/daylight_demo.py
update demo script

@@ -3,7 +3,7 @@ import os
 import ujson
 import multiprocessing as mp
 import time
-# import cv2
+import cv2
 import numpy as np
 # import matplotlib.pyplot as plt
 # from matplotlib import collections as mc

### 2022-01-05 paper/preprint/appendix.Rmd
wrangling lmer tables

--- 2022-01-04 paper/preprint/appendix.Rmd
@@
 
-```{r}
+```{r, echo=F, message=F}
 library(tidyverse)
@@
 library(egg)
+library(stargazer)
+
+knitr::opts_chunk$set(echo=F, warning=F, cache=F, 
+                      message=F, sanitize = T)
 ```
@@
 ```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 6-31 month-old.
-Each dot represents the average position from one video within a given age range."}
+Each dot represents the average position from one video within a given age range.", warning=F}
 
@@
 library(lmerTest)
-library(sjPlot)
-library(sjmisc)
 # https://rpsychologist.com/r-guide-longitudinal-lme-lmer
@@
 # so we drop random slopes
+
+face_sit <- lmer(prop_faces ~ age * sit + (1 | child_id), 
+     data=face_hand_by_age_milestones) 
+hand_sit <- lmer(prop_hands ~ age * sit + (1 | child_id), 
+     data=face_hand_by_age_milestones)
+
+face_cruise <- lmer(prop_faces ~ age * cruise + (1 | child_id), 
+     data=face_hand_by_age_milestones)
+hand_cruise <- lmer(prop_hands ~ age * cruise + (1 | child_id), 
+     data=face_hand_by_age_milestones)
+
+face_walk <- lmer(prop_faces ~ age * walk + (1 | child_id), 
+     data=face_hand_by_age_milestones)
+hand_walk <- lmer(prop_hands ~ age * walk + (1 | child_id), 
+     data=face_hand_by_age_milestones)
+# make models compatible with stargazer
+class(face_sit) <- "lmerMod"
+class(hand_sit) <- "lmerMod"
+class(face_cruise) <- "lmerMod"
+class(hand_cruise) <- "lmerMod"
+class(face_walk) <- "lmerMod"
+class(hand_walk) <- "lmerMod"
 ```
@@
 
-```{r}
-face_sit <- lmer(prop_faces ~ age * sit + (1 | child_id), 
-     data=face_hand_by_age_milestones) 
+```{r, include=F, results='asis'}
 #summary(face_sit) # ns
-tab_model(face_sit, show.re.var=F, dv.labels = "Proportion of Faces")
+stargazer(face_sit, title="Predicting Faces by Ability to Sit", 
+          header=F, dep.var.labels = "Proportion of Faces")
+
+stargazer(face_sit, hand_sit)
 ```
 
-```{r}
-hand_sit <- lmer(prop_hands ~ age * sit + (1 | child_id), 
-     data=face_hand_by_age_milestones) 
+```{r, include=F, results='asis'}
 #summary(hand_sit) # ns
-tab_model(hand_sit, show.re.var=F, dv.labels = "Proportion of Hands")
+stargazer(hand_sit, title="Predicting Hands by Ability to Sit", 
+          header=F, dep.var.labels = "Proportion of Hands")
+```
+
+```{r, results='asis'}
+stargazer(face_sit, hand_sit, title="Change in Face and Hand Prevalence by Ability to Sit", 
+          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
 ```
@@
 
-```{r}
-face_cruise <- lmer(prop_faces ~ age * cruise + (1 | child_id), 
-     data=face_hand_by_age_milestones)
-summary(face_cruise) 
+```{r, include=F, results='asis'}
+#summary(face_cruise) 
 # age+., cruise+*, age*cruise-*
-tab_model(face_cruise, show.re.var=F, dv.labels = "Proportion of Faces")
+stargazer(face_cruise, title="Predicting Faces by Ability to Cruise", 
+          header=F, dep.var.labels = "Proportion of Faces")
 ```
@@
 
-```{r}
-hand_cruise <- lmer(prop_hands ~ age * cruise + (1 | child_id), 
-     data=face_hand_by_age_milestones)
-summary(hand_cruise) 
+```{r, include=F, results='asis'}
+#summary(hand_cruise) 
 # cruise+*, age*cruise-.
-tab_model(hand_cruise, show.re.var=F, dv.labels = "Proportion of Hands") # show.obs=F
+stargazer(hand_cruise, title="Predicting Hands by Ability to Cruise", 
+          header=F, dep.var.labels = "Proportion of Hands") 
+```
+
+```{r, results='asis'}
+stargazer(face_cruise, hand_cruise, title="Change in Face and Hand Prevalence by Ability to Cruise", 
+          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
 ```
@@
 
-```{r}
-face_walk <- lmer(prop_faces ~ age * walk + (1 | child_id), 
-     data=face_hand_by_age_milestones)
+```{r, include=F, results='asis'}
 #summary(face_walk) # ns
-tab_model(face_walk, show.re.var=F, dv.labels = "Proportion of Faces")
+stargazer(face_walk, title="Predicting Faces by Ability to Walk", 
+          header=F, dep.var.labels = "Proportion of Faces")
 ```
 
-```{r}
-hand_walk <- lmer(prop_hands ~ age * walk + (1 | child_id), 
-     data=face_hand_by_age_milestones)
+```{r, include=F, results='asis'}
 #summary(hand_walk) # walk+.
-tab_model(hand_walk, show.re.var=F, dv.labels = "Proportion of Hands")
+stargazer(hand_walk, title="Predicting Hands by Ability to Walk", 
+          header=F, dep.var.labels = "Proportion of Hands")
 ```
+
+```{r, results='asis'}
+stargazer(face_walk, hand_walk, title="Change in Face and Hand Prevalence by Ability to Walk", 
+          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
+```

### 2022-01-05 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
fix figure 5, add refs

@@
   geom_smooth(method='lm') + 
-  ylab('Log (average area)') +
-  xlab('Age in days') +
+  ylab('Log area (average proportion of frame)') +
+  xlab('Age (in months)') +
   scale_color_brewer(palette="Dark2", name = "Child") +
@@
 ```{r}
-# eye distance dataframe
+# eye distance data frame
 eye_dist <- all_vid_data %>%
@@
 We also used these detailed pose annotations to explore finer-grained changes in how children experience the faces and hands of their caregivers over development.
-We found that the faces, hands, and people in the infant view tended to become smaller and that faces tended to be farther away and in more variable horizontal positions, in keeping with prior work examining the sizes of faces in the infant view during the first year of life [@Jayaraman2015].
+We found that the faces, hands, and people in the infant view tended to become smaller and that faces tended to be farther away and in more variable horizontal positions, in keeping with prior work examining the sizes of faces in the infant view during the first year of life [@Jayaraman2015; @sugden2017hey; @sugden2014spy; @sugden2019these].
 Overall, these data support the idea that the social information in view changes across development as infants become increasingly mobile and independent [@franchak2017see; @fausey2016]. 

### 2022-01-05 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
GD mention of activity x location Appendix, flesh out

@@
 
-We also found an unexpectedly high proportion of hands in infants' view, even when restricting the field-of-view to the center field-of-view to make the viewpoints comparable to those of headcams used in prior work.
+We also found an unexpectedly high proportion of hands in infants' view, even when restricting the analysis to detections in the center field-of-view to make the viewpoints comparable to those of headcams used in prior work.
 Why might this be the case?
@@
 Indeed, using the same pose detector on videos from in-lab play sessions, @long2021automated found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. 
-Work that directly examines the variability in the social information in view across more vs.
-less structured activity contexts could further test this idea.
+Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.
 
-A coarse analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations and between individual children.
+A coarse analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations (see Appendix, Figure S7?) and between individual children.
 Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations. 

### 2022-01-05 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
add discussion, intro paragraphs

--- 2022-01-05 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
@@
 
-Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of more than 1700 headcam videos collected from three children along a span of 6 to 32 months of age—--the SAYCam dataset [@SAYcam].
-In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways.
+Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of more than 1700 headcam videos collected at home from three children along a span of 6 to 32 months of age—--the SAYCam dataset [@SAYcam].
+We thus analyze the video data from this dense, longitudinal dataset as case studies of how the social information in the infant view changes over the course of development.
+These kinds of longitudinal case studies provide an important counterpoint to cross-sectional investigations for several reasons.
+By repeatedly recording data from the same child, they allow us to investigate developmental changes within each child and to relate these to developmental milestones (e.g., the onset of walking).
+Second, they eliminate several nuance sources of variability (e.g., parent/child familiarity with camera, home environment) that may obscure fine-grained developmental patterns.
+
+Finally, longitudinal case studies allow us to investigate the ecological validity of results in everyday, naturalistic learning contexts.
+Indeed, in addition to its size and longitudinal nature, the SAYCam dataset is more naturalistic than those previously used in two key ways.
 First, recordings were taken under a large variety of activity contexts [@roy2015predicting; @bruner1985role] encompassing infants' viewpoints during both activities outside and inside the home.
@@
 Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that most frames are typically not inspected, even in the most comprehensive studies. 
-For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand-annotated (by four coders), totalling 103,383 frames (per coder)—an impressive number of annotations but nonetheless only 0.67% of the collected footage.
+For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand-annotated (by four coders), totalling 103,383 frames (per coder)--an impressive number of annotations but nonetheless only 0.67% of the collected footage.
+
 To address this challenge, we use a modern computer vision model of pose detection to automatically detect the presence of hands and faces from the infant egocentric viewpoint. 
-Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints that operates well on scenes including multiple people, even if they are partially-occluded (see Figure 1).
-In prior work examining egocentric videos taken from the infant perspective, OpenPose performed comparably to other modern face detection models [@long2021automated].
+Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints. 
+In prior work examining egocentric videos taken from the infant perspective during in-lab play sessions, OpenPose performed comparably to other modern face detection models [@long2021automated].
+However, these at-home, naturalistic videos contain more cluttered visual environments, challenging lighting conditions, and many different novel viewpoints.
+This this paper, we first validate the use of OpenPose by comparing face and hand detections to a human-annotated set of 24,000 frames.
+Overall, we find that OpenPose operates relatively on egocentric scenes including multiple people, even if they are partially-occluded (see Figure 1), nd and discuss the benefits and drawbacks of this automated annotation strategy.
 
-In this paper, we first describe the dataset and validate the use of this model by comparing face and hand detections to a human-annotated set of 24,000 frames. 
-Next, we report how the proportion of faces and hands changes with age in each of the three children in the dataset. 
-We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the head cameras as well as a diversity of locations in which videos were recorded.
-Finally, making use of automated annotation of pose bounding boxes, we analyze the size, location, and variability of detected faces and poses across development.
+We next capitalize on this computational advance to annotate the entirety of this large, longitudinal video dataset.
+We use these detections to report how the proportion of faces and hands changes with age and motor development milestones in each of the three children in the dataset.
+Weinvestigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the head cameras as well as a diversity of locations in which videos were recorded.
+Finally, making use of automated annotation of pose bounding boxes, we analyze the size, location, and variability of detected faces and poses across development in these three children.
 
@@
 
+## Variation with motor development
+In a set of exploratory analyses, we examined how the onset of sitting, cruising, and walking in each individual child changed the proportion of faces and hands in view.
+Each parent completed the Ages and Stages Questionnaire (ASQ), and we coded the age at which each child reached each motor milestone.
+To do so, we used a mixed-effects regression with per-child random intercepts
+
+We next examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the amount of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
+[table with each child's age of onset per milestone?]
+
 ## Variability in social information across learning contexts 
@@
 
-# Variation with motor development
-```{r}
-motor = read_csv(file=here::here('data/raw_data/saycam_walking_asq.csv'))
+# General Discussion
+Here, we first validated the use of an automated pose detection model to detect the faces and hands in view in a longitudinal dataset of egocentric, everyday visual experience.
+We then used these detections to analyze the social information seen from each of three children's egocentric perspective from 6 to 32 months of age.
 
-```
-
-# General Discussion
-Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.
 First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016; @Jayaraman2015]. 
@@
 
-We also found an unexpectedly high proportion of hands in infants' view, even when restricting the field-of-view to the center field-of-view to make the viewpoints comparable to those of headcams used in prior work.
+Second, we also found an unexpectedly high proportion of hands in infants' view, even when restricting the field-of-view to the center field-of-view to make the viewpoints comparable to those of headcams used in prior work.
 Why might this be the case?
@@
 
-A coarse analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations and between individual children.
+An analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations and between individual children.
 Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations.
@@
 
-In future work, the adaptation of deep neural networks for the infant egocentric view remains a promising avenue for collaboration between computer vision experts and developmental psychologists. 
+Importantly, however, these automated detections do not entirely obviate the need for careful inspection and manual annotation of dense video data.
+While the present results suggest that OpenPose achieves moderate performance at detecting faces and hands in egocentric videos -- as does @Long2021automated -- these results do not guarantee that OpenPose will generalize with similar accuracy to other video datasets.
+By using manual annotations to estimate the accuracy of these automated techniques for their video datasets, researchers can weigh the pros and cons of automated detections for answering their particular research questions.
+While OpenPose does provide a considerable amount of about all of the people in a given image -- estimating the entire poses for every individual -- it may not always perform similarly in challenging viewpoints.
+
+So, how might OpenPose -- or other pose detection algorithms -- be improved upon and used in future work?
+One promising direction may be to use detailed pose annotations of the people in the infant view to fine-tune later layers of pose detection networks.
+This has the potential to improve upon the overall accuracy of the network to detect the social information in infant egocentric videos and yield more reliable, detailed detections.
+A second potential area for innovation lies in leveraging the dense nature of these large-scale annotations to improve model accuracy: By pooling detections from surrounding frames, we may be able to build classifiers that perform more accurately on a single challenging viewpoint.
+Finally, a third area for improvement consists of building classifiers that can accurately distinguish between children's hands (as seen from the egocentric point of view) versus adults' hands--a notoriously challenging problem in computer vision [@bambach2017lending].
+We expect that these goals may become more and more feasible as we simultaneously improve the head-mounted cameras that are used in both at-home and in-lab studies; increasing the resolution and quality of the images we record will no doubt improve the ability of computer vision algorithms to extract detailed information from them.
+
+More broadly, we believe that the adaptation of deep neural networks for the infant egocentric view remains a promising avenue for collaboration between computer vision experts and developmental psychologists.
 Indeed, this combination has already yielded new insights about the learning mechanisms needed to build visual representations [@tsutsui2020computational; @zhuang2020unsupervised; @orhan2020self]. 

### 2022-01-05 paper/preprint/appendix.Rmd

@@
 
-# Discontinuity Analysis
+# Motor Milestones Analysis
 
-We next examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the amount of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
-[table with each child's age of onset per milestone?]
+We next examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the proportion of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
+We tried including random slopes by age and milestone, but the models did not converge and/or were singular.
+Thus, for each milestone the R syntax was: \texttt{prop_faces ~ age * milestone + (1 | child_id)}.
+
+Children's age of achieving each milestone was dummy-coded (i.e., 0=milestone not reached; 1=milestone reached).
+Participants S and A were already able to sit at 6 months of age, while Y began achieving this milestone at 8 months.
+A was able to cruise at 9 months of age, while S reached that milestone at 10 months, with Y just behind.
+Learning to walk showed the most variation, with S walking after 10 months, A after 13 months, and Y after 16 months of age.
 
@@
 # so we drop random slopes
+
+face_all <- lmer(prop_faces ~ age * (sit + cruise + walk) + (1 | child_id), 
+     data=face_hand_by_age_milestones) 
+#summary(face_all) # cruise+ age:cruise-
+
+hand_all <- lmer(prop_hands ~ age * (sit + cruise + walk) + (1 | child_id), 
+     data=face_hand_by_age_milestones) 
+#summary(hand_all) # cruise+ age:cruise-.
 

### 2022-01-05 paper/preprint/manuscript_dec2021_apa_blinded.Rmd

@@
 
-Second, we also found an unexpectedly high proportion of hands in infants' view, even when restricting the field-of-view to the center field-of-view to make the viewpoints comparable to those of headcams used in prior work.
+Second, we also found an unexpectedly high proportion of hands in infants' view, even when restricting the analysis to detections in the center field-of-view to make the viewpoints comparable to those of headcams used in prior work.
 Why might this be the case?
@@
 Indeed, using the same pose detector on videos from in-lab play sessions, @long2021automated found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. 
-Work that directly examines the variability in the social information in view across more vs.
-less structured activity contexts could further test this idea.
-
-An analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations and between individual children.
+Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.
+
+An analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations (see Appendix, Figure S7?) and between individual children.
 Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations. 

### 2022-01-06 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
add motor development section

@@
 
-As we found that children's hands tended to occur in the lower visual field (see Figure Appendix \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, and face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%.
-This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
-Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}B). 
-We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure \ref{fig:goldSetSanity}).
-
 Finally, we analyzed how these two sources of social information co-occurred.
@@
 
-## Variation with motor development
-In a set of exploratory analyses, we examined how the onset of sitting, cruising, and walking in each individual child changed the proportion of faces and hands in view.
-Each parent completed the Ages and Stages Questionnaire (ASQ), and we coded the age at which each child reached each motor milestone.
-To do so, we used a mixed-effects regression with per-child random intercepts
-
-We next examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the amount of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
-[table with each child's age of onset per milestone?]
+## Variability with motor development milestones
+How does the social information in view change as a function of motor development?
+One idea is that children’s ability to stand and move on their own may fundamentally change the visual social information that they see (e.g., facial expressions, gaze cues, pointing)  [@walle2016infant] relative to infants who are still sitting and crawling.
+Indeed, in in-lab studies, research has found that children's in-the-moment posture -- and that of their caregiver -- is a strong predictor of the visual social information in view [@franchak2017see; @long2021automated].
+
+We thus next analyzed how the social information in view changed as a function of each child reaching particular developmental motor milestones.
+Each parent completed the Ages and Stages Questionnaire (ASQ) [@bricker1999ages], which includes questions about their child's motor abilities, and we used the responses from this questionnaire to code the age (in months) at which each child became able to sit, cruise, and walk on their own (questions about crawling were not included in the questionnaire)..
+We found considerable variability in the age at which each child achieved these three milestones.
+Participants S and A were already able to sit at 6 months of age, while Y began achieving this milestone at 8 months.
+A was able to cruise at 9 months of age, while S reached that milestone at 10 months, with Y just behind.
+Learning to walk showed the most variation, with S walking after 10 months, A after 13 months, and Y after 16 months of age.
+
+We then used a discontinuity analysis to estimate whether the onset of each of these three motor milestones changed the proportion of faces/hands in each chid's view.
+Specifically, we used mixed-effects regressions with per-child random intercepts to estimate whether children's age (in months), each motor milestone, and their interaction significantly influenced the proportion of hands or faces that each child saw; see Appendix for tables with full model specifications and tables with all coefficients.
+Overall, we found that the age at which these children began sitting did not significantly predict changes in either the amount of faces or hands that they saw.
+However, as children became able to cruise, they saw significantly more faces ($\beta = 0.27$) and hands ($\beta = 0.26$), suggesting that the ability to be upright and locomote even somewhat independently was sufficient to significantly change children's visual social environment.
+For faces, however, there was also a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$).
+However, we did not find major differences with the onset of walking; as these children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$).
+Thus, these analyses confirm and extend cross-sectional finding, leveraging dense, within-child data to help elucidate the complex relationship between motor development and the social information in view.
 

### 2022-01-06 paper/preprint/appendix.Rmd
graphs for cruising milestone (not currently included)

@@
 library(stargazer)
+library(ggeffects)
 
@@
 ```{r, include=F}
-# need to also include main effect terms ("age" and "cruise")?
-face_cruise_eff <- effects::effect(term="age:cruise", mod=face_cruise)
-fc_dat <- data.frame(face_cruise_eff) %>% filter(cruise==0 | cruise==1)
-fc_dat %>% ggplot(aes(x=age, y=fit, group=cruise, color=cruise)) +
-  geom_line() +
-  geom_ribbon(aes(x=age, ymin=lower, ymax=upper, fill=cruise), alpha= 0.3) +
-  geom_point(data=face_hand_by_age_milestones, aes(x=age, y=prop_faces))
+f1 <- ggpredict(face_cruise, c("age", "cruise")) %>% plot(add.data=T) +
+  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on faces seen") + 
+  xlab("Age (months)") + ylab("Proportion of faces") + theme_classic()
+
+h1 <- ggpredict(hand_cruise, c("age", "cruise")) %>% plot(add.data=T) +
+  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on hands seen") + 
+  xlab("Age (months)") + ylab("Proportion of hands") + theme_classic()
+
+ggpubr::ggarrange(f1, h1, nrow=1, common.legend=T)
 ```

### 2022-01-06 paper/preprint/appendix.Rmd
fix appendix f-score graphs, trim motor appendix

--- 2022-01-05 paper/preprint/appendix.Rmd
@@
 library(stargazer)
+library(magick)
 
@@
 ```{r}
-# file not found - name changed?
+# with all thresholds
 load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections_all_thresholds.RData"))
@@
 ```{r}
-ggplot(data=roc_data, aes(x=fpr_faces, y=tpr_faces, color=detection_threshold)) +
+face_roc = ggplot(data=roc_data, aes(x=fpr_faces, y=tpr_faces, color=detection_threshold)) +
   geom_point() +
@@
   xlab('False Positive Rate') +
-  ylab('True Positive Rate')
+  ylab('True Positive Rate') +
+  ggtitle('Face detections') +
+  theme(legend.position = 'none')
 
-ggplot(data=roc_data, aes(x=fpr_hands, y=tpr_hands, color=detection_threshold)) +
+hand_roc = ggplot(data=roc_data, aes(x=fpr_hands, y=tpr_hands, color=detection_threshold)) +
   geom_point() +
@@
   xlab('False Positive Rate') +
-  ylab('True Positive Rate')
+  ylab('True Positive Rate') +
+  ggtitle('Hand detections') +
+  theme(legend.position = 'none')
 
@@
 
+```{r}
+ggarrange(face_roc, hand_roc, nrow=1)
+```
+
 # OpenPose Error Analyses
+```{r}
+# remove big data frame with thresholds
+rm(all_gold_sample_frames_op)
 
-```{r}
+# without thresholds
+load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections.RData"))
+
 # join human and OP detections
@@
 
-```{r, fig.width=6.5, fig.height=3.2, fig.cap="F-score of OpenPose hand and face detections in the gold sample by child and age. Size indicates number of detections age bin/child."}
+```{r det_perf_by_age, fig.width=6.5, fig.height=3.2, fig.cap="F-score of OpenPose hand and face detections in the gold sample by child and age. Size indicates number of detections age bin/child."}
 
@@
 
-```{r, fig.width=6.5, fig.height=3.0, fig.cap="F-score of OpenPose hand and face detections in the gold sample by location.
+```{r det_perf_by_locations, fig.width=6.5, fig.height=3.0, fig.cap="F-score of OpenPose hand and face detections in the gold sample by location.
 Size indicates number of detections per location: minimum = 55 (car); maximum = 1753 (living room)."}
@@
 
-# Discontinuity Analysis
+# Motor Milestones Analysis Details
 
-We next examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the amount of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
-[table with each child's age of onset per milestone?]
+We examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the proportion of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
+
+We tried including random slopes by age and milestone, but the models did not converge and/or were singular.
+Thus, for each milestone the R syntax was: \texttt{prop_faces ~ age * milestone + (1 | child_id)}.Children's age of achieving each milestone was dummy-coded (i.e., 0=milestone not reached; 1=milestone reached).
 

### 2022-01-06 paper/preprint/appendix.Rmd

@@
 library(magick)
+library(ggeffects)
 

### 2022-01-06 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
add more OP qualitative results to paper

@@
 In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.
-We also found that restricting our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
 
@@
 
-Finally, we examined whether the precision, recall, and F-score for hands and faces varied with age or child, and did not find substantial variation.
-Thus, while OpenPose was trained on photographs from the adult perspective, this model still generalized relatively well to the egocentric infant viewpoint with no fine-tuning or post-processing of the detections.
-As these detections were imperfect compared to human annotators, fine-tuning these models to better optimize for the infant viewpoint remains an open avenue for future work.
-Standard computer vision models are rarely trained on the egocentric viewpoint, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors.
+Next, we examined the degree to which the detector confidence changed model performance.
+We found that restricting our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
+Overall, our analyses suggested that including all detections was the most beneficial for optimizing precision; see Appendix for a full ROC curve detailing all detector confidence confidence thresholds.
+
+Finally, we examined whether model accuracy for hands and faces varied across age or between child and location  (see plots for age/child in Appendix, Figure \ref{fig:det_perf_by_age}, and location in Figure \ref{fig:det_perf_by_locations}).
+Some of the videos at taken at older ages for child A did seem to show lower hand detection accuracy, perhaps due the presence of child's hands; however, there were also fewer videos at these time points.
+In general, however, we found evidence for considerable variation in model accuracy across different videos, suggesting that particular recording contexts, activities, or lighting could cause conditions that would impair detector performance.
+
+In a qualitative analysis, we also inspected frames where OpenPose failed to detect faces/hands or erroneously detected them to gain insight into the factors driving performance.
+Figure \ref{fig:error_examples} shows examples of both missed detections and false alarms for both faces and hands and highlights the challenging detection conditions presented by these at-home, naturalistic videos.
+Many missed faces included very far away or very close up views of faces at odd angles, as well as faces that were partially occluded by odd lighting conditions.
+False alarms for faces included animal faces depicted in picture books and poses where the person was not facing a camera.
+Hands were often missed when they were seen only from the side and unconnected to a pose, whereas hands were sometimes erroneously detected when a pose was present but the hands were out of view.
+Thus, while OpenPose was trained on photographs from the adult perspective, this model still performed relatively well on these challenging the egocentric infant viewpoint with no fine-tuning or post-processing of the detections, especially given these challenging and varied videos.
 
@@
 
-An analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations (see Appendix, Figure S7?) and between individual children.
+An analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations (see Appendix, Figure S7) and between individual children.
 Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations. 
@@
 One promising direction may be to use detailed pose annotations of the people in the infant view to fine-tune later layers of pose detection networks.
-This has the potential to improve upon the overall accuracy of the network to detect the social information in infant egocentric videos and yield more reliable, detailed detections.
+This has the potential to improve upon the overall accuracy of the network to detect the social information in infant egocentric videos.
+Standard computer vision models are rarely trained on the egocentric viewpoint, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors.
 A second potential area for innovation lies in leveraging the dense nature of these large-scale annotations to improve model accuracy: By pooling detections from surrounding frames, we may be able to build classifiers that perform more accurately on a single challenging viewpoint.

### 2022-01-06 paper/preprint/appendix.Rmd
add reference to activity x location graph and names in appendix, rmd

@@
 
-```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos."}
+```{r activities_by_lo, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos."}
 meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))

### 2022-01-06 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
add reference to activity x location graph and names in appendix, rmd

@@
   ungroup() %>%
-  tidyr::replace_na(list(faces_and_hands=0)) %>%
+  tidyr::replace_na(list(faces_and_hands=0)) %>%c
   group_by(age_day_bin, child_id) %>%
@@
 In our viewing of the SAYCam videos and in other annotations available with the dataset, activities varied somewhat predictably by location: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.
+However, every location was of course associated with multiple activities; see Appendix Figure \ref{fig:activities_by_loc} for a heatmap relating individual activities to locations in the dataset.
 
@@
 
-Second, we also found an unexpectedly high proportion of hands in infants' view, even when restricting the analysis to detections in the center field-of-view to make the viewpoints comparable to those of headcams used in prior work.
+Second, we also found an unexpectedly high proportion of hands in infants' view, even when restricting the analysis to detections in the center field-of-view to make the viewpoints comparable to those of headcams used in prior work and to exclude the portion of the frame most likely to contain children's own hands.
 Why might this be the case?

### 2022-01-06 preprocessing/step5_preprocess_fullset_from_bb_outputs.Rmd
full roi sweep
add code to get all dets for gold sample frames

@@
 
-## Main detections: read in bounding box outputs from each vid, summarize and compile.
 ```{r}
-reload_data=TRUE
-
 # cropping paramts
@@
 x_max = 640
+```
+
+## Main detections: read in bounding box outputs from each vid, summarize and compile.
+```{r}
+reload_data=TRUE
 
@@
 
+   gold_sample_raw_dets <- this_vid_data %>%
+     filter(frame %in% frames_to_get$frame) %>%
+     mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
+     group_by(frame, vid_name, child_id)
+
    gold_sample_op_center <- this_vid_data %>%
@@
    gold_sample_op<- gold_sample_op %>%
-      right_join(gold_sample_op_center)[1:]
+      right_join(gold_sample_op_center)
 
@@
      all_gold_sample_frames_op <- gold_sample_op
+     gold_sample_all_dets <- gold_sample_raw_dets 
    }
@@
      full_join(gold_sample_op)
+
+   gold_sample_all_dets <- gold_sample_all_dets %>%
+     full_join(gold_sample_raw_dets)
+
    }
@@
 }
+```
+
+# Save it out
+```{r}
+# gold sample individual detections for each frame with position data
+save(gold_sample_all_dets, file = here::here('data/preprocessed_data_2021/',paste0('gold_sample_all_indiivdual_dets.RData')))
+
+```
+
+```{r}
 
@@
 
-all_thresholds = seq(0,.9,.1)
+all_thresholds = seq(0,.99,.01)
 

### 2022-01-06 paper/preprint/appendix.Rmd
added density plots of OpenPose hand/face false positives (for gold set)

@@
 
+## Location of OpenPose False Positives
+
+Below we visualize the locations of the 1229 faces (in 1093 frames) that OpenPose detected in the gold set frames that were not actually there, as well as the 1778 OpenPose false positive hands (in 1237 frames) from the gold set.
+The average location of OpenPose's false positives for both faces (left) and hands (right) are somewhat more common in the center of the frame, but some are scattered across the frame.
+Qualitatively, the location of these false positives do not look much different than the true positive detections.
+
+```{r density-op-fps, fig.width=6, fig.height=3}
+load(here::here('data/preprocessed_data_2021/gold_sample_all_indiivdual_dets.RData'))
+ddd <- gold_sample_all_dets %>% left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan))
+
+# density plot of OP's false positive face/hand locations
+p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
+  mutate(x=left+0.5*width,
+         y=top-0.5*height) %>% # could actually overplot all the face rectangles? prob very messy...
+  ggplot(aes(x=x, y=y, fill=..level..)) + 
+  stat_density_2d(geom = "polygon") + xlim(-.05,1.1) + ylim(-.1,1.0) + 
+  xlab("Mean x-position of OpenPose Detection") + 
+  ylab("Mean y-position of OpenPose Detection") + 
+  ggtitle("Face False Positives") + theme(legend.position = "none")
+
+p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
+  mutate(x=left+0.5*width,
+         y=top-0.5*height) %>%
+  ggplot(aes(x=x, y=y, fill=..level..)) + 
+  stat_density_2d(geom = "polygon") + xlim(-.05,1.1) + ylim(-.1,1.0) + 
+  xlab("Mean x-position of OpenPose Detection") + 
+  ylab("Mean y-position of OpenPose Detection") + 
+  ggtitle("Hand False Positives") + theme(legend.position = "none")
+
+ggpubr::ggarrange(p1, p2)
+```
+
 # Activity by Location

### 2022-01-06 paper/preprint/appendix.Rmd
flip y-axis of OP FPs (top-left is origin)

--- 2022-01-06 paper/preprint/appendix.Rmd
@@
 
+## Location of OpenPose False Positives
+
+Below we visualize the locations of the 1229 faces (in 1093 frames) that OpenPose detected in the gold set frames that were not actually there, as well as the 1778 OpenPose false positive hands (in 1237 frames) from the gold set.
+The average location of OpenPose's false positives for both faces (left) and hands (right) are somewhat more common in the center of the frame, but some are scattered across the frame.
+Qualitatively, the location of these false positives do not look much different than the true positive detections.
+
+```{r density-op-fps, fig.width=6, fig.height=3}
+load(here::here('data/preprocessed_data_2021/gold_sample_all_indiivdual_dets.RData'))
+ddd <- gold_sample_all_dets %>% left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan))
+
+# density plot of OP's false positive face/hand locations
+p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
+  mutate(x=left+0.5*width,
+         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
+  ggplot(aes(x=x, y=y, fill=..level..)) + 
+  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
+  xlab("Mean x-position of OpenPose Detection") + 
+  ylab("Mean y-position of OpenPose Detection") + 
+  ggtitle("Face False Positives") + theme(legend.position = "none")
+
+p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
+  mutate(x=left+0.5*width,
+         y=1-(top+0.5*height)) %>% # top-left is 0,0
+  ggplot(aes(x=x, y=y, fill=..level..)) + 
+  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
+  xlab("Mean x-position of OpenPose Detection") + 
+  ylab("Mean y-position of OpenPose Detection") + 
+  ggtitle("Hand False Positives") + theme(legend.position = "none")
+
+ggpubr::ggarrange(p1, p2)
+```
+
 # Activity by Location

### 2022-01-06 paper/preprint/appendix.Rmd
fix roc curves figure

@@
 
-```{r}
+```{r roc_curves, fig.width=6.5, fig.height=3.2, fig.cap="ROC curves relating the rate of true vs.
+false positives for both face and hand detections at each level of detector confidence thresholds (lighter values = stricter cutoffs)."}
 ggarrange(face_roc, hand_roc, nrow=1)
@@
   ylab("Mean y-position of OpenPose Detection") + 
-  ggtitle("Face False Positives") + theme(legend.position = "none")
+  ggtitle("Face False Positives") + theme(legend.position = "none") +
+  +
+  scale_y_reverse()
 
@@
   ylab("Mean y-position of OpenPose Detection") + 
-  ggtitle("Hand False Positives") + theme(legend.position = "none")
+  ggtitle("Hand False Positives") + theme(legend.position = "none") +
+  +
+  scale_y_reverse()
 

### 2022-01-06 preprocessing/step5_preprocess_fullset_from_bb_outputs.Rmd
update code to get center dets for gold sample

--- 2021-12-23 preprocessing/step5_preprocess_fullset_from_bb_outputs.Rmd
@@
    # now get vid level data
-   gold_sample_op <- this_vid_data %>%
+   gold_sample_op_all <- this_vid_data %>%
      filter(frame %in% frames_to_get$frame) %>%
@@
      summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)
+
+   # gold_sample_raw_dets <- this_vid_data %>%
+   #   filter(frame %in% frames_to_get$frame) %>%
+   #   mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
+   #   group_by(frame, vid_name, child_id)
 
@@
 
-   gold_sample_op<- gold_sample_op %>%
-      right_join(gold_sample_op_center)[1:]
+   gold_sample_op<- gold_sample_op_all %>%
+      left_join(gold_sample_op_center, by=c('vid_name','child_id','frame')) %>%
+      mutate(hand_detected_center = replace_na(hand_detected_center, 'FALSE')) %>%
+      mutate(face_detected_center = replace_na(face_detected_center, 'FALSE'))
 
@@
      all_gold_sample_frames_op <- gold_sample_op
+     # gold_sample_all_dets <- gold_sample_raw_dets 
    }
@@
      full_join(gold_sample_op)
+
+   # gold_sample_all_dets <- gold_sample_all_dets %>%
+   #   full_join(gold_sample_raw_dets)
+
    }

### 2022-01-06 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
Substantial edits to detector validation, intro, and GD sections

@@
 Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of more than 1700 headcam videos collected at home from three children along a span of 6 to 32 months of age—--the SAYCam dataset [@SAYcam].
-We thus analyze the video data from this dense, longitudinal dataset as case studies of how the social information in the infant view changes over the course of development.
+We analyze the video data from this dense, longitudinal dataset as case studies of how the social information in the infant view changes over the course of development in individual children.
 These kinds of longitudinal case studies provide an important counterpoint to cross-sectional investigations for several reasons.
@@
 
+However, it is important to note that these data -- albeit naturalistic and densely sampled within individuals -- come from only a few children in western contexts [@@henrich2010most], and as such cannot on their own yield generalizable conclusions about developmental changes in the infant view.
+Instead, they serve as a testbed for validating prior developmental findings within the daily lives of individual children -- and for generating novel hypotheses that can be tested in cross-sectional datasets or targeted in-lab experiments.
+
 With hundreds of hours of footage (>42M frames), however, this large dataset necessitates a shift to an automated annotation strategy.
@@
 However, these at-home, naturalistic videos contain more cluttered visual environments, challenging lighting conditions, and many different novel viewpoints.
-This this paper, we first validate the use of OpenPose by comparing face and hand detections to a human-annotated set of 24,000 frames.
-Overall, we find that OpenPose operates relatively on egocentric scenes including multiple people, even if they are partially-occluded (see Figure 1), nd and discuss the benefits and drawbacks of this automated annotation strategy.
-
-We next capitalize on this computational advance to annotate the entirety of this large, longitudinal video dataset.
-We use these detections to report how the proportion of faces and hands changes with age and motor development milestones in each of the three children in the dataset.
-Weinvestigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the head cameras as well as a diversity of locations in which videos were recorded.
+In this paper, we first validate the use of OpenPose by comparing face and hand detections to a human-annotated set of 24,000 frames.
+Though OpenPose does not detect faces and hands with perfect accuracy, we find that this model still operates relatively well on these challenging egocentric scenes including multiple people, even if they are partially-occluded (see Figure 1 for example detections and Appendix Figure \ref{fig:error_examples} for examples of missed detections and false alarms).
+
+We thus capitalize on this computational advance to annotate the entirety of this large, longitudinal video dataset. 
+We use these detections to first report how the proportion of faces and hands changes with age and motor development milestones in each of the three children in the dataset. 
+We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the head cameras as well as a diversity of locations in which videos were recorded.
 Finally, making use of automated annotation of pose bounding boxes, we analyze the size, location, and variability of detected faces and poses across development in these three children.
+Overall, these findings largely validate prior cross-sectional findings, and further suggest that automated annotated can be used to analyze naturalistic video datasets to build towards generalizable conclusions about the statistics of the social information in the infant view across a wide variety of populations.
 
@@
 # load all detections for gold sample frames
-load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_all_detections.RData')) 
+load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_with_centerall_detections.RData')) 
 ```
@@
 
-## Detection Validation
+## Detector Validation
 ```{r}
@@
   right_join(all_gold_sample_frames_op) %>%
-  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))
+  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) %>%
+   mutate(face_eval_ketan_center = evaluate_detector(face_present_ketan, face_detected_center), hand_eval_ketan_center = evaluate_detector(hand_present_ketan, hand_detected_center))
 
@@
  hand_performance = return_prf_short(gold_sample$hand_eval_ketan)
+
+ face_performance_center = return_prf_short(gold_sample$face_eval_ketan_center)
+ hand_performance_center = return_prf_short(gold_sample$hand_eval_ketan_center)
 ```
@@
   mutate(hand_eval_adults = evaluate_detector(hand_present_ketan, hand_detected))
+
+gold_sample_child_hands <- gold_sample %>%
+  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
+  filter(child_hand_seg==TRUE)
 
@@
 
-To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A).
-Frames were jointly annotated for the presence of faces and hands by one author.
-A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated 3150 frames; agreement with the primary coder was >95%.
-Upon manually inspecting these 24K frames, we noticed that `r  num_frames_excluded` were sampled from videos taken from the allocentric perspective (i.e., not from the infant viewpoint); these frames and videos containing these frames were subsequently excluded from all other analyses.
-
 As has been observed in other studies on automated annotation of headcam data [e.g.
@@
 
-To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / (hits + false alarms)), recall (hits / (hits + misses)), and F-score (the harmonic mean of precision and recall).
+### Detector vs. human annotations of faces/hands
+To test the validity of OpenPose's hand and face detections, we compared the accuracy detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A); this sample was conducted before child Y was added to the dataset.
+Frames were jointly annotated for the presence of faces and hands by one author.
+A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated 3150 frames; agreement with the primary coder was >95%.
+Upon manually inspecting these 24K frames, we noticed that `r  num_frames_excluded` were sampled from videos taken from the allocentric perspective (i.e., not from the infant viewpoint); these frames and videos containing these frames were subsequently excluded from all other analyses.
+
+To evaluate OpenPose's performance, we compared its detections to the manually-annotated "gold set" of frames, calculating precision (hits / (hits + false alarms)), recall (hits / (hits + misses)), and F-score (the harmonic mean of precision and recall).
 In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`.
@@
 
-We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose -- a notoriously challenging detection problem [@bambach2015lending].
-To assess this possibility, we obtained additional human annotations for the subsample of 9051 frames in the gold set frames where a hand was present; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands.
-Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100`% of missed hand detections were of child hands.
-When frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`.
-We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Appendix Figure \ref{fig:handLocation}.
-
-Next, we examined the degree to which the detector confidence changed model performance.
-We found that restricting our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
-Overall, our analyses suggested that including all detections was the most beneficial for optimizing precision; see Appendix for a full ROC curve detailing all detector confidence confidence thresholds.
-
-Finally, we examined whether model accuracy for hands and faces varied across age or between child and location  (see plots for age/child in Appendix, Figure \ref{fig:det_perf_by_age}, and location in Figure \ref{fig:det_perf_by_locations}).
-Some of the videos at taken at older ages for child A did seem to show lower hand detection accuracy, perhaps due the presence of child's hands; however, there were also fewer videos at these time points.
-In general, however, we found evidence for considerable variation in model accuracy across different videos, suggesting that particular recording contexts, activities, or lighting could cause conditions that would impair detector performance.
-
-In a qualitative analysis, we also inspected frames where OpenPose failed to detect faces/hands or erroneously detected them to gain insight into the factors driving performance.
-Figure \ref{fig:error_examples} shows examples of both missed detections and false alarms for both faces and hands and highlights the challenging detection conditions presented by these at-home, naturalistic videos.
+We next inspected frames where OpenPose failed to detect faces/hands or erroneously detected them to gain insight into the factors driving performance.
+Appendix Figure \ref{fig:error_examples} shows randomly sampled examples of both missed detections and false alarms for both faces and hands and highlights the challenging detection conditions presented by these at-home, naturalistic videos.
 Many missed faces included very far away or very close up views of faces at odd angles, as well as faces that were partially occluded by odd lighting conditions.
 False alarms for faces included animal faces depicted in picture books and poses where the person was not facing a camera.
-Hands were often missed when they were seen only from the side and unconnected to a pose, whereas hands were sometimes erroneously detected when a pose was present but the hands were out of view.
+Hands were sometimes erroneously detected when a pose was present but the hands were out of view, and hands were often missed when they were seen only from the side and unconnected to a pose or belonged to the child.
+
+### Detecting children's own hands 
+We thus suspected that OpenPose's low recall for hands in this dataset was because children’s own hands were often in view of the camera and unconnected to a pose -- a notoriously challenging detection problem [@bambach2015lending].
+To assess this possibility, we obtained additional human annotations for the subsample of 9051 frames in the gold set frames where a hand was present; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands.
+Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100`% of missed hand detections were of child hands; OpenPose was only able to detect children's hands when there were in view `r round(mean(gold_sample_child_hands$hand_detected),2)*100`% of the time.
+Accordingly, when frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`.
+We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Appendix Figure \ref{fig:handLocation}.
+
+### Restricting detections to the center field-of-view
+Given that the fish-eye lens may have distorted the edges of the visual field in the videos, we also examined whether we would see improved precision by restricting the included detections to the center field-of-view, and excluding detections that occured in the outer 20\% of each frame.
+This restricted field-of-view is also more comparable to video data from other head-mounted cameras.
+However, we found that excluding these detections did not improve the model's precision for either faces or hands; rather, it only decreased recall.
+Excluding peripehral detections led to an overall f-score of `r round(face_performance_center[3],2)`, for faces with a precision of `r round(face_performance_center[1],2)` and recall of `r round(face_performance_center[2],2)`.
+For hands, the F-score for center detections was `r round(hand_performance)center[3],2)`, with a precision of `r round((hand_performance)[1],2)` and recall of `r round((hand_performance)[2],2)`.
+Thus, detections that were made in the periphery of these videos were not more likely to be false alarms for either faces or hands.
+Appendix Figure \ref{fig: density-op-fps} illustrates this finding, showing the density of false positives for both faces and hands that are concentrated in the center of the fied of view.
+
+### Detector confidence
+We next examined the degree to which including detections that the model was more or less confident in changed overall model performance for face/hand detection.
+When we restricted detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
+Further analyses sweeping across the entire range of possible confidence detection thresholds revealed that including all detections was the most beneficial for optimizing the rate of true positives (see Appendix Figure \ref{fig:roc_curves} for full ROC curves for both face and hand detections).
+
+### Accuracy across child, location, and age
+Finally, we examined whether model accuracy for hands and faces varied across age or between child and the location in which the videos were filmed (e.g., kitchen vs.
+living room).
+Some of the videos at taken at older ages for child A did seem to show lower hand detection accuracy, perhaps due the presence of child's hands; however, there were also fewer videos at these time points (see plots for age/child in Appendix, Figure \ref{fig:det_perf_by_age}).
+We did not find any discernible trends in face/hand detection accuracy across different filming locations (see Figure \ref{fig:det_perf_by_locations}).
+However, we did still see considerable variation in model accuracy across different videos, suggesting that particular recording activities, lighting conditions, or situations could cause conditions that would impair detector performance.
+
 Thus, while OpenPose was trained on photographs from the adult perspective, this model still performed relatively well on these challenging the egocentric infant viewpoint with no fine-tuning or post-processing of the detections, especially given these challenging and varied videos.
+Including all detections made by OpenPose in all locations led to the most accurate model performance.
+We next use this detection method to analyze the rest of the large dataset, with the caveat that we are likely underestimating the proportion of hands in the infant view.
 
@@
 Finally, we analyzed how these two sources of social information co-occurred.
-To do so, we  calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range.
+To do so, wecalculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range.
 Faces and hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}C).
@@
 One idea is that children’s ability to stand and move on their own may fundamentally change the visual social information that they see (e.g., facial expressions, gaze cues, pointing)  [@walle2016infant] relative to infants who are still sitting and crawling.
-Indeed, in in-lab studies, research has found that children's in-the-moment posture -- and that of their caregiver -- is a strong predictor of the visual social information in view [@franchak2017see; @long2021automated].
+Indeed, in in-lab studies, children's in-the-moment posture -- and that of their caregiver -- is a strong predictor of the visual social information that children see [@franchak2017see; @long2021automated].
 
 We thus next analyzed how the social information in view changed as a function of each child reaching particular developmental motor milestones.
-Each parent completed the Ages and Stages Questionnaire (ASQ) [@bricker1999ages], which includes questions about their child's motor abilities, and we used the responses from this questionnaire to code the age (in months) at which each child became able to sit, cruise, and walk on their own (questions about crawling were not included in the questionnaire)..
+Each parent in the SAYCam dataset completed the Ages and Stages Questionnaire (ASQ) [@bricker1999ages], which includes questions about their child's motor abilities, and we used the responses from this questionnaire to code the age (in months) at which each child became able to sit, cruise, and walk on their own (questions about crawling were not included in the questionnaire).
 We found considerable variability in the age at which each child achieved these three milestones.
@@
 However, we did not find major differences with the onset of walking; as these children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$).
-Thus, these analyses confirm and extend cross-sectional finding, leveraging dense, within-child data to help elucidate the complex relationship between motor development and the social information in view.
+Thus, these analyses confirm and extend cross-sectional findings, leveraging dense, within-child data to help elucidate the complex relationship between motor development and the social information in view.
 
@@
 Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime).
-We did not have access to annotations of activity. 
+We did not have access to detailed annotations of activity; each video was associated with several different activities. 
 Thus, following @roy2015predicting, we used spatial location as a proxy for activity context, taking advantage of the presence of these annotations for a subset of the SAYCam videos. 
+In our viewing of the SAYCam videos and in other annotations available with the dataset, activities varied somewhat predictably by location: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.
+However, every location was associated with multiple activities; see Appendix Figure \ref{fig:activities_by_loc} for a heatmap relating individual activities to locations in the dataset.
 Of the `r num_videos` videos in the dataset, `r num_videos_annotated` were annotated for the location or locations they were filmed in. 
@@
 Of this set, `r videos_included` videos were filmed in only a single location (e.g., the location label did not change within the video), representing 17 percent of the dataset and over 5 million frames.
-In our viewing of the SAYCam videos and in other annotations available with the dataset, activities varied somewhat predictably by location: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.
-However, every location was of course associated with multiple activities; see Appendix Figure \ref{fig:activities_by_loc} for a heatmap relating individual activities to locations in the dataset.
 
@@
 ```
-In a third set of analyses, we explored fine-grained changes in the SAYCam infants' access to social information across development.
+In a final set of analyses, we explored fine-grained changes in the SAYCam infants' access to social information across development.
 In these analyses, we capitalize on the fact that OpenPose provides not only face and hand detections but also positional keypoints. 
@@
 # General Discussion
-Here, we first validated the use of an automated pose detection model to detect the faces and hands in view in a longitudinal dataset of egocentric, everyday visual experience.
+Here, we validated the use of an automated pose detection model to detect the faces and hands in view in a longitudinal dataset of egocentric, everyday visual experience.
 We then used these detections to analyze the social information seen from each of three children's egocentric perspective from 6 to 32 months of age.
@@
 
-Second, we also found an unexpectedly high proportion of hands in infants' view, even when restricting the analysis to detections in the center field-of-view to make the viewpoints comparable to those of headcams used in prior work and to exclude the portion of the frame most likely to contain children's own hands.
+Second, we also found an unexpectedly high proportion of hands in the egocentric experience of these three infants.
+We found this to be true even when restricting the analysis to detections in the center field-of-view to make the viewpoints comparable to those of headcams used in prior work and to exclude the portion of the frame most likely to contain children's own hands.
 Why might this be the case?
@@
 While OpenPose did not provide annotations that were as accurate as those provided by human annotators, we found relatively consistent results with prior literature, suggesting that the sheer scale and density of the annotations provided by this method may overcome some of its limitations.
-
-Importantly, however, these automated detections do not entirely obviate the need for careful inspection and manual annotation of dense video data.
-While the present results suggest that OpenPose achieves moderate performance at detecting faces and hands in egocentric videos -- as does @Long2021automated -- these results do not guarantee that OpenPose will generalize with similar accuracy to other video datasets.
-By using manual annotations to estimate the accuracy of these automated techniques for their video datasets, researchers can weigh the pros and cons of automated detections for answering their particular research questions.
-While OpenPose does provide a considerable amount of about all of the people in a given image -- estimating the entire poses for every individual -- it may not always perform similarly in challenging viewpoints.
-
-So, how might OpenPose -- or other pose detection algorithms -- be improved upon and used in future work?
+Thus, OpenPose may alleviate the burden of manually annotating large egocentric video datasets for the social information in view, helping the field build more generalizable conclusions about how infants experience their early visual social environment.
+
+Of course, these automated detections do not entirely obviate the need for careful inspection and manual annotation of dense video data.
+While the present results suggest that OpenPose achieves moderate performance at detecting faces and hands in infant egocentric videos -- as in @Long2021automated -- these results do not guarantee that OpenPose will generalize with similar accuracy to other video datasets.
+While OpenPose does provide a considerable amount of about all of the people in a given image -- estimating the entire poses for every individual -- it may not perform accurately enough to answer certain fine-grained research questions.
+Going forward, we suggest that researchers continue to compare a small set of manual annotations relevant to their research questions of interest to OpenPose's performance.
+
+How might pose detection algorithms be improved upon such that they can achieve greater accuracy in analyzing infant egocentric videos?
+This question is ripe for collaboration between computer vision experts and devleopmental psychologists.
 One promising direction may be to use detailed pose annotations of the people in the infant view to fine-tune later layers of pose detection networks.
@@
 A second potential area for innovation lies in leveraging the dense nature of these large-scale annotations to improve model accuracy: By pooling detections from surrounding frames, we may be able to build classifiers that perform more accurately on a single challenging viewpoint.
-Finally, a third area for improvement consists of building classifiers that can accurately distinguish between children's hands (as seen from the egocentric point of view) versus adults' hands--a notoriously challenging problem in computer vision [@bambach2017lending].
-We expect that these goals may become more and more feasible as we simultaneously improve the head-mounted cameras that are used in both at-home and in-lab studies; increasing the resolution and quality of the images we record will no doubt improve the ability of computer vision algorithms to extract detailed information from them.
+Finally, a third area for improvement consists of building classifiers that can accurately distinguish between children's hands (as seen from the egocentric point of view) versus adults' hands--a notoriously challenging problem in computer vision [@bambach2015lending].
+We expect that these goals may become more and more feasible as we also improve the head-mounted cameras that are used in both at-home and in-lab studies; increasing the resolution and quality of the images we record will no doubt improve the ability of computer vision algorithms to extract detailed information.
 

### 2022-01-06 paper/manuscript/_intermediate_version/paper_revised_submission_april2021_apa.Rmd
rename writing folder structure

--- 2021-06-10 paper/preprint/manuscript_june2021_apa.Rmd
@@
 
-authornote: |
-  The data and code that support the findings of this study are available at https://osf.io/cdhw4/.
+# authornote: |
+#   Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+# 
+#   Enter author note here.
 
@@
 footnotelist      : no
-linenumbers       : no
+linenumbers       : yes
 mask              : no
@@
 In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.
-We also found that restricting our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
+We also found that restricting our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`).
 
 We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose -- a notoriously challenging detection problem [@bambach2015lending].
-To assess this possibility, we obtained additional human annotations for the subsample of 9051 frames in the gold set frames where a hand was present; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands.
+To assess this possibility, we obtained additional human annotations for the subsample of 9051 frames in the gold set frames where which a hand was present; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands.
 Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100`% of missed hand detections were of child hands.
@@
 As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, and decreasing face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%.
-This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure Appendix \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
+This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
 Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}).
@@
 @bruner1985role discussed the role of children's activities in shaping the information present for learning.
-Following this idea, we investigated whether there were differences in access to faces and hands by the activity that the child was engaged in.
+Following this idea, we investigated whether there were differences in access to faces by the activity that the child was engaged in.
 This hypothesis seems intuitively appealing.
@@
 Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime).
+
 We did not have access to annotations of activity. 
@@
 
-```{r avgSizes, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Average size of poses, faces, and hands detected in the dataset as a function of age for each child in the dataset (each color = different child).
+```{r avgSizes, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Average size of poses, faces, and hands detected in the dataset  between eyes in faces detected as a function of age for each child in the dataset (each color = different child).
 Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range."}
@@
 Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.
+
 First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016; @Jayaraman2015]. 
@@
 During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1).
-Indeed, using the same pose detector on videos from in-lab play sessions, @long2021automated found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age.
+Indeed, using the same pose detector on videos from in-lab play sessions, @sanchez2018postural found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age.
 Work that directly examines the variability in the social information in view across more vs.
@@
 # Acknowledgements
-Thanks to the creators of the SAYCam dataset who made this work possible and to Alessandro Sanchez for his contributions to the codebase.
-This work was funded by a Jacobs Foundation Fellowship to MCF, a John Merck Scholars award to MCF, and NSF #1714726 to BLL.
 

### 2022-01-06 paper/manuscript/appendix.Rmd
rename writing folder structure

--- 2022-01-06 paper/preprint/appendix.Rmd
@@
 
-knitr::opts_chunk$set(echo=F, warning=F, cache=F, 
+knitr::opts_chunk$set(echo=F, warning=F, cache=T, 
                       message=F, sanitize = T)
@@
 ## Read in preprocessed data 
-load(here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
+load(here::here('data/preprocessed_data_2022/all_vid_data_from_bbs_all_detections.RData')) # all detections
 
 ## all bounding boxes
-load(file=here::here('data/preprocessed_data_2021/bounding_box_summaries.RData'))
+load(file=here::here('data/preprocessed_data_2022/bounding_box_summaries.RData'))
 
@@
 ## Load in gold sample detections
-load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
-load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_with_centerall_detections.RData'))
+load(here::here('data/preprocessed_data_2022/gold_sample_annotations2020-01-31.RData')) # human annotations
+load(here::here('data/preprocessed_data_2022/gold_sample_from_bbs_2021_with_centerall_detections.RData'))
 
-# all_gold_sample_frames_op_hc = load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_high_conf_detections.RData')) 
+# all_gold_sample_frames_op_hc = load(here::here('data/preprocessed_data_2022/gold_sample_from_bbs_2021_high_conf_detections.RData')) 
 ```
@@
 ### Examine gold sample performance by child hands
-load(here::here('data/preprocessed_data_2021/child_adult_hand_annotations_by_frame.RData'))
+load(here::here('data/preprocessed_data_2022/child_adult_hand_annotations_by_frame.RData'))
 
@@
 ### Load turk hand annotations with all bounding boxes (multiple dets per frame)
-load(here::here('data/preprocessed_data_2021/hand_annotations_2020-01-29.RData'))
+load(here::here('data/preprocessed_data_2022/hand_annotations_2020-01-29.RData'))
 
@@
 # with all thresholds
-load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections_all_thresholds.RData"))
+load(here::here("data","preprocessed_data_2022","gold_sample_from_bbs_2021_all_detections_all_thresholds.RData"))
 
-load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
+load(here::here('data/preprocessed_data_2022/gold_sample_annotations2020-01-31.RData')) # human annotations
 ```
@@
 # without thresholds
-load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections.RData"))
+load(here::here("data","preprocessed_data_2022","gold_sample_from_bbs_2021_all_detections.RData"))
 
@@
 
-    # mutate(face_eval_ketan_center = evaluate_detector(face_present_ketan, face_detected_center), hand_eval_ketan_center = evaluate_detector(hand_present_ketan, hand_detected_center)) 
 ```
@@
 # add age day bins to gold_sample
-load(file=here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
+load(file=here::here('data/preprocessed_data_2022/all_vid_data_from_bbs_all_detections.RData')) # all detections
 bin_size = 7 # days
@@
   do(return_prf(.$hand_eval_ketan)) 
-```
-
-```{r}
-# Evaluating prfs in center detections is challenging because we ONLY have ground truth on the full image -- so it's not that informative.
-
-# return_prf_short(gold_sample$hand_eval_ketan_center)
-# return_prf_short(gold_sample$face_eval_ketan_center)
 ```
@@
 ```{r}
-load(here::here('data/preprocessed_data_2021/saycam_metadata.RData')) # meta
+load(here::here('data/preprocessed_data_2022/saycam_metadata.RData')) # meta
 
@@
 ```{r include=FALSE}
-load(file = here::here('data/preprocessed_data_2021/goldset_category_annotations.RData'))
+# load(file = here::here('data/preprocessed_data_2022/goldset_category_annotations.RData'))
 
-fp_face_examples <- d %>%
-  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-  filter(face_eval_ketan == 'FP')
-
-fp_hand_examples <- d %>%
-  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-  filter(hand_eval_ketan == 'FP')
-
-fn_face_examples <- d %>%
-  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-  filter(face_eval_ketan == 'FN')
-
-fn_hand_examples <- d %>%
-  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-  filter(face_eval_ketan == 'FN')
-
-images_to_render =  fp_hand_examples
-which_images = 'fp_hand_examples'
-
-public_urls = unique(images_to_render$public_url)
-img_names_short = unique(images_to_render$img_name)
-
-dir.create(here::here("data/annotation_examples/", which_images),recursive = TRUE)
-
-  for (i in 1:length(public_urls)){
-    this_image = image_read(public_urls[i])
-    image_write(this_image,here::here("data/annotation_examples/",which_images, img_names_short[i]))
-  }
+# fp_face_examples <- d %>%
+#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+#   filter(face_eval_ketan == 'FP')
+# 
+# fp_hand_examples <- d %>%
+#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+#   filter(hand_eval_ketan == 'FP')
+# 
+# fn_face_examples <- d %>%
+#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+#   filter(face_eval_ketan == 'FN')
+# 
+# fn_hand_examples <- d %>%
+#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+#   filter(face_eval_ketan == 'FN')
+# 
+# images_to_render =  fp_hand_examples
+# which_images = 'fp_hand_examples'
+# 
+# public_urls = unique(images_to_render$public_url)
+# img_names_short = unique(images_to_render$img_name)
+# 
+# dir.create(here::here("data/annotation_examples/", which_images),recursive = TRUE)
+# 
+#   for (i in 1:length(public_urls)){
+#     this_image = image_read(public_urls[i])
+#     image_write(this_image,here::here("data/annotation_examples/",which_images, img_names_short[i]))
+#   }
 
@@
 ```{r}
-det_types = c('FP','FN')
-
-render_examples = FALSE
-if (render_examples == TRUE) {
-for (det_type in det_types) {
-  to_render_hands <- d %>%
-    distinct(vid_name, frame, public_url) %>%
-    left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-    filter(hand_eval_ketan == det_type) %>%
-    ungroup() %>%
-    dplyr::sample_n(7)
-
-  image_read(to_render_hands$public_url) %>%
-    image_append(stack = FALSE) %>%
-    image_write(paste0(here::here("data/annotation_examples/"), 'example_hands_', det_type,".png"))
-
-  ###
-    to_render_faces <- d %>%
-    distinct(vid_name, frame, public_url) %>%
-    left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-    filter(face_eval_ketan == det_type) %>%
-    ungroup() %>%
-    dplyr::sample_n(7)
-
-  image_read(to_render_faces$public_url) %>%
-    image_append(stack = FALSE) %>%
-    image_write(paste0(here::here("data/annotation_examples/"), 'example_faces_', det_type,".png"))
-
-}
-}
+# det_types = c('FP','FN')
+# render_examples = FALSE
+# if (render_examples == TRUE) {
+# for (det_type in det_types) {
+#   to_render_hands <- d %>%
+#     distinct(vid_name, frame, public_url) %>%
+#     left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+#     filter(hand_eval_ketan == det_type) %>%
+#     ungroup() %>%
+#     dplyr::sample_n(7)
+# 
+#   image_read(to_render_hands$public_url) %>%
+#     image_append(stack = FALSE) %>%
+#     image_write(paste0(here::here("data/annotation_examples/"), 'example_hands_', det_type,".png"))
+#   
+#   ###
+#     to_render_faces <- d %>%
+#     distinct(vid_name, frame, public_url) %>%
+#     left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+#     filter(face_eval_ketan == det_type) %>%
+#     ungroup() %>%
+#     dplyr::sample_n(7)
+# 
+#   image_read(to_render_faces$public_url) %>%
+#     image_append(stack = FALSE) %>%
+#     image_write(paste0(here::here("data/annotation_examples/"), 'example_faces_', det_type,".png"))
+#   
+# }
+# }
 
@@
 ```{r density-op-fps, fig.width=6, fig.height=3}
-load(here::here('data/preprocessed_data_2021/gold_sample_all_indiivdual_dets.RData'))
+load(here::here('data/preprocessed_data_2022/gold_sample_all_indiivdual_dets.RData'))
 ddd <- gold_sample_all_dets %>% left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan))
@@
   ggtitle("Face False Positives") + theme(legend.position = "none") +
-  +
   scale_y_reverse()
@@
   ggtitle("Hand False Positives") + theme(legend.position = "none") +
-  +
   scale_y_reverse()

### 2022-01-06 paper/manuscript/initial_submission/appendix.Rmd
rename writing folder structure

--- 2022-01-06 paper/preprint/appendix.Rmd
@@
 
-```{r, echo=F, message=F}
+```{r}
 library(tidyverse)
@@
 library(ggthemes)
-library(egg)
-library(stargazer)
-library(magick)
-library(ggeffects)
-
-knitr::opts_chunk$set(echo=F, warning=F, cache=F, 
-                      message=F, sanitize = T)
 ```
@@
 load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
-load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_with_centerall_detections.RData'))
+load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_all_detections.RData'))
 
@@
 # function to return prfs
- return_prf_short <- function(eval){
+ return_prf_short = function(eval){
   tp=sum(eval == "TP")
@@
  }
+
+#
 
@@
 ```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 6-31 month-old.
-Each dot represents the average position from one video within a given age range.", warning=F}
+Each dot represents the average position from one video within a given age range."}
 
@@
 ```
-
-# Detection threshold estimations
-
-```{r}
-# with all thresholds
-load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections_all_thresholds.RData"))
-
-load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
-```
-
-```{r}
-evaluate_detector <- function(truth, detection) {
-  if (truth == TRUE) {
-    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
-    else return("FN") # was face/wrist, missed face/wrist
-  }
-  else {
-    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
-    else return("FP") # was not face/wrist, detected face/wrist
-  }
-}
-
- return_tpr = function(eval){
-  tp=sum(eval == "TP")
-  fp=sum(eval == "FP")
-  fn=sum(eval == "FN")
-  tn=sum(eval == "TN")
-  tpr = tp / (tp + fn)
-  return(tpr)
- }
-
-return_fpr = function(eval){
-  tp=sum(eval == "TP")
-  fp=sum(eval == "FP")
-  fn=sum(eval == "FN")
-  tn=sum(eval == "TN")
-  fpr = fp / (fp + tn)
-  return(fpr)
- }
-
-```
-
-```{r}
-roc_data <- gold_sample %>%
-  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
-  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
-  right_join(all_gold_sample_frames_op) %>%
-   mutate(hand_detected = hand_detected>0, face_detected = face_detected > 0) %>% # number = number of faces/hands detected
-  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) %>%
-  group_by(detection_threshold) %>%
-  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan))
-```
-
-```{r}
-face_roc = ggplot(data=roc_data, aes(x=fpr_faces, y=tpr_faces, color=detection_threshold)) +
-  geom_point() +
-  geom_line() +
-  ylim(0,1) +
-  xlim(0,1) +
-  geom_abline(color = 'grey') +
-  xlab('False Positive Rate') +
-  ylab('True Positive Rate') +
-  ggtitle('Face detections') +
-  theme(legend.position = 'none')
-
-hand_roc = ggplot(data=roc_data, aes(x=fpr_hands, y=tpr_hands, color=detection_threshold)) +
-  geom_point() +
-  geom_line() +
-  ylim(0,1) +
-  xlim(0,1) +
-  geom_abline(color = 'grey') +
-  xlab('False Positive Rate') +
-  ylab('True Positive Rate') +
-  ggtitle('Hand detections') +
-  theme(legend.position = 'none')
-
-```
-
-```{r}
-ggarrange(face_roc, hand_roc, nrow=1)
-```
-
-# OpenPose Error Analyses
-```{r}
-# remove big data frame with thresholds
-rm(all_gold_sample_frames_op)
-
-# without thresholds
-load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections.RData"))
-
-# join human and OP detections
-gold_sample <- gold_sample %>%
-  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
-  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
-  right_join(all_gold_sample_frames_op) %>%
-  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))
-
-    # mutate(face_eval_ketan_center = evaluate_detector(face_present_ketan, face_detected_center), hand_eval_ketan_center = evaluate_detector(hand_present_ketan, hand_detected_center)) 
-```
-
-```{r}
-# add age day bins to gold_sample
-load(file=here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
-bin_size = 7 # days
-min_age = min(all_vid_data$age_days, na.rm=TRUE) # 182
-max_age = max(all_vid_data$age_days, na.rm=TRUE) # 966
-bin_starts = seq(min_age-1, max_age+1,bin_size)
-bins = c(bin_starts, max_age)
-
-gold_sample <- gold_sample %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) 
-```
-
-```{r}
- return_prf = function(eval){
-  tp=sum(eval == "TP")
-  fp=sum(eval == "FP")
-  fn=sum(eval == "FN")
-  p = tp / (tp + fp)
-  r = tp / (tp + fn)
-  f=( 2 * p * r )/ (p + r)
-  num_detect = length(eval)
-  out <- data.frame(p,r,f,num_detect)
-  return(out)
- }
-
-# function to return prfs
- return_prf_short = function(eval){
-  tp=sum(eval == "TP")
-  fp=sum(eval == "FP")
-  fn=sum(eval == "FN")
-  p = tp / (tp + fp)
-  r = tp / (tp + fn)
-  f=( 2 * p * r )/ (p + r)
-  return(c(p,r,f))
- }
-
-```
-
-```{r}
-prf_by_age_faces <-  gold_sample %>%
-  group_by(child_id, age_day_bin) %>%
-  do(return_prf(.$face_eval_ketan))
-
-prf_by_age_hands <-  gold_sample %>%
-  group_by(child_id, age_day_bin) %>%
-  do(return_prf(.$hand_eval_ketan)) 
-```
-
-```{r}
-# Evaluating prfs in center detections is challenging because we ONLY have ground truth on the full image -- so it's not that informative.
-
-# return_prf_short(gold_sample$hand_eval_ketan_center)
-# return_prf_short(gold_sample$face_eval_ketan_center)
-```
-
-```{r det_perf_by_age, fig.width=6.5, fig.height=3.2, fig.cap="F-score of OpenPose hand and face detections in the gold sample by child and age. Size indicates number of detections age bin/child."}
-
-prf_by_age_faces$age_day_bin = as.numeric(prf_by_age_faces$age_day_bin)
-
-prf_by_age_hands$age_day_bin = as.numeric(prf_by_age_hands$age_day_bin)
-
-p1 <- ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
-  geom_point(alpha=.5) +
-  geom_smooth(span=20, alpha=.1)  +
-  ylim(0,1) +
-  ylab('F-score') + xlab('Age (months)') +
-  ggtitle("Face detections") + 
-  theme(legend.position= 'none')
-
-p2 <- ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
-  geom_point(alpha=.5) +
-  geom_smooth(span=20, alpha=.1)  +
-  ylim(0,1) +
-  ylab('F-score') + xlab('Age (months)') +
-  ggtitle("Hand detections") + 
-  theme(legend.position= 'none')
-```
-
-```{r}
-ggarrange(p1, p2, nrow=1)
-```
-
-```{r}
-# p2 = ggplot(prf_by_age_faces, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
-#   geom_point(alpha=.5) +
-#   geom_smooth(span=10, alpha=.1)  +
-#   ylim(0,1) +
-#   ylab('Precision - Face detection')+
-#   xlab('Age (months)') +
-#   theme(legend.position= 'none')
-# 
-# p3 =ggplot(prf_by_age_faces, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
-#   geom_point(alpha=.5) +
-#   geom_smooth(span=10, alpha=.1)  +
-#   ylim(0,1) +
-#   ylab('Recall - Face detection')+
-#   xlab('Age (months)') +
-#   theme(legend.position= 'none')
-# #
-# ggarrange(p1,p2,p3)
-
-```
-
-```{r}
-load(here::here('data/preprocessed_data_2021/saycam_metadata.RData')) # meta
-
-num_videos_annotated = sum(!is.na(meta$Location))
-videos_included = sum(!is.na(meta$Location) & meta$count_locations==1)
-```
-
-```{r}
-gold_sample_by_location <- gold_sample %>%
-  left_join(meta) %>%
-  filter(!is.na(Location)) %>%
-  filter(count_locations==1) 
-```
-
-```{r}
-prf_by_location_faces <-  gold_sample_by_location %>%
-  group_by(Location) %>%
-  do(return_prf(.$face_eval_ketan)) %>%
-  filter(num_detect > 50)
-
-prf_by_location_hands <-  gold_sample_by_location %>%
-  group_by(Location) %>%
-  do(return_prf(.$hand_eval_ketan)) %>%
-  filter(num_detect > 50)
-```
-
-```{r det_perf_by_locations, fig.width=6.5, fig.height=3.0, fig.cap="F-score of OpenPose hand and face detections in the gold sample by location.
-Size indicates number of detections per location: minimum = 55 (car); maximum = 1753 (living room)."}
-p1 <- ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=num_detect)) +
-  geom_point(alpha=.5) +
-  ylab('F-score') + ggtitle("Face detections") +
-  theme(legend.position = 'none') +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  ylim(0,1)
-
-p2 <- ggplot(prf_by_location_hands, aes(x=Location, y=f, col=Location, size=num_detect)) +
-  geom_point(alpha=.5) +
-  ylab('F-score') + ggtitle("Hand detections") +
-  theme(legend.position = 'none') +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  ylim(0,1)
-
-ggarrange(p1, p2, nrow=1)
-```
-
-# OpenPose Annotation Examples
-```{r include=FALSE}
-load(file = here::here('data/preprocessed_data_2021/goldset_category_annotations.RData'))
-
-fp_face_examples <- d %>%
-  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-  filter(face_eval_ketan == 'FP')
-
-fp_hand_examples <- d %>%
-  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-  filter(hand_eval_ketan == 'FP')
-
-fn_face_examples <- d %>%
-  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-  filter(face_eval_ketan == 'FN')
-
-fn_hand_examples <- d %>%
-  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-  filter(face_eval_ketan == 'FN')
-
-images_to_render =  fp_hand_examples
-which_images = 'fp_hand_examples'
-
-public_urls = unique(images_to_render$public_url)
-img_names_short = unique(images_to_render$img_name)
-
-dir.create(here::here("data/annotation_examples/", which_images),recursive = TRUE)
-
-  for (i in 1:length(public_urls)){
-    this_image = image_read(public_urls[i])
-    image_write(this_image,here::here("data/annotation_examples/",which_images, img_names_short[i]))
-  }
-
-```
-
-```{r}
-det_types = c('FP','FN')
-
-render_examples = FALSE
-if (render_examples == TRUE) {
-for (det_type in det_types) {
-  to_render_hands <- d %>%
-    distinct(vid_name, frame, public_url) %>%
-    left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-    filter(hand_eval_ketan == det_type) %>%
-    ungroup() %>%
-    dplyr::sample_n(7)
-
-  image_read(to_render_hands$public_url) %>%
-    image_append(stack = FALSE) %>%
-    image_write(paste0(here::here("data/annotation_examples/"), 'example_hands_', det_type,".png"))
-
-  ###
-    to_render_faces <- d %>%
-    distinct(vid_name, frame, public_url) %>%
-    left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-    filter(face_eval_ketan == det_type) %>%
-    ungroup() %>%
-    dplyr::sample_n(7)
-
-  image_read(to_render_faces$public_url) %>%
-    image_append(stack = FALSE) %>%
-    image_write(paste0(here::here("data/annotation_examples/"), 'example_faces_', det_type,".png"))
-
-}
-}
-
-```
-
-```{r error_examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=6, set.cap.width=T, num.cols.cap=2,  fig.fullwidth = TRUE, fig.align = "center", fig.cap = "Example false alarms/misses for faces/hands randomly sampled from the larger set of manual annotations."}
-error_examples <- png::readPNG("figs/OP_errors.png")
-grid::grid.raster(error_examples)
-```
-
-## Location of OpenPose False Positives
-
-Below we visualize the locations of the 1229 faces (in 1093 frames) that OpenPose detected in the gold set frames that were not actually there, as well as the 1778 OpenPose false positive hands (in 1237 frames) from the gold set.
-The average location of OpenPose's false positives for both faces (left) and hands (right) are somewhat more common in the center of the frame, but some are scattered across the frame.
-Qualitatively, the location of these false positives do not look much different than the true positive detections.
-
-```{r density-op-fps, fig.width=6, fig.height=3}
-load(here::here('data/preprocessed_data_2021/gold_sample_all_indiivdual_dets.RData'))
-ddd <- gold_sample_all_dets %>% left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan))
-
-# density plot of OP's false positive face/hand locations
-p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
-  mutate(x=left+0.5*width,
-         y=top-0.5*height) %>% # could actually overplot all the face rectangles? prob very messy...
-  ggplot(aes(x=x, y=y, fill=..level..)) + 
-  stat_density_2d(geom = "polygon") + xlim(-.05,1.1) + ylim(-.1,1.0) + 
-  xlab("Mean x-position of OpenPose Detection") + 
-  ylab("Mean y-position of OpenPose Detection") + 
-  ggtitle("Face False Positives") + theme(legend.position = "none")
-
-p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
-  mutate(x=left+0.5*width,
-         y=top-0.5*height) %>%
-  ggplot(aes(x=x, y=y, fill=..level..)) + 
-  stat_density_2d(geom = "polygon") + xlim(-.05,1.1) + ylim(-.1,1.0) + 
-  xlab("Mean x-position of OpenPose Detection") + 
-  ylab("Mean y-position of OpenPose Detection") + 
-  ggtitle("Hand False Positives") + theme(legend.position = "none")
-
-ggpubr::ggarrange(p1, p2)
-```
-
-# Activity by Location
-
-```{r activities_by_lo, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos."}
-meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))
-
-meta_wide <- meta2 %>% filter(Activity!="N/A", !is.na(Location)) %>%
-  select(Child, `File Name`, Activity, Location) %>%
-  separate(Activity, c("Act.1","Act.2","Act.3","Act.4","Act.5","Act.6","Act.7","Act.8","Act.9","Act.10","Act.11","Act.12"), sep=',') %>%
-  pivot_longer(cols = starts_with("Act."), 
-                                        names_to = "activity_index",
-                                        names_prefix = "Act.",
-                                        values_to = "Activity",
-                                        values_drop_na = T) %>%
-  mutate(Activity = case_when(Activity=="Waving" ~ "Gesturing",
-                              Activity=="Imitation" ~ "Imitating",
-                              Activity=="Talking Walk" ~ "Walking",
-                              Activity=="Tidying" ~ "Cleaning",
-                              Activity=="Preparing for Outing" ~ "Getting Changed/Dressed",
-                              Activity=="Play Pretend" ~ "Playing",
-                              TRUE ~ Activity))
-
-# include videos with multiple locations
-meta_long <- meta_wide %>% 
-  separate(Location, c("Loc.1","Loc.2","Loc.3","Loc.4","Loc.5","Loc.6"), sep=',') %>%
-  pivot_longer(cols = starts_with("Loc."),
-               names_to = "location_index",
-               names_prefix = "Loc.",
-               values_to = "Location",
-               values_drop_na = T)
-
-single_locations = c("Bedroom","Car","Deck/Porch","Kitchen","Living Room","Off Property","Office","Outside on Property")
-
-# single-location videos
-meta_long_1loc <- meta_wide %>%
-  filter(is.element(Location, single_locations)) %>%
-  filter(Activity!="N/A", Activity!="Consequence", Activity!="Gesturing")
-
-# what is "California Room" ?
-meta_long <- meta_long %>% mutate(Location = ifelse(Location=="Bedroom Alice/Sam", "Bedroom", Location))
-
-loc_freq = sort(table(meta_long_1loc$Location))
-
-# multi-location videos
-meta_long %>% filter(Activity!="N/A", Activity!="Consequence", Activity!="Kicking",
-                     Activity!="Gesturing", Activity!="Look and Listen", 
-                     Location!="N/A", Location!="California Room",
-                     Location!="Rapidly Moving Between Locations", Location!="Piano Room") %>%
-  mutate(Location = ifelse(Location=="Dog Park/Park/Field", "Off Property", Location)) %>%
-  group_by(Activity, Location) %>%
-  summarise(n = n()) %>% 
-  ggplot(aes(x=Activity, y=Location, fill=n)) +
-  geom_tile() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-```
-
-```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location in videos taking place in only a single location."}
-# single location videos
-meta_long_1loc %>% 
-  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
-  group_by(Activity, Location) %>%
-  summarise(n = n()) %>% 
-  ggplot(aes(x=Activity, y=Location, fill=n)) +
-  geom_tile() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-#ggsave("activity_by_location.pdf", width=6.5, height=3.5)
-```
-
-```{r, fig.width=6.5, fig.height=3.0, fig.cap="Probability of different activities, given location (in single-location videos)."}
-# normalize by location
-meta_long_1loc %>% 
-  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
-  left_join(meta_long_1loc %>% group_by(Location) %>% summarise(loc_freq = n())) %>%
-  group_by(Activity, Location) %>%
-  summarise(n = n(),
-            prop_loc = n / loc_freq) %>% 
-  ggplot(aes(x=Activity, y=Location, fill=prop_loc)) +
-  geom_tile() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-```
-
-# Motor Milestones Analysis Details
-
-We examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the proportion of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
-
-We tried including random slopes by age and milestone, but the models did not converge and/or were singular.
-Thus, for each milestone the R syntax was: \texttt{prop_faces ~ age * milestone + (1 | child_id)}.Children's age of achieving each milestone was dummy-coded (i.e., 0=milestone not reached; 1=milestone reached).
-
-```{r, get-milestones, echo=F}
-motor <- read_csv(here::here("data","raw_data", "saycam_walking_asq.csv"))
-# A and S are sitting at 6mos
-face_hand_by_age_milestones <- face_hand_by_age %>%
-  mutate(sit = ifelse(child_id=="S" | child_id=="A", 1, 
-                      ifelse(child_id=="Y" & age_day_bin > 8, 1, 0))) %>%
-  mutate(cruise = ifelse((child_id=="S" & age_day_bin >= 9) | 
-                      (child_id=="A" & age_day_bin >= 10) | 
-                      (child_id=="Y" & age_day_bin > 9), 1, 0)) %>%
-  mutate(walk = ifelse((child_id=="S" & age_day_bin > 10) |
-                       (child_id=="A" & age_day_bin > 13) |
-                       (child_id=="Y" & age_day_bin > 16), 1, 0)) %>%
-  mutate(age = age_day_bin)
-
-library(lmerTest)
-# https://rpsychologist.com/r-guide-longitudinal-lme-lmer
-# with random slopes and intercepts ((age_day_bin | child_id): is singular / not converging
-# so we drop random slopes
-
-face_all <- lmer(prop_faces ~ age * (sit + cruise + walk) + (1 | child_id), 
-     data=face_hand_by_age_milestones) 
-#summary(face_all) # cruise+ age:cruise-
-
-hand_all <- lmer(prop_hands ~ age * (sit + cruise + walk) + (1 | child_id), 
-     data=face_hand_by_age_milestones) 
-#summary(hand_all) # cruise+ age:cruise-.
-
-face_sit <- lmer(prop_faces ~ age * sit + (1 | child_id), 
-     data=face_hand_by_age_milestones) 
-hand_sit <- lmer(prop_hands ~ age * sit + (1 | child_id), 
-     data=face_hand_by_age_milestones)
-
-face_cruise <- lmer(prop_faces ~ age * cruise + (1 | child_id), 
-     data=face_hand_by_age_milestones)
-hand_cruise <- lmer(prop_hands ~ age * cruise + (1 | child_id), 
-     data=face_hand_by_age_milestones)
-
-face_walk <- lmer(prop_faces ~ age * walk + (1 | child_id), 
-     data=face_hand_by_age_milestones)
-hand_walk <- lmer(prop_hands ~ age * walk + (1 | child_id), 
-     data=face_hand_by_age_milestones)
-# make models compatible with stargazer
-class(face_sit) <- "lmerMod"
-class(hand_sit) <- "lmerMod"
-class(face_cruise) <- "lmerMod"
-class(hand_cruise) <- "lmerMod"
-class(face_walk) <- "lmerMod"
-class(hand_walk) <- "lmerMod"
-```
-
-## Sitting
-
-Children's age at which they began sitting did not significantly predict changes in either the amount of faces or hands that they saw.
-
-```{r, include=F, results='asis'}
-#summary(face_sit) # ns
-stargazer(face_sit, title="Predicting Faces by Ability to Sit", 
-          header=F, dep.var.labels = "Proportion of Faces")
-
-stargazer(face_sit, hand_sit)
-```
-
-```{r, include=F, results='asis'}
-#summary(hand_sit) # ns
-stargazer(hand_sit, title="Predicting Hands by Ability to Sit", 
-          header=F, dep.var.labels = "Proportion of Hands")
-```
-
-```{r, results='asis'}
-stargazer(face_sit, hand_sit, title="Change in Face and Hand Prevalence by Ability to Sit", 
-          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
-```
-
-## Cruising
-
-As children became able to cruise, they saw significantly more faces ($\beta = 0.27$) and hands ($\beta = 0.26$. 
-For faces, there was a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$).
-
-```{r, include=F, results='asis'}
-#summary(face_cruise) 
-# age+., cruise+*, age*cruise-*
-stargazer(face_cruise, title="Predicting Faces by Ability to Cruise", 
-          header=F, dep.var.labels = "Proportion of Faces")
-```
-
-```{r, include=F}
-f1 <- ggpredict(face_cruise, c("age", "cruise")) %>% plot(add.data=T) +
-  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on faces seen") + 
-  xlab("Age (months)") + ylab("Proportion of faces") + theme_classic()
-
-h1 <- ggpredict(hand_cruise, c("age", "cruise")) %>% plot(add.data=T) +
-  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on hands seen") + 
-  xlab("Age (months)") + ylab("Proportion of hands") + theme_classic()
-
-ggpubr::ggarrange(f1, h1, nrow=1, common.legend=T)
-```
-
-```{r, include=F, results='asis'}
-#summary(hand_cruise) 
-# cruise+*, age*cruise-.
-stargazer(hand_cruise, title="Predicting Hands by Ability to Cruise", 
-          header=F, dep.var.labels = "Proportion of Hands") 
-```
-
-```{r, results='asis'}
-stargazer(face_cruise, hand_cruise, title="Change in Face and Hand Prevalence by Ability to Cruise", 
-          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
-```
-
-## Walking
-
-As children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$).
-
-```{r, include=F, results='asis'}
-#summary(face_walk) # ns
-stargazer(face_walk, title="Predicting Faces by Ability to Walk", 
-          header=F, dep.var.labels = "Proportion of Faces")
-```
-
-```{r, include=F, results='asis'}
-#summary(hand_walk) # walk+.
-stargazer(hand_walk, title="Predicting Hands by Ability to Walk", 
-          header=F, dep.var.labels = "Proportion of Hands")
-```
-
-```{r, results='asis'}
-stargazer(face_walk, hand_walk, title="Change in Face and Hand Prevalence by Ability to Walk", 
-          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
-```

### 2022-01-06 paper/manuscript/manuscript_dec2021_apa_blinded.Rmd
rename writing folder structure

--- 2022-01-06 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
@@
                       fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=F, 
+                      echo=F, warning=F, cache=T, 
                       message=F, sanitize = T)
@@
 ## Face/hand detections by video
-load(file=here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
+load(file=here::here('data/preprocessed_data_2022/all_vid_data_from_bbs_all_detections.RData')) # all detections
 ```
@@
 # load bounding box summaries by video
-load(file=here::here('data/preprocessed_data_2021/bounding_box_summaries_all.RData'))
+load(file=here::here('data/preprocessed_data_2022/bounding_box_summaries_all.RData'))
 ```
@@
 # gold sample annotations for these specific frames
-load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
+load(here::here('data/preprocessed_data_2022/gold_sample_annotations2020-01-31.RData')) # human annotations
 ```
@@
 # load high confidence detections for gold sample frames
-load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_high_conf_detections.RData'))
+load(here::here('data/preprocessed_data_2022/gold_sample_from_bbs_2021_high_conf_detections.RData'))
 all_gold_sample_frames_op_hc = all_gold_sample_frames_op
@@
 # load all detections for gold sample frames
-load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_with_centerall_detections.RData')) 
+load(here::here('data/preprocessed_data_2022/gold_sample_from_bbs_2021_with_centerall_detections.RData')) 
 ```
@@
 ### Examine gold sample performance by child hands
-load(here::here('data/preprocessed_data_2021/child_adult_hand_annotations_by_frame.RData'))
+load(here::here('data/preprocessed_data_2022/child_adult_hand_annotations_by_frame.RData'))
 # 
@@
 Excluding peripehral detections led to an overall f-score of `r round(face_performance_center[3],2)`, for faces with a precision of `r round(face_performance_center[1],2)` and recall of `r round(face_performance_center[2],2)`.
-For hands, the F-score for center detections was `r round(hand_performance)center[3],2)`, with a precision of `r round((hand_performance)[1],2)` and recall of `r round((hand_performance)[2],2)`.
+For hands, the F-score for center detections was `r round(hand_performance_center[3],2)`, with a precision of `r round(hand_performance_center[1],2)` and recall of `r round(hand_performance_center[2],2)`.
 Thus, detections that were made in the periphery of these videos were not more likely to be false alarms for either faces or hands.
@@
   ungroup() %>%
-  tidyr::replace_na(list(faces_and_hands=0)) %>%c
+  tidyr::replace_na(list(faces_and_hands=0)) %>%
   group_by(age_day_bin, child_id) %>%
@@
 How does the social information in view change as a function of motor development?
-One idea is that children’s ability to stand and move on their own may fundamentally change the visual social information that they see (e.g., facial expressions, gaze cues, pointing)  [@walle2016infant] relative to infants who are still sitting and crawling.
+One idea is that children’s ability to stand and move on their own may fundamentally change the visual social information that they see (e.g., facial expressions, gaze cues, pointing)  [@walle2014infant; @walle2016] relative to infants who are still sitting and crawling.
 Indeed, in in-lab studies, children's in-the-moment posture -- and that of their caregiver -- is a strong predictor of the visual social information that children see [@franchak2017see; @long2021automated].
@@
 Of course, these automated detections do not entirely obviate the need for careful inspection and manual annotation of dense video data.
-While the present results suggest that OpenPose achieves moderate performance at detecting faces and hands in infant egocentric videos -- as in @Long2021automated -- these results do not guarantee that OpenPose will generalize with similar accuracy to other video datasets.
+While the present results suggest that OpenPose achieves moderate performance at detecting faces and hands in infant egocentric videos -- as in @long2021automated -- these results do not guarantee that OpenPose will generalize with similar accuracy to other video datasets.
 While OpenPose does provide a considerable amount of about all of the people in a given image -- estimating the entire poses for every individual -- it may not perform accurately enough to answer certain fine-grained research questions.

### 2022-01-06 paper/manuscript/render_annotations.Rmd
rename writing folder structure

---
title: "render_annotations"
author: "Bria Long"
date: "12/22/2021"
output: html_document
---

```{r setup, echo=FALSE}
library(tidyverse)
library(here)
library(ggthemes)
library(magick)
library(viridis)
```

```{r, echo=FALSE}
load(file = here::here('data/preprocessed_data_2021/goldset_category_annotations.RData'))
```

```{r, echo=FALSE}
load(file = here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_all_detections.RData'))

```

```{r}
load(file=here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
bin_size = 7 # days
min_age = min(all_vid_data$age_days, na.rm=TRUE) # 182
max_age = max(all_vid_data$age_days, na.rm=TRUE) # 966
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

```

## Render out child hand examples
```{r}

  child_hands <- d %>%
    filter(child_hand_seg == TRUE)

  public_urls = unique(child_hands$public_url)
  img_names_short = unique(child_hands$img_name)

  dir.create(here::here("data/annotation_examples/child_hands_take2"),recursive = TRUE)

  for (i in 1:length(public_urls)){
    this_image = image_read(public_urls[i])
    image_write(this_image,here::here("data/annotation_examples/child_hands_take2", img_names_short[i]))
  }

```

```{r}
  child_hands <- d %>%
    filter(child_hand_seg == TRUE) %>%
    filter(category=='Food')

  public_urls = unique(child_hands$public_url)
  img_names_short = unique(child_hands$img_name)

  dir.create(here::here("data/annotation_examples/hands_food"),recursive = TRUE)

  for (i in 1:length(public_urls)){
    this_image = image_read(public_urls[i])
    image_write(this_image,here::here("data/annotation_examples/hands_food", img_names_short[i]))
  }
```

```{r}
  hands_toys <- d %>%
    filter(child_hand_seg == TRUE) %>%
    filter(category=='Toy')

  public_urls = unique(hands_toys$public_url)
  img_names_short = unique(hands_toys$img_name)

  dir.create(here::here("data/annotation_examples/hands_toys"),recursive = TRUE)

  for (i in 1:length(public_urls)){
    this_image = image_read(public_urls[i])
    image_write(this_image,here::here("data/annotation_examples/hands_toys", img_names_short[i]))
  }
```

```{r}
  hands_toys <- d %>%
    filter(child_hand_seg == TRUE) %>%
    filter(category=='Toy')

  public_urls = unique(hands_toys$public_url)
  img_names_short = unique(hands_toys$img_name)

  dir.create(here::here("data/annotation_examples/hands_toys"),recursive = TRUE)

  for (i in 1:length(public_urls)){
    this_image = image_read(public_urls[i])
    image_write(this_image,here::here("data/annotation_examples/hands_toys", img_names_short[i]))
  }
```

```{r}
  dishes <- d %>%
    filter(child_hand_seg == TRUE) %>%
    filter(category=='Utensil-Dish')

  public_urls = unique(dishes$public_url)
  img_names_short = unique(dishes$img_name)

  dir.create(here::here("data/annotation_examples/hands_dishes"),recursive = TRUE)

  for (i in 1:length(public_urls)){
    this_image = image_read(public_urls[i])
    image_write(this_image,here::here("data/annotation_examples/hands_dishes", img_names_short[i]))
  }
```

```{r}
ugh_books <- d %>%
  filter(basic_level == 'book') %>%
  group_by(public_url, img_name) %>%
  mutate(book_ok = (category=='Book')) %>%
  filter(book_ok == FALSE)

  public_urls = unique(ugh_books$public_url)
  img_names_short = unique(ugh_books$img_name)

  dir.create(here::here("data/images/annotation_examples/ugh_books"),recursive = TRUE)

  for (i in 1:length(public_urls)){
    this_image = image_read(public_urls[i])
    image_write(this_image,here::here("data/images/annotation_examples/ugh_books", img_names_short[i]))
  }
```

## Render out individual categories
```{r}
reallyRun =0
if (reallyRun){
class_list  = unique(d$category)

for (c in class_list) {
  examples <- d %>%
    filter(category == c) %>%
    dplyr::sample_n(200)

  public_urls = unique(examples$public_url)
  img_names_short = unique(examples$img_name)

  dir.create(here::here("data/annotation_examples/",c),recursive = TRUE)

  for (i in 1:length(public_urls)){
    this_image = image_read(public_urls[i])
    image_write(this_image,here::here("data/annotation_examples/", c, img_names_short[i]))
  }
}
}
```

### 2022-01-06 paper/manuscript/appendix.Rmd
tweaks to figure captions, themes, and sizes

@@
 library(ggeffects)
+
+theme_set(theme_classic())
 
@@
 
-```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 6-31 month-old.
+```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 5-31 months of age.
 Each dot represents the average position from one video within a given age range.", warning=F}
@@
   ggthemes::scale_color_solarized(name = "")  +
-  ggthemes::scale_fill_solarized(name = "") 
+  ggthemes::scale_fill_solarized(name = "") +
+  theme(legend.position = c(0.8, 0.1))
 ```
@@
 
-```{r det_perf_by_age, fig.width=6.5, fig.height=3.2, fig.cap="F-score of OpenPose hand and face detections in the gold sample by child and age. Size indicates number of detections age bin/child."}
+```{r det_perf_by_age, fig.width=6.5, fig.height=3.1, fig.cap="F-score of OpenPose hand and face detections in the gold sample by child and age. Size indicates number of detections age bin/child."}
 
@@
   theme(legend.position= 'none')
-```
 
-```{r}
 ggarrange(p1, p2, nrow=1)
@@
 
-```{r density-op-fps, fig.width=6, fig.height=3}
+```{r density-op-fps, fig.width=6.5, fig.height=3.2, fig.cap="Density plot of the locations of false positives for OpenPose detections for faces (left) and hands (right) in the gold set."}
 load(here::here('data/preprocessed_data_2022/gold_sample_all_indiivdual_dets.RData'))
@@
   stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
-  xlab("Mean x-position of OpenPose Detection") + 
-  ylab("Mean y-position of OpenPose Detection") + 
+  xlab("Center of OpenPose Detection") + 
+  ylab("Center of OpenPose Detection") + 
   ggtitle("Face False Positives") + theme(legend.position = "none") +
@@
   stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
-  xlab("Mean x-position of OpenPose Detection") + 
-  ylab("Mean y-position of OpenPose Detection") + 
+  xlab("Center of OpenPose Detection") + 
+  ylab("Center of OpenPose Detection") + 
   ggtitle("Hand False Positives") + theme(legend.position = "none") +
@@
 
-```{r activities_by_lo, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos."}
+```{r activities_by_lo, fig.width=6.5, fig.height=3.2, fig.cap="Counts of activities by location, including multilocation videos."}
 meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))
@@
   xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on faces seen") + 
-  xlab("Age (months)") + ylab("Proportion of faces") + theme_classic()
+  xlab("Age (months)") + ylab("Proportion of faces")
 
@@
   xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on hands seen") + 
-  xlab("Age (months)") + ylab("Proportion of hands") + theme_classic()
+  xlab("Age (months)") + ylab("Proportion of hands")
 

### 2022-01-06 paper/manuscript/appendix.Rmd
tweaks to appendix formatting

--- 2022-01-06 paper/manuscript/appendix.Rmd
@@
 output:
-  pdf_document: default
+  papaja::apa6_pdf: default
 ---
@@
 We explored where in the visual field children tended to see faces and hands, suspecting that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank (2012).
-As expected, faces tended to appear in the upper visual field in contrast to hands, which tended to be more centrally located (see Figure C1). 
+As expected, faces tended to appear in the upper visual field in contrast to hands, which tended to be more centrally located (see Figure).
 However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ visual environment from 6 months of age.
@@
   ylim(0,1) +
+  theme_few(base_size=12) +
   ylab('F-score') + xlab('Age (months)') +
@@
   geom_point(alpha=.5) +
+  theme_few(base_size=12) +
   ylab('F-score') + ggtitle("Face detections") +
@@
   geom_point(alpha=.5) +
+  theme_few(base_size=12) +
   ylab('F-score') + ggtitle("Hand detections") +
@@
   ggtitle("Face False Positives") + theme(legend.position = "none") +
-  scale_y_reverse()
+  scale_y_reverse() +
+  theme_few(base_size=12)
 
@@
   ggtitle("Hand False Positives") + theme(legend.position = "none") +
-  scale_y_reverse()
+  scale_y_reverse() +
+  theme_few(base_size=12)
 

### 2022-01-06 paper/manuscript/manuscript_dec2021_apa_blinded.Rmd
tweaks to appendix formatting

@@
 keywords          : "social cognition; face perception; infancy; head cameras; deep learning"
-wordcount         : "4681"
+wordcount         : "X"
 
@@
 How does the social information in view change as a function of motor development?
-One idea is that children’s ability to stand and move on their own may fundamentally change the visual social information that they see (e.g., facial expressions, gaze cues, pointing)  [@walle2014infant; @walle2016] relative to infants who are still sitting and crawling.
+One idea is that children’s ability to stand and move on their own may fundamentally change the visual social information that they see (e.g., facial expressions, gaze cues, pointing)  [@walle2014infant; @walle2016infant] relative to infants who are still sitting and crawling.
 Indeed, in in-lab studies, children's in-the-moment posture -- and that of their caregiver -- is a strong predictor of the visual social information that children see [@franchak2017see; @long2021automated].
@@
 ggplot(avg_area_by_age, aes(x=age_day_bin, y=log(avg_area), col=child_id, size=num_detect)) +
+  theme_few(base_size=12) +
   geom_point(alpha=.1) +
@@
 CV_faces_plot <- ggplot(CV_faces, aes(x=age_day_bin, y = CV, size=num_detect, color=child_id)) +
+  theme_few(base_size=12) +
   geom_point(alpha=.15) + 

### 2022-01-07 paper/manuscript/appendix.Rmd
reorder appendix, integrate several google doc changes

@@
----
-title: Appendix to 'Detecting social information in a dense database of infants’ natural
-  visual experience'
-date: "`r Sys.Date()`"
-output:
-  papaja::apa6_pdf: default
----
-
 ```{r, echo=F, message=F}
@@
 library(ggeffects)
-
-theme_set(theme_classic())
-
+library(papaja)
+theme_set(theme_few())
 knitr::opts_chunk$set(echo=F, warning=F, cache=T, 
@@
 load(here::here('data/preprocessed_data_2022/gold_sample_from_bbs_2021_with_centerall_detections.RData')) 
-
-# all_gold_sample_frames_op_hc = load(here::here('data/preprocessed_data_2022/gold_sample_from_bbs_2021_high_conf_detections.RData')) 
 ```
@@
 ```{r}
-## Move to appendix
 ## get out summary by age for goldset hand-labeled frames
@@
 
-# Face/hand detections relative to human annotations
-```{r goldSetSanity, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=4, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset.
-Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range.
-Dashed lines show estimated trend lines from proportion of faces/hands in view when analyzing the gold set of frames made by human annotators.
-Dotted lines show trend lines from the goldset when frames containing children's own hands were excluded." }
+## A1 OpenPose Annotation Examples
+```{r include=FALSE}
+# load(file = here::here('data/preprocessed_data_2022/goldset_category_annotations.RData'))
 
-ggplot(all_detections %>% filter(child_id %in% c('S','A')), 
-       aes(x=age_day_bin, y=prop, 
-           size=log10(num_frames_total),
-           col=region)) +
-  geom_point(alpha=.2) +
-  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
-  geom_smooth(data = goldset_adult_hands, span=10, aes(weight = num_frames_total), show.legend = FALSE,
-              lty = 2, span=10, se = FALSE) +
-  geom_smooth(data = goldset, span=10, aes(weight = num_frames_total), show.legend = FALSE,
-              lty = 3, span=10, se = FALSE) +
-  ylab('Proportion Detections') + 
-  xlab('Age (Months)') +
-  ylim(0,.6) +
-  facet_grid(.~child_id) + 
-  theme_few(base_size=10) +
-  ggthemes::scale_color_solarized(name = "") + 
-  scale_size_continuous(name = "Detections (Log 10)") +
-  theme(legend.text=element_text(size=10)) +
-  theme(legend.position="bottom")
+# fp_face_examples <- d %>%
+#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+#   filter(face_eval_ketan == 'FP')
+# 
+# fp_hand_examples <- d %>%
+#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+#   filter(hand_eval_ketan == 'FP')
+# 
+# fn_face_examples <- d %>%
+#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+#   filter(face_eval_ketan == 'FN')
+# 
+# fn_hand_examples <- d %>%
+#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+#   filter(face_eval_ketan == 'FN')
+# 
+# images_to_render =  fp_hand_examples
+# which_images = 'fp_hand_examples'
+# 
+# public_urls = unique(images_to_render$public_url)
+# img_names_short = unique(images_to_render$img_name)
+# 
+# dir.create(here::here("data/annotation_examples/", which_images),recursive = TRUE)
+# 
+#   for (i in 1:length(public_urls)){
+#     this_image = image_read(public_urls[i])
+#     image_write(this_image,here::here("data/annotation_examples/",which_images, img_names_short[i]))
+#   }
 
@@
 
-# Density of child vs. adults hands in the visual field
+```{r}
+# det_types = c('FP','FN')
+# render_examples = FALSE
+# if (render_examples == TRUE) {
+# for (det_type in det_types) {
+#   to_render_hands <- d %>%
+#     distinct(vid_name, frame, public_url) %>%
+#     left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+#     filter(hand_eval_ketan == det_type) %>%
+#     ungroup() %>%
+#     dplyr::sample_n(7)
+# 
+#   image_read(to_render_hands$public_url) %>%
+#     image_append(stack = FALSE) %>%
+#     image_write(paste0(here::here("data/annotation_examples/"), 'example_hands_', det_type,".png"))
+#   
+#   ###
+#     to_render_faces <- d %>%
+#     distinct(vid_name, frame, public_url) %>%
+#     left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
+#     filter(face_eval_ketan == det_type) %>%
+#     ungroup() %>%
+#     dplyr::sample_n(7)
+# 
+#   image_read(to_render_faces$public_url) %>%
+#     image_append(stack = FALSE) %>%
+#     image_write(paste0(here::here("data/annotation_examples/"), 'example_faces_', det_type,".png"))
+#   
+# }
+# }
 
+```
+
+```{r error_examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=6, set.cap.width=T, num.cols.cap=2,  fig.fullwidth = TRUE, fig.align = "center", fig.cap = "Example false alarms/misses for faces/hands randomly sampled from the larger set of manual annotations."}
+error_examples <- png::readPNG("figs/OP_errors.png")
+grid::grid.raster(error_examples)
+```
+
+## A2 Density of child vs. adults hands in the visual field
 ```{r} 
@@
 
-# Distribution of faces and hands in the visual field
-We explored where in the visual field children tended to see faces and hands, suspecting that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank (2012).
-As expected, faces tended to appear in the upper visual field in contrast to hands, which tended to be more centrally located (see Figure).
-However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ visual environment from 6 months of age.
+## A3 Location of OpenPose False Positives
+Below we visualize the locations of the 1229 faces (in 1093 frames) that OpenPose detected in the gold set frames that were not actually there, as well as the 1778 OpenPose false positive hands (in 1237 frames) from the gold set.
+The average location of OpenPose's false positives for both faces (left) and hands (right) are somewhat more common in the center of the frame, but some are scattered across the frame.
+Qualitatively, the location of these false positives do not look much different than the true positive detections.
 
-```{r}
-bin_size=7
-min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
-max_age = max(all_vid_bbs$age_days, na.rm=TRUE)
-bin_starts = seq(min_age-1, max_age+1,bin_size)
-bins = c(bin_starts, max_age)
+```{r density-op-fps, fig.width=6.5, fig.height=3.2, fig.cap="Density plot of the locations of false positives for OpenPose detections for faces (left) and hands (right) in the gold set."}
+load(here::here('data/preprocessed_data_2022/gold_sample_all_indiivdual_dets.RData'))
+ddd <- gold_sample_all_dets %>% left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan))
 
-all_vid_bbs <- all_vid_bbs %>%
-  mutate(age_months = age_days/30.4) %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=floor(bin_starts/30.4))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
-  mutate(avg_center_y = avg_top + avg_height/2, avg_center_x = avg_left + avg_width/2) %>%
-  filter(num_detect > 100)
+# density plot of OP's false positive face/hand locations
+p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
+  mutate(x=left+0.5*width,
+         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
+  ggplot(aes(x=x, y=y, fill=..level..)) + 
+  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
+  xlab("Center of OpenPose Detection") + 
+  ylab("Center of OpenPose Detection") + 
+  ggtitle("Face False Positives") + theme(legend.position = "none") +
+  scale_y_reverse() +
+  theme_few(base_size=12)
 
+p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
+  mutate(x=left+0.5*width,
+         y=1-(top+0.5*height)) %>% # top-left is 0,0
+  ggplot(aes(x=x, y=y, fill=..level..)) + 
+  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
+  xlab("Center of OpenPose Detection") + 
+  ylab("Center of OpenPose Detection") + 
+  ggtitle("Hand False Positives") + theme(legend.position = "none") +
+  scale_y_reverse() +
+  theme_few(base_size=12)
+
+ggpubr::ggarrange(p1, p2)
 ```
 
-```{r, eval=F, include=F}
-# add back to text when high-conf BBs are processed:
-# We also evaluated OpenPose's performance while restricting detections to high-confidence detections (>.5 confidence, default threshold for visualization). 
-#For faces, we found that the F-score was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`. 
-#For hands, the F-score for high-confidence detections was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
-#Thus, as in prior work [@long2020automated], while precision was much higher for both faces and hands, the lower recall for high-confidence detections indicates that these lower-confidence detections still index the presence of social information in the infant view.
-```
-
-```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 5-31 months of age.
-Each dot represents the average position from one video within a given age range.", warning=F}
-
-ggplot(all_vid_bbs %>% filter(label %in% c('face','hand')), aes(x=avg_center_x , y = avg_center_y, size=num_detect, color=label)) +
-  geom_point(alpha=.3) + 
-  stat_density2d(aes(fill = label, color=label), geom="polygon", alpha=.6) +
-  coord_fixed(ratio=.76) +
-  # ggtitle('Face/hand density') +
-  ylab('') +
-  xlab('') +
-  theme_few(base_size=14) +
-  theme(legend.position="top", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
-  scale_y_reverse() +
-  facet_wrap(~age_day_bin) +
-  guides(size = FALSE) +
-  ggthemes::scale_color_solarized(name = "")  +
-  ggthemes::scale_fill_solarized(name = "") +
-  theme(legend.position = c(0.8, 0.1))
-```
-
-# Detection threshold estimations
+## A4 Detection threshold estimations
 
@@
 
-```{r roc_curves, fig.width=6.5, fig.height=3.2, fig.cap="ROC curves relating the rate of true vs.
+```{r roc_curves, fig.width=6.5, fig.height=3.2, fig.env="figure", fig.cap="ROC curves relating the rate of true vs.
 false positives for both face and hand detections at each level of detector confidence thresholds (lighter values = stricter cutoffs)."}
-ggarrange(face_roc, hand_roc, nrow=1)
+ggpubr::ggarrange(face_roc, hand_roc, nrow=1)
 ```
 
-# OpenPose Error Analyses
+## A5/A6 OpenPose Error Analyses
 ```{r}
@@
 
-```{r det_perf_by_age, fig.width=6.5, fig.height=3.1, fig.cap="F-score of OpenPose hand and face detections in the gold sample by child and age. Size indicates number of detections age bin/child."}
+```{r det_perf_by_age, fig.width=6.5, fig.env="figure", fig.height=3.1, fig.cap="F-score of OpenPose hand and face detections in the gold sample by child and age.
+Size indicates number of detections age bin/child."}
 
@@
 
-ggarrange(p1, p2, nrow=1)
+ggpubr::ggarrange(p1, p2, nrow=1)
 ```
@@
 
-ggarrange(p1, p2, nrow=1)
+ggpubr::ggarrange(p1, p2, nrow=1)
 ```
 
-# OpenPose Annotation Examples
-```{r include=FALSE}
-# load(file = here::here('data/preprocessed_data_2022/goldset_category_annotations.RData'))
+## A7 Face/hand detections relative to human annotations
+```{r goldSetSanity, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=4, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset.
+Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range.
+Dashed lines show estimated trend lines from proportion of faces/hands in view when analyzing the gold set of frames made by human annotators.
+Dotted lines show trend lines from the goldset when frames containing children's own hands were excluded." }
 
-# fp_face_examples <- d %>%
-#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-#   filter(face_eval_ketan == 'FP')
-# 
-# fp_hand_examples <- d %>%
-#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-#   filter(hand_eval_ketan == 'FP')
-# 
-# fn_face_examples <- d %>%
-#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-#   filter(face_eval_ketan == 'FN')
-# 
-# fn_hand_examples <- d %>%
-#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-#   filter(face_eval_ketan == 'FN')
-# 
-# images_to_render =  fp_hand_examples
-# which_images = 'fp_hand_examples'
-# 
-# public_urls = unique(images_to_render$public_url)
-# img_names_short = unique(images_to_render$img_name)
-# 
-# dir.create(here::here("data/annotation_examples/", which_images),recursive = TRUE)
-# 
-#   for (i in 1:length(public_urls)){
-#     this_image = image_read(public_urls[i])
-#     image_write(this_image,here::here("data/annotation_examples/",which_images, img_names_short[i]))
-#   }
+ggplot(all_detections %>% filter(child_id %in% c('S','A')), 
+       aes(x=age_day_bin, y=prop, 
+           size=log10(num_frames_total),
+           col=region)) +
+  geom_point(alpha=.2) +
+  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
+  geom_smooth(data = goldset_adult_hands, span=10, aes(weight = num_frames_total), show.legend = FALSE,
+              lty = 2, span=10, se = FALSE) +
+  geom_smooth(data = goldset, span=10, aes(weight = num_frames_total), show.legend = FALSE,
+              lty = 3, span=10, se = FALSE) +
+  ylab('Proportion Detections') + 
+  xlab('Age (Months)') +
+  ylim(0,.6) +
+  facet_grid(.~child_id) + 
+  theme_few(base_size=10) +
+  ggthemes::scale_color_solarized(name = "") + 
+  scale_size_continuous(name = "Detections (Log 10)") +
+  theme(legend.text=element_text(size=10)) +
+  theme(legend.position="bottom")
 
@@
 
-```{r}
-# det_types = c('FP','FN')
-# render_examples = FALSE
-# if (render_examples == TRUE) {
-# for (det_type in det_types) {
-#   to_render_hands <- d %>%
-#     distinct(vid_name, frame, public_url) %>%
-#     left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-#     filter(hand_eval_ketan == det_type) %>%
-#     ungroup() %>%
-#     dplyr::sample_n(7)
-# 
-#   image_read(to_render_hands$public_url) %>%
-#     image_append(stack = FALSE) %>%
-#     image_write(paste0(here::here("data/annotation_examples/"), 'example_hands_', det_type,".png"))
-#   
-#   ###
-#     to_render_faces <- d %>%
-#     distinct(vid_name, frame, public_url) %>%
-#     left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-#     filter(face_eval_ketan == det_type) %>%
-#     ungroup() %>%
-#     dplyr::sample_n(7)
-# 
-#   image_read(to_render_faces$public_url) %>%
-#     image_append(stack = FALSE) %>%
-#     image_write(paste0(here::here("data/annotation_examples/"), 'example_faces_', det_type,".png"))
-#   
-# }
-# }
-
-```
-
-```{r error_examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=6, set.cap.width=T, num.cols.cap=2,  fig.fullwidth = TRUE, fig.align = "center", fig.cap = "Example false alarms/misses for faces/hands randomly sampled from the larger set of manual annotations."}
-error_examples <- png::readPNG("figs/OP_errors.png")
-grid::grid.raster(error_examples)
-```
-
-## Location of OpenPose False Positives
-
-Below we visualize the locations of the 1229 faces (in 1093 frames) that OpenPose detected in the gold set frames that were not actually there, as well as the 1778 OpenPose false positive hands (in 1237 frames) from the gold set.
-The average location of OpenPose's false positives for both faces (left) and hands (right) are somewhat more common in the center of the frame, but some are scattered across the frame.
-Qualitatively, the location of these false positives do not look much different than the true positive detections.
-
-```{r density-op-fps, fig.width=6.5, fig.height=3.2, fig.cap="Density plot of the locations of false positives for OpenPose detections for faces (left) and hands (right) in the gold set."}
-load(here::here('data/preprocessed_data_2022/gold_sample_all_indiivdual_dets.RData'))
-ddd <- gold_sample_all_dets %>% left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan))
-
-# density plot of OP's false positive face/hand locations
-p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
-  mutate(x=left+0.5*width,
-         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
-  ggplot(aes(x=x, y=y, fill=..level..)) + 
-  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
-  xlab("Center of OpenPose Detection") + 
-  ylab("Center of OpenPose Detection") + 
-  ggtitle("Face False Positives") + theme(legend.position = "none") +
-  scale_y_reverse() +
-  theme_few(base_size=12)
-
-p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
-  mutate(x=left+0.5*width,
-         y=1-(top+0.5*height)) %>% # top-left is 0,0
-  ggplot(aes(x=x, y=y, fill=..level..)) + 
-  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
-  xlab("Center of OpenPose Detection") + 
-  ylab("Center of OpenPose Detection") + 
-  ggtitle("Hand False Positives") + theme(legend.position = "none") +
-  scale_y_reverse() +
-  theme_few(base_size=12)
-
-ggpubr::ggarrange(p1, p2)
-```
-
-# Activity by Location
-
-```{r activities_by_lo, fig.width=6.5, fig.height=3.2, fig.cap="Counts of activities by location, including multilocation videos."}
-meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))
-
-meta_wide <- meta2 %>% filter(Activity!="N/A", !is.na(Location)) %>%
-  select(Child, `File Name`, Activity, Location) %>%
-  separate(Activity, c("Act.1","Act.2","Act.3","Act.4","Act.5","Act.6","Act.7","Act.8","Act.9","Act.10","Act.11","Act.12"), sep=',') %>%
-  pivot_longer(cols = starts_with("Act."), 
-                                        names_to = "activity_index",
-                                        names_prefix = "Act.",
-                                        values_to = "Activity",
-                                        values_drop_na = T) %>%
-  mutate(Activity = case_when(Activity=="Waving" ~ "Gesturing",
-                              Activity=="Imitation" ~ "Imitating",
-                              Activity=="Talking Walk" ~ "Walking",
-                              Activity=="Tidying" ~ "Cleaning",
-                              Activity=="Preparing for Outing" ~ "Getting Changed/Dressed",
-                              Activity=="Play Pretend" ~ "Playing",
-                              TRUE ~ Activity))
-
-# include videos with multiple locations
-meta_long <- meta_wide %>% 
-  separate(Location, c("Loc.1","Loc.2","Loc.3","Loc.4","Loc.5","Loc.6"), sep=',') %>%
-  pivot_longer(cols = starts_with("Loc."),
-               names_to = "location_index",
-               names_prefix = "Loc.",
-               values_to = "Location",
-               values_drop_na = T)
-
-single_locations = c("Bedroom","Car","Deck/Porch","Kitchen","Living Room","Off Property","Office","Outside on Property")
-
-# single-location videos
-meta_long_1loc <- meta_wide %>%
-  filter(is.element(Location, single_locations)) %>%
-  filter(Activity!="N/A", Activity!="Consequence", Activity!="Gesturing")
-
-# what is "California Room" ?
-meta_long <- meta_long %>% mutate(Location = ifelse(Location=="Bedroom Alice/Sam", "Bedroom", Location))
-
-loc_freq = sort(table(meta_long_1loc$Location))
-
-# multi-location videos
-meta_long %>% filter(Activity!="N/A", Activity!="Consequence", Activity!="Kicking",
-                     Activity!="Gesturing", Activity!="Look and Listen", 
-                     Location!="N/A", Location!="California Room",
-                     Location!="Rapidly Moving Between Locations", Location!="Piano Room") %>%
-  mutate(Location = ifelse(Location=="Dog Park/Park/Field", "Off Property", Location)) %>%
-  group_by(Activity, Location) %>%
-  summarise(n = n()) %>% 
-  ggplot(aes(x=Activity, y=Location, fill=n)) +
-  geom_tile() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-```
-
-```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location in videos taking place in only a single location."}
-# single location videos
-meta_long_1loc %>% 
-  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
-  group_by(Activity, Location) %>%
-  summarise(n = n()) %>% 
-  ggplot(aes(x=Activity, y=Location, fill=n)) +
-  geom_tile() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-#ggsave("activity_by_location.pdf", width=6.5, height=3.5)
-```
-
-```{r, fig.width=6.5, fig.height=3.0, fig.cap="Probability of different activities, given location (in single-location videos)."}
-# normalize by location
-meta_long_1loc %>% 
-  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
-  left_join(meta_long_1loc %>% group_by(Location) %>% summarise(loc_freq = n())) %>%
-  group_by(Activity, Location) %>%
-  summarise(n = n(),
-            prop_loc = n / loc_freq) %>% 
-  ggplot(aes(x=Activity, y=Location, fill=prop_loc)) +
-  geom_tile() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-```
-
-# Motor Milestones Analysis Details
+## Tables 1&2 Motor Milestones Analysis Details
 
@@
 
-## Sitting
+### Sitting
 
@@
 
-## Cruising
+### Cruising
 
@@
 
-## Walking
+### Walking
 
@@
 ```
+
+## A8 Activity by Location
+
+```{r}
+meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))
+
+meta_wide <- meta2 %>% filter(Activity!="N/A", !is.na(Location)) %>%
+  select(Child, `File Name`, Activity, Location) %>%
+  separate(Activity, c("Act.1","Act.2","Act.3","Act.4","Act.5","Act.6","Act.7","Act.8","Act.9","Act.10","Act.11","Act.12"), sep=',') %>%
+  pivot_longer(cols = starts_with("Act."), 
+                                        names_to = "activity_index",
+                                        names_prefix = "Act.",
+                                        values_to = "Activity",
+                                        values_drop_na = T) %>%
+  mutate(Activity = case_when(Activity=="Waving" ~ "Gesturing",
+                              Activity=="Imitation" ~ "Imitating",
+                              Activity=="Talking Walk" ~ "Walking",
+                              Activity=="Tidying" ~ "Cleaning",
+                              Activity=="Preparing for Outing" ~ "Getting Changed/Dressed",
+                              Activity=="Play Pretend" ~ "Playing",
+                              TRUE ~ Activity))
+
+# include videos with multiple locations
+meta_long <- meta_wide %>% 
+  separate(Location, c("Loc.1","Loc.2","Loc.3","Loc.4","Loc.5","Loc.6"), sep=',') %>%
+  pivot_longer(cols = starts_with("Loc."),
+               names_to = "location_index",
+               names_prefix = "Loc.",
+               values_to = "Location",
+               values_drop_na = T)
+
+single_locations = c("Bedroom","Car","Deck/Porch","Kitchen","Living Room","Off Property","Office","Outside on Property")
+
+# single-location videos
+meta_long_1loc <- meta_wide %>%
+  filter(is.element(Location, single_locations)) %>%
+  filter(Activity!="N/A", Activity!="Consequence", Activity!="Gesturing")
+
+# what is "California Room" ?
+meta_long <- meta_long %>% mutate(Location = ifelse(Location=="Bedroom Alice/Sam", "Bedroom", Location))
+
+loc_freq = sort(table(meta_long_1loc$Location))
+
+```
+
+```{r activities_by_lo, fig.width=6.5, fig.height=3.2, fig.cap="Counts of activities by location, including multilocation videos."}
+
+# multi-location videos
+meta_long %>% filter(Activity!="N/A", Activity!="Consequence", Activity!="Kicking",
+                     Activity!="Gesturing", Activity!="Look and Listen", 
+                     Location!="N/A", Location!="California Room",
+                     Location!="Rapidly Moving Between Locations", Location!="Piano Room") %>%
+  mutate(Location = ifelse(Location=="Dog Park/Park/Field", "Off Property", Location)) %>%
+  group_by(Activity, Location) %>%
+  summarise(n = n()) %>% 
+  ggplot(aes(x=Activity, y=Location, fill=n)) +
+  geom_tile() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+```
+
+```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location in videos taking place in only a single location."}
+# single location videos
+meta_long_1loc %>% 
+  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
+  group_by(Activity, Location) %>%
+  summarise(n = n()) %>% 
+  ggplot(aes(x=Activity, y=Location, fill=n)) +
+  geom_tile() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+#ggsave("activity_by_location.pdf", width=6.5, height=3.5)
+```
+
+```{r, fig.width=6.5, fig.height=3.0, fig.cap="Probability of different activities, given location (in single-location videos)."}
+# normalize by location
+meta_long_1loc %>% 
+  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
+  left_join(meta_long_1loc %>% group_by(Location) %>% summarise(loc_freq = n())) %>%
+  group_by(Activity, Location) %>%
+  summarise(n = n(),
+            prop_loc = n / loc_freq) %>% 
+  ggplot(aes(x=Activity, y=Location, fill=prop_loc)) +
+  geom_tile() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+## A9 Distribution of faces and hands in the visual field
+We explored where in the visual field children tended to see faces and hands, suspecting that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank (2012).
+As expected, faces tended to appear in the upper visual field in contrast to hands, which tended to be more centrally located (see Figure).
+However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ visual environment from 6 months of age.
+
+```{r}
+bin_size=7
+min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
+max_age = max(all_vid_bbs$age_days, na.rm=TRUE)
+bin_starts = seq(min_age-1, max_age+1,bin_size)
+bins = c(bin_starts, max_age)
+
+all_vid_bbs <- all_vid_bbs %>%
+  mutate(age_months = age_days/30.4) %>%
+  mutate(age_day_bin = cut(age_days, bins, labels=floor(bin_starts/30.4))) %>%
+  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
+  mutate(avg_center_y = avg_top + avg_height/2, avg_center_x = avg_left + avg_width/2) %>%
+  filter(num_detect > 100)
+
+```
+
+```{r, eval=F, include=F}
+# add back to text when high-conf BBs are processed:
+# We also evaluated OpenPose's performance while restricting detections to high-confidence detections (>.5 confidence, default threshold for visualization). 
+#For faces, we found that the F-score was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`. 
+#For hands, the F-score for high-confidence detections was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
+#Thus, as in prior work [@long2020automated], while precision was much higher for both faces and hands, the lower recall for high-confidence detections indicates that these lower-confidence detections still index the presence of social information in the infant view.
+```
+
+```{r faceHandDensity, fig.env="figure", fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 5-31 months of age.
+Each dot represents the average position from one video within a given age range.", warning=F}
+
+ggplot(all_vid_bbs %>% filter(label %in% c('face','hand')), aes(x=avg_center_x , y = avg_center_y, size=num_detect, color=label)) +
+  geom_point(alpha=.3) + 
+  stat_density2d(aes(fill = label, color=label), geom="polygon", alpha=.6) +
+  coord_fixed(ratio=.76) +
+  # ggtitle('Face/hand density') +
+  ylab('') +
+  xlab('') +
+  theme_few(base_size=14) +
+  theme(legend.position="top", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
+  scale_y_reverse() +
+  facet_wrap(~age_day_bin) +
+  guides(size = FALSE) +
+  ggthemes::scale_color_solarized(name = "")  +
+  ggthemes::scale_fill_solarized(name = "") +
+  theme(legend.position = c(0.8, 0.1))
+```

### 2022-01-07 paper/manuscript/manuscript_dec2021_apa_blinded.Rmd
reorder appendix, integrate several google doc changes

@@
 ---
-title             : "A longitudinal analysis of the social information in infants' naturalistic visual experience using automated detections"
-shorttitle        : "Longitudinal analysis of social information"
-
+title: A longitudinal analysis of the social information in infants' naturalistic
+  visual experience using automated detections
 author:
-  - name          : "Blinded"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : ""
-    email         : " "
-  - name          : " "
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Blinded"
-
-authornote: |
-  The data and code that support the findings of this study are available at https://osf.io/cdhw4/.
-
+- name: Blinded
+  affiliation: '1'
+  corresponding: yes
+  address: ''
+  email: ' '
+- name: ' '
+  affiliation: '1'
+shorttitle: Longitudinal analysis of social information
+output: papaja::apa6_docx
+authornote: "The data and code that support the findings of this study are available
+  at https://osf.io/cdhw4/. \n"
 abstract: |
@@
 These analyses provide new insight into the changes in the social information in view across the first few years of life and call for further work that examines their generalizability across populations and their relationship to learning outcomes.
-
-keywords          : "social cognition; face perception; infancy; head cameras; deep learning"
-wordcount         : "X"
-
-bibliography      : ["library.bib"]
-
-floatsintext      : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : no
-mask              : no
-draft             : no
-
-documentclass     : "apa6"
-classoption       : "man"
-output            : 
-  papaja::apa6_docx:
-    includes:
-      after_body: "appendix.tex"
+keywords: social cognition; face perception; infancy; head cameras; deep learning
+wordcount: X
+bibliography: library.bib
+floatsintext: yes
+figurelist: no
+tablelist: no
+footnotelist: no
+linenumbers: no
+mask: no
+draft: no
+documentclass: apa6
+classoption: man
+affiliation:
+- id: '1'
+  institution: Blinded
+
 ---
@@
                       fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=T, 
+                      echo=F, warning=F, cache=F, 
                       message=F, sanitize = T)
@@
 By equipping infants and toddlers with head-mounted cameras, researchers have begun to document the infant's egocentric perspective on the world [@smith2015contributions; @smith2018developing; @franchak2011] and the consequences of this changing view for early learning.
-Using these methods, a growing body of work now demonstrates that the viewpoints of very young infants (less than 4 months of age) are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @jayaraman2013visual; @jayaraman2017faces; @Sugden2014; @Jayaraman2018].
+Using these methods, a growing body of work now demonstrates that the viewpoints of very young infants (less than 4 months of age) are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @jayaraman2013visual; @jayaraman2017faces; @sugden2014spy; @Jayaraman2018].
 
@@
 These kinds of longitudinal case studies provide an important counterpoint to cross-sectional investigations for several reasons.
-By repeatedly recording data from the same child, they allow us to investigate developmental changes within each child and to relate these to developmental milestones (e.g., the onset of walking).
-Second, they eliminate several nuance sources of variability (e.g., parent/child familiarity with camera, home environment) that may obscure fine-grained developmental patterns.
+By repeatedly recording data from the same child, they allow us to investigate developmental changes within each child, avoiding the ecological fallacy of assuming that between-person patterns reflect within-person mechanisms [@piantadosi1988ecological].
+Second, they allow us to relate developmental changes to milestones achieved by an individual child (e.g., the onset of walking).
+Second, they eliminate several sources of variability (e.g., parent/child familiarity with camera, home environment) that may obscure fine-grained developmental patterns.
 
@@
 Even in other naturalistic datasets, the incredible variety in a typical infant's experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth).
-Second, the head-mounted cameras used in the SAYCam dataset captured a larger field of view than those typically used, allowing a more complete picture of the infant perspective.
+Second, the head-mounted camera devices used in the SAYCam dataset captured a larger field of view than those typically used, allowing a more complete picture of the infant perspective.
 While head-mounted cameras with a more restricted field of view do represent where infants are foveating most of the time [@yoshida2008; @smith2015contributions], they may fail when faces or hands appear in children's peripheral vision but are still part of a joint interaction.
 
-However, it is important to note that these data -- albeit naturalistic and densely sampled within individuals -- come from only a few children in western contexts [@@henrich2010most], and as such cannot on their own yield generalizable conclusions about developmental changes in the infant view.
-Instead, they serve as a testbed for validating prior developmental findings within the daily lives of individual children -- and for generating novel hypotheses that can be tested in cross-sectional datasets or targeted in-lab experiments.
-
-With hundreds of hours of footage (>42M frames), however, this large dataset necessitates a shift to an automated annotation strategy.
+However, the SAYCam data – while naturalistic and densely sampled within individuals – come from only a handful of children.
+These are a group of three children of developmental psychologists growing up in US contexts that conform to the WEIRD rubric [@henrich2010most] for numerous reasons they cannot on their own yield generalizable conclusions about developmental changes in the infant view.
+Instead, they serve as a testbed for validating prior developmental findings within the daily lives of individual children – and for generating novel hypotheses that can be tested in cross-sectional datasets or targeted in-lab experiments.
+
+With hundreds of hours of footage (>42M frames), this large dataset necessitates a shift to an automated annotation strategy.
 Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that most frames are typically not inspected, even in the most comprehensive studies. 
@@
 We next inspected frames where OpenPose failed to detect faces/hands or erroneously detected them to gain insight into the factors driving performance.
-Appendix Figure \ref{fig:error_examples} shows randomly sampled examples of both missed detections and false alarms for both faces and hands and highlights the challenging detection conditions presented by these at-home, naturalistic videos.
+Appendix Figure A1 shows randomly sampled examples of both missed detections and false alarms for both faces and hands and highlights the challenging detection conditions presented by these at-home, naturalistic videos.
 Many missed faces included very far away or very close up views of faces at odd angles, as well as faces that were partially occluded by odd lighting conditions.
@@
 Hands were sometimes erroneously detected when a pose was present but the hands were out of view, and hands were often missed when they were seen only from the side and unconnected to a pose or belonged to the child.
+One conclusion of this examination is that egocentric videos using cameras with larger view angles, higher resolution, and more lighting-invariant sensors may lead to better performance, even in the absence of better detection models.
 
@@
 Accordingly, when frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`.
-We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Appendix Figure \ref{fig:handLocation}.
+We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Appendix Figure A2.
 
@@
 Thus, detections that were made in the periphery of these videos were not more likely to be false alarms for either faces or hands.
-Appendix Figure \ref{fig: density-op-fps} illustrates this finding, showing the density of false positives for both faces and hands that are concentrated in the center of the fied of view.
+Appendix Figure A3 illustrates this finding, showing the density of false positives for both faces and hands that are concentrated in the center of the fied of view.
 
@@
 When we restricted detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
-Further analyses sweeping across the entire range of possible confidence detection thresholds revealed that including all detections was the most beneficial for optimizing the rate of true positives (see Appendix Figure \ref{fig:roc_curves} for full ROC curves for both face and hand detections).
+Further analyses sweeping across the entire range of possible confidence detection thresholds revealed that including all detections was the most beneficial for optimizing the rate of true positives (see Appendix Figure A4 for full ROC curves for both face and hand detections).
 
@@
 living room).
-Some of the videos at taken at older ages for child A did seem to show lower hand detection accuracy, perhaps due the presence of child's hands; however, there were also fewer videos at these time points (see plots for age/child in Appendix, Figure \ref{fig:det_perf_by_age}).
-We did not find any discernible trends in face/hand detection accuracy across different filming locations (see Figure \ref{fig:det_perf_by_locations}).
+Some of the videos at taken at older ages for child A did seem to show lower hand detection accuracy, perhaps due the presence of child's hands; however, there were also fewer videos at these time points (see plots for age/child in Appendix, Figure A5).
+We did not find any discernible trends in face/hand detection accuracy across different filming locations (see Figure A6).
 However, we did still see considerable variation in model accuracy across different videos, suggesting that particular recording activities, lighting conditions, or situations could cause conditions that would impair detector performance.
@@
 However, the most striking result from these analyses is a much greater overall proportion of hands in view than has previously been reported [@Fausey2016].
-We found this observation to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Appendix Figure \ref{fig:goldSetSanity}) or OpenPose annotations on the entire dataset (see Figure \ref{fig:faceHandDetailed}A).
+We found this observation to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Appendix Figure A7) or OpenPose annotations on the entire dataset (see Figure \ref{fig:faceHandDetailed}A).
 This finding is notable especially given that OpenPose showed relatively low recall for hands, indicating that our measurements may in fact be an underestimate of the proportion of hands in view.
@@
 
-As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, and decreasing face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%.
-This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure Appendix \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view.
+As we found that children's hands tended to occur in the lower visual field (see Appendix Figure A2), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, and decreasing face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%.
+This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure Appendix A2), especially as OpenPose was biased to miss children's hands when they were in view.
 Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}).
-We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure \ref{fig:goldSetSanity}).
+We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure A7).
 
 Finally, we analyzed how these two sources of social information co-occurred.
-To do so, wecalculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range.
+To do so, we calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range.
 Faces and hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}C).
@@
 We then used a discontinuity analysis to estimate whether the onset of each of these three motor milestones changed the proportion of faces/hands in each chid's view.
-Specifically, we used mixed-effects regressions with per-child random intercepts to estimate whether children's age (in months), each motor milestone, and their interaction significantly influenced the proportion of hands or faces that each child saw; see Appendix for tables with full model specifications and tables with all coefficients.
+Specifically, we used mixed-effects regressions with per-child random intercepts to estimate whether children's age (in months), each motor milestone, and their interaction significantly influenced the proportion of hands or faces that each child saw; see Appendix Tables A1-3 for full model specifications and tables with all coefficients.
 Overall, we found that the age at which these children began sitting did not significantly predict changes in either the amount of faces or hands that they saw.
@@
 In our viewing of the SAYCam videos and in other annotations available with the dataset, activities varied somewhat predictably by location: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.
-However, every location was associated with multiple activities; see Appendix Figure \ref{fig:activities_by_loc} for a heatmap relating individual activities to locations in the dataset.
+However, every location was associated with multiple activities; see Appendix Figure A8 for a heatmap relating individual activities to locations in the dataset.
 Of the `r num_videos` videos in the dataset, `r num_videos_annotated` were annotated for the location or locations they were filmed in. 
@@
 Finally, we also examined whether there were changes in where faces tended to appear in the camera's (and hence, by proxy, the child's) field of view. 
-As expected, faces tended to be located towards the upper field of view, while views of hands were more centrally distributed (see Appendix, Figure \ref{fig:faceHandDensity} for average density distributions).
+As expected, faces tended to be located towards the upper field of view, while views of hands were more centrally distributed (see Appendix, Figure A9 for average density distributions). 
 However, we also found evidence that older children tended to see more faces in more variable positions than younger children. 
@@
 
-```{r appendix, include = FALSE}
-render_appendix("appendix.Rmd")
-```
-
 # References

### 2022-01-07 paper/manuscript/manuscript_dec2021_apa_blinded.Rmd
manual call outs to appendix figures

@@
 In this paper, we first validate the use of OpenPose by comparing face and hand detections to a human-annotated set of 24,000 frames.
-Though OpenPose does not detect faces and hands with perfect accuracy, we find that this model still operates relatively well on these challenging egocentric scenes including multiple people, even if they are partially-occluded (see Figure 1 for example detections and Appendix Figure \ref{fig:error_examples} for examples of missed detections and false alarms).
+Though OpenPose does not detect faces and hands with perfect accuracy, we find that this model still operates relatively well on these challenging egocentric scenes including multiple people, even if they are partially-occluded (see Figure 1 for example detections and Appendix Figure A1 for examples of missed detections and false alarms).
 

### 2022-01-07 paper/manuscript/appendix.Rmd
add sep file for motor milestone attempt?

@@
+---
+title: "Appendix"
+author: "Bria Long"
+date: "1/6/2022"
+output: word_document
+---
+
 ```{r, echo=F, message=F}
@@
 
-## Tables 1&2 Motor Milestones Analysis Details
-
-We examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the proportion of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
-
-We tried including random slopes by age and milestone, but the models did not converge and/or were singular.
-Thus, for each milestone the R syntax was: \texttt{prop_faces ~ age * milestone + (1 | child_id)}.Children's age of achieving each milestone was dummy-coded (i.e., 0=milestone not reached; 1=milestone reached).
-
-```{r, get-milestones, echo=F}
-motor <- read_csv(here::here("data","raw_data", "saycam_walking_asq.csv"))
-# A and S are sitting at 6mos
-face_hand_by_age_milestones <- face_hand_by_age %>%
-  mutate(sit = ifelse(child_id=="S" | child_id=="A", 1, 
-                      ifelse(child_id=="Y" & age_day_bin > 8, 1, 0))) %>%
-  mutate(cruise = ifelse((child_id=="S" & age_day_bin >= 9) | 
-                      (child_id=="A" & age_day_bin >= 10) | 
-                      (child_id=="Y" & age_day_bin > 9), 1, 0)) %>%
-  mutate(walk = ifelse((child_id=="S" & age_day_bin > 10) |
-                       (child_id=="A" & age_day_bin > 13) |
-                       (child_id=="Y" & age_day_bin > 16), 1, 0)) %>%
-  mutate(age = age_day_bin)
-
-library(lmerTest)
-# https://rpsychologist.com/r-guide-longitudinal-lme-lmer
-# with random slopes and intercepts ((age_day_bin | child_id): is singular / not converging
-# so we drop random slopes
-
-face_all <- lmer(prop_faces ~ age * (sit + cruise + walk) + (1 | child_id), 
-     data=face_hand_by_age_milestones) 
-#summary(face_all) # cruise+ age:cruise-
-
-hand_all <- lmer(prop_hands ~ age * (sit + cruise + walk) + (1 | child_id), 
-     data=face_hand_by_age_milestones) 
-#summary(hand_all) # cruise+ age:cruise-.
-
-face_sit <- lmer(prop_faces ~ age * sit + (1 | child_id), 
-     data=face_hand_by_age_milestones) 
-hand_sit <- lmer(prop_hands ~ age * sit + (1 | child_id), 
-     data=face_hand_by_age_milestones)
-
-face_cruise <- lmer(prop_faces ~ age * cruise + (1 | child_id), 
-     data=face_hand_by_age_milestones)
-hand_cruise <- lmer(prop_hands ~ age * cruise + (1 | child_id), 
-     data=face_hand_by_age_milestones)
-
-face_walk <- lmer(prop_faces ~ age * walk + (1 | child_id), 
-     data=face_hand_by_age_milestones)
-hand_walk <- lmer(prop_hands ~ age * walk + (1 | child_id), 
-     data=face_hand_by_age_milestones)
-# make models compatible with stargazer
-class(face_sit) <- "lmerMod"
-class(hand_sit) <- "lmerMod"
-class(face_cruise) <- "lmerMod"
-class(hand_cruise) <- "lmerMod"
-class(face_walk) <- "lmerMod"
-class(hand_walk) <- "lmerMod"
-```
-
-### Sitting
-
-Children's age at which they began sitting did not significantly predict changes in either the amount of faces or hands that they saw.
-
-```{r, include=F, results='asis'}
-#summary(face_sit) # ns
-stargazer(face_sit, title="Predicting Faces by Ability to Sit", 
-          header=F, dep.var.labels = "Proportion of Faces")
-
-stargazer(face_sit, hand_sit)
-```
-
-```{r, include=F, results='asis'}
-#summary(hand_sit) # ns
-stargazer(hand_sit, title="Predicting Hands by Ability to Sit", 
-          header=F, dep.var.labels = "Proportion of Hands")
-```
-
-```{r, results='asis'}
-stargazer(face_sit, hand_sit, title="Change in Face and Hand Prevalence by Ability to Sit", 
-          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
-```
-
-### Cruising
-
-As children became able to cruise, they saw significantly more faces ($\beta = 0.27$) and hands ($\beta = 0.26$. 
-For faces, there was a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$).
-
-```{r, include=F, results='asis'}
-#summary(face_cruise) 
-# age+., cruise+*, age*cruise-*
-stargazer(face_cruise, title="Predicting Faces by Ability to Cruise", 
-          header=F, dep.var.labels = "Proportion of Faces")
-```
-
-```{r, include=F}
-f1 <- ggpredict(face_cruise, c("age", "cruise")) %>% plot(add.data=T) +
-  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on faces seen") + 
-  xlab("Age (months)") + ylab("Proportion of faces")
-
-h1 <- ggpredict(hand_cruise, c("age", "cruise")) %>% plot(add.data=T) +
-  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on hands seen") + 
-  xlab("Age (months)") + ylab("Proportion of hands")
-
-ggpubr::ggarrange(f1, h1, nrow=1, common.legend=T)
-```
-
-```{r, include=F, results='asis'}
-#summary(hand_cruise) 
-# cruise+*, age*cruise-.
-stargazer(hand_cruise, title="Predicting Hands by Ability to Cruise", 
-          header=F, dep.var.labels = "Proportion of Hands") 
-```
-
-```{r, results='asis'}
-stargazer(face_cruise, hand_cruise, title="Change in Face and Hand Prevalence by Ability to Cruise", 
-          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
-```
-
-### Walking
-
-As children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$).
-
-```{r, include=F, results='asis'}
-#summary(face_walk) # ns
-stargazer(face_walk, title="Predicting Faces by Ability to Walk", 
-          header=F, dep.var.labels = "Proportion of Faces")
-```
-
-```{r, include=F, results='asis'}
-#summary(hand_walk) # walk+.
-stargazer(hand_walk, title="Predicting Hands by Ability to Walk", 
-          header=F, dep.var.labels = "Proportion of Hands")
-```
-
-```{r, results='asis'}
-stargazer(face_walk, hand_walk, title="Change in Face and Hand Prevalence by Ability to Walk", 
-          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
-```
-
 ## A8 Activity by Location

### 2022-01-07 paper/manuscript/motor_milestones_attempt.Rmd
add sep file for motor milestone attempt?

--- 2022-01-06 paper/preprint/appendix.Rmd
@@
 ---
-title: Appendix to 'Detecting social information in a dense database of infants’ natural
-  visual experience'
-date: "`r Sys.Date()`"
-output:
-  pdf_document: default
+title: "motor_milestone_attempt"
+author: "Bria Long"
+date: "1/6/2022"
+output: html_document
 ---
@@
 library(ggeffects)
-
-knitr::opts_chunk$set(echo=F, warning=F, cache=F, 
+library(papaja)
+theme_set(theme_few())
+knitr::opts_chunk$set(echo=F, warning=F, cache=T, 
                       message=F, sanitize = T)
@@
 
-```{r}
-## Read in preprocessed data 
-load(here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
+## Motor Milestones Analysis 
+Each parent in the SAYCam dataset completed the Ages and Stages Questionnaire (ASQ), which includes questions about their child's motor abilities, and we used the responses from this questionnaire to code the age (in months) at which each child became able to sit, cruise, and walk on their own (questions about crawling were not included in the questionnaire).
+We found considerable variability in the age at which each child achieved these three milestones.
+Participants S and A were already able to sit at 6 months of age, while Y began achieving this milestone at 8 months.
+A was able to cruise at 9 months of age, while S reached that milestone at 10 months, with Y just behind.
+Learning to walk showed the most variation, with S walking after 10 months, A after 13 months, and Y after 16 months of age.
 
-## all bounding boxes
-load(file=here::here('data/preprocessed_data_2021/bounding_box_summaries.RData'))
+We attempted to whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the proportion of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
+We tried including random slopes by age and milestone, but the models did not converge and/or were singular.
+Thus, for each milestone the R syntax was: \textit{prop_faces ~ age * milestone + (1 | child_id)}.
+Children's age of achieving each milestone was dummy-coded (i.e., 0=milestone not reached; 1=milestone reached).
 
-```
+We then used a discontinuity analysis to estimate whether the onset of each of these three motor milestones changed the proportion of faces/hands in each chid's view.
+Specifically, we used mixed-effects regressions with per-child random intercepts to estimate whether children's age (in months), each motor milestone, and their interaction significantly influenced the proportion of hands or faces that each child saw.
 
-```{r}
-## Load in gold sample detections
-load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
-load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_with_centerall_detections.RData'))
-
-# all_gold_sample_frames_op_hc = load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_high_conf_detections.RData')) 
-```
-
-```{r}
-## summary for all detections
-face_hand_by_age <- all_vid_data %>%
-  ungroup() %>%
-  tidyr::replace_na(list(faces_and_hands=0)) %>%
-  group_by(age_day_bin, child_id) %>%
-  summarize(num_frames_total = sum(num_frames), 
-            # prop faces overall
-            num_faces = sum(num_faces), 
-            num_hands = sum(num_hands), 
-            prop_faces = num_faces / num_frames_total, 
-            prop_hands = num_hands / num_frames_total,
-            # in center FOV
-            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
-            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
-            prop_faces_center = num_faces_center / num_frames_total, 
-            prop_hands_center = num_hands_center / num_frames_total,
-            # detailed face info
-            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
-            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
-            # face/hand contingency
-            prop_faces_with_hands = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
-            prop_hands_with_faces = sum(faces_and_hands, na.rm=TRUE)/num_hands 
-            )
-
-all_detections <- face_hand_by_age %>%
-  filter(num_frames_total > 2000) %>% # eliminate small data point that skews scaling
-  select(prop_faces, prop_hands, num_frames_total, age_day_bin, child_id) %>%
-  pivot_longer(cols = c(prop_faces, prop_hands), names_to = "region", values_to = "prop") %>%
-  mutate(approach = "uncropped",
-         region = ifelse(region == "prop_faces","Faces","Hands"))
-
-```
-
-```{r}
-# Function to evaluate detectors
-evaluate_detector <- function(truth, detection) {
-  if (truth == TRUE) {
-    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
-    else return("FN") # was face/wrist, missed face/wrist
-  }
-  else {
-    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
-    else return("FP") # was not face/wrist, detected face/wrist
-  }
-}
-
-# function to return prfs
- return_prf_short <- function(eval){
-  tp=sum(eval == "TP")
-  fp=sum(eval == "FP")
-  fn=sum(eval == "FN")
-  p = tp / (tp + fp)
-  r = tp / (tp + fn)
-  f=( 2 * p * r )/ (p + r)
-  return(c(p,r,f))
- }
-
-# join human and OP detections
-gold_sample <- gold_sample %>%
-  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
-  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
-  right_join(all_gold_sample_frames_op) %>%
-  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))
-
- ## output prfs
- face_performance = return_prf_short(gold_sample$face_eval_ketan)
- hand_performance = return_prf_short(gold_sample$hand_eval_ketan)
-
-```
-
-```{r}
-## Move to appendix
-## get out summary by age for goldset hand-labeled frames
-vid_info <- all_vid_data  %>%
-  select(child_id, vid_name, age_days, age_day_bin)
-
-summary_by_age_gold <- gold_sample %>%
-  left_join(vid_info) %>%
-  group_by(age_day_bin, child_id) %>%
-  summarize(num_frames_total = n(), num_faces = sum(face_present_ketan), num_hands = sum(hand_present_ketan), prop_faces= num_faces / num_frames_total, prop_hands = num_hands / num_frames_total)
-```
-
-```{r}
-### Examine gold sample performance by child hands
-load(here::here('data/preprocessed_data_2021/child_adult_hand_annotations_by_frame.RData'))
-
-gold_sample_no_child_hands <- gold_sample %>%
-  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
-  replace_na(list(child_hand_seg = FALSE)) %>% # replace NAs with false (frames not in annotations (NAs) did not have hands) 
-  filter(child_hand_seg==FALSE) %>% # now these are counted as frames where OP didn't need to detect something
-  mutate(hand_eval_adults = evaluate_detector(hand_present_ketan, hand_detected))
-
-summary_by_age_adult_hands_gold <- gold_sample_no_child_hands %>%
-  left_join(vid_info) %>%
-  group_by(age_day_bin, child_id) %>%
-  summarize(num_frames_total = n(), num_faces = sum(face_present_ketan), num_hands = sum(hand_present_ketan), prop_faces = num_faces / num_frames_total, prop_hands = num_hands / num_frames_total)
-```
-
-```{r}
-goldset <- summary_by_age_gold %>%
-  gather(region, prop, prop_faces, prop_hands) %>%
-  mutate(approach = "goldset",
-         region = ifelse(region == "prop_faces","Faces","Hands"))
-
-goldset_adult_hands <- summary_by_age_adult_hands_gold %>%
-  gather(region, prop, prop_faces, prop_hands) %>%
-  mutate(approach = "goldset",
-         region = ifelse(region == "prop_faces","Faces","Hands"))
-
-```
-
-# Face/hand detections relative to human annotations
-```{r goldSetSanity, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=4, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset.
-Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range.
-Dashed lines show estimated trend lines from proportion of faces/hands in view when analyzing the gold set of frames made by human annotators.
-Dotted lines show trend lines from the goldset when frames containing children's own hands were excluded." }
-
-ggplot(all_detections %>% filter(child_id %in% c('S','A')), 
-       aes(x=age_day_bin, y=prop, 
-           size=log10(num_frames_total),
-           col=region)) +
-  geom_point(alpha=.2) +
-  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
-  geom_smooth(data = goldset_adult_hands, span=10, aes(weight = num_frames_total), show.legend = FALSE,
-              lty = 2, span=10, se = FALSE) +
-  geom_smooth(data = goldset, span=10, aes(weight = num_frames_total), show.legend = FALSE,
-              lty = 3, span=10, se = FALSE) +
-  ylab('Proportion Detections') + 
-  xlab('Age (Months)') +
-  ylim(0,.6) +
-  facet_grid(.~child_id) + 
-  theme_few(base_size=10) +
-  ggthemes::scale_color_solarized(name = "") + 
-  scale_size_continuous(name = "Detections (Log 10)") +
-  theme(legend.text=element_text(size=10)) +
-  theme(legend.position="bottom")
-
-```
-
-# Density of child vs. adults hands in the visual field
-
-```{r} 
-### Load turk hand annotations with all bounding boxes (multiple dets per frame)
-load(here::here('data/preprocessed_data_2021/hand_annotations_2020-01-29.RData'))
-
-child_hands <- hand_annotations %>%
-  filter(label=="Child hand")
-
-adult_hands <- hand_annotations %>%
-  filter(label=="Adult hand")
-```
-
-```{r}
-### plot centers of the bounding boxes made for child and adult hands
-child_hand_plot <- ggplot(child_hands, aes(x=center_x, y=center_y)) +
-  geom_point(alpha=.1) + 
-  stat_density_2d(aes(fill = ..level..), geom="polygon", alpha=.8) +
-  coord_fixed(ratio=1) +
-  ggtitle('A. Child hand density') +
-  ylim(0,480) +
-  xlim(0,640) +
-  ylab('') +
-  xlab('') +
-  theme_few(base_size=10) +
-  theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
-  scale_y_reverse()
-##
-adult_hand_plot <- ggplot(adult_hands, aes(x=center_x, y=center_y)) +
-  geom_point(alpha=.1) + 
-  stat_density_2d(aes(fill = ..level..), geom="polygon", alpha=.8) +
-  coord_fixed(ratio=1) +
-  ylim(0,480) +
-  xlim(0,640) +
-  scale_y_reverse() +
-  ylab('') +
-  xlab('') +
-  theme_few(base_size=10) +
-    theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
-  ggtitle('B. Adult hand density')
-```
-
-```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=6.5, fig.height=3.5, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant.
-Brighter values indicate more detections."}
-cowplot::plot_grid(child_hand_plot, adult_hand_plot, nrow=1)
-```
-
-# Distribution of faces and hands in the visual field
-We explored where in the visual field children tended to see faces and hands, suspecting that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank (2012).
-As expected, faces tended to appear in the upper visual field in contrast to hands, which tended to be more centrally located (see Figure C1). 
-However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ visual environment from 6 months of age.
-
-```{r}
-bin_size=7
-min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
-max_age = max(all_vid_bbs$age_days, na.rm=TRUE)
-bin_starts = seq(min_age-1, max_age+1,bin_size)
-bins = c(bin_starts, max_age)
-
-all_vid_bbs <- all_vid_bbs %>%
-  mutate(age_months = age_days/30.4) %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=floor(bin_starts/30.4))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
-  mutate(avg_center_y = avg_top + avg_height/2, avg_center_x = avg_left + avg_width/2) %>%
-  filter(num_detect > 100)
-
-```
-
-```{r, eval=F, include=F}
-# add back to text when high-conf BBs are processed:
-# We also evaluated OpenPose's performance while restricting detections to high-confidence detections (>.5 confidence, default threshold for visualization). 
-#For faces, we found that the F-score was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`. 
-#For hands, the F-score for high-confidence detections was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
-#Thus, as in prior work [@long2020automated], while precision was much higher for both faces and hands, the lower recall for high-confidence detections indicates that these lower-confidence detections still index the presence of social information in the infant view.
-```
-
-```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 6-31 month-old.
-Each dot represents the average position from one video within a given age range.", warning=F}
-
-ggplot(all_vid_bbs %>% filter(label %in% c('face','hand')), aes(x=avg_center_x , y = avg_center_y, size=num_detect, color=label)) +
-  geom_point(alpha=.3) + 
-  stat_density2d(aes(fill = label, color=label), geom="polygon", alpha=.6) +
-  coord_fixed(ratio=.76) +
-  # ggtitle('Face/hand density') +
-  ylab('') +
-  xlab('') +
-  theme_few(base_size=14) +
-  theme(legend.position="top", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
-  scale_y_reverse() +
-  facet_wrap(~age_day_bin) +
-  guides(size = FALSE) +
-  ggthemes::scale_color_solarized(name = "")  +
-  ggthemes::scale_fill_solarized(name = "") 
-```
-
-# Detection threshold estimations
-
-```{r}
-# with all thresholds
-load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections_all_thresholds.RData"))
-
-load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
-```
-
-```{r}
-evaluate_detector <- function(truth, detection) {
-  if (truth == TRUE) {
-    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
-    else return("FN") # was face/wrist, missed face/wrist
-  }
-  else {
-    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
-    else return("FP") # was not face/wrist, detected face/wrist
-  }
-}
-
- return_tpr = function(eval){
-  tp=sum(eval == "TP")
-  fp=sum(eval == "FP")
-  fn=sum(eval == "FN")
-  tn=sum(eval == "TN")
-  tpr = tp / (tp + fn)
-  return(tpr)
- }
-
-return_fpr = function(eval){
-  tp=sum(eval == "TP")
-  fp=sum(eval == "FP")
-  fn=sum(eval == "FN")
-  tn=sum(eval == "TN")
-  fpr = fp / (fp + tn)
-  return(fpr)
- }
-
-```
-
-```{r}
-roc_data <- gold_sample %>%
-  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
-  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
-  right_join(all_gold_sample_frames_op) %>%
-   mutate(hand_detected = hand_detected>0, face_detected = face_detected > 0) %>% # number = number of faces/hands detected
-  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) %>%
-  group_by(detection_threshold) %>%
-  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan))
-```
-
-```{r}
-face_roc = ggplot(data=roc_data, aes(x=fpr_faces, y=tpr_faces, color=detection_threshold)) +
-  geom_point() +
-  geom_line() +
-  ylim(0,1) +
-  xlim(0,1) +
-  geom_abline(color = 'grey') +
-  xlab('False Positive Rate') +
-  ylab('True Positive Rate') +
-  ggtitle('Face detections') +
-  theme(legend.position = 'none')
-
-hand_roc = ggplot(data=roc_data, aes(x=fpr_hands, y=tpr_hands, color=detection_threshold)) +
-  geom_point() +
-  geom_line() +
-  ylim(0,1) +
-  xlim(0,1) +
-  geom_abline(color = 'grey') +
-  xlab('False Positive Rate') +
-  ylab('True Positive Rate') +
-  ggtitle('Hand detections') +
-  theme(legend.position = 'none')
-
-```
-
-```{r}
-ggarrange(face_roc, hand_roc, nrow=1)
-```
-
-# OpenPose Error Analyses
-```{r}
-# remove big data frame with thresholds
-rm(all_gold_sample_frames_op)
-
-# without thresholds
-load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections.RData"))
-
-# join human and OP detections
-gold_sample <- gold_sample %>%
-  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
-  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
-  right_join(all_gold_sample_frames_op) %>%
-  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))
-
-    # mutate(face_eval_ketan_center = evaluate_detector(face_present_ketan, face_detected_center), hand_eval_ketan_center = evaluate_detector(hand_present_ketan, hand_detected_center)) 
-```
-
-```{r}
-# add age day bins to gold_sample
-load(file=here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
-bin_size = 7 # days
-min_age = min(all_vid_data$age_days, na.rm=TRUE) # 182
-max_age = max(all_vid_data$age_days, na.rm=TRUE) # 966
-bin_starts = seq(min_age-1, max_age+1,bin_size)
-bins = c(bin_starts, max_age)
-
-gold_sample <- gold_sample %>%
-  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
-  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) 
-```
-
-```{r}
- return_prf = function(eval){
-  tp=sum(eval == "TP")
-  fp=sum(eval == "FP")
-  fn=sum(eval == "FN")
-  p = tp / (tp + fp)
-  r = tp / (tp + fn)
-  f=( 2 * p * r )/ (p + r)
-  num_detect = length(eval)
-  out <- data.frame(p,r,f,num_detect)
-  return(out)
- }
-
-# function to return prfs
- return_prf_short = function(eval){
-  tp=sum(eval == "TP")
-  fp=sum(eval == "FP")
-  fn=sum(eval == "FN")
-  p = tp / (tp + fp)
-  r = tp / (tp + fn)
-  f=( 2 * p * r )/ (p + r)
-  return(c(p,r,f))
- }
-
-```
-
-```{r}
-prf_by_age_faces <-  gold_sample %>%
-  group_by(child_id, age_day_bin) %>%
-  do(return_prf(.$face_eval_ketan))
-
-prf_by_age_hands <-  gold_sample %>%
-  group_by(child_id, age_day_bin) %>%
-  do(return_prf(.$hand_eval_ketan)) 
-```
-
-```{r}
-# Evaluating prfs in center detections is challenging because we ONLY have ground truth on the full image -- so it's not that informative.
-
-# return_prf_short(gold_sample$hand_eval_ketan_center)
-# return_prf_short(gold_sample$face_eval_ketan_center)
-```
-
-```{r det_perf_by_age, fig.width=6.5, fig.height=3.2, fig.cap="F-score of OpenPose hand and face detections in the gold sample by child and age. Size indicates number of detections age bin/child."}
-
-prf_by_age_faces$age_day_bin = as.numeric(prf_by_age_faces$age_day_bin)
-
-prf_by_age_hands$age_day_bin = as.numeric(prf_by_age_hands$age_day_bin)
-
-p1 <- ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
-  geom_point(alpha=.5) +
-  geom_smooth(span=20, alpha=.1)  +
-  ylim(0,1) +
-  ylab('F-score') + xlab('Age (months)') +
-  ggtitle("Face detections") + 
-  theme(legend.position= 'none')
-
-p2 <- ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
-  geom_point(alpha=.5) +
-  geom_smooth(span=20, alpha=.1)  +
-  ylim(0,1) +
-  ylab('F-score') + xlab('Age (months)') +
-  ggtitle("Hand detections") + 
-  theme(legend.position= 'none')
-```
-
-```{r}
-ggarrange(p1, p2, nrow=1)
-```
-
-```{r}
-# p2 = ggplot(prf_by_age_faces, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
-#   geom_point(alpha=.5) +
-#   geom_smooth(span=10, alpha=.1)  +
-#   ylim(0,1) +
-#   ylab('Precision - Face detection')+
-#   xlab('Age (months)') +
-#   theme(legend.position= 'none')
-# 
-# p3 =ggplot(prf_by_age_faces, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
-#   geom_point(alpha=.5) +
-#   geom_smooth(span=10, alpha=.1)  +
-#   ylim(0,1) +
-#   ylab('Recall - Face detection')+
-#   xlab('Age (months)') +
-#   theme(legend.position= 'none')
-# #
-# ggarrange(p1,p2,p3)
-
-```
-
-```{r}
-load(here::here('data/preprocessed_data_2021/saycam_metadata.RData')) # meta
-
-num_videos_annotated = sum(!is.na(meta$Location))
-videos_included = sum(!is.na(meta$Location) & meta$count_locations==1)
-```
-
-```{r}
-gold_sample_by_location <- gold_sample %>%
-  left_join(meta) %>%
-  filter(!is.na(Location)) %>%
-  filter(count_locations==1) 
-```
-
-```{r}
-prf_by_location_faces <-  gold_sample_by_location %>%
-  group_by(Location) %>%
-  do(return_prf(.$face_eval_ketan)) %>%
-  filter(num_detect > 50)
-
-prf_by_location_hands <-  gold_sample_by_location %>%
-  group_by(Location) %>%
-  do(return_prf(.$hand_eval_ketan)) %>%
-  filter(num_detect > 50)
-```
-
-```{r det_perf_by_locations, fig.width=6.5, fig.height=3.0, fig.cap="F-score of OpenPose hand and face detections in the gold sample by location.
-Size indicates number of detections per location: minimum = 55 (car); maximum = 1753 (living room)."}
-p1 <- ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=num_detect)) +
-  geom_point(alpha=.5) +
-  ylab('F-score') + ggtitle("Face detections") +
-  theme(legend.position = 'none') +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  ylim(0,1)
-
-p2 <- ggplot(prf_by_location_hands, aes(x=Location, y=f, col=Location, size=num_detect)) +
-  geom_point(alpha=.5) +
-  ylab('F-score') + ggtitle("Hand detections") +
-  theme(legend.position = 'none') +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  ylim(0,1)
-
-ggarrange(p1, p2, nrow=1)
-```
-
-# OpenPose Annotation Examples
-```{r include=FALSE}
-load(file = here::here('data/preprocessed_data_2021/goldset_category_annotations.RData'))
-
-fp_face_examples <- d %>%
-  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-  filter(face_eval_ketan == 'FP')
-
-fp_hand_examples <- d %>%
-  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-  filter(hand_eval_ketan == 'FP')
-
-fn_face_examples <- d %>%
-  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-  filter(face_eval_ketan == 'FN')
-
-fn_hand_examples <- d %>%
-  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-  filter(face_eval_ketan == 'FN')
-
-images_to_render =  fp_hand_examples
-which_images = 'fp_hand_examples'
-
-public_urls = unique(images_to_render$public_url)
-img_names_short = unique(images_to_render$img_name)
-
-dir.create(here::here("data/annotation_examples/", which_images),recursive = TRUE)
-
-  for (i in 1:length(public_urls)){
-    this_image = image_read(public_urls[i])
-    image_write(this_image,here::here("data/annotation_examples/",which_images, img_names_short[i]))
-  }
-
-```
-
-```{r}
-det_types = c('FP','FN')
-
-render_examples = FALSE
-if (render_examples == TRUE) {
-for (det_type in det_types) {
-  to_render_hands <- d %>%
-    distinct(vid_name, frame, public_url) %>%
-    left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-    filter(hand_eval_ketan == det_type) %>%
-    ungroup() %>%
-    dplyr::sample_n(7)
-
-  image_read(to_render_hands$public_url) %>%
-    image_append(stack = FALSE) %>%
-    image_write(paste0(here::here("data/annotation_examples/"), 'example_hands_', det_type,".png"))
-
-  ###
-    to_render_faces <- d %>%
-    distinct(vid_name, frame, public_url) %>%
-    left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
-    filter(face_eval_ketan == det_type) %>%
-    ungroup() %>%
-    dplyr::sample_n(7)
-
-  image_read(to_render_faces$public_url) %>%
-    image_append(stack = FALSE) %>%
-    image_write(paste0(here::here("data/annotation_examples/"), 'example_faces_', det_type,".png"))
-
-}
-}
-
-```
-
-```{r error_examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=6, set.cap.width=T, num.cols.cap=2,  fig.fullwidth = TRUE, fig.align = "center", fig.cap = "Example false alarms/misses for faces/hands randomly sampled from the larger set of manual annotations."}
-error_examples <- png::readPNG("figs/OP_errors.png")
-grid::grid.raster(error_examples)
-```
-
-## Location of OpenPose False Positives
-
-Below we visualize the locations of the 1229 faces (in 1093 frames) that OpenPose detected in the gold set frames that were not actually there, as well as the 1778 OpenPose false positive hands (in 1237 frames) from the gold set.
-The average location of OpenPose's false positives for both faces (left) and hands (right) are somewhat more common in the center of the frame, but some are scattered across the frame.
-Qualitatively, the location of these false positives do not look much different than the true positive detections.
-
-```{r density-op-fps, fig.width=6, fig.height=3}
-load(here::here('data/preprocessed_data_2021/gold_sample_all_indiivdual_dets.RData'))
-ddd <- gold_sample_all_dets %>% left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan))
-
-# density plot of OP's false positive face/hand locations
-p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
-  mutate(x=left+0.5*width,
-         y=top-0.5*height) %>% # could actually overplot all the face rectangles? prob very messy...
-  ggplot(aes(x=x, y=y, fill=..level..)) + 
-  stat_density_2d(geom = "polygon") + xlim(-.05,1.1) + ylim(-.1,1.0) + 
-  xlab("Mean x-position of OpenPose Detection") + 
-  ylab("Mean y-position of OpenPose Detection") + 
-  ggtitle("Face False Positives") + theme(legend.position = "none")
-
-p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
-  mutate(x=left+0.5*width,
-         y=top-0.5*height) %>%
-  ggplot(aes(x=x, y=y, fill=..level..)) + 
-  stat_density_2d(geom = "polygon") + xlim(-.05,1.1) + ylim(-.1,1.0) + 
-  xlab("Mean x-position of OpenPose Detection") + 
-  ylab("Mean y-position of OpenPose Detection") + 
-  ggtitle("Hand False Positives") + theme(legend.position = "none")
-
-ggpubr::ggarrange(p1, p2)
-```
-
-# Activity by Location
-
-```{r activities_by_lo, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos."}
-meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))
-
-meta_wide <- meta2 %>% filter(Activity!="N/A", !is.na(Location)) %>%
-  select(Child, `File Name`, Activity, Location) %>%
-  separate(Activity, c("Act.1","Act.2","Act.3","Act.4","Act.5","Act.6","Act.7","Act.8","Act.9","Act.10","Act.11","Act.12"), sep=',') %>%
-  pivot_longer(cols = starts_with("Act."), 
-                                        names_to = "activity_index",
-                                        names_prefix = "Act.",
-                                        values_to = "Activity",
-                                        values_drop_na = T) %>%
-  mutate(Activity = case_when(Activity=="Waving" ~ "Gesturing",
-                              Activity=="Imitation" ~ "Imitating",
-                              Activity=="Talking Walk" ~ "Walking",
-                              Activity=="Tidying" ~ "Cleaning",
-                              Activity=="Preparing for Outing" ~ "Getting Changed/Dressed",
-                              Activity=="Play Pretend" ~ "Playing",
-                              TRUE ~ Activity))
-
-# include videos with multiple locations
-meta_long <- meta_wide %>% 
-  separate(Location, c("Loc.1","Loc.2","Loc.3","Loc.4","Loc.5","Loc.6"), sep=',') %>%
-  pivot_longer(cols = starts_with("Loc."),
-               names_to = "location_index",
-               names_prefix = "Loc.",
-               values_to = "Location",
-               values_drop_na = T)
-
-single_locations = c("Bedroom","Car","Deck/Porch","Kitchen","Living Room","Off Property","Office","Outside on Property")
-
-# single-location videos
-meta_long_1loc <- meta_wide %>%
-  filter(is.element(Location, single_locations)) %>%
-  filter(Activity!="N/A", Activity!="Consequence", Activity!="Gesturing")
-
-# what is "California Room" ?
-meta_long <- meta_long %>% mutate(Location = ifelse(Location=="Bedroom Alice/Sam", "Bedroom", Location))
-
-loc_freq = sort(table(meta_long_1loc$Location))
-
-# multi-location videos
-meta_long %>% filter(Activity!="N/A", Activity!="Consequence", Activity!="Kicking",
-                     Activity!="Gesturing", Activity!="Look and Listen", 
-                     Location!="N/A", Location!="California Room",
-                     Location!="Rapidly Moving Between Locations", Location!="Piano Room") %>%
-  mutate(Location = ifelse(Location=="Dog Park/Park/Field", "Off Property", Location)) %>%
-  group_by(Activity, Location) %>%
-  summarise(n = n()) %>% 
-  ggplot(aes(x=Activity, y=Location, fill=n)) +
-  geom_tile() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-```
-
-```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location in videos taking place in only a single location."}
-# single location videos
-meta_long_1loc %>% 
-  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
-  group_by(Activity, Location) %>%
-  summarise(n = n()) %>% 
-  ggplot(aes(x=Activity, y=Location, fill=n)) +
-  geom_tile() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-#ggsave("activity_by_location.pdf", width=6.5, height=3.5)
-```
-
-```{r, fig.width=6.5, fig.height=3.0, fig.cap="Probability of different activities, given location (in single-location videos)."}
-# normalize by location
-meta_long_1loc %>% 
-  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
-  left_join(meta_long_1loc %>% group_by(Location) %>% summarise(loc_freq = n())) %>%
-  group_by(Activity, Location) %>%
-  summarise(n = n(),
-            prop_loc = n / loc_freq) %>% 
-  ggplot(aes(x=Activity, y=Location, fill=prop_loc)) +
-  geom_tile() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-```
-
-# Motor Milestones Analysis Details
-
-We examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the proportion of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
-
-We tried including random slopes by age and milestone, but the models did not converge and/or were singular.
-Thus, for each milestone the R syntax was: \texttt{prop_faces ~ age * milestone + (1 | child_id)}.Children's age of achieving each milestone was dummy-coded (i.e., 0=milestone not reached; 1=milestone reached).
+Overall, we did not find strong effects based on these motor milestones.
+We found that the age at which these children began sitting did not significantly predict changes in either the amount of faces or hands that they saw.
+As children became able to cruise, they saw more faces ($\beta = 0.27$) and hands ($\beta = 0.26$).
+For faces, however, there was also a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$).
+We did not find major differences with the onset of walking.
 
@@
 
-## Sitting
-
-Children's age at which they began sitting did not significantly predict changes in either the amount of faces or hands that they saw.
+### Sitting
 
@@
 
-## Cruising
-
-As children became able to cruise, they saw significantly more faces ($\beta = 0.27$) and hands ($\beta = 0.26$. 
-For faces, there was a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$).
+### Cruising
 
@@
 
-## Walking
-
-As children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$).
+### Walking
 

### 2022-01-07 paper/manuscript/manuscript_dec2021_apa_blinded.Rmd
incorporate last changes from google doc pass

@@
 We thus capitalize on this computational advance to annotate the entirety of this large, longitudinal video dataset. 
-We use these detections to first report how the proportion of faces and hands changes with age and motor development milestones in each of the three children in the dataset. 
+We use these detections to first report how the proportion of faces and hands changes with age in each of the three children in the dataset. 
 We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the head cameras as well as a diversity of locations in which videos were recorded.
@@
 
-### Detector vs. human annotations of faces/hands
+### OpenPose vs. human annotations of faces/hands
 To test the validity of OpenPose's hand and face detections, we compared the accuracy detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A); this sample was conducted before child Y was added to the dataset.
@@
 Thus, detections that were made in the periphery of these videos were not more likely to be false alarms for either faces or hands.
-Appendix Figure A3 illustrates this finding, showing the density of false positives for both faces and hands that are concentrated in the center of the fied of view.
-
-### Detector confidence
+Appendix Figure A3 illustrates this finding, showing the density of false positives for both faces and hands that are concentrated in the center of the field of view.
+
+### Accuracy as a function of detection confidence
 We next examined the degree to which including detections that the model was more or less confident in changed overall model performance for face/hand detection.
@@
 
-## Variability with motor development milestones
-How does the social information in view change as a function of motor development?
-One idea is that children’s ability to stand and move on their own may fundamentally change the visual social information that they see (e.g., facial expressions, gaze cues, pointing)  [@walle2014infant; @walle2016infant] relative to infants who are still sitting and crawling.
-Indeed, in in-lab studies, children's in-the-moment posture -- and that of their caregiver -- is a strong predictor of the visual social information that children see [@franchak2017see; @long2021automated].
-
-We thus next analyzed how the social information in view changed as a function of each child reaching particular developmental motor milestones.
-Each parent in the SAYCam dataset completed the Ages and Stages Questionnaire (ASQ) [@bricker1999ages], which includes questions about their child's motor abilities, and we used the responses from this questionnaire to code the age (in months) at which each child became able to sit, cruise, and walk on their own (questions about crawling were not included in the questionnaire).
-We found considerable variability in the age at which each child achieved these three milestones.
-Participants S and A were already able to sit at 6 months of age, while Y began achieving this milestone at 8 months.
-A was able to cruise at 9 months of age, while S reached that milestone at 10 months, with Y just behind.
-Learning to walk showed the most variation, with S walking after 10 months, A after 13 months, and Y after 16 months of age.
-
-We then used a discontinuity analysis to estimate whether the onset of each of these three motor milestones changed the proportion of faces/hands in each chid's view.
-Specifically, we used mixed-effects regressions with per-child random intercepts to estimate whether children's age (in months), each motor milestone, and their interaction significantly influenced the proportion of hands or faces that each child saw; see Appendix Tables A1-3 for full model specifications and tables with all coefficients.
-Overall, we found that the age at which these children began sitting did not significantly predict changes in either the amount of faces or hands that they saw.
-However, as children became able to cruise, they saw significantly more faces ($\beta = 0.27$) and hands ($\beta = 0.26$), suggesting that the ability to be upright and locomote even somewhat independently was sufficient to significantly change children's visual social environment.
-For faces, however, there was also a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$).
-However, we did not find major differences with the onset of walking; as these children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$).
-Thus, these analyses confirm and extend cross-sectional findings, leveraging dense, within-child data to help elucidate the complex relationship between motor development and the social information in view.
-
 ## Variability in social information across learning contexts 
@@
 How might pose detection algorithms be improved upon such that they can achieve greater accuracy in analyzing infant egocentric videos?
-This question is ripe for collaboration between computer vision experts and devleopmental psychologists.
+This step is ripe for collaboration between computer vision experts and developmental psychologists.
 One promising direction may be to use detailed pose annotations of the people in the infant view to fine-tune later layers of pose detection networks.
@@
 A second potential area for innovation lies in leveraging the dense nature of these large-scale annotations to improve model accuracy: By pooling detections from surrounding frames, we may be able to build classifiers that perform more accurately on a single challenging viewpoint.
-Finally, a third area for improvement consists of building classifiers that can accurately distinguish between children's hands (as seen from the egocentric point of view) versus adults' hands--a notoriously challenging problem in computer vision [@bambach2015lending].
+Finally, a third area for improvement consists of building classifiers that can accurately distinguish between children's hands (as seen from the egocentric point of view) versus adults' hands -- a notoriously challenging problem in computer vision [@bambach2015lending].
 We expect that these goals may become more and more feasible as we also improve the head-mounted cameras that are used in both at-home and in-lab studies; increasing the resolution and quality of the images we record will no doubt improve the ability of computer vision algorithms to extract detailed information.

### 2022-01-07 analysis/motor_milestones.Rmd
walking milestone analysis

---
title: "Motor Milestone Analysis"
output: pdf_document
---

```{r setup, include=FALSE, echo=F, message=F}
knitr::opts_chunk$set(echo = F, warning=F, message=F)
library(tidyverse)
library(lme4)
library(stargazer)
library(lmerTest)
library(ggeffects)
```

We examine whether the SAYcam participants' age at which they started walking significantly influenced the proportion of hands or faces that they saw, using mixed-effects regressions with per-child random intercepts.
We tried including random slopes by age and milestone, but the models did not converge and/or were singular. The R syntax for the linear regression was thus: prop_faces ~ age * walk + (1 | child_id).
We also tested inclusion of a quadratic term for age (prop_faces ~ poly(age,2) * walk + (1 | child_id)).
Children's age of achieving the milestone was dummy-coded (i.e., 0=unable to walk; 1=able to walk).

```{r}
## Load in gold sample detections
load(here::here('data/preprocessed_data_2022/gold_sample_annotations2020-01-31.RData')) # human annotations
load(here::here('data/preprocessed_data_2022/gold_sample_from_bbs_2021_with_centerall_detections.RData')) 
load(here::here('data/preprocessed_data_2022/all_vid_data_from_bbs_all_detections.RData')) # all detections

```

```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_faces_with_hands = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_hands_with_faces = sum(faces_and_hands, na.rm=TRUE)/num_hands 
            )

all_detections <- face_hand_by_age %>%
  filter(num_frames_total > 2000) %>% # eliminate small data point that skews scaling
  select(prop_faces, prop_hands, num_frames_total, age_day_bin, child_id) %>%
  pivot_longer(cols = c(prop_faces, prop_hands), names_to = "region", values_to = "prop") %>%
  mutate(approach = "uncropped",
         region = ifelse(region == "prop_faces","Faces","Hands"))

```

```{r, get-milestones, echo=F}
motor <- read_csv(here::here("data","raw_data", "saycam_walking_asq.csv"))
# A and S are sitting at 6mos
face_hand_by_age_milestones <- face_hand_by_age %>%
  mutate(sit = ifelse(child_id=="S" | child_id=="A", 1, 
                      ifelse(child_id=="Y" & age_day_bin > 8, 1, 0))) %>%
  mutate(cruise = ifelse((child_id=="S" & age_day_bin >= 9) | 
                      (child_id=="A" & age_day_bin >= 10) | 
                      (child_id=="Y" & age_day_bin > 9), 1, 0)) %>%
  mutate(walk = ifelse((child_id=="S" & age_day_bin > 10) |
                       (child_id=="A" & age_day_bin > 13) |
                       (child_id=="Y" & age_day_bin > 16), 1, 0)) %>%
  mutate(age = age_day_bin)

library(lmerTest)
# https://rpsychologist.com/r-guide-longitudinal-lme-lmer
# with random slopes and intercepts ((age_day_bin | child_id): is singular / not converging
# so we drop random slopes

# cruise
face_cruise <- lmer(prop_faces ~ age * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)
hand_cruise <- lmer(prop_hands ~ age * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)

face_cruise2 <- lmer(prop_faces ~ poly(age,2) * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)
hand_cruise2 <- lmer(prop_hands ~ poly(age,2) * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)

# walk
face_walk <- lmer(prop_faces ~ age * walk + (1 | child_id), 
     data=face_hand_by_age_milestones)
hand_walk <- lmer(prop_hands ~ age * walk + (1 | child_id), 
     data=face_hand_by_age_milestones)

face_walk2 <- lmer(prop_faces ~ poly(age,2) * walk + (1 | child_id), 
     data=face_hand_by_age_milestones)
hand_walk2 <- lmer(prop_hands ~ poly(age,2) * walk + (1 | child_id), 
     data=face_hand_by_age_milestones)

#summary(face_walk2)
#summary(hand_walk2)

# make models compatible with stargazer
class(face_cruise) <- "lmerMod"
class(hand_cruise) <- "lmerMod"
class(face_cruise2) <- "lmerMod"
class(hand_cruise2) <- "lmerMod"

class(face_walk) <- "lmerMod"
class(hand_walk) <- "lmerMod"
class(face_walk2) <- "lmerMod"
class(hand_walk2) <- "lmerMod"
```

<!--
## Cruising

#The quadratic term was justified for the hands model ($\chi^2(2)=16.29$, $p<.001$), but not for the faces model ($\chi^2(2)=5.77$, $p=.06$).
#As children became able to cruise, they saw significantly more faces ($\beta = 0.27$), but there was no significant effect on hands. 
#For faces, there was a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$).
-->

```{r, include=F}
anova(face_cruise, face_cruise2) # marginal
anova(hand_cruise, hand_cruise2) # sig
```

```{r, results='asis', include=F}
stargazer(face_cruise, hand_cruise2, title="Change in face and hand prevalence by ability to cruise", 
          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
```

```{r, fig.width=6.5, fig.height=3, include=F}
f1 <- ggpredict(face_cruise, c("age", "cruise")) %>% plot(add.data=T) +
  xlim(5, 30) + ylim(0,1) + ggtitle("Predicted effect on faces seen") + 
  xlab("Age (months)") + ylab("Proportion of faces")

h1 <- ggpredict(hand_cruise2, c("age", "cruise")) %>% plot(add.data=T) +
  xlim(5, 30) + ylim(0,1) + ggtitle("Predicted effect on hands seen") + 
  xlab("Age (months)") + ylab("Proportion of hands")

ggpubr::ggarrange(f1, h1, nrow=1, common.legend=T)
```

<!-- ## Walking -->

The quadratic term was justified for both the hands model ($\chi^2(2)=22.15$, $p<.001$) and the faces model ($\chi^2(2)=10.21$, $p<.01$).
As children became able to walk, they saw significantly more faces ($\beta = 0.26$, $p=0.02$) and hands ($\beta = 0.32$, $p=0.01$). 
The linear and quadratic age terms and their interactions with walking were also significant (see Table 1).
The models' predicted conditional effects are shown in Figure 1.

```{r, include=F}
anova(face_walk, face_walk2) # sig
anova(hand_walk, hand_walk2) # sig
```

```{r, results='asis'}
stargazer(face_walk2, hand_walk2, title="Change in face and hand prevalence by ability to walk", 
          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
```

```{r, fig.width=6.5, fig.height=3}
f1 <- ggpredict(face_walk2, c("age", "walk")) %>% plot(add.data=T) +
  xlim(5, 30) + ylim(0,1) + ggtitle("Predicted effect on faces seen") + 
  xlab("Age (months)") + ylab("Proportion of faces")

h1 <- ggpredict(hand_walk2, c("age", "walk")) %>% plot(add.data=T) +
  xlim(5, 30) + ylim(0,1) + ggtitle("Predicted effect on hands seen") + 
  xlab("Age (months)") + ylab("Proportion of hands")

ggpubr::ggarrange(f1, h1, nrow=1, common.legend=T)
```

### 2022-01-07 paper/manuscript/appendix.Rmd
save appendix pdf figs in line

@@
 cowplot::plot_grid(child_hand_plot, adult_hand_plot, nrow=1)
+
+ggsave('appendix_figs/handdensity.pdf', width = 7, height = 3)
 ```
@@
   stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
+theme_few(base_size=12) +
   xlab("Center of OpenPose Detection") + 
@@
   ggtitle("Face False Positives") + theme(legend.position = "none") +
-  scale_y_reverse() +
-  theme_few(base_size=12)
+  scale_y_reverse()
 
@@
   stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
+   theme_few(base_size=12) +
   xlab("Center of OpenPose Detection") + 
@@
   ggtitle("Hand False Positives") + theme(legend.position = "none") +
-  scale_y_reverse() +
-  theme_few(base_size=12)
+  scale_y_reverse()
 
 ggpubr::ggarrange(p1, p2)
+ggsave('appendix_figs/op_falsepositives.pdf', width = 7, height = 3)
+
 ```
@@
 ggpubr::ggarrange(face_roc, hand_roc, nrow=1)
+ggsave('appendix_figs/rocs.pdf', width = 7, height = 3)
 ```
@@
 ggpubr::ggarrange(p1, p2, nrow=1)
+ggsave('appendix_figs/fscore_by_age_child.pdf', width = 7, height = 5)
 ```
@@
 ggpubr::ggarrange(p1, p2, nrow=1)
+ggsave('appendix_figs/fscore_by_location.pdf', width = 7, height = 3)
 ```
@@
   theme(legend.position="bottom")
+
+ggsave('appendix_figs/humans_vs_op.pdf', width = 7, height = 5)
 
@@
 
+ggsave('appendix_figs/activities_by_location.pdf', width = 7, height = 4)
+
 ```
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
-#ggsave("activity_by_location.pdf", width=6.5, height=3.5)
+
+ggsave('appendix_figs/activities_by_single_location.pdf', width = 7, height = 4)
+
 ```
@@
   theme(legend.position = c(0.8, 0.1))
+
+ggsave('appendix_figs/face_hand_density.pdf', width = 7, height = 7)
 ```
+
+## A10 Face/hand detections by walking ability
+
+Each parent in the SAYCam dataset completed the Ages and Stages Questionnaire (ASQ), which includes questions about their child's motor abilities, and we used the responses from this questionnaire to code the age (in months) at which each child became able to walk on their own.
+We found considerable variability in the age at which each child achieved this milestone: S began walking after 10 months, A after 13 months, and Y after 16 months of age.
+
+Below, we plot face and hand detections for each child as a function of when each child started walking independently.
+
+```{r}
+face_hand_by_age_milestones <- face_hand_by_age %>%
+  filter(num_frames_total > 5000) %>%
+  mutate(walking = ifelse((child_id=="S" & age_day_bin > 10) |
+                       (child_id=="A" & age_day_bin > 13) |
+                       (child_id=="Y" & age_day_bin > 16), 'Walking', 'Not Yet Walking')) %>%
+  mutate(child_name = case_when(child_id =='A' ~ "Child A",
+                      child_id == "S" ~ "Child S",
+                      child_id == "Y" ~ "Child Y")) %>%
+  select(prop_faces, prop_hands, num_frames_total, age_day_bin, child_name, walking) %>%
+  pivot_longer(cols = c(prop_faces, prop_hands), names_to = "region", values_to = "prop")  %>%
+    mutate(region = case_when(region =='prop_hands' ~ "Hands",
+                      region == "prop_faces" ~ "Faces"))
+
+```
+
+```{r}
+ggplot(face_hand_by_age_milestones,
+       aes(x=age_day_bin, y=prop,
+           size=log10(num_frames_total),
+           col=walking)) +
+  geom_point(alpha=.3) +
+  ylab('Proportion Detections') +
+  xlab('Age (Months)') +
+  ylim(0,.5) +
+  facet_grid(region ~ child_name) +
+  theme_few(base_size=10) +
+  viridis::scale_color_viridis(name = "", option="C", discrete=TRUE, begin=0, end=.4) +
+  theme(legend.text=element_text(size=10)) +
+  guides(size = FALSE) +
+  theme(legend.position="right")
+
+ggsave('face_hand_by_motor.pdf', width=7, height=5)
+```

### 2022-01-07 paper/manuscript/manuscript_dec2021_apa_blinded.Rmd
save appendix pdf figs in line

@@
 abstract: |
-  The faces and hands of caregivers and other social partners offer a rich source of social and causal information that is likely critical for infants' cognitive and linguistic development.
+  The faces and hands of caregivers and other social partners offer a rich source of social and causal information that is likely critical for infants’ cognitive and linguistic development.
 Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants.
-Here, we examine the prevalence of faces and hands in a longitudinal collection of more than 1700 headcam videos from three children ages 6 to 32 months.
-To analyze these naturalistic infant egocentric videos, we validated the use of a modern convolutional neural network (OpenPose) for the detection of faces and hands and then applied this model to the entire dataset.
-First, we found a higher proportion of hands in view than previously reported and a moderate decrease in the proportion of faces in children's view across age.
-Second, we found substantial variability in the proportion of faces and hands viewed by different children in different locations (e.g., living room vs.
+Here, we validated the use of a modern convolutional neural network (OpenPose) for the detection of faces and hands in naturalistic egocentric videos.
+We then applied this model to a longitudinal collection of more than 1700 headcam videos from three children ages 6 to 32 months.
+Using these detections, we confirm and extend prior results from cross-sectional studies.
+First, we found a moderate decrease in the proportion of faces in children’s view across age and a higher proportion of hands in view than previously reported.
+Second, we found variability in the proportion of faces and hands viewed by different children in different locations (e.g., living room vs.
 kitchen), suggesting that individual activity contexts may shape the social information that infants experience.
 Third, we found evidence that children may see closer, larger views of people, hands, and faces earlier in development.
-These analyses provide new insight into the changes in the social information in view across the first few years of life and call for further work that examines their generalizability across populations and their relationship to learning outcomes.
+These longitudinal analyses provide an additional perspective on the changes in the social information in view across the first few years of life and suggest that pose detection models can successfully be applied to naturalistic egocentric video datasets to extract descriptives about infants’ changing social environment.
 keywords: social cognition; face perception; infancy; head cameras; deep learning
@@
 bibliography: library.bib
-floatsintext: yes
+floatsintext: no
 figurelist: no
@@
 
-Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of more than 1700 headcam videos collected at home from three children along a span of 6 to 32 months of age—--the SAYCam dataset [@SAYcam].
+Here, we examine the social information present in the infant visual perspective -- the presence of faces and hands -- by analyzing a longitudinal collection of more than 1700 headcam videos collected at home from three children along a span of 6 to 32 months of age -- the SAYCam dataset [@SAYcam].
 We analyze the video data from this dense, longitudinal dataset as case studies of how the social information in the infant view changes over the course of development in individual children.
@@
 Second, they allow us to relate developmental changes to milestones achieved by an individual child (e.g., the onset of walking).
-Second, they eliminate several sources of variability (e.g., parent/child familiarity with camera, home environment) that may obscure fine-grained developmental patterns.
+Third, they eliminate several sources of variability (e.g., parent/child familiarity with camera, home environment) that may obscure fine-grained developmental patterns.
 
@@
 Finally, making use of automated annotation of pose bounding boxes, we analyze the size, location, and variability of detected faces and poses across development in these three children.
-Overall, these findings largely validate prior cross-sectional findings, and further suggest that automated annotated can be used to analyze naturalistic video datasets to build towards generalizable conclusions about the statistics of the social information in the infant view across a wide variety of populations.
+Overall, these findings largely validate prior cross-sectional findings, and further suggest that automated annotations can be used to analyze naturalistic video datasets to build towards generalizable conclusions about the statistics of the social information in the infant view across a wide variety of populations.
 
@@
 However, we found that excluding these detections did not improve the model's precision for either faces or hands; rather, it only decreased recall.
-Excluding peripehral detections led to an overall f-score of `r round(face_performance_center[3],2)`, for faces with a precision of `r round(face_performance_center[1],2)` and recall of `r round(face_performance_center[2],2)`.
+Excluding peripheral detections led to an overall f-score of `r round(face_performance_center[3],2)`, for faces with a precision of `r round(face_performance_center[1],2)` and recall of `r round(face_performance_center[2],2)`.
 For hands, the F-score for center detections was `r round(hand_performance_center[3],2)`, with a precision of `r round(hand_performance_center[1],2)` and recall of `r round(hand_performance_center[2],2)`.
@@
   guides(size = FALSE) +
-  theme(legend.position="right")
+  theme(legend.position="bottom") +
+  ggtitle('A.')
 
@@
   guides(size = FALSE) +
-  theme(legend.position="right")
+  theme(legend.position="bottom")  +
+  ggtitle('B.')
 
@@
   guides(size = FALSE) +
-  theme(legend.position="right")
-
-```
-
-```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=6, fig.cap = "Proportion of frames with (A) All face and hand detections,  (B) Face/hand detections that fell within the center field-of-view (reducing the contribution of children's own hands) and (C) Face detections that were full faces (e.g., eyes, nose, and mouth all visible) and that co-occurred with hands, plotted as a function of age for each child (A, S, and Y).
+  theme(legend.position="bottom") +
+  ggtitle('C.')
+
+```
+
+```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=9, fig.cap = "Proportion of frames with (A) All face and hand detections,  (B) Face/hand detections that fell within the center field-of-view (reducing the contribution of children's own hands) and (C) Face detections that were full faces (e.g., eyes, nose, and mouth all visible) and that co-occurred with hands, plotted as a function of age for each child (A, S, and Y).
 Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range."}
 
-cowplot::plot_grid(first_panel, second_panel, third_panel, labels='AUTO', nrow=3, align = "v", axis = "b")
+cowplot::plot_grid(first_panel, second_panel, third_panel, labels=NULL, nrow=3, label_fontface = "bold", align = "v", axis = "b")
+ggsave('figs_pdfs/test.pdf', width = 7, height = 9)
 ```

### 2022-01-07 paper/manuscript/appendix.Rmd
add goldset face/hand analysis and figure updates

@@
   ggplot(aes(x=x, y=y, fill=..level..)) + 
+  theme_few(base_size=12) +
   stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
-theme_few(base_size=12) +
   xlab("Center of OpenPose Detection") + 
@@
   ggplot(aes(x=x, y=y, fill=..level..)) + 
+  theme_few(base_size=12) +
   stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
-   theme_few(base_size=12) +
   xlab("Center of OpenPose Detection") + 
@@
 
+```{r}
+summary_by_age_days_gold <- gold_sample %>%
+  group_by(age_days,child_id) %>%
+  summarize(num_faces = sum(face_present_ketan), 
+            num_hands = sum(hand_present_ketan), 
+            num_detect = n()) %>%
+  mutate(prop_faces = num_faces / num_detect, 
+         prop_hands = num_hands / num_detect) %>%
+  select(prop_faces, prop_hands, age_days, child_id) %>%
+  pivot_longer(col = c(prop_faces, prop_hands), names_to="region", values_to = "prop")
+
+summary_by_age_days_gold$age_scale <- scale(summary_by_age_days_gold$age_days, scale = FALSE)[,1] / 30.3
+```
+
+```{r}
+
+## add face vs. hands model on gold sample to sanity check
+diff_model2_gold <- summary(lmer(prop ~ region*poly(age_scale, 2) + (1 | child_id), data = summary_by_age_days_gold))
+
+xtable(diff_model2_gold$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of faces and hands seen by infants based on human annotations.")
+
+```
+
 ## A8 Activity by Location
@@
   guides(size = FALSE) +
-  theme(legend.position="right")
+  theme(legend.position="bottom")
 

### 2022-01-07 paper/manuscript/appendix.Rmd
figure tweaks

@@
 ---
-title: "Appendix"
-author: "Bria Long"
+title: "Appendix to ``A longitudinal analysis of the social information in infants' naturalistic
+  visual experience using automated detections''"
 date: "1/6/2022"
@@
   left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
-  replace_na(list(child_hand_seg = FALSE)) %>% # replace NAs with false (frames not in annotations (NAs) did not have hands) 
+  tidyr::replace_na(list(child_hand_seg = FALSE)) %>% # replace NAs with false (frames not in annotations (NAs) did not have hands) 
   filter(child_hand_seg==FALSE) %>% # now these are counted as frames where OP didn't need to detect something
@@
   mutate(x=left+0.5*width,
-         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
+         y=top+0.5*height) %>% # could actually overplot all the face rectangles? prob very messy...
   ggplot(aes(x=x, y=y, fill=..level..)) + 
+  stat_density_2d(geom = "polygon") + 
 theme_few(base_size=12) +
-  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
   xlab("Center of OpenPose Detection") + 
@@
   ggtitle("Face False Positives") + theme(legend.position = "none") +
-  scale_y_reverse()
+  scale_y_reverse() + xlim(-.05,1.05) + ylim(1.05,-.05)
 
@@
   mutate(x=left+0.5*width,
-         y=1-(top+0.5*height)) %>% # top-left is 0,0
+         y=top+0.5*height) %>% # top-left is 0,0
   ggplot(aes(x=x, y=y, fill=..level..)) + 
+  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
    theme_few(base_size=12) +
-  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
   xlab("Center of OpenPose Detection") + 
@@
   ggtitle("Hand False Positives") + theme(legend.position = "none") +
-  scale_y_reverse()
+  scale_y_reverse() + xlim(-.05,1.05) + ylim(1.05,-.05)
 
 ggpubr::ggarrange(p1, p2)
-ggsave('appendix_figs/op_falsepositives.pdf', width = 7, height = 3)
+ggsave('appendix_figs/op_falsepositives.pdf', width = 7, height = 3.4)
 
@@
 
-```{r}
-summary_by_age_days_gold <- gold_sample %>%
-  group_by(age_days,child_id) %>%
-  summarize(num_faces = sum(face_present_ketan), 
-            num_hands = sum(hand_present_ketan), 
-            num_detect = n()) %>%
-  mutate(prop_faces = num_faces / num_detect, 
-         prop_hands = num_hands / num_detect) %>%
-  select(prop_faces, prop_hands, age_days, child_id) %>%
-  pivot_longer(col = c(prop_faces, prop_hands), names_to="region", values_to = "prop")
-
-summary_by_age_days_gold$age_scale <- scale(summary_by_age_days_gold$age_days, scale = FALSE)[,1] / 30.3
-```
-
-```{r}
-
-## add face vs. hands model on gold sample to sanity check
-diff_model2_gold <- summary(lmer(prop ~ region*poly(age_scale, 2) + (1 | child_id), data = summary_by_age_days_gold))
-
-xtable(diff_model2_gold$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of faces and hands seen by infants based on human annotations.")
-
-```
-
 ## A8 Activity by Location
@@
   ggplot(aes(x=Activity, y=Location, fill=n)) +
-  geom_tile() +
+  geom_tile() + theme_few(base_size=11) +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
-ggsave('appendix_figs/activities_by_location.pdf', width = 7, height = 4)
+ggsave('appendix_figs/activities_by_location.pdf', width = 8, height = 4)
 
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+ggsave('appendix_figs/prob_activity_by_single_location.pdf', width = 8, height = 4)
 ```
@@
 
-ggsave('face_hand_by_motor.pdf', width=7, height=5)
+ggsave('appendix_figs/face_hand_by_motor.pdf', width=7, height=5)
 ```

### 2022-01-07 paper/manuscript/appendix.Rmd
add new f scores by thres plot

--- 2022-01-07 paper/manuscript/appendix.Rmd
@@
 
+ return_f_score = function(eval){
+  tp=sum(eval == "TP")
+  fp=sum(eval == "FP")
+  fn=sum(eval == "FN")
+  p = tp / (tp + fp)
+  r = tp / (tp + fn)
+  f=( 2 * p * r )/ (p + r)
+  return(f)
+ }
+
 ```
@@
   group_by(detection_threshold) %>%
-  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan))
+  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan), )
+
 ```

### 2022-01-07 paper/manuscript/appendix.Rmd

--- 2022-01-07 paper/manuscript/appendix.Rmd
@@
   ggplot(aes(x=x, y=y, fill=..level..)) + 
-  stat_density_2d(geom = "polygon") + 
   theme_few(base_size=12) +

### 2022-01-10 paper/manuscript/appendix.Rmd
add code for f scores by conf threshold, lme4 tests on gold set

--- 2022-01-07 paper/manuscript/appendix.Rmd
@@
 date: "1/6/2022"
-output: word_document
+output:
+  word_document: default
+  html_document:
+    df_print: paged
 ---
@@
 library(papaja)
+library(lme4)
+library(xtable)
+library(lmerTest)
 theme_set(theme_few())
@@
   group_by(detection_threshold) %>%
-  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan), )
+  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan), f_faces = return_f_score(face_eval_ketan), f_hands = return_f_score(hand_eval_ketan) )
 
@@
 ggsave('appendix_figs/rocs.pdf', width = 7, height = 3)
+```
+
+```{r}
+
+f_faces = ggplot(data=roc_data, aes(x=detection_threshold, y=f_faces, color=detection_threshold)) +
+  geom_point() +
+  geom_line() +
+  ylim(0,1) +
+  xlim(0,1) +
+  xlab('Detection Threshold') +
+  ylab('F-score') +
+  ggtitle('Face detections') +
+  theme(legend.position = 'none')
+
+f_hands = ggplot(data=roc_data, aes(x=detection_threshold, y=f_hands, color=detection_threshold)) +
+  geom_point() +
+  geom_line() +
+  ylim(0,1) +
+  xlim(0,1) +
+  xlab('Detection Threshold') +
+  ylab('F-score') +
+  ggtitle('Hand detections') +
+  theme(legend.position = 'none')
+
+```
+
+```{r}
+
+ggpubr::ggarrange(f_hands, f_faces, nrow=1)
+ggsave('appendix_figs/f_scores_by_thres.pdf', width = 7, height = 3)
+ggsave('appendix_figs/f_scores_by_thres.png', device = "png", width = 7, height = 3)
+
 ```
@@
            col=region)) +
-  geom_point(alpha=.2) +
+  geom_point(alpha=.5) +
+  # geom_point(alpha=.2, data = goldset) +
   geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
@@
 ggsave('appendix_figs/humans_vs_op.pdf', width = 7, height = 5)
+
+```
+
+```{r}
 

### 2022-01-10 paper/manuscript/motor_milestones_attempt.Rmd
update gitignore, figures

@@
 
-We attempted to whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the proportion of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
+We examined the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the proportion of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
 We tried including random slopes by age and milestone, but the models did not converge and/or were singular.

### 2022-01-10 paper/manuscript/appendix.Rmd

--- 2022-01-07 paper/manuscript/appendix.Rmd
@@
   group_by(detection_threshold) %>%
-  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan))
+  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan), f_faces = return_f_score(face_eval_ketan), f_hands = return_f_score(hand_eval_ketan) )
+
 ```

### 2022-04-21 paper/manuscript/manuscript_april2022_apa_blinded.Rmd
latest revisions to manuscript / figures

--- 2022-01-07 paper/manuscript/manuscript_dec2021_apa_blinded.Rmd
@@
 Finally, making use of automated annotation of pose bounding boxes, we analyze the size, location, and variability of detected faces and poses across development in these three children.
-Overall, these findings largely validate prior cross-sectional findings, and further suggest that automated annotations can be used to analyze naturalistic video datasets to build towards generalizable conclusions about the statistics of the social information in the infant view across a wide variety of populations.
+Overall, these results largely validate prior cross-sectional findings within more naturalistic learning contexts and individual children.
+These results also highlight some of the challenges of automated coding of infant egocentric headcam data, raising key areas for future computational and empirical work.
+At the same time, these findings highlight the promise of using automated annotations to analyze large, naturalistic video datasets, advancing the overarching goal of building generalizable conclusions about the statistics of the social information in the infant view across a wide variety of populations.
 
@@
 
+However, compared to prior work annotating in-lab, egocentric headcam videos, OpenPose performed somewhat less accurately: in Long et al., 2021, the F-score for faces was F = .83 (vs.
+.64 here), while the F-score for hands was F = .73 (vs.
+.51 here) (see Table 2, Long et al., 2021).
 We next inspected frames where OpenPose failed to detect faces/hands or erroneously detected them to gain insight into the factors driving performance.
@@
 Hands were sometimes erroneously detected when a pose was present but the hands were out of view, and hands were often missed when they were seen only from the side and unconnected to a pose or belonged to the child.
-One conclusion of this examination is that egocentric videos using cameras with larger view angles, higher resolution, and more lighting-invariant sensors may lead to better performance, even in the absence of better detection models.
+
+Overall, these results suggest that at-home, naturalistic videos taken with these lightweight cameras present unique challenges for applying computer vision methods that may be absent in controlled laboratory settings.
+In addition, they suggest that the development and use of head-mounted cameras with larger view angles, higher resolution, and more lighting-invariant sensors may lead to better performance, even in the absence of better detection models.
 
@@
 When we restricted detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.
+This is consistent with findings from Long et al., 2021, where restricting analyses to high-confidence detections also impaired detector performance.
 Further analyses sweeping across the entire range of possible confidence detection thresholds revealed that including all detections was the most beneficial for optimizing the rate of true positives (see Appendix Figure A4 for full ROC curves for both face and hand detections).
@@
 However, we did still see considerable variation in model accuracy across different videos, suggesting that particular recording activities, lighting conditions, or situations could cause conditions that would impair detector performance.
+For example, challenging lighting conditions in a poorly-lit room or very bright outdoor day could lead to overall lower detection accuracy, as could activities where caregivers are moving rapidly, leading to more blurred views of faces that can be difficult to detect.
 
@@
   theme_few(base_size=12) +
+  ylim(0,1) +
   facet_grid(~region) +
   # scale_color_manual(values = c( "#DAA0EE","#710D93"), name="") +
-  scale_color_brewer(palette="Dark2") +
+  scale_color_brewer(palette="Dark2", name = "Child") +
   guides(size = FALSE) +
   theme(legend.text=element_text(size=10))
+
+ggsave('figs_pdfs/face_hand_contingency.pdf', width=7, height=3, units='in')
 ```
@@
 
+ggsave('figs_pdfs/dets_by_location.pdf', width=7, height=5, units='in')
 ```
@@
   guides(size = FALSE)
+
+ggsave('figs_pdfs/size_by_age.pdf', width=7, height=3, units='in')
+```
+
+```{r}
+body_size_summary = summary(lmer(data = all_vid_bbs %>% filter(label=='pose'), log(avg_area) ~ scale(age_days) + scale(num_detect) + (1|child_id)))
+
+faces_size_summary = summary(lmer(data = all_vid_bbs %>% filter(label=='face'), log(avg_area) ~ scale(age_days) + scale(num_detect) + (1|child_id)))
+
+hands_size_summary = summary(lmer(data = all_vid_bbs %>% filter(label=='hand'), log(avg_area) ~ scale(age_days) + scale(num_detect) + (1|child_id)))
+
 ```
@@
   mutate(variable = 'Eye distance')
+```
+
+```{r}
+eye_dist_summary = summary(lmer(data = all_vid_data, avg_eye_distance ~ scale(age_days) + scale(num_frames) + (1|child_id)))
 ```
@@
 
+```{r}
+x_vs_y_summary = summary(lmer(data=CV_faces, CV ~ scale(age_day_bin) + position + scale(num_detect) +  (1|child_id)))
+
+```
+
 ```{r faceDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "(A) Average distance between eyes and (B) average coefficient of variation for the x and y position of faces detected by OpenPose as a function of each child's age at the time of filming.
@@
 cowplot::plot_grid(eye_dist_plot, CV_faces_plot, rel_widths=c(1,2))
+ggsave('figs_pdfs/detailed_changes.pdf',units='in',width=7, height=3)
 ```
@@
 Supporting this idea, we found that the averages sizes of the people, faces, and hands in the infant view became smaller over development (Figure \ref{fig:avgSizes}).
+To assess these trends, we fit three linear mixed-effect models, asking whether the average sizes of people, faces, and hands declined with children’s age, and found significant effects in each case (People, B = `r round(body_size_summary$coefficients,4)[2,1]`,
+SE = `r round(body_size_summary$coefficients,4)[2,2]`, df = `r round(body_size_summary$coefficients,4)[2,3]`, t = `r round(body_size_summary$coefficients,4)[2,4]`, 
+p = `r round(body_size_summary$coefficients,4)[2,5]`;Faces, B = `r round(faces_size_summary$coefficients,3)[2,1]`,
+SE = `r round(faces_size_summary$coefficients,4)[2,2]`, df = `r round(faces_size_summary$coefficients,4)[2,3]`, t = `r round(faces_size_summary$coefficients,4)[2,4]`,
+p = `r round(faces_size_summary$coefficients,4)[2,5]`); Hands, B = `r round(hands_size_summary$coefficients,4)[2,1]`,
+SE = `r round(hands_size_summary$coefficients,4)[2,2]`, df = `r round(hands_size_summary$coefficients,4)[2,3]`, t =`r round(hands_size_summary$coefficients,4)[2,4]`, p = `r round(hands_size_summary$coefficients,4)[2,5]`).
+
 This effect was relatively consistent across the three children in the dataset, despite the fact that the three children showed sometimes disparate overall proportions of faces/hands in view. 
@@
 Figure \ref{fig:faceDetailed}A shows the average interpupillary distance on faces as a function of each child’s age at the time of recording. 
-There was a trend from larger, closer faces (with a larger interpupillary distance) to smaller faces that were farther away (with a smaller interpupillary distance).
+There was a trend from larger, closer faces (with a larger interpupillary distance) to smaller faces that were farther away (with a smaller interpupillary distance);  this finding was confirmed in a linear-mixed effect model (B = `r round(eye_dist_summary$coefficients,4)[2,1]`, SE = `r round(eye_dist_summary$coefficients,4)[2,2]`, df = `r round(eye_dist_summary$coefficients,4)[2,3]`, t = `r round(eye_dist_summary$coefficients,4)[2,4]`, P = `r round(eye_dist_summary$coefficients,4)[2,5]`).
 
@@
 To do so, we calculated the coefficient of variation of the horizontal (x) and vertical (y) positions of centers of the faces detected by OpenPose (see Figure \ref{fig:faceDetailed}B), and examined changes across age.
-Faces tended to be more variable in the vertical than their horizontal position (see Figure \ref{fig:faceDetailed}B). 
-We also found that as children got older, they tended to see faces that varied more in their horizontal -- but not their vertical position -- suggesting that older children might be more likely to see more smaller faces in their periphery (see Figure \ref{fig:faceDetailed}B).
+Faces tended to be more variable in the vertical than their horizontal position (see Figure \ref{fig:faceDetailed}B, Main effect of position type on variability, B = `r round(x_vs_y_summary$coefficients,4)[3,1]`, SE = `r round(x_vs_y_summary$coefficients,4)[3,2]`, df = `r round(x_vs_y_summary$coefficients,4)[3,3]`, t = `r round(x_vs_y_summary$coefficients,4)[3,4]`, P = `r round(x_vs_y_summary$coefficients,4)[3,5]`).
+We also found that as children got older, they tended to see faces that varied more in their horizontal -- but not their vertical position -- suggesting that older children might be more likely to see more smaller faces in their periphery (see Figure \ref{fig:faceDetailed}B), (Main effect of age of horizontal position, B = `r round(x_pos_summary$coefficients,4)[2,1]`, SE = `r round(x_pos_summary$coefficients,4)[2,2]`, df = `r round(x_pos_summary$coefficients,4)[2,3]`, t = `r round(x_pos_summary$coefficients,4)[2,4]`, P = `r round(x_pos_summary$coefficients,4)[2,5]`; No main effect of age on vertical position, Main effect of age of horizontal position, B = `r round(y_pos_summary$coefficients,4)[2,1]`, SE = `r round(y_pos_summary$coefficients,4)[2,2]`, df = `r round(y_pos_summary$coefficients,4)[2,3]`, t = `r round(y_pos_summary$coefficients,4)[2,4]`, P = `r round(y_pos_summary$coefficients,4)[2,5]`; )
 
@@
 Going forward, we suggest that researchers continue to compare a small set of manual annotations relevant to their research questions of interest to OpenPose's performance.
+Indeed, different cameras, lighting conditions, or recording environments may change the accuracy of the detections and thus the inferences that can be made.
+In particular, we suggest that researchers continue to annotate a set of randomly sampled frames from each child across an entire dataset to assess the rates of both misses as well as false alarms.
+While we recommend at least a few thousand frames be annotated, additional annotations will allow for more precise estimates of model performance in a given dataset.
 
@@
 # Acknowledgements
-Blinded.
+Thanks to the creators of the SAYCam dataset who made this work possible and to Alessandro Sanchez for his contributions to the codebase.
+This work was funded by a Jacobs Foundation Fellowship to MCF, a John Merck Scholars award to MCF, and NSF #1714726 to BLL.
 

### 2022-07-19 paper/manuscript/appendix.Rmd
reorganization of manuscript folder & final updated figures

@@
 library(lmerTest)
+library(viridis)
 theme_set(theme_few())
@@
 
-ggsave('appendix_figs/handdensity.pdf', width = 7, height = 3)
+ggsave('figs_publication_final/figurea2_handdensity.pdf', width = 7.2, height = 3)
 ```
@@
   mutate(x=left+0.5*width,
-         y=top+0.5*height) %>% # could actually overplot all the face rectangles? prob very messy...
+         y=top+0.5*height) %>% 
   ggplot(aes(x=x, y=y, fill=..level..)) + 
-  theme_few(base_size=12) +
+  theme_few(base_size=10) +
+  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
   xlab("Center of OpenPose Detection") + 
@@
   ggplot(aes(x=x, y=y, fill=..level..)) + 
-  theme_few(base_size=12) +
+  theme_few(base_size=10) +
   stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
@@
 ggpubr::ggarrange(p1, p2)
-ggsave('appendix_figs/op_falsepositives.pdf', width = 7, height = 3.4)
+ggsave('figs_publication_final/figurea3_op_falsepositives.pdf', width = 7.2, height = 3.4)
 
@@
 face_roc = ggplot(data=roc_data, aes(x=fpr_faces, y=tpr_faces, color=detection_threshold)) +
+  theme_few(base_size=10) +
   geom_point() +
@@
   geom_point() +
+  theme_few(base_size=10) +
   geom_line() +
@@
 ggpubr::ggarrange(face_roc, hand_roc, nrow=1)
-ggsave('appendix_figs/rocs.pdf', width = 7, height = 3)
+ggsave('figs_publication_final/figurea4_rocs.pdf', width = 7.2, height = 3)
 ```
@@
 f_hands = ggplot(data=roc_data, aes(x=detection_threshold, y=f_hands, color=detection_threshold)) +
+  theme_few(base_size=10) +
   geom_point() +
@@
 ggpubr::ggarrange(f_hands, f_faces, nrow=1)
-ggsave('appendix_figs/f_scores_by_thres.pdf', width = 7, height = 3)
-ggsave('appendix_figs/f_scores_by_thres.png', device = "png", width = 7, height = 3)
+ggsave('figs_publication_final/figurea4b_fscore_by_thres.pdf', width = 7.2, height = 3)
+ggsave('figs_publication_final/f_scores_by_thres.png', device = "png", width = 7, height = 3)
 
@@
   ylim(0,1) +
-  theme_few(base_size=12) +
+  theme_few(base_size=10) +
   ylab('F-score') + xlab('Age (months)') +
   ggtitle("Face detections") + 
+  scale_color_viridis(option='viridis', discrete=TRUE, begin=.2, end=.6) +
   theme(legend.position= 'none')
@@
   ylim(0,1) +
-  theme_few(base_size=12) +
+  theme_few(base_size=10) +
   ylab('F-score') + xlab('Age (months)') +
   ggtitle("Hand detections") + 
+  scale_color_viridis(option='viridis', discrete=TRUE, begin=.2, end=.6) +
   theme(legend.position= 'none')
@@
 ggpubr::ggarrange(p1, p2, nrow=1)
-ggsave('appendix_figs/fscore_by_age_child.pdf', width = 7, height = 5)
+ggsave('figs_publication_final/figurea5_fscore_by_age_child.pdf', width = 7.2, height = 4)
 ```
@@
   geom_point(alpha=.5) +
-  theme_few(base_size=12) +
+  theme_few(base_size=10) +
   ylab('F-score') + ggtitle("Face detections") +
   theme(legend.position = 'none') +
+  # scale_color_viridis(option='mako', discrete=TRUE) +
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
@@
   geom_point(alpha=.5) +
-  theme_few(base_size=12) +
+  theme_few(base_size=10) +
   ylab('F-score') + ggtitle("Hand detections") +
   theme(legend.position = 'none') +
+  # scale_color_viridis(option='mako', discrete=TRUE) +
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
@@
 ggpubr::ggarrange(p1, p2, nrow=1)
-ggsave('appendix_figs/fscore_by_location.pdf', width = 7, height = 3)
+ggsave('figs_publication_final/figurea6_fscore_by_location.pdf', width = 7.2, height = 3)
 ```
@@
            col=region)) +
-  geom_point(alpha=.5) +
+  geom_point(alpha=.2) +
   # geom_point(alpha=.2, data = goldset) +
   geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) +
-  geom_smooth(data = goldset_adult_hands, span=10, aes(weight = num_frames_total), show.legend = FALSE,
-              lty = 2, span=10, se = FALSE) +
-  geom_smooth(data = goldset, span=10, aes(weight = num_frames_total), show.legend = FALSE,
-              lty = 3, span=10, se = FALSE) +
+  geom_smooth(data = goldset_adult_hands, span=10, aes(weight = num_frames_total), show.legend = FALSE, lty = 2, span=10, se = FALSE) +
+  geom_smooth(data = goldset, span=10, aes(weight = num_frames_total), show.legend = FALSE, lty = 3, span=10, se = FALSE) +
   ylab('Proportion Detections') + 
@@
   theme_few(base_size=10) +
-  ggthemes::scale_color_solarized(name = "") + 
+  scale_color_manual(values = c("#1266a2","#CB4B16"), name = "") +
   scale_size_continuous(name = "Detections (Log 10)") +
@@
 
-ggsave('appendix_figs/humans_vs_op.pdf', width = 7, height = 5)
-
-```
-
-```{r}
+ggsave('figs_publication_final/figurea7_humans_vs_op.pdf', width = 7.2, height = 4)
 
@@
 
-ggsave('appendix_figs/activities_by_location.pdf', width = 8, height = 4)
+ggsave('figs_publication_final/figurea8_activities_by_location.pdf', width = 7.2 , height = 4)
 
@@
 
-ggsave('appendix_figs/activities_by_single_location.pdf', width = 7, height = 4)
+ggsave('figs_publication_final/figurea8b_activities_by_single_location.pdf', width = 7.2, height = 4)
 
@@
 
-ggsave('appendix_figs/prob_activity_by_single_location.pdf', width = 8, height = 4)
+ggsave('figs_publication_final/figurea8b_prob_activity_by_single_location.pdf', width = 7.2, height = 4)
 ```
@@
   guides(size = FALSE) +
-  ggthemes::scale_color_solarized(name = "")  +
-  ggthemes::scale_fill_solarized(name = "") +
+      scale_color_manual(values = c("#1266a2","#CB4B16"), name = "") +
+      scale_fill_manual(values = c("#1266a2","#CB4B16"), name = "") +
   theme(legend.position = c(0.8, 0.1))
 
-ggsave('appendix_figs/face_hand_density.pdf', width = 7, height = 7)
+ggsave('figs_publication_final/figurea9_face_hand_density.pdf', width = 7, height = 7)
 ```
@@
   theme(legend.text=element_text(size=10)) +
-  guides(size = FALSE) +
+  guides(size = 'none') +
   theme(legend.position="bottom")
 
-ggsave('appendix_figs/face_hand_by_motor.pdf', width=7, height=5)
+ggsave('figs_publication_final/figurea10_face_hand_by_motor.pdf', width=7.2, height=5)
 ```

### 2022-07-19 paper/manuscript/manuscript_april2022_apa_blinded.Rmd
reorganization of manuscript folder & final updated figures

@@
 library(papaja)
+library(viridis)
 theme_set(theme_few())
@@
   theme_few(base_size=10) +
-  ggthemes::scale_color_solarized(name = "") + 
+  scale_color_manual(values = c("#1266a2","#CB4B16"), name = "") +
   theme(legend.text=element_text(size=10)) +
-  guides(size = FALSE) +
-  theme(legend.position="bottom") +
-  ggtitle('A.')
+  guides(size = "none") +
+  theme(legend.position="none", aspect.ratio=.75) 
+  # ggtitle('A.')
+
+  # scale_color_manual(values = c("#1266a2","#1b91e6", "#CB4B16","#eb7443"), name = "") +
 
@@
   theme_few(base_size=10) +
-  ggthemes::scale_color_solarized(name = "") + 
+  # scale_color_viridis(option = "turbo", discrete=TRUE, begin=0.05, end=.85, name="") +
+  # scale_color_manual(values = c("#92c5de","#ef8a62"), name = "") +
+      scale_color_manual(values = c("#1b91e6","#eb7443"), name = "") +
   theme(legend.text=element_text(size=10)) +
-  guides(size = FALSE) +
-  theme(legend.position="bottom")  +
-  ggtitle('B.')
+  guides(size = "none") +
+  theme(legend.position="none", aspect.ratio=.75)  
+  # ggtitle('B.')
 
@@
   theme_few(base_size=10) +
-  scale_color_manual(values = c("#751098","#142c83"), name = "") +
+  # scale_color_viridis(option = "viridis", discrete=TRUE, begin=0.3, end=.8, name="") + 
+  # scale_color_manual(values = c("#751098","#142c83"), name = "") +
+  scale_color_manual(values = c("#a21266","#142c83"), name = "") +
   theme(legend.text=element_text(size=10)) +
-  guides(size = FALSE) +
-  theme(legend.position="bottom") +
-  ggtitle('C.')
+  guides(size = "none") +
+  theme(legend.position="none", aspect.ratio=.75) 
+  # ggtitle('C.')
 
@@
 
-cowplot::plot_grid(first_panel, second_panel, third_panel, labels=NULL, nrow=3, label_fontface = "bold", align = "v", axis = "b")
-ggsave('figs_pdfs/test.pdf', width = 7, height = 9)
+cowplot::plot_grid(first_panel, second_panel, third_panel, labels='auto', nrow=3, label_fontface = "bold", align = "hv", axis = "b")
+ggsave(filename='figs_publication_final/figure2_updated.pdf', width = 7.2, height=8, dpi=300)
 ```
@@
 ```{r faceHandContingency, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of joint face and hands detection within frames where hands (left) or faces (right) were detected." }
-ggplot(face_hand_contingency, 
+ggplot(face_hand_contingency %>% filter(num_frames_total>20000), 
        aes(x=age_day_bin, y=prop, 
@@
   xlab('Age (Months)') +
-  theme_few(base_size=12) +
+  theme_few(base_size=10) +
   ylim(0,1) +
@@
   # scale_color_manual(values = c( "#DAA0EE","#710D93"), name="") +
-  scale_color_brewer(palette="Dark2", name = "Child") +
-  guides(size = FALSE) +
-  theme(legend.text=element_text(size=10))
-
-ggsave('figs_pdfs/face_hand_contingency.pdf', width=7, height=3, units='in')
+  # scale_color_brewer(palette="Dark2", name = "Child") +
+  scale_color_viridis(option='viridis', discrete=TRUE, begin=.2, end=.8) +
+  guides(size = "none") +
+  theme(legend.text=element_text(size=6), legend.position = "none")
+
+ggsave('figs_publication_final/figure3_face_hand_contingency.pdf', width=3.5, height=2.625, units='in')
 ```
@@
 ggplot(all_to_plot, aes(x = Location, y = mean, col=region)) + 
-  geom_point(aes(x=Location, y=prop, size=log10(num_detect)), alpha=.1, position = position_dodge(width=.6)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper, linetype=region),position = position_dodge(width=.6)) +
+  geom_point(aes(x=Location, y=prop, size=log10(num_detect)), alpha=.05, position = position_dodge(width=.6)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper, linetype=region),position = position_dodge(width=.8), size=.3) +
   coord_flip() + 
@@
   facet_grid(.~child_id)  + 
-  scale_size_continuous(name = "log(Detections)") +
+  scale_size_continuous(name = "") +
   scale_linetype_manual(values=c("solid", "dashed","solid","dashed"), name = "") +
-  scale_color_manual(values = c("#268bd2", "#51acec", "#dc322f","#ea5e5c"), name = "") +
-  theme(legend.text=element_text(size=8))
-
-ggsave('figs_pdfs/dets_by_location.pdf', width=7, height=5, units='in')
+  # scale_color_manual(values = c("#1a2591", "#7fb8f1", "#b9221f","#ea5e5c"), name = "") +
+  scale_color_manual(values = c("#1266a2","#1b91e6", "#CB4B16","#eb7443"), name = "") +
+  theme(legend.text=element_text(size=8)) +
+  guides(size = "none")
+
+ggsave('figs_publication_final/figure4_dets_by_location.pdf', width=7.2, height=5, units='in')
 ```
@@
 ggplot(avg_area_by_age, aes(x=age_day_bin, y=log(avg_area), col=child_id, size=num_detect)) +
-  theme_few(base_size=12) +
+  theme_few(base_size=10) +
   geom_point(alpha=.1) +
   facet_grid(~label) +
-  geom_smooth(method='lm') + 
+  theme(text=element_text(family="Helvetica"))  +
+  geom_smooth(method='lm', size=1) + 
   ylab('Log area (average proportion of frame)') +
   xlab('Age (in months)') +
-  scale_color_brewer(palette="Dark2", name = "Child") +
-  guides(size = FALSE)
-
-ggsave('figs_pdfs/size_by_age.pdf', width=7, height=3, units='in')
+  # scale_color_brewer(palette="Dark2", name = "Child") +
+  theme(legend.position='none') +
+  scale_color_viridis(option='viridis', discrete=TRUE, begin=.2, end=.8) +
+  guides(size = "none")
+
+ggsave('figs_publication_final/figure5_size_by_age.pdf', width=3.5, height=2.625, units='in')
 ```
@@
   xlab('Age (in months)') +
-  theme_few(base_size=12) +
+  theme_few(base_size=10) +
   facet_grid(~variable) +
-  scale_color_brewer(palette="Dark2", name='Child') +
-  guides(size = FALSE) +
-  ggtitle('A.') +
+  # scale_color_brewer(palette="Dark2", name='Child') +
+    scale_color_viridis(option='viridis', discrete=TRUE, begin=.2, end=.8) +
+  guides(size = 'none') +
+  # ggtitle('A.') +
   theme(legend.text=element_text(size=12))  +
@@
 CV_faces_plot <- ggplot(CV_faces, aes(x=age_day_bin, y = CV, size=num_detect, color=child_id)) +
-  theme_few(base_size=12) +
+  theme_few(base_size=10) +
   geom_point(alpha=.15) + 
@@
   geom_smooth(method='lm') +
-  ggtitle('B.') +
-  scale_color_brewer(palette='Dark2', name='Child') + 
+  # ggtitle('B.') +
+  # scale_color_brewer(palette='Dark2', name='Child') +
+  scale_color_viridis(option='viridis', discrete=TRUE, begin=.2, end=.8) +
+  theme(legend.position='none') +
     ylab('Coefficient of variation') +
   xlab('Age (in months)') +
-  guides(size = FALSE) 
+  guides(size = 'none') 
 ```
@@
 
-cowplot::plot_grid(eye_dist_plot, CV_faces_plot, rel_widths=c(1,2))
-ggsave('figs_pdfs/detailed_changes.pdf',units='in',width=7, height=3)
+cowplot::plot_grid(eye_dist_plot, CV_faces_plot, labels='AUTO', rel_widths=c(1,2))
+ggsave('figs_publication_final/figure6_detailed_changes.pdf',units='in',width=7, height=3)
 ```

### 2022-07-19 paper/manuscript/appendix.Rmd
last edits to figures/ms in first stage of proofs

@@
 ## A3 Location of OpenPose False Positives
-Below we visualize the locations of the 1229 faces (in 1093 frames) that OpenPose detected in the gold set frames that were not actually there, as well as the 1778 OpenPose false positive hands (in 1237 frames) from the gold set.
+
+```{r}
+load(here::here('data/preprocessed_data_2022/gold_sample_all_indiivdual_dets.RData'))
+
+ddd <- gold_sample_all_dets %>%  # has bounding box info
+  left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan)) %>%
+    mutate(x=left+0.5*width, y=top+0.5*height)  # gold_sample has manual annotations merged
+
+fp_faces <-  ddd %>% 
+  filter(face_eval_ketan=="F", label=="face")
+
+fp_hands <-  ddd %>% 
+  filter(hand_eval_ketan=="FP", label=="hand") 
+```
+
+Below we visualize the locations of the `r length(fp_faces)` faces in `r length(unique(fp_faces$frame))` frames that OpenPose detected in the gold set frames that were not actually there, as well as the `r length(fp_hands)`  OpenPose false positive hands (in `r length(unique(fp_hands$frame))` frames) from the gold set.
 The average location of OpenPose's false positives for both faces (left) and hands (right) are somewhat more common in the center of the frame, but some are scattered across the frame.
@@
 ```{r density-op-fps, fig.width=6.5, fig.height=3.2, fig.cap="Density plot of the locations of false positives for OpenPose detections for faces (left) and hands (right) in the gold set."}
-load(here::here('data/preprocessed_data_2022/gold_sample_all_indiivdual_dets.RData'))
-ddd <- gold_sample_all_dets %>% left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan))
 
 # density plot of OP's false positive face/hand locations
-p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
-  mutate(x=left+0.5*width,
-         y=top+0.5*height) %>% 
+p1 <- fp_faces %>%
   ggplot(aes(x=x, y=y, fill=..level..)) + 
@@
 
-p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
-  mutate(x=left+0.5*width,
-         y=top+0.5*height) %>% # top-left is 0,0
+p2 <- fp_hands %>%
   ggplot(aes(x=x, y=y, fill=..level..)) + 
@@
 
-ggsave('figs_publication_final/figurea8_activities_by_location.pdf', width = 7.2 , height = 4)
+# ggsave('figs_publication_final/figurea8_activities_by_location.pdf', width = 7.2 , height = 4)
 
@@
   geom_tile() +
+  theme_few(base_size=10) +
+  scale_fill_continuous(name = "Count") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
-ggsave('figs_publication_final/figurea8b_activities_by_single_location.pdf', width = 7.2, height = 4)
+ggsave('figs_publication_final/figurea8a_activities_by_single_location.pdf', width = 7.2, height = 4)
 
@@
 # normalize by location
+loc_freq_out = loc_freq
 meta_long_1loc %>% 
-  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
   left_join(meta_long_1loc %>% group_by(Location) %>% summarise(loc_freq = n())) %>%
@@
             prop_loc = n / loc_freq) %>% 
+  mutate(Location = factor(Location, levels=names(loc_freq_out))) %>%
   ggplot(aes(x=Activity, y=Location, fill=prop_loc)) +
   geom_tile() +
+  theme_few(base_size=10) +
+  scale_fill_continuous(name = "Prob.") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))

### 2022-07-19 paper/manuscript/manuscript_july2022_apa_final.Rmd
last edits to figures/ms in first stage of proofs

--- 2022-07-19 paper/manuscript/manuscript_april2022_apa_blinded.Rmd
@@
 Faces tended to be more variable in the vertical than their horizontal position (see Figure \ref{fig:faceDetailed}B, Main effect of position type on variability, B = `r round(x_vs_y_summary$coefficients,4)[3,1]`, SE = `r round(x_vs_y_summary$coefficients,4)[3,2]`, df = `r round(x_vs_y_summary$coefficients,4)[3,3]`, t = `r round(x_vs_y_summary$coefficients,4)[3,4]`, P = `r round(x_vs_y_summary$coefficients,4)[3,5]`).
-We also found that as children got older, they tended to see faces that varied more in their horizontal -- but not their vertical position -- suggesting that older children might be more likely to see more smaller faces in their periphery (see Figure \ref{fig:faceDetailed}B), (Main effect of age of horizontal position, B = `r round(x_pos_summary$coefficients,4)[2,1]`, SE = `r round(x_pos_summary$coefficients,4)[2,2]`, df = `r round(x_pos_summary$coefficients,4)[2,3]`, t = `r round(x_pos_summary$coefficients,4)[2,4]`, P = `r round(x_pos_summary$coefficients,4)[2,5]`; No main effect of age on vertical position, Main effect of age of horizontal position, B = `r round(y_pos_summary$coefficients,4)[2,1]`, SE = `r round(y_pos_summary$coefficients,4)[2,2]`, df = `r round(y_pos_summary$coefficients,4)[2,3]`, t = `r round(y_pos_summary$coefficients,4)[2,4]`, P = `r round(y_pos_summary$coefficients,4)[2,5]`; )
+We also found that as children got older, they tended to see faces that varied more in their horizontal -- but not their vertical position -- suggesting that older children might be more likely to see more smaller faces in their periphery (see Figure \ref{fig:faceDetailed}B), (Main effect of age of horizontal position, B = `r round(x_pos_summary$coefficients,4)[2,1]`, SE = `r round(x_pos_summary$coefficients,4)[2,2]`, df = `r round(x_pos_summary$coefficients,4)[2,3]`, t = `r round(x_pos_summary$coefficients,4)[2,4]`, P = `r round(x_pos_summary$coefficients,4)[2,5]`; No main effect of age on vertical position, B = `r round(y_pos_summary$coefficients,4)[2,1]`, SE = `r round(y_pos_summary$coefficients,4)[2,2]`, df = `r round(y_pos_summary$coefficients,4)[2,3]`, t = `r round(y_pos_summary$coefficients,4)[2,4]`, P = `r round(y_pos_summary$coefficients,4)[2,5]`).
 
@@
 
-An analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations (see Appendix, Figure S7) and between individual children.
+An analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations (see Figure 4 and Appendix, Figure A8) and between individual children.
 Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations. 
